### 2017-04-24 notes/initial_writeup/paper.tex
no message

\documentclass[sigconf]{acmart}

% BEGIN ACM HEADER

\usepackage{booktabs} % For formal tables
\usepackage{balance} % For balanced columns on the last page

% Copyright
\setcopyright{acmlicensed}

% DOI - Replace your DOI below...
\acmDOI{}

% ISBN - Replace your conference/workshop's ISBN below...
\acmISBN{}

% SELECT YOUR CONFERENCE/WORKSHOP BELOW...
\acmConference[]{}{}{}

\acmYear{2017}
\copyrightyear{2017}

\acmPrice{}

% END ACM HEADER

\usepackage{epstopdf}
\usepackage{url}

\usepackage{tikz}
\usetikzlibrary{shadows,shapes}
\usepackage{pgfplots}
\pgfplotsset{compat=1.10}

\usepackage{xcolor}
\usepackage{colortbl}
\definecolor{Gray}{gray}{0.90}

\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}

\usepackage[textsize=small]{todonotes}
\newcommand{\TODO}[1]{\todo[inline]{#1}}

\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

\newcommand{\vect}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\vpi}[0]{\vect{\pi}}

\newcommand{\calA}[0]{\ensuremath{\mathcal{A}}}
\newcommand{\calC}[0]{\ensuremath{\mathcal{C}}}
\newcommand{\calS}[0]{\ensuremath{\mathcal{S}}}

\begin{document}

\title[Blockchain as Middleware Services for Transactive Energy Applications]{Blockchain as Middleware Services for\\Transactive Energy Applications}

\author{Aron Laszka}
\affiliation{%
  \institution{Vanderbilt University}
  \city{Nashville} 
  \state{Tennessee} 
  \postcode{37212}
}
\email{aron.laszka@vanderbilt.edu}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{A. Laszka et al.}

\begin{abstract}
We develop a set of powerful and novel distributed market middleware services that enable local prosumers (a consumer with renewable generation capability) to trade with each other, as well as to bid for power resources, while following the suggested timing constraints.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002951.10003227</concept_id>
<concept_desc>Information systems~Information systems applications</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10003456.10003462.10003544</concept_id>
<concept_desc>Social and professional topics~Commerce policy</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10010583.10010662.10010663</concept_id>
<concept_desc>Hardware~Energy generation and storage</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10010583.10010662.10010674</concept_id>
<concept_desc>Hardware~Power estimation and optimization</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[300]{Information systems~Information systems applications}
\ccsdesc[300]{Social and professional topics~Commerce policy}
\ccsdesc[300]{Hardware~Energy generation and storage}
\ccsdesc[300]{Hardware~Power estimation and optimization}

\keywords{Transactive microgrid, blockchain}

\maketitle

%\section{Introduction}

\section{Architecture Overview}

\begin{figure}[h!]
\begin{tikzpicture}[
  x=1.04cm,
  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.04cm, shadow yshift=-0.05cm, fill=black}}]

\draw [fill=blue!5, nodeStyle] (0, 3.07) rectangle (1.55, 3.93) node [midway, align=center, font=\small] {Trading\\[-0.2em]Node};
\draw [fill=blue!5, nodeStyle] (1.65, 3.07) rectangle (3.15, 3.93) node [midway, align=center, font=\small] {Ledger\\[-0.2em]Node};
\draw [fill=blue!5, nodeStyle] (3.25, 3.07) rectangle (4.75, 3.93) node [midway, align=center, font=\small] {Prosumer\\[-0.2em]Node};
\draw [fill=blue!5, nodeStyle] (4.85, 3.07) rectangle (6.35, 3.93) node [midway, align=center, font=\small] {Smart Meter\\[-0.2em]Node};
\draw [fill=blue!5, nodeStyle] (6.45, 3.07) rectangle (8.0, 3.93) node [midway, align=center, font=\small] {DSO\\[-0.2em]Node};

\draw [fill=red!5, nodeStyle] (0, 2.07) rectangle (3.95, 2.93) node [midway] {Trading Platform};
\draw [fill=red!5, nodeStyle] (4.05, 2.07) rectangle (8, 2.93) node [midway] {Distributed Ledger};

\draw [fill=green!5, nodeStyle] (0, 1.07) rectangle (3.95, 1.93) node [midway] {RIAPS};
\draw [fill=green!5, nodeStyle] (4.05, 1.07) rectangle (8, 1.93) node [midway] {Cryptographic Libraries};

\draw [fill=black!5, nodeStyle] (0, 0.07) rectangle (8, 0.93) node [midway] {Operating System};
\end{tikzpicture}
\caption{High-level software architecture.}
\label{fig:softwareArchitecture}
\end{figure}

Figure~\ref{fig:softwareArchitecture} shows a high-level overview of the software architecture of our system.
Our system is -- in part -- built on the Resilient Information Architecture for Smart Grid (RIAPS) platform~\cite{eisele2017riaps}.

Figure~\ref{fig:logicalNodeArchitecture} shows a high-level overview of the trading platform, the distributed ledger, and the logical nodes implementing and interacting with these subsystems.

\paragraph{Trading Platform}
Although individual prosumers trade energy with each other, for the sake of scalability, we need a trading platform that enables prosumers to find trade partners.
By serving as a database for energy bids, the trading platform relieves prosumer nodes from communicating with all potential trade partners.~%
\footnote{Note that prosumers are not required to use the services of the trading platform, and they are allowed to communicate with each other for the sake of finding trade partners.
However, in a microgrids with a large number prosumers, the trading platform will be able to find partners more efficiently and promptly.}
In addition to receiving and storing bids from prosumers, the trading platform can also find matches and notify the prosumers of the opportunity to make an energy trade.
Even though the trading platform appears to the nodes as one entity, for the sake of scalability and reliability, it can be implemented in a distributed manner, using multiple trading nodes.

\paragraph{Distributed Ledger}
The distributed ledger stores transactions that specify energy trades, record energy production and consumption, and change regulatory policies for the microgrid, including energy prices.
Since the ledger is maintained by multiple ledger nodes, a key implementation requirement is reaching consensus on which transactions are valid and stored in the ledger.
This consensus must be reached quickly, reliably, and securely even in the presence of erroneous or even malicious ledger nodes.
We treat the consensus algorithm as a pluggable module, which can be based on blockchains with proof-of-stake consensus or Practical Byzantine Fault Tolerance algorithm~\cite{castro1999practical}.

\begin{figure}[h!]
\begin{tikzpicture}[
  x=1.6cm,
  font=\small,
  nodeStyle/.style={fill=white, draw=black, drop shadow=black!30, minimum size=0.5cm},
  arrowStyle/.style={->, >=stealth, shorten >=1.5pt, shorten <=1.5pt},
  transactionStyle/.style={draw, align=center, fill=black!10, font=\footnotesize}]
\draw [->, >=stealth] (0.6, 0) -- (5.4, 0) node [right] {time};

\foreach \pos in {1, 2, 3, 4, 5}
  \draw (\pos, 0.06cm) -- (\pos, -0.06cm);

\foreach \pos/\name in {{1/$T-2$}, {2/$T-1$}, {3/$T$}, {4/$T+1$}}
  \draw[decorate, decoration={brace,amplitude=0.15cm}, yshift=-0.12cm] ({\pos+0.95}, 0) -- ({\pos+0.05}, 0) node [midway, below=0.15cm, font=\small] {\name};

\node [nodeStyle, rounded corners=0.1cm] (prosumer) at (1.5, 1.5) {};
\node [nodeStyle, diamond] (smartmeter) at (4.5, 1.5) {};

\node [above=-0.05cm of prosumer] {prosumer};
\node [above=0cm of smartmeter] {smartmeter};

\node [transactionStyle] (financial) at (1.5, 0.5) {financial\\[-0.25em]transaction};
\node [transactionStyle] (energy) at (4.5, 0.5) {energy\\[-0.25em]transaction};

\draw [arrowStyle] (prosumer) -- (financial);
\draw [arrowStyle] (smartmeter) -- (energy);

\draw [arrowStyle, dashed] (financial) -- (3.25, 0.5) node [midway, above] {promise} -- (3.25, 0);
\draw [arrowStyle, dashed] (energy) -- (3.5, 0.5) node [midway, above] {record} -- (3.5, 0);
\end{tikzpicture}
\caption{Basic timeline of transactions.}
\label{fig:timeline}
\end{figure}

Time is divided into fixed-length intervals, and energy trades are specified with respect to these intervals: financial transactions promise to consume or produce a certain amount of energy in a future interval, while energy transactions record the actual amount of energy produced or consumed in an earlier interval. 
Figure~\ref{fig:timeline} shows a basic timeline of financial and energy transactions.

\begin{figure*}
\begin{tikzpicture}[
  x=1cm, 
  y=1cm,
  nodeStyle/.style={fill=white, draw=black, drop shadow=black!30, minimum size=0.5cm}]

% trading nodes
\begin{scope}[xshift=1cm]

\foreach \name/\x/\y in {{t1/0/0}, {t2/1/1.4}, {t3/2/0}}
  \node [regular polygon, regular polygon sides=5, nodeStyle] (\name) at (\x,\y) {};

\foreach \name/\x/\y in {{tAnchorRight/2.5/0.7}}
  \coordinate (\name) at (\x,\y);

\foreach \from/\to in {{t1/t2}, {t2/t3}, {t3/t1}}
  \draw [<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt] (\from) -- (\to);

\draw [decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm] (2.25, 0) -- (-0.25, 0) node [midway, below=0.2cm] {trading nodes};
\end{scope}

% prosumer nodes
\begin{scope}[xshift=6cm]

\foreach \name/\x/\y in {{p1/0/0}, {p2/1.4/0}, {p3/0/1.4}, {p4/1.4/1.4}}
  \node [nodeStyle, rounded corners=0.1cm] (\name) at (\x,\y) {};

\foreach \name/\x/\y in {{pAnchorLeft/-0.6/0.7}, {pAnchorRight/2/0.7}}
  \coordinate (\name) at (\x,\y);

\foreach \from/\to in {{p1/p2}, {p1/p3}, {p1/p4}, {p2/p3}, {p2/p4}, {p3/p4}}
  \draw [<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt, dashed] (\from) -- (\to);

\draw [decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm] (1.65, 0) -- (-0.25, 0) node [midway, below=0.2cm] {prosumer nodes};

\end{scope}

% smart-meter nodes
\begin{scope}[xshift=6cm, yshift=2.7cm]

\foreach \name/\x/\y in {{m1/0/0}, {m2/1.4/0}, {m3/0/1.4}, {m4/1.4/1.4}}
  \node [diamond, nodeStyle] (\name) at (\x,\y) {};

\foreach \name/\x/\y in {{mAnchorRight/2/0.7}}
  \coordinate (\name) at (\x,\y);

\foreach \from/\to in {{m1/m2}, {m1/m3}, {m1/m4}, {m2/m3}, {m2/m4}, {m3/m4}}
  \draw [<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt, dashed] (\from) -- (\to);

\draw [decorate, decoration={brace,amplitude=0.2cm}, yshift=0.4cm] (-0.25, 1.4) -- (1.65, 1.4) node [midway, above=0.2cm] {smart-meter nodes};

\end{scope}

% ledger nodes
\begin{scope}[xshift=11.5cm]

\foreach \name/\x/\y in {{l1/0/0}, {l2/1/1.4}, {l3/2/0}}
  \node [circle, nodeStyle] (\name) at (\x,\y) {};

\foreach \name/\x/\y in {{lAnchorLeft/-0.5/0.7}, {lAnchorTopLeft/0/1.6}, {lAnchorTopRight/1.6/1.0}}
  \coordinate (\name) at (\x,\y);

\foreach \from/\to in {{l1/l2}, {l2/l3}, {l3/l1}}
  \draw [<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt] (\from) -- (\to);

\draw [decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm] (2.25, 0) -- (-0.25, 0) node [midway, below=0.2cm] {ledger nodes};

\end{scope}

% additional nodes

\node [ellipse, nodeStyle] (dso) at (15.5cm, 3.0cm) {DSO node};

\draw [->, very thick, >=stealth, bend right=10, shorten <=0.5cm, shorten >=0.5cm] (dso) to node [midway, above left=0.0cm, align=center] {regulatory\\[-0.25em]transactions} (lAnchorTopRight);
\draw [<-, very thick, >=stealth, bend left=10, shorten <=0.5cm, shorten >=0.5cm] (dso) to node [midway, below right=0.0cm, align=center] {ledger status} (lAnchorTopRight);

% connections between systems
\draw [<-, very thick, >=stealth, bend left=5] ([yshift=0.0cm]tAnchorRight) to node [midway, above=0.1cm] {bids} ([yshift=0.0cm]pAnchorLeft);
\draw [->, very thick, >=stealth, bend right=5] ([yshift=-0.4cm]tAnchorRight) to node [midway, below=0.1cm] {matches} ([yshift=-0.4cm]pAnchorLeft);

\draw [->, very thick, >=stealth, bend left=5] ([yshift=0.0cm]pAnchorRight) to node [midway, above=0.1cm, align=center] {financial\\[-0.25em]transactions} ([yshift=0.0cm]lAnchorLeft);
\draw [<-, very thick, >=stealth, bend right=5] ([yshift=-0.4cm]pAnchorRight) to node [midway, below=0.1cm] {ledger status} ([yshift=-0.4cm]lAnchorLeft);

\draw [->, very thick, >=stealth, bend left=15] ([yshift=0.2cm]mAnchorRight) to node [midway, above right=0.0cm, align=center] {energy\\[-0.25em]transactions} ([yshift=0.2cm]lAnchorTopLeft);
\draw [<-, very thick, >=stealth, bend right=-5] ([yshift=-0.2cm]mAnchorRight) to node [midway, below left=0.0cm] {ledger status} ([yshift=-0.2cm]lAnchorTopLeft);

\end{tikzpicture}
\caption{High-level logical architecture of the trading platform and the distributed ledger. A physical node may implement multiple logical nodes.}
\label{fig:logicalNodeArchitecture}
\end{figure*}

\begin{table*}
\caption{Logical Node Types}
\label{tab:logicalNodeTypes}
\begin{tabular}{|c||l|l|l|}
\hline
\textbf{Type} & \textbf{Function} & \textbf{Cardinality} & \textbf{Physical node} \\
\hline\hline
\rowcolor{Gray} Ledger      & maintain distributed ledger                 & one or more           & any node (with enough computational power) \\ \hline
                Trading     & provide trading platform                    & one or more           & any node (with enough computational power) \\ \hline
\rowcolor{Gray} Prosumer    & trade electricity (on behalf of a prosumer) & one for each prosumer & smart inverter or smart meter \\ \hline
                Smart meter & record power consumption and production     & one for each prosumer & smart meter (must be trusted hardware) \\ \hline
\rowcolor{Gray} DSO         & regulate microgrid electricity market       & one                   & node owned by the DSO \\ \hline
\end{tabular}
\end{table*}

\subsection{Logical Nodes}

Next, we discuss the five types of logical nodes in our system: ledger, trading, prosumer, smart meter, and DSO nodes.
Table~\ref{tab:logicalNodeTypes} shows an overview of these logical-node types.

Every node has a pair of public and private keys as well as a digital certificate from the DSO, which proves the ownership of the public key.
The nodes can use the key pair and the certificate prove their identity and to sign messages or transactions.
A digital certificate may also specify the capabilities of a node.
For example, the certificate of a prosumer node may specify the amount of energy that the node is allowed to trade for a single time interval.

\subsubsection{Ledger nodes}
Ledger nodes implement the distributed ledger by forming a peer-to-peer network with each other and reaching a consensus on the state of the ledger.
A ledger node is responsible for receiving financial transactions from prosumer nodes, energy transactions from smart-meter nodes, and regulatory transactions from the DSO node.
The ledger nodes share these transactions with each other, verify them, and reach a consensus on which transactions are recorded in the ledger.

\subsubsection{Trading nodes}
Trading nodes implement the distributed trading platform by forming a peer-to-peer network with each other and providing services for prosumer nodes.
A trading node is responsible for receiving bids from prosumer nodes, sharing these bids with the other trading nodes, maintaining a distributed database of active bids, trying to match bids with each other, and notifying the prosumers of matches.
While this platform is similar to the distributed ledger in many ways, it is subject to much less stringent requirements.
For example, the trading platform does not have to store history in a reliable and verifiable manner.
Consequently, trading nodes can be implemented by computationally less capable physical nodes (e.g., with limited storage).

\begin{table*}
\caption{Transaction Types}
\label{tab:transactionTypes}
\begin{tabular}{|c||l|l|p{5.8cm}|}
\hline
\textbf{Type} & \textbf{Creator} & \textbf{Contents} & \textbf{Validity} \\
\hline\hline
\rowcolor{Gray} Financial  & prosumers    & identifiers, signatures, time interval, amount of energy & signed by buyer and seller, abides by the safety and security rules \\ \hline
                Energy     & smart meters & identifier, signature, time interval, amount of energy   & signed by smart meter \\ \hline
\rowcolor{Gray} Regulatory & DSO          & signature, time interval, set of policy updates            & signed by DSO \\ \hline
\end{tabular}
\end{table*}

\subsubsection{Prosumer nodes}
Each prosumer node represents a prosumer, such as a residential customer.
A prosumer node trades future electricity consumption and production on behalf of the prosumer.
As a first step in electricity trading, the prosumer node estimates the net energy demand of the prosumer for a future time interval.
At the same time, it queries the active regulatory policies, such as energy prices, from the distributed ledger.
Based on the estimated net demand and the active regulatory policies, it creates an energy trading bid, which it then submits to the trading platform.
If the trading platform responds with one (or more) matching bid, then the prosumer node contacts the node that submitted a matching bid.
The two nodes negotiate, agree on, create, and sign a new financial transaction, which they then submit to the distributed ledger.
Once the ledger has verified and recorded the transaction, the electricity trade has been set up.

\subsubsection{Smart-meter nodes}
Each smart-meter node measures the actual energy production and consumption of a prosumer.
For each time interval, the smart-meter node measures the net energy consumption of the prosumer, records the net consumption in an energy transaction, and then signs the transaction and submits it to the distributed ledger.
To ensure that the smart-meter node measures the correct amount of net consumption, the node must always be implemented by a trusted smart meter deployed at the prosumer.
Furthermore, we assume that the smart-meter devices are tamper-proof hardware, which prevents tampering attacks by the prosumers (e.g., to avoid paying for electricity).

\subsubsection{DSO node}
The DSO node represents the Distribution System Operator, and it is responsible for regulating the microgrid market using regulatory transactions.
These transactions enable the DSO, for example, to set a price policy for the microgrid or to remove misbehaving nodes by revoking their certificates.
Note that in order to enhance reliability and security, the DSO node may be split into multiple logical nodes.
For example, the DSO node can be split into a pricing node, which is authorized and responsible for setting the price policy, and a revocation node, which is authorized and responsible for revoking digital certificates.

\subsection{Transactions}

Transactions on the distributed ledger can be divided into three main types: financial, energy, and regulatory transactions.
Table~\ref{tab:transactionTypes} shows an overview of these transaction types.

\subsubsection{Financial Transactions}
A financial transaction represents an agreement between two prosumers, called the seller and the buyer, who promise to respectively produce and consume a certain amount of energy in a future time interval.

A financial transaction contains the following fields:
\begin{itemize}
\item \textbf{Seller ID}: Unique identifier of the selling prosumer node.
\item \textbf{Buyer ID}: Unique identifier of the buying prosumer node.
\item \textbf{Monetary value}: Value paid by the buyer to the seller, which can be denominated in either a fiat currency (e.g., US dollars) or a cryptocurrency.
\item \textbf{Time interval}: Identifier of the time interval in which energy will be produced and consumed.
\item \textbf{Energy value}: Amount of energy produced by the seller and consumed by the buyer.
\item \textbf{Seller signature}: Digital signature created using the private key of the seller, computed over all previous fields.
\item \textbf{Buyer signature}: Digital signature created using the private key of the seller, computed over all previous fields except the seller signature.
\end{itemize}

The ledger nodes accept and record a financial transaction if
\begin{itemize}
\item both signatures are valid,
\item time interval is in the future,
\item transaction abides by the safety and security rules set by the DSO (we will discuss these rules in detail later).
\end{itemize}

\subsubsection{Energy Transactions}
An energy transaction records the actual amount of energy consumed and produced by a prosumer in a past time interval.

An energy transaction contains the following fields:
\begin{itemize}
\item \textbf{Smart-meter ID}: Unique identifier of the smart meter.
\item \textbf{Energy value}: Net amount of energy consumed by the prosumer, which is computed as the difference between the consumption and the production of the prosumer (note that it may be a negative value if the prosumer produced more than its consumption).
\item \textbf{Time interval}: Identifier of the time interval in which energy consumption and production were measured.
\item \textbf{Smart-meter signature}: Digital signature created using the private key of the smart meter, computed over all previous fields.
\end{itemize}

The ledger nodes accept and record an energy transaction if
\begin{itemize}
\item signature is valid
\item time interval is in the past.
\end{itemize}

\subsubsection{Regulatory Transactions}
A regulatory transaction changes the set of active policies which all transactions are subject to.
To provide elaborate tools for regulating a microgrid, our system may support a variety of intricate regulatory transactions.
Here, we discuss two transactions that are necessary for regulating any microgrid market: price-policy and certificate-revocation transactions.

\paragraph{Price policy}
A price-policy transaction changes the active price policy of the DSO for the microgrid.
A price policy specifies how much a prosumer will have to pay to the DSO for the difference between its promised and actual net consumption.

A price-policy transaction contains the following fields:
\begin{itemize}
\item \textbf{Time interval}: Identifier of the time interval from which the new price policy will be active.
\item \textbf{Price policy}: Specification of the new price policy.
\item \textbf{DSO signature}: Digital signature created using the private key of the DSO, computed over all previous fields.
\end{itemize}

The ledger nodes accept and record a price-policy transaction if
\begin{itemize}
\item signature is valid
\item time interval is in the future.
\end{itemize}

\paragraph{Certificate Revocation}
A certificate-revocation transaction revokes some of the digital certificates that were issued to the nodes.
After a certificate has been revoked, ledger nodes will no longer accept digital signatures created using key pairs whose ownership was proven by the certificate.

A certificate-revocation transaction contains the following fields:
\begin{itemize}
\item \textbf{Time interval}: Identifier of the time interval in which the certificate is revoked.
\item \textbf{List of certificates}: Certificates to be revoked.
\item \textbf{DSO signature}: Digital signature created using the private key of the DSO, computed over all previous fields.
\end{itemize}

The ledger nodes accept and record a certificate-revocation transaction if
\begin{itemize}
\item signature is valid
\item time interval is in the future.
\end{itemize}

\section{Related Work}

Microsoft Azure Blockchain as a Service (BaaS) and Project Bletchley~\cite{gray2016introducing}.

Hyperledger Fabric~\cite{hyperledger2017fabric}.

Interledger~\cite{thomas_protocol}.

Bitcoin Lightning Network~\cite{poon2016bitcoin}.

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}

### 2017-04-27 notes/initial_writeup/paper.tex
no message

@@
 Every node has a pair of public and private keys as well as a digital certificate from the DSO, which proves the ownership of the public key.
-The nodes can use the key pair and the certificate prove their identity and to sign messages or transactions.
+The nodes can use the key pair and the certificate to prove their identity and to sign messages or transactions.
 A digital certificate may also specify the capabilities of a node.
 For example, the certificate of a prosumer node may specify the amount of energy that the node is allowed to trade for a single time interval.
+% physical node certificates may also describe roles that may be taken by the physical node
+% In addition to capabilities, the certificate may also describe roles, that is, logical nodes that can be implemented by the physical node.
 
@@
 
+\subsection{Privacy}
+
+Depending on the level of privacy that must be provided, the proposed system may be implemented in multiple ways.
+Here, we describe and discuss two approaches, called open and private systems, which are corner cases with respect to privacy.
+
+\subsubsection{Open System}
+This approach is aimed at cases when privacy within a microgrid is not a concern, and we can design the system to maximize its efficiency.
+\begin{itemize}
+\item We allow any physical node to become a trading or ledger node.
+This enhances reliability -- and potentially performance -- as the trading platform and distributed ledger can be implemented by a large set of physical nodes.
+\item The distributed ledger is public within the microgrid, which means that any node can query and receive the complete list of validated and recorded transactions.
+\end{itemize}
+% Advantages: easier accountability and reliability
+
+\subsubsection{Private System}
+This approach is aimed at cases when privacy is a crucial requirement, for example, when the DSO and the microgrid are legally required to provide privacy.
+% goal: hide any personal information
+\begin{itemize}
+\item We allow only a limited set of physical nodes to act as ledger or trading nodes. This constraint can be enforced through limiting the roles of a node within its certificate.
+\item The distributed ledger is private.
+When a node queries the status of the ledger, it will only receive 1) regulatory transactions, 2) aggregate information regarding expected consumption and production in future time steps, 3) list of transactions in which the node is involved.
+\end{itemize}
+To further enhance security, we can also enable the trading platform to mediate between prosumers who would like to trade energy.
+With the help of the trading platform, two prosumer nodes can create a financial transaction without learning each other's identity, and this transaction can then be submitted to the ledger by the trading platform.
+
+\subsection{Transaction Validation and Interpretation}
+
+Here, we discuss the validation and interpretation rules of financial and energy transactions.
+First, we detail the decision process of the ledger nodes that determines which transaction are valid and recorded in the distributed ledger.
+Second, we explain how the financial and energy transactions can be aggregated to determine the financial balance of a prosumer.
+
+Validation of Financial Transactions: Safety and Security
+
+First, the ledger nodes reach consensus on the order of the incoming transaction.
+Second, they reach consensus on validity of the ordered transaction.
+They determine the validity of the transactions one-by-one, making a decision for a transaction based on its contents and the contents of the valid preceding transactions.
+
+The certificate of each prosumer specifies the net amount of energy that the prosumer may trade for a single time step.
+More specifically, the certificate of prosumer $p$ states
+- net energy that prosumer $p$ may purchase $MaxNetBuy_p$
+- net energy that prosumer $p$ may sell $MaxNetSell_p$.
+
+To determine whether an incoming financial transaction is valid, the ledger nodes take the following steps:
+- let $T$ be the time step of the incoming transaction, and let $p_b$ and $p_s$ be the buying and selling prosumer, respectively;
+- let $NetBuy \gets 0$;
+- for every valid transaction on the ledger, if the tilmestep is $T$ and the buyer is $p_b$, then add the energy amount to $NetBuy$;
+- for every valid transaction on the ledger, if the tilmestep is $T$ and the seller is $p_b$, then subtract the energy amount from $NetBuy$;
+- let $NetSell \gets 0$;
+- for every valid transaction on the ledger, if the tilmestep is $T$ and the seller is $p_s$, then add the energy amount to $NetSell$;
+- for every valid transaction on the ledger, if the tilmestep is $T$ and the buyer is $p_s$, then subtract the energy amount from $NetSell$;
+- if $NetBuy \leq MaxNetBuy_{p_b}$, $NetSell \leq MaxNetSell_{p_s}$, signatures are valid, and $T$ is in the future, output valid;
+- else, output invalid.
+
+Aggregation of Financial and Energy Transactions: Financial Balance
+
+Even though prosumer nodes attempt to buy or sell the amount of energy that they will consumer or produce in advance, it is practically impossible to predict net consumption perfectly.
+Consequently, there will necessarily be an imbalance between the amount of energy bought in advance and the actual net consumption of the prosumer.
+This imbalance must be covered by the DSO, who will charge (or pay) the prosumer for the amount of energy consumed (or produced) beyond what was promised in the financial transactions.
+
+The amount that the DSO will charge (or pay) the prosumer is determined by the pricing policy of the DSO, which is set using regulatory transactions.
+
 \section{Related Work}

### 2017-04-27 notes/initial_writeup/paper.tex
no message

@@
 
-Here, we discuss the validation and interpretation rules of financial and energy transactions.
-First, we detail the decision process of the ledger nodes that determines which transaction are valid and recorded in the distributed ledger.
-Second, we explain how the financial and energy transactions can be aggregated to determine the financial balance of a prosumer.
+Here, we discuss the details of how to validate and interpret the financial and energy transactions.
+First, we detail how the ledger nodes determine which transactions are valid and recorded in the distributed ledger.
+Second, we explain how financial and energy transactions can be aggregated in order to determine the financial balance of a prosumer.
 
-Validation of Financial Transactions: Safety and Security
+\subsubsection{Validation of Financial Transactions: Safety and Security}
 
-First, the ledger nodes reach consensus on the order of the incoming transaction.
-Second, they reach consensus on validity of the ordered transaction.
-They determine the validity of the transactions one-by-one, making a decision for a transaction based on its contents and the contents of the valid preceding transactions.
+First, the ledger nodes reach consensus on the order of the transactions that have been submitted for recording on the ledger.
+Second, they reach consensus on the validity of the ordered transactions.
+They determine the validity of the transactions one-by-one, making a decision for each transaction based on its contents and the contents of the preceding valid transactions.
 
-The certificate of each prosumer specifies the net amount of energy that the prosumer may trade for a single time step.
-More specifically, the certificate of prosumer $p$ states
-- net energy that prosumer $p$ may purchase $MaxNetBuy_p$
-- net energy that prosumer $p$ may sell $MaxNetSell_p$.
+To ensure the safety and security of the microgrid, ledger nodes must be able to reject careless or malicious energy trading, which could destabilize the microgrid.
+To this end, the certificate of each prosumer specifies the net amount of energy that the prosumer may trade for a single time step.
+More specifically, the certificate of prosumer $p$ includes the following fields:
+\begin{itemize}
+\item $MaxNetBuy_p$: net energy that prosumer $p$ may purchase,
+\item $MaxNetSell_p$: net energy that prosumer $p$ may sell.
+\end{itemize}
 
-To determine whether an incoming financial transaction is valid, the ledger nodes take the following steps:
-- let $T$ be the time step of the incoming transaction, and let $p_b$ and $p_s$ be the buying and selling prosumer, respectively;
-- let $NetBuy \gets 0$;
-- for every valid transaction on the ledger, if the tilmestep is $T$ and the buyer is $p_b$, then add the energy amount to $NetBuy$;
-- for every valid transaction on the ledger, if the tilmestep is $T$ and the seller is $p_b$, then subtract the energy amount from $NetBuy$;
-- let $NetSell \gets 0$;
-- for every valid transaction on the ledger, if the tilmestep is $T$ and the seller is $p_s$, then add the energy amount to $NetSell$;
-- for every valid transaction on the ledger, if the tilmestep is $T$ and the buyer is $p_s$, then subtract the energy amount from $NetSell$;
-- if $NetBuy \leq MaxNetBuy_{p_b}$, $NetSell \leq MaxNetSell_{p_s}$, signatures are valid, and $T$ is in the future, output valid;
-- else, output invalid.
+To determine whether an incoming financial transaction is valid, a ledger node runs Algorithm~\ref{alg:validateFinancialTransaction}.
+%\begin{enumerate}
+%\item let $T$ be the time step of the incoming transaction, and let $p_b$ and $p_s$ be the buying and selling prosumers, respectively;
+%\item let $NetBuy \gets 0$;
+%\item for every valid transaction on the ledger, if the time step is $T$ and the buyer is $p_b$, then add the energy amount to $NetBuy$;
+%\item for every valid transaction on the ledger, if the time step is $T$ and the seller is $p_b$, then subtract the energy amount from $NetBuy$;
+%\item let $NetSell \gets 0$;
+%\item for every valid transaction on the ledger, if the time step is $T$ and the seller is $p_s$, then add the energy amount to $NetSell$;
+%\item for every valid transaction on the ledger, if the time step is $T$ and the buyer is $p_s$, then subtract the energy amount from $NetSell$;
+%\item if $NetBuy \leq MaxNetBuy_{p_b}$, $NetSell \leq MaxNetSell_{p_s}$, the signatures are valid, and $T$ is in the future, then output valid;
+%\item else, output invalid.
+%\end{enumerate}
 
-Aggregation of Financial and Energy Transactions: Financial Balance
+\begin{algorithm}[h!]
+\caption{Validation of Financial Transaction}
+\label{alg:validateFinancialTransaction}
+\begin{algorithmic}[1]
+\State{let $T$ be the time step of the incoming transaction, and let $p_b$ and $p_s$ be the buying and selling prosumers, respectively}
+\State{$NetBuy \gets 0$}
+\For{valid transaction on the ledger}
+  \If{time step is $T$ and buyer is $p_b$}
+    \State{$NetBuy \gets NetBuy + $ energy amount}
+  \EndIf
+  \If{time step is $T$ and seller is $p_b$}
+    \State{$NetBuy \gets NetBuy - $ energy amount}
+  \EndIf
+\EndFor
+\State{$NetSell \gets 0$}
+\For{valid transaction on the ledger}
+  \If{time step is $T$ and seller is $p_b$}
+    \State{$NetSell \gets NetSell + $ energy amount}
+  \EndIf
+  \If{time step is $T$ and buyer is $p_b$}
+    \State{$NetSell \gets NetSell - $ energy amount}
+  \EndIf
+\EndFor
+\If{$NetBuy \leq MaxNetBuy_{p_b}$, $NetSell \leq MaxNetSell_{p_s}$, the signatures are valid, and $T$ is in the future}
+  \State{\textbf{return} valid}
+\Else
+  \State{\textbf{return} invalid}
+\EndIf
+%
+%\State{$A \gets (\emptyset, \emptyset)$} 
+%\State{$\Loss^* \gets -\infty$}
+%\For{$b = 1, \ldots, B_A$}
+%  \For{$v \in V_A$}
+%    \For{$k \in \Gamma^{-1}(v)$}
+%      \State{$A' \gets A \cup \left(\{s\}, \left\{\hat{p}_{kv} = 1, \forall j \neq k : \hat{p}_{jv} = 0\right\}\right)$}
+%      \State{$\Loss' \gets \big[\left(1 - \Pr[\text{detect}]\right) \cdot \Loss(C, A)$}
+%      \State{\hspace{3.5em} $+ \Pr[\text{detect}] \cdot \min_M \max_R \Loss(C, A, M, R) \big]$}
+%      \If{$\Loss' \geq \Loss^*$}
+%        \State{$A^* \gets A'$}
+%        \State{$\Loss^* \gets \Loss'$}
+%      \EndIf
+%    \EndFor
+%    \State{$A \gets A^*$}
+%  \EndFor
+%\EndFor
+%\State{Output $A$}
+\end{algorithmic}
+\end{algorithm}
 
-Even though prosumer nodes attempt to buy or sell the amount of energy that they will consumer or produce in advance, it is practically impossible to predict net consumption perfectly.
-Consequently, there will necessarily be an imbalance between the amount of energy bought in advance and the actual net consumption of the prosumer.
+\subsubsection{Aggregation of Financial and Energy Transactions: Financial Balance}
+
+Even though prosumer nodes attempt to buy or sell in advance the amount of energy that they will consume or produce, it is practically impossible to predict their net consumption perfectly.
+Consequently, there will necessarily be an imbalance between the amount of energy bought (or sold) in advance and the actual net consumption (or production) of the prosumer.
 This imbalance must be covered by the DSO, who will charge (or pay) the prosumer for the amount of energy consumed (or produced) beyond what was promised in the financial transactions.

### 2017-04-27 notes/initial_writeup/paper.tex
no message

@@
 
-Microsoft Azure Blockchain as a Service (BaaS) and Project Bletchley~\cite{gray2016introducing}.
+Microsoft offers Blockchain as a Service (BaaS) on Azure.
+Project Bletchley is Microsoft's architectural approach to building an Enterprise Consortium Blockchain Ecosystem, introducing two new concepts: blockchain middleware and cryptlets~\cite{gray2016introducing}.
 
-Hyperledger Fabric~\cite{hyperledger2017fabric}.
+Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}.
 
-Interledger~\cite{thomas_protocol}.
+Interledger is a protocol for payments across payment systems, which enables anyone with accounts on two ledgers to create
+a connection between them~\cite{thomas_protocol}.
 
-Bitcoin Lightning Network~\cite{poon2016bitcoin}.
+Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}.
 

### 2017-05-01 notes/initial_writeup/paper.tex
no message

@@
 
+\subsection{Timing}
+
+\todo[inline]{
+\textbullet 
+look up timing assumptions from proposal, which are driven by control requirements
+\textbullet 
+map those timing assumptions to time interval in the transactive microgrid system
+\textbullet 
+discuss how supply and demand can be forecasted from energy trading between prosumers
+}
+
 \begin{figure}[h!]
@@
 
-Time is divided into fixed-length intervals, and energy trades are specified with respect to these intervals: financial transactions promise to consume or produce a certain amount of energy in a future interval, while energy transactions record the actual amount of energy produced or consumed in an earlier interval.
-Figure~\ref{fig:timeline} shows a basic timeline of financial and energy transactions.
-
-\begin{figure*}
+\begin{figure*}[h!]
 \begin{tikzpicture}[
@@
   y=1cm,
-  nodeStyle/.style={fill=white, draw=black, drop shadow=black!30, minimum size=0.5cm}]
+  nodeStyle/.style={fill=white, draw=black, drop shadow=black!30, minimum size=0.5cm},
+  linkStyle/.style={<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt},
+  batchStyle/.style={->, very thick, >=stealth},
+  braceStyle/.style={decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm},
+]
 
@@
 \foreach \name/\x/\y in {{t1/0/0}, {t2/1/1.4}, {t3/2/0}}
-  \node [regular polygon, regular polygon sides=5, nodeStyle] (\name) at (\x,\y) {};
+  \node [nodeStyle, regular polygon, regular polygon sides=5] (\name) at (\x,\y) {};
 
-\foreach \name/\x/\y in {{tAnchorRight/2.5/0.7}}
+\foreach \name/\x/\y in {{tRight/2.5/0.7}}
   \coordinate (\name) at (\x,\y);
@@
 \foreach \from/\to in {{t1/t2}, {t2/t3}, {t3/t1}}
-  \draw [<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt] (\from) -- (\to);
+  \draw [linkStyle] (\from) -- (\to);
 
-\draw [decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm] (2.25, 0) -- (-0.25, 0) node [midway, below=0.2cm] {trading nodes};
+\draw [braceStyle] (2.25, 0) -- (-0.25, 0) node [midway, below=0.2cm] {trading nodes};
 \end{scope}
@@
 
-\foreach \name/\x/\y in {{pAnchorLeft/-0.6/0.7}, {pAnchorRight/2/0.7}}
+\foreach \name/\x/\y in {{pLeft/-0.6/0.7}, {pRight/2/0.7}}
   \coordinate (\name) at (\x,\y);
@@
 \foreach \from/\to in {{p1/p2}, {p1/p3}, {p1/p4}, {p2/p3}, {p2/p4}, {p3/p4}}
-  \draw [<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt, dashed] (\from) -- (\to);
+  \draw [linkStyle, dashed] (\from) -- (\to);
 
-\draw [decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm] (1.65, 0) -- (-0.25, 0) node [midway, below=0.2cm] {prosumer nodes};
-
+\draw [braceStyle] (1.65, 0) -- (-0.25, 0) node [midway, below=0.2cm] {prosumer nodes};
 \end{scope}
@@
 
-\foreach \name/\x/\y in {{mAnchorRight/2/0.7}}
+\foreach \name/\x/\y in {{mRight/2/0.7}}
   \coordinate (\name) at (\x,\y);
@@
 \foreach \from/\to in {{m1/m2}, {m1/m3}, {m1/m4}, {m2/m3}, {m2/m4}, {m3/m4}}
-  \draw [<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt, dashed] (\from) -- (\to);
+  \draw [linkStyle, dashed] (\from) -- (\to);
 
-\draw [decorate, decoration={brace,amplitude=0.2cm}, yshift=0.4cm] (-0.25, 1.4) -- (1.65, 1.4) node [midway, above=0.2cm] {smart-meter nodes};
-
+\draw [braceStyle, yshift=0.8cm] (-0.25, 1.4) -- (1.65, 1.4) node [midway, above=0.2cm] {smart-meter nodes};
 \end{scope}
@@
 
-\foreach \name/\x/\y in {{lAnchorLeft/-0.5/0.7}, {lAnchorTopLeft/0/1.6}, {lAnchorTopRight/1.6/1.0}}
+\foreach \name/\x/\y in {{lLeft/-0.5/0.7}, {lTopLeft/0/1.6}, {lTopRight/1.6/1.0}}
   \coordinate (\name) at (\x,\y);
@@
 \draw [decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm] (2.25, 0) -- (-0.25, 0) node [midway, below=0.2cm] {ledger nodes};
-
 \end{scope}
@@
 % additional nodes
+\node [ellipse, nodeStyle] (dso) at (15cm, 3.1cm) {DSO node};
 
-\node [ellipse, nodeStyle] (dso) at (15.5cm, 3.0cm) {DSO node};
+\draw [->, >=stealth, bend right=10, shorten <=0.25cm, shorten >=0.5cm] (dso) to node [midway, above left=0cm, align=center] {regulatory\\[-0.25em]transactions} (lTopRight);
+\draw [<-, >=stealth, bend left=10, shorten <=0.25cm, shorten >=0.5cm] (dso) to node [midway, below right=0cm, align=center] {ledger status} (lTopRight);
 
-\draw [->, very thick, >=stealth, bend right=10, shorten <=0.5cm, shorten >=0.5cm] (dso) to node [midway, above left=0.0cm, align=center] {regulatory\\[-0.25em]transactions} (lAnchorTopRight);
-\draw [<-, very thick, >=stealth, bend left=10, shorten <=0.5cm, shorten >=0.5cm] (dso) to node [midway, below right=0.0cm, align=center] {ledger status} (lAnchorTopRight);
+\node [above=1.2cm of dso] (controller) {control algorithm};
+
+\draw [<-, >=stealth, bend right=10, shorten <=1.5pt] (dso) to node [midway, left=0.3cm, align=center] {measured and\\[-0.25em]expected load} (controller);
+\draw [->, >=stealth, bend left=10, shorten <=1.5pt] (dso) to node [midway, right=0.3cm, align=center] {control\\[-0.25em]signal} (controller);
 
 % connections between systems
-\draw [<-, very thick, >=stealth, bend left=5] ([yshift=0.0cm]tAnchorRight) to node [midway, above=0.1cm] {bids} ([yshift=0.0cm]pAnchorLeft);
-\draw [->, very thick, >=stealth, bend right=5] ([yshift=-0.4cm]tAnchorRight) to node [midway, below=0.1cm] {matches} ([yshift=-0.4cm]pAnchorLeft);
+\draw [batchStyle, <-, bend left=5] (tRight) to node [midway, above=0.1cm] {bids} (pLeft);
+\draw [batchStyle, bend right=5] ([yshift=-0.4cm]tRight) to node [midway, below=0.1cm] {matches} ([yshift=-0.4cm]pLeft);
 
-\draw [->, very thick, >=stealth, bend left=5] ([yshift=0.0cm]pAnchorRight) to node [midway, above=0.1cm, align=center] {financial\\[-0.25em]transactions} ([yshift=0.0cm]lAnchorLeft);
-\draw [<-, very thick, >=stealth, bend right=5] ([yshift=-0.4cm]pAnchorRight) to node [midway, below=0.1cm] {ledger status} ([yshift=-0.4cm]lAnchorLeft);
+\draw [batchStyle, bend left=5] (pRight) to node [midway, above=0.1cm, align=center] {financial\\[-0.25em]transactions} ([yshift=0cm]lLeft);
+\draw [batchStyle, <-, bend right=5] ([yshift=-0.4cm]pRight) to node [midway, below=0.1cm] {ledger status} ([yshift=-0.4cm]lLeft);
 
-\draw [->, very thick, >=stealth, bend left=15] ([yshift=0.2cm]mAnchorRight) to node [midway, above right=0.0cm, align=center] {energy\\[-0.25em]transactions} ([yshift=0.2cm]lAnchorTopLeft);
-\draw [<-, very thick, >=stealth, bend right=-5] ([yshift=-0.2cm]mAnchorRight) to node [midway, below left=0.0cm] {ledger status} ([yshift=-0.2cm]lAnchorTopLeft);
+\draw [batchStyle, bend left=15] ([yshift=0.2cm]mRight) to node [midway, above right=0cm, align=center] {energy\\[-0.25em]transactions} ([yshift=0.2cm]lTopLeft);
+\draw [batchStyle, <-, bend right=-5] ([yshift=-0.2cm]mRight) to node [midway, below left=0cm] {ledger status} ([yshift=-0.2cm]lTopLeft);
 
@@
 \end{figure*}
+
+Time is divided into fixed-length intervals, and energy trades are specified with respect to these intervals: financial transactions promise to consume or produce a certain amount of energy in a future interval, while energy transactions record the actual amount of energy produced or consumed in an earlier interval.
+Figure~\ref{fig:timeline} shows a basic timeline of financial and energy transactions.
 
@@
 \begin{algorithmic}[1]
+\Statex{\hspace{-\algorithmicindent}\textbf{Input:} incoming transaction, valid transactions on the ledger}
+\Statex{\hspace{-\algorithmicindent}\textbf{Output:} valid / invalid}
 \State{let $T$ be the time step of the incoming transaction, and let $p_b$ and $p_s$ be the buying and selling prosumers, respectively}
 \State{$NetBuy \gets 0$}
+\State{$NetSell \gets 0$}
 \For{valid transaction on the ledger}
-  \If{time step is $T$ and buyer is $p_b$}
+  \If{time step is $T$}
+    \If{buyer is $p_b$}
       \State{$NetBuy \gets NetBuy + $ energy amount}
     \EndIf
-  \If{time step is $T$ and seller is $p_b$}
+    \If{seller is $p_b$}
       \State{$NetBuy \gets NetBuy - $ energy amount}
     \EndIf
-\EndFor
-\State{$NetSell \gets 0$}
-\For{valid transaction on the ledger}
-  \If{time step is $T$ and seller is $p_b$}
+    \If{seller is $p_s$}
       \State{$NetSell \gets NetSell + $ energy amount}
     \EndIf
-  \If{time step is $T$ and buyer is $p_b$}
+    \If{buyer is $p_s$}
       \State{$NetSell \gets NetSell - $ energy amount}
+    \EndIf
   \EndIf

### 2017-05-01 notes/initial_writeup/paper.tex
no message

@@
 
+\paragraph{Controller}
+The controller is responsible for stabilizing load within the microgrid and controlling it based on the load in the rest of the grid.
+
+\todo[inline]{
+\textbullet 
+receives measured and expected load values from the ledger (as well as from the rest of the grid)
+\textbullet 
+produces a control signal that specifies the desired load for the future (may also include a tolerance level that specifies how much deviation from this load level is tolerable)
+\textbullet 
+may be implemented by the DSO node, as part of the RIAPS-based platform, or may be a legacy controller that interfaces with the DSO node
+}
+
+\input{figArchitecture.tex}
+
 \subsection{Timing}
@@
 \textbullet 
-look up timing assumptions from proposal, which are driven by control requirements
+control signal from DSO may change at a 4 second interval
+\textbullet 
+we make 4 second the basic unit of timing in our platform
+(energy consumption and production are measured over 4 second units, prosumers may trade energy for durations that are multiples of 4 second units, etc.)
 \textbullet 
@@
 \end{figure}
-
-\begin{figure*}[h!]
-\begin{tikzpicture}[
-  x=1cm, 
-  y=1cm,
-  nodeStyle/.style={fill=white, draw=black, drop shadow=black!30, minimum size=0.5cm},
-  linkStyle/.style={<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt},
-  batchStyle/.style={->, very thick, >=stealth},
-  braceStyle/.style={decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm},
-]
-
-% trading nodes
-\begin{scope}[xshift=1cm]
-
-\foreach \name/\x/\y in {{t1/0/0}, {t2/1/1.4}, {t3/2/0}}
-  \node [nodeStyle, regular polygon, regular polygon sides=5] (\name) at (\x,\y) {};
-
-\foreach \name/\x/\y in {{tRight/2.5/0.7}}
-  \coordinate (\name) at (\x,\y);
-
-\foreach \from/\to in {{t1/t2}, {t2/t3}, {t3/t1}}
-  \draw [linkStyle] (\from) -- (\to);
-
-\draw [braceStyle] (2.25, 0) -- (-0.25, 0) node [midway, below=0.2cm] {trading nodes};
-\end{scope}
-
-% prosumer nodes
-\begin{scope}[xshift=6cm]
-
-\foreach \name/\x/\y in {{p1/0/0}, {p2/1.4/0}, {p3/0/1.4}, {p4/1.4/1.4}}
-  \node [nodeStyle, rounded corners=0.1cm] (\name) at (\x,\y) {};
-
-\foreach \name/\x/\y in {{pLeft/-0.6/0.7}, {pRight/2/0.7}}
-  \coordinate (\name) at (\x,\y);
-
-\foreach \from/\to in {{p1/p2}, {p1/p3}, {p1/p4}, {p2/p3}, {p2/p4}, {p3/p4}}
-  \draw [linkStyle, dashed] (\from) -- (\to);
-
-\draw [braceStyle] (1.65, 0) -- (-0.25, 0) node [midway, below=0.2cm] {prosumer nodes};
-\end{scope}
-
-% smart-meter nodes
-\begin{scope}[xshift=6cm, yshift=2.7cm]
-
-\foreach \name/\x/\y in {{m1/0/0}, {m2/1.4/0}, {m3/0/1.4}, {m4/1.4/1.4}}
-  \node [diamond, nodeStyle] (\name) at (\x,\y) {};
-
-\foreach \name/\x/\y in {{mRight/2/0.7}}
-  \coordinate (\name) at (\x,\y);
-
-\foreach \from/\to in {{m1/m2}, {m1/m3}, {m1/m4}, {m2/m3}, {m2/m4}, {m3/m4}}
-  \draw [linkStyle, dashed] (\from) -- (\to);
-
-\draw [braceStyle, yshift=0.8cm] (-0.25, 1.4) -- (1.65, 1.4) node [midway, above=0.2cm] {smart-meter nodes};
-\end{scope}
-
-% ledger nodes
-\begin{scope}[xshift=11.5cm]
-
-\foreach \name/\x/\y in {{l1/0/0}, {l2/1/1.4}, {l3/2/0}}
-  \node [circle, nodeStyle] (\name) at (\x,\y) {};
-
-\foreach \name/\x/\y in {{lLeft/-0.5/0.7}, {lTopLeft/0/1.6}, {lTopRight/1.6/1.0}}
-  \coordinate (\name) at (\x,\y);
-
-\foreach \from/\to in {{l1/l2}, {l2/l3}, {l3/l1}}
-  \draw [<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt] (\from) -- (\to);
-
-\draw [decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm] (2.25, 0) -- (-0.25, 0) node [midway, below=0.2cm] {ledger nodes};
-\end{scope}
-
-% additional nodes
-\node [ellipse, nodeStyle] (dso) at (15cm, 3.1cm) {DSO node};
-
-\draw [->, >=stealth, bend right=10, shorten <=0.25cm, shorten >=0.5cm] (dso) to node [midway, above left=0cm, align=center] {regulatory\\[-0.25em]transactions} (lTopRight);
-\draw [<-, >=stealth, bend left=10, shorten <=0.25cm, shorten >=0.5cm] (dso) to node [midway, below right=0cm, align=center] {ledger status} (lTopRight);
-
-\node [above=1.2cm of dso] (controller) {control algorithm};
-
-\draw [<-, >=stealth, bend right=10, shorten <=1.5pt] (dso) to node [midway, left=0.3cm, align=center] {measured and\\[-0.25em]expected load} (controller);
-\draw [->, >=stealth, bend left=10, shorten <=1.5pt] (dso) to node [midway, right=0.3cm, align=center] {control\\[-0.25em]signal} (controller);
-
-% connections between systems
-\draw [batchStyle, <-, bend left=5] (tRight) to node [midway, above=0.1cm] {bids} (pLeft);
-\draw [batchStyle, bend right=5] ([yshift=-0.4cm]tRight) to node [midway, below=0.1cm] {matches} ([yshift=-0.4cm]pLeft);
-
-\draw [batchStyle, bend left=5] (pRight) to node [midway, above=0.1cm, align=center] {financial\\[-0.25em]transactions} ([yshift=0cm]lLeft);
-\draw [batchStyle, <-, bend right=5] ([yshift=-0.4cm]pRight) to node [midway, below=0.1cm] {ledger status} ([yshift=-0.4cm]lLeft);
-
-\draw [batchStyle, bend left=15] ([yshift=0.2cm]mRight) to node [midway, above right=0cm, align=center] {energy\\[-0.25em]transactions} ([yshift=0.2cm]lTopLeft);
-\draw [batchStyle, <-, bend right=-5] ([yshift=-0.2cm]mRight) to node [midway, below left=0cm] {ledger status} ([yshift=-0.2cm]lTopLeft);
-
-\end{tikzpicture}
-\caption{High-level logical architecture of the trading platform and the distributed ledger. A physical node may implement multiple logical nodes.}
-\label{fig:logicalNodeArchitecture}
-\end{figure*}
 

### 2017-05-03 notes/initial_writeup/paper.tex
no message

@@
 \paragraph{Controller}
-The controller is responsible for stabilizing load within the microgrid and controlling it based on the load in the rest of the grid.
-
-\todo[inline]{
-\textbullet 
-receives measured and expected load values from the ledger (as well as from the rest of the grid)
-\textbullet 
-produces a control signal that specifies the desired load for the future (may also include a tolerance level that specifies how much deviation from this load level is tolerable)
-\textbullet 
-may be implemented by the DSO node, as part of the RIAPS-based platform, or may be a legacy controller that interfaces with the DSO node
-}
+The controller is responsible for stabilizing load within the microgrid and controlling it based on the expected load in the rest of the grid.
+To this end, the controller first estimates the expected load in the microgrid based on outstanding energy trades on the ledger.
+By combining this estimate with the expected load in the remainder of the grid, the controller produces a control signal that specifies how much the load in the microgrid needs to be decreased or increased.
+Finally, based on this control signal, the controller updates the price policy for the microgrid to influence energy production and consumption.
+The controller may be implemented by the DSO node, as part of the RIAPS-based platform, or may be a legacy controller that interfaces with the DSO node.
 
@@
 
-\todo[inline]{
-\textbullet 
-control signal from DSO may change at a 4 second interval
-\textbullet 
-we make 4 second the basic unit of timing in our platform
-(energy consumption and production are measured over 4 second units, prosumers may trade energy for durations that are multiples of 4 second units, etc.)
-\textbullet 
-map those timing assumptions to time interval in the transactive microgrid system
-\textbullet 
-discuss how supply and demand can be forecasted from energy trading between prosumers
-}
+Timing is a crucial part of our platform.
+For example, control signals specify how the load should change at certain points in time, energy trades specify when energy will be consumed or produced, etc.
+To facilitate processing signals and transactions, we divide time into fixed-length intervals, and specify points or periods in time using these discrete time intervals.
+The length of the time interval is determined by mapping the timing assumptions of the power system to our platform.
+In our implementation, for example, the default length of the time interval is 4 seconds, which corresponds to how frequently the control signal of the DSO changes.
 
@@
 
-Time is divided into fixed-length intervals, and energy trades are specified with respect to these intervals: financial transactions promise to consume or produce a certain amount of energy in a future interval, while energy transactions record the actual amount of energy produced or consumed in an earlier interval.
+All transactions for energy trading are specified with respect to these discrete intervals: financial transactions promise to consume or produce a certain amount of energy in a future interval, while energy transactions record the actual amount of energy produced or consumed in an earlier interval.
 Figure~\ref{fig:timeline} shows a basic timeline of financial and energy transactions.
@@
 
+\subsection{Control Algorithm}
+
+\todo[inline]{
+\textbullet 
+receives measured and expected load values from the ledger (as well as from the rest of the grid)
+\textbullet 
+produces a control signal that specifies the desired load for the future (may also include a tolerance level that specifies how much deviation from this load level is tolerable)
+}
+
 \section{Related Work}

### 2017-05-03 notes/initial_writeup/paper.tex
no message

@@
 The two nodes negotiate, agree on, create, and sign a new financial transaction, which they then submit to the distributed ledger.
+\todo[inline]{Extend: prosumer nodes may buy/sell electricity from/to DSO in advance. This is key to load prediction.}
 Once the ledger has verified and recorded the transaction, the electricity trade has been set up.
@@
 A financial transaction contains the following fields:
+\todo[inline]{Extend: prosumer nodes may buy/sell electricity from/to DSO in advance. This is key to load prediction.}
 \begin{itemize}
@@
 
+\todo[inline]{Extend: prosumer nodes may buy/sell electricity from/to DSO in advance. This is key to load prediction.}
+
 \begin{algorithm}[h!]
@@
 
+\todo[inline]{Firstly, the prosumer must pay (or be paid) for the financial transactions recorded on the ledger in either a fiat currency (e.g., US dollars) or a cryptocurrency.}
+
 Even though prosumer nodes attempt to buy or sell in advance the amount of energy that they will consume or produce, it is practically impossible to predict their net consumption perfectly.
@@
 }
+
+\todo[inline]{Figure: - data flow between nodes - control signals}
 

### 2017-05-15 papers/IoT2017/figArchitecture.tex
IoT 2017 paper started

\begin{figure*}
\begin{tikzpicture}[
  x=1cm, 
  y=1cm,
  nodeStyle/.style={fill=white, draw=black, drop shadow=black!30, minimum size=0.5cm},
  linkStyle/.style={<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt},
  batchStyle/.style={->, very thick, >=stealth},
  braceStyle/.style={decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm},
]

% trading nodes
\begin{scope}[xshift=1cm]

\foreach \name/\x/\y in {{t1/0/0}, {t2/1/1.4}, {t3/2/0}}
  \node [nodeStyle, regular polygon, regular polygon sides=5] (\name) at (\x,\y) {};

\foreach \name/\x/\y in {{tRight/2.5/0.7}}
  \coordinate (\name) at (\x,\y);

\foreach \from/\to in {{t1/t2}, {t2/t3}, {t3/t1}}
  \draw [linkStyle] (\from) -- (\to);

\draw [braceStyle] (2.25, 0) -- (-0.25, 0) node [midway, below=0.2cm] {trading nodes};
\end{scope}

% prosumer nodes
\begin{scope}[xshift=6cm]

\foreach \name/\x/\y in {{p1/0/0}, {p2/1.4/0}, {p3/0/1.4}, {p4/1.4/1.4}}
  \node [nodeStyle, rounded corners=0.1cm] (\name) at (\x,\y) {};

\foreach \name/\x/\y in {{pLeft/-0.6/0.7}, {pRight/2/0.7}}
  \coordinate (\name) at (\x,\y);

\foreach \from/\to in {{p1/p2}, {p1/p3}, {p1/p4}, {p2/p3}, {p2/p4}, {p3/p4}}
  \draw [linkStyle, dashed] (\from) -- (\to);

\draw [braceStyle] (1.65, 0) -- (-0.25, 0) node [midway, below=0.2cm] {prosumer nodes};
\end{scope}

% smart-meter nodes
\begin{scope}[xshift=6cm, yshift=2.7cm]

\foreach \name/\x/\y in {{m1/0/0}, {m2/1.4/0}, {m3/0/1.4}, {m4/1.4/1.4}}
  \node [diamond, nodeStyle] (\name) at (\x,\y) {};

\foreach \name/\x/\y in {{mRight/2/0.7}}
  \coordinate (\name) at (\x,\y);

\foreach \from/\to in {{m1/m2}, {m1/m3}, {m1/m4}, {m2/m3}, {m2/m4}, {m3/m4}}
  \draw [linkStyle, dashed] (\from) -- (\to);

\draw [braceStyle, yshift=0.8cm] (-0.25, 1.4) -- (1.65, 1.4) node [midway, above=0.2cm] {smart-meter nodes};
\end{scope}

% ledger nodes
\begin{scope}[xshift=11.5cm]

\foreach \name/\x/\y in {{l1/0/0}, {l2/1/1.4}, {l3/2/0}}
  \node [circle, nodeStyle] (\name) at (\x,\y) {};

\foreach \name/\x/\y in {{lLeft/-0.5/0.7}, {lTopLeft/0/1.6}, {lTopRight/1.6/1.0}}
  \coordinate (\name) at (\x,\y);

\foreach \from/\to in {{l1/l2}, {l2/l3}, {l3/l1}}
  \draw [<->, >=stealth, shorten >=1.5pt, shorten <=1.5pt] (\from) -- (\to);

\draw [decorate, decoration={brace,amplitude=0.2cm}, yshift=-0.4cm] (2.25, 0) -- (-0.25, 0) node [midway, below=0.2cm] {ledger nodes};
\end{scope}

% additional nodes
\node [ellipse, nodeStyle] (dso) at (15cm, 3.1cm) {DSO node};

\draw [->, >=stealth, bend right=10, shorten <=0.25cm, shorten >=0.5cm] (dso) to node [midway, above left=0cm, align=center] {regulatory\\[-0.25em]transactions} (lTopRight);
\draw [<-, >=stealth, bend left=10, shorten <=0.25cm, shorten >=0.5cm] (dso) to node [midway, below right=0cm, align=center] {ledger status} (lTopRight);

\node [above=1.2cm of dso] (controller) {control algorithm};

\draw [<-, >=stealth, bend right=10, shorten <=1.5pt] (dso) to node [midway, left=0.3cm, align=center] {measured and\\[-0.25em]expected load} (controller);
\draw [->, >=stealth, bend left=10, shorten <=1.5pt] (dso) to node [midway, right=0.3cm, align=center] {control\\[-0.25em]signal} (controller);

% connections between systems
\draw [batchStyle, <-, bend left=5] (tRight) to node [midway, above=0.1cm] {bids} (pLeft);
\draw [batchStyle, bend right=5] ([yshift=-0.4cm]tRight) to node [midway, below=0.1cm] {matches} ([yshift=-0.4cm]pLeft);

\draw [batchStyle, bend left=5] (pRight) to node [midway, above=0.1cm, align=center] {financial\\[-0.25em]transactions} ([yshift=0cm]lLeft);
\draw [batchStyle, <-, bend right=5] ([yshift=-0.4cm]pRight) to node [midway, below=0.1cm] {ledger status} ([yshift=-0.4cm]lLeft);

\draw [batchStyle, bend left=15] ([yshift=0.2cm]mRight) to node [midway, above right=0cm, align=center] {energy\\[-0.25em]transactions} ([yshift=0.2cm]lTopLeft);
\draw [batchStyle, <-, bend right=-5] ([yshift=-0.2cm]mRight) to node [midway, below left=0cm] {ledger status} ([yshift=-0.2cm]lTopLeft);

\end{tikzpicture}
\caption{High-level logical architecture of the trading platform and the distributed ledger. A physical node may implement multiple logical nodes.}
\label{fig:logicalNodeArchitecture}
\end{figure*}

### 2017-05-15 papers/IoT2017/paper.tex
IoT 2017 paper started

--- 2017-05-03 notes/initial_writeup/paper.tex
@@
-\documentclass[sigconf]{acmart}
+\documentclass[chi_draft]{sigchi}
 
-% BEGIN ACM HEADER
-
-\usepackage{booktabs} % For formal tables
-\usepackage{balance} % For balanced columns on the last page
+% Use this section to set the ACM copyright statement (e.g. for
+% preprints).  Consult the conference website for the camera-ready
+% copyright statement.
 
 % Copyright
+\CopyrightYear{2017}
+%\setcopyright{acmcopyright}
 \setcopyright{acmlicensed}
+%\setcopyright{rightsretained}
+%\setcopyright{usgov}
+%\setcopyright{usgovmixed}
+%\setcopyright{cagov}
+%\setcopyright{cagovmixed}
+% DOI
+\doi{} %http://dx.doi.org/10.475/123_4}
+% ISBN
+\isbn{} %123-4567-24-567/08/06}
+%Conference
+\conferenceinfo{IoT'17,}{October 22--25, 2017, Linz, Austria}
+%Price
+\acmPrice{\$15.00}
 
-% DOI - Replace your DOI below...
-\acmDOI{}
+% Use this command to override the default ACM copyright statement
+% (e.g. for preprints).  Consult the conference website for the
+% camera-ready copyright statement.
 
-% ISBN - Replace your conference/workshop's ISBN below...
-\acmISBN{}
+%% HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP --
+%% Please note you need to make sure the copy for your specific
+%% license is used here!
+% \toappear{
+% Permission to make digital or hard copies of all or part of this work
+% for personal or classroom use is granted without fee provided that
+% copies are not made or distributed for profit or commercial advantage
+% and that copies bear this notice and the full citation on the first
+% page. Copyrights for components of this work owned by others than ACM
+% must be honored. Abstracting with credit is permitted. To copy
+% otherwise, or republish, to post on servers or to redistribute to
+% lists, requires prior specific permission and/or a fee. Request
+% permissions from \href{mailto:Permissions@acm.org}{Permissions@acm.org}. \\
+% \emph{CHI '16},  May 07--12, 2016, San Jose, CA, USA \\
+% ACM xxx-x-xxxx-xxxx-x/xx/xx\ldots \$15.00 \\
+% DOI: \url{http://dx.doi.org/xx.xxxx/xxxxxxx.xxxxxxx}
+% }
 
-% SELECT YOUR CONFERENCE/WORKSHOP BELOW...
-\acmConference[]{}{}{}
+% Arabic page numbers for submission.  Remove this line to eliminate
+% page numbers for the camera ready copy
+% \pagenumbering{arabic}
 
-\acmYear{2017}
-\copyrightyear{2017}
+% Load basic packages
+\usepackage{balance}       % to better equalize the last page
+\usepackage{graphics}      % for EPS, load graphicx instead 
+\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
+\usepackage{txfonts}
+\usepackage{mathptmx}
+\usepackage[pdflang={en-US},pdftex]{hyperref}
+\usepackage{color}
+\usepackage{booktabs}
+\usepackage{textcomp}
 
-\acmPrice{}
+% Some optional stuff you might like/need.
+\usepackage{microtype}        % Improved Tracking and Kerning
+% \usepackage[all]{hypcap}    % Fixes bug in hyperref caption linking
+\usepackage{ccicons}          % Cite your images correctly!
+% \usepackage[utf8]{inputenc} % for a UTF8 editor only
 
-% END ACM HEADER
-
-\usepackage{epstopdf}
-\usepackage{url}
+% Custom packages
 
@@
 
+% If you want to use todo notes, marginpars etc. during creation of
+% your draft document, you have to enable the "chi_draft" option for
+% the document class. To do this, change the very first line to:
+% "\documentclass[chi_draft]{sigchi}". You can then place todo notes
+% by using the "\todo{...}"  command. Make sure to disable the draft
+% option again before submitting your final document.
 \usepackage[textsize=small]{todonotes}
@@
 
-\DeclareMathOperator*{\argmin}{argmin}
-\DeclareMathOperator*{\argmax}{argmax}
+% Paper metadata (use plain text, for PDF inclusion and later
+% re-using, if desired).  Use \emtpyauthor when submitting for review
+% so you remain anonymous.
+\def\plaintitle{Private Blockchains for Transactive Energy}
+\def\plainauthor{First Author, Second Author, Third Author}
+\def\emptyauthor{}
+\def\plainkeywords{Transactive microgrid; blockchain; privacy; security.}
+\def\plaingeneralterms{} % TODO!
 
-\newcommand{\vect}[1]{\ensuremath{\boldsymbol{#1}}}
-\newcommand{\vpi}[0]{\vect{\pi}}
+% llt: Define a global style for URLs, rather that the default one
+\makeatletter
+\def\url@leostyle{%
+  \@ifundefined{selectfont}{
+    \def\UrlFont{\sf}
+  }{
+    \def\UrlFont{\small\bf\ttfamily}
+  }}
+\makeatother
+\urlstyle{leo}
 
-\newcommand{\calA}[0]{\ensuremath{\mathcal{A}}}
-\newcommand{\calC}[0]{\ensuremath{\mathcal{C}}}
-\newcommand{\calS}[0]{\ensuremath{\mathcal{S}}}
+% To make various LaTeX processors do the right thing with page size.
+\def\pprw{8.5in}
+\def\pprh{11in}
+\special{papersize=\pprw,\pprh}
+\setlength{\paperwidth}{\pprw}
+\setlength{\paperheight}{\pprh}
+\setlength{\pdfpagewidth}{\pprw}
+\setlength{\pdfpageheight}{\pprh}
 
+% Make sure hyperref comes last of your loaded packages, to give it a
+% fighting chance of not being over-written, since its job is to
+% redefine many LaTeX commands.
+\definecolor{linkColor}{RGB}{6,125,233}
+\hypersetup{%
+  pdftitle={\plaintitle},
+% Use \plainauthor for final version.
+%  pdfauthor={\plainauthor},
+  pdfauthor={\emptyauthor},
+  pdfkeywords={\plainkeywords},
+  pdfdisplaydoctitle=true, % For Accessibility
+  bookmarksnumbered,
+  pdfstartview={FitH},
+  colorlinks,
+  citecolor=black,
+  filecolor=black,
+  linkcolor=black,
+  urlcolor=linkColor,
+  breaklinks=true,
+  hypertexnames=false
+}
+
+% create a shortcut to typeset table headings
+% \newcommand\tabhead[1]{\small\textbf{#1}}
+
+% End of preamble. Here it comes the document.
 \begin{document}
 
-\title[Blockchain as Middleware Services for Transactive Energy Applications]{Blockchain as Middleware Services for\\Transactive Energy Applications}
+\title{\plaintitle}
 
-\author{Aron Laszka}
-\affiliation{%
-  \institution{Vanderbilt University}
-  \city{Nashville} 
-  \state{Tennessee} 
-  \postcode{37212}
+\numberofauthors{3}
+\author{%
+  \alignauthor{Leave Authors Anonymous\\
+    \affaddr{for Submission}\\
+    \affaddr{City, Country}\\
+    \email{e-mail address}}\\
+  \alignauthor{Leave Authors Anonymous\\
+    \affaddr{for Submission}\\
+    \affaddr{City, Country}\\
+    \email{e-mail address}}\\
+  \alignauthor{Leave Authors Anonymous\\
+    \affaddr{for Submission}\\
+    \affaddr{City, Country}\\
+    \email{e-mail address}}\\
 }
-\email{aron.laszka@vanderbilt.edu}
 
-% The default list of authors is too long for headers}
-\renewcommand{\shortauthors}{A. Laszka et al.}
+\maketitle
 
@@
 
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10002951.10003227</concept_id>
-<concept_desc>Information systems~Information systems applications</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10003456.10003462.10003544</concept_id>
-<concept_desc>Social and professional topics~Commerce policy</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10010583.10010662.10010663</concept_id>
-<concept_desc>Hardware~Energy generation and storage</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10010583.10010662.10010674</concept_id>
-<concept_desc>Hardware~Power estimation and optimization</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
+% TODO!
+\category{H.5.m.}{Information Interfaces and Presentation
+  (e.g. HCI)}{Miscellaneous} \category{See
+  \url{http://acm.org/about/class/1998/} for the full list of ACM
+  classifiers. This section is required.}{}{}
 
-\ccsdesc[300]{Information systems~Information systems applications}
-\ccsdesc[300]{Social and professional topics~Commerce policy}
-\ccsdesc[300]{Hardware~Energy generation and storage}
-\ccsdesc[300]{Hardware~Power estimation and optimization}
+\keywords{\plainkeywords}
 
-\keywords{Transactive microgrid, blockchain}
-
-\maketitle
-
-%\section{Introduction}
+\section{Introduction}
 
@@
 
-\bibliographystyle{ACM-Reference-Format}
+\url{https://geli.net/residential/}
+\url{https://www.greentechmedia.com/articles/read/geli-raises-7m-to-take-energy-storage-software-to-the-next-level}
+
+% BALANCE COLUMNS
+\balance{}
+
+% REFERENCES FORMAT
+% References must be the same font size as other body text.
+\bibliographystyle{SIGCHI-Reference-Format}
 \bibliography{references}

### 2017-05-15 papers/IoT2017/paper.tex
formatting fixes

@@
 % so you remain anonymous.
-\def\plaintitle{Private Blockchains for Transactive Energy}
+\def\plaintitle{Private Blockchains for Transactive Energy:\\Security, Privacy, and Safety}
 \def\plainauthor{First Author, Second Author, Third Author}
 \def\emptyauthor{}
-\def\plainkeywords{Transactive microgrid; blockchain; privacy; security.}
-\def\plaingeneralterms{} % TODO!
+\def\plainkeywords{Internet of Things; blockchain; transactive energy; privacy; security; transactive microgrid.}
+\def\plaingeneralterms{Design, Human Factors, Reliability, Security} % TODO: revise
 
@@
 % TODO!
-\category{H.5.m.}{Information Interfaces and Presentation
-  (e.g. HCI)}{Miscellaneous} \category{See
-  \url{http://acm.org/about/class/1998/} for the full list of ACM
-  classifiers. This section is required.}{}{}
+\category{K.6.m}{Miscellaneous}{Security}
+\category{D.4.7}{Organization and Design}{Distributed systems}
 
@@
 \begin{figure}[h!]
+\center
 \begin{tikzpicture}[
@@
 \begin{table*}
+\center
 \caption{Logical Node Types}
 \label{tab:logicalNodeTypes}
-\begin{tabular}{|c||l|l|l|}
+\begin{tabular}{|c||p{4.6cm}|l|l|}
 \hline
@@
 \begin{table*}
+\center
 \caption{Transaction Types}
 \label{tab:transactionTypes}
-\begin{tabular}{|c||l|l|p{5.8cm}|}
+\begin{tabular}{|c||l|l|p{5cm}|}
 \hline

### 2017-05-22 papers/IoT2017/paper.tex
no message

@@
 \begin{abstract}
-We develop a set of powerful and novel distributed market middleware services that enable local prosumers (a consumer with renewable generation capability) to trade with each other, as well as to bid for power resources, while following the suggested timing constraints.
+We design a secure and efficient trading platform for transactive microgrids, which enables prosumers to trade energy without sacrificing their privacy.
 \end{abstract}
@@
 \section{Introduction}
+
+In order to take advantage of these capabilities, electric grids need to become more decentralized.
+
+%However, simply broadcasting these bids would be catastrophic for privacy, since all the prosumers within a microgrid would learn of each others' expected consumption and production.
+
+Transactive energy may pose a much greater threat to prosumers' privacy than smart metering.
+\begin{itemize}
+\item Firstly, since prosumers may purchase energy from each other in a transactive microgrid, transactions may inadvertently reveal the prosumers' detailed energy usage patterns to other prosumers within the microgrid.
+Addressing this issue in a decentralized trading platform is quite challenging as it requires hiding the identities of trade partners from each other.
+In comparison, secure smart metering reveals the prosumers' energy usage patterns only to the provider. 
+\item Secondly, transactions may reveal the future energy usage of a prosumer, which could be used to infer private information.
+For example, a smart home may know that its inhabitants will go out in the evening (e.g., by looking at their calendar), and it may trade energy futures accordingly in the morning.
+Without adequate privacy measures, these trades may reveal to other prosumers in the microgrid that the inhabitants will not be at home later.
+Note that energy futures, whose delivery may happen several hours after when the transaction is made, can play a very important role in predicting and controlling microgrid load.
+In comparison, smart metering reveals only current (and past) usage.
+\item Thirdly, transactions and energy usage data in a transactive microgrid are much richer source of information than the simple energy usage data collected by smart meters.
+More specifically, the information available in a transactive microgrid is a superset of what is available from smart metering, and it may be used to infer personal information, such as risk propensity and financial standing.
+\end{itemize}
+
+\section{Solution Approaches}
+
+\begin{figure*}[h]
+\center
+\begin{tikzpicture}[x=3.5cm, y=2cm, font=\small,
+  system/.style={draw, align=center, rounded corners=0.1cm, fill=black!5},
+  entity/.style={draw, align=center, rounded corners=0.1cm},
+  asset/.style={midway, align=center},
+  transfer/.style={->, >=stealth, shorten <=0.05cm, shorten >=0.05cm},
+]
+\node[entity] (smartmeter) at (0, 1) {smart\\meter};
+\node[entity] (prosumer1) at (1, 1) {prosumer};
+\node[system] (mixing1) at (2, 1) {mixing\\service};
+\node[entity] (prosumer2) at (3, 1) {prosumer\\(alternative ID)};
+\node[system] (bidstorage) at (4, 1) {bid\\storage};
+\node[entity] (partner) at (4, 0) {other prosumer};
+\node[entity] (prosumer3) at (3, 0) {prosumer\\(alternative ID)};
+\node[system] (mixing2) at (2, 0) {mixing\\service};
+\node[entity] (prosumer4) at (1, 0) {prosumer\\(second alternative ID)};
+
+\draw[transfer] (smartmeter) -- node [asset, above] {energy\\asset} (prosumer1);
+\draw[transfer] (prosumer1) -- node [asset, above] {energy\\asset} (mixing1);
+\draw[transfer] (mixing1) -- node [asset, above] {energy\\asset} (prosumer2);
+\draw[transfer, dashed] (prosumer2) -- node [asset, above] {sell\\bid} (bidstorage);
+\draw[transfer, dashed] (bidstorage) -- node [asset, right] {sell\\bid} (partner);
+\draw[transfer, bend right] (partner) to node [asset, below] {financial\\asset} (prosumer3);
+\draw[transfer] (prosumer2) -- node [asset, above right] {energy\\asset} (partner);
+\draw[transfer] (prosumer3) -- node [asset, below] {financial\\asset} (mixing2);
+\draw[transfer] (mixing2) -- node [asset, below] {financial\\asset} (prosumer4);
+\draw[transfer] (prosumer4) -- node [asset, below left] {financial\\asset} (smartmeter);
+\end{tikzpicture}
+\caption{Simplified overview of transactions for selling energy. Note that in order to prevent de-anonymization, a prosumer should use multiple addresses for mixing.}
+\end{figure*}
+
+\subsection{Communication Anonymity}
+Firstly, we must provide an anonymous communication layer, on which we can build an anonymous trading platform.
+Without this communication layer, bids and transactions could be easily de-anonymized based on the network identifiers of the sources (e.g., IP or MAC addresses).
+
+We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}.
+To build an onion network, the smart meters, inverters, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on a private blockchain.
+In our first implementation, we can use the free and open-source Tor software with private Directory Authorities.
+% ritter.vg: "run your own tor network"
+% https://ritter.vg/blog-run_your_own_tor_network.html
+
+\subsection{Transaction Anonymity}
+We must provide prosumers with the ability to create and publish transactions anonymously.
+More specifically, prosumers should be able to purchase or sell energy without revealing their identity; however, these transaction must also be verifiable and enforceable.
+
+We may achieve this goal using multiple approaches for blockchain transaction anonymity:
+\begin{itemize}
+\item Mixing services (also known as tumblers) mix potentially identifiable assets on a blockchain with others, thereby preventing tracing individual assets back to their original source. 
+In our case, assets to be mixed can include virtual balances of both fiat currencies and energy.
+\item Cryptographic anonymity for transactions is provided, for example, by Zerocoin~\cite{miers2013zerocoin}. Similarly to mixing service, Zerocoin can prevent tracing assets on a blockchain.
+\end{itemize}
+Using the above techniques, we can enable prosumers to trade energy anonymously (i.e., without revealing their true identities), but at the same time prevent them from altering their energy or financial balances without a valid transaction.
+
+However,
+
+\subsection{Bidding Anonymity}
+Finally, we must provide prosumers with the ability to publish energy buy and sell bids anonymously.
+To this end, we create a storage for anonymous bids that is readable by all the prosumers in the microgrid.
+Any prosumer may submit a bid to this storage; however, in order to do so, they must provide a zero-knowledge proof of owning the assets that are to be traded:
+\begin{itemize}
+\item To submit an energy sell bid, the prosumer must prove that it owns an energy production asset on the chain.
+\item To submit an energy buy bid, the prosumer must prove that it own an energy consumption asset as well as financial assets on the chain.
+\end{itemize}
+
+\section{Related Work}
+
+\subsection{Smart Grid and Meter Privacy}
+
+\subsection{Blockchain Technology}
+
+Microsoft offers Blockchain as a Service (BaaS) on Azure.
+Project Bletchley is Microsoft's architectural approach to building an Enterprise Consortium Blockchain Ecosystem, introducing two new concepts: blockchain middleware and cryptlets~\cite{gray2016introducing}.
+
+Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}.
+
+Interledger is a protocol for payments across payment systems, which enables anyone with accounts on two ledgers to create
+a connection between them~\cite{thomas_protocol}.
+
+Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}.
+
+\url{https://geli.net/residential/}
+\url{https://www.greentechmedia.com/articles/read/geli-raises-7m-to-take-energy-storage-software-to-the-next-level}
+
+% BALANCE COLUMNS
+\balance{}
+
+% REFERENCES FORMAT
+% References must be the same font size as other body text.
+\bibliographystyle{SIGCHI-Reference-Format}
+\bibliography{references}
+
+\clearpage
+\appendix
 
@@
 
-\section{Related Work}
-
-Microsoft offers Blockchain as a Service (BaaS) on Azure.
-Project Bletchley is Microsoft's architectural approach to building an Enterprise Consortium Blockchain Ecosystem, introducing two new concepts: blockchain middleware and cryptlets~\cite{gray2016introducing}.
-
-Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}.
-
-Interledger is a protocol for payments across payment systems, which enables anyone with accounts on two ledgers to create
-a connection between them~\cite{thomas_protocol}.
-
-Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}.
-
-\url{https://geli.net/residential/}
-\url{https://www.greentechmedia.com/articles/read/geli-raises-7m-to-take-energy-storage-software-to-the-next-level}
-
-% BALANCE COLUMNS
-\balance{}
-
-% REFERENCES FORMAT
-% References must be the same font size as other body text.
-\bibliographystyle{SIGCHI-Reference-Format}
-\bibliography{references}
-
 \end{document}

### 2017-05-22 papers/IoT2017/paper.tex
no message

@@
 \center
-\begin{tikzpicture}[x=3.5cm, y=2cm, font=\small,
+\begin{tikzpicture}[x=4.15cm, y=2cm, font=\small,
   system/.style={draw, align=center, rounded corners=0.1cm, fill=black!5},
@@
 
-\draw[transfer] (smartmeter) -- node [asset, above] {energy\\asset} (prosumer1);
-\draw[transfer] (prosumer1) -- node [asset, above] {energy\\asset} (mixing1);
-\draw[transfer] (mixing1) -- node [asset, above] {energy\\asset} (prosumer2);
-\draw[transfer, dashed] (prosumer2) -- node [asset, above] {sell\\bid} (bidstorage);
+\draw[transfer] (smartmeter) -- node [asset, above] {energy\\production asset} (prosumer1);
+\draw[transfer] (prosumer1) -- node [asset, above] {energy\\production asset} (mixing1);
+\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
+\draw[transfer, dashed] (prosumer2) -- node [asset, above] {energy production asset,\\sell bid} (bidstorage);
 \draw[transfer, dashed] (bidstorage) -- node [asset, right] {sell\\bid} (partner);
-\draw[transfer, bend right] (partner) to node [asset, below] {financial\\asset} (prosumer3);
-\draw[transfer] (prosumer2) -- node [asset, above right] {energy\\asset} (partner);
-\draw[transfer] (prosumer3) -- node [asset, below] {financial\\asset} (mixing2);
-\draw[transfer] (mixing2) -- node [asset, below] {financial\\asset} (prosumer4);
+\draw[transfer, bend right=15] (partner) to node [asset, below] {financial asset,\\energy\\consumption asset} (prosumer3);
+\draw[transfer, bend right=7.5] (prosumer2) to node [asset, above right] {energy\\prod. asset} (partner);
+\draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
+energy consumption asset} (mixing2);
+\draw[transfer] (mixing2) -- node [asset, below] {financial asset,\\energy consumption asset} (prosumer4);
 \draw[transfer] (prosumer4) -- node [asset, below left] {financial\\asset} (smartmeter);
 \end{tikzpicture}
-\caption{Simplified overview of transactions for selling energy. Note that in order to prevent de-anonymization, a prosumer should use multiple addresses for mixing.}
+\caption{Simplified overview of transactions for selling energy. Note that in order to prevent de-anonymization, a prosumer should use multiple addresses for mixing and multiple rounds of mixing.}
 \end{figure*}
@@
 \item Mixing services (also known as tumblers) mix potentially identifiable assets on a blockchain with others, thereby preventing tracing individual assets back to their original source. 
-In our case, assets to be mixed can include virtual balances of both fiat currencies and energy.
+In our case, assets to be mixed include virtual balances of fiat currencies as well as energy production and consumption.
 \item Cryptographic anonymity for transactions is provided, for example, by Zerocoin~\cite{miers2013zerocoin}. Similarly to mixing service, Zerocoin can prevent tracing assets on a blockchain.
@@
 
-However,
+However, we must also ensure that 1) smart meters know the amount of energy purchased or sold by their prosumer and 2) prosumers cannot purchase or sell more energy than their capacity.
+To satisfy both of these constraints, all energy trades must start with the prosumer withdrawing a certain amount of energy production or consumption from its smart meter:
+\begin{itemize}
+\item If a prosumer wishes to sell energy, it must first obtain an energy asset from its smart meter using a blockchain transaction.
+This transaction must be signed by the smart meter, which enables the smart meter to 1) keep track of the amount of energy traded by the prosumer as well as to 2) enforce safety requirements by limiting the amount of energy that can be withdrawn.
+\item If a prosumer wishes to buy energy, it must first obtain an energy consumption asset from its smart meter in a way similar to obtaining an energy production asset.
+\end{itemize}
 

### 2017-05-24 notes/hyperledger_ethereum_compare_contrast/paper.tex
Adding of Beginning of Compare/Contrast paper/notes between Hyperledger/Ethereum.

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}

% Select what to do with command \comment:  
\newcommand{\comment}[1]{}  %comment not showed
%\newcommand{\comment}[1]
%{\par {\bfseries \color{blue} #1 \par}} %comment showed

%opening
\title{}
\author{}

\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Introduction 
% A. Briefly introduce significance of subject matter 
% B. Thesis statement 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

Distributed power systems require a whole host of boht physical and electronic components to all work to allow for a marketplace to exist that allows for power distribution transactions to occur between the power company and users, but between users. In this paper we focus on the use of different blockchain implementations targetting this domain and discuss which we believe provides a better a distributed ledger.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Brief explanation of Work 1 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Ehtereum}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Brief explanation of Work 2 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Hyperledger Fabric}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Comparative Points
%    Relation of point to first work
%    Relation of point to second work
%    Use specific examples from the readings and texts to support your argument
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Concensus}

Determining concensus in a distributed system such as a ledger is one of the key advances that Bitcoin\comment{find good citation} contributed. However, Bitcoin's concensus methodology Proof-of-Work, is computationally intensive and prevents smaller more specialized ledgers from existing because it would allow for easy 50\%+1 attacks. Hyperledger provides an alternative to proof-of-work called proof-of-stake, where peers in the network are known stakeholders and are assumed to be good actors by default. Peers/Stakeholders are believed to be responsible/good actors because they would be punished by some kind of mechanism outside of the concensus algorithm, such as the fining of money, removal from authorized distributed ledger user list, etc.

\section{System Complexity}

Ethereum when compared to Hyperledger is a much more robust ecosystem of capabilities. However, this robustness comes at the cost of additional system complexity. This complexity isn't just in the size of the codebase required to be maintained, it also includes the additional complexity of managing Ethereum specific currency tokens: Eth. Ethereum lists 4 drawbacks with the Bitcoin scripting language UTXO that is used to process transactions and why it prefers its implementation of Smart Contracts: Lack of Turing-completeness, Value-blindness, Lack of state, and Blockchain-blindness\cite{Buterin2014}. Throughout this paper we discuss each one of these and explain why their drawbacks of bitcoin's implementation aren't applicable in a domain specific usage such as a distributed energy marketplace.

\subsection{Authorization Tokens}

Blockchain is not a new technology or technique, but instead a combination of existing techniques and technologies to provide a distributed ledger. Ethereum requies the use of Ethereum specific tokens(cryptocurrency) to allow transactional edits to the distributed ledger to occur. Ethereum calls these tokens Ether and can be subdivided on a as-needed basis. However, Hyperledger doesn't require any authorization token to allow edits to the distributed ledger. Hyperledger's approach is more direct and doesn't require the pre-propagation of any sort of authorization token(s) to the nodes in the network before operations can begin when using the proof-of-stake concensus model. This cuts down on operational complexity and encourages the use of ledger as a distributed logging platform at all levels since there is no 'cost' for each log statement. A counter-argument can be made that Ethereum's approach of authorization tokens makes developers more selfconscious about what information they deem 'worthy' of logging to the distributed ledger. However, in the domain of distributed power grids, it is our belief that the scope of potential related transactions is small enough to encourage, indead of discourage, developers to make use of the distributed ledger. Ethereum's 'Value-blindness' and 'Blockchain-blindness' drawbacks are both eliminated with the usage of a system without authorization tokens.

\subsection{Code Complexity}

Ethereum contains an entire virtual machine in which Turing-Complete Smart Contracts are ran to make modifications of the Ethereum blockchain. Whereas Hyperledger is only a library that allows for simple TCP/IP connections to be made between hosts and for custom written code to be executed to handle transactions. A case can be made that Ethereum's Smart-Contracts provide a faster turnaround when adding new features to the system. However, this comes with a significant increase in complexity of the blockchain ledger-portion of any system.

\section{Security}

The nature of the Turing-Complete virtual machine that Ethereum runs to process the transactions on the ledger inherently adds another layer of potential security vulnerabilities that need to be addressed before, during, and after deployment. The RIAPS platform already provides a means for deployed nodes to recieve updates to the code they are running.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Conclusion
%   Restate thesis
%   Brief summary of how you proved your argument
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

\bibliography{blockchain} 
\bibliographystyle{ieeetr}

\end{document}

### 2017-05-31 papers/IoT2017/paper.tex
no message

@@
 
+\usepackage{paralist}
+
 \usepackage{tikz}
@@
 \newcommand{\TODO}[1]{\todo[inline]{#1}}
+
+\newcommand{\field}[1]{\texttt{#1}}
 
@@
 
+% electric grid is changing: renewables, storage capacity, etc. -> prosumers
+
 In order to take advantage of these capabilities, electric grids need to become more decentralized.
 
-%However, simply broadcasting these bids would be catastrophic for privacy, since all the prosumers within a microgrid would learn of each others' expected consumption and production.
+% transactive microgrid
+
+% there are pilot studies, however, providing privacy is an open problem
 
@@
 
-\section{Solution Approaches}
+We propose a solution that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, enables the DSO to regulate the trading platform and enforce certain safety rules.
+
+\section{Preliminaries and Requirements}
+
+\subsection{Transactive Microgrid}
+
+Here, we describe a basic system model for a transactive microgrid based on a distributed ledger, such as a blockchain.
+% - smart meters
+% - distributed ledger, such as blockchain
+
+\subsubsection{Distributed Ledger}
+The distributed ledger stores transactions that specify energy trades, change regulatory policies for the microgrid, etc.
+Since the ledger is maintained by multiple ledger nodes, a key implementation requirement is reaching consensus on which transactions are valid and stored in the ledger.
+This consensus must be reached quickly, reliably, and securely even in the presence of erroneous or even malicious ledger nodes.
+We treat the consensus algorithm as a pluggable module, which can be based on blockchains with proof-of-stake consensus or Practical Byzantine Fault Tolerance algorithm~\cite{castro1999practical}.
+
+\subsubsection{Bid Storage Service}
+Although individual prosumers trade energy with each other, for the sake of scalability, we need a service that enables prosumers to find trade partners.
+By providing a storage service for buy and sell bids, we relieve prosumer nodes from communicating with all potential trade partners.
+In addition to receiving and storing bids from prosumers, the bid storage service can also find matches and notify prosumers of the opportunity to make an energy trade.
+Even though the bid storage appears to the nodes as one entity, for the sake of scalability and reliability, it can be implemented in a distributed manner, using multiple nodes.
+
+\subsubsection{Microgrid Controller}
+The microgrid controller is responsible for stabilizing load within the microgrid and controlling it based on the expected load in the rest of the grid.
+To this end, the controller first estimates the expected load in the microgrid based on buy and sell bids in the bid storage as well as on outstanding energy trades in the ledger.
+By combining this estimate with the expected load in the remainder of the grid, the controller produces a control signal that specifies how much the microgrid load should be decreased or increased.
+Finally, based on this control signal, the controller updates the price policy for the microgrid to influence energy production and consumption.
+
+\subsection{Requirements}
+
+\subsubsection{Security}
+Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.
+
+\subsubsection{Safety}
+A careless or malicious prosumer may destabilize the grid by promising to produce (or consume) a large amount of energy, but failing to deliver.
+Trades which are unlikely to be delivered and would result in a gap between actual production and demand should be prevented.
+
+\subsubsection{Privacy} 
+Energy trading should not compromise the privacy of prosumers.
+More specifically, prosumers' private information, including energy consumption and production values, are available only to the DSO.
+
+\section{Solution}
+
+In section, we describe our solution for providing privacy for prosumers without compromising the safety and security of the microgrid.
+Figure~\ref{fig:softwareArchitecture} shows a high-level overview of the architecture of our solution.
+
+\begin{figure}[h!]
+\center
+\begin{tikzpicture}[x=8cm, y=1.2cm,
+  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
+]
+\draw [nodeStyle, fill=white]   (0, 0) rectangle    (1, 0.9) node [midway, align=center] {Communication network\\and operating system};
+
+\draw [nodeStyle, fill=red!10]  (0, 1) rectangle    (1, 1.9) node [midway, align=center] {Communication anonymity\\(onion routing)};
+
+\draw [nodeStyle, fill=blue!10] (0, 2) rectangle    (1, 2.9) node [midway, align=center] {Distributed ledger\\(blockchain)};
+
+\draw [nodeStyle, fill=red!10]  (0,    3) rectangle (0.45, 3.9) node [midway, align=center] {Transaction anonymity\\(mixing service)};
+\draw [nodeStyle, fill=blue!10] (0.47, 3) rectangle (0.72, 3.9) node [midway, align=center] {Bid storage};
+\draw [nodeStyle, fill=red!10 ] (0.74, 3) rectangle (1,    3.9) node [midway, align=center] {Active\\smart meter};
+
+\draw [nodeStyle, fill=blue!10] (0,    4) rectangle (0.49, 4.9) node [midway, align=center] {Prosumer trading\\algorithm};
+\draw [nodeStyle, fill=blue!10] (0.51, 4) rectangle (1,    4.9) node [midway, align=center] {DSO control\\algorithm};
+\end{tikzpicture}
+\caption{High-level architecture of the proposed solution.
+Components marked red are introduced to provide privacy in a safe and secure manner.
+Components marked in blue are typical elements of a decentralized transactive microgrid.}
+\label{fig:softwareArchitecture}
+\end{figure}
 
@@
 \center
-\begin{tikzpicture}[x=4.15cm, y=2cm, font=\small,
+\begin{tikzpicture}[x=3.8cm, y=2cm, font=\small,
   system/.style={draw, align=center, rounded corners=0.1cm, fill=black!5},
@@
 ]
-\node[entity] (smartmeter) at (0, 1) {smart\\meter};
+%\node[entity] (smartmeter) at (0.75, 0.5) {smart\\meter};
+%\node[entity] (prosumer1) at (1.25, 1) {prosumer};
+%\node[system] (mixing1) at (2, 1) {mixing\\service};
+%\node[entity] (prosumer2) at (3, 1) {prosumer\\(alternative address)};
+%\node[system] (bidstorage) at (4, 1) {bid\\storage};
+%\node[entity] (partner) at (4, 0) {other prosumer};
+%\node[entity] (prosumer3) at (3, 0) {prosumer\\(alternative address)};
+%\node[system] (mixing2) at (2, 0) {mixing\\service};
+%\node[entity] (prosumer4) at (1.25, 0) {prosumer};
+\node[entity] (smartmeter) at (0, 1) {smart meter};
 \node[entity] (prosumer1) at (1, 1) {prosumer};
-\node[system] (mixing1) at (2, 1) {mixing\\service};
-\node[entity] (prosumer2) at (3, 1) {prosumer\\(alternative ID)};
-\node[system] (bidstorage) at (4, 1) {bid\\storage};
-\node[entity] (partner) at (4, 0) {other prosumer};
-\node[entity] (prosumer3) at (3, 0) {prosumer\\(alternative ID)};
-\node[system] (mixing2) at (2, 0) {mixing\\service};
-\node[entity] (prosumer4) at (1, 0) {prosumer\\(second alternative ID)};
+\node[system] (mixing1) at (1.9, 1) {mixing\\service};
+\node[entity] (prosumer2) at (3, 1) {prosumer\\(anonymous address)};
+\node[system] (bidstorage) at (4, 0.5) {bid\\storage};
+\node[entity] (partner) at (3, 0) {other prosumer};
+\node[entity] (prosumer3) at (1.5, 0) {prosumer\\(anonymous address)};
+\node[entity] (smartmeter2) at (0, 0) {smart meter\\(anonymous address)};
+
+%\draw[transfer] (smartmeter) -- node [asset, above left] {energy\\production asset} (prosumer1);
+%\draw[transfer] (prosumer1) -- node [asset, above] {energy\\production asset} (mixing1);
+%\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
+%\draw[transfer, dashed] (prosumer2) -- node [asset, above] {energy production asset,\\sell bid} (bidstorage);
+%\draw[transfer, dashed] (bidstorage) -- node [asset, right] {sell\\bid} (partner);
+%\draw[transfer, bend right=15] (partner) to node [asset, below] {financial asset,\\energy\\consumption asset} (prosumer3);
+%\draw[transfer, bend right=7.5] (prosumer2) to node [asset, above right] {energy\\prod. asset} (partner);
+%\draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
+%energy consumption asset} (mixing2);
+%\draw[transfer] (mixing2) -- node [asset, below] {financial asset,\\energy consumption asset} (prosumer4);
+%\draw[transfer] (prosumer4) -- node [asset, below left] {financial\\asset} (smartmeter);
 
@@
 \draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
-\draw[transfer, dashed] (prosumer2) -- node [asset, above] {energy production asset,\\sell bid} (bidstorage);
-\draw[transfer, dashed] (bidstorage) -- node [asset, right] {sell\\bid} (partner);
-\draw[transfer, bend right=15] (partner) to node [asset, below] {financial asset,\\energy\\consumption asset} (prosumer3);
-\draw[transfer, bend right=7.5] (prosumer2) to node [asset, above right] {energy\\prod. asset} (partner);
+\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {energy production asset,\\sell bid} (bidstorage);
+\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {sell\\bid} (partner);
+\draw[transfer, bend right=30] (partner) to node [asset, below] {financial asset,\\energy consumption asset} (prosumer3);
+\draw[transfer, bend right=50] (prosumer2) to node [asset, right] {energy\\production asset} (partner);
 \draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
-energy consumption asset} (mixing2);
-\draw[transfer] (mixing2) -- node [asset, below] {financial asset,\\energy consumption asset} (prosumer4);
-\draw[transfer] (prosumer4) -- node [asset, below left] {financial\\asset} (smartmeter);
+energy consumption asset} (smartmeter2);
 \end{tikzpicture}
-\caption{Simplified overview of transactions for selling energy. Note that in order to prevent de-anonymization, a prosumer should use multiple addresses for mixing and multiple rounds of mixing.}
+\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy production.
+Note that in order to prevent de-anonymization, a prosumer should use multiple addresses for mixing and multiple rounds of mixing.}
 \end{figure*}
 
-\subsection{Communication Anonymity}
+\subsection{Timing}
+The ability to specify points or intervals in time is crucial.
+For example, control signals specify how the load should change at certain points in time, energy trades specify when energy will be consumed or produced, etc.
+To facilitate processing signals and transactions, we divide time into fixed-length intervals, and specify points or periods in time using these discrete timesteps.
+The length of the time interval is determined by mapping the timing assumptions of the power system to our platform.
+%In our implementation, 
+For example, the default length of the time interval may be 4 seconds, which corresponds to how frequently the control signal of the DSO typically changes.
+
+\subsection{Services}
+
+Here, we describe three services that must be implemented for our solution: communication anonymity, mixing service for transaction anonymity, and anonymous bid storage for bidding anonymity.
+
+\subsubsection{Communication Anonymity}
 Firstly, we must provide an anonymous communication layer, on which we can build an anonymous trading platform.
@@
 
-\subsection{Transaction Anonymity}
+\subsubsection{Transaction Anonymity}
 We must provide prosumers with the ability to create and publish transactions anonymously.
@@
 
-\subsection{Bidding Anonymity}
+\subsubsection{Bidding Anonymity}
 Finally, we must provide prosumers with the ability to publish energy buy and sell bids anonymously.
@@
 
+\subsection{Transaction Types}
+
+Before we can discuss transaction types, we must first define the three assets that these transactions may transfer.
+
+An \emph{energy production asset} (EPA) is defined by
+\begin{compactitem}
+\item \field{power}: non-negative amount of power to produced (for example, measured in watts).
+\item \field{start}: first time interval in which energy is to be produced. 
+\item \field{end}: last time interval in which energy is to be produced.
+\end{compactitem}
+An \emph{energy consumption asset} (ECA) is defined by the same fields; however, for this asset, the fields define consumption instead of production.
+Finally, a \emph{financial asset} (FA) is defined by a single non-negative field \field{amount}, which can be denominated in either a fiat currency (e.g., US dollars) or a cryptocurrency.
+
+\subsubsection{Energy and Financial Transactions}
+
+Energy and financial transactions transfer energy and financial asset from one address to another.
+Prosumers use these transactions for multiple purposes: to trade energy by exchanging assets with other prosumers, to prove to the bid storage that they have production or consumption capacity, to hide their identity by transferring assets to and from mixing services, and to deposit assets at their smart meter.
+%
+An energy and financial transaction contains the following fields:
+\begin{compactitem}
+\item List of EPA inputs, each of which is defined by:
+\begin{compactitem}
+\item \field{out}: EPA output from a previous transaction,
+\item \field{sig}: signature for this output.
+\end{compactitem}
+\item List of ECA inputs, each of which is defined by:
+\begin{compactitem}
+\item \field{out}: ECA output from a previous transaction,
+\item \field{sig}: signature for this output.
+\end{compactitem}
+\item List of FA inputs, each of which is defined by:
+\begin{compactitem}
+\item \field{out}: FA output from a previous transaction,
+\item \field{sig}: signature for this output.
+\end{compactitem}
+\item List of EPA outputs, each of which is defined by:
+\begin{compactitem}
+\item an EPA and an address to which it is transferred.
+\end{compactitem}
+\item List of ECA outputs, each of which is defined by:
+\begin{compactitem}
+\item an ECA and an address to which it is transferred.
+\end{compactitem}
+\item List of FA outputs, each of which is defined by:
+\begin{compactitem}
+\item an FA and an address to which it is transferred.
+\end{compactitem}
+\end{compactitem}
+
+An energy and financial transaction is valid if the following three conditions hold.
+\begin{compactitem}
+\item None of the outputs referenced by the inputs have been spent by a transaction that has been recorded on the ledger.
+\item All of the signatures are valid.
+\item For each asset type (and for each timestep), the sum of inputs and outputs is the same.
+For example, in the case of energy production assets, the condition is:
+\begin{align}
+\forall t: & \sum_{out \in \text{EPA outputs}} out.\mathtt{power} \cdot 1_{\left\{out.\mathtt{start} \leq t \leq out.\mathtt{end}\right\}} \nonumber \\
+& = \sum_{in \in \text{EPA inputs}} in.\mathtt{out}.\mathtt{power} \cdot 1_{\left\{in.\mathtt{out}.\mathtt{start} \leq t \leq in.\mathtt{out}.\mathtt{end}\right\}} ,
+\end{align}
+where $1_x$ is equal to $1$ if $x$ is true, and it is $0$ otherwise.
+%\begin{equation}
+%\forall t: \sum_{out \in \left\{out' \middle| out' \in \text{ EPA outputs} \wedge out'.EPA.start \leq t \leq out'.EPA.end\right\}} out.EPA.Power = \sum_{in \in \left\{in' \middle| in' \in \text{ EPA inputs} \wedge in'.EPA.start \leq t \leq in'.EPA.end\right\}} in.EPA.Power .
+%\end{equation}
+\end{compactitem}
+If a transaction submitted to the ledger is valid, it will be permanently recorded.
+
+\subsubsection{Smart-Meter Transactions}
+
+Prosumers use smart-meter transactions to withdraw energy and financial assets from their own smart meters, before they engage in energy trading.
+%
+A smart-meter transaction contains the following fields:
+\begin{compactitem}
+\item List of EPA outputs, each of which is defined by:
+\begin{compactitem}
+\item an EPA and an address to which it is transferred.
+\end{compactitem}
+\item List of ECA outputs, each of which is defined by:
+\begin{compactitem}
+\item an ECA and an address to which it is transferred.
+\end{compactitem}
+\item List of FA outputs, each of which is defined by:
+\begin{compactitem}
+\item an FA and an address to which it is transferred.
+\end{compactitem}
+\item \field{id}: Identifier of the smart meter.
+\item \field{sig}: Smart meter's signature over the transaction.
+\end{compactitem}
+
+A smart-meter transaction is valid if the following two conditions hold:
+\begin{compactitem}
+\item The smart meter identified in the transaction has been authorized by a regulatory transaction that has been recorded on the ledger.
+\item The smart meter's signature is valid.
+\end{compactitem}
+\todo{To address malfunctioning or compromised smart meters, we could also impose a limit on withdrawals.}
+
+\subsubsection{Regulatory Transactions}
+
+The DSO uses regulatory transactions to authorize or ban smart meters and to control the microgrid load through setting a price policy.
+Since these transactions provide a diverse set of functionality, they are divided into two types.
+
+\paragraph{Authorize or Ban Smart Meters}
+The DSO uses these transactions to manage the set of authorized smart meters in the microgrid.
+Whenever a new smart meter is installed, the DSO notifies the members of the microgrid using a regulatory transaction.
+Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or it is believed to be malfunctioning or compromised), the DSO notifies the members of the microgrid using a regulatory transaction.
+These transactions contain the following fields:
+\begin{compactitem}
+\item List of smart meters to be authorized, each of which is defined by:
+\begin{compactitem}
+\item \field{id}: Identifier of the smart meter.
+\item \field{pubkey}: Public key of the smart meter.
+\end{compactitem}
+\item List of smart meters to be banned, each of which is given using its identifier.
+\item \field{time}: Timestep in which smart meters are authorized and banned.
+\item \field{sig}: DSO's signature over the transaction.
+\end{compactitem}
+
+A regulatory transaction of this type is valid if the following two conditions hold:
+\begin{compactitem}
+\item The timestep specified in the transaction is in the future.
+\item The DSO's signature is valid.
+\end{compactitem}
+
+\paragraph{Price Policy}
+
+\section{Analysis}
+\label{sec:analysis}
+
+Here, we present a semi-formal analysis of the proposed solution, and show that it satisfies the security, safety, and privacy requirements.
+
+\subsection{Security}
+
+\subsection{Safety}
+
+\subsection{Privacy}
+
+Due to the communication anonymity and mixing services, members of a microgrid can see only the amount of energy and financial assets withdrawn by a prosumer.
+Since all trading transactions are anonymous, the amount of assets traded by the prosumer will not be publicly known.
+In case a prosumer does not wish to trade, it can anonymously deposit its assets to a random address that was freshly generated by its smart meter.
+Note that even if a prosumer does not wish to trade, it should always withdraw and mix assets; otherwise, the lack of withdrawal would leak information.
+
+As for the DSO, it can receive the same information from the smart meter as in a non-transactive grid (i.e., amount of energy produced and consumed).
+\todo{Also knows financial amounts, but those are necessary for billing.}
+Since trading is anonymous, it does not receive any further information.
+
+In fact, we can provide an even higher-level of privacy.
+Since price policies are recorded on the ledger, which the smart meters may read, the smart meters can calculate the prosumer's monthly bill, and send only this single financial amount to the DSO each month.
+Meanwhile, the DSO can still obtain current and future load information from the bid storage and from the trades recorded on the ledger.
+
 \section{Related Work}
+\label{sec:related}
 
@@
 \url{https://www.greentechmedia.com/articles/read/geli-raises-7m-to-take-energy-storage-software-to-the-next-level}
+
+\section{Conclusion}
+\label{sec:concl}
 

### 2017-05-31 papers/IoT2017/paper.tex
no message

@@
 \begin{abstract}
+While transactive microgrids must satisfy the same security requirements as non-transactive ones, they must also satisfy additional safety and privacy requirements.
 We design a secure and efficient trading platform for transactive microgrids, which enables prosumers to trade energy without sacrificing their privacy.
@@
 In order to take advantage of these capabilities, electric grids need to become more decentralized.
+% what are the advantages of decentralization?
 
@@
 % there are pilot studies, however, providing privacy is an open problem
+For example, the Brooklyn Microgrid developed by LO3 Energy is a peer-to-peer energy market for locally generated renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}
 
@@
 
+% http://ieeexplore.ieee.org/abstract/document/5054916/
+McDaniel and McLaughlin discuss privacy challenges in smart grids~\cite{mcdaniel2009security}.
+
+% https://arxiv.org/pdf/1108.2234.pdf
+% https://pdfs.semanticscholar.org/cdf8/a5b6256823bca38a1d2347ab36f8e4a2ca94.pdf
+Rajagopalan et al.\ use tools from information theory to present a framework, which abstracts both the privacy and the utility requirements of smart meter data~\cite{rajagopalan2011smart,sankar2013smart}.
+Their framework leads to a novel privacy-utility tradeoff problem with minimal assumptions.
+%, which is tractable.
+
+% http://www.comm.toronto.edu/~akhisti/sm.pdf
+Varodayan and Khisti study using rechargeable battery for partially protecting the privacy of information contained in a household's electrical load profile~\cite{varodayan2011smart}.
+They show that stochastic battery policies may leak 26\% less information than a best-effort policy, holds the output load constant whenever possible.
+
+% https://www.researchgate.net/profile/Georgios_Kalogridis/publication/224189766_Smart_Grid_Privacy_via_Anonymization_of_Smart_Metering_Data/links/541169510cf2b4da1bec4193.pdf
+Efthymiou and Kalogridis describe a method for securely anonymizing frequent electrical metering data sent by a smart meter~\cite{efthymiou2010smart}. 
+Their approach is based on the observation that frequent metering data may be required by an energy distribution network for operational reasons, but it may not necessarily need to be attributable to a specific smart meter.
+The authors describe a method that provides a third-party escrow mechanism for authenticated anonymous meter readings, which are difficult to associate with particular smart meter.
+
+% https://arxiv.org/pdf/1305.0735.pdf
+Tan et al.\ study privacy in a smart metering system from an information theoretic perspective in the presence of energy harvesting and storage units~\cite{tan2013increasing}. 
+They show that energy harvesting provides increased privacy by diversifying the energy source, while a storage device can be used to increase both energy efficiency and privacy. 
+They show that there exists a trade-off between the information leakage rate and the wasted energy rate, and study the impact of the energy harvesting rate and the size of the storage device on this trade-off.
+
 \subsection{Blockchain Technology}
@@
 
-\clearpage
-\appendix
-
-\section{Architecture Overview}
-
-\begin{figure}[h!]
-\center
-\begin{tikzpicture}[
-  x=1.04cm,
-  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.04cm, shadow yshift=-0.05cm, fill=black}}]
-
-\draw [fill=blue!5, nodeStyle] (0, 3.07) rectangle (1.55, 3.93) node [midway, align=center, font=\small] {Trading\\[-0.2em]Node};
-\draw [fill=blue!5, nodeStyle] (1.65, 3.07) rectangle (3.15, 3.93) node [midway, align=center, font=\small] {Ledger\\[-0.2em]Node};
-\draw [fill=blue!5, nodeStyle] (3.25, 3.07) rectangle (4.75, 3.93) node [midway, align=center, font=\small] {Prosumer\\[-0.2em]Node};
-\draw [fill=blue!5, nodeStyle] (4.85, 3.07) rectangle (6.35, 3.93) node [midway, align=center, font=\small] {Smart Meter\\[-0.2em]Node};
-\draw [fill=blue!5, nodeStyle] (6.45, 3.07) rectangle (8.0, 3.93) node [midway, align=center, font=\small] {DSO\\[-0.2em]Node};
-
-\draw [fill=red!5, nodeStyle] (0, 2.07) rectangle (3.95, 2.93) node [midway] {Trading Platform};
-\draw [fill=red!5, nodeStyle] (4.05, 2.07) rectangle (8, 2.93) node [midway] {Distributed Ledger};
-
-\draw [fill=green!5, nodeStyle] (0, 1.07) rectangle (3.95, 1.93) node [midway] {RIAPS};
-\draw [fill=green!5, nodeStyle] (4.05, 1.07) rectangle (8, 1.93) node [midway] {Cryptographic Libraries};
-
-\draw [fill=black!5, nodeStyle] (0, 0.07) rectangle (8, 0.93) node [midway] {Operating System};
-\end{tikzpicture}
-\caption{High-level software architecture.}
-\label{fig:softwareArchitecture}
-\end{figure}
-
-Figure~\ref{fig:softwareArchitecture} shows a high-level overview of the software architecture of our system.
-Our system is -- in part -- built on the Resilient Information Architecture for Smart Grid (RIAPS) platform~\cite{eisele2017riaps}.
-
-Figure~\ref{fig:logicalNodeArchitecture} shows a high-level overview of the trading platform, the distributed ledger, and the logical nodes implementing and interacting with these subsystems.
-
-\paragraph{Trading Platform}
-Although individual prosumers trade energy with each other, for the sake of scalability, we need a trading platform that enables prosumers to find trade partners.
-By serving as a database for energy bids, the trading platform relieves prosumer nodes from communicating with all potential trade partners.~%
-\footnote{Note that prosumers are not required to use the services of the trading platform, and they are allowed to communicate with each other for the sake of finding trade partners.
-However, in a microgrids with a large number prosumers, the trading platform will be able to find partners more efficiently and promptly.}
-In addition to receiving and storing bids from prosumers, the trading platform can also find matches and notify the prosumers of the opportunity to make an energy trade.
-Even though the trading platform appears to the nodes as one entity, for the sake of scalability and reliability, it can be implemented in a distributed manner, using multiple trading nodes.
-
-\paragraph{Distributed Ledger}
-The distributed ledger stores transactions that specify energy trades, record energy production and consumption, and change regulatory policies for the microgrid, including energy prices.
-Since the ledger is maintained by multiple ledger nodes, a key implementation requirement is reaching consensus on which transactions are valid and stored in the ledger.
-This consensus must be reached quickly, reliably, and securely even in the presence of erroneous or even malicious ledger nodes.
-We treat the consensus algorithm as a pluggable module, which can be based on blockchains with proof-of-stake consensus or Practical Byzantine Fault Tolerance algorithm~\cite{castro1999practical}.
-
-\paragraph{Controller}
-The controller is responsible for stabilizing load within the microgrid and controlling it based on the expected load in the rest of the grid.
-To this end, the controller first estimates the expected load in the microgrid based on outstanding energy trades on the ledger.
-By combining this estimate with the expected load in the remainder of the grid, the controller produces a control signal that specifies how much the load in the microgrid needs to be decreased or increased.
-Finally, based on this control signal, the controller updates the price policy for the microgrid to influence energy production and consumption.
-The controller may be implemented by the DSO node, as part of the RIAPS-based platform, or may be a legacy controller that interfaces with the DSO node.
-
-\input{figArchitecture.tex}
-
-\subsection{Timing}
-
-Timing is a crucial part of our platform.
-For example, control signals specify how the load should change at certain points in time, energy trades specify when energy will be consumed or produced, etc.
-To facilitate processing signals and transactions, we divide time into fixed-length intervals, and specify points or periods in time using these discrete time intervals.
-The length of the time interval is determined by mapping the timing assumptions of the power system to our platform.
-In our implementation, for example, the default length of the time interval is 4 seconds, which corresponds to how frequently the control signal of the DSO changes.
-
-\begin{figure}[h!]
-\center
-\begin{tikzpicture}[
-  x=1.6cm,
-  font=\small,
-  nodeStyle/.style={fill=white, draw=black, drop shadow=black!30, minimum size=0.5cm},
-  arrowStyle/.style={->, >=stealth, shorten >=1.5pt, shorten <=1.5pt},
-  transactionStyle/.style={draw, align=center, fill=black!10, font=\footnotesize}]
-\draw [->, >=stealth] (0.6, 0) -- (5.4, 0) node [right] {time};
-
-\foreach \pos in {1, 2, 3, 4, 5}
-  \draw (\pos, 0.06cm) -- (\pos, -0.06cm);
-
-\foreach \pos/\name in {{1/$T-2$}, {2/$T-1$}, {3/$T$}, {4/$T+1$}}
-  \draw[decorate, decoration={brace,amplitude=0.15cm}, yshift=-0.12cm] ({\pos+0.95}, 0) -- ({\pos+0.05}, 0) node [midway, below=0.15cm, font=\small] {\name};
-
-\node [nodeStyle, rounded corners=0.1cm] (prosumer) at (1.5, 1.5) {};
-\node [nodeStyle, diamond] (smartmeter) at (4.5, 1.5) {};
-
-\node [above=-0.05cm of prosumer] {prosumer};
-\node [above=0cm of smartmeter] {smartmeter};
-
-\node [transactionStyle] (financial) at (1.5, 0.5) {financial\\[-0.25em]transaction};
-\node [transactionStyle] (energy) at (4.5, 0.5) {energy\\[-0.25em]transaction};
-
-\draw [arrowStyle] (prosumer) -- (financial);
-\draw [arrowStyle] (smartmeter) -- (energy);
-
-\draw [arrowStyle, dashed] (financial) -- (3.25, 0.5) node [midway, above] {promise} -- (3.25, 0);
-\draw [arrowStyle, dashed] (energy) -- (3.5, 0.5) node [midway, above] {record} -- (3.5, 0);
-\end{tikzpicture}
-\caption{Basic timeline of transactions.}
-\label{fig:timeline}
-\end{figure}
-
-All transactions for energy trading are specified with respect to these discrete intervals: financial transactions promise to consume or produce a certain amount of energy in a future interval, while energy transactions record the actual amount of energy produced or consumed in an earlier interval.
-Figure~\ref{fig:timeline} shows a basic timeline of financial and energy transactions.
-
-\begin{table*}
-\center
-\caption{Logical Node Types}
-\label{tab:logicalNodeTypes}
-\begin{tabular}{|c||p{4.6cm}|l|l|}
-\hline
-\textbf{Type} & \textbf{Function} & \textbf{Cardinality} & \textbf{Physical node} \\
-\hline\hline
-\rowcolor{Gray} Ledger      & maintain distributed ledger                 & one or more           & any node (with enough computational power) \\ \hline
-                Trading     & provide trading platform                    & one or more           & any node (with enough computational power) \\ \hline
-\rowcolor{Gray} Prosumer    & trade electricity (on behalf of a prosumer) & one for each prosumer & smart inverter or smart meter \\ \hline
-                Smart meter & record power consumption and production     & one for each prosumer & smart meter (must be trusted hardware) \\ \hline
-\rowcolor{Gray} DSO         & regulate microgrid electricity market       & one                   & node owned by the DSO \\ \hline
-\end{tabular}
-\end{table*}
-
-\subsection{Logical Nodes}
-
-Next, we discuss the five types of logical nodes in our system: ledger, trading, prosumer, smart meter, and DSO nodes.
-Table~\ref{tab:logicalNodeTypes} shows an overview of these logical-node types.
-
-Every node has a pair of public and private keys as well as a digital certificate from the DSO, which proves the ownership of the public key.
-The nodes can use the key pair and the certificate to prove their identity and to sign messages or transactions.
-A digital certificate may also specify the capabilities of a node.
-For example, the certificate of a prosumer node may specify the amount of energy that the node is allowed to trade for a single time interval.
-% physical node certificates may also describe roles that may be taken by the physical node
-% In addition to capabilities, the certificate may also describe roles, that is, logical nodes that can be implemented by the physical node.
-
-\subsubsection{Ledger nodes}
-Ledger nodes implement the distributed ledger by forming a peer-to-peer network with each other and reaching a consensus on the state of the ledger.
-A ledger node is responsible for receiving financial transactions from prosumer nodes, energy transactions from smart-meter nodes, and regulatory transactions from the DSO node.
-The ledger nodes share these transactions with each other, verify them, and reach a consensus on which transactions are recorded in the ledger.
-
-\subsubsection{Trading nodes}
-Trading nodes implement the distributed trading platform by forming a peer-to-peer network with each other and providing services for prosumer nodes.
-A trading node is responsible for receiving bids from prosumer nodes, sharing these bids with the other trading nodes, maintaining a distributed database of active bids, trying to match bids with each other, and notifying the prosumers of matches.
-While this platform is similar to the distributed ledger in many ways, it is subject to much less stringent requirements.
-For example, the trading platform does not have to store history in a reliable and verifiable manner.
-Consequently, trading nodes can be implemented by computationally less capable physical nodes (e.g., with limited storage).
-
-\begin{table*}
-\center
-\caption{Transaction Types}
-\label{tab:transactionTypes}
-\begin{tabular}{|c||l|l|p{5cm}|}
-\hline
-\textbf{Type} & \textbf{Creator} & \textbf{Contents} & \textbf{Validity} \\
-\hline\hline
-\rowcolor{Gray} Financial  & prosumers    & identifiers, signatures, time interval, amount of energy & signed by buyer and seller, abides by the safety and security rules \\ \hline
-                Energy     & smart meters & identifier, signature, time interval, amount of energy   & signed by smart meter \\ \hline
-\rowcolor{Gray} Regulatory & DSO          & signature, time interval, set of policy updates            & signed by DSO \\ \hline
-\end{tabular}
-\end{table*}
-
-\subsubsection{Prosumer nodes}
-Each prosumer node represents a prosumer, such as a residential customer.
-A prosumer node trades future electricity consumption and production on behalf of the prosumer.
-As a first step in electricity trading, the prosumer node estimates the net energy demand of the prosumer for a future time interval.
-At the same time, it queries the active regulatory policies, such as energy prices, from the distributed ledger.
-Based on the estimated net demand and the active regulatory policies, it creates an energy trading bid, which it then submits to the trading platform.
-If the trading platform responds with one (or more) matching bid, then the prosumer node contacts the node that submitted a matching bid.
-The two nodes negotiate, agree on, create, and sign a new financial transaction, which they then submit to the distributed ledger.
-\todo[inline]{Extend: prosumer nodes may buy/sell electricity from/to DSO in advance. This is key to load prediction.}
-Once the ledger has verified and recorded the transaction, the electricity trade has been set up.
-
-\subsubsection{Smart-meter nodes}
-Each smart-meter node measures the actual energy production and consumption of a prosumer.
-For each time interval, the smart-meter node measures the net energy consumption of the prosumer, records the net consumption in an energy transaction, and then signs the transaction and submits it to the distributed ledger.
-To ensure that the smart-meter node measures the correct amount of net consumption, the node must always be implemented by a trusted smart meter deployed at the prosumer.
-Furthermore, we assume that the smart-meter devices are tamper-proof hardware, which prevents tampering attacks by the prosumers (e.g., to avoid paying for electricity).
-
-\subsubsection{DSO node}
-The DSO node represents the Distribution System Operator, and it is responsible for regulating the microgrid market using regulatory transactions.
-These transactions enable the DSO, for example, to set a price policy for the microgrid or to remove misbehaving nodes by revoking their certificates.
-Note that in order to enhance reliability and security, the DSO node may be split into multiple logical nodes.
-For example, the DSO node can be split into a pricing node, which is authorized and responsible for setting the price policy, and a revocation node, which is authorized and responsible for revoking digital certificates.
-
-\subsection{Transactions}
-
-Transactions on the distributed ledger can be divided into three main types: financial, energy, and regulatory transactions.
-Table~\ref{tab:transactionTypes} shows an overview of these transaction types.
-
-\subsubsection{Financial Transactions}
-A financial transaction represents an agreement between two prosumers, called the seller and the buyer, who promise to respectively produce and consume a certain amount of energy in a future time interval.
-
-A financial transaction contains the following fields:
-\todo[inline]{Extend: prosumer nodes may buy/sell electricity from/to DSO in advance. This is key to load prediction.}
-\begin{itemize}
-\item \textbf{Seller ID}: Unique identifier of the selling prosumer node.
-\item \textbf{Buyer ID}: Unique identifier of the buying prosumer node.
-\item \textbf{Monetary value}: Value paid by the buyer to the seller, which can be denominated in either a fiat currency (e.g., US dollars) or a cryptocurrency.
-\item \textbf{Time interval}: Identifier of the time interval in which energy will be produced and consumed.
-\item \textbf{Energy value}: Amount of energy produced by the seller and consumed by the buyer.
-\item \textbf{Seller signature}: Digital signature created using the private key of the seller, computed over all previous fields.
-\item \textbf{Buyer signature}: Digital signature created using the private key of the seller, computed over all previous fields except the seller signature.
-\end{itemize}
-
-The ledger nodes accept and record a financial transaction if
-\begin{itemize}
-\item both signatures are valid,
-\item time interval is in the future,
-\item transaction abides by the safety and security rules set by the DSO (we will discuss these rules in detail later).
-\end{itemize}
-
-\subsubsection{Energy Transactions}
-An energy transaction records the actual amount of energy consumed and produced by a prosumer in a past time interval.
-
-An energy transaction contains the following fields:
-\begin{itemize}
-\item \textbf{Smart-meter ID}: Unique identifier of the smart meter.
-\item \textbf{Energy value}: Net amount of energy consumed by the prosumer, which is computed as the difference between the consumption and the production of the prosumer (note that it may be a negative value if the prosumer produced more than its consumption).
-\item \textbf{Time interval}: Identifier of the time interval in which energy consumption and production were measured.
-\item \textbf{Smart-meter signature}: Digital signature created using the private key of the smart meter, computed over all previous fields.
-\end{itemize}
-
-The ledger nodes accept and record an energy transaction if
-\begin{itemize}
-\item signature is valid
-\item time interval is in the past.
-\end{itemize}
-
-\subsubsection{Regulatory Transactions}
-A regulatory transaction changes the set of active policies which all transactions are subject to.
-To provide elaborate tools for regulating a microgrid, our system may support a variety of intricate regulatory transactions.
-Here, we discuss two transactions that are necessary for regulating any microgrid market: price-policy and certificate-revocation transactions.
-
-\paragraph{Price policy}
-A price-policy transaction changes the active price policy of the DSO for the microgrid.
-A price policy specifies how much a prosumer will have to pay to the DSO for the difference between its promised and actual net consumption.
-
-A price-policy transaction contains the following fields:
-\begin{itemize}
-\item \textbf{Time interval}: Identifier of the time interval from which the new price policy will be active.
-\item \textbf{Price policy}: Specification of the new price policy.
-\item \textbf{DSO signature}: Digital signature created using the private key of the DSO, computed over all previous fields.
-\end{itemize}
-
-The ledger nodes accept and record a price-policy transaction if
-\begin{itemize}
-\item signature is valid
-\item time interval is in the future.
-\end{itemize}
-
-\paragraph{Certificate Revocation}
-A certificate-revocation transaction revokes some of the digital certificates that were issued to the nodes.
-After a certificate has been revoked, ledger nodes will no longer accept digital signatures created using key pairs whose ownership was proven by the certificate.
-
-A certificate-revocation transaction contains the following fields:
-\begin{itemize}
-\item \textbf{Time interval}: Identifier of the time interval in which the certificate is revoked.
-\item \textbf{List of certificates}: Certificates to be revoked.
-\item \textbf{DSO signature}: Digital signature created using the private key of the DSO, computed over all previous fields.
-\end{itemize}
-
-The ledger nodes accept and record a certificate-revocation transaction if
-\begin{itemize}
-\item signature is valid
-\item time interval is in the future.
-\end{itemize}
-
-\subsection{Privacy}
-
-Depending on the level of privacy that must be provided, the proposed system may be implemented in multiple ways.
-Here, we describe and discuss two approaches, called open and private systems, which are corner cases with respect to privacy.
-
-\subsubsection{Open System}
-This approach is aimed at cases when privacy within a microgrid is not a concern, and we can design the system to maximize its efficiency.
-\begin{itemize}
-\item We allow any physical node to become a trading or ledger node.
-This enhances reliability -- and potentially performance -- as the trading platform and distributed ledger can be implemented by a large set of physical nodes.
-\item The distributed ledger is public within the microgrid, which means that any node can query and receive the complete list of validated and recorded transactions.
-\end{itemize}
-% Advantages: easier accountability and reliability
-
-\subsubsection{Private System}
-This approach is aimed at cases when privacy is a crucial requirement, for example, when the DSO and the microgrid are legally required to provide privacy.
-% goal: hide any personal information
-\begin{itemize}
-\item We allow only a limited set of physical nodes to act as ledger or trading nodes. This constraint can be enforced through limiting the roles of a node within its certificate.
-\item The distributed ledger is private.
-When a node queries the status of the ledger, it will only receive 1) regulatory transactions, 2) aggregate information regarding expected consumption and production in future time steps, 3) list of transactions in which the node is involved.
-\end{itemize}
-To further enhance security, we can also enable the trading platform to mediate between prosumers who would like to trade energy.
-With the help of the trading platform, two prosumer nodes can create a financial transaction without learning each other's identity, and this transaction can then be submitted to the ledger by the trading platform.
-
-\subsection{Transaction Validation and Interpretation}
-
-Here, we discuss the details of how to validate and interpret the financial and energy transactions.
-First, we detail how the ledger nodes determine which transactions are valid and recorded in the distributed ledger.
-Second, we explain how financial and energy transactions can be aggregated in order to determine the financial balance of a prosumer.
-
-\subsubsection{Validation of Financial Transactions: Safety and Security}
-
-First, the ledger nodes reach consensus on the order of the transactions that have been submitted for recording on the ledger.
-Second, they reach consensus on the validity of the ordered transactions.
-They determine the validity of the transactions one-by-one, making a decision for each transaction based on its contents and the contents of the preceding valid transactions.
-
-To ensure the safety and security of the microgrid, ledger nodes must be able to reject careless or malicious energy trading, which could destabilize the microgrid.
-To this end, the certificate of each prosumer specifies the net amount of energy that the prosumer may trade for a single time step.
-More specifically, the certificate of prosumer $p$ includes the following fields:
-\begin{itemize}
-\item $MaxNetBuy_p$: net energy that prosumer $p$ may purchase,
-\item $MaxNetSell_p$: net energy that prosumer $p$ may sell.
-\end{itemize}
-
-To determine whether an incoming financial transaction is valid, a ledger node runs Algorithm~\ref{alg:validateFinancialTransaction}.
-%\begin{enumerate}
-%\item let $T$ be the time step of the incoming transaction, and let $p_b$ and $p_s$ be the buying and selling prosumers, respectively;
-%\item let $NetBuy \gets 0$;
-%\item for every valid transaction on the ledger, if the time step is $T$ and the buyer is $p_b$, then add the energy amount to $NetBuy$;
-%\item for every valid transaction on the ledger, if the time step is $T$ and the seller is $p_b$, then subtract the energy amount from $NetBuy$;
-%\item let $NetSell \gets 0$;
-%\item for every valid transaction on the ledger, if the time step is $T$ and the seller is $p_s$, then add the energy amount to $NetSell$;
-%\item for every valid transaction on the ledger, if the time step is $T$ and the buyer is $p_s$, then subtract the energy amount from $NetSell$;
-%\item if $NetBuy \leq MaxNetBuy_{p_b}$, $NetSell \leq MaxNetSell_{p_s}$, the signatures are valid, and $T$ is in the future, then output valid;
-%\item else, output invalid.
-%\end{enumerate}
-
-\todo[inline]{Extend: prosumer nodes may buy/sell electricity from/to DSO in advance. This is key to load prediction.}
-
-\begin{algorithm}[h!]
-\caption{Validation of Financial Transaction}
-\label{alg:validateFinancialTransaction}
-\begin{algorithmic}[1]
-\Statex{\hspace{-\algorithmicindent}\textbf{Input:} incoming transaction, valid transactions on the ledger}
-\Statex{\hspace{-\algorithmicindent}\textbf{Output:} valid / invalid}
-\State{let $T$ be the time step of the incoming transaction, and let $p_b$ and $p_s$ be the buying and selling prosumers, respectively}
-\State{$NetBuy \gets 0$}
-\State{$NetSell \gets 0$}
-\For{valid transaction on the ledger}
-  \If{time step is $T$}
-    \If{buyer is $p_b$}
-      \State{$NetBuy \gets NetBuy + $ energy amount}
-    \EndIf
-    \If{seller is $p_b$}
-      \State{$NetBuy \gets NetBuy - $ energy amount}
-    \EndIf
-    \If{seller is $p_s$}
-      \State{$NetSell \gets NetSell + $ energy amount}
-    \EndIf
-    \If{buyer is $p_s$}
-      \State{$NetSell \gets NetSell - $ energy amount}
-    \EndIf
-  \EndIf
-\EndFor
-\If{$NetBuy \leq MaxNetBuy_{p_b}$, $NetSell \leq MaxNetSell_{p_s}$, the signatures are valid, and $T$ is in the future}
-  \State{\textbf{return} valid}
-\Else
-  \State{\textbf{return} invalid}
-\EndIf
-%
-%\State{$A \gets (\emptyset, \emptyset)$} 
-%\State{$\Loss^* \gets -\infty$}
-%\For{$b = 1, \ldots, B_A$}
-%  \For{$v \in V_A$}
-%    \For{$k \in \Gamma^{-1}(v)$}
-%      \State{$A' \gets A \cup \left(\{s\}, \left\{\hat{p}_{kv} = 1, \forall j \neq k : \hat{p}_{jv} = 0\right\}\right)$}
-%      \State{$\Loss' \gets \big[\left(1 - \Pr[\text{detect}]\right) \cdot \Loss(C, A)$}
-%      \State{\hspace{3.5em} $+ \Pr[\text{detect}] \cdot \min_M \max_R \Loss(C, A, M, R) \big]$}
-%      \If{$\Loss' \geq \Loss^*$}
-%        \State{$A^* \gets A'$}
-%        \State{$\Loss^* \gets \Loss'$}
-%      \EndIf
-%    \EndFor
-%    \State{$A \gets A^*$}
-%  \EndFor
-%\EndFor
-%\State{Output $A$}
-\end{algorithmic}
-\end{algorithm}
-
-\subsubsection{Aggregation of Financial and Energy Transactions: Financial Balance}
-
-\todo[inline]{Firstly, the prosumer must pay (or be paid) for the financial transactions recorded on the ledger in either a fiat currency (e.g., US dollars) or a cryptocurrency.}
-
-Even though prosumer nodes attempt to buy or sell in advance the amount of energy that they will consume or produce, it is practically impossible to predict their net consumption perfectly.
-Consequently, there will necessarily be an imbalance between the amount of energy bought (or sold) in advance and the actual net consumption (or production) of the prosumer.
-This imbalance must be covered by the DSO, who will charge (or pay) the prosumer for the amount of energy consumed (or produced) beyond what was promised in the financial transactions.
-
-The amount that the DSO will charge (or pay) the prosumer is determined by the pricing policy of the DSO, which is set using regulatory transactions.
-
-\subsection{Control Algorithm}
-
-\todo[inline]{
-\textbullet 
-receives measured and expected load values from the ledger (as well as from the rest of the grid)
-\textbullet 
-produces a control signal that specifies the desired load for the future (may also include a tolerance level that specifies how much deviation from this load level is tolerable)
-}
-
-\todo[inline]{Figure: - data flow between nodes - control signals}
-
 \end{document}

### 2017-06-01 papers/IoT2017/intro.tex
no message

--- 2017-05-31 papers/IoT2017/paper.tex
@@
-\documentclass[chi_draft]{sigchi}
-
-% Use this section to set the ACM copyright statement (e.g. for
-% preprints).  Consult the conference website for the camera-ready
-% copyright statement.
-
-% Copyright
-\CopyrightYear{2017}
-%\setcopyright{acmcopyright}
-\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-% DOI
-\doi{} %http://dx.doi.org/10.475/123_4}
-% ISBN
-\isbn{} %123-4567-24-567/08/06}
-%Conference
-\conferenceinfo{IoT'17,}{October 22--25, 2017, Linz, Austria}
-%Price
-\acmPrice{\$15.00}
-
-% Use this command to override the default ACM copyright statement
-% (e.g. for preprints).  Consult the conference website for the
-% camera-ready copyright statement.
-
-%% HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP --
-%% Please note you need to make sure the copy for your specific
-%% license is used here!
-% \toappear{
-% Permission to make digital or hard copies of all or part of this work
-% for personal or classroom use is granted without fee provided that
-% copies are not made or distributed for profit or commercial advantage
-% and that copies bear this notice and the full citation on the first
-% page. Copyrights for components of this work owned by others than ACM
-% must be honored. Abstracting with credit is permitted. To copy
-% otherwise, or republish, to post on servers or to redistribute to
-% lists, requires prior specific permission and/or a fee. Request
-% permissions from \href{mailto:Permissions@acm.org}{Permissions@acm.org}. \\
-% \emph{CHI '16},  May 07--12, 2016, San Jose, CA, USA \\
-% ACM xxx-x-xxxx-xxxx-x/xx/xx\ldots \$15.00 \\
-% DOI: \url{http://dx.doi.org/xx.xxxx/xxxxxxx.xxxxxxx}
-% }
-
-% Arabic page numbers for submission.  Remove this line to eliminate
-% page numbers for the camera ready copy
-% \pagenumbering{arabic}
-
-% Load basic packages
-\usepackage{balance}       % to better equalize the last page
-\usepackage{graphics}      % for EPS, load graphicx instead 
-\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
-\usepackage{txfonts}
-\usepackage{mathptmx}
-\usepackage[pdflang={en-US},pdftex]{hyperref}
-\usepackage{color}
-\usepackage{booktabs}
-\usepackage{textcomp}
-
-% Some optional stuff you might like/need.
-\usepackage{microtype}        % Improved Tracking and Kerning
-% \usepackage[all]{hypcap}    % Fixes bug in hyperref caption linking
-\usepackage{ccicons}          % Cite your images correctly!
-% \usepackage[utf8]{inputenc} % for a UTF8 editor only
-
-% Custom packages
-
-\usepackage{paralist}
-
-\usepackage{tikz}
-\usetikzlibrary{shadows,shapes}
-\usepackage{pgfplots}
-\pgfplotsset{compat=1.10}
-
-\usepackage{xcolor}
-\usepackage{colortbl}
-\definecolor{Gray}{gray}{0.90}
-
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage{algpseudocode}
-
-% If you want to use todo notes, marginpars etc. during creation of
-% your draft document, you have to enable the "chi_draft" option for
-% the document class. To do this, change the very first line to:
-% "\documentclass[chi_draft]{sigchi}". You can then place todo notes
-% by using the "\todo{...}"  command. Make sure to disable the draft
-% option again before submitting your final document.
-\usepackage[textsize=small]{todonotes}
-\newcommand{\TODO}[1]{\todo[inline]{#1}}
-
-\newcommand{\field}[1]{\texttt{#1}}
-
-% Paper metadata (use plain text, for PDF inclusion and later
-% re-using, if desired).  Use \emtpyauthor when submitting for review
-% so you remain anonymous.
-\def\plaintitle{Private Blockchains for Transactive Energy:\\Security, Privacy, and Safety}
-\def\plainauthor{First Author, Second Author, Third Author}
-\def\emptyauthor{}
-\def\plainkeywords{Internet of Things; blockchain; transactive energy; privacy; security; transactive microgrid.}
-\def\plaingeneralterms{Design, Human Factors, Reliability, Security} % TODO: revise
-
-% llt: Define a global style for URLs, rather that the default one
-\makeatletter
-\def\url@leostyle{%
-  \@ifundefined{selectfont}{
-    \def\UrlFont{\sf}
-  }{
-    \def\UrlFont{\small\bf\ttfamily}
-  }}
-\makeatother
-\urlstyle{leo}
-
-% To make various LaTeX processors do the right thing with page size.
-\def\pprw{8.5in}
-\def\pprh{11in}
-\special{papersize=\pprw,\pprh}
-\setlength{\paperwidth}{\pprw}
-\setlength{\paperheight}{\pprh}
-\setlength{\pdfpagewidth}{\pprw}
-\setlength{\pdfpageheight}{\pprh}
-
-% Make sure hyperref comes last of your loaded packages, to give it a
-% fighting chance of not being over-written, since its job is to
-% redefine many LaTeX commands.
-\definecolor{linkColor}{RGB}{6,125,233}
-\hypersetup{%
-  pdftitle={\plaintitle},
-% Use \plainauthor for final version.
-%  pdfauthor={\plainauthor},
-  pdfauthor={\emptyauthor},
-  pdfkeywords={\plainkeywords},
-  pdfdisplaydoctitle=true, % For Accessibility
-  bookmarksnumbered,
-  pdfstartview={FitH},
-  colorlinks,
-  citecolor=black,
-  filecolor=black,
-  linkcolor=black,
-  urlcolor=linkColor,
-  breaklinks=true,
-  hypertexnames=false
-}
-
-% create a shortcut to typeset table headings
-% \newcommand\tabhead[1]{\small\textbf{#1}}
-
-% End of preamble. Here it comes the document.
-\begin{document}
-
-\title{\plaintitle}
-
-\numberofauthors{3}
-\author{%
-  \alignauthor{Leave Authors Anonymous\\
-    \affaddr{for Submission}\\
-    \affaddr{City, Country}\\
-    \email{e-mail address}}\\
-  \alignauthor{Leave Authors Anonymous\\
-    \affaddr{for Submission}\\
-    \affaddr{City, Country}\\
-    \email{e-mail address}}\\
-  \alignauthor{Leave Authors Anonymous\\
-    \affaddr{for Submission}\\
-    \affaddr{City, Country}\\
-    \email{e-mail address}}\\
-}
-
-\maketitle
-
-\begin{abstract}
-While transactive microgrids must satisfy the same security requirements as non-transactive ones, they must also satisfy additional safety and privacy requirements.
-We design a secure and efficient trading platform for transactive microgrids, which enables prosumers to trade energy without sacrificing their privacy.
-\end{abstract}
-
-% TODO!
-\category{K.6.m}{Miscellaneous}{Security}
-\category{D.4.7}{Organization and Design}{Distributed systems}
-
-\keywords{\plainkeywords}
-
 \section{Introduction}
@@
 We propose a solution that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, enables the DSO to regulate the trading platform and enforce certain safety rules.
-
-\section{Preliminaries and Requirements}
-
-\subsection{Transactive Microgrid}
-
-Here, we describe a basic system model for a transactive microgrid based on a distributed ledger, such as a blockchain.
-% - smart meters
-% - distributed ledger, such as blockchain
-
-\subsubsection{Distributed Ledger}
-The distributed ledger stores transactions that specify energy trades, change regulatory policies for the microgrid, etc.
-Since the ledger is maintained by multiple ledger nodes, a key implementation requirement is reaching consensus on which transactions are valid and stored in the ledger.
-This consensus must be reached quickly, reliably, and securely even in the presence of erroneous or even malicious ledger nodes.
-We treat the consensus algorithm as a pluggable module, which can be based on blockchains with proof-of-stake consensus or Practical Byzantine Fault Tolerance algorithm~\cite{castro1999practical}.
-
-\subsubsection{Bid Storage Service}
-Although individual prosumers trade energy with each other, for the sake of scalability, we need a service that enables prosumers to find trade partners.
-By providing a storage service for buy and sell bids, we relieve prosumer nodes from communicating with all potential trade partners.
-In addition to receiving and storing bids from prosumers, the bid storage service can also find matches and notify prosumers of the opportunity to make an energy trade.
-Even though the bid storage appears to the nodes as one entity, for the sake of scalability and reliability, it can be implemented in a distributed manner, using multiple nodes.
-
-\subsubsection{Microgrid Controller}
-The microgrid controller is responsible for stabilizing load within the microgrid and controlling it based on the expected load in the rest of the grid.
-To this end, the controller first estimates the expected load in the microgrid based on buy and sell bids in the bid storage as well as on outstanding energy trades in the ledger.
-By combining this estimate with the expected load in the remainder of the grid, the controller produces a control signal that specifies how much the microgrid load should be decreased or increased.
-Finally, based on this control signal, the controller updates the price policy for the microgrid to influence energy production and consumption.
-
-\subsection{Requirements}
-
-\subsubsection{Security}
-Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.
-
-\subsubsection{Safety}
-A careless or malicious prosumer may destabilize the grid by promising to produce (or consume) a large amount of energy, but failing to deliver.
-Trades which are unlikely to be delivered and would result in a gap between actual production and demand should be prevented.
-
-\subsubsection{Privacy} 
-Energy trading should not compromise the privacy of prosumers.
-More specifically, prosumers' private information, including energy consumption and production values, are available only to the DSO.
-
-\section{Solution}
-
-In section, we describe our solution for providing privacy for prosumers without compromising the safety and security of the microgrid.
-Figure~\ref{fig:softwareArchitecture} shows a high-level overview of the architecture of our solution.
-
-\begin{figure}[h!]
-\center
-\begin{tikzpicture}[x=8cm, y=1.2cm,
-  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
-]
-\draw [nodeStyle, fill=white]   (0, 0) rectangle    (1, 0.9) node [midway, align=center] {Communication network\\and operating system};
-
-\draw [nodeStyle, fill=red!10]  (0, 1) rectangle    (1, 1.9) node [midway, align=center] {Communication anonymity\\(onion routing)};
-
-\draw [nodeStyle, fill=blue!10] (0, 2) rectangle    (1, 2.9) node [midway, align=center] {Distributed ledger\\(blockchain)};
-
-\draw [nodeStyle, fill=red!10]  (0,    3) rectangle (0.45, 3.9) node [midway, align=center] {Transaction anonymity\\(mixing service)};
-\draw [nodeStyle, fill=blue!10] (0.47, 3) rectangle (0.72, 3.9) node [midway, align=center] {Bid storage};
-\draw [nodeStyle, fill=red!10 ] (0.74, 3) rectangle (1,    3.9) node [midway, align=center] {Active\\smart meter};
-
-\draw [nodeStyle, fill=blue!10] (0,    4) rectangle (0.49, 4.9) node [midway, align=center] {Prosumer trading\\algorithm};
-\draw [nodeStyle, fill=blue!10] (0.51, 4) rectangle (1,    4.9) node [midway, align=center] {DSO control\\algorithm};
-\end{tikzpicture}
-\caption{High-level architecture of the proposed solution.
-Components marked red are introduced to provide privacy in a safe and secure manner.
-Components marked in blue are typical elements of a decentralized transactive microgrid.}
-\label{fig:softwareArchitecture}
-\end{figure}
-
-\begin{figure*}[h]
-\center
-\begin{tikzpicture}[x=3.8cm, y=2cm, font=\small,
-  system/.style={draw, align=center, rounded corners=0.1cm, fill=black!5},
-  entity/.style={draw, align=center, rounded corners=0.1cm},
-  asset/.style={midway, align=center},
-  transfer/.style={->, >=stealth, shorten <=0.05cm, shorten >=0.05cm},
-]
-%\node[entity] (smartmeter) at (0.75, 0.5) {smart\\meter};
-%\node[entity] (prosumer1) at (1.25, 1) {prosumer};
-%\node[system] (mixing1) at (2, 1) {mixing\\service};
-%\node[entity] (prosumer2) at (3, 1) {prosumer\\(alternative address)};
-%\node[system] (bidstorage) at (4, 1) {bid\\storage};
-%\node[entity] (partner) at (4, 0) {other prosumer};
-%\node[entity] (prosumer3) at (3, 0) {prosumer\\(alternative address)};
-%\node[system] (mixing2) at (2, 0) {mixing\\service};
-%\node[entity] (prosumer4) at (1.25, 0) {prosumer};
-\node[entity] (smartmeter) at (0, 1) {smart meter};
-\node[entity] (prosumer1) at (1, 1) {prosumer};
-\node[system] (mixing1) at (1.9, 1) {mixing\\service};
-\node[entity] (prosumer2) at (3, 1) {prosumer\\(anonymous address)};
-\node[system] (bidstorage) at (4, 0.5) {bid\\storage};
-\node[entity] (partner) at (3, 0) {other prosumer};
-\node[entity] (prosumer3) at (1.5, 0) {prosumer\\(anonymous address)};
-\node[entity] (smartmeter2) at (0, 0) {smart meter\\(anonymous address)};
-
-%\draw[transfer] (smartmeter) -- node [asset, above left] {energy\\production asset} (prosumer1);
-%\draw[transfer] (prosumer1) -- node [asset, above] {energy\\production asset} (mixing1);
-%\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
-%\draw[transfer, dashed] (prosumer2) -- node [asset, above] {energy production asset,\\sell bid} (bidstorage);
-%\draw[transfer, dashed] (bidstorage) -- node [asset, right] {sell\\bid} (partner);
-%\draw[transfer, bend right=15] (partner) to node [asset, below] {financial asset,\\energy\\consumption asset} (prosumer3);
-%\draw[transfer, bend right=7.5] (prosumer2) to node [asset, above right] {energy\\prod. asset} (partner);
-%\draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
-%energy consumption asset} (mixing2);
-%\draw[transfer] (mixing2) -- node [asset, below] {financial asset,\\energy consumption asset} (prosumer4);
-%\draw[transfer] (prosumer4) -- node [asset, below left] {financial\\asset} (smartmeter);
-
-\draw[transfer] (smartmeter) -- node [asset, above] {energy\\production asset} (prosumer1);
-\draw[transfer] (prosumer1) -- node [asset, above] {energy\\production asset} (mixing1);
-\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
-\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {energy production asset,\\sell bid} (bidstorage);
-\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {sell\\bid} (partner);
-\draw[transfer, bend right=30] (partner) to node [asset, below] {financial asset,\\energy consumption asset} (prosumer3);
-\draw[transfer, bend right=50] (prosumer2) to node [asset, right] {energy\\production asset} (partner);
-\draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
-energy consumption asset} (smartmeter2);
-\end{tikzpicture}
-\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy production.
-Note that in order to prevent de-anonymization, a prosumer should use multiple addresses for mixing and multiple rounds of mixing.}
-\end{figure*}
-
-\subsection{Timing}
-The ability to specify points or intervals in time is crucial.
-For example, control signals specify how the load should change at certain points in time, energy trades specify when energy will be consumed or produced, etc.
-To facilitate processing signals and transactions, we divide time into fixed-length intervals, and specify points or periods in time using these discrete timesteps.
-The length of the time interval is determined by mapping the timing assumptions of the power system to our platform.
-%In our implementation, 
-For example, the default length of the time interval may be 4 seconds, which corresponds to how frequently the control signal of the DSO typically changes.
-
-\subsection{Services}
-
-Here, we describe three services that must be implemented for our solution: communication anonymity, mixing service for transaction anonymity, and anonymous bid storage for bidding anonymity.
-
-\subsubsection{Communication Anonymity}
-Firstly, we must provide an anonymous communication layer, on which we can build an anonymous trading platform.
-Without this communication layer, bids and transactions could be easily de-anonymized based on the network identifiers of the sources (e.g., IP or MAC addresses).
-
-We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}.
-To build an onion network, the smart meters, inverters, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on a private blockchain.
-In our first implementation, we can use the free and open-source Tor software with private Directory Authorities.
-% ritter.vg: "run your own tor network"
-% https://ritter.vg/blog-run_your_own_tor_network.html
-
-\subsubsection{Transaction Anonymity}
-We must provide prosumers with the ability to create and publish transactions anonymously.
-More specifically, prosumers should be able to purchase or sell energy without revealing their identity; however, these transaction must also be verifiable and enforceable.
-
-We may achieve this goal using multiple approaches for blockchain transaction anonymity:
-\begin{itemize}
-\item Mixing services (also known as tumblers) mix potentially identifiable assets on a blockchain with others, thereby preventing tracing individual assets back to their original source. 
-In our case, assets to be mixed include virtual balances of fiat currencies as well as energy production and consumption.
-\item Cryptographic anonymity for transactions is provided, for example, by Zerocoin~\cite{miers2013zerocoin}. Similarly to mixing service, Zerocoin can prevent tracing assets on a blockchain.
-\end{itemize}
-Using the above techniques, we can enable prosumers to trade energy anonymously (i.e., without revealing their true identities), but at the same time prevent them from altering their energy or financial balances without a valid transaction.
-
-However, we must also ensure that 1) smart meters know the amount of energy purchased or sold by their prosumer and 2) prosumers cannot purchase or sell more energy than their capacity.
-To satisfy both of these constraints, all energy trades must start with the prosumer withdrawing a certain amount of energy production or consumption from its smart meter:
-\begin{itemize}
-\item If a prosumer wishes to sell energy, it must first obtain an energy asset from its smart meter using a blockchain transaction.
-This transaction must be signed by the smart meter, which enables the smart meter to 1) keep track of the amount of energy traded by the prosumer as well as to 2) enforce safety requirements by limiting the amount of energy that can be withdrawn.
-\item If a prosumer wishes to buy energy, it must first obtain an energy consumption asset from its smart meter in a way similar to obtaining an energy production asset.
-\end{itemize}
-
-\subsubsection{Bidding Anonymity}
-Finally, we must provide prosumers with the ability to publish energy buy and sell bids anonymously.
-To this end, we create a storage for anonymous bids that is readable by all the prosumers in the microgrid.
-Any prosumer may submit a bid to this storage; however, in order to do so, they must provide a zero-knowledge proof of owning the assets that are to be traded:
-\begin{itemize}
-\item To submit an energy sell bid, the prosumer must prove that it owns an energy production asset on the chain.
-\item To submit an energy buy bid, the prosumer must prove that it own an energy consumption asset as well as financial assets on the chain.
-\end{itemize}
-
-\subsection{Transaction Types}
-
-Before we can discuss transaction types, we must first define the three assets that these transactions may transfer.
-
-An \emph{energy production asset} (EPA) is defined by
-\begin{compactitem}
-\item \field{power}: non-negative amount of power to produced (for example, measured in watts).
-\item \field{start}: first time interval in which energy is to be produced. 
-\item \field{end}: last time interval in which energy is to be produced.
-\end{compactitem}
-An \emph{energy consumption asset} (ECA) is defined by the same fields; however, for this asset, the fields define consumption instead of production.
-Finally, a \emph{financial asset} (FA) is defined by a single non-negative field \field{amount}, which can be denominated in either a fiat currency (e.g., US dollars) or a cryptocurrency.
-
-\subsubsection{Energy and Financial Transactions}
-
-Energy and financial transactions transfer energy and financial asset from one address to another.
-Prosumers use these transactions for multiple purposes: to trade energy by exchanging assets with other prosumers, to prove to the bid storage that they have production or consumption capacity, to hide their identity by transferring assets to and from mixing services, and to deposit assets at their smart meter.
-%
-An energy and financial transaction contains the following fields:
-\begin{compactitem}
-\item List of EPA inputs, each of which is defined by:
-\begin{compactitem}
-\item \field{out}: EPA output from a previous transaction,
-\item \field{sig}: signature for this output.
-\end{compactitem}
-\item List of ECA inputs, each of which is defined by:
-\begin{compactitem}
-\item \field{out}: ECA output from a previous transaction,
-\item \field{sig}: signature for this output.
-\end{compactitem}
-\item List of FA inputs, each of which is defined by:
-\begin{compactitem}
-\item \field{out}: FA output from a previous transaction,
-\item \field{sig}: signature for this output.
-\end{compactitem}
-\item List of EPA outputs, each of which is defined by:
-\begin{compactitem}
-\item an EPA and an address to which it is transferred.
-\end{compactitem}
-\item List of ECA outputs, each of which is defined by:
-\begin{compactitem}
-\item an ECA and an address to which it is transferred.
-\end{compactitem}
-\item List of FA outputs, each of which is defined by:
-\begin{compactitem}
-\item an FA and an address to which it is transferred.
-\end{compactitem}
-\end{compactitem}
-
-An energy and financial transaction is valid if the following three conditions hold.
-\begin{compactitem}
-\item None of the outputs referenced by the inputs have been spent by a transaction that has been recorded on the ledger.
-\item All of the signatures are valid.
-\item For each asset type (and for each timestep), the sum of inputs and outputs is the same.
-For example, in the case of energy production assets, the condition is:
-\begin{align}
-\forall t: & \sum_{out \in \text{EPA outputs}} out.\mathtt{power} \cdot 1_{\left\{out.\mathtt{start} \leq t \leq out.\mathtt{end}\right\}} \nonumber \\
-& = \sum_{in \in \text{EPA inputs}} in.\mathtt{out}.\mathtt{power} \cdot 1_{\left\{in.\mathtt{out}.\mathtt{start} \leq t \leq in.\mathtt{out}.\mathtt{end}\right\}} ,
-\end{align}
-where $1_x$ is equal to $1$ if $x$ is true, and it is $0$ otherwise.
-%\begin{equation}
-%\forall t: \sum_{out \in \left\{out' \middle| out' \in \text{ EPA outputs} \wedge out'.EPA.start \leq t \leq out'.EPA.end\right\}} out.EPA.Power = \sum_{in \in \left\{in' \middle| in' \in \text{ EPA inputs} \wedge in'.EPA.start \leq t \leq in'.EPA.end\right\}} in.EPA.Power .
-%\end{equation}
-\end{compactitem}
-If a transaction submitted to the ledger is valid, it will be permanently recorded.
-
-\subsubsection{Smart-Meter Transactions}
-
-Prosumers use smart-meter transactions to withdraw energy and financial assets from their own smart meters, before they engage in energy trading.
-%
-A smart-meter transaction contains the following fields:
-\begin{compactitem}
-\item List of EPA outputs, each of which is defined by:
-\begin{compactitem}
-\item an EPA and an address to which it is transferred.
-\end{compactitem}
-\item List of ECA outputs, each of which is defined by:
-\begin{compactitem}
-\item an ECA and an address to which it is transferred.
-\end{compactitem}
-\item List of FA outputs, each of which is defined by:
-\begin{compactitem}
-\item an FA and an address to which it is transferred.
-\end{compactitem}
-\item \field{id}: Identifier of the smart meter.
-\item \field{sig}: Smart meter's signature over the transaction.
-\end{compactitem}
-
-A smart-meter transaction is valid if the following two conditions hold:
-\begin{compactitem}
-\item The smart meter identified in the transaction has been authorized by a regulatory transaction that has been recorded on the ledger.
-\item The smart meter's signature is valid.
-\end{compactitem}
-\todo{To address malfunctioning or compromised smart meters, we could also impose a limit on withdrawals.}
-
-\subsubsection{Regulatory Transactions}
-
-The DSO uses regulatory transactions to authorize or ban smart meters and to control the microgrid load through setting a price policy.
-Since these transactions provide a diverse set of functionality, they are divided into two types.
-
-\paragraph{Authorize or Ban Smart Meters}
-The DSO uses these transactions to manage the set of authorized smart meters in the microgrid.
-Whenever a new smart meter is installed, the DSO notifies the members of the microgrid using a regulatory transaction.
-Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or it is believed to be malfunctioning or compromised), the DSO notifies the members of the microgrid using a regulatory transaction.
-These transactions contain the following fields:
-\begin{compactitem}
-\item List of smart meters to be authorized, each of which is defined by:
-\begin{compactitem}
-\item \field{id}: Identifier of the smart meter.
-\item \field{pubkey}: Public key of the smart meter.
-\end{compactitem}
-\item List of smart meters to be banned, each of which is given using its identifier.
-\item \field{time}: Timestep in which smart meters are authorized and banned.
-\item \field{sig}: DSO's signature over the transaction.
-\end{compactitem}
-
-A regulatory transaction of this type is valid if the following two conditions hold:
-\begin{compactitem}
-\item The timestep specified in the transaction is in the future.
-\item The DSO's signature is valid.
-\end{compactitem}
-
-\paragraph{Price Policy}
-
-\section{Analysis}
-\label{sec:analysis}
-
-Here, we present a semi-formal analysis of the proposed solution, and show that it satisfies the security, safety, and privacy requirements.
-
-\subsection{Security}
-
-\subsection{Safety}
-
-\subsection{Privacy}
-
-Due to the communication anonymity and mixing services, members of a microgrid can see only the amount of energy and financial assets withdrawn by a prosumer.
-Since all trading transactions are anonymous, the amount of assets traded by the prosumer will not be publicly known.
-In case a prosumer does not wish to trade, it can anonymously deposit its assets to a random address that was freshly generated by its smart meter.
-Note that even if a prosumer does not wish to trade, it should always withdraw and mix assets; otherwise, the lack of withdrawal would leak information.
-
-As for the DSO, it can receive the same information from the smart meter as in a non-transactive grid (i.e., amount of energy produced and consumed).
-\todo{Also knows financial amounts, but those are necessary for billing.}
-Since trading is anonymous, it does not receive any further information.
-
-In fact, we can provide an even higher-level of privacy.
-Since price policies are recorded on the ledger, which the smart meters may read, the smart meters can calculate the prosumer's monthly bill, and send only this single financial amount to the DSO each month.
-Meanwhile, the DSO can still obtain current and future load information from the bid storage and from the trades recorded on the ledger.
-
-\section{Related Work}
-\label{sec:related}
-
-\subsection{Smart Grid and Meter Privacy}
-
-% http://ieeexplore.ieee.org/abstract/document/5054916/
-McDaniel and McLaughlin discuss privacy challenges in smart grids~\cite{mcdaniel2009security}.
-
-% https://arxiv.org/pdf/1108.2234.pdf
-% https://pdfs.semanticscholar.org/cdf8/a5b6256823bca38a1d2347ab36f8e4a2ca94.pdf
-Rajagopalan et al.\ use tools from information theory to present a framework, which abstracts both the privacy and the utility requirements of smart meter data~\cite{rajagopalan2011smart,sankar2013smart}.
-Their framework leads to a novel privacy-utility tradeoff problem with minimal assumptions.
-%, which is tractable.
-
-% http://www.comm.toronto.edu/~akhisti/sm.pdf
-Varodayan and Khisti study using rechargeable battery for partially protecting the privacy of information contained in a household's electrical load profile~\cite{varodayan2011smart}.
-They show that stochastic battery policies may leak 26\% less information than a best-effort policy, holds the output load constant whenever possible.
-
-% https://www.researchgate.net/profile/Georgios_Kalogridis/publication/224189766_Smart_Grid_Privacy_via_Anonymization_of_Smart_Metering_Data/links/541169510cf2b4da1bec4193.pdf
-Efthymiou and Kalogridis describe a method for securely anonymizing frequent electrical metering data sent by a smart meter~\cite{efthymiou2010smart}. 
-Their approach is based on the observation that frequent metering data may be required by an energy distribution network for operational reasons, but it may not necessarily need to be attributable to a specific smart meter.
-The authors describe a method that provides a third-party escrow mechanism for authenticated anonymous meter readings, which are difficult to associate with particular smart meter.
-
-% https://arxiv.org/pdf/1305.0735.pdf
-Tan et al.\ study privacy in a smart metering system from an information theoretic perspective in the presence of energy harvesting and storage units~\cite{tan2013increasing}. 
-They show that energy harvesting provides increased privacy by diversifying the energy source, while a storage device can be used to increase both energy efficiency and privacy. 
-They show that there exists a trade-off between the information leakage rate and the wasted energy rate, and study the impact of the energy harvesting rate and the size of the storage device on this trade-off.
-
-\subsection{Blockchain Technology}
-
-Microsoft offers Blockchain as a Service (BaaS) on Azure.
-Project Bletchley is Microsoft's architectural approach to building an Enterprise Consortium Blockchain Ecosystem, introducing two new concepts: blockchain middleware and cryptlets~\cite{gray2016introducing}.
-
-Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}.
-
-Interledger is a protocol for payments across payment systems, which enables anyone with accounts on two ledgers to create
-a connection between them~\cite{thomas_protocol}.
-
-Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}.
-
-\url{https://geli.net/residential/}
-\url{https://www.greentechmedia.com/articles/read/geli-raises-7m-to-take-energy-storage-software-to-the-next-level}
-
-\section{Conclusion}
-\label{sec:concl}
-
-% BALANCE COLUMNS
-\balance{}
-
-% REFERENCES FORMAT
-% References must be the same font size as other body text.
-\bibliographystyle{SIGCHI-Reference-Format}
-\bibliography{references}
-
-\end{document}

### 2017-06-01 papers/IoT2017/paper.tex
no message

@@
 \begin{abstract}
-While transactive microgrids must satisfy the same security requirements as non-transactive ones, they must also satisfy additional safety and privacy requirements.
-We design a secure and efficient trading platform for transactive microgrids, which enables prosumers to trade energy without sacrificing their privacy.
+Power grids are undergoing major changes due to rapid growth in renewable energy resources and improvements in battery technology.
+While these changes enhance sustainability and efficiency, they also create significant management challenges as the complexity of power systems increases.
+To tackle these challenges, decentralized solutions are emerging, which arrange local communities into microgrids.
+Within a transactive microgrid, consumers with energy generation and storage capabilities may trade energy with each other, thereby smoothing the load on the main grid using local supply.
+However, providing security, safety, and privacy in a decentralized and transactive energy system is very challenging.
+On the one hand, consumers' personal information must be protected from their their trade partners and the system operator.
+On the other hand, the system must be protected from careless or malicious trading, which could destabilize the entire grid. 
+In this paper, we design a secure and safe solution for transactive microgrids, which enables consumers to trade energy without sacrificing their privacy.
+Our solution builds on distributed ledgers, such as blockchains, and provides anonymity for communication, bidding, and trading.
 \end{abstract}
@@
 
-\section{Introduction}
+\input{intro.tex}
 
-% electric grid is changing: renewables, storage capacity, etc. -> prosumers
+\input{prelim.tex}
 
-In order to take advantage of these capabilities, electric grids need to become more decentralized.
-% what are the advantages of decentralization?
-
-% transactive microgrid
-
-% there are pilot studies, however, providing privacy is an open problem
-For example, the Brooklyn Microgrid developed by LO3 Energy is a peer-to-peer energy market for locally generated renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}
-
-Transactive energy may pose a much greater threat to prosumers' privacy than smart metering.
-\begin{itemize}
-\item Firstly, since prosumers may purchase energy from each other in a transactive microgrid, transactions may inadvertently reveal the prosumers' detailed energy usage patterns to other prosumers within the microgrid.
-Addressing this issue in a decentralized trading platform is quite challenging as it requires hiding the identities of trade partners from each other.
-In comparison, secure smart metering reveals the prosumers' energy usage patterns only to the provider. 
-\item Secondly, transactions may reveal the future energy usage of a prosumer, which could be used to infer private information.
-For example, a smart home may know that its inhabitants will go out in the evening (e.g., by looking at their calendar), and it may trade energy futures accordingly in the morning.
-Without adequate privacy measures, these trades may reveal to other prosumers in the microgrid that the inhabitants will not be at home later.
-Note that energy futures, whose delivery may happen several hours after when the transaction is made, can play a very important role in predicting and controlling microgrid load.
-In comparison, smart metering reveals only current (and past) usage.
-\item Thirdly, transactions and energy usage data in a transactive microgrid are much richer source of information than the simple energy usage data collected by smart meters.
-More specifically, the information available in a transactive microgrid is a superset of what is available from smart metering, and it may be used to infer personal information, such as risk propensity and financial standing.
-\end{itemize}
-
-We propose a solution that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, enables the DSO to regulate the trading platform and enforce certain safety rules.
-
-\section{Preliminaries and Requirements}
-
-\subsection{Transactive Microgrid}
-
-Here, we describe a basic system model for a transactive microgrid based on a distributed ledger, such as a blockchain.
-% - smart meters
-% - distributed ledger, such as blockchain
-
-\subsubsection{Distributed Ledger}
-The distributed ledger stores transactions that specify energy trades, change regulatory policies for the microgrid, etc.
-Since the ledger is maintained by multiple ledger nodes, a key implementation requirement is reaching consensus on which transactions are valid and stored in the ledger.
-This consensus must be reached quickly, reliably, and securely even in the presence of erroneous or even malicious ledger nodes.
-We treat the consensus algorithm as a pluggable module, which can be based on blockchains with proof-of-stake consensus or Practical Byzantine Fault Tolerance algorithm~\cite{castro1999practical}.
-
-\subsubsection{Bid Storage Service}
-Although individual prosumers trade energy with each other, for the sake of scalability, we need a service that enables prosumers to find trade partners.
-By providing a storage service for buy and sell bids, we relieve prosumer nodes from communicating with all potential trade partners.
-In addition to receiving and storing bids from prosumers, the bid storage service can also find matches and notify prosumers of the opportunity to make an energy trade.
-Even though the bid storage appears to the nodes as one entity, for the sake of scalability and reliability, it can be implemented in a distributed manner, using multiple nodes.
-
-\subsubsection{Microgrid Controller}
-The microgrid controller is responsible for stabilizing load within the microgrid and controlling it based on the expected load in the rest of the grid.
-To this end, the controller first estimates the expected load in the microgrid based on buy and sell bids in the bid storage as well as on outstanding energy trades in the ledger.
-By combining this estimate with the expected load in the remainder of the grid, the controller produces a control signal that specifies how much the microgrid load should be decreased or increased.
-Finally, based on this control signal, the controller updates the price policy for the microgrid to influence energy production and consumption.
-
-\subsection{Requirements}
-
-\subsubsection{Security}
-Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.
-
-\subsubsection{Safety}
-A careless or malicious prosumer may destabilize the grid by promising to produce (or consume) a large amount of energy, but failing to deliver.
-Trades which are unlikely to be delivered and would result in a gap between actual production and demand should be prevented.
-
-\subsubsection{Privacy} 
-Energy trading should not compromise the privacy of prosumers.
-More specifically, prosumers' private information, including energy consumption and production values, are available only to the DSO.
-
-\section{Solution}
-
-In section, we describe our solution for providing privacy for prosumers without compromising the safety and security of the microgrid.
-Figure~\ref{fig:softwareArchitecture} shows a high-level overview of the architecture of our solution.
-
-\begin{figure}[h!]
-\center
-\begin{tikzpicture}[x=8cm, y=1.2cm,
-  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
-]
-\draw [nodeStyle, fill=white]   (0, 0) rectangle    (1, 0.9) node [midway, align=center] {Communication network\\and operating system};
-
-\draw [nodeStyle, fill=red!10]  (0, 1) rectangle    (1, 1.9) node [midway, align=center] {Communication anonymity\\(onion routing)};
-
-\draw [nodeStyle, fill=blue!10] (0, 2) rectangle    (1, 2.9) node [midway, align=center] {Distributed ledger\\(blockchain)};
-
-\draw [nodeStyle, fill=red!10]  (0,    3) rectangle (0.45, 3.9) node [midway, align=center] {Transaction anonymity\\(mixing service)};
-\draw [nodeStyle, fill=blue!10] (0.47, 3) rectangle (0.72, 3.9) node [midway, align=center] {Bid storage};
-\draw [nodeStyle, fill=red!10 ] (0.74, 3) rectangle (1,    3.9) node [midway, align=center] {Active\\smart meter};
-
-\draw [nodeStyle, fill=blue!10] (0,    4) rectangle (0.49, 4.9) node [midway, align=center] {Prosumer trading\\algorithm};
-\draw [nodeStyle, fill=blue!10] (0.51, 4) rectangle (1,    4.9) node [midway, align=center] {DSO control\\algorithm};
-\end{tikzpicture}
-\caption{High-level architecture of the proposed solution.
-Components marked red are introduced to provide privacy in a safe and secure manner.
-Components marked in blue are typical elements of a decentralized transactive microgrid.}
-\label{fig:softwareArchitecture}
-\end{figure}
-
-\begin{figure*}[h]
-\center
-\begin{tikzpicture}[x=3.8cm, y=2cm, font=\small,
-  system/.style={draw, align=center, rounded corners=0.1cm, fill=black!5},
-  entity/.style={draw, align=center, rounded corners=0.1cm},
-  asset/.style={midway, align=center},
-  transfer/.style={->, >=stealth, shorten <=0.05cm, shorten >=0.05cm},
-]
-%\node[entity] (smartmeter) at (0.75, 0.5) {smart\\meter};
-%\node[entity] (prosumer1) at (1.25, 1) {prosumer};
-%\node[system] (mixing1) at (2, 1) {mixing\\service};
-%\node[entity] (prosumer2) at (3, 1) {prosumer\\(alternative address)};
-%\node[system] (bidstorage) at (4, 1) {bid\\storage};
-%\node[entity] (partner) at (4, 0) {other prosumer};
-%\node[entity] (prosumer3) at (3, 0) {prosumer\\(alternative address)};
-%\node[system] (mixing2) at (2, 0) {mixing\\service};
-%\node[entity] (prosumer4) at (1.25, 0) {prosumer};
-\node[entity] (smartmeter) at (0, 1) {smart meter};
-\node[entity] (prosumer1) at (1, 1) {prosumer};
-\node[system] (mixing1) at (1.9, 1) {mixing\\service};
-\node[entity] (prosumer2) at (3, 1) {prosumer\\(anonymous address)};
-\node[system] (bidstorage) at (4, 0.5) {bid\\storage};
-\node[entity] (partner) at (3, 0) {other prosumer};
-\node[entity] (prosumer3) at (1.5, 0) {prosumer\\(anonymous address)};
-\node[entity] (smartmeter2) at (0, 0) {smart meter\\(anonymous address)};
-
-%\draw[transfer] (smartmeter) -- node [asset, above left] {energy\\production asset} (prosumer1);
-%\draw[transfer] (prosumer1) -- node [asset, above] {energy\\production asset} (mixing1);
-%\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
-%\draw[transfer, dashed] (prosumer2) -- node [asset, above] {energy production asset,\\sell bid} (bidstorage);
-%\draw[transfer, dashed] (bidstorage) -- node [asset, right] {sell\\bid} (partner);
-%\draw[transfer, bend right=15] (partner) to node [asset, below] {financial asset,\\energy\\consumption asset} (prosumer3);
-%\draw[transfer, bend right=7.5] (prosumer2) to node [asset, above right] {energy\\prod. asset} (partner);
-%\draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
-%energy consumption asset} (mixing2);
-%\draw[transfer] (mixing2) -- node [asset, below] {financial asset,\\energy consumption asset} (prosumer4);
-%\draw[transfer] (prosumer4) -- node [asset, below left] {financial\\asset} (smartmeter);
-
-\draw[transfer] (smartmeter) -- node [asset, above] {energy\\production asset} (prosumer1);
-\draw[transfer] (prosumer1) -- node [asset, above] {energy\\production asset} (mixing1);
-\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
-\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {energy production asset,\\sell bid} (bidstorage);
-\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {sell\\bid} (partner);
-\draw[transfer, bend right=30] (partner) to node [asset, below] {financial asset,\\energy consumption asset} (prosumer3);
-\draw[transfer, bend right=50] (prosumer2) to node [asset, right] {energy\\production asset} (partner);
-\draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
-energy consumption asset} (smartmeter2);
-\end{tikzpicture}
-\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy production.
-Note that in order to prevent de-anonymization, a prosumer should use multiple addresses for mixing and multiple rounds of mixing.}
-\end{figure*}
-
-\subsection{Timing}
-The ability to specify points or intervals in time is crucial.
-For example, control signals specify how the load should change at certain points in time, energy trades specify when energy will be consumed or produced, etc.
-To facilitate processing signals and transactions, we divide time into fixed-length intervals, and specify points or periods in time using these discrete timesteps.
-The length of the time interval is determined by mapping the timing assumptions of the power system to our platform.
-%In our implementation, 
-For example, the default length of the time interval may be 4 seconds, which corresponds to how frequently the control signal of the DSO typically changes.
-
-\subsection{Services}
-
-Here, we describe three services that must be implemented for our solution: communication anonymity, mixing service for transaction anonymity, and anonymous bid storage for bidding anonymity.
-
-\subsubsection{Communication Anonymity}
-Firstly, we must provide an anonymous communication layer, on which we can build an anonymous trading platform.
-Without this communication layer, bids and transactions could be easily de-anonymized based on the network identifiers of the sources (e.g., IP or MAC addresses).
-
-We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}.
-To build an onion network, the smart meters, inverters, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on a private blockchain.
-In our first implementation, we can use the free and open-source Tor software with private Directory Authorities.
-% ritter.vg: "run your own tor network"
-% https://ritter.vg/blog-run_your_own_tor_network.html
-
-\subsubsection{Transaction Anonymity}
-We must provide prosumers with the ability to create and publish transactions anonymously.
-More specifically, prosumers should be able to purchase or sell energy without revealing their identity; however, these transaction must also be verifiable and enforceable.
-
-We may achieve this goal using multiple approaches for blockchain transaction anonymity:
-\begin{itemize}
-\item Mixing services (also known as tumblers) mix potentially identifiable assets on a blockchain with others, thereby preventing tracing individual assets back to their original source. 
-In our case, assets to be mixed include virtual balances of fiat currencies as well as energy production and consumption.
-\item Cryptographic anonymity for transactions is provided, for example, by Zerocoin~\cite{miers2013zerocoin}. Similarly to mixing service, Zerocoin can prevent tracing assets on a blockchain.
-\end{itemize}
-Using the above techniques, we can enable prosumers to trade energy anonymously (i.e., without revealing their true identities), but at the same time prevent them from altering their energy or financial balances without a valid transaction.
-
-However, we must also ensure that 1) smart meters know the amount of energy purchased or sold by their prosumer and 2) prosumers cannot purchase or sell more energy than their capacity.
-To satisfy both of these constraints, all energy trades must start with the prosumer withdrawing a certain amount of energy production or consumption from its smart meter:
-\begin{itemize}
-\item If a prosumer wishes to sell energy, it must first obtain an energy asset from its smart meter using a blockchain transaction.
-This transaction must be signed by the smart meter, which enables the smart meter to 1) keep track of the amount of energy traded by the prosumer as well as to 2) enforce safety requirements by limiting the amount of energy that can be withdrawn.
-\item If a prosumer wishes to buy energy, it must first obtain an energy consumption asset from its smart meter in a way similar to obtaining an energy production asset.
-\end{itemize}
-
-\subsubsection{Bidding Anonymity}
-Finally, we must provide prosumers with the ability to publish energy buy and sell bids anonymously.
-To this end, we create a storage for anonymous bids that is readable by all the prosumers in the microgrid.
-Any prosumer may submit a bid to this storage; however, in order to do so, they must provide a zero-knowledge proof of owning the assets that are to be traded:
-\begin{itemize}
-\item To submit an energy sell bid, the prosumer must prove that it owns an energy production asset on the chain.
-\item To submit an energy buy bid, the prosumer must prove that it own an energy consumption asset as well as financial assets on the chain.
-\end{itemize}
-
-\subsection{Transaction Types}
-
-Before we can discuss transaction types, we must first define the three assets that these transactions may transfer.
-
-An \emph{energy production asset} (EPA) is defined by
-\begin{compactitem}
-\item \field{power}: non-negative amount of power to produced (for example, measured in watts).
-\item \field{start}: first time interval in which energy is to be produced. 
-\item \field{end}: last time interval in which energy is to be produced.
-\end{compactitem}
-An \emph{energy consumption asset} (ECA) is defined by the same fields; however, for this asset, the fields define consumption instead of production.
-Finally, a \emph{financial asset} (FA) is defined by a single non-negative field \field{amount}, which can be denominated in either a fiat currency (e.g., US dollars) or a cryptocurrency.
-
-\subsubsection{Energy and Financial Transactions}
-
-Energy and financial transactions transfer energy and financial asset from one address to another.
-Prosumers use these transactions for multiple purposes: to trade energy by exchanging assets with other prosumers, to prove to the bid storage that they have production or consumption capacity, to hide their identity by transferring assets to and from mixing services, and to deposit assets at their smart meter.
-%
-An energy and financial transaction contains the following fields:
-\begin{compactitem}
-\item List of EPA inputs, each of which is defined by:
-\begin{compactitem}
-\item \field{out}: EPA output from a previous transaction,
-\item \field{sig}: signature for this output.
-\end{compactitem}
-\item List of ECA inputs, each of which is defined by:
-\begin{compactitem}
-\item \field{out}: ECA output from a previous transaction,
-\item \field{sig}: signature for this output.
-\end{compactitem}
-\item List of FA inputs, each of which is defined by:
-\begin{compactitem}
-\item \field{out}: FA output from a previous transaction,
-\item \field{sig}: signature for this output.
-\end{compactitem}
-\item List of EPA outputs, each of which is defined by:
-\begin{compactitem}
-\item an EPA and an address to which it is transferred.
-\end{compactitem}
-\item List of ECA outputs, each of which is defined by:
-\begin{compactitem}
-\item an ECA and an address to which it is transferred.
-\end{compactitem}
-\item List of FA outputs, each of which is defined by:
-\begin{compactitem}
-\item an FA and an address to which it is transferred.
-\end{compactitem}
-\end{compactitem}
-
-An energy and financial transaction is valid if the following three conditions hold.
-\begin{compactitem}
-\item None of the outputs referenced by the inputs have been spent by a transaction that has been recorded on the ledger.
-\item All of the signatures are valid.
-\item For each asset type (and for each timestep), the sum of inputs and outputs is the same.
-For example, in the case of energy production assets, the condition is:
-\begin{align}
-\forall t: & \sum_{out \in \text{EPA outputs}} out.\mathtt{power} \cdot 1_{\left\{out.\mathtt{start} \leq t \leq out.\mathtt{end}\right\}} \nonumber \\
-& = \sum_{in \in \text{EPA inputs}} in.\mathtt{out}.\mathtt{power} \cdot 1_{\left\{in.\mathtt{out}.\mathtt{start} \leq t \leq in.\mathtt{out}.\mathtt{end}\right\}} ,
-\end{align}
-where $1_x$ is equal to $1$ if $x$ is true, and it is $0$ otherwise.
-%\begin{equation}
-%\forall t: \sum_{out \in \left\{out' \middle| out' \in \text{ EPA outputs} \wedge out'.EPA.start \leq t \leq out'.EPA.end\right\}} out.EPA.Power = \sum_{in \in \left\{in' \middle| in' \in \text{ EPA inputs} \wedge in'.EPA.start \leq t \leq in'.EPA.end\right\}} in.EPA.Power .
-%\end{equation}
-\end{compactitem}
-If a transaction submitted to the ledger is valid, it will be permanently recorded.
-
-\subsubsection{Smart-Meter Transactions}
-
-Prosumers use smart-meter transactions to withdraw energy and financial assets from their own smart meters, before they engage in energy trading.
-%
-A smart-meter transaction contains the following fields:
-\begin{compactitem}
-\item List of EPA outputs, each of which is defined by:
-\begin{compactitem}
-\item an EPA and an address to which it is transferred.
-\end{compactitem}
-\item List of ECA outputs, each of which is defined by:
-\begin{compactitem}
-\item an ECA and an address to which it is transferred.
-\end{compactitem}
-\item List of FA outputs, each of which is defined by:
-\begin{compactitem}
-\item an FA and an address to which it is transferred.
-\end{compactitem}
-\item \field{id}: Identifier of the smart meter.
-\item \field{sig}: Smart meter's signature over the transaction.
-\end{compactitem}
-
-A smart-meter transaction is valid if the following two conditions hold:
-\begin{compactitem}
-\item The smart meter identified in the transaction has been authorized by a regulatory transaction that has been recorded on the ledger.
-\item The smart meter's signature is valid.
-\end{compactitem}
-\todo{To address malfunctioning or compromised smart meters, we could also impose a limit on withdrawals.}
-
-\subsubsection{Regulatory Transactions}
-
-The DSO uses regulatory transactions to authorize or ban smart meters and to control the microgrid load through setting a price policy.
-Since these transactions provide a diverse set of functionality, they are divided into two types.
-
-\paragraph{Authorize or Ban Smart Meters}
-The DSO uses these transactions to manage the set of authorized smart meters in the microgrid.
-Whenever a new smart meter is installed, the DSO notifies the members of the microgrid using a regulatory transaction.
-Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or it is believed to be malfunctioning or compromised), the DSO notifies the members of the microgrid using a regulatory transaction.
-These transactions contain the following fields:
-\begin{compactitem}
-\item List of smart meters to be authorized, each of which is defined by:
-\begin{compactitem}
-\item \field{id}: Identifier of the smart meter.
-\item \field{pubkey}: Public key of the smart meter.
-\end{compactitem}
-\item List of smart meters to be banned, each of which is given using its identifier.
-\item \field{time}: Timestep in which smart meters are authorized and banned.
-\item \field{sig}: DSO's signature over the transaction.
-\end{compactitem}
-
-A regulatory transaction of this type is valid if the following two conditions hold:
-\begin{compactitem}
-\item The timestep specified in the transaction is in the future.
-\item The DSO's signature is valid.
-\end{compactitem}
-
-\paragraph{Price Policy}
+\input{solution.tex}
 
@@
 
-\section{Related Work}
-\label{sec:related}
+\input{related.tex}
 
-\subsection{Smart Grid and Meter Privacy}
-
-% http://ieeexplore.ieee.org/abstract/document/5054916/
-McDaniel and McLaughlin discuss privacy challenges in smart grids~\cite{mcdaniel2009security}.
-
-% https://arxiv.org/pdf/1108.2234.pdf
-% https://pdfs.semanticscholar.org/cdf8/a5b6256823bca38a1d2347ab36f8e4a2ca94.pdf
-Rajagopalan et al.\ use tools from information theory to present a framework, which abstracts both the privacy and the utility requirements of smart meter data~\cite{rajagopalan2011smart,sankar2013smart}.
-Their framework leads to a novel privacy-utility tradeoff problem with minimal assumptions.
-%, which is tractable.
-
-% http://www.comm.toronto.edu/~akhisti/sm.pdf
-Varodayan and Khisti study using rechargeable battery for partially protecting the privacy of information contained in a household's electrical load profile~\cite{varodayan2011smart}.
-They show that stochastic battery policies may leak 26\% less information than a best-effort policy, holds the output load constant whenever possible.
-
-% https://www.researchgate.net/profile/Georgios_Kalogridis/publication/224189766_Smart_Grid_Privacy_via_Anonymization_of_Smart_Metering_Data/links/541169510cf2b4da1bec4193.pdf
-Efthymiou and Kalogridis describe a method for securely anonymizing frequent electrical metering data sent by a smart meter~\cite{efthymiou2010smart}. 
-Their approach is based on the observation that frequent metering data may be required by an energy distribution network for operational reasons, but it may not necessarily need to be attributable to a specific smart meter.
-The authors describe a method that provides a third-party escrow mechanism for authenticated anonymous meter readings, which are difficult to associate with particular smart meter.
-
-% https://arxiv.org/pdf/1305.0735.pdf
-Tan et al.\ study privacy in a smart metering system from an information theoretic perspective in the presence of energy harvesting and storage units~\cite{tan2013increasing}. 
-They show that energy harvesting provides increased privacy by diversifying the energy source, while a storage device can be used to increase both energy efficiency and privacy. 
-They show that there exists a trade-off between the information leakage rate and the wasted energy rate, and study the impact of the energy harvesting rate and the size of the storage device on this trade-off.
-
-\subsection{Blockchain Technology}
-
-Microsoft offers Blockchain as a Service (BaaS) on Azure.
-Project Bletchley is Microsoft's architectural approach to building an Enterprise Consortium Blockchain Ecosystem, introducing two new concepts: blockchain middleware and cryptlets~\cite{gray2016introducing}.
-
-Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}.
-
-Interledger is a protocol for payments across payment systems, which enables anyone with accounts on two ledgers to create
-a connection between them~\cite{thomas_protocol}.
-
-Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}.
-
-\url{https://geli.net/residential/}
-\url{https://www.greentechmedia.com/articles/read/geli-raises-7m-to-take-energy-storage-software-to-the-next-level}
-
-\section{Conclusion}
-\label{sec:concl}
+\input{concl.tex}
 

### 2017-06-01 papers/IoT2017/prelim.tex
no message

\section{Preliminaries and Requirements}

\subsection{Transactive Microgrid}

Here, we describe a basic system model for a transactive microgrid based on a distributed ledger, such as a blockchain.
% - smart meters
% - distributed ledger, such as blockchain

\subsubsection{Distributed Ledger}
The distributed ledger stores transactions that specify energy trades, change regulatory policies for the microgrid, etc.
Since the ledger is maintained by multiple ledger nodes, a key implementation requirement is reaching consensus on which transactions are valid and stored in the ledger.
This consensus must be reached quickly, reliably, and securely even in the presence of erroneous or even malicious ledger nodes.
We treat the consensus algorithm as a pluggable module, which can be based on blockchains with proof-of-stake consensus or Practical Byzantine Fault Tolerance algorithm~\cite{castro1999practical}.

\subsubsection{Bid Storage Service}
Although individual prosumers trade energy with each other, for the sake of scalability, we need a service that enables prosumers to find trade partners.
By providing a storage service for buy and sell bids, we relieve prosumer nodes from communicating with all potential trade partners.
In addition to receiving and storing bids from prosumers, the bid storage service can also find matches and notify prosumers of the opportunity to make an energy trade.
Even though the bid storage appears to the nodes as one entity, for the sake of scalability and reliability, it can be implemented in a distributed manner, using multiple nodes.

\subsubsection{Microgrid Controller}
The microgrid controller is responsible for stabilizing load within the microgrid and controlling it based on the expected load in the rest of the grid.
To this end, the controller first estimates the expected load in the microgrid based on buy and sell bids in the bid storage as well as on outstanding energy trades in the ledger.
By combining this estimate with the expected load in the remainder of the grid, the controller produces a control signal that specifies how much the microgrid load should be decreased or increased.
Finally, based on this control signal, the controller updates the price policy for the microgrid to influence energy production and consumption.

\subsection{Requirements}

\subsubsection{Security}
Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.

\subsubsection{Safety}
A careless or malicious prosumer may destabilize the grid by promising to produce (or consume) a large amount of energy, but failing to deliver.
Trades which are unlikely to be delivered and would result in a gap between actual production and demand should be prevented.

\subsubsection{Privacy} 
Energy trading should not compromise the privacy of prosumers.
More specifically, prosumers' private information, including energy consumption and production values, are available only to the DSO.

### 2017-06-01 papers/IoT2017/related.tex
no message

\section{Related Work}
\label{sec:related}

\subsection{Smart Grid and Meter Privacy}

% http://ieeexplore.ieee.org/abstract/document/5054916/
McDaniel and McLaughlin discuss privacy challenges in smart grids~\cite{mcdaniel2009security}.

% https://arxiv.org/pdf/1108.2234.pdf
% https://pdfs.semanticscholar.org/cdf8/a5b6256823bca38a1d2347ab36f8e4a2ca94.pdf
Rajagopalan et al.\ use tools from information theory to present a framework, which abstracts both the privacy and the utility requirements of smart meter data~\cite{rajagopalan2011smart,sankar2013smart}. Their framework leads to a novel privacy-utility tradeoff problem with minimal assumptions. %, which is tractable.

% http://www.comm.toronto.edu/~akhisti/sm.pdf
Varodayan and Khisti study using rechargeable battery for partially protecting the privacy of information contained in a household's electrical load profile~\cite{varodayan2011smart}.
They show that stochastic battery policies may leak 26\% less information than a best-effort policy, holds the output load constant whenever possible.

% https://www.researchgate.net/profile/Georgios_Kalogridis/publication/224189766_Smart_Grid_Privacy_via_Anonymization_of_Smart_Metering_Data/links/541169510cf2b4da1bec4193.pdf
Efthymiou and Kalogridis describe a method for securely anonymizing frequent electrical metering data sent by a smart meter~\cite{efthymiou2010smart}. 
Their approach is based on the observation that frequent metering data may be required by an energy distribution network for operational reasons, but it may not necessarily need to be attributable to a specific smart meter.
The authors describe a method that provides a third-party escrow mechanism for authenticated anonymous meter readings, which are difficult to associate with particular smart meter.

% https://arxiv.org/pdf/1305.0735.pdf
Tan et al.\ study privacy in a smart metering system from an information theoretic perspective in the presence of energy harvesting and storage units~\cite{tan2013increasing}. 
They show that energy harvesting provides increased privacy by diversifying the energy source, while a storage device can be used to increase both energy efficiency and privacy. 
They show that there exists a trade-off between the information leakage rate and the wasted energy rate, and study the impact of the energy harvesting rate and the size of the storage device on this trade-off.

\subsection{Blockchain Technology}

Microsoft offers Blockchain as a Service (BaaS) on Azure.
Project Bletchley is Microsoft's architectural approach to building an Enterprise Consortium Blockchain Ecosystem, introducing two new concepts: blockchain middleware and cryptlets~\cite{gray2016introducing}.

Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}.

Interledger is a protocol for payments across payment systems, which enables anyone with accounts on two ledgers to create
a connection between them~\cite{thomas_protocol}.

Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}.

\url{https://geli.net/residential/}
\url{https://www.greentechmedia.com/articles/read/geli-raises-7m-to-take-energy-storage-software-to-the-next-level}

### 2017-06-01 papers/IoT2017/solution.tex
no message

\section{Solution}

In section, we describe our solution for providing privacy for prosumers without compromising the safety and security of the microgrid.
Figure~\ref{fig:softwareArchitecture} shows a high-level overview of the architecture of our solution.

\begin{figure}[h!]
\center
\begin{tikzpicture}[x=8cm, y=1.2cm,
  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
]
\draw [nodeStyle, fill=white]   (0, 0) rectangle    (1, 0.9) node [midway, align=center] {Communication network\\and operating system};

\draw [nodeStyle, fill=red!10]  (0, 1) rectangle    (1, 1.9) node [midway, align=center] {Communication anonymity\\(onion routing)};

\draw [nodeStyle, fill=blue!10] (0, 2) rectangle    (1, 2.9) node [midway, align=center] {Distributed ledger\\(blockchain)};

\draw [nodeStyle, fill=red!10]  (0,    3) rectangle (0.45, 3.9) node [midway, align=center] {Transaction anonymity\\(mixing service)};
\draw [nodeStyle, fill=blue!10] (0.47, 3) rectangle (0.72, 3.9) node [midway, align=center] {Bid storage};
\draw [nodeStyle, fill=red!10 ] (0.74, 3) rectangle (1,    3.9) node [midway, align=center] {Active\\smart meter};

\draw [nodeStyle, fill=blue!10] (0,    4) rectangle (0.49, 4.9) node [midway, align=center] {Prosumer trading\\algorithm};
\draw [nodeStyle, fill=blue!10] (0.51, 4) rectangle (1,    4.9) node [midway, align=center] {DSO control\\algorithm};
\end{tikzpicture}
\caption{High-level architecture of the proposed solution. Components marked red are introduced to provide privacy in a safe and secure manner. Components marked in blue are typical elements of a decentralized transactive microgrid.}
\label{fig:softwareArchitecture}
\end{figure}

\begin{figure*}[h]
\center
\begin{tikzpicture}[x=3.8cm, y=2cm, font=\small,
  system/.style={draw, align=center, rounded corners=0.1cm, fill=black!5},
  entity/.style={draw, align=center, rounded corners=0.1cm},
  asset/.style={midway, align=center},
  transfer/.style={->, >=stealth, shorten <=0.05cm, shorten >=0.05cm},
]
%\node[entity] (smartmeter) at (0.75, 0.5) {smart\\meter};
%\node[entity] (prosumer1) at (1.25, 1) {prosumer};
%\node[system] (mixing1) at (2, 1) {mixing\\service};
%\node[entity] (prosumer2) at (3, 1) {prosumer\\(alternative address)};
%\node[system] (bidstorage) at (4, 1) {bid\\storage};
%\node[entity] (partner) at (4, 0) {other prosumer};
%\node[entity] (prosumer3) at (3, 0) {prosumer\\(alternative address)};
%\node[system] (mixing2) at (2, 0) {mixing\\service};
%\node[entity] (prosumer4) at (1.25, 0) {prosumer};
\node[entity] (smartmeter) at (0, 1) {smart meter};
\node[entity] (prosumer1) at (1, 1) {prosumer};
\node[system] (mixing1) at (1.9, 1) {mixing\\service};
\node[entity] (prosumer2) at (3, 1) {prosumer\\(anonymous address)};
\node[system] (bidstorage) at (4, 0.5) {bid\\storage};
\node[entity] (partner) at (3, 0) {other prosumer};
\node[entity] (prosumer3) at (1.5, 0) {prosumer\\(anonymous address)};
\node[entity] (smartmeter2) at (0, 0) {smart meter\\(anonymous address)};

%\draw[transfer] (smartmeter) -- node [asset, above left] {energy\\production asset} (prosumer1);
%\draw[transfer] (prosumer1) -- node [asset, above] {energy\\production asset} (mixing1);
%\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
%\draw[transfer, dashed] (prosumer2) -- node [asset, above] {energy production asset,\\sell bid} (bidstorage);
%\draw[transfer, dashed] (bidstorage) -- node [asset, right] {sell\\bid} (partner);
%\draw[transfer, bend right=15] (partner) to node [asset, below] {financial asset,\\energy\\consumption asset} (prosumer3);
%\draw[transfer, bend right=7.5] (prosumer2) to node [asset, above right] {energy\\prod. asset} (partner);
%\draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
%energy consumption asset} (mixing2);
%\draw[transfer] (mixing2) -- node [asset, below] {financial asset,\\energy consumption asset} (prosumer4);
%\draw[transfer] (prosumer4) -- node [asset, below left] {financial\\asset} (smartmeter);

\draw[transfer] (smartmeter) -- node [asset, above] {energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {energy production asset,\\sell bid} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {sell\\bid} (partner);
\draw[transfer, bend right=30] (partner) to node [asset, below] {financial asset,\\energy consumption asset} (prosumer3);
\draw[transfer, bend right=50] (prosumer2) to node [asset, right] {energy\\production asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
energy consumption asset} (smartmeter2);
\end{tikzpicture}
\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy production. Note that in order to prevent de-anonymization, a prosumer should use multiple addresses for mixing and multiple rounds of mixing.}
\end{figure*}

\subsection{Timing}
The ability to specify points or intervals in time is crucial.
For example, control signals specify how the load should change at certain points in time, energy trades specify when energy will be consumed or produced, etc.
To facilitate processing signals and transactions, we divide time into fixed-length intervals, and specify points or periods in time using these discrete timesteps.
The length of the time interval is determined by mapping the timing assumptions of the power system to our platform.
%In our implementation, 
For example, the default length of the time interval may be 4 seconds, which corresponds to how frequently the control signal of the DSO typically changes.

\subsection{Services}

Here, we describe three services that must be implemented for our solution: communication anonymity, mixing service for transaction anonymity, and anonymous bid storage for bidding anonymity.

\subsubsection{Communication Anonymity}
Firstly, we must provide an anonymous communication layer, on which we can build an anonymous trading platform.
Without this communication layer, bids and transactions could be easily de-anonymized based on the network identifiers of the sources (e.g., IP or MAC addresses).

We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}.
To build an onion network, the smart meters, inverters, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on a private blockchain.
In our first implementation, we can use the free and open-source Tor software with private Directory Authorities.
% ritter.vg: "run your own tor network"
% https://ritter.vg/blog-run_your_own_tor_network.html

\subsubsection{Transaction Anonymity}
We must provide prosumers with the ability to create and publish transactions anonymously.
More specifically, prosumers should be able to purchase or sell energy without revealing their identity; however, these transaction must also be verifiable and enforceable.

We may achieve this goal using multiple approaches for blockchain transaction anonymity:
\begin{itemize}
\item Mixing services (also known as tumblers) mix potentially identifiable assets on a blockchain with others, thereby preventing tracing individual assets back to their original source. 
In our case, assets to be mixed include virtual balances of fiat currencies as well as energy production and consumption.
\item Cryptographic anonymity for transactions is provided, for example, by Zerocoin~\cite{miers2013zerocoin}. Similarly to mixing service, Zerocoin can prevent tracing assets on a blockchain.
\end{itemize}
Using the above techniques, we can enable prosumers to trade energy anonymously (i.e., without revealing their true identities), but at the same time prevent them from altering their energy or financial balances without a valid transaction.

However, we must also ensure that 1) smart meters know the amount of energy purchased or sold by their prosumer and 2) prosumers cannot purchase or sell more energy than their capacity.
To satisfy both of these constraints, all energy trades must start with the prosumer withdrawing a certain amount of energy production or consumption from its smart meter:
\begin{itemize}
\item If a prosumer wishes to sell energy, it must first obtain an energy asset from its smart meter using a blockchain transaction.
This transaction must be signed by the smart meter, which enables the smart meter to 1) keep track of the amount of energy traded by the prosumer as well as to 2) enforce safety requirements by limiting the amount of energy that can be withdrawn.
\item If a prosumer wishes to buy energy, it must first obtain an energy consumption asset from its smart meter in a way similar to obtaining an energy production asset.
\end{itemize}

\subsubsection{Bidding Anonymity}
Finally, we must provide prosumers with the ability to publish energy buy and sell bids anonymously.
To this end, we create a storage for anonymous bids that is readable by all the prosumers in the microgrid.
Any prosumer may submit a bid to this storage; however, in order to do so, they must provide a zero-knowledge proof of owning the assets that are to be traded:
\begin{itemize}
\item To submit an energy sell bid, the prosumer must prove that it owns an energy production asset on the chain.
\item To submit an energy buy bid, the prosumer must prove that it own an energy consumption asset as well as financial assets on the chain.
\end{itemize}

\subsection{Transaction Types}

Before we can discuss transaction types, we must first define the three assets that these transactions may transfer.

An \emph{energy production asset} (EPA) is defined by
\begin{compactitem}
\item \field{power}: non-negative amount of power to produced (for example, measured in watts).
\item \field{start}: first time interval in which energy is to be produced. 
\item \field{end}: last time interval in which energy is to be produced.
\end{compactitem}
An \emph{energy consumption asset} (ECA) is defined by the same fields; however, for this asset, the fields define consumption instead of production.
Finally, a \emph{financial asset} (FA) is defined by a single non-negative field \field{amount}, which can be denominated in either a fiat currency (e.g., US dollars) or a cryptocurrency.

\subsubsection{Energy and Financial Transactions}

Energy and financial transactions transfer energy and financial asset from one address to another.
Prosumers use these transactions for multiple purposes: to trade energy by exchanging assets with other prosumers, to prove to the bid storage that they have production or consumption capacity, to hide their identity by transferring assets to and from mixing services, and to deposit assets at their smart meter.
%
An energy and financial transaction contains the following fields:
\begin{compactitem}
\item List of EPA inputs, each of which is defined by:
\begin{compactitem}
\item \field{out}: EPA output from a previous transaction,
\item \field{sig}: signature for this output.
\end{compactitem}
\item List of ECA inputs, each of which is defined by:
\begin{compactitem}
\item \field{out}: ECA output from a previous transaction,
\item \field{sig}: signature for this output.
\end{compactitem}
\item List of FA inputs, each of which is defined by:
\begin{compactitem}
\item \field{out}: FA output from a previous transaction,
\item \field{sig}: signature for this output.
\end{compactitem}
\item List of EPA outputs, each of which is defined by:
\begin{compactitem}
\item an EPA and an address to which it is transferred.
\end{compactitem}
\item List of ECA outputs, each of which is defined by:
\begin{compactitem}
\item an ECA and an address to which it is transferred.
\end{compactitem}
\item List of FA outputs, each of which is defined by:
\begin{compactitem}
\item an FA and an address to which it is transferred.
\end{compactitem}
\end{compactitem}

An energy and financial transaction is valid if the following three conditions hold.
\begin{compactitem}
\item None of the outputs referenced by the inputs have been spent by a transaction that has been recorded on the ledger.
\item All of the signatures are valid.
\item For each asset type (and for each timestep), the sum of inputs and outputs is the same.
For example, in the case of energy production assets, the condition is:
\begin{align}
\forall t: & \sum_{out \in \text{EPA outputs}} out.\mathtt{power} \cdot 1_{\left\{out.\mathtt{start} \leq t \leq out.\mathtt{end}\right\}} \nonumber \\
& = \sum_{in \in \text{EPA inputs}} in.\mathtt{out}.\mathtt{power} \cdot 1_{\left\{in.\mathtt{out}.\mathtt{start} \leq t \leq in.\mathtt{out}.\mathtt{end}\right\}} ,
\end{align}
where $1_x$ is equal to $1$ if $x$ is true, and it is $0$ otherwise.
%\begin{equation}
%\forall t: \sum_{out \in \left\{out' \middle| out' \in \text{ EPA outputs} \wedge out'.EPA.start \leq t \leq out'.EPA.end\right\}} out.EPA.Power = \sum_{in \in \left\{in' \middle| in' \in \text{ EPA inputs} \wedge in'.EPA.start \leq t \leq in'.EPA.end\right\}} in.EPA.Power .
%\end{equation}
\end{compactitem}
If a transaction submitted to the ledger is valid, it will be permanently recorded.

\subsubsection{Smart-Meter Transactions}

Prosumers use smart-meter transactions to withdraw energy and financial assets from their own smart meters, before they engage in energy trading.
%
A smart-meter transaction contains the following fields:
\begin{compactitem}
\item List of EPA outputs, each of which is defined by:
\begin{compactitem}
\item an EPA and an address to which it is transferred.
\end{compactitem}
\item List of ECA outputs, each of which is defined by:
\begin{compactitem}
\item an ECA and an address to which it is transferred.
\end{compactitem}
\item List of FA outputs, each of which is defined by:
\begin{compactitem}
\item an FA and an address to which it is transferred.
\end{compactitem}
\item \field{id}: Identifier of the smart meter.
\item \field{sig}: Smart meter's signature over the transaction.
\end{compactitem}

A smart-meter transaction is valid if the following two conditions hold:
\begin{compactitem}
\item The smart meter identified in the transaction has been authorized by a regulatory transaction that has been recorded on the ledger.
\item The smart meter's signature is valid.
\end{compactitem}
\todo{To address malfunctioning or compromised smart meters, we could also impose a limit on withdrawals.}

\subsubsection{Regulatory Transactions}

The DSO uses regulatory transactions to authorize or ban smart meters and to control the microgrid load through setting a price policy.
Since these transactions provide a diverse set of functionality, they are divided into two types.

\paragraph{Authorize or Ban Smart Meters}
The DSO uses these transactions to manage the set of authorized smart meters in the microgrid.
Whenever a new smart meter is installed, the DSO notifies the members of the microgrid using a regulatory transaction.
Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or it is believed to be malfunctioning or compromised), the DSO notifies the members of the microgrid using a regulatory transaction.
These transactions contain the following fields:
\begin{compactitem}
\item List of smart meters to be authorized, each of which is defined by:
\begin{compactitem}
\item \field{id}: Identifier of the smart meter.
\item \field{pubkey}: Public key of the smart meter.
\end{compactitem}
\item List of smart meters to be banned, each of which is given using its identifier.
\item \field{time}: Timestep in which smart meters are authorized and banned.
\item \field{sig}: DSO's signature over the transaction.
\end{compactitem}

A regulatory transaction of this type is valid if the following two conditions hold:
\begin{compactitem}
\item The timestep specified in the transaction is in the future.
\item The DSO's signature is valid.
\end{compactitem}

\paragraph{Price Policy}

### 2017-06-02 papers/IoT2017/intro.tex
Updated - added introduction

@@
+%!TEX root = paper.tex
 \section{Introduction}
+
+% What are transactive energy systems
+% What is the key challenge : decentralized information architecture
+% What is the related research
+% What are the contributions of this paper
+% What is the outline of this paper
+
+Power grids are undergoing major changes due to rapid
+acceleration in renewable energy resources, such as wind and solar power \cite{EIA2014, 5430489}. For example, 
+$4,143$ megawatts of solar panels were installed in third quarter of 2016 \cite{seia}.
+This capacity is estimated to grow from 4\% in 2015 to 29\% in 2040 \cite{Randal}.
+At the same time the battery technology costs per kWh have been dropping significantly \cite{stock2015powerful}, reaching grid parity \cite{bronski2015economics}.
+This massive integration of renewable energy requires detailed information and visibility into all aspects of this network, making it difficult to manage, especially in the presence of variable distributed energy resources \cite{7452738}.
+Therefore, a different vision for the future of power-grid operations is emerging: a decentralized system in which local communities are arranged in microgrids \cite{rahimi2012transactive}.
+In this vision, energy generation, transmission, distribution and even storage (e.g., electric vehicles in a community) can be strategically used to balance load and demand spikes.
+
+Furthering the concept of microgrids, transactive energy models have been proposed to support the next distribution system evolution \cite{kok2016society,cox2013structured,melton2013gridwise}.
+Transactive Energy is a set of market based constructs for dynamically balancing the demand and supply across the electrical infrastructure \cite{melton2013gridwise}.
+In this approach, customers on the same feeder (i.e.
+sharing a power line link) can operate in an open market, trading and exchanging generated energy locally.
+Distribution System Operators can be the custodian of this market, while still meeting the net demand \cite{7462854}.
+For example, the Brooklyn Microgrid developed by LO3 Energy is a peer-to-peer energy market for locally generated renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}
+
+On one hand, transactive energy is a decentralized power system controls problem \cite{7452738}, requiring strategic microgrid control to maintain the stability of the community and the utility.
+On the other hand, it is a distributed market problem where erroneous as well as malicious transactions can create a gap between demand and supply, eventually destabilizing the system.
+However, in both cases, this system requires a distributed  infrastructure comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator, which has to provide the necessary computation fabric to support the interplay between the energy control and the fiscal market challenges.
+For example, the Resilient Information Architecture Platform for Smart Grid (RIAPS) \cite{eisele2017riaps} is a distributed IoT  `operating system' that provides the foundations for all algorithms, isolates the hardware details from the algorithms, and provides essential mechanisms for resource management, fault tolerance, and security.
+\cite{Scott2017ICCPS} also describes a simple transactive energy application using the RIAPS platform.
+However, it does not provide the key supports required to handle the privacy challenges that arise from the required information exchange in this decentralized transactive system.
+
+% connect this back to the challenges described below
+Specifcally,
+
+% This is where the RIAPS and computing services discussion will be included. However, it does not solve the following challenges, which is the focus of this paper.
+%
 
@@
 % there are pilot studies, however, providing privacy is an open problem
-For example, the Brooklyn Microgrid developed by LO3 Energy is a peer-to-peer energy market for locally generated renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}
 

### 2017-06-04 papers/IoT2017/intro.tex
no message

@@
 This capacity is estimated to grow from 4\% in 2015 to 29\% in 2040 \cite{Randal}.
-At the same time the battery technology costs per kWh have been dropping significantly \cite{stock2015powerful}, reaching grid parity \cite{bronski2015economics}.
+At the same time, the battery technology costs per kWh have been dropping significantly \cite{stock2015powerful}, reaching grid parity \cite{bronski2015economics}.
 This massive integration of renewable energy requires detailed information and visibility into all aspects of this network, making it difficult to manage, especially in the presence of variable distributed energy resources \cite{7452738}.
@@
 Furthering the concept of microgrids, transactive energy models have been proposed to support the next distribution system evolution \cite{kok2016society,cox2013structured,melton2013gridwise}.
-Transactive Energy is a set of market based constructs for dynamically balancing the demand and supply across the electrical infrastructure \cite{melton2013gridwise}.
+Transactive energy is a set of market based constructs for dynamically balancing the demand and supply across the electrical infrastructure \cite{melton2013gridwise}.
 In this approach, customers on the same feeder (i.e.
 sharing a power line link) can operate in an open market, trading and exchanging generated energy locally.
-Distribution System Operators can be the custodian of this market, while still meeting the net demand \cite{7462854}.
-For example, the Brooklyn Microgrid developed by LO3 Energy is a peer-to-peer energy market for locally generated renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}
+Distribution System Operators (DSO) can be the custodian of this market, while still meeting the net demand \cite{7462854}.
+For example, the Brooklyn Microgrid, which was developed by LO3 Energy as a pilot project, is a peer-to-peer energy market for locally generated renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}
 
@@
 
+% This is where the RIAPS and computing services discussion will be included. However, it does not solve the following challenges, which is the focus of this paper.
+
 % connect this back to the challenges described below
-Specifcally,
-
-% This is where the RIAPS and computing services discussion will be included. However, it does not solve the following challenges, which is the focus of this paper.
-%
-
-% electric grid is changing: renewables, storage capacity, etc. -> prosumers
-
-In order to take advantage of these capabilities, electric grids need to become more decentralized.
-% what are the advantages of decentralization?
-
-% transactive microgrid
-
-% there are pilot studies, however, providing privacy is an open problem
-
-Transactive energy may pose a much greater threat to prosumers' privacy than smart metering.
+Specifically, 
+in order to take advantage of local energy production and storage capabilities, 
+%in order to take advantage of these capabilities, 
+electric grids need to become more decentralized.
+However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
 \begin{itemize}
-\item Firstly, since prosumers may purchase energy from each other in a transactive microgrid, transactions may inadvertently reveal the prosumers' detailed energy usage patterns to other prosumers within the microgrid.
-Addressing this issue in a decentralized trading platform is quite challenging as it requires hiding the identities of trade partners from each other.
+\item Firstly, since prosumers\footnote{We refer to customers as \emph{prosumers} to emphasize that they can not only consume energy, but may also produce it.}  may purchase energy from each other in a transactive microgrid, transactions may inadvertently reveal the prosumers' detailed energy usage patterns to other prosumers within the microgrid.
+Addressing this issue in a decentralized trading system is quite challenging as it requires hiding the identities of trade partners from each other.
 In comparison, secure smart metering reveals the prosumers' energy usage patterns only to the provider. 
@@
 
-We propose a solution that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, enables the DSO to regulate the trading platform and enforce certain safety rules.
+Before transactive energy system can be deployed in practice, we must address these privacy issues.
+However, this is a challenging task, as the system also has to satisfy security and safety requirements, which often conflict with privacy goals.
+For example, to prevent a prosumer from destabilizing the grid through careless of malicious energy trading, the system must check all of the prosumers' transactions.
+In a decentralized system, this requires disseminating information, which could be used to infer the prosumer's future energy consumption.
+
+In this paper, we propose a system that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, and enables the DSO to regulate the trading platform and enforce certain safety rules.
+\todo{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}
+First, we describe the basic elements of a transactive microgrid, and we formulate security, safety, and privacy requirements. 
+Then, we introduce a decentralized system for transactive microgrids based on distributed ledgers, and describe in detail the transactions and services that are used to implement this system.
+Next, we discuss how the system satisfies the security, safety, and privacy requirements.
+Finally, we give a brief overview of related work and offer concluding remarks.

### 2017-06-04 papers/IoT2017/prelim.tex
no message

@@
 
-Here, we describe a basic system model for a transactive microgrid based on a distributed ledger, such as a blockchain.
-% - smart meters
-% - distributed ledger, such as blockchain
+Here, we describe a basic system model of a transactive microgrid based on a distributed ledger, such as a blockchain.
 
 \subsubsection{Distributed Ledger}
+% - energy trades must be stored on a ledger (to prevent malleability)
+% - distributed ledger for reliability
 The distributed ledger stores transactions that specify energy trades, change regulatory policies for the microgrid, etc.
@@
 This consensus must be reached quickly, reliably, and securely even in the presence of erroneous or even malicious ledger nodes.
+% actually, we simply don't care about the consensus mechanism in this paper
 We treat the consensus algorithm as a pluggable module, which can be based on blockchains with proof-of-stake consensus or Practical Byzantine Fault Tolerance algorithm~\cite{castro1999practical}.
@@
 
+\subsubsection{Smart Meters}
+\TODO{measures energy production / consumption}
+\TODO{may record energy production / consumption on the ledger or directly report it to the DSO}
+
 \subsection{Requirements}
@@
 Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.
+\TODO{ensure correct billing (i.e., prosumer cannot tamper with energy production / consumption or financial balances of any prosumer)}
+\TODO{ensure that prosumers cannot back out of trades unilaterally, or tamper with other prosumers trading or bids}
+\TODO{ensure that prosumers cannot change policies that are to be set by the DSO for the microgird}
+\TODO{impact of node compromise is limited, and can be mitigated (i.e., offending node may be removed)}
 
@@
 A careless or malicious prosumer may destabilize the grid by promising to produce (or consume) a large amount of energy, but failing to deliver.
+\TODO{this could destabilize the microgrid, or even the main grid}
 Trades which are unlikely to be delivered and would result in a gap between actual production and demand should be prevented.
+\TODO{net amount of energy sold (or bought) by a prosumer is limited (by a constant set by the DSO), where net amount of energy sold is the difference between the amount of energy sold and bought (net amount of energy bought is defined analogously)}
+\TODO{energy bids posted by the prosumer are limited in the same way}
 
@@
 More specifically, prosumers' private information, including energy consumption and production values, are available only to the DSO.
+\TODO{other prosumers should not be able to tell how much energy was consumed / produced by a prosumer, or what bids the prosumer has posted (or with whom the prosumer traded}

### 2017-06-04 papers/IoT2017/intro.tex
no message

@@
 \todo{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}
-First, we describe the basic elements of a transactive microgrid, and we formulate security, safety, and privacy requirements. 
+First, we describe the basic components of a transactive microgrid, and we formulate security, safety, and privacy requirements. 
 Then, we introduce a decentralized system for transactive microgrids based on distributed ledgers, and describe in detail the transactions and services that are used to implement this system.

### 2017-06-04 papers/IoT2017/prelim.tex
no message

@@
 
-\subsection{Transactive Microgrid}
+\subsection{Transactive Microgrid Components}
 
-Here, we describe a basic system model of a transactive microgrid based on a distributed ledger, such as a blockchain.
+Here, we describe a basic system model of transactive microgrids.
+We discuss the following components: a distributed ledger for recording transactions, a bid storage service that facilitates finding trade partners, a microgrid controller for regulating the microgrid load, and smart meters for measuring energy production and consumption.
 
 \subsubsection{Distributed Ledger}
-% - energy trades must be stored on a ledger (to prevent malleability)
-% - distributed ledger for reliability
-The distributed ledger stores transactions that specify energy trades, change regulatory policies for the microgrid, etc.
-Since the ledger is maintained by multiple ledger nodes, a key implementation requirement is reaching consensus on which transactions are valid and stored in the ledger.
-This consensus must be reached quickly, reliably, and securely even in the presence of erroneous or even malicious ledger nodes.
-% actually, we simply don't care about the consensus mechanism in this paper
-We treat the consensus algorithm as a pluggable module, which can be based on blockchains with proof-of-stake consensus or Practical Byzantine Fault Tolerance algorithm~\cite{castro1999practical}.
+The ledger permanently stores transactions that specify energy trades, change regulatory policies for the microgrid, etc.
+For providing security and safety, it is crucial that transactions are non-malleable, that is, once a transaction has been recorded, it cannot be modified or removed from the ledger.
+However, for the sake of fault tolerance, the ledger also needs to be distributed.
+Since a distributed ledger is maintained by multiple nodes, a key implementation requirement is reaching consensus on which transactions are valid and stored in the ledger.
+Further, this consensus must be reached quickly and reliably, even in the presence of faulty or malicious (e.g., compromised) ledger nodes.
+In this paper, we assume that a distributed ledger service is available, but do not make any assumption about the implementation, such as the particulars of the consensus algorithm.
+In practice, a distributed ledger can be implemented using, for example, \emph{blockchains} with proof-of-stake consensus or Practical Byzantine Fault Tolerance algorithm~\cite{castro1999practical}.
 
@@
 Although individual prosumers trade energy with each other, for the sake of scalability, we need a service that enables prosumers to find trade partners.
-By providing a storage service for buy and sell bids, we relieve prosumer nodes from communicating with all potential trade partners.
-In addition to receiving and storing bids from prosumers, the bid storage service can also find matches and notify prosumers of the opportunity to make an energy trade.
-Even though the bid storage appears to the nodes as one entity, for the sake of scalability and reliability, it can be implemented in a distributed manner, using multiple nodes.
+%A bid storage service receives energy buy and sell bids from prosumers, stores these 
+We assume that there is a bid storage service that enables prosumers to post and read energy \emph{bids} and \emph{asks}.\footnote{A \emph{bid} is an offer to buy at a certain price, while an \emph{ask} is an offer to sell at a certain price.}
+This service relieves prosumers from communicating with a large number of potential trade partners, since they only have to communicate with the service in order to discover trade partners.
+Moreover, in addition to simply storing bids and asks, the service may also find matches in the posted bids and asks, and it may notify the posting prosumers of the trade opportunity.
+Note that
+%Even though the bid storage appears to the nodes as one entity, 
+for the sake of scalability and reliability, this service can also be implemented in a distributed manner, using multiple nodes.
 
@@
 The microgrid controller is responsible for stabilizing load within the microgrid and controlling it based on the expected load in the rest of the grid.
-To this end, the controller first estimates the expected load in the microgrid based on buy and sell bids in the bid storage as well as on outstanding energy trades in the ledger.
+To this end, the controller first estimates the expected load in the microgrid based on the bids and asks in the bid storage as well as on outstanding energy trades in the ledger.
 By combining this estimate with the expected load in the remainder of the grid, the controller produces a control signal that specifies how much the microgrid load should be decreased or increased.

### 2017-06-05 papers/IoT2017/prelim.tex
no message

@@
 \subsubsection{Smart Meters}
-\TODO{measures energy production / consumption}
-\TODO{may record energy production / consumption on the ledger or directly report it to the DSO}
+To measure energy production and consumption, a smart meter must be deployed at each prosumer.
+Further, these smart meters must be tamper resistant to prevent prosumers from ``stealing electricity'' by tampering with their meters.
+Once a smart meter has measured the amount of energy produced and consumed by the prosumer, it can send this information to the DSO for billing purposes.
 
 \subsection{Requirements}
+Next, we discuss the security, safety, and privacy requirements that must be satisfied by a transactive energy system.
 
 \subsubsection{Security}
-Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.
-\TODO{ensure correct billing (i.e., prosumer cannot tamper with energy production / consumption or financial balances of any prosumer)}
-\TODO{ensure that prosumers cannot back out of trades unilaterally, or tamper with other prosumers trading or bids}
-\TODO{ensure that prosumers cannot change policies that are to be set by the DSO for the microgird}
-\TODO{impact of node compromise is limited, and can be mitigated (i.e., offending node may be removed)}
+Security requirements primarily ensure that every prosumer is billed correctly, but they also provide necessary prerequisite properties for safety.
+%Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.
+More specifically, we require that 
+\begin{compactitem}
+\item prosumers are billed correctly based on the energy prices set by the DSO, their energy trades, and their energy production and consumption measured by the smart meters (i.e., energy production and consumption measurements and financial balances cannot be tampered with),
+\item prosumers or outside attackers cannot change microgrid policies that are to be set by the DSO,
+\item prosumers cannot back out of trades unilaterally, and they cannot tamper with other prosumers' trading and bidding,
+\item financial and physical impact of a compromised or faulty node is limited, and the node can be banned by the DSO.
+\end{compactitem}
 
@@
 A careless or malicious prosumer may destabilize the grid by promising to produce (or consume) a large amount of energy, but failing to deliver.
-\TODO{this could destabilize the microgrid, or even the main grid}
-Trades which are unlikely to be delivered and would result in a gap between actual production and demand should be prevented.
-\TODO{net amount of energy sold (or bought) by a prosumer is limited (by a constant set by the DSO), where net amount of energy sold is the difference between the amount of energy sold and bought (net amount of energy bought is defined analogously)}
-\TODO{energy bids posted by the prosumer are limited in the same way}
+A significant difference between promised and delivered energy production (or consumption) can result in a large gap between actual production and consumption in the microgrid, which threatens the stability of not only the microgrid but also the main power grid.
+Consequently, prosumers should not be able to trade large amounts of energy, which they are unlikely to deliver.
+%Trades which are unlikely to be delivered and would result in a gap between actual production and demand should be prevented.
+Specifically, we require that
+\begin{compactitem}
+\item net amount of energy sold (or bought) by a prosumer is upper bounded (by an amount set by the DSO), where the net amount of energy sold is the difference between the amount of energy sold and bought by the prosumer, and the net amount of energy bought is defined analogously,
+\item energy bids and asks posted by the prosumer are limited in a similar way.
+\end{compactitem}
 
 \subsubsection{Privacy} 
-Energy trading should not compromise the privacy of prosumers.
-More specifically, prosumers' private information, including energy consumption and production values, are available only to the DSO.
-\TODO{other prosumers should not be able to tell how much energy was consumed / produced by a prosumer, or what bids the prosumer has posted (or with whom the prosumer traded}
+Privacy requirements ensure that the prosumers' privacy is not compromised when they participate in energy trading.
+We use non-transactive smart metering as a baseline, and require that the transactive system does not leak any additional information compared to the baseline.
+More specifically, we require that
+\begin{compactitem}
+\item only the corresponding smart meter and the DSO may gain information regarding the amount of energy produced, consumed, bought, or sold by a prosumer,\footnote{Note that this requirement is impossible to satisfy if all other prosumers may collude against one target.
+However, we can assume that the majority of prosumers are non-colluding.}
+\item only the prosumer may know which bids and asks it has posted, and no one can know who traded energy with whom.
+\end{compactitem}

### 2017-06-05 papers/IoT2017/solution.tex
no message

@@
 
-In section, we describe our solution for providing privacy for prosumers without compromising the safety and security of the microgrid.
+In this section, we describe our solution for providing privacy for prosumers without compromising the safety and security of the microgrid.
 Figure~\ref{fig:softwareArchitecture} shows a high-level overview of the architecture of our solution.
@@
 
-\draw [nodeStyle, fill=blue!10] (0,    4) rectangle (0.49, 4.9) node [midway, align=center] {Prosumer trading\\algorithm};
-\draw [nodeStyle, fill=blue!10] (0.51, 4) rectangle (1,    4.9) node [midway, align=center] {DSO control\\algorithm};
+\draw [nodeStyle, fill=red!10] (0,    4) rectangle (0.49, 4.9) node [midway, align=center] {Prosumer anonymous\\trading algorithm};
+\draw [nodeStyle, fill=blue!10] (0.51, 4) rectangle (1,    4.9) node [midway, align=center] {Microgrid\\controller};
 \end{tikzpicture}
@@
 %\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
-%\draw[transfer, dashed] (prosumer2) -- node [asset, above] {energy production asset,\\sell bid} (bidstorage);
-%\draw[transfer, dashed] (bidstorage) -- node [asset, right] {sell\\bid} (partner);
+%\draw[transfer, dashed] (prosumer2) -- node [asset, above] {energy production asset,\\energy bid} (bidstorage);
+%\draw[transfer, dashed] (bidstorage) -- node [asset, right] {energy\\bid} (partner);
 %\draw[transfer, bend right=15] (partner) to node [asset, below] {financial asset,\\energy\\consumption asset} (prosumer3);
@@
 \draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
-\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {energy production asset,\\sell bid} (bidstorage);
-\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {sell\\bid} (partner);
+\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {energy production asset,\\energy bid} (bidstorage);
+\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\bid} (partner);
 \draw[transfer, bend right=30] (partner) to node [asset, below] {financial asset,\\energy consumption asset} (prosumer3);
@@
 \end{tikzpicture}
-\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy production.
-Note that in order to prevent de-anonymization, a prosumer should use multiple addresses for mixing and multiple rounds of mixing.}
+\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy.
+Note that in order to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing.}
+\
 \end{figure*}
+
+\subsection{Overview}
+We
 

### 2017-06-05 papers/IoT2017/solution.tex
no message

@@
 Note that in order to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing.}
-\
+\label{fig:sellFlow}
 \end{figure*}
@@
 \subsection{Overview}
-We
+We begin with a semi-formal description of the energy trading process from the prosumers' perspective.
+In subsequent subsections, we will describe the assets, transactions, and services in our system in more detail.
+
+First, consider a prosumer who would like to sell energy to another prosumer (this case is illustrated in Figure~\ref{fig:sellFlow}).
+As its very first step, the prosumer obtains an \emph{energy production asset} from its smart meter.
+An energy production asset represents a permission to sell a certain amount of energy, and it is used to enforce safety requirements.
+If the prosumer has sufficient unsold production capacity, the smart meter creates and transfers a production asset to the prosumer using a \emph{smart meter transaction}, which is recorded on the distributed ledger.
+
+At this point, the production asset can still be traced back to the prosumer since the ledger is public.
+To achieve anonymity, the prosumer transfers the production asset to a \emph{mixing service} using an \emph{energy and financial transaction}, which is also recorded on the distributed ledger.
+In turn, the mixing service transfers the production asset to an \emph{anonymous address}\todo{We should probably insert a good definition here for reader who are unfamiliar with blockchain transactions.}, which is randomly generated and controlled by the prosumer.
+Since the mixing service transfers assets from multiple prosumers to multiple anonymous addresses at the same time, and the anonymous addresses were chosen at random by the prosumers, the assets cannot be traced back to the original prosumers after mixing.\footnote{Note that prosumers should divide their assets between multiple anonymous addresses; otherwise, each asset might be traced back to its prosumer based on the amount of energy that it contains.}
+
+Now, the prosumer can engage in energy trading anonymously.
+To find a trade partner, it can either post an \emph{energy bid} on the bid storage, or simply search the storage for an acceptable \emph{energy ask}.
+To post an energy bid, the prosumer first proves to the storage service -- without revealing its original identity -- that it owns a production asset stored at an anonymous address.
+It can then post the energy bid, which contains an anonymous communication address\footnote{We discuss communication anonymity later.}, a price, and a reference to the production asset.
+If another prosumer, who would like to buy energy, finds the bid acceptable, it can contact the selling prosumer at the communication address given by the bid.
 

### 2017-06-05 papers/IoT2017/paper.tex
no message

@@
 % option again before submitting your final document.
-\usepackage[textsize=small]{todonotes}
+\usepackage[textsize=tiny, textwidth=1.3cm]{todonotes}
 \newcommand{\TODO}[1]{\todo[inline]{#1}}
+
+\newcommand{\circled}[1]{\tikz[baseline=(char.base)]{\node[shape=circle, draw, inner sep=0.5pt, solid] (char) {#1};}}
 
@@
 \def\emptyauthor{}
-\def\plainkeywords{Internet of Things; blockchain; transactive energy; privacy; security; transactive microgrid.}
+\def\plainkeywords{Internet of Things; blockchain; transactive energy; privacy; security; transactive microgrid; smart grid; anonymity.}
 \def\plaingeneralterms{Design, Human Factors, Reliability, Security} % TODO: revise
@@
 \author{%
-  \alignauthor{Leave Authors Anonymous\\
-    \affaddr{for Submission}\\
-    \affaddr{City, Country}\\
-    \email{e-mail address}}\\
-  \alignauthor{Leave Authors Anonymous\\
-    \affaddr{for Submission}\\
-    \affaddr{City, Country}\\
-    \email{e-mail address}}\\
-  \alignauthor{Leave Authors Anonymous\\
-    \affaddr{for Submission}\\
-    \affaddr{City, Country}\\
-    \email{e-mail address}}\\
+%  \alignauthor{Leave Authors Anonymous\\
+%    \affaddr{for Submission}\\
+%    \affaddr{City, Country}\\
+%    \email{e-mail address}}\\
+%  \alignauthor{Leave Authors Anonymous\\
+%    \affaddr{for Submission}\\
+%    \affaddr{City, Country}\\
+%    \email{e-mail address}}\\
+%  \alignauthor{Leave Authors Anonymous\\
+%    \affaddr{for Submission}\\
+%    \affaddr{City, Country}\\
+%    \email{e-mail address}}\\
 }

### 2017-06-05 papers/IoT2017/solution.tex
no message

@@
 
-\draw [nodeStyle, fill=red!10] (0,    4) rectangle (0.49, 4.9) node [midway, align=center] {Prosumer anonymous\\trading algorithm};
+\draw [nodeStyle, fill=red!10] (0,    4) rectangle (0.49, 4.9) node [midway, align=center] {Prosumer anonymous\\trading process};
 \draw [nodeStyle, fill=blue!10] (0.51, 4) rectangle (1,    4.9) node [midway, align=center] {Microgrid\\controller};
@@
 
-\draw[transfer] (smartmeter) -- node [asset, above] {energy\\production asset} (prosumer1);
-\draw[transfer] (prosumer1) -- node [asset, above] {energy\\production asset} (mixing1);
-\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
-\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {energy production asset,\\energy bid} (bidstorage);
+\draw[transfer] (smartmeter) -- node [asset, above] {\circled{1} energy\\production asset} (prosumer1);
+\draw[transfer] (prosumer1) -- node [asset, above] {\circled{2} energy\\production asset} (mixing1);
+\draw[transfer] (mixing1) -- node [asset, above] {\circled{3} energy\\production asset} (prosumer2);
+\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {\circled{4} energy production asset,\\energy bid} (bidstorage);
 \draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\bid} (partner);
-\draw[transfer, bend right=30] (partner) to node [asset, below] {financial asset,\\energy consumption asset} (prosumer3);
-\draw[transfer, bend right=50] (prosumer2) to node [asset, right] {energy\\production asset} (partner);
-\draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
+\draw[transfer, bend right=30] (partner) to node [asset, below] {\circled{5} financial asset,\\energy consumption asset} (prosumer3);
+\draw[transfer, bend right=50] (prosumer2) to node [asset, right] {\circled{5} energy\\production asset} (partner);
+\draw[transfer] (prosumer3) -- node [asset, below] {\circled{6} financial asset,\\
 energy consumption asset} (smartmeter2);
@@
 An energy production asset represents a permission to sell a certain amount of energy, and it is used to enforce safety requirements.
-If the prosumer has sufficient unsold production capacity, the smart meter creates and transfers a production asset to the prosumer using a \emph{smart meter transaction}, which is recorded on the distributed ledger.
+If the prosumer has sufficient unsold production capacity, the smart meter creates and transfers a production asset to the prosumer using a \emph{smart meter transaction} \circled{1}, which is recorded on the distributed ledger.
 
 At this point, the production asset can still be traced back to the prosumer since the ledger is public.
-To achieve anonymity, the prosumer transfers the production asset to a \emph{mixing service} using an \emph{energy and financial transaction}, which is also recorded on the distributed ledger.
-In turn, the mixing service transfers the production asset to an \emph{anonymous address}\todo{We should probably insert a good definition here for reader who are unfamiliar with blockchain transactions.}, which is randomly generated and controlled by the prosumer.
+To achieve anonymity, the prosumer transfers the production asset to a \emph{mixing service} using an \emph{energy and financial transaction} \circled{2}, which is also recorded on the distributed ledger.
+In turn, the mixing service transfers the production asset to an \emph{anonymous address} \circled{3}\todo{We should probably insert a good definition here for reader who are unfamiliar with blockchain transactions.}, which is randomly generated and controlled by the prosumer.
 Since the mixing service transfers assets from multiple prosumers to multiple anonymous addresses at the same time, and the anonymous addresses were chosen at random by the prosumers, the assets cannot be traced back to the original prosumers after mixing.\footnote{Note that prosumers should divide their assets between multiple anonymous addresses; otherwise, each asset might be traced back to its prosumer based on the amount of energy that it contains.}
@@
 To post an energy bid, the prosumer first proves to the storage service -- without revealing its original identity -- that it owns a production asset stored at an anonymous address.
-It can then post the energy bid, which contains an anonymous communication address\footnote{We discuss communication anonymity later.}, a price, and a reference to the production asset.
+It can then post the energy bid \circled{4}, which contains an anonymous communication address\footnote{We discuss communication anonymity later.}, a price, and a reference to the production asset.
 If another prosumer, who would like to buy energy, finds the bid acceptable, it can contact the selling prosumer at the communication address given by the bid.
+
+The seller and buyer can execute the trade by creating an energy and financial transaction together \circled{5}, and recording it on the ledger.
+This transaction transfers the production asset from the seller to the buyer, and a \emph{financial asset} and an \emph{energy consumption asset} from the buyer to the seller.
+A financial asset represents a certain amount of money, while a consumption asset represents a permission to buy a certain amount of energy, which is used to enforce safety requirements similarly to production assets.
+
+Finally, the selling prosumer deposits the financial and consumption assets to its smart meter using an energy and financial transaction.
+To ensure that the prosumer remains anonymous, it transfers the assets to an anonymous address that is randomly generated and controlled by the smart meter \circled{6}.
+Once the smart meter has received the assets, it credits the financial amount to and deducts the energy amount from the prosumer, for billing purposes.
+Note that in order to enforce safety requirements, the prosumer must always deposit the same amount of consumption assets as the amount of production assets obtained at the beginning; otherwise, unaccounted consumption assets might be used to trade excessive amounts.
+
+Second, consider a prosumer who would like to buy energy from another prosumer.
+Since the trading process is very similar to the case of the selling prosumer, we will discuss only the differences.
+In the first step, the prosumer tries to obtain a financial asset and an energy consumption asset from its smart meter.
+If the prosumer has the consumption capacity and good financial standing, the smart meter transfers the assets to the prosumer and adds the financial amount to the prosumer's bill.
+After transferring the assets through a mixing service, the prosumer is ready to post an energy ask on the bid service.
+To do so, it first proves the ownership of both the financial asset and the consumption asset to the service, and then posts the energy ask, which includes an anonymous communication address.
+If a partner is found, the trade is executed as described before, the prosumer playing the role of the buyer.
+Finally, the prosumer deposits the purchased energy production asset to the anonymous address of its smart meter,
+which credits the energy amount to the prosumer, for billing purposes.
+Note that if the prosumer has not used up the financial asset completely, then the remainder may also be deposited back to the smart meter.
 

### 2017-06-05 papers/IoT2017/solution.tex
restructuring

@@
-\section{Solution}
+\section{Proposed System}
 
@@
 
-\subsection{Overview}
+\subsection{Overview of the Trading Process}
 We begin with a semi-formal description of the energy trading process from the prosumers' perspective.
@@
 
-\subsection{Services}
+\input{transactions.tex}
 
-Here, we describe three services that must be implemented for our solution: communication anonymity, mixing service for transaction anonymity, and anonymous bid storage for bidding anonymity.
-
-\subsubsection{Communication Anonymity}
-Firstly, we must provide an anonymous communication layer, on which we can build an anonymous trading platform.
-Without this communication layer, bids and transactions could be easily de-anonymized based on the network identifiers of the sources (e.g., IP or MAC addresses).
-
-We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}.
-To build an onion network, the smart meters, inverters, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on a private blockchain.
-In our first implementation, we can use the free and open-source Tor software with private Directory Authorities.
-% ritter.vg: "run your own tor network"
-% https://ritter.vg/blog-run_your_own_tor_network.html
-
-\subsubsection{Transaction Anonymity}
-We must provide prosumers with the ability to create and publish transactions anonymously.
-More specifically, prosumers should be able to purchase or sell energy without revealing their identity; however, these transaction must also be verifiable and enforceable.
-
-We may achieve this goal using multiple approaches for blockchain transaction anonymity:
-\begin{itemize}
-\item Mixing services (also known as tumblers) mix potentially identifiable assets on a blockchain with others, thereby preventing tracing individual assets back to their original source. 
-In our case, assets to be mixed include virtual balances of fiat currencies as well as energy production and consumption.
-\item Cryptographic anonymity for transactions is provided, for example, by Zerocoin~\cite{miers2013zerocoin}. Similarly to mixing service, Zerocoin can prevent tracing assets on a blockchain.
-\end{itemize}
-Using the above techniques, we can enable prosumers to trade energy anonymously (i.e., without revealing their true identities), but at the same time prevent them from altering their energy or financial balances without a valid transaction.
-
-However, we must also ensure that 1) smart meters know the amount of energy purchased or sold by their prosumer and 2) prosumers cannot purchase or sell more energy than their capacity.
-To satisfy both of these constraints, all energy trades must start with the prosumer withdrawing a certain amount of energy production or consumption from its smart meter:
-\begin{itemize}
-\item If a prosumer wishes to sell energy, it must first obtain an energy asset from its smart meter using a blockchain transaction.
-This transaction must be signed by the smart meter, which enables the smart meter to 1) keep track of the amount of energy traded by the prosumer as well as to 2) enforce safety requirements by limiting the amount of energy that can be withdrawn.
-\item If a prosumer wishes to buy energy, it must first obtain an energy consumption asset from its smart meter in a way similar to obtaining an energy production asset.
-\end{itemize}
-
-\subsubsection{Bidding Anonymity}
-Finally, we must provide prosumers with the ability to publish energy buy and sell bids anonymously.
-To this end, we create a storage for anonymous bids that is readable by all the prosumers in the microgrid.
-Any prosumer may submit a bid to this storage; however, in order to do so, they must provide a zero-knowledge proof of owning the assets that are to be traded:
-\begin{itemize}
-\item To submit an energy sell bid, the prosumer must prove that it owns an energy production asset on the chain.
-\item To submit an energy buy bid, the prosumer must prove that it own an energy consumption asset as well as financial assets on the chain.
-\end{itemize}
-
-\subsection{Transaction Types}
-
-Before we can discuss transaction types, we must first define the three assets that these transactions may transfer.
-
-An \emph{energy production asset} (EPA) is defined by
-\begin{compactitem}
-\item \field{power}: non-negative amount of power to produced (for example, measured in watts).
-\item \field{start}: first time interval in which energy is to be produced. 
-\item \field{end}: last time interval in which energy is to be produced.
-\end{compactitem}
-An \emph{energy consumption asset} (ECA) is defined by the same fields; however, for this asset, the fields define consumption instead of production.
-Finally, a \emph{financial asset} (FA) is defined by a single non-negative field \field{amount}, which can be denominated in either a fiat currency (e.g., US dollars) or a cryptocurrency.
-
-\subsubsection{Energy and Financial Transactions}
-
-Energy and financial transactions transfer energy and financial asset from one address to another.
-Prosumers use these transactions for multiple purposes: to trade energy by exchanging assets with other prosumers, to prove to the bid storage that they have production or consumption capacity, to hide their identity by transferring assets to and from mixing services, and to deposit assets at their smart meter.
-%
-An energy and financial transaction contains the following fields:
-\begin{compactitem}
-\item List of EPA inputs, each of which is defined by:
-\begin{compactitem}
-\item \field{out}: EPA output from a previous transaction,
-\item \field{sig}: signature for this output.
-\end{compactitem}
-\item List of ECA inputs, each of which is defined by:
-\begin{compactitem}
-\item \field{out}: ECA output from a previous transaction,
-\item \field{sig}: signature for this output.
-\end{compactitem}
-\item List of FA inputs, each of which is defined by:
-\begin{compactitem}
-\item \field{out}: FA output from a previous transaction,
-\item \field{sig}: signature for this output.
-\end{compactitem}
-\item List of EPA outputs, each of which is defined by:
-\begin{compactitem}
-\item an EPA and an address to which it is transferred.
-\end{compactitem}
-\item List of ECA outputs, each of which is defined by:
-\begin{compactitem}
-\item an ECA and an address to which it is transferred.
-\end{compactitem}
-\item List of FA outputs, each of which is defined by:
-\begin{compactitem}
-\item an FA and an address to which it is transferred.
-\end{compactitem}
-\end{compactitem}
-
-An energy and financial transaction is valid if the following three conditions hold.
-\begin{compactitem}
-\item None of the outputs referenced by the inputs have been spent by a transaction that has been recorded on the ledger.
-\item All of the signatures are valid.
-\item For each asset type (and for each timestep), the sum of inputs and outputs is the same.
-For example, in the case of energy production assets, the condition is:
-\begin{align}
-\forall t: & \sum_{out \in \text{EPA outputs}} out.\mathtt{power} \cdot 1_{\left\{out.\mathtt{start} \leq t \leq out.\mathtt{end}\right\}} \nonumber \\
-& = \sum_{in \in \text{EPA inputs}} in.\mathtt{out}.\mathtt{power} \cdot 1_{\left\{in.\mathtt{out}.\mathtt{start} \leq t \leq in.\mathtt{out}.\mathtt{end}\right\}} ,
-\end{align}
-where $1_x$ is equal to $1$ if $x$ is true, and it is $0$ otherwise.
-%\begin{equation}
-%\forall t: \sum_{out \in \left\{out' \middle| out' \in \text{ EPA outputs} \wedge out'.EPA.start \leq t \leq out'.EPA.end\right\}} out.EPA.Power = \sum_{in \in \left\{in' \middle| in' \in \text{ EPA inputs} \wedge in'.EPA.start \leq t \leq in'.EPA.end\right\}} in.EPA.Power .
-%\end{equation}
-\end{compactitem}
-If a transaction submitted to the ledger is valid, it will be permanently recorded.
-
-\subsubsection{Smart-Meter Transactions}
-
-Prosumers use smart-meter transactions to withdraw energy and financial assets from their own smart meters, before they engage in energy trading.
-%
-A smart-meter transaction contains the following fields:
-\begin{compactitem}
-\item List of EPA outputs, each of which is defined by:
-\begin{compactitem}
-\item an EPA and an address to which it is transferred.
-\end{compactitem}
-\item List of ECA outputs, each of which is defined by:
-\begin{compactitem}
-\item an ECA and an address to which it is transferred.
-\end{compactitem}
-\item List of FA outputs, each of which is defined by:
-\begin{compactitem}
-\item an FA and an address to which it is transferred.
-\end{compactitem}
-\item \field{id}: Identifier of the smart meter.
-\item \field{sig}: Smart meter's signature over the transaction.
-\end{compactitem}
-
-A smart-meter transaction is valid if the following two conditions hold:
-\begin{compactitem}
-\item The smart meter identified in the transaction has been authorized by a regulatory transaction that has been recorded on the ledger.
-\item The smart meter's signature is valid.
-\end{compactitem}
-\todo{To address malfunctioning or compromised smart meters, we could also impose a limit on withdrawals.}
-
-\subsubsection{Regulatory Transactions}
-
-The DSO uses regulatory transactions to authorize or ban smart meters and to control the microgrid load through setting a price policy.
-Since these transactions provide a diverse set of functionality, they are divided into two types.
-
-\paragraph{Authorize or Ban Smart Meters}
-The DSO uses these transactions to manage the set of authorized smart meters in the microgrid.
-Whenever a new smart meter is installed, the DSO notifies the members of the microgrid using a regulatory transaction.
-Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or it is believed to be malfunctioning or compromised), the DSO notifies the members of the microgrid using a regulatory transaction.
-These transactions contain the following fields:
-\begin{compactitem}
-\item List of smart meters to be authorized, each of which is defined by:
-\begin{compactitem}
-\item \field{id}: Identifier of the smart meter.
-\item \field{pubkey}: Public key of the smart meter.
-\end{compactitem}
-\item List of smart meters to be banned, each of which is given using its identifier.
-\item \field{time}: Timestep in which smart meters are authorized and banned.
-\item \field{sig}: DSO's signature over the transaction.
-\end{compactitem}
-
-A regulatory transaction of this type is valid if the following two conditions hold:
-\begin{compactitem}
-\item The timestep specified in the transaction is in the future.
-\item The DSO's signature is valid.
-\end{compactitem}
-
-\paragraph{Price Policy}
+\input{services.tex}

### 2017-06-05 papers/IoT2017/transactions.tex
restructuring

\subsection{Transaction Types}

Before we can discuss transaction types, we must first define the three assets that these transactions may transfer.

An \emph{energy production asset} (EPA) is defined by
\begin{compactitem}
\item \field{power}: non-negative amount of power to produced (for example, measured in watts).
\item \field{start}: first time interval in which energy is to be produced. 
\item \field{end}: last time interval in which energy is to be produced.
\end{compactitem}
An \emph{energy consumption asset} (ECA) is defined by the same fields; however, for this asset, the fields define consumption instead of production.
Finally, a \emph{financial asset} (FA) is defined by a single non-negative field \field{amount}, which can be denominated in either a fiat currency (e.g., US dollars) or a cryptocurrency.

\subsubsection{Energy and Financial Transactions}

Energy and financial transactions transfer energy and financial asset from one address to another.
Prosumers use these transactions for multiple purposes: to trade energy by exchanging assets with other prosumers, to prove to the bid storage that they have production or consumption capacity, to hide their identity by transferring assets to and from mixing services, and to deposit assets at their smart meter.
%
An energy and financial transaction contains the following fields:
\begin{compactitem}
\item List of EPA inputs, each of which is defined by:
\begin{compactitem}
\item \field{out}: EPA output from a previous transaction,
\item \field{sig}: signature for this output.
\end{compactitem}
\item List of ECA inputs, each of which is defined by:
\begin{compactitem}
\item \field{out}: ECA output from a previous transaction,
\item \field{sig}: signature for this output.
\end{compactitem}
\item List of FA inputs, each of which is defined by:
\begin{compactitem}
\item \field{out}: FA output from a previous transaction,
\item \field{sig}: signature for this output.
\end{compactitem}
\item List of EPA outputs, each of which is defined by:
\begin{compactitem}
\item an EPA and an address to which it is transferred.
\end{compactitem}
\item List of ECA outputs, each of which is defined by:
\begin{compactitem}
\item an ECA and an address to which it is transferred.
\end{compactitem}
\item List of FA outputs, each of which is defined by:
\begin{compactitem}
\item an FA and an address to which it is transferred.
\end{compactitem}
\end{compactitem}

An energy and financial transaction is valid if the following three conditions hold.
\begin{compactitem}
\item None of the outputs referenced by the inputs have been spent by a transaction that has been recorded on the ledger.
\item All of the signatures are valid.
\item For each asset type (and for each timestep), the sum of inputs and outputs is the same.
For example, in the case of energy production assets, the condition is:
\begin{align}
\forall t: & \sum_{out \in \text{EPA outputs}} out.\mathtt{power} \cdot 1_{\left\{out.\mathtt{start} \leq t \leq out.\mathtt{end}\right\}} \nonumber \\
& = \sum_{in \in \text{EPA inputs}} in.\mathtt{out}.\mathtt{power} \cdot 1_{\left\{in.\mathtt{out}.\mathtt{start} \leq t \leq in.\mathtt{out}.\mathtt{end}\right\}} ,
\end{align}
where $1_x$ is equal to $1$ if $x$ is true, and it is $0$ otherwise.
%\begin{equation}
%\forall t: \sum_{out \in \left\{out' \middle| out' \in \text{ EPA outputs} \wedge out'.EPA.start \leq t \leq out'.EPA.end\right\}} out.EPA.Power = \sum_{in \in \left\{in' \middle| in' \in \text{ EPA inputs} \wedge in'.EPA.start \leq t \leq in'.EPA.end\right\}} in.EPA.Power .
%\end{equation}
\end{compactitem}
If a transaction submitted to the ledger is valid, it will be permanently recorded.

\subsubsection{Smart-Meter Transactions}

Prosumers use smart-meter transactions to withdraw energy and financial assets from their own smart meters, before they engage in energy trading.
%
A smart-meter transaction contains the following fields:
\begin{compactitem}
\item List of EPA outputs, each of which is defined by:
\begin{compactitem}
\item an EPA and an address to which it is transferred.
\end{compactitem}
\item List of ECA outputs, each of which is defined by:
\begin{compactitem}
\item an ECA and an address to which it is transferred.
\end{compactitem}
\item List of FA outputs, each of which is defined by:
\begin{compactitem}
\item an FA and an address to which it is transferred.
\end{compactitem}
\item \field{id}: Identifier of the smart meter.
\item \field{sig}: Smart meter's signature over the transaction.
\end{compactitem}

A smart-meter transaction is valid if the following two conditions hold:
\begin{compactitem}
\item The smart meter identified in the transaction has been authorized by a regulatory transaction that has been recorded on the ledger.
\item The smart meter's signature is valid.
\end{compactitem}
\todo{To address malfunctioning or compromised smart meters, we could also impose a limit on withdrawals.}

\subsubsection{Regulatory Transactions}

The DSO uses regulatory transactions to authorize or ban smart meters and to control the microgrid load through setting a price policy.
Since these transactions provide a diverse set of functionality, they are divided into two types.

\paragraph{Authorize or Ban Smart Meters}
The DSO uses these transactions to manage the set of authorized smart meters in the microgrid.
Whenever a new smart meter is installed, the DSO notifies the members of the microgrid using a regulatory transaction.
Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or it is believed to be malfunctioning or compromised), the DSO notifies the members of the microgrid using a regulatory transaction.
These transactions contain the following fields:
\begin{compactitem}
\item List of smart meters to be authorized, each of which is defined by:
\begin{compactitem}
\item \field{id}: Identifier of the smart meter.
\item \field{pubkey}: Public key of the smart meter.
\end{compactitem}
\item List of smart meters to be banned, each of which is given using its identifier.
\item \field{time}: Timestep in which smart meters are authorized and banned.
\item \field{sig}: DSO's signature over the transaction.
\end{compactitem}

A regulatory transaction of this type is valid if the following two conditions hold:
\begin{compactitem}
\item The timestep specified in the transaction is in the future.
\item The DSO's signature is valid.
\end{compactitem}

\paragraph{Price Policy}

### 2017-06-05 papers/IoT2017/solution.tex
no message

@@
 To achieve anonymity, the prosumer transfers the production asset to a \emph{mixing service} using an \emph{energy and financial transaction} \circled{2}, which is also recorded on the distributed ledger.
-In turn, the mixing service transfers the production asset to an \emph{anonymous address} \circled{3}\todo{We should probably insert a good definition here for reader who are unfamiliar with blockchain transactions.}, which is randomly generated and controlled by the prosumer.
+In turn, the mixing service transfers the production asset to an \emph{anonymous address} \circled{3}\todo{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}, which is randomly generated and controlled by the prosumer.
 Since the mixing service transfers assets from multiple prosumers to multiple anonymous addresses at the same time, and the anonymous addresses were chosen at random by the prosumers, the assets cannot be traced back to the original prosumers after mixing.\footnote{Note that prosumers should divide their assets between multiple anonymous addresses; otherwise, each asset might be traced back to its prosumer based on the amount of energy that it contains.}
@@
 
-\subsection{Timing}
-The ability to specify points or intervals in time is crucial.
-For example, control signals specify how the load should change at certain points in time, energy trades specify when energy will be consumed or produced, etc.
-To facilitate processing signals and transactions, we divide time into fixed-length intervals, and specify points or periods in time using these discrete timesteps.
-The length of the time interval is determined by mapping the timing assumptions of the power system to our platform.
-%In our implementation, 
-For example, the default length of the time interval may be 4 seconds, which corresponds to how frequently the control signal of the DSO typically changes.
-
 \input{transactions.tex}

### 2017-06-05 papers/IoT2017/transactions.tex
no message

@@
-\subsection{Transaction Types}
+\subsection{Transactions}
+
+\subsection{Timing}
+
+The ability to specify points or intervals in time is crucial.
+For example, control signals specify how the load should change at certain points in time, energy trades specify when energy will be consumed or produced, etc.
+To facilitate processing signals and transactions, we divide time into fixed-length intervals, and specify points or periods in time using these discrete timesteps.
+The length of the time interval is determined by mapping the timing assumptions of the power system to our platform.
+%In our implementation, 
+For example, the default length of the time interval may be 4 seconds, which corresponds to how frequently the control signal of the DSO typically changes.
+
+\subsubsection{Assets}
 
@@
 
+\TODO{For brevity, combine regulatory transactions into one type.}
+
 \paragraph{Authorize or Ban Smart Meters}

### 2017-06-05 papers/IoT2017/services.tex

\subsection{Services}

Here, we describe three services that must be implemented for our solution: communication anonymity, mixing service for transaction anonymity, and anonymous bid storage for bidding anonymity.

\subsubsection{Communication Anonymity}
Firstly, we must provide an anonymous communication layer, on which we can build an anonymous trading platform.
Without this communication layer, bids and transactions could be easily de-anonymized based on the network identifiers of the sources (e.g., IP or MAC addresses).

We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}.
To build an onion network, the smart meters, inverters, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on a private blockchain.
In our first implementation, we can use the free and open-source Tor software with private Directory Authorities.
% ritter.vg: "run your own tor network"
% https://ritter.vg/blog-run_your_own_tor_network.html

\subsubsection{Transaction Anonymity}
We must provide prosumers with the ability to create and publish transactions anonymously.
More specifically, prosumers should be able to purchase or sell energy without revealing their identity; however, these transaction must also be verifiable and enforceable.

We may achieve this goal using multiple approaches for blockchain transaction anonymity:
\begin{itemize}
\item Mixing services (also known as tumblers) mix potentially identifiable assets on a blockchain with others, thereby preventing tracing individual assets back to their original source. 
In our case, assets to be mixed include virtual balances of fiat currencies as well as energy production and consumption.
\item Cryptographic anonymity for transactions is provided, for example, by Zerocoin~\cite{miers2013zerocoin}. Similarly to mixing service, Zerocoin can prevent tracing assets on a blockchain.
\end{itemize}
Using the above techniques, we can enable prosumers to trade energy anonymously (i.e., without revealing their true identities), but at the same time prevent them from altering their energy or financial balances without a valid transaction.

However, we must also ensure that 1) smart meters know the amount of energy purchased or sold by their prosumer and 2) prosumers cannot purchase or sell more energy than their capacity.
To satisfy both of these constraints, all energy trades must start with the prosumer withdrawing a certain amount of energy production or consumption from its smart meter:
\begin{itemize}
\item If a prosumer wishes to sell energy, it must first obtain an energy asset from its smart meter using a blockchain transaction.
This transaction must be signed by the smart meter, which enables the smart meter to 1) keep track of the amount of energy traded by the prosumer as well as to 2) enforce safety requirements by limiting the amount of energy that can be withdrawn.
\item If a prosumer wishes to buy energy, it must first obtain an energy consumption asset from its smart meter in a way similar to obtaining an energy production asset.
\end{itemize}

\subsubsection{Bidding Anonymity}
Finally, we must provide prosumers with the ability to publish energy buy and sell bids anonymously.
To this end, we create a storage for anonymous bids that is readable by all the prosumers in the microgrid.
Any prosumer may submit a bid to this storage; however, in order to do so, they must provide a zero-knowledge proof of owning the assets that are to be traded:
\begin{itemize}
\item To submit an energy sell bid, the prosumer must prove that it owns an energy production asset on the chain.
\item To submit an energy buy bid, the prosumer must prove that it own an energy consumption asset as well as financial assets on the chain.
\end{itemize}

### 2017-06-05 papers/IoT2017/services.tex
no message

@@
 \begin{itemize}
-\item If a prosumer wishes to sell energy, it must first obtain an energy asset from its smart meter using a blockchain transaction.
+\item If a prosumer wishes to sell energy, it must first withdraw an energy asset from its smart meter using a blockchain transaction.
 This transaction must be signed by the smart meter, which enables the smart meter to 1) keep track of the amount of energy traded by the prosumer as well as to 2) enforce safety requirements by limiting the amount of energy that can be withdrawn.
-\item If a prosumer wishes to buy energy, it must first obtain an energy consumption asset from its smart meter in a way similar to obtaining an energy production asset.
+\item If a prosumer wishes to buy energy, it must first withdraw an energy consumption asset from its smart meter in a way similar to withdrawing an energy production asset.
 \end{itemize}

### 2017-06-05 papers/IoT2017/solution.tex
no message

@@
 
-First, consider a prosumer who would like to sell energy to another prosumer (this case is illustrated in Figure~\ref{fig:sellFlow}).
-As its very first step, the prosumer obtains an \emph{energy production asset} from its smart meter.
+First, consider a prosumer who wishes sell energy to another prosumer (this case is illustrated in Figure~\ref{fig:sellFlow}).
+As its very first step, the prosumer withdraws an \emph{energy production asset} from its smart meter.
 An energy production asset represents a permission to sell a certain amount of energy, and it is used to enforce safety requirements.
@@
 Once the smart meter has received the assets, it credits the financial amount to and deducts the energy amount from the prosumer, for billing purposes.
-Note that in order to enforce safety requirements, the prosumer must always deposit the same amount of consumption assets as the amount of production assets obtained at the beginning; otherwise, unaccounted consumption assets might be used to trade excessive amounts.
+Note that in order to enforce safety requirements, the prosumer must always deposit the same amount of consumption assets as the amount of production assets withdrawn at the beginning; otherwise, unaccounted consumption assets might be used to trade excessive amounts.
 
@@
 Since the trading process is very similar to the case of the selling prosumer, we will discuss only the differences.
-In the first step, the prosumer tries to obtain a financial asset and an energy consumption asset from its smart meter.
+In the first step, the prosumer tries to withdraw a financial asset and an energy consumption asset from its smart meter.
 If the prosumer has the consumption capacity and good financial standing, the smart meter transfers the assets to the prosumer and adds the financial amount to the prosumer's bill.

### 2017-06-05 papers/IoT2017/transactions.tex
no message

@@
 
-\subsection{Timing}
+In the previous subsection, we gave an overview of how transactions are used in the trading process to transfer various assets.
+Here, we detail the format of these transactions, and the rules that they have to satisfy to be valid and recorded on the ledger.
+We also introduce and detail the format of regulatory transactions, which the DSO uses to regulate the microgrid.
+
+\subsubsection{Timing}
 
 The ability to specify points or intervals in time is crucial.
-For example, control signals specify how the load should change at certain points in time, energy trades specify when energy will be consumed or produced, etc.
+For example, control signals specify how the microgrid load should change at certain points in time, energy trades specify when energy will be consumed or produced, etc.
 To facilitate processing signals and transactions, we divide time into fixed-length intervals, and specify points or periods in time using these discrete timesteps.
-The length of the time interval is determined by mapping the timing assumptions of the power system to our platform.
-%In our implementation, 
+The length of the time interval is determined based on the timing assumptions of the physical power system.
 For example, the default length of the time interval may be 4 seconds, which corresponds to how frequently the control signal of the DSO typically changes.
@@
 
-Before we can discuss transaction types, we must first define the three assets that these transactions may transfer.
-
-An \emph{energy production asset} (EPA) is defined by
+Before we can discuss transactions, we must define the format of three assets that these transactions may transfer.
+First, an \emph{energy production asset} (EPA) is defined by
 \begin{compactitem}
-\item \field{power}: non-negative amount of power to produced (for example, measured in watts).
-\item \field{start}: first time interval in which energy is to be produced. 
+\item \field{power}: non-negative amount of power to produced (for example, measured in watts),
+\item \field{start}: first time interval in which energy is to be produced,
 \item \field{end}: last time interval in which energy is to be produced.
 \end{compactitem}
-An \emph{energy consumption asset} (ECA) is defined by the same fields; however, for this asset, the fields define consumption instead of production.
-Finally, a \emph{financial asset} (FA) is defined by a single non-negative field \field{amount}, which can be denominated in either a fiat currency (e.g., US dollars) or a cryptocurrency.
+Second, an \emph{energy consumption asset} (ECA) is defined by the same fields; however, for this asset, the fields define energy consumption instead of production.
+Finally, a \emph{financial asset} (FA) is defined by a single non-negative number \field{amount}, which can be denominated in either a fiat currency (e.g., US dollars) or a cryptocurrency.
 
@@
 
-Energy and financial transactions transfer energy and financial asset from one address to another.
+Energy and financial transactions transfer energy and financial assets from one address to another.
 Prosumers use these transactions for multiple purposes: to trade energy by exchanging assets with other prosumers, to prove to the bid storage that they have production or consumption capacity, to hide their identity by transferring assets to and from mixing services, and to deposit assets at their smart meter.
@@
 \begin{compactitem}
-\item List of EPA inputs, each of which is defined by:
-\begin{compactitem}
-\item \field{out}: EPA output from a previous transaction,
-\item \field{sig}: signature for this output.
+\item \field{EPA\_in}: list of EPA inputs, each of which is defined by
+\begin{itemize}[leftmargin=0.5em,nosep]
+\item \field{out}: reference to an EPA output of a previous transaction,
+\item \field{sig}: signature for referenced output,
+\end{itemize}
+\item \field{ECA\_in}: list of ECA inputs, each of which is defined by
+\begin{itemize}[leftmargin=0.5em,nosep]
+\item \field{out}: reference to an ECA output of a previous transaction,
+\item \field{sig}: signature for referenced output,
+\end{itemize}
+\item \field{FA\_in}: list of FA inputs, each of which is defined by
+\begin{itemize}[leftmargin=0.5em,nosep]
+\item \field{out}: reference to an FA output of a previous transaction,
+\item \field{sig}: signature for referenced output,
+\end{itemize}
+\item \field{EPA\_out}: list of EPA outputs, each of which is defined by
+\begin{itemize}[leftmargin=0.5em,nosep]
+\item \field{EPA}: an energy production asset,
+\item \field{address}: address to which EPA is transferred,
+\end{itemize}
+\item \field{ECA\_out}: list of ECA outputs, each of which is defined by
+\begin{itemize}[leftmargin=0.5em,nosep]
+\item \field{EPA}: an energy consumption asset,
+\item \field{address}: address to which ECA is transferred,
+\end{itemize}
+\item \field{FA\_out}: list of FA outputs, each of which is defined by
+\begin{itemize}[leftmargin=0.5em,nosep]
+\item \field{EPA}: a financial asset,
+\item \field{address}: address to which FA is transferred,
+\end{itemize}
 \end{compactitem}
-\item List of ECA inputs, each of which is defined by:
-\begin{compactitem}
-\item \field{out}: ECA output from a previous transaction,
-\item \field{sig}: signature for this output.
-\end{compactitem}
-\item List of FA inputs, each of which is defined by:
-\begin{compactitem}
-\item \field{out}: FA output from a previous transaction,
-\item \field{sig}: signature for this output.
-\end{compactitem}
-\item List of EPA outputs, each of which is defined by:
-\begin{compactitem}
-\item an EPA and an address to which it is transferred.
-\end{compactitem}
-\item List of ECA outputs, each of which is defined by:
-\begin{compactitem}
-\item an ECA and an address to which it is transferred.
-\end{compactitem}
-\item List of FA outputs, each of which is defined by:
-\begin{compactitem}
-\item an FA and an address to which it is transferred.
-\end{compactitem}
-\end{compactitem}
+This transaction transfers the assets specified in the input lists to the addresses specified in the output lists. 
+Note that assets may be divided or combined, as the input and output lists may differ in length.
 
-An energy and financial transaction is valid if the following three conditions hold.
+An energy and financial transaction is valid (and can be recorded on the ledger) if the following three conditions hold.
 \begin{compactitem}
 \item None of the outputs referenced by the inputs have been spent by a transaction that has been recorded on the ledger.
-\item All of the signatures are valid.
-\item For each asset type (and for each timestep), the sum of inputs and outputs is the same.
-For example, in the case of energy production assets, the condition is:
-\begin{align}
-\forall t: & \sum_{out \in \text{EPA outputs}} out.\mathtt{power} \cdot 1_{\left\{out.\mathtt{start} \leq t \leq out.\mathtt{end}\right\}} \nonumber \\
-& = \sum_{in \in \text{EPA inputs}} in.\mathtt{out}.\mathtt{power} \cdot 1_{\left\{in.\mathtt{out}.\mathtt{start} \leq t \leq in.\mathtt{out}.\mathtt{end}\right\}} ,
-\end{align}
-where $1_x$ is equal to $1$ if $x$ is true, and it is $0$ otherwise.
+\item All of the signatures are valid, which ensures that only the current owner can transfer an asset.
+\item For each asset type (and for each timestep), the sum of inputs and outputs is equal.
+For example, in the case of energy production assets, the condition is
+\begin{align*}
+& \forall t: \sum_{\substack{out \,\in\, \field{EPA\_out}:\\out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}}} out.\field{EPA}.\field{power} \nonumber \\
+& = \sum_{\substack{in \,\in\, \field{EPA\_in}:\\in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}}} in.\field{out}.\field{EPA}.\field{power}  .
+%
+%& \forall t: \sum_{out \in \field{EPA\_out}} out.\field{EPA}.\field{power} \cdot 1_{\left\{out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}\right\}} \nonumber \\
+%& = \sum_{in \in \field{EPA\_in}} in.\field{out}.\field{EPA}.\field{power} \cdot 1_{\left\{in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}\right\}} ,
+\end{align*}
+%where $1_x$ is equal to $1$ if $x$ is true, and it is $0$ otherwise.
 %\begin{equation}
@@
 %\end{equation}
+The conditions for consumption and financial assets can be described formally in similar ways.
 \end{compactitem}
-If a transaction submitted to the ledger is valid, it will be permanently recorded.
+%If a transaction submitted to the ledger is valid, it will be permanently recorded.
 
@@
 
-Prosumers use smart-meter transactions to withdraw energy and financial assets from their own smart meters, before they engage in energy trading.
+Prosumers use smart-meter transactions to withdraw energy and financial assets from their own smart meters, before they engage in trading.
 %
-A smart-meter transaction contains the following fields:
+A transaction contains the following fields:
 \begin{compactitem}
-\item List of EPA outputs, each of which is defined by:
+\item \field{EPA\_out}: list of EPA outputs (see above),
+\item \field{ECA\_out}: list of ECA outputs (see above),
+\item \field{FA\_out}: list of FA outputs (see above),
+\item \field{id}: smart meter's identifier,
+\item \field{sig}: smart meter's signature over the transaction.
+\end{compactitem}
+This transaction creates and transfers the assets to the prosumer's addresses, which are specified in the output lists.
+
+The smart meter signs the transaction only if the prosumer is allowed to withdraw these assets.
+More specifically, the amount of withdrawn assets can never exceed certain limits that are set by the DSO.
+For example, in the case of EPA, the following condition must be satisfied for prosumer $i$:
+\begin{equation}
+\forall t: \sum_{tr \,\in\, \field{TR}_i} \sum_{\substack{out \,\in\, tr.\field{EPA\_out}:\\out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}}} out.\field{EPA}.\field{power} < \field{MAXEPA}_i ,
+\end{equation}
+where $\field{TR}_i$ is the set of smart-meter transactions recorded for prosumer $i$ and $\field{MAXEPA}_i$ is the withdrawal limit.
+The condition for consumption assets is similar, based on a limit $\field{MAXECA}_i$.
+For financial assets, the smart meter takes into account the amounts withdrawn and deposited, as well as the outside bill payments to the DSO.
+
+\todo{To address malfunctioning or compromised smart meters, we could also impose a limit on withdrawals.}
+A transaction is valid if the following two conditions hold.
 \begin{compactitem}
-\item an EPA and an address to which it is transferred.
+\item The smart meter identified in the transaction has been authorized by a regulatory transaction that was previously recorded on the ledger.
+\item The smart meter's signature is valid (for public key, see regulatory transactions).
 \end{compactitem}
-\item List of ECA outputs, each of which is defined by:
-\begin{compactitem}
-\item an ECA and an address to which it is transferred.
-\end{compactitem}
-\item List of FA outputs, each of which is defined by:
-\begin{compactitem}
-\item an FA and an address to which it is transferred.
-\end{compactitem}
-\item \field{id}: Identifier of the smart meter.
-\item \field{sig}: Smart meter's signature over the transaction.
-\end{compactitem}
-
-A smart-meter transaction is valid if the following two conditions hold:
-\begin{compactitem}
-\item The smart meter identified in the transaction has been authorized by a regulatory transaction that has been recorded on the ledger.
-\item The smart meter's signature is valid.
-\end{compactitem}
-\todo{To address malfunctioning or compromised smart meters, we could also impose a limit on withdrawals.}
 
@@
 
-\paragraph{Authorize or Ban Smart Meters}
 The DSO uses these transactions to manage the set of authorized smart meters in the microgrid.
@@
 \begin{compactitem}
-\item List of smart meters to be authorized, each of which is defined by:
+\item \field{allow}: list of smart meters to be authorized, each of which is defined by
 \begin{compactitem}
-\item \field{id}: Identifier of the smart meter.
-\item \field{pubkey}: Public key of the smart meter.
+\item \field{id}: identifier of the smart meter.
+\item \field{pubkey}: public key of the smart meter,
 \end{compactitem}
-\item List of smart meters to be banned, each of which is given using its identifier.
-\item \field{time}: Timestep in which smart meters are authorized and banned.
+\item \field{ban}: list of identifiers of smart meters to be banned, 
+\item \field{timestep}: timestep in which authorizations and bans should take effect,
 \item \field{sig}: DSO's signature over the transaction.
@@
 
-A regulatory transaction of this type is valid if the following two conditions hold:
-\begin{compactitem}
-\item The timestep specified in the transaction is in the future.
-\item The DSO's signature is valid.
-\end{compactitem}
-
-\paragraph{Price Policy}
+A regulatory transaction of this type is valid if %the following two conditions hold:
+%\begin{compactitem}
+%\item 
+\field{timestep} is not in the past and % specified in the transaction is in the future.
+%\item 
+the DSO's signature is valid.
+%\end{compactitem}

### 2017-06-05 papers/IoT2017/paper.tex
no message

@@
 \usepackage{paralist}
+\usepackage{enumitem}
 
@@
 
+\allowdisplaybreaks
+
 \title{\plaintitle}
@@
 
-\section{Analysis}
-\label{sec:analysis}
+\section{Discussion}
+\label{sec:discussion}
 
@@
 
+Most of our security requirements follow readily from 
+\begin{compactitem}
+\item the non-malleability of transactions in the distributed ledger 
+\item the signature based validation of transactions
+\item tamper-resistance of smart meters.
+\end{compactitem}
+
 \subsection{Safety}
+
+First, we can easily see that the net amount of energy sold by a prosumer for each timestep is at most $\field{MAXEPA}_i$.
+The amount of energy sold by the prosumer for a timetep is less than or equal to the amount of EPA obtained for that timestep.
+The prosumer can withdraw $\field{MAXEPA}_i$ amount of EPA from its smart meter.
+However, to obtain any amount of further EPA, the prosumer has to buy energy from another prosumer, which would decrease its net energy sold by the same amount.
+Similarly, the net amount of energy sold is at most $\field{MAXECA}_i$.
+
+Second, we can see that the amount of bids posted at the same time by prosumer $i$ for timestep $t$ is at most $\field{MAXEPA}_i + \field{MAXECA}_i$.
 

### 2017-06-05 papers/IoT2017/services.tex
no message

@@
 
-Here, we describe three services that must be implemented for our solution: communication anonymity, mixing service for transaction anonymity, and anonymous bid storage for bidding anonymity.
+In this subsection, we describe the services on which transactions are built and which build on transactions.
+We have already discussed distributed ledgers, which permanently store transactions.
+Now, we will introduce anonymous communication service, mixing service for transaction anonymity, anonymous bid storage, and billing.\todo{Revise list based on final organization!}
 
 \subsubsection{Communication Anonymity}
-Firstly, we must provide an anonymous communication layer, on which we can build an anonymous trading platform.
-Without this communication layer, bids and transactions could be easily de-anonymized based on the network identifiers of the sources (e.g., IP or MAC addresses).
+Firstly, we must provide an anonymous communication layer, on which we can build all other services within our system.
+Without this communication layer, transactions and bids could be easily de-anonymized based on the network identifiers of the sources (e.g., IP or MAC addresses).
 
 We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}.
-To build an onion network, the smart meters, inverters, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on a private blockchain.
-In our first implementation, we can use the free and open-source Tor software with private Directory Authorities.
+To build an onion network, the smart meters, prosumers, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on the ledger.
+In practice, this service can built on 
+%In our first implementation, we can use
+ the free and open-source Tor software with private Directory Authorities.
+In this case, anonymous communication addresses in bids and asks correspond to public-keys that identify Tor hidden services.
 % ritter.vg: "run your own tor network"
@@
 \subsubsection{Bidding Anonymity}
-Finally, we must provide prosumers with the ability to publish energy buy and sell bids anonymously.
+Finally, we must provide prosumers with the ability to post energy bids and asks anonymously.
 To this end, we create a storage for anonymous bids that is readable by all the prosumers in the microgrid.
@@
 \end{itemize}
+
+\subsubsection{Billing and Microgrid Control}
+
+The energy consumption balance $E_i^t$ of prosumer $i$ in timeslot~$t$ is
+\begin{align*}
+E_i^t = & \hphantom{+} \text{measured consumption} - \text{measured production} \\
+ & + \text{EPA deposited by $i$} - \text{EPA withdrawn by $i$} .
+\end{align*}
+Notice that energy consumption assets are not necessary for billing, they are only used to enforce safety requirements.
+
+The financial balance $F_i^t$ of prosumer $i$ in timeslot $t$, which is to be paid by the prosumer to the DSO, is
+\begin{align*}
+F_i^t = & \hphantom{+} \text{FA deposited by $i$ in $t$} - \text{FA withdrawn by $i$ in $t$} \\
+ & + \begin{cases}
+E_i^t \cdot \field{priceProduction} & \text{ if } E_i^t < 0 \\
+- E_i^t \cdot \field{priceConsumption} & \text{ otherwise.} 
+\end{cases}
+\end{align*}
+
+\TODO{discussion of microgrid control based on bids and trades? (update subsubsection title)}

### 2017-06-05 papers/IoT2017/solution.tex
no message

@@
 
-\draw [nodeStyle, fill=red!10]  (0, 1) rectangle    (1, 1.9) node [midway, align=center] {Communication anonymity\\(onion routing)};
+\draw [nodeStyle, fill=red!10]  (0, 1) rectangle    (1, 1.9) node [midway, align=center] {Communication anonymity\\(e.g., onion routing)};
 
-\draw [nodeStyle, fill=blue!10] (0, 2) rectangle    (1, 2.9) node [midway, align=center] {Distributed ledger\\(blockchain)};
+\draw [nodeStyle, fill=blue!10] (0, 2) rectangle    (1, 2.9) node [midway, align=center] {Distributed ledger\\(e.g., blockchain)};
 

### 2017-06-05 papers/IoT2017/transactions.tex
no message

@@
 
-The DSO uses regulatory transactions to authorize or ban smart meters and to control the microgrid load through setting a price policy.
-Since these transactions provide a diverse set of functionality, they are divided into two types.
+The DSO uses regulatory transactions for two purposes: to manage authorized smart meters and to set a price policy.
+First, to change the set of smart meters that are authorized to sign transactions, the DSO authorizes or bans individual smart meters.
+Whenever a new smart meter is installed, the DSO notifies the microgrid by authorizing the device using a regulatory transaction.
+Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or the device is believed to be malfunctioning or compromised), the DSO notifies the microgrid by banning the device.
+Second, to influence microgrid load, the DSO can set a price policy, which includes a price at which prosumer may buy energy from the DSO and a price at which they may sell energy to the DSO.
 
-\TODO{For brevity, combine regulatory transactions into one type.}
-
-The DSO uses these transactions to manage the set of authorized smart meters in the microgrid.
-Whenever a new smart meter is installed, the DSO notifies the members of the microgrid using a regulatory transaction.
-Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or it is believed to be malfunctioning or compromised), the DSO notifies the members of the microgrid using a regulatory transaction.
-These transactions contain the following fields:
+A regulatory transactions contain the following fields:
 \begin{compactitem}
-\item \field{allow}: list of smart meters to be authorized, each of which is defined by
+\item \field{authorize}: list of smart meters to be authorized, each of which is defined by
 \begin{compactitem}
-\item \field{id}: identifier of the smart meter.
+\item \field{id}: identifier of the smart meter,
 \item \field{pubkey}: public key of the smart meter,
@@
 \item \field{ban}: list of identifiers of smart meters to be banned, 
-\item \field{timestep}: timestep in which authorizations and bans should take effect,
+\item \field{priceConsumption}: price at which DSO sells energy,
+\item \field{priceProduction}: price at which DSO buys energy,
+\item \field{time}: timestep after which authorizations, bans, and price changes should take effect,
 \item \field{sig}: DSO's signature over the transaction.
@@
 %\end{compactitem}
+%
+The active prices for timestep $t$ are given by the last regulatory transaction recorded on the ledger whose \field{time} is less than $t$.
+Similarly, later regulatory transactions recorded on the ledger override the authorization and bans of earlier transactions.

### 2017-06-05 papers/IoT2017/intro.tex
no message

--- 2017-06-04 papers/IoT2017/intro.tex
@@
 In this paper, we propose a system that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, and enables the DSO to regulate the trading platform and enforce certain safety rules.
-\todo{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}
-First, we describe the basic elements of a transactive microgrid, and we formulate security, safety, and privacy requirements. 
+\Aron{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}
+First, we describe the basic components of a transactive microgrid, and we formulate security, safety, and privacy requirements. 
 Then, we introduce a decentralized system for transactive microgrids based on distributed ledgers, and describe in detail the transactions and services that are used to implement this system.

### 2017-06-05 papers/IoT2017/prelim.tex
no message

@@
 Finally, based on this control signal, the controller updates the price policy for the microgrid to influence energy production and consumption.
+\Abhishek{Mention that we assume the presence of a secondary controller that balances the voltage and frequency in the microgrid.}
 
@@
 \subsection{Requirements}
-Next, we discuss the security, safety, and privacy requirements that must be satisfied by a transactive energy system.
+Next, we discuss the security, safety, and privacy requirements that must be satisfied by a transactive energy IoT system.
 
@@
 \item prosumers are billed correctly based on the energy prices set by the DSO, their energy trades, and their energy production and consumption measured by the smart meters (i.e., energy production and consumption measurements and financial balances cannot be tampered with),
-\item prosumers or outside attackers cannot change microgrid policies that are to be set by the DSO,
+\item prosumers or outside attackers cannot change microgrid regulatory policies that are set by the DSO,
 \item prosumers cannot back out of trades unilaterally, and they cannot tamper with other prosumers' trading and bidding,

### 2017-06-05 papers/IoT2017/services.tex
no message

@@
 We have already discussed distributed ledgers, which permanently store transactions.
-Now, we will introduce anonymous communication service, mixing service for transaction anonymity, anonymous bid storage, and billing.\todo{Revise list based on final organization!}
+Now, we will introduce anonymous communication service, mixing service for transaction anonymity, anonymous bid storage, and billing.\Aron{Revise list based on final organization!}
 
@@
 More specifically, prosumers should be able to purchase or sell energy without revealing their identity; however, these transaction must also be verifiable and enforceable.
+
+% discuss three approaches:
+% - third-party based services: not really suitable
+% - decentralized protocols: can work
+``In this paper we propose CoinShuffle, a completely decentralized Bitcoin mixing protocol that allows users to utilize Bitcoin in a truly anonymous manner. ''~\cite{ruffing2014coinshuffle}
+``As a solution, we propose Xim, a two-party mixing protocol that is compatible with Bitcoin and related virtual currencies.''~\cite{bissias2014sybil}
+% - cryptographic anonymity (buit-in)
+% Zerocoin
 
@@
 
-\subsubsection{Billing and Microgrid Control}
+\subsubsection{Billing}
 

### 2017-06-05 papers/IoT2017/solution.tex
no message

@@
 At this point, the production asset can still be traced back to the prosumer since the ledger is public.
-To achieve anonymity, the prosumer transfers the production asset to a \emph{mixing service} using an \emph{energy and financial transaction} \circled{2}, which is also recorded on the distributed ledger.
-In turn, the mixing service transfers the production asset to an \emph{anonymous address} \circled{3}\todo{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}, which is randomly generated and controlled by the prosumer.
+To achieve anonymity, the prosumer uses a \emph{mixing service}, which in practice may be implemented as a decentralized protocol, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
+The prosumer transfers the production asset to the mixing service using an \emph{energy and financial transaction} \circled{2}, which is also recorded on the distributed ledger.
+In turn, the mixing service transfers the production asset to an \emph{anonymous address} \circled{3}\Aron{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}, which is randomly generated and controlled by the prosumer.
 Since the mixing service transfers assets from multiple prosumers to multiple anonymous addresses at the same time, and the anonymous addresses were chosen at random by the prosumers, the assets cannot be traced back to the original prosumers after mixing.\footnote{Note that prosumers should divide their assets between multiple anonymous addresses; otherwise, each asset might be traced back to its prosumer based on the amount of energy that it contains.}

### 2017-06-05 papers/IoT2017/transactions.tex
no message

@@
 For example, the default length of the time interval may be 4 seconds, which corresponds to how frequently the control signal of the DSO typically changes.
+\Abhishek{We need to add citation here. I will add that tomorrow.}
+\Abhishek{What about the deadline within which the transactions should finish? Do we need to say anything here?}
+\Aron{Ideally, we should discuss the timing constraints of the ledger (probably when we introduce it), but we would first need to make space for this discussion.}
 
@@
 
-\todo{To address malfunctioning or compromised smart meters, we could also impose a limit on withdrawals.}
+\Aron{To address malfunctioning or compromised smart meters, we could also impose a limit on withdrawals.}
 A transaction is valid if the following two conditions hold.

### 2017-06-05 papers/IoT2017/intro.tex
no message

@@
 On the other hand, it is a distributed market problem where erroneous as well as malicious transactions can create a gap between demand and supply, eventually destabilizing the system.
-However, in both cases, this system requires a distributed  infrastructure comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator, which has to provide the necessary computation fabric to support the interplay between the energy control and the fiscal market challenges.
+\Abhishek{We need to bring out the IoT aspect here a bit.} However, in both cases, this system requires a distributed  infrastructure comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator, which has to provide the necessary computation fabric to support the interplay between the energy control and the fiscal market challenges.
 For example, the Resilient Information Architecture Platform for Smart Grid (RIAPS) \cite{eisele2017riaps} is a distributed IoT  `operating system' that provides the foundations for all algorithms, isolates the hardware details from the algorithms, and provides essential mechanisms for resource management, fault tolerance, and security.
@@
 
-% connect this back to the challenges described below
+\Abhishek{Can we merge this with last paragraph? It seems repetitive.}
+\Aron{I'll probably just remove this.}
 Specifically, 
@@
 However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
+\Abhishek{We can introduce these bullets by stating that the privacy challenges specifically are (the privacy challenges were mentioned at the end of the paragraph above.)}
 \begin{itemize}
@@
 Addressing this issue in a decentralized trading system is quite challenging as it requires hiding the identities of trade partners from each other.
-In comparison, secure smart metering reveals the prosumers' energy usage patterns only to the provider. 
-\item Secondly, transactions may reveal the future energy usage of a prosumer, which could be used to infer private information.
+In comparison, secure smart metering reveals the prosumers' energy usage patterns \Abhishek{Earlier we mentioned the challenge of privacy with respect to system operator in the abstract.
+I think the system operator and provider are the same.
+My question and comment were included in the abstract about this.} only to the provider.
+\item Secondly, \Abhishek{Is this not related to the first point?
+Perhaps the first point can be just about identity and second point can be specifically about consumption patterns.}\Aron{The first point is about to whom information might be leaked, and the second point is about the type of information.
+I'll make this more clear.} transactions may reveal the future energy usage of a prosumer, which could be used to infer private information.
 For example, a smart home may know that its inhabitants will go out in the evening (e.g., by looking at their calendar), and it may trade energy futures accordingly in the morning.
@@
 
+\Abhishek{Can we cite an example of such a service?}
+\Aron{I am not sure what you mean by ``such a service.''}
+\Abhishek{We should connect the paper and our work back to IoT in this paragraph.}
 In this paper, we propose a system that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, and enables the DSO to regulate the trading platform and enforce certain safety rules.

### 2017-06-05 papers/IoT2017/paper.tex
no message

@@
 \newcommand{\TODO}[1]{\todo[inline]{#1}}
+\newcommand{\Abhishek}[1]{\todo[color=yellow!50, linecolor=black!50]{\textbf{Abhishek}: #1}}
+\newcommand{\Aron}[1]{\todo[color=green!40, linecolor=black!50]{\textbf{Aron}: #1}}
 
@@
 While these changes enhance sustainability and efficiency, they also create significant management challenges as the complexity of power systems increases.
-To tackle these challenges, decentralized solutions are emerging, which arrange local communities into microgrids.
+To tackle these challenges, decentralized IoT solutions are emerging, which may arrange local communities into transactive microgrids.
 Within a transactive microgrid, consumers with energy generation and storage capabilities may trade energy with each other, thereby smoothing the load on the main grid using local supply.
 However, providing security, safety, and privacy in a decentralized and transactive energy system is very challenging.
-On the one hand, consumers' personal information must be protected from their their trade partners and the system operator.
+On the one hand, consumers' personal information must be protected from their trade partners and \Abhishek{To what extent is this different that the information already known by the system operator?
+Is this more related to the ``real-time'' nature of transactive information?
+Rather than aggregative total information which is available at the end of billing cycle today.} \Aron{Do we need to detail this in the abstract?} the system operator.
 On the other hand, the system must be protected from careless or malicious trading, which could destabilize the entire grid. 
@@
 As for the DSO, it can receive the same information from the smart meter as in a non-transactive grid (i.e., amount of energy produced and consumed).
-\todo{Also knows financial amounts, but those are necessary for billing.}
+\Aron{Also knows financial amounts, but those are necessary for billing.}
 Since trading is anonymous, it does not receive any further information.

### 2017-06-05 papers/IoT2017/prelim.tex
no message

@@
 
+\Abhishek{This is the perfect paragraph to define transactive microgrid as a special application of IoT spread over a large area. Perhaps we can find a citation that makes this point.}
 Here, we describe a basic system model of transactive microgrids.

### 2017-06-05 papers/IoT2017/solution.tex
no message

@@
 \center
-\begin{tikzpicture}[x=8cm, y=1.2cm,
+\begin{tikzpicture}[x=8cm, y=0.8cm, font=\small,
   nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
 ]
-\draw [nodeStyle, fill=white]   (0, 0) rectangle    (1, 0.9) node [midway, align=center] {Communication network\\and operating system};
+%\draw [nodeStyle, fill=white]   (0, 0) rectangle    (1, 0.9) node [midway, align=center] {Communication network\\[-0.2em]and operating system};
 
-\draw [nodeStyle, fill=red!10]  (0, 1) rectangle    (1, 1.9) node [midway, align=center] {Communication anonymity\\(e.g., onion routing)};
+%\draw [nodeStyle, fill=red!10]  (0, 1) rectangle    (1, 1.9) node [midway, align=center] {Communication anonymity\\[-0.2em](e.g., onion routing)};
 
-\draw [nodeStyle, fill=blue!10] (0, 2) rectangle    (1, 2.9) node [midway, align=center] {Distributed ledger\\(e.g., blockchain)};
+%\draw [nodeStyle, fill=blue!10] (0, 2) rectangle    (1, 2.9) node [midway, align=center] {Distributed ledger\\[-0.2em](e.g., blockchain)};
 
-\draw [nodeStyle, fill=red!10]  (0,    3) rectangle (0.45, 3.9) node [midway, align=center] {Transaction anonymity\\(mixing service)};
-\draw [nodeStyle, fill=blue!10] (0.47, 3) rectangle (0.72, 3.9) node [midway, align=center] {Bid storage};
-\draw [nodeStyle, fill=red!10 ] (0.74, 3) rectangle (1,    3.9) node [midway, align=center] {Active\\smart meter};
+%\draw [nodeStyle, fill=red!10]  (0,    3) rectangle (0.45, 3.9) node [midway, align=center] {Transaction anonymity\\[-0.2em](mixing service)};
+%\draw [nodeStyle, fill=blue!10] (0.47, 3) rectangle (0.72, 3.9) node [midway, align=center] {Bid storage};
+%\draw [nodeStyle, fill=red!10 ] (0.74, 3) rectangle (1,    3.9) node [midway, align=center] {Active\\[-0.2em]smart meter};
 
-\draw [nodeStyle, fill=red!10] (0,    4) rectangle (0.49, 4.9) node [midway, align=center] {Prosumer anonymous\\trading process};
-\draw [nodeStyle, fill=blue!10] (0.51, 4) rectangle (1,    4.9) node [midway, align=center] {Microgrid\\controller};
+%\draw [nodeStyle, fill=red!10] (0,    4) rectangle (0.49, 4.9) node [midway, align=center] {Prosumer anonymous\\[-0.2em]trading process};
+%\draw [nodeStyle, fill=blue!10] (0.51, 4) rectangle (1,    4.9) node [midway, align=center] {Microgrid\\[-0.2em]controller};
+\draw [nodeStyle, fill=white]   (0, 0.9) rectangle    (1, 1.5) node [midway, align=center] {Communication network and operating system};
+
+\draw [nodeStyle, fill=red!10]  (0, 1.65) rectangle    (1, 2.25) node [midway, align=center] {Communication anonymity (e.g., onion routing)};
+
+\draw [nodeStyle, fill=blue!10] (0, 2.4) rectangle    (1, 3.0) node [midway, align=center] {Distributed ledger (e.g., blockchain)};
+
+\draw [nodeStyle, fill=red!10]  (0, 3.15) rectangle (0.45, 4.05) node [midway, align=center] {Transaction anonymity\\[-0.2em](mixing service)};
+\draw [nodeStyle, fill=blue!10] (0.47, 3.15) rectangle (0.72, 4.05) node [midway, align=center] {Bid storage};
+\draw [nodeStyle, fill=red!10 ] (0.74, 3.15) rectangle (1, 4.05) node [midway, align=center] {Active\\[-0.2em]smart meter};
+
+\draw [nodeStyle, fill=red!10] (0, 4.2) rectangle (0.49, 5.1) node [midway, align=center] {Prosumer anonymous\\[-0.2em]trading process};
+\draw [nodeStyle, fill=blue!10] (0.51, 4.2) rectangle (1, 5.1) node [midway, align=center] {Microgrid controller};
 \end{tikzpicture}

### 2017-06-05 papers/IoT2017/analysis.tex
no message

\section{Discussion}
\label{sec:discussion}

In this section, we present a semi-formal analysis of the proposed solution, and show that it satisfies the security, safety, and privacy requirements that were formulated earlier.

\subsection{Security}
Satisfaction of the security requirements follows from:
\begin{itemize}[noitemsep,topsep=-\parskip]
\item non-malleability of transactions in the distributed ledger,
\item validity conditions of the transactions, which include conditions on both signatures and asset balances,
\item and tamper-resistance of smart meters.
\end{itemize}
Together, these properties ensure that only the right entities may create and sign a transaction, that transactions adhere to the rules of the trading process, and that transactions cannot be tampered with.
Due to lack of space, we leave a detailed discussion and proof for future work.

\subsection{Safety}
Next, we demonstrate that faulty or malicious prosumers cannot trade excessive amounts of energy if normal prosumers follow the rules of the trading process. 
%
First, we can show that the net amount of energy sold by prosumer $i$ for each timestep is at most $\field{MAXEPA}_i$.
By definition, the amount of energy sold is less than or equal to the amount of EPA obtained by prosumer $i$.
A prosumer can obtain EPA either by withdrawing from its smart meter or by purchasing form another prosumer.
From its smart meter, prosumer $i$ can withdraw at most $\field{MAXEPA}_i$. % amount of EPA.
The prosumer may also buy EPA from another prosumer; however, this constitutes buying energy, which decreases the net amount of energy sold with the same amount.
%However, to obtain more EPA, the prosumer has to buy energy from another prosumer, which would decrease its net energy sold by the same amount.
Hence, the net amount of energy sold by prosumer $i$ cannot exceed $\field{MAXEPA}_i$.
By extending the argument, we can show that the net amount of energy sold by a group of prosumers~$G$ cannot exceed $\sum_{i \in G} \field{MAXEPA}_i$.
Similarly, we can show that the net amount of energy bought by a group of prosumers $G$ cannot exceed $\sum_{i \in G} \field{MAXECA}_i$.

Second, we can show that the amount of energy bids (or asks) posted at the same time by prosumer $i$ for each timestep is at most $\field{MAXEPA}_i + \field{MAXECA}_i$.
Notice that the limit is higher than for net energy sold or bought, since prosumer $i$ may purchase $\field{MAXECA}_i$ amount of EPA (or $\field{MAXEPA}_i$ amount of ECA) from other prosumers, and then post an energy ask (or bid) in the amount of $\field{MAXEPA}_i + \field{MAXECA}_i$.

\subsection{Privacy}

Due to the communication anonymity and mixing services, members of a microgrid can see only the amount of energy and financial assets withdrawn by a prosumer.
Since all trading transactions are anonymous, the amount of assets traded by the prosumer will not be publicly known.
In case a prosumer does not wish to trade, it can anonymously deposit its assets to a random address that was freshly generated by its smart meter.
Note that even if a prosumer does not wish to trade, it should always withdraw and mix assets; otherwise, the lack of withdrawal would leak information.

As for the DSO, it can receive the same information from the smart meter as in a non-transactive grid (i.e., amount of energy produced and consumed).
\Aron{Also knows financial amounts, but those are necessary for billing.}
Since trading is anonymous, it does not receive any further information.

In fact, we can provide an even higher-level of privacy.
Since price policies are recorded on the ledger, which the smart meters may read, the smart meters can calculate the prosumer's monthly bill, and send only this single financial amount to the DSO each month.
Meanwhile, the DSO can still obtain current and future load information from the bid storage and from the trades recorded on the ledger.

### 2017-06-05 papers/IoT2017/solution.tex
no message

@@
 \draw[transfer] (mixing1) -- node [asset, above] {\circled{3} energy\\production asset} (prosumer2);
-\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {\circled{4} energy production asset,\\energy bid} (bidstorage);
-\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\bid} (partner);
+\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {\circled{4} energy production asset,\\energy ask} (bidstorage);
+\draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\ask} (partner);
 \draw[transfer, bend right=30] (partner) to node [asset, below] {\circled{5} financial asset,\\energy consumption asset} (prosumer3);
@@
 Now, the prosumer can engage in energy trading anonymously.
-To find a trade partner, it can either post an \emph{energy bid} on the bid storage, or simply search the storage for an acceptable \emph{energy ask}.
-To post an energy bid, the prosumer first proves to the storage service -- without revealing its original identity -- that it owns a production asset stored at an anonymous address.
-It can then post the energy bid \circled{4}, which contains an anonymous communication address\footnote{We discuss communication anonymity later.}, a price, and a reference to the production asset.
-If another prosumer, who would like to buy energy, finds the bid acceptable, it can contact the selling prosumer at the communication address given by the bid.
+To find a trade partner, it can either post an \emph{energy ask} on the bid storage, or simply search the storage for an acceptable \emph{energy bid}.
+To post an energy ask, the prosumer first proves to the storage service -- without revealing its original identity -- that it owns a production asset stored at an anonymous address.
+It can then post the energy ask \circled{4}, which contains an anonymous communication address\footnote{We discuss communication anonymity later.}, a price, and a reference to the production asset.
+If another prosumer, who would like to buy energy, finds the ask acceptable, it can contact the selling prosumer at the communication address given by the ask.
 
@@
 Once the smart meter has received the assets, it credits the financial amount to and deducts the energy amount from the prosumer, for billing purposes.
-Note that in order to enforce safety requirements, the prosumer must always deposit the same amount of consumption assets as the amount of production assets withdrawn at the beginning; otherwise, unaccounted consumption assets might be used to trade excessive amounts.
+Note that in order to enforce safety requirements, the prosumer must always deposit the same amount of consumption assets as the amount of production assets withdrawn at the beginning; otherwise, unaccounted assets might be used to trade excessive amounts.
 
@@
 If the prosumer has the consumption capacity and good financial standing, the smart meter transfers the assets to the prosumer and adds the financial amount to the prosumer's bill.
-After transferring the assets through a mixing service, the prosumer is ready to post an energy ask on the bid service.
-To do so, it first proves the ownership of both the financial asset and the consumption asset to the service, and then posts the energy ask, which includes an anonymous communication address.
+After transferring the assets through a mixing service, the prosumer is ready to post an energy bid on the bid service.
+To do so, it first proves the ownership of both the financial asset and the consumption asset to the service, and then posts the energy bid, which includes an anonymous communication address.
 If a partner is found, the trade is executed as described before, the prosumer playing the role of the buyer.

### 2017-06-05 papers/IoT2017/analysis.tex
no message

@@
 \subsection{Privacy}
+Due to the use of communication anonymity and mixing services, members of a microgrid can observe only the amount of assets withdrawn by a prosumer from its smart meter.
+% the amount of energy and financial assets withdrawn by a prosumer.
+Since all trading transactions are anonymous, they do not reveal the actual amount of assets traded by the prosumer.
+If a prosumer does not wish to trade, it can anonymously deposit its assets to a random address that was freshly generated by its smart meter.
+Note that even if a prosumer does not wish to trade, it should always withdraw, mix, and deposit the same amount of assets.
+Otherwise, the lack (or varying amount) of withdrawal would leak information.
 
-Due to the communication anonymity and mixing services, members of a microgrid can see only the amount of energy and financial assets withdrawn by a prosumer.
-Since all trading transactions are anonymous, the amount of assets traded by the prosumer will not be publicly known.
-In case a prosumer does not wish to trade, it can anonymously deposit its assets to a random address that was freshly generated by its smart meter.
-Note that even if a prosumer does not wish to trade, it should always withdraw and mix assets; otherwise, the lack of withdrawal would leak information.
+As for the DSO, it receives the same information from the smart meter as in a non-transactive smart grid (i.e., amount of energy produced and consumed).
+Since trading is anonymous, the DSO learns only the financial balance of the prosumer, which is necessary for billing.
 
-As for the DSO, it can receive the same information from the smart meter as in a non-transactive grid (i.e., amount of energy produced and consumed).
-\Aron{Also knows financial amounts, but those are necessary for billing.}
-Since trading is anonymous, it does not receive any further information.
-
-In fact, we can provide an even higher-level of privacy.
-Since price policies are recorded on the ledger, which the smart meters may read, the smart meters can calculate the prosumer's monthly bill, and send only this single financial amount to the DSO each month.
-Meanwhile, the DSO can still obtain current and future load information from the bid storage and from the trades recorded on the ledger.
+However, we can provide an even higher-level of privacy.
+Since price policies are recorded on the ledger, which the smart meters may read, each prosumer's smart meter may calculate and send the prosumer's monthly bill to the DSO, without revealing the prosumer's energy consumption or production.
+Meanwhile, the DSO can still obtain very detailed load information (including predictions) for the microgrid from the bid storage and the trades recorded on the ledger.

### 2017-06-06 papers/IoT2017/services.tex
no message

--- 2017-06-05 papers/IoT2017/services.tex
@@
 
-In this subsection, we describe the services on which transactions are built and which build on transactions.
-We have already discussed distributed ledgers, which permanently store transactions.
-Now, we will introduce anonymous communication service, mixing service for transaction anonymity, anonymous bid storage, and billing.\todo{Revise list based on final organization!}
+In this subsection, we describe the various services that are implemented in our system. %on which transactions are built and which build on transactions.
+We have already discussed the distributed ledger, which permanently stores valid transactions.
+Now, we will introduce anonymous communication service, mixing service for transaction anonymity, anonymous bid storage, and smart-meter based billing.\Aron{Revise list based on final organization!}
 
 \subsubsection{Communication Anonymity}
-Firstly, we must provide an anonymous communication layer, on which we can build all other services within our system.
-Without this communication layer, transactions and bids could be easily de-anonymized based on the network identifiers of the sources (e.g., IP or MAC addresses).
+Firstly, we must provide an anonymous communication layer, on which we can build all the other services in our system.
+Without this communication layer, transactions and bids could be easily de-anonymized based on their sources' network identifiers (e.g., IP or MAC addresses).
 
-We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}.
+We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}~\cite{reed1998anonymous}.
 To build an onion network, the smart meters, prosumers, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on the ledger.
@@
 \subsubsection{Transaction Anonymity}
+Communication anonymity is necessary for anonymous trading, but it is not sufficient: if prosumers used their own accounts to transfer assets, trades would not be anonymous.
+Fortunately, most distributed ledgers allow users to easily generate new addresses\footnote{The usage of the term \emph{address} varies between distributed ledgers, but our system could be implemented using any popular ledger, such as Bitcoin and Ethereum.
+Specifically, we use the term address to denote a possible destination for asset transfers. 
+Assets transferred to an address can be used only by someone who knows the private key of the address (typically, the one who generated the address).} 
+at random.
+Since these addresses are generated randomly, they are anonymous in the sense that no one can tell who generated them.
+However, if prosumers simply transferred assets to these addresses, they could be easily de-anonymized by tracing the assets back to the prosumers.
+
+To prevent this, prosumers transfer assets to their anonymous addresses through a \emph{mixing service}. 
+The mixing service prevents tracing the assets back to their original owners by mixing together multiple incoming transfers and multiple outgoing transfers, thereby hiding the connections between the prosumers and the anonymous addresses.
+In practice, a mixing service can be implemented using multiple approaches.
+The simplest one is to use a \emph{trusted third party}, called a cryptocurrency tumbler, which can receive and send assets.
+However, anonymity in this case depends on the trustworthiness and reliability of the third party, who could easily de-anonymize the addresses.
+A more secure approach is to used decentralized protocols, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
+These protocols enable participants to mix assets with each other, thereby eliminating the need for a trusted third party, which would constitute a single point of failure.
+Some newer cryptocurrencies, such as Zerocoin~\cite{miers2013zerocoin},  provide built-in mixing services, which are often based on cryptographic principles and proofs.
+
+\begin{comment}
 We must provide prosumers with the ability to create and publish transactions anonymously.
@@
 \end{itemize}
+\end{comment}
 

### 2017-06-06 papers/IoT2017/transactions.tex
no message

@@
 An energy and financial transaction is valid (and can be recorded on the ledger) if the following three conditions hold.
-\begin{compactitem}
+\begin{itemize}[noitemsep,topsep=-\parskip]
 \item None of the outputs referenced by the inputs have been spent by a transaction that has been recorded on the ledger.
@@
 The conditions for consumption and financial assets can be described formally in similar ways.
-\end{compactitem}
+\end{itemize}
 %If a transaction submitted to the ledger is valid, it will be permanently recorded.
@@
 A transaction is valid if the following two conditions hold.
-\begin{compactitem}
+\begin{itemize}[noitemsep,topsep=-\parskip]
 \item The smart meter identified in the transaction has been authorized by a regulatory transaction that was previously recorded on the ledger.
 \item The smart meter's signature is valid (for public key, see regulatory transactions).
-\end{compactitem}
+\end{itemize}
 
@@
 
-The DSO uses regulatory transactions for two purposes: to manage authorized smart meters and to set a price policy.
-First, to change the set of smart meters that are authorized to sign transactions, the DSO authorizes or bans individual smart meters.
-Whenever a new smart meter is installed, the DSO notifies the microgrid by authorizing the device using a regulatory transaction.
+The DSO uses regulatory transactions for two purposes: to manage the set of authorized smart meters and to change the price policy.
+%First, to change the set of smart meters that are authorized to sign transactions, the DSO authorizes or bans individual smart meters.
+First, whenever a new smart meter is installed, the DSO notifies the microgrid by authorizing the device using a regulatory transaction.
 Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or the device is believed to be malfunctioning or compromised), the DSO notifies the microgrid by banning the device.
@@
 The active prices for timestep $t$ are given by the last regulatory transaction recorded on the ledger whose \field{time} is less than $t$.
-Similarly, later regulatory transactions recorded on the ledger override the authorization and bans of earlier transactions.
+Similarly, regulatory transactions that are recorded on the ledger later override the authorizations and bans of earlier transactions.

### 2017-06-06 papers/IoT2017/paper.tex
space saving (without sacrificing content)

@@
 % option again before submitting your final document.
-\usepackage[textsize=tiny, textwidth=1.3cm]{todonotes}
+\usepackage[textsize=tiny, textwidth=1.3cm, disable]{todonotes}
 \newcommand{\TODO}[1]{\todo[inline]{#1}}
@@
 
-\section{Discussion}
-\label{sec:discussion}
-
-Here, we present a semi-formal analysis of the proposed solution, and show that it satisfies the security, safety, and privacy requirements.
-
-\subsection{Security}
-
-Most of our security requirements follow readily from 
-\begin{compactitem}
-\item the non-malleability of transactions in the distributed ledger 
-\item the signature based validation of transactions
-\item tamper-resistance of smart meters.
-\end{compactitem}
-
-\subsection{Safety}
-
-First, we can easily see that the net amount of energy sold by a prosumer for each timestep is at most $\field{MAXEPA}_i$.
-The amount of energy sold by the prosumer for a timetep is less than or equal to the amount of EPA obtained for that timestep.
-The prosumer can withdraw $\field{MAXEPA}_i$ amount of EPA from its smart meter.
-However, to obtain any amount of further EPA, the prosumer has to buy energy from another prosumer, which would decrease its net energy sold by the same amount.
-Similarly, the net amount of energy sold is at most $\field{MAXECA}_i$.
-
-Second, we can see that the amount of bids posted at the same time by prosumer $i$ for timestep $t$ is at most $\field{MAXEPA}_i + \field{MAXECA}_i$.
-
-\subsection{Privacy}
-
-Due to the communication anonymity and mixing services, members of a microgrid can see only the amount of energy and financial assets withdrawn by a prosumer.
-Since all trading transactions are anonymous, the amount of assets traded by the prosumer will not be publicly known.
-In case a prosumer does not wish to trade, it can anonymously deposit its assets to a random address that was freshly generated by its smart meter.
-Note that even if a prosumer does not wish to trade, it should always withdraw and mix assets; otherwise, the lack of withdrawal would leak information.
-
-As for the DSO, it can receive the same information from the smart meter as in a non-transactive grid (i.e., amount of energy produced and consumed).
-\Aron{Also knows financial amounts, but those are necessary for billing.}
-Since trading is anonymous, it does not receive any further information.
-
-In fact, we can provide an even higher-level of privacy.
-Since price policies are recorded on the ledger, which the smart meters may read, the smart meters can calculate the prosumer's monthly bill, and send only this single financial amount to the DSO each month.
-Meanwhile, the DSO can still obtain current and future load information from the bid storage and from the trades recorded on the ledger.
+\input{analysis.tex}
 

### 2017-06-06 papers/IoT2017/solution.tex
space saving (without sacrificing content)

@@
 \center
-\begin{tikzpicture}[x=3.8cm, y=2cm, font=\small,
+\begin{tikzpicture}[x=3.8cm, y=1.6cm, font=\small,
   system/.style={draw, align=center, rounded corners=0.1cm, fill=black!5},
@@
 \draw[transfer, bend right=30] (partner) to node [asset, below] {\circled{5} financial asset,\\energy consumption asset} (prosumer3);
-\draw[transfer, bend right=50] (prosumer2) to node [asset, right] {\circled{5} energy\\production asset} (partner);
+\draw[transfer, bend right=50] (prosumer2) to node [asset, right, yshift=0.25em] {\circled{5} energy\\production asset} (partner);
 \draw[transfer] (prosumer3) -- node [asset, below] {\circled{6} financial asset,\\
@@
 \end{tikzpicture}
+\vspace{-1em}
 \caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy.

### 2017-06-06 papers/IoT2017/transactions.tex
space saving (without sacrificing content)

@@
 First, an \emph{energy production asset} (EPA) is defined by
-\begin{compactitem}
+\begin{itemize}[noitemsep,topsep=-\parskip]
 \item \field{power}: non-negative amount of power to produced (for example, measured in watts),
@@
 \item \field{end}: last time interval in which energy is to be produced.
-\end{compactitem}
+\end{itemize}
+\vspace{\parskip}
 Second, an \emph{energy consumption asset} (ECA) is defined by the same fields; however, for this asset, the fields define energy consumption instead of production.
@@
 An energy and financial transaction contains the following fields:
-\begin{compactitem}
+\begin{itemize}[noitemsep,topsep=-\parskip]
 \item \field{EPA\_in}: list of EPA inputs, each of which is defined by
@@
 \end{itemize}
-\end{compactitem}
+\end{itemize}
+\vspace{0.5\parskip}
 This transaction transfers the assets specified in the input lists to the addresses specified in the output lists. 
@@
 A transaction contains the following fields:
-\begin{compactitem}
+\begin{itemize}[noitemsep,topsep=-\parskip]
 \item \field{EPA\_out}: list of EPA outputs (see above),
@@
 \item \field{sig}: smart meter's signature over the transaction.
-\end{compactitem}
+\end{itemize}
+\vspace{0.5\parskip}
 This transaction creates and transfers the assets to the prosumer's addresses, which are specified in the output lists.
@@
 For example, in the case of EPA, the following condition must be satisfied for prosumer $i$:
-\begin{equation}
+\begin{equation*}
 \forall t: \sum_{tr \,\in\, \field{TR}_i} \sum_{\substack{out \,\in\, tr.\field{EPA\_out}:\\out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}}} out.\field{EPA}.\field{power} < \field{MAXEPA}_i ,
-\end{equation}
+\end{equation*}
 where $\field{TR}_i$ is the set of smart-meter transactions recorded for prosumer $i$ and $\field{MAXEPA}_i$ is the withdrawal limit.
@@
 A regulatory transactions contain the following fields:
-\begin{compactitem}
+\begin{itemize}[noitemsep,topsep=-\parskip]
 \item \field{authorize}: list of smart meters to be authorized, each of which is defined by
@@
 \item \field{sig}: DSO's signature over the transaction.
-\end{compactitem}
+\end{itemize}
+\vspace{\parskip}
 

### 2017-06-06 papers/IoT2017/services.tex
no message

@@
 We have already discussed the distributed ledger, which permanently stores valid transactions.
-Now, we will introduce anonymous communication service, mixing service for transaction anonymity, anonymous bid storage, and smart-meter based billing.\Aron{Revise list based on final organization!}
+Now, we will introduce anonymous communication service, mixing service for transaction anonymity, anonymous bid storage, and smart-meter based billing.
 
@@
 
-\subsubsection{Billing}
+\subsubsection{Smart-Meter Based Billing}
+Once a prosumer has finished trading, it deposits all of its EPA, ECA, and FA to the smart meter, by transferring them to an anonymous address generated by the smart meter.
+Later, during timeslot $t$, the smart meter measures the amount of energy actually consumed (or produced) by the prosumer using physical sensors.
+Then, the meter can compute the prosumer's bill for timeslot $t$, which is to be paid to the DSO, as follows.
 
-The energy consumption balance $E_i^t$ of prosumer $i$ in timeslot~$t$ is
+The energy consumption balance $E_i^t$ of prosumer $i$ is
 \begin{align*}
-E_i^t = & \hphantom{+} \text{measured consumption} - \text{measured production} \\
- & + \text{EPA deposited by $i$} - \text{EPA withdrawn by $i$} .
+E_i^t = & \hphantom{+} \text{measured net energy consumption during timeslot } t \\ %\text{measured consumption} - \text{measured production} \\
+ & - \sum_{epa \,\in\, \{\text{EPA deposited by } i\}: ~ epa.\field{start} \,\leq\, epa.\field{end}} epa.\field{power} \\
+ & + \sum_{epa \,\in\, \{\text{EPA withdrawn by } i\}: ~ epa.\field{start} \,\leq\, epa.\field{end}} epa.\field{power} .
+% & + \text{EPA deposited by $i$} - \text{EPA withdrawn by $i$} .
 \end{align*}
-Notice that energy consumption assets are not necessary for billing, they are only used to enforce safety requirements.
+Notice that consumption assets are not used directly for billing, they are only used to enforce security and safety requirements.
 
-The financial balance $F_i^t$ of prosumer $i$ in timeslot $t$, which is to be paid by the prosumer to the DSO, is
+The bill $B_i^t$ of prosumer $i$ for timeslot $t$, which is to be paid by the prosumer to the DSO, is
 \begin{align*}
-F_i^t = & \hphantom{+} \text{FA deposited by $i$ in $t$} - \text{FA withdrawn by $i$ in $t$} \\
+B_i^t = &  \text{FA withdrawn by $i$ during $t$} - \text{FA deposited by $i$ during $t$} \\
  & + \begin{cases}
-E_i^t \cdot \field{priceProduction} & \text{ if } E_i^t < 0 \\
-- E_i^t \cdot \field{priceConsumption} & \text{ otherwise.} 
+- E_i^t \cdot \field{priceProduction} & \text{ if } E_i^t < 0 \\
+ E_i^t \cdot \field{priceConsumption} & \text{ otherwise,} 
 \end{cases}
 \end{align*}
-
-\TODO{discussion of microgrid control based on bids and trades? (update subsubsection title)}
+where {\field{priceProduction}} and {\field{priceConsumption}} are the prices set by the latest regulatory transactions for timeslot $t$.

### 2017-06-06 papers/IoT2017/services.tex
no message

@@
  the free and open-source Tor software with private Directory Authorities.
-In this case, anonymous communication addresses in bids and asks correspond to public-keys that identify Tor hidden services.
+In this case, anonymous communication identifiers in bids and asks correspond to public-keys that identify Tor hidden services.
 % ritter.vg: "run your own tor network"
@@
 \subsubsection{Bidding Anonymity}
-Finally, we must provide prosumers with the ability to post energy bids and asks anonymously.
-To this end, we create a storage for anonymous bids that is readable by all the prosumers in the microgrid.
-Any prosumer may submit a bid to this storage; however, in order to do so, they must provide a zero-knowledge proof of owning the assets that are to be traded:
-\begin{itemize}
-\item To submit an energy sell bid, the prosumer must prove that it owns an energy production asset on the chain.
-\item To submit an energy buy bid, the prosumer must prove that it own an energy consumption asset as well as financial assets on the chain.
-\end{itemize}
+Finally, we must enable prosumers to anonymously post energy bids and asks on the bid storage service.
+An anonymous bid (or ask) contains an ECA (or EPA), a price, and an anonymous communication identifier (e.g., Tor hidden service), which can be used to contact the bidding (or asking) prosumer.
+To enforce safety requirements, the bid storage service must verify that the prosumer actually owns the asset to be traded.
+To this end, the prosumer first has to prove that it controls the anonymous address where the asset is stored, which can be performed in multiple ways.
+In many distributed ledgers, an address represents a public key, and controlling means knowing the corresponding private key.
+In this case, the prosumer can prove that it controls an address by signing a challenge, which was freshly generated by the service, with the private key of the address.
+Alternatively, the prosumer may also prove control by transferring zero amount of assets to a random address that was freshly generated by the service.
+
+%Finally, we must provide prosumers with the ability to post energy bids and asks anonymously.
+%To this end, we create a storage for anonymous bids that is readable by all the prosumers in the microgrid.
+%Any prosumer may submit a bid to this storage; however, in order to do so, they must provide a zero-knowledge proof of owning the assets that are to be traded:
+%\begin{itemize}
+%\item To submit an energy sell bid, the prosumer must prove that it owns an energy production asset on the chain.
+%\item To submit an energy buy bid, the prosumer must prove that it own an energy consumption asset as well as financial assets on the chain.
+%\end{itemize}
 

### 2017-06-06 papers/IoT2017/solution.tex
no message

@@
 \draw[transfer] (mixing1) -- node [asset, above] {\circled{3} energy\\production asset} (prosumer2);
-\draw[transfer, dashed] (prosumer2) -- node [asset, above right] {\circled{4} energy production asset,\\energy ask} (bidstorage);
+\draw[transfer, dashed] (prosumer2) -- node [asset, above right, xshift=-1.5em, yshift=0.5em] {\circled{4} energy production asset,\\energy ask} (bidstorage);
 \draw[transfer, dashed] (bidstorage) -- node [asset, below right] {energy\\ask} (partner);
@@
 \end{tikzpicture}
-\vspace{-1em}
 \caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy.
@@
 To post an energy ask, the prosumer first proves to the storage service -- without revealing its original identity -- that it owns a production asset stored at an anonymous address.
-It can then post the energy ask \circled{4}, which contains an anonymous communication address\footnote{We discuss communication anonymity later.}, a price, and a reference to the production asset.
-If another prosumer, who would like to buy energy, finds the ask acceptable, it can contact the selling prosumer at the communication address given by the ask.
+It can then post the energy ask \circled{4}, which contains an anonymous communication identifier\footnote{We discuss communication anonymity later.}, a price, and a reference to the production asset.
+If another prosumer, who would like to buy energy, finds the ask acceptable, it can contact the selling prosumer at the communication identifier given by the ask.
 
@@
 After transferring the assets through a mixing service, the prosumer is ready to post an energy bid on the bid service.
-To do so, it first proves the ownership of both the financial asset and the consumption asset to the service, and then posts the energy bid, which includes an anonymous communication address.
+To do so, it first proves the ownership of both the financial asset and the consumption asset to the service, and then posts the energy bid, which includes an anonymous communication identifier.
 If a partner is found, the trade is executed as described before, the prosumer playing the role of the buyer.

### 2017-06-06 papers/IoT2017/related.tex
no message
Update of Related Work + 1 citation addition

@@
 % http://ieeexplore.ieee.org/abstract/document/5054916/
-McDaniel and McLaughlin discuss privacy challenges in smart grids~\cite{mcdaniel2009security}.
+%McDaniel and McLaughlin discuss privacy challenges in smart grids~\cite{mcdaniel2009security}.
 
@@
 % https://pdfs.semanticscholar.org/cdf8/a5b6256823bca38a1d2347ab36f8e4a2ca94.pdf
-Rajagopalan et al.\ use tools from information theory to present a framework, which abstracts both the privacy and the utility requirements of smart meter data~\cite{rajagopalan2011smart,sankar2013smart}.
-Their framework leads to a novel privacy-utility tradeoff problem with minimal assumptions.
-%, which is tractable.
 
 % http://www.comm.toronto.edu/~akhisti/sm.pdf
-Varodayan and Khisti study using rechargeable battery for partially protecting the privacy of information contained in a household's electrical load profile~\cite{varodayan2011smart}.
-They show that stochastic battery policies may leak 26\% less information than a best-effort policy, holds the output load constant whenever possible.
 
 % https://www.researchgate.net/profile/Georgios_Kalogridis/publication/224189766_Smart_Grid_Privacy_via_Anonymization_of_Smart_Metering_Data/links/541169510cf2b4da1bec4193.pdf
+
+% https://arxiv.org/pdf/1305.0735.pdf
+
+Both old and new security and privacy concerns arise with the continuing adoption of smart grids.
+In addition to both old and new security threats, such as energy theft and smart meter malware, McDaniel and McLaughlin discuss the privacy concerns of energy usage profiling that smart grids could potentially enable\cite{mcdaniel2009security}.
+
+Several approaches have been investigated as potential means to provide privacy protections for energy consumers.
+Some approaches look to the use of protocols and/or frameworks to help protect privacy.
+Rajagopalan et al.\ use tools from information theory to present a framework, which abstracts both the privacy and the utility requirements of smart meter data~\cite{rajagopalan2011smart,sankar2013smart}.
+Their framework leads to a novel tractable privacy-utility tradeoff problem with minimal assumptions.
 Efthymiou and Kalogridis describe a method for securely anonymizing frequent electrical metering data sent by a smart meter~\cite{efthymiou2010smart}.
@@
 
-% https://arxiv.org/pdf/1305.0735.pdf
-Tan et al.\ study privacy in a smart metering system from an information theoretic perspective in the presence of energy harvesting and storage units~\cite{tan2013increasing}. 
+Additionally, other approaches such as additional hardware components are explored for potential privacy gains.
+Varodayan and Khisti study using rechargeable battery for partially protecting the privacy of information contained in a household's electrical load profile~\cite{varodayan2011smart}.
+They show that stochastic battery policies may leak 26\% less information than a best-effort policy, holds the output load constant whenever possible.
+Tan et al.
+study privacy in a smart metering system from an information theoretic perspective in the presence of energy harvesting and storage units\cite{tan2013increasing}.
 They show that energy harvesting provides increased privacy by diversifying the energy source, while a storage device can be used to increase both energy efficiency and privacy. 
@@
 
+As Blockchain technology continues to develop and mature, new frameworks, services, and protocols are being developed to leverage blockchain's distributed ledger.
 Microsoft offers Blockchain as a Service (BaaS) on Azure.
-Project Bletchley is Microsoft's architectural approach to building an Enterprise Consortium Blockchain Ecosystem, introducing two new concepts: blockchain middleware and cryptlets~\cite{gray2016introducing}.
-
+Additionally, Microsoft has Project Bletchley as its architectural approach to building an Enterprise Consortium Blockchain Ecosystem, introducing two new concepts: blockchain middleware and cryptlets a secure means for calling code or data outside a SmartContract or blockchain~\cite{gray2016introducing}.
 Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}.
-
+Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}.
 Interledger is a protocol for payments across payment systems, which enables anyone with accounts on two ledgers to create
 a connection between them~\cite{thomas_protocol}.
+Xu et al.\ discuss the use of two pools of proxy agents, agreement pool and payment pool, to assist in protection of privacy when using blockchain technologies for transactions on tangible goods.
+\cite{Xu2017}
 
-Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}.
+%\url{https://geli.net/residential/}
+%\url{https://www.greentechmedia.com/articles/read/geli-raises-7m-to-take-energy-storage-software-to-the-next-level}
 
-\url{https://geli.net/residential/}
-\url{https://www.greentechmedia.com/articles/read/geli-raises-7m-to-take-energy-storage-software-to-the-next-level}
+%\url{http://ethembedded.com/}

### 2017-06-06 papers/IoT2017/related.tex
minor update to related.tex

@@
 Both old and new security and privacy concerns arise with the continuing adoption of smart grids.
-In addition to both old and new security threats, such as energy theft and smart meter malware, McDaniel and McLaughlin discuss the privacy concerns of energy usage profiling that smart grids could potentially enable\cite{mcdaniel2009security}.
+In addition to both old and new security threats, such as energy theft and smart meter malware, McDaniel and McLaughlin discuss the privacy concerns of energy usage profiling that smart grids could potentially enable~\cite{mcdaniel2009security}.
 
@@
 Tan et al.
-study privacy in a smart metering system from an information theoretic perspective in the presence of energy harvesting and storage units\cite{tan2013increasing}.
+study privacy in a smart metering system from an information theoretic perspective in the presence of energy harvesting and storage units~\cite{tan2013increasing}.
 They show that energy harvesting provides increased privacy by diversifying the energy source, while a storage device can be used to increase both energy efficiency and privacy. 
@@
 a connection between them~\cite{thomas_protocol}.
-Xu et al.\ discuss the use of two pools of proxy agents, agreement pool and payment pool, to assist in protection of privacy when using blockchain technologies for transactions on tangible goods.
-\cite{Xu2017}
+Xu et al.\ discuss the use of two pools of proxy agents, agreement pool and payment pool, to assist in protection of privacy when using blockchain technologies for transactions on tangible goods~\cite{Xu2017}.
 

### 2017-06-06 papers/IoT2017/related.tex
minor update to related

@@
 % https://arxiv.org/pdf/1305.0735.pdf
+New privacy concerns arise with the continuing adoption of smart grids.
+In addition to both old and new security threats, such as energy theft and smart meter malware, McDaniel and McLaughlin discuss the privacy concerns of energy usage profiling that smart grids could potentially enable~\cite{mcdaniel2009security}.
+Several approaches have been investigated as potential means to provide privacy protections for smart grid users.
 
-Both old and new security and privacy concerns arise with the continuing adoption of smart grids.
-In addition to both old and new security threats, such as energy theft and smart meter malware, McDaniel and McLaughlin discuss the privacy concerns of energy usage profiling that smart grids could potentially enable~\cite{mcdaniel2009security}.
-
-Several approaches have been investigated as potential means to provide privacy protections for energy consumers.
 Some approaches look to the use of protocols and/or frameworks to help protect privacy.
@@
 Microsoft offers Blockchain as a Service (BaaS) on Azure.
-Additionally, Microsoft has Project Bletchley as its architectural approach to building an Enterprise Consortium Blockchain Ecosystem, introducing two new concepts: blockchain middleware and cryptlets a secure means for calling code or data outside a SmartContract or blockchain~\cite{gray2016introducing}.
+Additionally, Microsoft has Project Bletchley as its architectural approach to building an Enterprise Consortium Blockchain Ecosystem, introducing two new concepts: blockchain middleware and a secure means for calling code or data outside a SmartContract or blockchain called cryptlets~\cite{gray2016introducing}.
 Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}.
@@
 a connection between them~\cite{thomas_protocol}.
-Xu et al.\ discuss the use of two pools of proxy agents, agreement pool and payment pool, to assist in protection of privacy when using blockchain technologies for transactions on tangible goods~\cite{Xu2017}.
+Xu et al.\ discuss the use of two pools of proxy agents, an agreement pool and a payment pool, to assist in protection of privacy when using blockchain technologies for transactions on tangible goods~\cite{Xu2017}.
 

### 2017-06-06 papers/IoT2017/prelim.tex
space saving (without sacrificing content)
polishing

@@
 \Abhishek{This is the perfect paragraph to define transactive microgrid as a special application of IoT spread over a large area. Perhaps we can find a citation that makes this point.}
-Here, we describe a basic system model of transactive microgrids.
-We discuss the following components: a distributed ledger for recording transactions, a bid storage service that facilitates finding trade partners, a microgrid controller for regulating the microgrid load, and smart meters for measuring energy production and consumption.
+We begin by describing a basic system model of transactive microgrids.
+We discuss the following components: a distributed ledger for recording transactions, a bid storage service that facilitates finding trade partners, a microgrid controller for regulating the microgrid load, and smart meters for measuring the prosumers' energy production and consumption.
 
@@
 However, for the sake of fault tolerance, the ledger also needs to be distributed.
-Since a distributed ledger is maintained by multiple nodes, a key implementation requirement is reaching consensus on which transactions are valid and stored in the ledger.
+Since a distributed ledger is maintained by multiple nodes, a key implementation requirement is reaching consensus on which transactions are valid and stored on the ledger.
 Further, this consensus must be reached quickly and reliably, even in the presence of faulty or malicious (e.g., compromised) ledger nodes.
-In this paper, we assume that a distributed ledger service is available, but do not make any assumption about the implementation, such as the particulars of the consensus algorithm.
+In this paper, we assume that a distributed ledger service is available, but do not make any assumptions about the implementation, such as the particulars of the consensus algorithm.
 In practice, a distributed ledger can be implemented using, for example, \emph{blockchains} with proof-of-stake consensus or Practical Byzantine Fault Tolerance algorithm~\cite{castro1999practical}.
@@
 \subsubsection{Bid Storage Service}
-Although individual prosumers trade energy with each other, for the sake of scalability, we need a service that enables prosumers to find trade partners.
+Although prosumers trade energy with each other directly (i.e., without a middleman), for the sake of scalability, we need a service that enables prosumers to find trade partners.
 %A bid storage service receives energy buy and sell bids from prosumers, stores these 
-We assume that there is a bid storage service that enables prosumers to post and read energy \emph{bids} and \emph{asks}.\footnote{A \emph{bid} is an offer to buy at a certain price, while an \emph{ask} is an offer to sell at a certain price.}
-This service relieves prosumers from communicating with a large number of potential trade partners, since they only have to communicate with the service in order to discover trade partners.
-Moreover, in addition to simply storing bids and asks, the service may also find matches in the posted bids and asks, and it may notify the posting prosumers of the trade opportunity.
+We assume that there is a bid storage service that allows prosumers to post and read energy \emph{bids} and \emph{asks}.\footnote{A \emph{bid} is an offer to buy at a certain price, while an \emph{ask} is an offer to sell at a certain price.}
+This service relieves prosumers from contacting a large number of potential trade partners, since they only have to communicate with the service in order to discover trade partners.
+%Moreover, in addition to simply storing bids and asks, the service may also find matches in the posted bids and asks, and it may notify the posting prosumers of the trade opportunity.
 Note that
-%Even though the bid storage appears to the nodes as one entity, 
 for the sake of scalability and reliability, this service can also be implemented in a distributed manner, using multiple nodes.
@@
 \subsubsection{Microgrid Controller}
-The microgrid controller is responsible for stabilizing load within the microgrid and controlling it based on the expected load in the rest of the grid.
-To this end, the controller first estimates the expected load in the microgrid based on the bids and asks in the bid storage as well as on outstanding energy trades in the ledger.
-By combining this estimate with the expected load in the remainder of the grid, the controller produces a control signal that specifies how much the microgrid load should be decreased or increased.
-Finally, based on this control signal, the controller updates the price policy for the microgrid to influence energy production and consumption.
-\Abhishek{Mention that we assume the presence of a secondary controller that balances the voltage and frequency in the microgrid.}
+The microgrid controller is responsible for stabilizing the load within the microgrid and for influencing it based on the predicted future load within the microgrid and the rest of the grid. 
+To this end, the controller first predicts load in the microgrid based on 1) bids and asks in the bid storage and 2) outstanding energy trades in the ledger.
+By combining this  with the prediction for the rest of the grid, the controller produces a control signal that specifies how much the microgrid load should be decreased or increased.
+Finally, based on this signal, the controller updates the price policy for the microgrid to influence energy production and consumption.
+We also assume the presence of a secondary controller that balances voltage and frequency in the microgrid.
 
 \subsubsection{Smart Meters}
-To measure energy production and consumption, a smart meter must be deployed at each prosumer.
-Further, these smart meters must be tamper resistant to prevent prosumers from ``stealing electricity'' by tampering with their meters.
-Once a smart meter has measured the amount of energy produced and consumed by the prosumer, it can send this information to the DSO for billing purposes.
+To measure the prosumers' energy production and consumption, a smart meter must be deployed at each prosumer.
+In practice, these smart meters must be tamper resistant to prevent prosumers from ``stealing electricity'' by tampering with their meters.
+Once a smart meter has measured the net amount of energy consumed by the prosumer in some time interval, it can send this information to the DSO for billing purposes.
 
@@
 \subsubsection{Security}
-Security requirements primarily ensure that every prosumer is billed correctly, but they also provide necessary prerequisite properties for safety.
+Security requirements ensure primarily that prosumers are billed correctly, but they also provide necessary prerequisite properties for safety.
 %Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.
-More specifically, we require that 
-\begin{compactitem}
-\item prosumers are billed correctly based on the energy prices set by the DSO, their energy trades, and their energy production and consumption measured by the smart meters (i.e., energy production and consumption measurements and financial balances cannot be tampered with),
+More specifically, they require that 
+\begin{itemize}[noitemsep,topsep=-\parskip]
+\item prosumers are billed correctly based on the energy prices set by the DSO, their energy trades, and their actual energy production and consumption measured by the smart meters, % (i.e., prosumers or outside attackers cannot tamper with energy production, consumption, and financial balances) % attackers cannot tamper with energy production and consumption balances or financial balances),
 \item prosumers or outside attackers cannot change microgrid regulatory policies that are set by the DSO,
-\item prosumers cannot back out of trades unilaterally, and they cannot tamper with other prosumers' trading and bidding,
-\item financial and physical impact of a compromised or faulty node is limited, and the node can be banned by the DSO.
-\end{compactitem}
+\item prosumers cannot back out of trades unilaterally, and they cannot tamper with other prosumers' trading or bidding,
+\item financial and physical impact of compromised or faulty nodes is limited, and nodes can be banned by the DSO.
+\end{itemize}
 
@@
 Specifically, we require that
-\begin{compactitem}
+\begin{itemize}[noitemsep,topsep=-\parskip]
 \item net amount of energy sold (or bought) by a prosumer is upper bounded (by an amount set by the DSO), where the net amount of energy sold is the difference between the amount of energy sold and bought by the prosumer, and the net amount of energy bought is defined analogously,
 \item energy bids and asks posted by the prosumer are limited in a similar way.
-\end{compactitem}
+\end{itemize}
 
@@
 More specifically, we require that
-\begin{compactitem}
+\begin{itemize}[noitemsep,topsep=-\parskip]
 \item only the corresponding smart meter and the DSO may gain information regarding the amount of energy produced, consumed, bought, or sold by a prosumer,\footnote{Note that this requirement is impossible to satisfy if all other prosumers may collude against one target.
@@
 \item only the prosumer may know which bids and asks it has posted, and no one can know who traded energy with whom.
-\end{compactitem}
+\end{itemize}

### 2017-06-06 papers/IoT2017/solution.tex
no message

@@
 
-In this section, we describe our solution for providing privacy for prosumers without compromising the safety and security of the microgrid.
+In this section, we describe our solution for providing privacy to prosumers in a transactive energy IoT system, without compromising grid safety and security.
 Figure~\ref{fig:softwareArchitecture} shows a high-level overview of the architecture of our solution.
@@
 
-\draw [nodeStyle, fill=red!10] (0, 4.2) rectangle (0.49, 5.1) node [midway, align=center] {Prosumer anonymous\\[-0.2em]trading process};
+\draw [nodeStyle, fill=red!10] (0, 4.2) rectangle (0.49, 5.1) node [midway, align=center] {Anonymous trading\\[-0.2em]process for prosumers};
 \draw [nodeStyle, fill=blue!10] (0.51, 4.2) rectangle (1, 5.1) node [midway, align=center] {Microgrid controller};

### 2017-06-07 papers/IoT2017/solution.tex
polishing

@@
 \subsection{Overview of the Trading Process}
-We begin with a semi-formal description of the energy trading process from the prosumers' perspective.
-In subsequent subsections, we will describe the assets, transactions, and services in our system in more detail.
+We first provide a semi-formal description of the energy trading process from the prosumers' perspective.
+In subsequent subsections, we will describe the assets, transactions, and services used for trading in more detail.
 
-First, consider a prosumer who wishes sell energy to another prosumer (this case is illustrated in Figure~\ref{fig:sellFlow}).
+First, consider a prosumer who wishes to sell energy to another prosumer (this case is illustrated in Figure~\ref{fig:sellFlow}).
 As its very first step, the prosumer withdraws an \emph{energy production asset} from its smart meter.
@@
 In turn, the mixing service transfers the production asset to an \emph{anonymous address} \circled{3}\Aron{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}, which is randomly generated and controlled by the prosumer.
-Since the mixing service transfers assets from multiple prosumers to multiple anonymous addresses at the same time, and the anonymous addresses were chosen at random by the prosumers, the assets cannot be traced back to the original prosumers after mixing.\footnote{Note that prosumers should divide their assets between multiple anonymous addresses; otherwise, each asset might be traced back to its prosumer based on the amount of energy that it contains.}
+Since the mixing service transfers assets from multiple prosumers to multiple anonymous addresses at the same time, and the anonymous addresses were generated at random by the prosumers, the assets cannot be traced back to the original prosumers after mixing.\footnote{Note that prosumers should divide their assets between multiple anonymous addresses; otherwise, each asset might be traced back to its prosumer based on the amount of energy that it contains.}
 
@@
 It can then post the energy ask \circled{4}, which contains an anonymous communication identifier\footnote{We discuss communication anonymity later.}, a price, and a reference to the production asset.
-If another prosumer, who would like to buy energy, finds the ask acceptable, it can contact the selling prosumer at the communication identifier given by the ask.
+If another prosumer, who would like to buy energy, finds the ask acceptable, it can contact the seller using the communication identifier given included in the ask.
 
@@
 Once the smart meter has received the assets, it credits the financial amount to and deducts the energy amount from the prosumer, for billing purposes.
-Note that in order to enforce safety requirements, the prosumer must always deposit the same amount of consumption assets as the amount of production assets withdrawn at the beginning; otherwise, unaccounted assets might be used to trade excessive amounts.
+In order to enforce safety requirements, the prosumer is required to always deposit the same amount of consumption assets as the amount of production assets withdrawn at the beginning; otherwise, unaccounted assets might be used to trade excessive amounts.
 
@@
 To do so, it first proves the ownership of both the financial asset and the consumption asset to the service, and then posts the energy bid, which includes an anonymous communication identifier.
-If a partner is found, the trade is executed as described before, the prosumer playing the role of the buyer.
+If a partner is found, the trade is executed as described before, the prosumer playing the role of the buyer this time.
 Finally, the prosumer deposits the purchased energy production asset to the anonymous address of its smart meter,
 which credits the energy amount to the prosumer, for billing purposes.
-Note that if the prosumer has not used up the financial asset completely, then the remainder may also be deposited back to the smart meter.
+Note that if the prosumer has not spent all of its financial assets, then the remainder may also be deposited back to the smart meter.
 

### 2017-06-07 papers/IoT2017/paper.tex
no message
updates for emphasizing the IoT aspect

@@
 % option again before submitting your final document.
-\usepackage[textsize=tiny, textwidth=1.3cm, disable]{todonotes}
+\usepackage[textsize=tiny, textwidth=1.3cm]{todonotes}
 \newcommand{\TODO}[1]{\todo[inline]{#1}}
@@
 However, providing security, safety, and privacy in a decentralized and transactive energy system is very challenging.
-On the one hand, consumers' personal information must be protected from their trade partners and \Abhishek{To what extent is this different that the information already known by the system operator?
+On the one hand, consumers' personal information must be protected from their trade partners and
+\Abhishek{To what extent is this different that the information already known by the system operator?
 Is this more related to the ``real-time'' nature of transactive information?
-Rather than aggregative total information which is available at the end of billing cycle today.} \Aron{Do we need to detail this in the abstract?} the system operator.
+Rather than aggregative total information which is available at the end of billing cycle today.} \Aron{Do we need to detail this in the abstract?}\Abhishek{we dont have to} the system operator.
 On the other hand, the system must be protected from careless or malicious trading, which could destabilize the entire grid. 

### 2017-06-07 papers/IoT2017/transactions.tex
no message

@@
 For example, control signals specify how the microgrid load should change at certain points in time, energy trades specify when energy will be consumed or produced, etc.
-To facilitate processing signals and transactions, we divide time into fixed-length intervals, and specify points or periods in time using these discrete timesteps.
+To facilitate representing signals and transactions, we divide time into fixed-length intervals, and specify points or periods in time using these discrete timesteps.
 The length of the time interval is determined based on the timing assumptions of the physical power system.
@@
 
-Before we can discuss transactions, we must define the format of three assets that these transactions may transfer.
+Before we can discuss transactions, we must define the format of the three types of assets that these transactions may transfer.
 First, an \emph{energy production asset} (EPA) is defined by
@@
 Energy and financial transactions transfer energy and financial assets from one address to another.
-Prosumers use these transactions for multiple purposes: to trade energy by exchanging assets with other prosumers, to prove to the bid storage that they have production or consumption capacity, to hide their identity by transferring assets to and from mixing services, and to deposit assets at their smart meter.
+Prosumers can use these transactions for multiple purposes: to trade energy by exchanging assets with other prosumers, to prove to the bid storage service that they possess an asset, to hide their identity by transferring assets to and from mixing services, and to deposit assets at their smart meter.
 %
@@
 \item \field{out}: reference to an EPA output of a previous transaction,
-\item \field{sig}: signature for referenced output,
+\item \field{sig}: signature of the referenced output's address,
 \end{itemize}
@@
 \item \field{out}: reference to an ECA output of a previous transaction,
-\item \field{sig}: signature for referenced output,
+\item \field{sig}: signature of the referenced output's address,
 \end{itemize}
@@
 \item \field{out}: reference to an FA output of a previous transaction,
-\item \field{sig}: signature for referenced output,
+\item \field{sig}: signature of the referenced output's address,
 \end{itemize}
@@
 \item \field{EPA}: a financial asset,
-\item \field{address}: address to which FA is transferred,
+\item \field{address}: address to which FA is transferred.
 \end{itemize}
@@
 This transaction transfers the assets specified in the input lists to the addresses specified in the output lists. 
-Note that assets may be divided or combined, as the input and output lists may differ in length.
+Input and output lists may differ in length, so one asset may be divided into multiple assets, and multiple assets may be combined into one.
 
@@
 \item None of the outputs referenced by the inputs have been spent by a transaction that has been recorded on the ledger.
-\item All of the signatures are valid, which ensures that only the current owner can transfer an asset.
-\item For each asset type (and for each timestep), the sum of inputs and outputs is equal.
+\item All of the signatures are valid, which ensures that an asset can be transferred only by its current owner. % current owner can transfer an asset.
+\item For each asset type (and for each timestep), the sums of the input and output assets are equal.
 For example, in the case of energy production assets, the condition is
@@
 The smart meter signs the transaction only if the prosumer is allowed to withdraw these assets.
-More specifically, the amount of withdrawn assets can never exceed certain limits that are set by the DSO.
+More specifically, the amount of assets withdrawn can never exceed certain limits that are set by the DSO.
 For example, in the case of EPA, the following condition must be satisfied for prosumer $i$:
 \begin{equation*}
-\forall t: \sum_{tr \,\in\, \field{TR}_i} \sum_{\substack{out \,\in\, tr.\field{EPA\_out}:\\out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}}} out.\field{EPA}.\field{power} < \field{MAXEPA}_i ,
+\forall t: \sum_{tr \,\in\, \field{STR}_i} \sum_{\substack{out \,\in\, tr.\field{EPA\_out}:\\out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}}} \hspace{-1em} out.\field{EPA}.\field{power} < \field{MAXEPA}_i ,
 \end{equation*}
-where $\field{TR}_i$ is the set of smart-meter transactions recorded for prosumer $i$ and $\field{MAXEPA}_i$ is the withdrawal limit.
-The condition for consumption assets is similar, based on a limit $\field{MAXECA}_i$.
-For financial assets, the smart meter takes into account the amounts withdrawn and deposited, as well as the outside bill payments to the DSO.
+where $\field{STR}_i$ is the set of smart-meter transactions created for prosumer $i$, and $\field{MAXEPA}_i$ is the withdrawal limit.
+The condition for consumption assets is similar, based on a withdrawal limit $\field{MAXECA}_i$.
+For financial assets, the smart meter can take into account the amounts withdrawn and deposited, as well as the outside bill payments to the DSO.
 
@@
 \begin{itemize}[noitemsep,topsep=-\parskip]
-\item The smart meter identified in the transaction has been authorized by a regulatory transaction that was previously recorded on the ledger.
-\item The smart meter's signature is valid (for public key, see regulatory transactions).
+\item The smart meter identified in the transaction has been authorized (and not been banned) by regulatory transactions. % that was previously recorded on the ledger.
+\item The smart meter's signature is valid (for the smart meter's public key, see regulatory transactions).
 \end{itemize}
@@
 First, whenever a new smart meter is installed, the DSO notifies the microgrid by authorizing the device using a regulatory transaction.
-Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or the device is believed to be malfunctioning or compromised), the DSO notifies the microgrid by banning the device.
+Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or the device is believed to be faulty or compromised), the DSO notifies the microgrid by banning the device.
 Second, to influence microgrid load, the DSO can set a price policy, which includes a price at which prosumer may buy energy from the DSO and a price at which they may sell energy to the DSO.

### 2017-06-07 papers/IoT2017/intro.tex

@@
 On the other hand, it is a distributed market problem where erroneous as well as malicious transactions can create a gap between demand and supply, eventually destabilizing the system.
-\Abhishek{We need to bring out the IoT aspect here a bit.} However, in both cases, this system requires a distributed  infrastructure comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator, which has to provide the necessary computation fabric to support the interplay between the energy control and the fiscal market challenges.
-For example, the Resilient Information Architecture Platform for Smart Grid (RIAPS) \cite{eisele2017riaps} is a distributed IoT  `operating system' that provides the foundations for all algorithms, isolates the hardware details from the algorithms, and provides essential mechanisms for resource management, fault tolerance, and security.
-\cite{Scott2017ICCPS} also describes a simple transactive energy application using the RIAPS platform.
-However, it does not provide the key supports required to handle the privacy challenges that arise from the required information exchange in this decentralized transactive system.
+However, in both cases, this system requires a distributed  infrastructure comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator, which has to provide the necessary computation fabric to support the interplay between the energy control and the fiscal market challenges.
+With the advent of IoT-based solutions in smart grid  dynamic demand response systems, which are a precursor to transactive sytems have been made possible \cite{Haider2016166}.
+
+In general the focus is now on creating a distributed  IoT infrastructure comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator, which has to provide the necessary computation fabric to support the interplay between the energy control and the fiscal market challenges, as shown by Volttron \cite{katipamula2016volttron},  OpenFMB \cite{gunthersmart}, and the Resilient Information Architecture Platform for Smart Grid (RIAPS) \cite{eisele2017riaps}\cite{Scott2017ICCPS}, which is a distributed IoT  `operating system' that provides the foundations for all algorithms, isolates the hardware details from the algorithms, and provides essential mechanisms for resource management, fault tolerance, and security.
+However, most of these efforts are focusing on the computation and distribution of information and do not provide the key supports required to handle the privacy challenges that arise from the required information exchange in this decentralized transactive system.
+
+In this paper, we assume the existence of the IoT infrastructure and specifically focus on the privacy challenges mentined below.
 
@@
 
-\Abhishek{Can we merge this with last paragraph? It seems repetitive.}
-\Aron{I'll probably just remove this.}
-Specifically, 
-in order to take advantage of local energy production and storage capabilities, 
+%\Abhishek{Can we merge this with last paragraph? It seems repetitive.}
+%\Aron{I'll probably just remove this.}
+%Specifically, 
+%in order to take advantage of local energy production and storage capabilities, 
 %in order to take advantage of these capabilities, 
-electric grids need to become more decentralized.
-However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
-\Abhishek{We can introduce these bullets by stating that the privacy challenges specifically are (the privacy challenges were mentioned at the end of the paragraph above.)}
+%electric grids need to become more decentralized.
+%However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
+%\Abhishek{We can introduce these bullets by stating that the privacy challenges specifically are (the privacy challenges were mentioned at the end of the paragraph above.)}
 \begin{itemize}

### 2017-06-07 papers/IoT2017/services.tex
no message

@@
 
-In this subsection, we describe the various services that are implemented in our system. %on which transactions are built and which build on transactions.
+In this subsection, we describe the various services that are provided in our system. %on which transactions are built and which build on transactions.
 We have already discussed the distributed ledger, which permanently stores valid transactions.
-Now, we will introduce anonymous communication service, mixing service for transaction anonymity, anonymous bid storage, and smart-meter based billing.
+Now, we will introduce the anonymous communication service, the mixing service for transaction anonymity, the anonymous bid storage, and smart-meter based billing.
 
@@
 To build an onion network, the smart meters, prosumers, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on the ledger.
-In practice, this service can built on 
+In practice, this service can be built on 
 %In our first implementation, we can use

### 2017-06-07 papers/IoT2017/related.tex
added %!TEX root = paper.tex

@@
+%!TEX root = paper.tex
 \section{Related Work}
@@
 
+In this section we describe the related research.
+It has been divided into two subsections to focus on blockchains, which we are using to implement the distributed ledger service described earlier, and other works on smart grid privacy concerns.
+
 \subsection{Smart Grid and Meter Privacy}
-
 % http://ieeexplore.ieee.org/abstract/document/5054916/
 %McDaniel and McLaughlin discuss privacy challenges in smart grids~\cite{mcdaniel2009security}.
-
 % https://arxiv.org/pdf/1108.2234.pdf
 % https://pdfs.semanticscholar.org/cdf8/a5b6256823bca38a1d2347ab36f8e4a2ca94.pdf
-
 % http://www.comm.toronto.edu/~akhisti/sm.pdf
-
 % https://www.researchgate.net/profile/Georgios_Kalogridis/publication/224189766_Smart_Grid_Privacy_via_Anonymization_of_Smart_Metering_Data/links/541169510cf2b4da1bec4193.pdf
-
 % https://arxiv.org/pdf/1305.0735.pdf
@@
 
+\Abhishek{Aron this section should end with a few sentence about how our approach fits in. Perhaps just a few sentences reworded from introduction will be sufficient}
+
 \subsection{Blockchain Technology}

### 2017-06-07 papers/IoT2017/analysis.tex
no message

@@
 
-Second, we can show that the amount of energy bids (or asks) posted at the same time by prosumer $i$ for each timestep is at most $\field{MAXEPA}_i + \field{MAXECA}_i$.
+Second, we can show that the total amount of energy bids (or asks) posted at the same time by prosumer $i$ for each timestep is at most $\field{MAXEPA}_i + \field{MAXECA}_i$.
 Notice that the limit is higher than for net energy sold or bought, since prosumer $i$ may purchase $\field{MAXECA}_i$ amount of EPA (or $\field{MAXEPA}_i$ amount of ECA) from other prosumers, and then post an energy ask (or bid) in the amount of $\field{MAXEPA}_i + \field{MAXECA}_i$.

### 2017-06-07 papers/IoT2017/services.tex
no message

@@
 A more secure approach is to used decentralized protocols, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
-These protocols enable participants to mix assets with each other, thereby eliminating the need for a trusted third party, which would constitute a single point of failure.
+These protocols enable participants to mix assets with each other, thereby eliminating the need for a trusted third party. %, which would constitute a single point of failure.
 Some newer cryptocurrencies, such as Zerocoin~\cite{miers2013zerocoin},  provide built-in mixing services, which are often based on cryptographic principles and proofs.
@@
 E_i^t = & \hphantom{+} \text{measured net energy consumption during timeslot } t \\ %\text{measured consumption} - \text{measured production} \\
- & - \sum_{epa \,\in\, \{\text{EPA deposited by } i\}: ~ epa.\field{start} \,\leq\, epa.\field{end}} epa.\field{power} \\
- & + \sum_{epa \,\in\, \{\text{EPA withdrawn by } i\}: ~ epa.\field{start} \,\leq\, epa.\field{end}} epa.\field{power} .
+ & - \sum_{epa \,\in\, \{\text{EPA deposited by } i\}: ~ epa.\field{start} \,\leq\, t \,\leq\, epa.\field{end}} epa.\field{power} \\
+ & + \sum_{epa \,\in\, \{\text{EPA withdrawn by } i\}: ~ epa.\field{start} \,\leq\, t \,\leq\, epa.\field{end}} epa.\field{power} .
 % & + \text{EPA deposited by $i$} - \text{EPA withdrawn by $i$} .

### 2017-06-07 papers/IoT2017/intro.tex
no message

@@
 Power grids are undergoing major changes due to rapid
-acceleration in renewable energy resources, such as wind and solar power \cite{EIA2014, 5430489}. For example, 
-$4,143$ megawatts of solar panels were installed in third quarter of 2016 \cite{seia}.
+acceleration in renewable energy resources, such as wind and solar power \cite{5430489}. % \cite{EIA2014}
+For example, 
+$4,\!143$ megawatts of solar panels were installed in the third quarter of 2016 \cite{seia}.
 This capacity is estimated to grow from 4\% in 2015 to 29\% in 2040 \cite{Randal}.
-At the same time, the battery technology costs per kWh have been dropping significantly \cite{stock2015powerful}, reaching grid parity \cite{bronski2015economics}.
-This massive integration of renewable energy requires detailed information and visibility into all aspects of this network, making it difficult to manage, especially in the presence of variable distributed energy resources \cite{7452738}.
+At the same time, battery technology costs per kWh have been dropping significantly \cite{stock2015powerful}, reaching grid parity.
+% \cite{bronski2015economics}
+This massive integration of renewable energy requires detailed information and visibility into all aspects of the network, making it difficult to manage, especially in the presence of variable distributed energy resources \cite{7452738}.
 Therefore, a different vision for the future of power-grid operations is emerging: a decentralized system in which local communities are arranged in microgrids \cite{rahimi2012transactive}.
@@
 Distribution System Operators (DSO) can be the custodian of this market, while still meeting the net demand \cite{7462854}.
-For example, the Brooklyn Microgrid, which was developed by LO3 Energy as a pilot project, is a peer-to-peer energy market for locally generated renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}
+For example, the Brooklyn Microgrid, which was developed by LO3 Energy as a pilot project, is a peer-to-peer market for locally generated renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}
 
@@
 However, in both cases, this system requires a distributed  infrastructure comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator, which has to provide the necessary computation fabric to support the interplay between the energy control and the fiscal market challenges.
-With the advent of IoT-based solutions in smart grid  dynamic demand response systems, which are a precursor to transactive sytems have been made possible \cite{Haider2016166}.
+Recently, demand-response systems have been enabled as applications of IoT in smart grid~\cite{Haider2016166}. Transactive energy systems are the next step for smart grid.
+% With the advent of IoT-based solutions in smart-grid  dynamic demand response systems, which are a precursor to transactive sytems have been made possible.
 
-In general the focus is now on creating a distributed  IoT infrastructure comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator, which has to provide the necessary computation fabric to support the interplay between the energy control and the fiscal market challenges, as shown by Volttron \cite{katipamula2016volttron},  OpenFMB \cite{gunthersmart}, and the Resilient Information Architecture Platform for Smart Grid (RIAPS) \cite{eisele2017riaps}\cite{Scott2017ICCPS}, which is a distributed IoT  `operating system' that provides the foundations for all algorithms, isolates the hardware details from the algorithms, and provides essential mechanisms for resource management, fault tolerance, and security.
-However, most of these efforts are focusing on the computation and distribution of information and do not provide the key supports required to handle the privacy challenges that arise from the required information exchange in this decentralized transactive system.
+In general, the focus is now on creating a distributed IoT infrastructure%  comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator
+, which provides the necessary computation fabric to support the interplay between energy control and fiscal market challenges, as shown by Volttron \cite{katipamula2016volttron},  OpenFMB \cite{gunthersmart}, and the Resilient Information Architecture Platform for Smart Grid (RIAPS) \cite{eisele2017riaps,Scott2017ICCPS}.
+For instance, the latter is a distributed IoT  ``operating system'' that provides the foundations for all algorithms, isolates the hardware details from the algorithms, and provides essential mechanisms for resource management, fault tolerance, and security.
+However, most of these efforts are focusing on the computation and distribution of information and, and they do not provide the key support required to handle the privacy challenges that arise from the required information exchange in this decentralized transactive system.
 
-In this paper, we assume the existence of the IoT infrastructure and specifically focus on the privacy challenges mentined below.
-
+In this paper, we assume the existence of the IoT infrastructure and specifically focus on the following privacy challenges.
+%
+%
 % This is where the RIAPS and computing services discussion will be included. However, it does not solve the following challenges, which is the focus of this paper.
-
+%
 %\Abhishek{Can we merge this with last paragraph? It seems repetitive.}
@@
 %\Abhishek{We can introduce these bullets by stating that the privacy challenges specifically are (the privacy challenges were mentioned at the end of the paragraph above.)}
-\begin{itemize}
+\begin{itemize}[itemsep=0.25\parskip,topsep=-0.5\parskip]
 \item Firstly, since prosumers\footnote{We refer to customers as \emph{prosumers} to emphasize that they can not only consume energy, but may also produce it.}  may purchase energy from each other in a transactive microgrid, transactions may inadvertently reveal the prosumers' detailed energy usage patterns to other prosumers within the microgrid.
@@
 Note that energy futures, whose delivery may happen several hours after when the transaction is made, can play a very important role in predicting and controlling microgrid load.
-In comparison, smart metering reveals only current (and past) usage.
-\item Thirdly, transactions and energy usage data in a transactive microgrid are much richer source of information than the simple energy usage data collected by smart meters.
+In comparison, smart metering reveals only current (or past) usage.
+\item Thirdly, transactions and energy usage data in a transactive microgrid are much richer sources of information than the simple energy usage data collected by smart meters.
 More specifically, the information available in a transactive microgrid is a superset of what is available from smart metering, and it may be used to infer personal information, such as risk propensity and financial standing.
 \end{itemize}
+\vspace{0.5\parskip}
 
@@
 However, this is a challenging task, as the system also has to satisfy security and safety requirements, which often conflict with privacy goals.
-For example, to prevent a prosumer from destabilizing the grid through careless of malicious energy trading, the system must check all of the prosumers' transactions.
+For example, to prevent a prosumer from destabilizing the grid through careless of malicious energy trading, the system must check all of the prosumer's transactions.
 In a decentralized system, this requires disseminating information, which could be used to infer the prosumer's future energy consumption.

### 2017-06-07 papers/IoT2017/related.tex

--- 2017-06-06 papers/IoT2017/related.tex
@@
 
-\subsection{Smart Grid and Meter Privacy}
+%In this section we describe the related research.
+It has been divided into two subsections to focus on blockchains, which we are using to implement the distributed ledger service described earlier, and other works on smart grid privacy concerns.
 
+%\subsection{Smart Grid and Meter Privacy}
 % http://ieeexplore.ieee.org/abstract/document/5054916/
 %McDaniel and McLaughlin discuss privacy challenges in smart grids~\cite{mcdaniel2009security}.
-
 % https://arxiv.org/pdf/1108.2234.pdf
 % https://pdfs.semanticscholar.org/cdf8/a5b6256823bca38a1d2347ab36f8e4a2ca94.pdf
-
 % http://www.comm.toronto.edu/~akhisti/sm.pdf
-
 % https://www.researchgate.net/profile/Georgios_Kalogridis/publication/224189766_Smart_Grid_Privacy_via_Anonymization_of_Smart_Metering_Data/links/541169510cf2b4da1bec4193.pdf
-
 % https://arxiv.org/pdf/1305.0735.pdf
@@
 
-\subsection{Blockchain Technology}
+Our solution extends earlier work by considering a decentralized IoT system for transactive energy, and addressing the novel privacy threat posed by trading.
+In other words, while earlier results protected prosumers' privacy from the DSO, we protect privacy from other prosumers as well as from outside attackers.
+
+A key element of our approach is the ability to distribute the informtion among peers. For that purpose, we rely on the use of Blockchains. 
+As Blockchain technology continues to develop and mature, new frameworks, services, and protocols are being developed to leverage blockchain's distributed ledger.
+Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}.
+Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}.
+However, this paper focuses on theoretical aspects of our implementation and as such any one of these distributed ledgers provide the required capabilities.\Abhishek{Aron please see this paragraph}
+
+%\Abhishek{Aron this section should end with a few sentence about how our approach fits in. Perhaps just a few sentences reworded from introduction will be sufficient}
+
+\iffalse
+\subsection{Blockchains as Distributed Ledgers}
 
@@
 Xu et al.\ discuss the use of two pools of proxy agents, an agreement pool and a payment pool, to assist in protection of privacy when using blockchain technologies for transactions on tangible goods~\cite{Xu2017}.
+\fi
 

### 2017-06-07 papers/IoT2017/concl.tex
final

\section{Conclusion}
\label{sec:concl}

As the complexity of power systems increases due to the evolution of power grids, decentralized transactive-energy IoT systems are emerging to tackle this complexity.
However, these decentralized systems also give rise to new privacy challenges, which are further complicated by the stringent safety and security requirements of power systems.
We have addressed these challenges by providing a novel solution for anonymous energy trading within a transactive microgrid.
Our solution builds on distributed ledgers, such as blockchains, and other proven techniques for anonymity, such as mixing services and onion routing.
We have described the novel process of anonymous energy trading and detailed the novel transactions and services used in our system.
Finally, we have discussed how the proposed solution satisfies security, safety, and privacy requirements.
In future work, we will provide rigorous proofs of satisfying these requirements, and we will present an implementation of our system with performance results.

### 2017-06-07 papers/IoT2017/intro.tex
final

@@
 Addressing this issue in a decentralized trading system is quite challenging as it requires hiding the identities of trade partners from each other.
-In comparison, secure smart metering reveals the prosumers' energy usage patterns \Abhishek{Earlier we mentioned the challenge of privacy with respect to system operator in the abstract.
-I think the system operator and provider are the same.
-My question and comment were included in the abstract about this.} only to the provider.
+In comparison, secure smart metering reveals the prosumers' energy usage patterns only to the operator. 
 \item Secondly, \Abhishek{Is this not related to the first point?
@@
 \Abhishek{We should connect the paper and our work back to IoT in this paragraph.}
-In this paper, we propose a system that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, and enables the DSO to regulate the trading platform and enforce certain safety rules.
+In this paper, we propose a solution that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, and enables the DSO to regulate the trading platform and enforce certain safety rules.
 \Aron{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}
-First, we describe the basic components of a transactive microgrid, and we formulate security, safety, and privacy requirements. 
+First, we describe the basic components of a transactive IoT microgrid, and we formulate security, safety, and privacy requirements. 
 Then, we introduce a decentralized system for transactive microgrids based on distributed ledgers, and describe in detail the transactions and services that are used to implement this system.

### 2017-06-07 papers/IoT2017/paper.tex
no message
final

@@
 % so you remain anonymous.
-\def\plaintitle{Private Blockchains for Transactive Energy:\\Security, Privacy, and Safety}
+\def\plaintitle{Providing Privacy, Safety, and Security in IoT-Based Transactive Energy Systems}
 \def\plainauthor{First Author, Second Author, Third Author}
@@
 To tackle these challenges, decentralized IoT solutions are emerging, which may arrange local communities into transactive microgrids.
-Within a transactive microgrid, consumers with energy generation and storage capabilities may trade energy with each other, thereby smoothing the load on the main grid using local supply.
+Within a transactive microgrid, consumers with energy generation and storage capabilities can trade energy with each other, thereby smoothing the load on the main grid using local supply.
 However, providing security, safety, and privacy in a decentralized and transactive energy system is very challenging.

### 2017-06-07 papers/IoT2017/related.tex
final

@@
 New privacy concerns arise with the continuing adoption of smart grids.
-In addition to both old and new security threats, such as energy theft and smart meter malware, McDaniel and McLaughlin discuss the privacy concerns of energy usage profiling that smart grids could potentially enable~\cite{mcdaniel2009security}.
+In addition to both old and new security threats, such as energy theft and smart-meter malware, McDaniel and McLaughlin discuss the privacy concerns of energy usage profiling that smart grids could potentially enable~\cite{mcdaniel2009security}.
 Several approaches have been investigated as potential means to provide privacy protections for smart grid users.
@@
 Some approaches look to the use of protocols and/or frameworks to help protect privacy.
-Rajagopalan et al.\ use tools from information theory to present a framework, which abstracts both the privacy and the utility requirements of smart meter data~\cite{rajagopalan2011smart,sankar2013smart}.
+Rajagopalan et al.\ use tools from information theory to present a framework, which abstracts both the privacy and the utility requirements of smart-meter data~\cite{rajagopalan2011smart,sankar2013smart}.
 Their framework leads to a novel tractable privacy-utility tradeoff problem with minimal assumptions.
@@
 Their approach is based on the observation that frequent metering data may be required by an energy distribution network for operational reasons, but it may not necessarily need to be attributable to a specific smart meter.
-The authors describe a method that provides a third-party escrow mechanism for authenticated anonymous meter readings, which are difficult to associate with particular smart meter.
+The authors describe a method that provides a third-party escrow mechanism for authenticated anonymous meter readings, which are difficult to associate with a particular smart meter.
 
 Additionally, other approaches such as additional hardware components are explored for potential privacy gains.
-Varodayan and Khisti study using rechargeable battery for partially protecting the privacy of information contained in a household's electrical load profile~\cite{varodayan2011smart}.
-They show that stochastic battery policies may leak 26\% less information than a best-effort policy, holds the output load constant whenever possible.
-Tan et al.
-study privacy in a smart metering system from an information theoretic perspective in the presence of energy harvesting and storage units~\cite{tan2013increasing}.
+Varodayan and Khisti study using a rechargeable battery for partially protecting the privacy of information contained in a household's electrical load profile~\cite{varodayan2011smart}.
+They show that stochastic battery policies may leak 26\% less information than a best-effort policy, which holds the output load constant whenever possible.
+Tan et al.\ study privacy in a smart metering system from an information theoretic perspective in the presence of energy harvesting and storage units~\cite{tan2013increasing}.
 They show that energy harvesting provides increased privacy by diversifying the energy source, while a storage device can be used to increase both energy efficiency and privacy.
-They show that there exists a trade-off between the information leakage rate and the wasted energy rate, and study the impact of the energy harvesting rate and the size of the storage device on this trade-off.
+% They show that there exists a trade-off between the information leakage rate and the wasted energy rate, and study the impact of the energy harvesting rate and the size of the storage device on this trade-off.
 
 Our solution extends earlier work by considering a decentralized IoT system for transactive energy, and addressing the novel privacy threat posed by trading.
-In other words, while earlier results protected prosumers' privacy from the DSO, we protect privacy from other prosumers as well as from outside attackers.
+In other words, while earlier results protected the prosumers' privacy from the DSO, we protect privacy from other prosumers as well as from outside attackers.
 
-A key element of our approach is the ability to distribute the informtion among peers. For that purpose, we rely on the use of Blockchains. 
-As Blockchain technology continues to develop and mature, new frameworks, services, and protocols are being developed to leverage blockchain's distributed ledger.
+A key element of our approach is the ability to distribute information among peers. For that purpose, we rely on the use of blockchains. 
+As blockchain technology continues to develop and mature, new frameworks, services, and protocols are being developed to leverage blockchain's distributed ledger.
 Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}.
-Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}.
-However, this paper focuses on theoretical aspects of our implementation and as such any one of these distributed ledgers provide the required capabilities.\Abhishek{Aron please see this paragraph}
+Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels, whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}.
+However, this paper focuses on theoretical aspects of our implementation and as such, any one of the distributed ledgers provide the required capabilities.
 

### 2017-06-07 papers/IoT2017/services.tex
final

@@
 Communication anonymity is necessary for anonymous trading, but it is not sufficient: if prosumers used their own accounts to transfer assets, trades would not be anonymous.
-Fortunately, most distributed ledgers allow users to easily generate new addresses\footnote{The usage of the term \emph{address} varies between distributed ledgers, but our system could be implemented using any popular ledger, such as Bitcoin and Ethereum.
-Specifically, we use the term address to denote a possible destination for asset transfers. 
-Assets transferred to an address can be used only by someone who knows the private key of the address (typically, the one who generated the address).} 
+Fortunately, most distributed ledgers allow users to easily generate new addresses %\footnote{The usage of the term \emph{address} varies between distributed ledgers, but our system could be implemented using any popular ledger, such as Bitcoin and Ethereum.
+%Specifically, we use the term address to denote a possible destination for asset transfers. 
+%Assets transferred to an address can be used only by someone who knows the private key of the address (typically, the one who generated the address).} 
 at random.

### 2017-06-07 papers/IoT2017/solution.tex
final

@@
 \center
-\begin{tikzpicture}[x=8cm, y=0.8cm, font=\small,
+\begin{tikzpicture}[x=8cm, y=1.1cm, font=\small,
   nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
@@
 The prosumer transfers the production asset to the mixing service using an \emph{energy and financial transaction} \circled{2}, which is also recorded on the distributed ledger.
-In turn, the mixing service transfers the production asset to an \emph{anonymous address} \circled{3}\Aron{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}, which is randomly generated and controlled by the prosumer.
+In turn, the mixing service transfers the production asset to an \emph{anonymous address} \circled{3}%\Aron{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}
+, which is randomly generated and controlled by the prosumer.\footnote{The usage of the term \emph{address} varies between distributed ledgers, but our system could be implemented using any popular blockchain, such as Bitcoin and Ethereum.
+Specifically, we use the term address to denote a possible destination for asset transfers. 
+Assets that have been transferred to an address can be used only by someone who ``controls'' the address (typically, the one who generated it), which usually means knowing a private key that corresponds to the address.} % knows the private key of the address (typically, the one who generated the address).}
 Since the mixing service transfers assets from multiple prosumers to multiple anonymous addresses at the same time, and the anonymous addresses were generated at random by the prosumers, the assets cannot be traced back to the original prosumers after mixing.\footnote{Note that prosumers should divide their assets between multiple anonymous addresses; otherwise, each asset might be traced back to its prosumer based on the amount of energy that it contains.}

### 2017-06-16 papers/IoT2017/intro.tex
updates

@@
 Power grids are undergoing major changes due to rapid
-acceleration in renewable energy resources, such as wind and solar power \cite{5430489}. % \cite{EIA2014}
-For example, 
-$4,\!143$ megawatts of solar panels were installed in the third quarter of 2016 \cite{seia}.
-This capacity is estimated to grow from 4\% in 2015 to 29\% in 2040 \cite{Randal}.
-At the same time, battery technology costs per kWh have been dropping significantly \cite{stock2015powerful}, reaching grid parity.
-% \cite{bronski2015economics}
-This massive integration of renewable energy requires detailed information and visibility into all aspects of the network, making it difficult to manage, especially in the presence of variable distributed energy resources \cite{7452738}.
-Therefore, a different vision for the future of power-grid operations is emerging: a decentralized system in which local communities are arranged in microgrids \cite{rahimi2012transactive}.
-In this vision, energy generation, transmission, distribution and even storage (e.g., electric vehicles in a community) can be strategically used to balance load and demand spikes.
+acceleration in renewable energy resources, such as wind and solar power \cite{5430489}. 
+% \cite{EIA2014}
+For example, $4,\!143$ megawatts of solar panels were installed in the
+third quarter of 2016 \cite{seia}. This capacity is estimated to grow
+from 4\% in 2015 to 29\% in 2040 \cite{Randal}. At the same time,
+battery technology costs per kWh have dropped significantly
+\cite{stock2015powerful}, reaching grid parity.
+%\cite{bronski2015economics}
+This massive integration of renewable energy requires detailed
+information and visibility into all aspects of the network, making it
+hard to manage, especially in the presence of variable distributed
+energy resources \cite{7452738}. A different vision for the future of
+power-grid operations is therefore emerging: {\em a decentralized
+  system in which local communities are arranged in microgrids}
+\cite{rahimi2012transactive}. In this vision, energy generation,
+transmission, distribution, and even storage (\em{e.g.}, electric
+vehicles in a community) can be strategically used to balance load and
+demand spikes.
 
-Furthering the concept of microgrids, transactive energy models have been proposed to support the next distribution system evolution \cite{kok2016society,cox2013structured,melton2013gridwise}.
-Transactive energy is a set of market based constructs for dynamically balancing the demand and supply across the electrical infrastructure \cite{melton2013gridwise}.
-In this approach, customers on the same feeder (i.e.
-sharing a power line link) can operate in an open market, trading and exchanging generated energy locally.
-Distribution System Operators (DSO) can be the custodian of this market, while still meeting the net demand \cite{7462854}.
-For example, the Brooklyn Microgrid, which was developed by LO3 Energy as a pilot project, is a peer-to-peer market for locally generated renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}
+Furthering the concept of microgrids, transactive energy models have
+been proposed to support the next distribution system evolution
+\cite{kok2016society,cox2013structured,melton2013gridwise}. Transactive
+energy is a set of market-based constructs for dynamically balancing
+the demand and supply across the electrical infrastructure
+\cite{melton2013gridwise}. In this approach, customers on the same
+feeder (\em{i.e.}, those sharing a power line link) can operate in an
+open market, trading and exchanging generated energy
+locally. Distribution System Operators (DSOs) can be the custodian of
+this market, while still meeting the net demand \cite{7462854}. For
+example, the Brooklyn Microgrid, which was developed by LO3 Energy as
+a pilot project, is a peer-to-peer market for locally generated
+renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}
 
-On one hand, transactive energy is a decentralized power system controls problem \cite{7452738}, requiring strategic microgrid control to maintain the stability of the community and the utility.
-On the other hand, it is a distributed market problem where erroneous as well as malicious transactions can create a gap between demand and supply, eventually destabilizing the system.
-However, in both cases, this system requires a distributed  infrastructure comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator, which has to provide the necessary computation fabric to support the interplay between the energy control and the fiscal market challenges.
-Recently, demand-response systems have been enabled as applications of IoT in smart grid~\cite{Haider2016166}. Transactive energy systems are the next step for smart grid.
+On one hand, transactive energy is a decentralized power system
+controls problem \cite{7452738}, requiring strategic microgrid control
+to maintain the stability of the community and the utility. On the
+other hand, it is a distributed market problem where erroneous---as
+well as malicious---transactions can create a gap between demand and
+supply, eventually destabilizing the system. In both cases, however,
+this system requires a distributed infrastructure comprising of smart
+meters, feeders, smart inverters, utility substations, the utility
+central offices, and the transmission system operator, which must
+provide the necessary computation fabric to support the interplay
+between the energy control and the fiscal market challenges.
+Recently, demand-response systems have been enabled as applications of
+IoT in smart grid~\cite{Haider2016166}. Transactive energy systems are
+the next step for the smart grid.
 % With the advent of IoT-based solutions in smart-grid  dynamic demand response systems, which are a precursor to transactive sytems have been made possible.
 
-In general, the focus is now on creating a distributed IoT infrastructure%  comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator
-, which provides the necessary computation fabric to support the interplay between energy control and fiscal market challenges, as shown by Volttron \cite{katipamula2016volttron},  OpenFMB \cite{gunthersmart}, and the Resilient Information Architecture Platform for Smart Grid (RIAPS) \cite{eisele2017riaps,Scott2017ICCPS}.
-For instance, the latter is a distributed IoT  ``operating system'' that provides the foundations for all algorithms, isolates the hardware details from the algorithms, and provides essential mechanisms for resource management, fault tolerance, and security.
-However, most of these efforts are focusing on the computation and distribution of information and, and they do not provide the key support required to handle the privacy challenges that arise from the required information exchange in this decentralized transactive system.
+In general, the focus is now on creating a distributed IoT
+infrastructure
+%  comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator
+that provides the necessary computation fabric to support the
+interplay between energy control and fiscal market challenges, as
+shown by Volttron \cite{katipamula2016volttron}, OpenFMB
+\cite{gunthersmart}, and the Resilient Information Architecture
+Platform for Smart Grid (RIAPS)
+\cite{eisele2017riaps,Scott2017ICCPS}. For instance, the latter is a
+distributed IoT operating system that provides the foundations for all
+algorithms, isolates the hardware details from the algorithms, and
+provides essential mechanisms for resource management, fault
+tolerance, and security. Most of these efforts, however, focus on the
+computation and distribution of information, but do not provide the
+support required to handle the privacy challenges that arise from the
+required information exchange in this decentralized transactive
+system.
 
-In this paper, we assume the existence of the IoT infrastructure and specifically focus on the following privacy challenges.
+This paper assumes the existence of a distributed IoT infrastructure
+and specifically focus on the following privacy challenges:
 %
@@
 \begin{itemize}[itemsep=0.25\parskip,topsep=-0.5\parskip]
-\item Firstly, since prosumers\footnote{We refer to customers as \emph{prosumers} to emphasize that they can not only consume energy, but may also produce it.}  may purchase energy from each other in a transactive microgrid, transactions may inadvertently reveal the prosumers' detailed energy usage patterns to other prosumers within the microgrid.
-Addressing this issue in a decentralized trading system is quite challenging as it requires hiding the identities of trade partners from each other.
-In comparison, secure smart metering reveals the prosumers' energy usage patterns only to the operator. 
-\item Secondly, \Abhishek{Is this not related to the first point?
-Perhaps the first point can be just about identity and second point can be specifically about consumption patterns.}\Aron{The first point is about to whom information might be leaked, and the second point is about the type of information.
-I'll make this more clear.} transactions may reveal the future energy usage of a prosumer, which could be used to infer private information.
-For example, a smart home may know that its inhabitants will go out in the evening (e.g., by looking at their calendar), and it may trade energy futures accordingly in the morning.
-Without adequate privacy measures, these trades may reveal to other prosumers in the microgrid that the inhabitants will not be at home later.
-Note that energy futures, whose delivery may happen several hours after when the transaction is made, can play a very important role in predicting and controlling microgrid load.
-In comparison, smart metering reveals only current (or past) usage.
-\item Thirdly, transactions and energy usage data in a transactive microgrid are much richer sources of information than the simple energy usage data collected by smart meters.
-More specifically, the information available in a transactive microgrid is a superset of what is available from smart metering, and it may be used to infer personal information, such as risk propensity and financial standing.
+% Abhishek, can you please add a pithy summary of this challenge?
+\item \bf{Pithy challenge summary needed.} Since prosumers\footnote{We
+  refer to customers as \emph{prosumers} to emphasize that they can
+  not only consume energy, but may also produce it.} may purchase
+  energy from each other in a transactive microgrid, transactions may
+  inadvertently reveal the prosumers' detailed energy usage patterns
+  to other prosumers within the microgrid.  Addressing this issue in a
+  decentralized trading system is hard as it requires hiding the
+  identities of trade partners from each other. In comparison, secure
+  smart metering reveals the prosumers' energy usage patterns only to
+  the operator.
+
+% Abhishek, can you please add a pithy summary of this challenge?
+\item \bf{Pithy challenge summary needed.} \Abhishek{Is this not
+  related to the first point?  Perhaps the first point can be just
+  about identity and second point can be specifically about
+  consumption patterns.}\Aron{The first point is about to whom
+  information might be leaked, and the second point is about the type
+  of information. I'll make this more clear.}  Transactions may reveal
+  the future energy usage of a prosumer, which could be used to infer
+  private information.  For example, a smart home may know that its
+  inhabitants will go out in the evening (\em{e.g.}, by looking at
+  their calendar), and it may trade energy futures accordingly in the
+  morning.  Without adequate privacy measures, these trades may reveal
+  to other prosumers in the microgrid that the inhabitants will not be
+  at home later, which could be a security risk.  Note that energy
+  futures, whose delivery may happen several hours after when the
+  transaction is made, can play a important role in predicting and
+  controlling microgrid load.  In comparison, smart metering reveals
+  only current (or past) usage.
+
+% Abhishek, can you please add a pithy summary of this challenge?
+\item \bf{Pithy challenge summary needed.} Transactions and energy
+  usage data in a transactive microgrid are much richer sources of
+  information than the simple energy usage data collected by smart
+  meters.  More specifically, the information available in a
+  transactive microgrid is a superset of what is available from smart
+  metering, and it may be used to infer personal information, such as
+  risk propensity and financial standing.
 \end{itemize}
@@
 
-Before transactive energy system can be deployed in practice, we must address these privacy issues.
-However, this is a challenging task, as the system also has to satisfy security and safety requirements, which often conflict with privacy goals.
-For example, to prevent a prosumer from destabilizing the grid through careless of malicious energy trading, the system must check all of the prosumer's transactions.
-In a decentralized system, this requires disseminating information, which could be used to infer the prosumer's future energy consumption.
+Before transactive energy system can be deployed widely in practice,
+we must address the privacy issues described above.  Addressing these
+issues is hard, however, since solutions also must satisfy security
+and safety requirements, which often conflict with privacy goals.  For
+example, to prevent a prosumer from destabilizing the grid through
+careless of malicious energy trading, the system must check all of the
+prosumer's transactions.  In a decentralized system, this requires
+disseminating information, which could be used to infer the prosumer's
+future energy consumption.
 
-\Abhishek{Can we cite an example of such a service?}
-\Aron{I am not sure what you mean by ``such a service.''}
-\Abhishek{We should connect the paper and our work back to IoT in this paragraph.}
-In this paper, we propose a solution that enables trading energy futures in a secure and verifiable manner, preserves the prosumers' privacy, and enables the DSO to regulate the trading platform and enforce certain safety rules.
-\Aron{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}
-First, we describe the basic components of a transactive IoT microgrid, and we formulate security, safety, and privacy requirements. 
-Then, we introduce a decentralized system for transactive microgrids based on distributed ledgers, and describe in detail the transactions and services that are used to implement this system.
-Next, we discuss how the system satisfies the security, safety, and privacy requirements.
-Finally, we give a brief overview of related work and offer concluding remarks.
+\Abhishek{Can we cite an example of such a service?}  \Aron{I am not
+  sure what you mean by ``such a service.''}  \Abhishek{We should
+  connect the paper and our work back to IoT in this paragraph.}  This
+paper proposes a solution that (1) enables trading energy futures in a
+secure and verifiable manner, (2) preserves prosumer privacy, and (3)
+enables DSOs to regulate the trading platform and enforce certain
+safety rules.  \Aron{Since SIGCHI does not have section numbers, this
+  paragraph, which describes the organization of the paper, is not
+  very clear.}  We first describe the basic components of a
+transactive IoT microgrid and formulate security, safety, and privacy
+requirements.  We next introduce a decentralized system for
+transactive microgrids based on distributed ledgers and describe the
+transactions and services used to implement this system.  We then
+discuss how the system satisfies the security, safety, and privacy
+requirements.  Finally, we give a brief overview of related work and
+offer concluding remarks.

### 2017-06-16 papers/IoT2017/paper.tex
updates

@@
 \begin{abstract}
-Power grids are undergoing major changes due to rapid growth in renewable energy resources and improvements in battery technology.
-While these changes enhance sustainability and efficiency, they also create significant management challenges as the complexity of power systems increases.
-To tackle these challenges, decentralized IoT solutions are emerging, which may arrange local communities into transactive microgrids.
-Within a transactive microgrid, consumers with energy generation and storage capabilities can trade energy with each other, thereby smoothing the load on the main grid using local supply.
-However, providing security, safety, and privacy in a decentralized and transactive energy system is very challenging.
-On the one hand, consumers' personal information must be protected from their trade partners and
-\Abhishek{To what extent is this different that the information already known by the system operator?
-Is this more related to the ``real-time'' nature of transactive information?
-Rather than aggregative total information which is available at the end of billing cycle today.} \Aron{Do we need to detail this in the abstract?}\Abhishek{we dont have to} the system operator.
-On the other hand, the system must be protected from careless or malicious trading, which could destabilize the entire grid. 
-In this paper, we design a secure and safe solution for transactive microgrids, which enables consumers to trade energy without sacrificing their privacy.
-Our solution builds on distributed ledgers, such as blockchains, and provides anonymity for communication, bidding, and trading.
+Power grids are undergoing major changes due to rapid growth in
+renewable energy resources and improvements in battery technology.
+While these changes enhance sustainability and efficiency, they also
+create significant management challenges as the complexity of power
+systems increases.  To tackle these challenges, decentralized
+Internet-of-Things (IoT) solutions are emerging, which may arrange
+local communities into transactive microgrids.  Within a transactive
+microgrid, consumers with energy generation and storage capabilities
+can trade energy with each other, thereby smoothing the load on the
+main grid using local supply.  It is hard, however, to provide
+security, safety, and privacy in a decentralized and transactive
+energy system.  On the one hand, consumers' personal information must
+be protected from their trade partners and \Abhishek{To what extent is
+  this different that the information already known by the system
+  operator? Is this more related to the ``real-time'' nature of
+  transactive information?  Rather than aggregative total information
+  which is available at the end of billing cycle today.} \Aron{Do we
+  need to detail this in the abstract?}\Abhishek{we dont have to} the
+system operator.  On the other hand, the system must be protected from
+careless or malicious trading, which could destabilize the entire
+grid.  This paper describes our secure and safe solution for
+transactive microgrids, which enables consumers to trade energy
+without sacrificing their privacy.  Our solution builds on distributed
+ledgers, such as blockchains, and provides anonymity for
+communication, bidding, and trading.
 \end{abstract}

### 2017-06-16 papers/IoT2017/prelim.tex
final
updates

@@
 \section{Preliminaries and Requirements}
+
+This section describes the basic components of a transactive IoT
+microgrid and formulates security, safety, and privacy requirements.
 
@@
 \Abhishek{This is the perfect paragraph to define transactive microgrid as a special application of IoT spread over a large area. Perhaps we can find a citation that makes this point.}
-We begin by describing a basic system model of transactive microgrids.
-We discuss the following components: a distributed ledger for recording transactions, a bid storage service that facilitates finding trade partners, a microgrid controller for regulating the microgrid load, and smart meters for measuring the prosumers' energy production and consumption.
+We begin by describing a basic system model of decentralized
+% Abhishek, if there's room can we add a diagram showing how all these
+% components relate to each other?
+transactive IoT microgrids.  We discuss the following components: a
+distributed ledger for recording transactions, a bid storage service
+that facilitates finding trade partners, a microgrid controller for
+regulating the microgrid load, and smart meters for measuring the
+prosumers' energy production and consumption.
 
 \subsubsection{Distributed Ledger}
-The ledger permanently stores transactions that specify energy trades, change regulatory policies for the microgrid, etc.
-For providing security and safety, it is crucial that transactions are non-malleable, that is, once a transaction has been recorded, it cannot be modified or removed from the ledger.
-However, for the sake of fault tolerance, the ledger also needs to be distributed.
-Since a distributed ledger is maintained by multiple nodes, a key implementation requirement is reaching consensus on which transactions are valid and stored on the ledger.
-Further, this consensus must be reached quickly and reliably, even in the presence of faulty or malicious (e.g., compromised) ledger nodes.
-In this paper, we assume that a distributed ledger service is available, but do not make any assumptions about the implementation, such as the particulars of the consensus algorithm.
-In practice, a distributed ledger can be implemented using, for example, \emph{blockchains} with proof-of-stake consensus or Practical Byzantine Fault Tolerance algorithm~\cite{castro1999practical}.
+This ledger permanently stores transactions that specify energy
+trades, change regulatory policies for the microgrid, etc.  For
+providing security and safety, it is crucial that transactions are
+non-malleable, \em{i.e.}, after a transaction has been recorded, it
+cannot be modified or removed from the ledger.  To enhance fault
+tolerance, however, the ledger also should be distributed.
+
+Since a distributed ledger is maintained by multiple nodes, a key
+requirement is reaching consensus on which transactions are valid and
+stored on the ledger.  Moreover, this consensus must be reached
+quickly and reliably, even in the presence of faulty or malicious
+(\em{e.g.}, compromised) ledger nodes.  This paper assumes that a
+distributed ledger service is available, but makes no assumptions
+about the ledger implementation, such as the particulars of the
+consensus algorithm.  In practice, a distributed ledger can be
+implemented using, \em{e.g.}, \emph{blockchains} with proof-of-stake
+consensus or a practical Byzantine fault tolerance
+algorithm~\cite{castro1999practical}.
 
 \subsubsection{Bid Storage Service}
-Although prosumers trade energy with each other directly (i.e., without a middleman), for the sake of scalability, we need a service that enables prosumers to find trade partners.
+Although prosumers trade energy with each other directly (\em{i.e.},
+without a middleman), for the sake of scalability, we need a service
+that enables prosumers to find trade partners.
 %A bid storage service receives energy buy and sell bids from prosumers, stores these 
-We assume that there is a bid storage service that allows prosumers to post and read energy \emph{bids} and \emph{asks}.\footnote{A \emph{bid} is an offer to buy at a certain price, while an \emph{ask} is an offer to sell at a certain price.}
-This service relieves prosumers from contacting a large number of potential trade partners, since they only have to communicate with the service in order to discover trade partners.
+We assume that there is a bid storage service that allows prosumers to
+post and read energy \emph{bids} and \emph{asks}.\footnote{A
+  \emph{bid} is an offer to buy at a certain price, while an
+  \emph{ask} is an offer to sell at a certain price.}  This service
+relieves prosumers from contacting a large number of potential trade
+partners since they only communicate with the service to discover
+trade partners.
 %Moreover, in addition to simply storing bids and asks, the service may also find matches in the posted bids and asks, and it may notify the posting prosumers of the trade opportunity.
-Note that
-for the sake of scalability and reliability, this service can also be implemented in a distributed manner, using multiple nodes.
+To enhance scalability and reliability, this service can also be
+implemented in a distributed manner, using multiple nodes.
 
 \subsubsection{Microgrid Controller}
-The microgrid controller is responsible for stabilizing the load within the microgrid and for influencing it based on the predicted future load within the microgrid and the rest of the grid. 
-To this end, the controller first predicts load in the microgrid based on 1) bids and asks in the bid storage and 2) outstanding energy trades in the ledger.
-By combining this  with the prediction for the rest of the grid, the controller produces a control signal that specifies how much the microgrid load should be decreased or increased.
-Finally, based on this signal, the controller updates the price policy for the microgrid to influence energy production and consumption.
-We also assume the presence of a secondary controller that balances voltage and frequency in the microgrid.
+The microgrid controller stabilizes the load within the microgrid
+based on the predicted future load within the microgrid and the rest
+of the grid.  The controller thus first predicts load in the microgrid
+based on (1) bids and asks in the bid storage and (2) outstanding
+energy trades in the ledger.  By combining this information with the
+prediction for the rest of the grid, the controller produces a control
+signal that specifies how much the microgrid load should be decreased
+or increased.  Based on this signal, the controller then updates the
+price policy for the microgrid to influence energy production and
+consumption.  We also assume the presence of a secondary controller
+that balances voltage and frequency in the microgrid.
 
 \subsubsection{Smart Meters}
-To measure the prosumers' energy production and consumption, a smart meter must be deployed at each prosumer.
-In practice, these smart meters must be tamper resistant to prevent prosumers from ``stealing electricity'' by tampering with their meters.
-Once a smart meter has measured the net amount of energy consumed by the prosumer in some time interval, it can send this information to the DSO for billing purposes.
+To measure the prosumers' energy production and consumption, a smart
+meter must be deployed at each prosumer.  In practice, these smart
+meters must be tamper resistant to prevent prosumers from ``stealing
+electricity'' by tampering with their meters.  After a smart meter has
+measured the net amount of energy consumed by the prosumer in some
+time interval, it can send this information to the DSO for billing
+purposes.
 
 \subsection{Requirements}
-Next, we discuss the security, safety, and privacy requirements that must be satisfied by a transactive energy IoT system.
+We now discuss the security, safety, and privacy requirements that
+must be satisfied by a transactive energy IoT system.
 
 \subsubsection{Security}
-Security requirements ensure primarily that prosumers are billed correctly, but they also provide necessary prerequisite properties for safety.
+Security requirements ensure primarily that prosumers are billed
+correctly, but they also provide necessary prerequisite properties for
+safety.
 %Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.
@@
 \begin{itemize}[noitemsep,topsep=-\parskip]
-\item prosumers are billed correctly based on the energy prices set by the DSO, their energy trades, and their actual energy production and consumption measured by the smart meters, % (i.e., prosumers or outside attackers cannot tamper with energy production, consumption, and financial balances) % attackers cannot tamper with energy production and consumption balances or financial balances),
-\item prosumers or outside attackers cannot change microgrid regulatory policies that are set by the DSO,
-\item prosumers cannot back out of trades unilaterally, and they cannot tamper with other prosumers' trading or bidding,
-\item financial and physical impact of compromised or faulty nodes is limited, and nodes can be banned by the DSO.
+\item prosumers are billed correctly based on the energy prices set by
+  the DSO, their energy trades, and their actual energy production and
+  consumption measured by the smart meters,
+% (i.e., prosumers or outside attackers cannot tamper with energy production, consumption, and financial balances) % attackers cannot tamper with energy production and consumption balances or financial balances),
+\item prosumers or outside attackers cannot change microgrid
+  regulatory policies that are set by the DSO, 
+\item prosumers cannot back out of trades unilaterally, and they
+  cannot tamper with other prosumers' trading or bidding,
+\item financial and physical impact of compromised or faulty nodes is
+  limited, and nodes can be banned by the DSO. 
 \end{itemize}
@@
 \subsubsection{Safety}
-A careless or malicious prosumer may destabilize the grid by promising to produce (or consume) a large amount of energy, but failing to deliver.
-A significant difference between promised and delivered energy production (or consumption) can result in a large gap between actual production and consumption in the microgrid, which threatens the stability of not only the microgrid but also the main power grid.
-Consequently, prosumers should not be able to trade large amounts of energy, which they are unlikely to deliver.
+A careless or malicious prosumer may destabilize the grid by promising
+to produce/consume a large amount of energy, but failing to
+deliver/utilize it.  A significant difference between promised and
+delivered energy production/consumption can result in a large gap
+between actual production and consumption in the microgrid, which
+threatens the stability of not only the microgrid but also the main
+power grid.  Prosumers should therefore not be able to trade large
+amounts of energy that they are unlikely to deliver.
 %Trades which are unlikely to be delivered and would result in a gap between actual production and demand should be prevented.
@@
 \begin{itemize}[noitemsep,topsep=-\parskip]
-\item net amount of energy sold (or bought) by a prosumer is upper bounded (by an amount set by the DSO), where the net amount of energy sold is the difference between the amount of energy sold and bought by the prosumer, and the net amount of energy bought is defined analogously,
-\item energy bids and asks posted by the prosumer are limited in a similar way.
+\item the net amount of energy sold (or bought) by a prosumer is upper
+  bounded (by an amount set by the DSO), where the net amount of
+  energy sold is the difference between the amount of energy sold and
+  bought by the prosumer, and the net amount of energy bought is
+  defined analogously,
+\item the energy bids and asks posted by the prosumer are limited in a
+  similar way.
 \end{itemize}
@@
 \subsubsection{Privacy} 
-Privacy requirements ensure that the prosumers' privacy is not compromised when they participate in energy trading.
-We use non-transactive smart metering as a baseline, and require that the transactive system does not leak any additional information compared to the baseline.
-More specifically, we require that
+Privacy requirements ensure that the prosumers' privacy is not
+compromised when they participate in energy trading.  We use
+non-transactive smart metering as a baseline.  We also require that
+the transactive system does not leak any additional information
+compared to the baseline.  More specifically, we require that
 \begin{itemize}[noitemsep,topsep=-\parskip]
-\item only the corresponding smart meter and the DSO may gain information regarding the amount of energy produced, consumed, bought, or sold by a prosumer,\footnote{Note that this requirement is impossible to satisfy if all other prosumers may collude against one target.
-However, we can assume that the majority of prosumers are non-colluding.}
-\item only the prosumer may know which bids and asks it has posted, and no one can know who traded energy with whom.
+\item only the corresponding smart meter and the DSO may gain
+  information regarding the amount of energy produced, consumed,
+  bought, or sold by a prosumer,\footnote{Note that this requirement
+    is impossible to satisfy if all other prosumers may collude
+    against one target. However, we can assume that the majority of
+    prosumers are non-colluding.}
+\item only the prosumer may know which bids and asks it has posted,
+  and no one can know who traded energy with whom.
 \end{itemize}

### 2017-06-16 papers/IoT2017/analysis.tex
updates

--- 2017-06-05 papers/IoT2017/analysis.tex
@@
 
-In this section, we present a semi-formal analysis of the proposed solution, and show that it satisfies the security, safety, and privacy requirements that were formulated earlier.
+This section presents a semi-formal analysis of our proposed solution
+and show that it satisfies the security, safety, and privacy
+requirements formulated in earlier sections.
 
@@
 \end{itemize}
-Together, these properties ensure that only the right entities may create and sign a transaction, that transactions adhere to the rules of the trading process, and that transactions cannot be tampered with.
-Due to lack of space, we leave a detailed discussion and proof for future work.
+Together, these properties ensure that only the right entities may
+create and sign a transaction, that transactions adhere to the rules
+of the trading process, and that transactions cannot be tampered
+with.\footnote{Due to lack of space, we leave a detailed discussion
+  and proof for future work.}
 
 \subsection{Safety}
-Next, we demonstrate that faulty or malicious prosumers cannot trade excessive amounts of energy if normal prosumers follow the rules of the trading process. 
+We now demonstrate that faulty or malicious prosumers cannot trade
+excessive amounts of energy if normal prosumers follow the rules of
+the trading process.
 %
-First, we can show that the net amount of energy sold by prosumer $i$ for each timestep is at most $\field{MAXEPA}_i$.
-By definition, the amount of energy sold is less than or equal to the amount of EPA obtained by prosumer $i$.
-A prosumer can obtain EPA either by withdrawing from its smart meter or by purchasing form another prosumer.
-From its smart meter, prosumer $i$ can withdraw at most $\field{MAXEPA}_i$. % amount of EPA.
-The prosumer may also buy EPA from another prosumer; however, this constitutes buying energy, which decreases the net amount of energy sold with the same amount.
+First, we show that the net amount of energy sold by prosumer $i$ for
+each timestep is at most $\field{MAXEPA}_i$.  By definition, the
+amount of energy sold is less than or equal to the amount of EPA
+obtained by prosumer $i$.  A prosumer can obtain EPA either by
+withdrawing from its smart meter or by purchasing form another
+prosumer.  From its smart meter, prosumer $i$ can withdraw at most
+$\field{MAXEPA}_i$.
+% amount of EPA.
+Although the prosumer may also buy EPA from another prosumer, this
+constitutes buying energy, which decreases the net amount of energy
+sold with the same amount.
 %However, to obtain more EPA, the prosumer has to buy energy from another prosumer, which would decrease its net energy sold by the same amount.
-Hence, the net amount of energy sold by prosumer $i$ cannot exceed $\field{MAXEPA}_i$.
-By extending the argument, we can show that the net amount of energy sold by a group of prosumers~$G$ cannot exceed $\sum_{i \in G} \field{MAXEPA}_i$.
-Similarly, we can show that the net amount of energy bought by a group of prosumers $G$ cannot exceed $\sum_{i \in G} \field{MAXECA}_i$.
+Hence, the net amount of energy sold by prosumer $i$ cannot exceed
+$\field{MAXEPA}_i$.  By extending the argument, we show that the net
+amount of energy sold by a group of prosumers~$G$ cannot exceed
+$\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, we show that the net
+amount of energy bought by a group of prosumers $G$ cannot exceed
+$\sum_{i \in G} \field{MAXECA}_i$.
 
-Second, we can show that the amount of energy bids (or asks) posted at the same time by prosumer $i$ for each timestep is at most $\field{MAXEPA}_i + \field{MAXECA}_i$.
-Notice that the limit is higher than for net energy sold or bought, since prosumer $i$ may purchase $\field{MAXECA}_i$ amount of EPA (or $\field{MAXEPA}_i$ amount of ECA) from other prosumers, and then post an energy ask (or bid) in the amount of $\field{MAXEPA}_i + \field{MAXECA}_i$.
+We also show that the total amount of energy bids (or asks) posted at
+the same time by prosumer $i$ for each timestep is at most
+$\field{MAXEPA}_i + \field{MAXECA}_i$.  This limit is higher than for
+net energy sold or bought, since prosumer $i$ may purchase
+$\field{MAXECA}_i$ amount of EPA (or $\field{MAXEPA}_i$ amount of ECA)
+from other prosumers, and then post an energy ask (or bid) in the
+amount of $\field{MAXEPA}_i + \field{MAXECA}_i$.
 
 \subsection{Privacy}
-Due to the use of communication anonymity and mixing services, members of a microgrid can observe only the amount of assets withdrawn by a prosumer from its smart meter.
+Due to our use of communication anonymity and mixing services, members
+of a microgrid can observe only the amount of assets withdrawn by a
+prosumer from its smart meter.
 % the amount of energy and financial assets withdrawn by a prosumer.
-Since all trading transactions are anonymous, they do not reveal the actual amount of assets traded by the prosumer.
-If a prosumer does not wish to trade, it can anonymously deposit its assets to a random address that was freshly generated by its smart meter.
-Note that even if a prosumer does not wish to trade, it should always withdraw, mix, and deposit the same amount of assets.
-Otherwise, the lack (or varying amount) of withdrawal would leak information.
+Since all trading transactions are anonymous, they do not reveal the
+actual amount of assets traded by the prosumer.  If a prosumer does
+not wish to trade, therefore, it can anonymously deposit its assets to
+a random address that was freshly generated by its smart meter.  Even
+if a prosumer does not wish to trade, however, it should always
+withdraw, mix, and deposit the same amount of assets.  Otherwise, the
+lack (or varying amount) of withdrawal would leak information.
 
-As for the DSO, it receives the same information from the smart meter as in a non-transactive smart grid (i.e., amount of energy produced and consumed).
-Since trading is anonymous, the DSO learns only the financial balance of the prosumer, which is necessary for billing.
-
-However, we can provide an even higher-level of privacy.
-Since price policies are recorded on the ledger, which the smart meters may read, each prosumer's smart meter may calculate and send the prosumer's monthly bill to the DSO, without revealing the prosumer's energy consumption or production.
-Meanwhile, the DSO can still obtain very detailed load information (including predictions) for the microgrid from the bid storage and the trades recorded on the ledger.
+As for the DSO, it receives the same information from the smart meter
+as in a non-transactive smart grid (\em{i.e.}, amount of energy
+produced and consumed).  Since trading is anonymous, the DSO learns
+only the financial balance of the prosumer, which is necessary for
+billing.  However, we can provide an even higher-level of privacy.  In
+particular, since price policies are recorded on the ledger (which the
+smart meters may read), each prosumer's smart meter may calculate and
+send the prosumer's monthly bill to the DSO, without revealing the
+prosumer's energy consumption or production.  Meanwhile, the DSO can
+still obtain detailed load information (including predictions) for the
+microgrid from the bid storage and the trades recorded on the ledger.

### 2017-06-16 papers/IoT2017/related.tex
updates

@@
 % https://arxiv.org/pdf/1305.0735.pdf
-New privacy concerns arise with the continuing adoption of smart grids.
-In addition to both old and new security threats, such as energy theft and smart-meter malware, McDaniel and McLaughlin discuss the privacy concerns of energy usage profiling that smart grids could potentially enable~\cite{mcdaniel2009security}.
-Several approaches have been investigated as potential means to provide privacy protections for smart grid users.
+New privacy concerns arise with the continuing adoption of smart
+grids. In addition to old and new security threats (such as energy
+theft and smart-meter malware), McDaniel and McLaughlin discuss the
+privacy concerns of energy usage profiling that smart grids could
+potentially enable~\cite{mcdaniel2009security}. Several approaches
+have been investigated as potential means to provide privacy
+protections for smart grid users.
 
-Some approaches look to the use of protocols and/or frameworks to help protect privacy.
-Rajagopalan et al.\ use tools from information theory to present a framework, which abstracts both the privacy and the utility requirements of smart-meter data~\cite{rajagopalan2011smart,sankar2013smart}.
-Their framework leads to a novel tractable privacy-utility tradeoff problem with minimal assumptions.
-Efthymiou and Kalogridis describe a method for securely anonymizing frequent electrical metering data sent by a smart meter~\cite{efthymiou2010smart}.
-Their approach is based on the observation that frequent metering data may be required by an energy distribution network for operational reasons, but it may not necessarily need to be attributable to a specific smart meter.
-The authors describe a method that provides a third-party escrow mechanism for authenticated anonymous meter readings, which are difficult to associate with a particular smart meter.
+Some approaches look to the use of protocols and/or frameworks to help
+protect privacy. Rajagopalan et al.\ use tools from information theory
+to present a framework that abstracts both the privacy and the utility
+requirements of smart-meter
+data~\cite{rajagopalan2011smart,sankar2013smart}. Their framework
+leads to a novel tractable privacy-utility tradeoff problem with
+minimal assumptions. Efthymiou and Kalogridis describe a method for
+securely anonymizing frequent electrical metering data sent by a smart
+meter~\cite{efthymiou2010smart}. Their approach is based on the
+observation that frequent metering data may be required by an energy
+distribution network for operational reasons, but it may not
+necessarily need to be attributable to a specific smart meter. The
+authors describe a method that provides a third-party escrow mechanism
+for authenticated anonymous meter readings, which are hard to
+associate with a particular smart meter.
 
-Additionally, other approaches such as additional hardware components are explored for potential privacy gains.
-Varodayan and Khisti study using a rechargeable battery for partially protecting the privacy of information contained in a household's electrical load profile~\cite{varodayan2011smart}.
-They show that stochastic battery policies may leak 26\% less information than a best-effort policy, which holds the output load constant whenever possible.
-Tan et al.\ study privacy in a smart metering system from an information theoretic perspective in the presence of energy harvesting and storage units~\cite{tan2013increasing}.
-They show that energy harvesting provides increased privacy by diversifying the energy source, while a storage device can be used to increase both energy efficiency and privacy.
-% They show that there exists a trade-off between the information leakage rate and the wasted energy rate, and study the impact of the energy harvesting rate and the size of the storage device on this trade-off.
+Additionally, other approaches such as additional hardware components
+are explored for potential privacy gains. Varodayan and Khisti study
+using a rechargeable battery for partially protecting the privacy of
+information contained in a household's electrical load
+profile~\cite{varodayan2011smart}. They show that stochastic battery
+policies may leak 26\% less information than a best-effort policy,
+which holds the output load constant whenever possible. Tan et
+al.\ study privacy in a smart metering system from an information
+theoretic perspective in the presence of energy harvesting and storage
+units~\cite{tan2013increasing}. They show that energy harvesting
+provides increased privacy by diversifying the energy source, while a
+storage device can be used to increase both energy efficiency and
+privacy.
+% They show that there exists a trade-off between the information
+% leakage rate and the wasted energy rate, and study the impact of the
+% energy harvesting rate and the size of the storage device on this trade-off.
 
-Our solution extends earlier work by considering a decentralized IoT system for transactive energy, and addressing the novel privacy threat posed by trading.
-In other words, while earlier results protected the prosumers' privacy from the DSO, we protect privacy from other prosumers as well as from outside attackers.
+Our solution extends this earlier work by considering a decentralized
+IoT system for transactive energy, and addressing the novel privacy
+threat posed by trading. In particular, while earlier results
+protected the prosumers' privacy from the DSO, we protect privacy from
+other prosumers as well as from outside attackers.
 
-A key element of our approach is the ability to distribute information among peers. For that purpose, we rely on the use of blockchains. 
-As blockchain technology continues to develop and mature, new frameworks, services, and protocols are being developed to leverage blockchain's distributed ledger.
-Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}.
-Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels, whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}.
-However, this paper focuses on theoretical aspects of our implementation and as such, any one of the distributed ledgers provide the required capabilities.
+A key element of our approach is the ability to distribute information
+among peers via blockchains.  As blockchain technology develops and
+matures, new frameworks, services, and protocols are being developed
+to leverage blockchain's distributed ledger. For example, Hyperledger
+Fabric is a platform for distributed ledger solutions, which was
+designed to support pluggable implementations of different
+components~\cite{hyperledger2017fabric}. Bitcoin Lightning Network is
+decentralized system, in which transactions are sent over a network of
+micropayment channels, whose transfer of value occurs
+off-blockchain~\cite{poon2016bitcoin}. Since this paper focuses on
+theoretical foundations of our implementation, any of these
+distributed ledgers provide the required capabilities.
 

### 2017-06-16 papers/IoT2017/services.tex
updates

@@
 
-In this subsection, we describe the various services that are provided in our system. %on which transactions are built and which build on transactions.
-We have already discussed the distributed ledger, which permanently stores valid transactions.
-Now, we will introduce the anonymous communication service, the mixing service for transaction anonymity, the anonymous bid storage, and smart-meter based billing.
+We now describe the various services that are provided in our system.
+%on which transactions are built and which build on transactions.
+Earlier we discussed the distributed ledger, which permanently stores
+valid transactions.  Below we introduce the anonymous communication
+service, the mixing service for transaction anonymity, the anonymous
+bid storage, and smart-meter based billing.
 
 \subsubsection{Communication Anonymity}
-Firstly, we must provide an anonymous communication layer, on which we can build all the other services in our system.
-Without this communication layer, transactions and bids could be easily de-anonymized based on their sources' network identifiers (e.g., IP or MAC addresses).
+The anonymous communication layer is the infrastructure upon which all
+other services in our system are built.  Without this communication
+layer, transactions and bids could be easily de-anonymized based on
+their sources' network identifiers (\em{e.g.}, IP or MAC addresses).
 
-We can employ well-known and widely used techniques for anonymous communication, such as \emph{onion routing}~\cite{reed1998anonymous}.
-To build an onion network, the smart meters, prosumers, and other devices can act as onion routers, and the list of onion routers in a microgrid can be published on the ledger.
-In practice, this service can be built on 
+We employ well-known and widely used techniques for anonymous
+communication, such as \emph{onion routing}~\cite{reed1998anonymous}.
+To build an onion network, the smart meters, prosumers, and other
+devices can act as onion routers, and the list of onion routers in a
+microgrid can be published on the ledger.  In practice, this service
+is built on
 %In our first implementation, we can use
- the free and open-source Tor software with private Directory Authorities.
-In this case, anonymous communication identifiers in bids and asks correspond to public-keys that identify Tor hidden services.
+the free and open-source Tor software with private Directory
+Authorities.  In this case, anonymous communication identifiers in
+bids and asks correspond to public-keys that identify Tor hidden
+services.
 % ritter.vg: "run your own tor network"
@@
 \subsubsection{Transaction Anonymity}
-Communication anonymity is necessary for anonymous trading, but it is not sufficient: if prosumers used their own accounts to transfer assets, trades would not be anonymous.
-Fortunately, most distributed ledgers allow users to easily generate new addresses %\footnote{The usage of the term \emph{address} varies between distributed ledgers, but our system could be implemented using any popular ledger, such as Bitcoin and Ethereum.
+Communication anonymity is necessary, but not sufficient, for
+anonymous trading. In particular, if prosumers used their own accounts
+to transfer assets, their trades would not be anonymous.  Fortunately,
+most distributed ledgers allow users to easily generate new addresses
+%\footnote{The usage of the term \emph{address} varies between distributed ledgers, but our system could be implemented using any popular ledger, such as Bitcoin and Ethereum.
 %Specifically, we use the term address to denote a possible destination for asset transfers. 
 %Assets transferred to an address can be used only by someone who knows the private key of the address (typically, the one who generated the address).} 
-at random.
-Since these addresses are generated randomly, they are anonymous in the sense that no one can tell who generated them.
-However, if prosumers simply transferred assets to these addresses, they could be easily de-anonymized by tracing the assets back to the prosumers.
+at random, so they are anonymous in the sense that no one can tell who
+generated them.  If prosumers simply transferred assets to these
+addresses, however, they could be easily de-anonymized by tracing the
+assets back to the prosumers.
 
-To prevent this, prosumers transfer assets to their anonymous addresses through a \emph{mixing service}. 
-The mixing service prevents tracing the assets back to their original owners by mixing together multiple incoming transfers and multiple outgoing transfers, thereby hiding the connections between the prosumers and the anonymous addresses.
-In practice, a mixing service can be implemented using multiple approaches.
-The simplest one is to use a \emph{trusted third party}, called a cryptocurrency tumbler, which can receive and send assets.
-However, anonymity in this case depends on the trustworthiness and reliability of the third party, who could easily de-anonymize the addresses.
-A more secure approach is to used decentralized protocols, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
-These protocols enable participants to mix assets with each other, thereby eliminating the need for a trusted third party. %, which would constitute a single point of failure.
-Some newer cryptocurrencies, such as Zerocoin~\cite{miers2013zerocoin},  provide built-in mixing services, which are often based on cryptographic principles and proofs.
+To prevent this de-anonymization, prosumers transfer assets to their
+anonymous addresses through a \emph{mixing service}.  The mixing
+service prevents tracing assets back to their original owners by
+mixing together multiple incoming transfers and multiple outgoing
+transfers. This service thus hides the connections between the
+prosumers and the anonymous addresses.
 
+A mixing service can be implemented using multiple approaches.  The
+simplest one is to use a \emph{trusted third party}, called a
+cryptocurrency tumbler, which can receive and send assets.  Anonymity
+in this case, however, depends on the trustworthiness and reliability
+of the third party, who could easily de-anonymize the addresses.  A
+more secure approach is to used decentralized protocols, such as
+CoinShuffle~\cite{ruffing2014coinshuffle} or
+Xim~\cite{bissias2014sybil}.  These protocols enable participants to
+mix assets with each other, thereby eliminating the need for a trusted
+third party.
+%, which would constitute a single point of failure.
+Some newer cryptocurrencies, such as
+Zerocoin~\cite{miers2013zerocoin}, provide built-in mixing services,
+which are often based on cryptographic principles and proofs.
+
+% Abhishek, what does \begin{comment} mean in this context?
 \begin{comment}
-We must provide prosumers with the ability to create and publish transactions anonymously.
-More specifically, prosumers should be able to purchase or sell energy without revealing their identity; however, these transaction must also be verifiable and enforceable.
+We must provide prosumers with the ability to create and publish
+transactions anonymously.  More specifically, prosumers should be able
+to purchase or sell energy without revealing their identity; however,
+these transaction must also be verifiable and enforceable.
 
@@
 \begin{itemize}
-\item Mixing services (also known as tumblers) mix potentially identifiable assets on a blockchain with others, thereby preventing tracing individual assets back to their original source. 
-In our case, assets to be mixed include virtual balances of fiat currencies as well as energy production and consumption.
-\item Cryptographic anonymity for transactions is provided, for example, by Zerocoin~\cite{miers2013zerocoin}. Similarly to mixing service, Zerocoin can prevent tracing assets on a blockchain.
+\item Mixing services (also known as tumblers) mix potentially
+  identifiable assets on a blockchain with others, thereby preventing
+  tracing individual assets back to their original source.  In our
+  case, assets to be mixed include virtual balances of fiat currencies
+  as well as energy production and consumption.
+\item Cryptographic anonymity for transactions is provided, for
+  example, by Zerocoin~\cite{miers2013zerocoin}. Similarly to mixing
+  service, Zerocoin can prevent tracing assets on a blockchain.
 \end{itemize}
-Using the above techniques, we can enable prosumers to trade energy anonymously (i.e., without revealing their true identities), but at the same time prevent them from altering their energy or financial balances without a valid transaction.
+Using the above techniques, we can enable prosumers to trade energy
+anonymously (i.e., without revealing their true identities), but at
+the same time prevent them from altering their energy or financial
+balances without a valid transaction.
 
-However, we must also ensure that 1) smart meters know the amount of energy purchased or sold by their prosumer and 2) prosumers cannot purchase or sell more energy than their capacity.
-To satisfy both of these constraints, all energy trades must start with the prosumer withdrawing a certain amount of energy production or consumption from its smart meter:
+However, we must also ensure that 1) smart meters know the amount of
+energy purchased or sold by their prosumer and 2) prosumers cannot
+purchase or sell more energy than their capacity.  To satisfy both of
+these constraints, all energy trades must start with the prosumer
+withdrawing a certain amount of energy production or consumption from
+its smart meter:
 \begin{itemize}
-\item If a prosumer wishes to sell energy, it must first withdraw an energy asset from its smart meter using a blockchain transaction.
-This transaction must be signed by the smart meter, which enables the smart meter to 1) keep track of the amount of energy traded by the prosumer as well as to 2) enforce safety requirements by limiting the amount of energy that can be withdrawn.
-\item If a prosumer wishes to buy energy, it must first withdraw an energy consumption asset from its smart meter in a way similar to withdrawing an energy production asset.
+\item If a prosumer wishes to sell energy, it must first withdraw an
+  energy asset from its smart meter using a blockchain transaction.
+  This transaction must be signed by the smart meter, which enables
+  the smart meter to 1) keep track of the amount of energy traded by
+  the prosumer as well as to 2) enforce safety requirements by
+  limiting the amount of energy that can be withdrawn.
+\item If a prosumer wishes to buy energy, it must first withdraw an
+  energy consumption asset from its smart meter in a way similar to
+  withdrawing an energy production asset.
 \end{itemize}
@@
 \subsubsection{Bidding Anonymity}
-Finally, we must enable prosumers to anonymously post energy bids and asks on the bid storage service.
-An anonymous bid (or ask) contains an ECA (or EPA), a price, and an anonymous communication identifier (e.g., Tor hidden service), which can be used to contact the bidding (or asking) prosumer.
-To enforce safety requirements, the bid storage service must verify that the prosumer actually owns the asset to be traded.
-To this end, the prosumer first has to prove that it controls the anonymous address where the asset is stored, which can be performed in multiple ways.
-In many distributed ledgers, an address represents a public key, and controlling means knowing the corresponding private key.
-In this case, the prosumer can prove that it controls an address by signing a challenge, which was freshly generated by the service, with the private key of the address.
-Alternatively, the prosumer may also prove control by transferring zero amount of assets to a random address that was freshly generated by the service.
+Prosumers must be able to anonymously post energy bids and asks on the
+bid storage service.  An anonymous bid (or ask) contains an ECA (or
+EPA), a price, and an anonymous communication identifier (\em{e.g.},
+Tor hidden service), which can be used to contact the bidding (or
+asking) prosumer.  To enforce safety requirements, the bid storage
+service must verify that the prosumer actually owns the asset to be
+traded.  To this end, the prosumer first has to prove that it controls
+the anonymous address where the asset is stored, which can be
+performed in multiple ways.
+
+In many distributed ledgers, an address represents a public key, and
+controlling means knowing the corresponding private key.  In this
+case, the prosumer can prove that it controls an address by signing a
+challenge, which was freshly generated by the service, with the
+private key of the address.  Alternatively, the prosumer may also
+prove control by transferring zero amount of assets to a random
+address that was freshly generated by the service.
 
@@
 \subsubsection{Smart-Meter Based Billing}
-Once a prosumer has finished trading, it deposits all of its EPA, ECA, and FA to the smart meter, by transferring them to an anonymous address generated by the smart meter.
-Later, during timeslot $t$, the smart meter measures the amount of energy actually consumed (or produced) by the prosumer using physical sensors.
-Then, the meter can compute the prosumer's bill for timeslot $t$, which is to be paid to the DSO, as follows.
+After a prosumer has finished trading, it deposits all of its EPA,
+ECA, and FA to the smart meter by transferring them to an anonymous
+address generated by the smart meter.  Later, during timeslot $t$, the
+smart meter measures the amount of energy actually consumed (or
+produced) by the prosumer using physical sensors.  The meter can then
+compute the prosumer's bill for timeslot $t$, which will be paid to
+the DSO, as follows.
 
@@
 \end{align*}
-Notice that consumption assets are not used directly for billing, they are only used to enforce security and safety requirements.
+Consumption assets are only used to enforce security and safety
+requirements, but are not used directly for billing.
 
-The bill $B_i^t$ of prosumer $i$ for timeslot $t$, which is to be paid by the prosumer to the DSO, is
+The bill $B_i^t$ of prosumer $i$ for timeslot $t$, which will be paid
+by the prosumer to the DSO, is
 \begin{align*}
@@
 \end{align*}
-where {\field{priceProduction}} and {\field{priceConsumption}} are the prices set by the latest regulatory transactions for timeslot $t$.
+where {\field{priceProduction}} and {\field{priceConsumption}} are the
+prices set by the latest regulatory transactions for timeslot $t$.

### 2017-06-16 papers/IoT2017/solution.tex
updates

--- 2017-06-07 papers/IoT2017/solution.tex
@@
 
-In this section, we describe our solution for providing privacy to prosumers in a transactive energy IoT system, without compromising grid safety and security.
-Figure~\ref{fig:softwareArchitecture} shows a high-level overview of the architecture of our solution.
-
+This section describes our solution for providing privacy to prosumers
+in a transactive energy IoT system, without compromising grid safety
+and security.
+% Abhishek, could this figure appear earlier, i.e., in the previous
+% section, as per my comment three?
+Figure~\ref{fig:softwareArchitecture} shows the architecture of 
+% Abhishek, can we give ``our solution'' a name so that we can refer
+% to it by name throughout the paper?
+our solution.  In this figure components marked red are introduced to
+provide privacy in a safe and secure manner, whereas components marked
+in blue are typical elements of a decentralized transactive microgrid.
 \begin{figure}[h!]
 \center
-\begin{tikzpicture}[x=8cm, y=0.8cm, font=\small,
+\begin{tikzpicture}[x=8cm, y=1.1cm, font=\small,
   nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
@@
 \end{tikzpicture}
-\caption{High-level architecture of the proposed solution.
-Components marked red are introduced to provide privacy in a safe and secure manner.
-Components marked in blue are typical elements of a decentralized transactive microgrid.}
+\caption{High-level Architecture of Our Solution.}
 \label{fig:softwareArchitecture}
@@
 \end{tikzpicture}
-\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy.
-Note that in order to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing.}
+\caption{Simplified Overview of the Flow of Assets from the Perspective of a Prosumer Who Sells Energy.}
 \label{fig:sellFlow}
@@
 \subsection{Overview of the Trading Process}
-We first provide a semi-formal description of the energy trading process from the prosumers' perspective.
-In subsequent subsections, we will describe the assets, transactions, and services used for trading in more detail.
+We now provide a semi-formal description of the energy trading process
+from the prosumers' perspective (subsequent subsections will describe
+the assets, transactions, and services used for trading in more
+detail).  Consider a prosumer who wishes to sell energy to another
+prosumer, as shown in Figure~\ref{fig:sellFlow} In the initial step,
+the prosumer withdraws an \emph{energy production asset} from its
+smart meter.  An energy production asset represents a permission to
+sell a certain amount of energy, and it is used to enforce safety
+requirements.  If the prosumer has sufficient unsold production
+capacity, the smart meter creates and transfers a production asset to
+the prosumer using a \emph{smart meter transaction} \circled{1}, which
+is recorded on the distributed ledger.
 
-First, consider a prosumer who wishes to sell energy to another prosumer (this case is illustrated in Figure~\ref{fig:sellFlow}).
-As its very first step, the prosumer withdraws an \emph{energy production asset} from its smart meter.
-An energy production asset represents a permission to sell a certain amount of energy, and it is used to enforce safety requirements.
-If the prosumer has sufficient unsold production capacity, the smart meter creates and transfers a production asset to the prosumer using a \emph{smart meter transaction} \circled{1}, which is recorded on the distributed ledger.
+At this point, the production asset can still be traced back to the
+prosumer since the ledger is public.  To achieve anonymity, the
+prosumer uses a \emph{mixing service}, which could implemented as a
+decentralized protocol, such as
+CoinShuffle~\cite{ruffing2014coinshuffle} or
+Xim~\cite{bissias2014sybil}. To prevent de-anonymization, a prosumer
+should use multiple addresses and multiple rounds of mixing.
 
-At this point, the production asset can still be traced back to the prosumer since the ledger is public.
-To achieve anonymity, the prosumer uses a \emph{mixing service}, which in practice may be implemented as a decentralized protocol, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
-The prosumer transfers the production asset to the mixing service using an \emph{energy and financial transaction} \circled{2}, which is also recorded on the distributed ledger.
-In turn, the mixing service transfers the production asset to an \emph{anonymous address} \circled{3}\Aron{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}, which is randomly generated and controlled by the prosumer.
-Since the mixing service transfers assets from multiple prosumers to multiple anonymous addresses at the same time, and the anonymous addresses were generated at random by the prosumers, the assets cannot be traced back to the original prosumers after mixing.\footnote{Note that prosumers should divide their assets between multiple anonymous addresses; otherwise, each asset might be traced back to its prosumer based on the amount of energy that it contains.}
+The prosumer next transfers the production asset to the mixing service
+using an \emph{energy and financial transaction} \circled{2}, which is
+also recorded on the distributed ledger.  In turn, the mixing service
+transfers the production asset to an \emph{anonymous address},
+\circled{3}
+%\Aron{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}
+which is randomly generated and controlled by the
+prosumer.\footnote{The meaning of \emph{address} varies between
+  distributed ledgers. Since our system could be implemented using any
+  popular blockchain, such as Bitcoin and Ethereum, we use this term
+  to denote a possible destination for asset transfers.  Assets that
+  have been transferred to an address can be used only by someone who
+  ``controls'' the address (typically, the one who generated it),
+  which usually means knowing a private key that corresponds to the
+  address.}
+% knows the private key of the address (typically, the one who generated the address).}
+Since the mixing service transfers assets from multiple prosumers to
+multiple anonymous addresses at the same time---and the anonymous
+addresses were generated at random by the prosumers---the assets
+cannot be traced back to the original prosumers after
+mixing.\footnote{prosumers should divide their assets between multiple
+  anonymous addresses; otherwise, each asset might be traced back to
+  its prosumer based on the amount of energy that it contains.}
 
-Now, the prosumer can engage in energy trading anonymously.
-To find a trade partner, it can either post an \emph{energy ask} on the bid storage, or simply search the storage for an acceptable \emph{energy bid}.
-To post an energy ask, the prosumer first proves to the storage service -- without revealing its original identity -- that it owns a production asset stored at an anonymous address.
-It can then post the energy ask \circled{4}, which contains an anonymous communication identifier\footnote{We discuss communication anonymity later.}, a price, and a reference to the production asset.
-If another prosumer, who would like to buy energy, finds the ask acceptable, it can contact the seller using the communication identifier given included in the ask.
+A prosumer can now engage in energy trading anonymously.  To find a
+trade partner, it can either post an \emph{energy ask} on the bid
+storage, or simply search the storage for an acceptable \emph{energy
+  bid}.  To post an energy ask, the prosumer first proves to the
+storage service---without revealing its original identity---that it
+owns a production asset stored at an anonymous address.  It can then
+post the energy ask \circled{4}, which contains an anonymous
+communication identifier (discussed shortly), a price, and a reference
+to the production asset.  If another prosumer seeking to buy energy
+finds the ask acceptable it can contact the seller using the
+communication identifier included in the ask.
 
-The seller and buyer can execute the trade by creating an energy and financial transaction together \circled{5}, and recording it on the ledger.
-This transaction transfers the production asset from the seller to the buyer, and a \emph{financial asset} and an \emph{energy consumption asset} from the buyer to the seller.
-A financial asset represents a certain amount of money, while a consumption asset represents a permission to buy a certain amount of energy, which is used to enforce safety requirements similarly to production assets.
+The seller and buyer can execute the trade by creating an energy and
+financial transaction together \circled{5}, and recording it on the
+ledger.  This transaction transfers the production asset from the
+seller to the buyer, and a \emph{financial asset} and an \emph{energy
+  consumption asset} from the buyer to the seller.  A financial asset
+represents a certain amount of money, while a consumption asset
+represents a permission to buy a certain amount of energy, which is
+used to enforce safety requirements similarly to production assets.
 
-Finally, the selling prosumer deposits the financial and consumption assets to its smart meter using an energy and financial transaction.
-To ensure that the prosumer remains anonymous, it transfers the assets to an anonymous address that is randomly generated and controlled by the smart meter \circled{6}.
-Once the smart meter has received the assets, it credits the financial amount to and deducts the energy amount from the prosumer, for billing purposes.
-In order to enforce safety requirements, the prosumer is required to always deposit the same amount of consumption assets as the amount of production assets withdrawn at the beginning; otherwise, unaccounted assets might be used to trade excessive amounts.
+The selling prosumer finally deposits the financial and consumption
+assets to its smart meter using an energy and financial transaction.
+to ensure that the prosumer remains anonymous, it transfers the assets
+to an anonymous address that is randomly generated and controlled by
+the smart meter \circled{6}.  Once the smart meter has received the
+assets, it credits the financial amount to and deducts the energy
+amount from the prosumer for billing purposes.  To enforce safety
+requirements, the prosumer must always deposit the same amount of
+consumption assets as the amount of production assets withdrawn at the
+beginning since otherwise unaccounted assets might be used to trade
+excessive amounts.
 
-Second, consider a prosumer who would like to buy energy from another prosumer.
-Since the trading process is very similar to the case of the selling prosumer, we will discuss only the differences.
-In the first step, the prosumer tries to withdraw a financial asset and an energy consumption asset from its smart meter.
-If the prosumer has the consumption capacity and good financial standing, the smart meter transfers the assets to the prosumer and adds the financial amount to the prosumer's bill.
-After transferring the assets through a mixing service, the prosumer is ready to post an energy bid on the bid service.
-To do so, it first proves the ownership of both the financial asset and the consumption asset to the service, and then posts the energy bid, which includes an anonymous communication identifier.
-If a partner is found, the trade is executed as described before, the prosumer playing the role of the buyer this time.
-Finally, the prosumer deposits the purchased energy production asset to the anonymous address of its smart meter,
-which credits the energy amount to the prosumer, for billing purposes.
-Note that if the prosumer has not spent all of its financial assets, then the remainder may also be deposited back to the smart meter.
+% Abhishek, it seems like we might need a transition here since the
+% previous paragraph seemed to wrap up the ``Overview of the Trading
+% Process'' subsection above.  It's not clear how the rest of this
+% text ties in with that discussion.  Perhaps we could use
+% subsubsections to make these parts more distinct? 
+Consider a prosumer who wants to buy energy from another prosumer.
+Since the trading process is similar to the case of the selling
+prosumer, we only discuss the differences.  In the first step, the
+prosumer tries to withdraw a financial asset and an energy consumption
+asset from its smart meter.  If the prosumer has the consumption
+capacity and good financial standing, the smart meter transfers the
+assets to the prosumer and adds the financial amount to the prosumer's
+bill.
+
+After transferring the assets through a mixing service, the prosumer
+is ready to post an energy bid on the bid service.  To do so, it first
+proves the ownership of both the financial asset and the consumption
+asset to the service, and then posts the energy bid, which includes an
+anonymous communication identifier.  If a partner is found, the trade
+is executed as described above, with the prosumer playing the role of
+the buyer this time.
+
+The prosumer finally deposits the purchased energy production asset to
+the anonymous address of its smart meter, which credits the energy
+amount to the prosumer, for billing purposes.  Note that if the
+prosumer has not spent all of its financial assets, then the remainder
+may also be deposited back to the smart meter.
 

### 2017-06-16 papers/IoT2017/transactions.tex
updates

@@
 
-In the previous subsection, we gave an overview of how transactions are used in the trading process to transfer various assets.
-Here, we detail the format of these transactions, and the rules that they have to satisfy to be valid and recorded on the ledger.
-We also introduce and detail the format of regulatory transactions, which the DSO uses to regulate the microgrid.
+In the previous subsection, we gave an overview of how transactions
+are used in the trading process to transfer various assets.  We now
+describe the format of these transactions, as well as the rules that
+they must satisfy to be valid and recorded on the ledger.  We also
+introduce and detail the format of regulatory transactions, which the
+DSO uses to regulate the microgrid.
 
@@
 
-The ability to specify points or intervals in time is crucial.
-For example, control signals specify how the microgrid load should change at certain points in time, energy trades specify when energy will be consumed or produced, etc.
-To facilitate representing signals and transactions, we divide time into fixed-length intervals, and specify points or periods in time using these discrete timesteps.
-The length of the time interval is determined based on the timing assumptions of the physical power system.
-For example, the default length of the time interval may be 4 seconds, which corresponds to how frequently the control signal of the DSO typically changes.
-\Abhishek{We need to add citation here. I will add that tomorrow.}
-\Abhishek{What about the deadline within which the transactions should finish? Do we need to say anything here?}
-\Aron{Ideally, we should discuss the timing constraints of the ledger (probably when we introduce it), but we would first need to make space for this discussion.}
+The ability to specify points or intervals in time is crucial.  For
+example, control signals specify how the microgrid load should change
+at certain points in time, energy trades specify when energy will be
+consumed or produced, etc.  To facilitate representing signals and
+transactions, we divide time into fixed-length intervals, and specify
+points or periods in time using these discrete timesteps.  The length
+of the time interval is determined based on the timing assumptions of
+the physical power system.  For example, the default length of the
+time interval may be 4 seconds, which corresponds to how frequently
+the control signal of the DSO typically changes.  \Abhishek{We need to
+  add citation here. I will add that tomorrow.}  \Abhishek{What about
+  the deadline within which the transactions should finish? Do we need
+  to say anything here?}  \Aron{Ideally, we should discuss the timing
+  constraints of the ledger (probably when we introduce it), but we
+  would first need to make space for this discussion.}
 
 \subsubsection{Assets}
-
-Before we can discuss transactions, we must define the format of the three types of assets that these transactions may transfer.
-First, an \emph{energy production asset} (EPA) is defined by
+Before we discuss transactions, we'll define the format of the three
+types of assets that these transactions may transfer.  First, an
+\emph{energy production asset} (EPA) is defined by
 \begin{itemize}[noitemsep,topsep=-\parskip]
@@
 \end{itemize}
-\vspace{\parskip}
-Second, an \emph{energy consumption asset} (ECA) is defined by the same fields; however, for this asset, the fields define energy consumption instead of production.
-Finally, a \emph{financial asset} (FA) is defined by a single non-negative number \field{amount}, which can be denominated in either a fiat currency (e.g., US dollars) or a cryptocurrency.
+\vspace{\parskip} Second, an \emph{energy consumption asset} (ECA) is
+defined by the same fields.  For this asset, however, the fields
+define energy consumption instead of production.  Finally, a
+\emph{financial asset} (FA) is defined by a single non-negative number
+\field{amount}, which can be denominated in either a fiat currency
+(\em{e.g.}, Euros or US dollars) or a cryptocurrency (\em{e.g.},
+Bitcoin or Ether).
 
@@
 
-Energy and financial transactions transfer energy and financial assets from one address to another.
-Prosumers can use these transactions for multiple purposes: to trade energy by exchanging assets with other prosumers, to prove to the bid storage service that they possess an asset, to hide their identity by transferring assets to and from mixing services, and to deposit assets at their smart meter.
+Energy and financial transactions transfer energy and financial assets
+from one address to another.  Prosumers can use these transactions for
+multiple purposes, {\em e.g.}, to trade energy by exchanging assets
+with other prosumers, to prove to the bid storage service that they
+possess an asset, to hide their identity by transferring assets to and
+from mixing services, and to deposit assets at their smart meter.
 %
@@
 \end{itemize}
-\vspace{0.5\parskip}
-This transaction transfers the assets specified in the input lists to the addresses specified in the output lists. 
-Input and output lists may differ in length, so one asset may be divided into multiple assets, and multiple assets may be combined into one.
+\vspace{0.5\parskip} This transaction transfers the assets specified
+in the input lists to the addresses specified in the output lists.
+Input and output lists may differ in length, so one asset may be
+divided into multiple assets, and multiple assets may be combined into
+one.
 
-An energy and financial transaction is valid (and can be recorded on the ledger) if the following three conditions hold.
+An energy and financial transaction is valid (and can be recorded on
+the ledger) if the following three conditions hold.
 \begin{itemize}[noitemsep,topsep=-\parskip]
-\item None of the outputs referenced by the inputs have been spent by a transaction that has been recorded on the ledger.
-\item All of the signatures are valid, which ensures that an asset can be transferred only by its current owner. % current owner can transfer an asset.
-\item For each asset type (and for each timestep), the sums of the input and output assets are equal.
-For example, in the case of energy production assets, the condition is
+\item None of the outputs referenced by the inputs have been spent by
+  a transaction that has been recorded on the ledger.
+\item All the signatures are valid, which ensures that an asset can be
+  transferred only by its current owner. 
+% current owner can transfer an asset. 
+\item For each asset type (and for each timestep), the sums of the
+input and output assets are equal.  For example, in the case of
+energy production assets, the condition is
 \begin{align*}
@@
 %\end{equation}
-The conditions for consumption and financial assets can be described formally in similar ways.
+The conditions for consumption and financial assets can be described
+formally in similar ways.
 \end{itemize}
@@
 
-Prosumers use smart-meter transactions to withdraw energy and financial assets from their own smart meters, before they engage in trading.
+Prosumers use smart-meter transactions to withdraw energy and
+financial assets from their own smart meters, before they engage in
+trading.
 %
@@
 \end{itemize}
-\vspace{0.5\parskip}
-This transaction creates and transfers the assets to the prosumer's addresses, which are specified in the output lists.
+\vspace{0.5\parskip} This transaction creates and transfers the assets
+to the prosumer's addresses, which are specified in the output lists.
 
-The smart meter signs the transaction only if the prosumer is allowed to withdraw these assets.
-More specifically, the amount of assets withdrawn can never exceed certain limits that are set by the DSO.
-For example, in the case of EPA, the following condition must be satisfied for prosumer $i$:
+The smart meter signs the transaction only if the prosumer is allowed
+to withdraw these assets.  More specifically, the amount of assets
+withdrawn can never exceed certain limits that are set by the DSO.
+For example, in the case of EPA, the following condition must be
+satisfied for prosumer $i$:
 \begin{equation*}
@@
 \end{equation*}
-where $\field{STR}_i$ is the set of smart-meter transactions created for prosumer $i$, and $\field{MAXEPA}_i$ is the withdrawal limit.
-The condition for consumption assets is similar, based on a withdrawal limit $\field{MAXECA}_i$.
-For financial assets, the smart meter can take into account the amounts withdrawn and deposited, as well as the outside bill payments to the DSO.
+where $\field{STR}_i$ is the set of smart-meter transactions created
+for prosumer $i$, and $\field{MAXEPA}_i$ is the withdrawal limit.  The
+condition for consumption assets is similar, based on a withdrawal
+limit $\field{MAXECA}_i$.  For financial assets, the smart meter can
+take into account the amounts withdrawn and deposited, as well as the
+outside bill payments to the DSO.
 
@@
 
-The DSO uses regulatory transactions for two purposes: to manage the set of authorized smart meters and to change the price policy.
+The DSO uses regulatory transactions for two purposes: (1) to manage
+the set of authorized smart meters and (2) to change the price policy.
 %First, to change the set of smart meters that are authorized to sign transactions, the DSO authorizes or bans individual smart meters.
-First, whenever a new smart meter is installed, the DSO notifies the microgrid by authorizing the device using a regulatory transaction.
-Similarly, whenever a smart meter is deactivated (e.g., because service is stopped or the device is believed to be faulty or compromised), the DSO notifies the microgrid by banning the device.
-Second, to influence microgrid load, the DSO can set a price policy, which includes a price at which prosumer may buy energy from the DSO and a price at which they may sell energy to the DSO.
+Whenever a new smart meter is installed, the DSO notifies the
+microgrid by authorizing the device using a regulatory transaction.
+Likewise, whenever a smart meter is deactivated (\em{e.g.}, because
+service is stopped or the device is believed to be faulty or
+compromised), the DSO notifies the microgrid by banning the device.
+Second, to influence microgrid load, the DSO can set a price policy,
+which includes a price at which prosumer may buy energy from the DSO
+and a price at which they may sell energy to the DSO.
 
@@
 \begin{itemize}[noitemsep,topsep=-\parskip]
-\item \field{authorize}: list of smart meters to be authorized, each of which is defined by
+\item \field{authorize}: list of smart meters to be authorized, each
+  of which is defined by
 \begin{compactitem}
@@
 
-A regulatory transaction of this type is valid if %the following two conditions hold:
+A regulatory transaction of this type is valid if 
+%the following two conditions hold:
 %\begin{compactitem}
 %\item 
-\field{timestep} is not in the past and % specified in the transaction is in the future.
+\field{timestep} is not in the past and 
+% specified in the transaction is in the future.
 %\item 
@@
 %
-The active prices for timestep $t$ are given by the last regulatory transaction recorded on the ledger whose \field{time} is less than $t$.
-Similarly, regulatory transactions that are recorded on the ledger later override the authorizations and bans of earlier transactions.
+The active prices for timestep $t$ are given by the last regulatory
+transaction recorded on the ledger whose \field{time} is less than
+$t$.  Likewise, regulatory transactions that are recorded on the
+ledger later override the authorizations and bans of earlier
+transactions.

### 2017-06-16 papers/IoT2017/concl.tex
updates

@@
 
-As the complexity of power systems increases due to the evolution of power grids, decentralized transactive-energy IoT systems are emerging to tackle this complexity.
-However, these decentralized systems also give rise to new privacy challenges, which are further complicated by the stringent safety and security requirements of power systems.
-We have addressed these challenges by providing a novel solution for anonymous energy trading within a transactive microgrid.
-Our solution builds on distributed ledgers, such as blockchains, and other proven techniques for anonymity, such as mixing services and onion routing.
-We have described the novel process of anonymous energy trading and detailed the novel transactions and services used in our system.
-Finally, we have discussed how the proposed solution satisfies security, safety, and privacy requirements.
-In future work, we will provide rigorous proofs of satisfying these requirements, and we will present an implementation of our system with performance results.
+% Abhishek, as always, it would be best if we could revise this
+% summary of the paper's contents to be a summary of lessons learned
+% based upon our experiences to date!
+
+As the complexity of power systems increases due to the evolution of
+power grids, decentralized transactive-energy IoT systems are emerging
+to tackle this complexity.  Ironically, these decentralized systems
+also give rise to new privacy challenges, such as ...
+% Abhishek, please briefly list the key privacy challenges we cover in
+% this paper.
+These privacy challenges are exaccerbated by the stringent safety and
+security requirements of power systems.
+
+This paper describes how we are addressing these challenges via an
+innovative solution for anonymous energy trading within a transactive
+microgrid.  Our solution builds on distributed ledgers, such as
+blockchains, and other proven techniques for anonymity, such as mixing
+services and onion routing.  We described our robust process of
+anonymous energy trading and explain the novel transactions and
+services used in our system.  Finally, we discussed how the proposed
+solution satisfies security, safety, and privacy requirements.  In
+future work, we will provide rigorous proofs of satisfying these
+requirements, and we will present an implementation of our system with
+performance results.

### 2017-06-16 papers/IoT2017/analysis.tex
no message

@@
 This section presents a semi-formal analysis of our proposed solution
-and show that it satisfies the security, safety, and privacy
-requirements formulated in earlier sections.
+and shows that it satisfies the security, safety, and privacy
+requirements formulated in earlier sections\Aron{Why is ``sections'' plural? We formulated them in a single section.}.
 
@@
 %
-First, we show that the net amount of energy sold by prosumer $i$ for
+First, we can show that the net amount of energy sold by prosumer $i$ for
 each timestep is at most $\field{MAXEPA}_i$.  By definition, the
@@
 Hence, the net amount of energy sold by prosumer $i$ cannot exceed
-$\field{MAXEPA}_i$.  By extending the argument, we show that the net
+$\field{MAXEPA}_i$.  By extending the argument, we can show that the net
 amount of energy sold by a group of prosumers~$G$ cannot exceed
-$\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, we show that the net
+$\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, we can show that the net
 amount of energy bought by a group of prosumers $G$ cannot exceed
@@
 
-We also show that the total amount of energy bids (or asks) posted at
+We can also show that the total amount of energy bids (or asks) posted at
 the same time by prosumer $i$ for each timestep is at most
@@
 actual amount of assets traded by the prosumer.  If a prosumer does
-not wish to trade, therefore, it can anonymously deposit its assets to
+not wish to trade, it can anonymously deposit its assets to
 a random address that was freshly generated by its smart meter.  Even
-if a prosumer does not wish to trade, however, it should always
+if a prosumer does not wish to trade, it should always
 withdraw, mix, and deposit the same amount of assets.  Otherwise, the
@@
 As for the DSO, it receives the same information from the smart meter
-as in a non-transactive smart grid (\em{i.e.}, amount of energy
+as in a non-transactive smart grid (\emph{i.e.}, amount of energy
 produced and consumed).  Since trading is anonymous, the DSO learns

### 2017-06-16 papers/IoT2017/concl.tex
no message

--- 2017-06-07 papers/IoT2017/concl.tex
@@
 
-As the complexity of power systems increases due to the evolution of power grids, decentralized transactive-energy IoT systems are emerging to tackle this complexity.
-However, these decentralized systems also give rise to new privacy challenges, which are further complicated by the stringent safety and security requirements of power systems.
-We have addressed these challenges by providing a novel solution for anonymous energy trading within a transactive microgrid.
-Our solution builds on distributed ledgers, such as blockchains, and other proven techniques for anonymity, such as mixing services and onion routing.
-We have described the novel process of anonymous energy trading and detailed the novel transactions and services used in our system.
-Finally, we have discussed how the proposed solution satisfies security, safety, and privacy requirements.
-In future work, we will provide rigorous proofs of satisfying these requirements, and we will present an implementation of our system with performance results.
+\Doug{Abhishek, as always, it would be best if we could revise this summary of the paper's contents to be a summary of lessons learned based upon our experiences to date!}
+As the complexity of power systems increases due to the evolution of
+power grids, decentralized transactive-energy IoT systems are emerging
+to tackle this complexity. Ironically, these decentralized systems
+also give rise to new privacy challenges. %, such as ...
+\Doug{Abhishek, please briefly list the key privacy challenges we cover in this paper.}
+These privacy challenges are exacerbated by the stringent safety and
+security requirements of power systems.
+
+This paper describes how we address these challenges via an
+innovative solution for anonymous energy trading within a transactive
+microgrid.  Our solution builds on distributed ledgers, such as
+blockchains, and other proven techniques for anonymity, such as mixing
+services and onion routing.  We described our robust process of
+anonymous energy trading and explained the novel transactions and
+services used in our system.  Finally, we discussed how the proposed
+solution satisfies security, safety, and privacy requirements.  In
+future work, we will provide rigorous proofs of satisfying these
+requirements, and we will present an implementation of our system with
+performance results.

### 2017-06-16 papers/IoT2017/intro.tex
no message

@@
 \cite{rahimi2012transactive}. In this vision, energy generation,
-transmission, distribution, and even storage (\em{e.g.}, electric
+transmission, distribution, and even storage (\emph{e.g.}, electric
 vehicles in a community) can be strategically used to balance load and
@@
 \cite{melton2013gridwise}. In this approach, customers on the same
-feeder (\em{i.e.}, those sharing a power line link) can operate in an
+feeder (\emph{i.e.}, those sharing a power line link) can operate in an
 open market, trading and exchanging generated energy
@@
 tolerance, and security. Most of these efforts, however, focus on the
-computation and distribution of information, but do not provide the
+computation and distribution of information, and do not provide the
 support required to handle the privacy challenges that arise from the
@@
 This paper assumes the existence of a distributed IoT infrastructure
-and specifically focus on the following privacy challenges:
+and specifically focuses on the following privacy challenges:
 %
@@
 \begin{itemize}[itemsep=0.25\parskip,topsep=-0.5\parskip]
-% Abhishek, can you please add a pithy summary of this challenge?
-\item \bf{Pithy challenge summary needed.} Since prosumers\footnote{We
+\item \textbf{Pithy challenge summary needed.} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
+ Since prosumers\footnote{We
   refer to customers as \emph{prosumers} to emphasize that they can
@@
 
-% Abhishek, can you please add a pithy summary of this challenge?
-\item \bf{Pithy challenge summary needed.} \Abhishek{Is this not
+\item \textbf{Pithy challenge summary needed.} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
+ \Abhishek{Is this not
   related to the first point?  Perhaps the first point can be just
@@
   private information.  For example, a smart home may know that its
-  inhabitants will go out in the evening (\em{e.g.}, by looking at
+  inhabitants will go out in the evening (\emph{e.g.}, by looking at
   their calendar), and it may trade energy futures accordingly in the
@@
   to other prosumers in the microgrid that the inhabitants will not be
-  at home later, which could be a security risk.  Note that energy
+  at home later.  Note that energy
   futures, whose delivery may happen several hours after when the
-  transaction is made, can play a important role in predicting and
+  transaction is made, can play an important role in predicting and
   controlling microgrid load.  In comparison, smart metering reveals
@@
 
-% Abhishek, can you please add a pithy summary of this challenge?
-\item \bf{Pithy challenge summary needed.} Transactions and energy
+\item \textbf{Pithy challenge summary needed.} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
+  Transactions and energy
   usage data in a transactive microgrid are much richer sources of
@@
 
-Before transactive energy system can be deployed widely in practice,
+Before transactive energy systems can be deployed widely in practice,
 we must address the privacy issues described above.  Addressing these
-issues is hard, however, since solutions also must satisfy security
+issues is hard, however, since solutions must also satisfy security
 and safety requirements, which often conflict with privacy goals.  For
@@
 transactive IoT microgrid and formulate security, safety, and privacy
-requirements.  We next introduce a decentralized system for
+requirements.  Next, we introduce a decentralized system for
 transactive microgrids based on distributed ledgers and describe the

### 2017-06-16 papers/IoT2017/prelim.tex
no message

@@
 \section{Preliminaries and Requirements}
-
+\Aron{Redundant, previous and following paragraphs state what we do here anyway.}
 This section describes the basic components of a transactive IoT
@@
 We begin by describing a basic system model of decentralized 
-% Abhishek, if there's room can we add a diagram showing how all these
-% components relate to each other?
+\Doug{Abhishek, if there's room can we add a diagram showing how all these components relate to each other?} 
 transactive IoT microgrids.  We discuss the following components: a
@@
 providing security and safety, it is crucial that transactions are
-non-malleable, \em{i.e.}, after a transaction has been recorded, it
+non-malleable, \emph{i.e.}, after a transaction has been recorded, it
 cannot be modified or removed from the ledger.  To enhance fault
-tolerance, however, the ledger also should be distributed.
+tolerance, however, the ledger should also be distributed.
 
@@
 quickly and reliably, even in the presence of faulty or malicious
-(\em{e.g.}, compromised) ledger nodes.  This paper assumes that a
+(\emph{e.g.}, compromised) ledger nodes.  This paper assumes that a
 distributed ledger service is available, but makes no assumptions
@@
 consensus algorithm.  In practice, a distributed ledger can be
-implemented using, \em{e.g.}, \emph{blockchains} with proof-of-stake
+implemented using, \emph{e.g.}, \emph{blockchains} with proof-of-stake
 consensus or a practical Byzantine fault tolerance
@@
 \subsubsection{Bid Storage Service}
-Although prosumers trade energy with each other directly (\em{i.e.},
+Although prosumers trade energy with each other directly (\emph{i.e.},
 without a middleman), for the sake of scalability, we need a service
@@
 \subsubsection{Microgrid Controller}
+\Aron{Is this true?}
 The microgrid controller stabilizes the load within the microgrid
 based on the predicted future load within the microgrid and the rest
-of the grid.  The controller thus first predicts load in the microgrid
+of the grid.  The controller first predicts load in the microgrid
 based on (1) bids and asks in the bid storage and (2) outstanding
@@
 to produce/consume a large amount of energy, but failing to
-deliver/utilize it.  A significant difference between promised and
+deliver.  A significant difference between promised and
 delivered energy production/consumption can result in a large gap
@@
 threatens the stability of not only the microgrid but also the main
-power grid.  Prosumers should therefore not be able to trade large
+power grid.  Therefore, prosumers should not be able to trade large
 amounts of energy that they are unlikely to deliver.
@@
 compromised when they participate in energy trading.  We use
-non-transactive smart metering as a baseline.  We also require that
+non-transactive smart metering as a baseline, and we require that
 the transactive system does not leak any additional information
-compared to the baseline.  More specifically, we require that
+compared to this baseline.  More specifically, we require that
 \begin{itemize}[noitemsep,topsep=-\parskip]

### 2017-06-16 papers/IoT2017/services.tex
no message

@@
 %on which transactions are built and which build on transactions.
-Earlier we discussed the distributed ledger, which permanently stores
-valid transactions.  Below we introduce the anonymous communication
+Earlier, we discussed the distributed ledger, which permanently stores
+valid transactions.  Below, we introduce the anonymous communication
 service, the mixing service for transaction anonymity, the anonymous
@@
 layer, transactions and bids could be easily de-anonymized based on
-their sources' network identifiers (\em{e.g.}, IP or MAC addresses).
+their sources' network identifiers (\emph{e.g.}, IP or MAC addresses).
 
-We employ well-known and widely used techniques for anonymous
+We can employ well-known and widely used techniques for anonymous
 communication, such as \emph{onion routing}~\cite{reed1998anonymous}.
@@
 microgrid can be published on the ledger.  In practice, this service 
-is built on
+can be built on 
 %In our first implementation, we can use
@@
 %Assets transferred to an address can be used only by someone who knows the private key of the address (typically, the one who generated the address).} 
-at random, so they are anonymous in the sense that no one can tell who
-generated them.  If prosumers simply transferred assets to these
-addresses, however, they could be easily de-anonymized by tracing the
+at random, which are anonymous in the sense that no one can tell who
+generated them.  However, if prosumers simply transferred assets to these
+addresses, they could be easily de-anonymized by tracing the
 assets back to the prosumers.
@@
 simplest one is to use a \emph{trusted third party}, called a
-cryptocurrency tumbler, which can receive and send assets.  Anonymity
-in this case, however, depends on the trustworthiness and reliability
+cryptocurrency tumbler, which can receive and send assets. However, anonymity
+in this case depends on the trustworthiness and reliability
 of the third party, who could easily de-anonymize the addresses.  A
-more secure approach is to used decentralized protocols, such as
+more secure approach is to use decentralized protocols, such as
 CoinShuffle~\cite{ruffing2014coinshuffle} or
@@
 
-% Abhishek, what does \begin{comment} mean in this context?
 \begin{comment}
@@
 bid storage service.  An anonymous bid (or ask) contains an ECA (or
-EPA), a price, and an anonymous communication identifier (\em{e.g.},
+EPA), a price, and an anonymous communication identifier (\emph{e.g.},
 Tor hidden service), which can be used to contact the bidding (or
@@
 \end{align*}
-Consumption assets are only used to enforce security and safety
-requirements, but are not used directly for billing.
+Notice that consumption assets are not used directly for billing, they are only used to enforce security and safety requirements.
 

### 2017-06-16 papers/IoT2017/solution.tex
no message

--- 2017-06-07 papers/IoT2017/solution.tex
@@
 
-In this section, we describe our solution for providing privacy to prosumers in a transactive energy IoT system, without compromising grid safety and security.
-Figure~\ref{fig:softwareArchitecture} shows a high-level overview of the architecture of our solution.
+This section describes our solution for providing privacy to prosumers
+in a transactive energy IoT system, without compromising grid safety
+and security.
+\Doug{Abhishek, could this figure appear earlier, i.e., in the previous section, as per my comment three?}
+Figure~\ref{fig:softwareArchitecture} shows the architecture of 
+\Doug{Abhishek, can we give ``our solution'' a name so that we can refer to it by name throughout the paper?}
+our solution.  In this figure, components marked red are introduced to
+provide privacy in a safe and secure manner, whereas components marked
+in blue are typical elements of a decentralized transactive microgrid.
 
@@
 \end{tikzpicture}
-\caption{High-level architecture of the proposed solution.
-Components marked red are introduced to provide privacy in a safe and secure manner.
-Components marked in blue are typical elements of a decentralized transactive microgrid.}
+\caption{High-level architecture of our solution.}
 \label{fig:softwareArchitecture}
@@
 \caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy.
-Note that in order to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing.}
+Note that to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing, which we have omitted from the figure for ease of presentation.}
 \label{fig:sellFlow}
@@
 \subsection{Overview of the Trading Process}
-We first provide a semi-formal description of the energy trading process from the prosumers' perspective.
-In subsequent subsections, we will describe the assets, transactions, and services used for trading in more detail.
+We now provide a semi-formal description of the energy trading process
+from the prosumers' perspective. 
+Subsequent subsections will describe the assets, transactions, and services used for trading in more detail.
 
-First, consider a prosumer who wishes to sell energy to another prosumer (this case is illustrated in Figure~\ref{fig:sellFlow}).
-As its very first step, the prosumer withdraws an \emph{energy production asset} from its smart meter.
+First, consider a prosumer who wishes to sell energy to another
+prosumer, as shown in Figure~\ref{fig:sellFlow}. 
+As its first step, the prosumer withdraws an \emph{energy production asset} from its smart meter.
 An energy production asset represents a permission to sell a certain amount of energy, and it is used to enforce safety requirements.
@@
 At this point, the production asset can still be traced back to the prosumer since the ledger is public.
-To achieve anonymity, the prosumer uses a \emph{mixing service}, which in practice may be implemented as a decentralized protocol, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
-The prosumer transfers the production asset to the mixing service using an \emph{energy and financial transaction} \circled{2}, which is also recorded on the distributed ledger.
-In turn, the mixing service transfers the production asset to an \emph{anonymous address} \circled{3}\Aron{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}, which is randomly generated and controlled by the prosumer.
-Since the mixing service transfers assets from multiple prosumers to multiple anonymous addresses at the same time, and the anonymous addresses were generated at random by the prosumers, the assets cannot be traced back to the original prosumers after mixing.\footnote{Note that prosumers should divide their assets between multiple anonymous addresses; otherwise, each asset might be traced back to its prosumer based on the amount of energy that it contains.}
+To achieve anonymity, the prosumer uses a \emph{mixing service}, which could be implemented as a decentralized protocol, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
+In turn, the mixing service
+transfers the production asset to an \emph{anonymous address} \circled{3},
+%\Aron{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}
+which is randomly generated and controlled by the
+prosumer.\footnote{The meaning of \emph{address} varies between distributed ledgers, but our system could be implemented using any popular blockchain, such as Bitcoin and Ethereum. 
+Specifically, we use the term address to denote a possible destination for asset transfers. 
+Assets that have been transferred to an address can be used only by someone who ``controls'' the address (typically, the one who generated it), which usually means knowing a private key that corresponds to the address.} % knows the private key of the address (typically, the one who generated the address).}
+% knows the private key of the address (typically, the one who generated the address).}
+Since the mixing service transfers assets from multiple prosumers to
+multiple anonymous addresses at the same time, and the anonymous
+addresses were generated at random by the prosumers, the assets
+cannot be traced back to the original prosumers after
+mixing.\footnote{Note that prosumers should divide their assets between multiple
+  anonymous addresses; otherwise, each asset might be traced back to
+  its prosumer based on the amount of energy that it contains.}
 
-Now, the prosumer can engage in energy trading anonymously.
-To find a trade partner, it can either post an \emph{energy ask} on the bid storage, or simply search the storage for an acceptable \emph{energy bid}.
-To post an energy ask, the prosumer first proves to the storage service -- without revealing its original identity -- that it owns a production asset stored at an anonymous address.
-It can then post the energy ask \circled{4}, which contains an anonymous communication identifier\footnote{We discuss communication anonymity later.}, a price, and a reference to the production asset.
-If another prosumer, who would like to buy energy, finds the ask acceptable, it can contact the seller using the communication identifier given included in the ask.
+The prosumer can now engage in energy trading anonymously.  To find a
+trade partner, it can either post an \emph{energy ask} on the bid
+storage, or simply search the storage for an acceptable \emph{energy
+  bid}.  To post an energy ask, the prosumer first proves to the
+storage service---without revealing its original identity---that it
+owns a production asset stored at an anonymous address.  It can then
+post the energy ask \circled{4}, which contains an anonymous
+communication identifier\footnote{We discuss communication anonymity later.}, a price, and a reference
+to the production asset.  If another prosumer, who is seeking to buy energy,
+finds the ask acceptable it can contact the seller using the
+communication identifier included in the ask.
 
-The seller and buyer can execute the trade by creating an energy and financial transaction together \circled{5}, and recording it on the ledger.
-This transaction transfers the production asset from the seller to the buyer, and a \emph{financial asset} and an \emph{energy consumption asset} from the buyer to the seller.
-A financial asset represents a certain amount of money, while a consumption asset represents a permission to buy a certain amount of energy, which is used to enforce safety requirements similarly to production assets.
+The seller and buyer can execute the trade by creating an energy and
+financial transaction together \circled{5}, and recording it on the
+ledger.  This transaction transfers the production asset from the
+seller to the buyer, and a \emph{financial asset} and an \emph{energy
+  consumption asset} from the buyer to the seller.  A financial asset
+represents a certain amount of money, while a consumption asset
+represents a permission to buy a certain amount of energy, which is
+used to enforce safety requirements similarly to production assets.
 
-Finally, the selling prosumer deposits the financial and consumption assets to its smart meter using an energy and financial transaction.
-To ensure that the prosumer remains anonymous, it transfers the assets to an anonymous address that is randomly generated and controlled by the smart meter \circled{6}.
-Once the smart meter has received the assets, it credits the financial amount to and deducts the energy amount from the prosumer, for billing purposes.
-In order to enforce safety requirements, the prosumer is required to always deposit the same amount of consumption assets as the amount of production assets withdrawn at the beginning; otherwise, unaccounted assets might be used to trade excessive amounts.
+Finally, the selling prosumer deposits the financial and consumption
+assets to its smart meter using an energy and financial transaction.
+To ensure that the prosumer remains anonymous, it transfers the assets
+to an anonymous address that is randomly generated and controlled by
+the smart meter \circled{6}.  Once the smart meter has received the
+assets, it credits the financial amount to and deducts the energy
+amount from the prosumer for billing purposes.  To enforce safety
+requirements, the prosumer is required to always deposit the same amount of
+consumption assets as the amount of production assets withdrawn at the
+beginning; otherwise, unaccounted assets could be used to trade
+excessive amounts.
 
+\Doug{Abhishek, it seems like we might need a transition here since the previous paragraph seemed to wrap up the ``Overview of the Trading Process'' subsection above.
+It's not clear how the rest of this text ties in with that discussion.
+Perhaps we could use subsubsections to make these parts more distinct?}
+\Aron{It did not wrap up. We have only discussed the process from the seller's perspective.}
 Second, consider a prosumer who would like to buy energy from another prosumer.
@@
 If the prosumer has the consumption capacity and good financial standing, the smart meter transfers the assets to the prosumer and adds the financial amount to the prosumer's bill.
+
 After transferring the assets through a mixing service, the prosumer is ready to post an energy bid on the bid service.
 To do so, it first proves the ownership of both the financial asset and the consumption asset to the service, and then posts the energy bid, which includes an anonymous communication identifier.
-If a partner is found, the trade is executed as described before, the prosumer playing the role of the buyer this time.
+If a partner is found, the trade is executed as described above, with the prosumer playing the role of the buyer this time.
+
 Finally, the prosumer deposits the purchased energy production asset to the anonymous address of its smart meter,

### 2017-06-16 papers/IoT2017/transactions.tex
no message

@@
 describe the format of these transactions, as well as the rules that
-they must satisfy to be valid and recorded on the ledger.  We also
+they have to satisfy to be valid and recorded on the ledger.  We also
 introduce and detail the format of regulatory transactions, which the
@@
 \subsubsection{Assets}
-Before we discuss transactions, we'll define the format of the three
+Before we can discuss transactions, we need to define the format of the three
 types of assets that these transactions may transfer.  First, an
@@
 \field{amount}, which can be denominated in either a fiat currency
-(\em{e.g.}, Euros or US dollars) or a cryptocurrency (\em{e.g.},
+(\emph{e.g.}, Euros or US dollars) or a cryptocurrency (\emph{e.g.},
 Bitcoin or Ether).
@@
   a transaction that has been recorded on the ledger.
-\item All the signatures are valid, which ensures that an asset can be
+\item All signatures are valid, which ensures that an asset can be
   transferred only by its current owner. 
@@
 %First, to change the set of smart meters that are authorized to sign transactions, the DSO authorizes or bans individual smart meters.
-Whenever a new smart meter is installed, the DSO notifies the
+First, whenever a new smart meter is installed, the DSO notifies the
 microgrid by authorizing the device using a regulatory transaction.
-Likewise, whenever a smart meter is deactivated (\em{e.g.}, because
+Likewise, whenever a smart meter is deactivated (\emph{e.g.}, because
 service is stopped or the device is believed to be faulty or

### 2017-06-16 papers/IoT2017/analysis.tex
no message

@@
 and shows that it satisfies the security, safety, and privacy
-requirements formulated in earlier sections\Aron{Why is ``sections'' plural? We formulated them in a single section.}.
+requirements formulated earlier.
 
@@
 
-We can also show that the total amount of energy bids (or asks) posted at
+Using a similar argument, we can also show that the total amount of energy bids (or asks) posted at
 the same time by prosumer $i$ for each timestep is at most
@@
 Since all trading transactions are anonymous, they do not reveal the
-actual amount of assets traded by the prosumer.  If a prosumer does
-not wish to trade, it can anonymously deposit its assets to
-a random address that was freshly generated by its smart meter.  Even
+actual amount of assets traded by the prosumer.  If a prosumer has not traded away all of its assets, %is left with assets that were not traded, % does not wish to trade, 
+then it can also anonymously deposit the remainder to
+a random address that was freshly generated by its smart meter. Note that even
 if a prosumer does not wish to trade, it should always

### 2017-06-16 papers/IoT2017/intro.tex
no message

@@
 open market, trading and exchanging generated energy
-locally. Distribution System Operators (DSOs) can be the custodian of
+locally. Distribution System Operators (DSOs) can be the custodians of
 this market, while still meeting the net demand \cite{7462854}. For
@@
 Before transactive energy systems can be deployed widely in practice,
-we must address the privacy issues described above.  Addressing these
-issues is hard, however, since solutions must also satisfy security
+we must address the privacy issues described above. However, addressing these
+issues is hard since solutions must also satisfy security
 and safety requirements, which often conflict with privacy goals.  For

### 2017-06-16 papers/IoT2017/prelim.tex
no message

@@
 A careless or malicious prosumer may destabilize the grid by promising
-to produce/consume a large amount of energy, but failing to
-deliver.  A significant difference between promised and
-delivered energy production/consumption can result in a large gap
-between actual production and consumption in the microgrid, which
-threatens the stability of not only the microgrid but also the main
+to produce (or consume) a large amount of energy, but failing to actually
+produce (or consume) it.  A significant difference between promised and
+actual energy production (or consumption) can result in a large gap
+between the aggregate production and consumption of the microgrid.
+A large gap threatens the stability of not only the microgrid but also the main
 power grid.  Therefore, prosumers should not be able to trade large
@@
   defined analogously,
-\item the energy bids and asks posted by the prosumer are limited in a
+\item the energy bids and asks posted by a prosumer are limited in a
   similar way.

### 2017-06-16 papers/IoT2017/services.tex
no message

@@
 The anonymous communication layer is the infrastructure upon which all
-other services in our system are built.  Without this communication
+other anonymity services in our system are built.  Without this communication
 layer, transactions and bids could be easily de-anonymized based on
@@
 \subsubsection{Bidding Anonymity}
-Prosumers must be able to anonymously post energy bids and asks on the
+Prosumers must also be able to anonymously post energy bids and asks on the
 bid storage service.  An anonymous bid (or ask) contains an ECA (or

### 2017-06-16 papers/IoT2017/solution.tex
no message

@@
 \caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy.
-Note that to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing, which we have omitted from the figure for ease of presentation.}
+Note that to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing, which we have omitted from the figure for clarity of presentation.}
 \label{fig:sellFlow}
@@
 To achieve anonymity, the prosumer uses a \emph{mixing service}, which could be implemented as a decentralized protocol, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
+The prosumer transfers the production asset to the mixing service using an \emph{energy and financial transaction} \circled{2}, which is also recorded on the distributed ledger.
 In turn, the mixing service
@@
 which is randomly generated and controlled by the
-prosumer.\footnote{The meaning of \emph{address} varies between distributed ledgers, but our system could be implemented using any popular blockchain, such as Bitcoin and Ethereum. 
+prosumer.\footnote{The concept of \emph{address} varies between distributed ledgers, but our system could be implemented using any popular blockchain, such as Bitcoin and Ethereum. 
 Specifically, we use the term address to denote a possible destination for asset transfers. 
 Assets that have been transferred to an address can be used only by someone who ``controls'' the address (typically, the one who generated it), which usually means knowing a private key that corresponds to the address.} % knows the private key of the address (typically, the one who generated the address).}
-% knows the private key of the address (typically, the one who generated the address).}
 Since the mixing service transfers assets from multiple prosumers to

### 2017-06-17 papers/IoT2017/paper.tex
no message

@@
 \newcommand{\Aron}[1]{\todo[color=green!40, linecolor=black!50]{\textbf{Aron}: #1}}
+\newcommand{\Doug}[1]{\todo[color=red!40, linecolor=black!50]{\textbf{Doug}: #1}}
 
@@
 % so you remain anonymous.
-\def\plaintitle{Providing Privacy, Safety, and Security in IoT-Based Transactive Energy Systems}
+\def\plaintitle{Providing Privacy, Safety, and Security in IoT-Based Transactive Energy Systems using Distributed Ledgers}
 \def\plainauthor{First Author, Second Author, Third Author}
@@
 can trade energy with each other, thereby smoothing the load on the
-main grid using local supply.  It is hard, however, to provide
+main grid using local supply. However, it is hard to provide
 security, safety, and privacy in a decentralized and transactive

### 2017-06-17 papers/IoT2017/prelim.tex
no message

@@
 providing security and safety, it is crucial that transactions are
-non-malleable, \emph{i.e.}, after a transaction has been recorded, it
+immutable, \emph{i.e.}, after a transaction has been recorded, it
 cannot be modified or removed from the ledger.  To enhance fault

### 2017-06-17 papers/IoT2017/solution.tex
no message

@@
 
-First, consider a prosumer who wishes to sell energy to another
+\subsubsection{Energy Selling Process}
+Consider a prosumer who wishes to sell energy to another
 prosumer, as shown in Figure~\ref{fig:sellFlow}. 
@@
 
-\Doug{Abhishek, it seems like we might need a transition here since the previous paragraph seemed to wrap up the ``Overview of the Trading Process'' subsection above.
-It's not clear how the rest of this text ties in with that discussion.
-Perhaps we could use subsubsections to make these parts more distinct?}
-\Aron{It did not wrap up. We have only discussed the process from the seller's perspective.}
-Second, consider a prosumer who would like to buy energy from another prosumer.
+\subsubsection{Energy Buying Process}
+Consider a prosumer who would like to buy energy from another prosumer.
 Since the trading process is very similar to the case of the selling prosumer, we will discuss only the differences.

### 2017-06-17 papers/IoT2017/intro.tex
comments and edits.

@@
 Recently, demand-response systems have been enabled as applications of
-IoT in smart grid~\cite{Haider2016166}. Transactive energy systems are
-the next step for the smart grid.
+IoT in smart grid~\cite{Haider2016166}. Transactive grid is the next step \cite{collier2017emerging}.
 % With the advent of IoT-based solutions in smart-grid  dynamic demand response systems, which are a precursor to transactive sytems have been made possible.
@@
 \begin{itemize}[itemsep=0.25\parskip,topsep=-0.5\parskip]
-\item \textbf{Pithy challenge summary needed.} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
+\item \textbf{Leakage of Energy Usage Patterns to Other Prosumenrs} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
  Since prosumers\footnote{We
@@
 
-\item \textbf{Pithy challenge summary needed.} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
+\item \textbf{Preventing Inference of Future State of a Prosumer} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
  \Abhishek{Is this not
@@
 
-\item \textbf{Pithy challenge summary needed.} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
+\item \textbf{Preventing Personally Identifiable Information} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
   Transactions and energy
@@
 
-\Abhishek{Can we cite an example of such a service?}  \Aron{I am not
-  sure what you mean by ``such a service.''}  \Abhishek{We should
-  connect the paper and our work back to IoT in this paragraph.}  This
-paper proposes a solution that (1) enables trading energy futures in a
+In this paper, we describe an overview of the transactive sequence between different components of the systems.
+We also describe in the detail the structure of these transactions and show how these transactions  (1) enables trading energy futures in a
 secure and verifiable manner, (2) preserves prosumer privacy, and (3)
 enables DSOs to regulate the trading platform and enforce certain
-safety rules.  \Aron{Since SIGCHI does not have section numbers, this
-  paragraph, which describes the organization of the paper, is not
-  very clear.}  We first describe the basic components of a
+safety rules.
+
+%\Abhishek{Can we cite an example of such a service?}  \Aron{I am not
+%  sure what you mean by ``such a service.''}  \Abhishek{We should
+%  connect the paper and our work back to IoT in this paragraph.}  
+  %This
+%paper proposes a solution that (1) enables trading energy futures in a
+%secure and verifiable manner, (2) preserves prosumer privacy, and (3)
+%enables DSOs to regulate the trading platform and enforce certain
+%safety rules. 
+ %\Aron{Since SIGCHI does not have section numbers, this
+ % paragraph, which describes the organization of the paper, is not
+  %very clear.}
+
+%\Abhishek{I have commented the previous because it seems redundant}
+We first describe the basic components of a
 transactive IoT microgrid and formulate security, safety, and privacy

### 2017-06-17 papers/IoT2017/prelim.tex
comments and edits.

@@
+%!TEX root = paper.tex
 \section{Preliminaries and Requirements}
@@
 \subsection{Transactive Microgrid Components}
+\Abhishek{We need a figure here.
+We probably need to briefly describe a transactive energy architecture and then use that to set the requirements.
+The services described here will then better  fit in our section on solution }
 
@@
 
-\subsubsection{Microgrid Controller}
-\Aron{Is this true?}
-The microgrid controller stabilizes the load within the microgrid
-based on the predicted future load within the microgrid and the rest
-of the grid.  The controller first predicts load in the microgrid
+\subsubsection{Microgrid Controller (Distribution System Operator)}
+\Aron{Is this true?}\Abhishek{I have editied it. We need to mention distribution system operator here.}
+We assume the existence of a controller at the Distribution System Operator level that regulates the total load that the microgrid should present to the distribution system.
+%The microgrid controller stabilizes the load within the microgrid
+%based on the predicted future load within the microgrid and the rest
+%of the grid. 
+ The controller first predicts load in the microgrid
 based on (1) bids and asks in the bid storage and (2) outstanding

### 2017-06-17 papers/IoT2017/solution.tex
comments and edits.

@@
+%!TEX root = paper.tex
 \section{Proposed System}
@@
 Consider a prosumer who wishes to sell energy to another
-prosumer, as shown in Figure~\ref{fig:sellFlow}. 
+prosumer, as shown in Figure~\ref{fig:sellFlow}\Abhishek{We need to mention what is the expected deadline by which this sequence of task should finish. }. 
 As its first step, the prosumer withdraws an \emph{energy production asset} from its smart meter.

### 2017-06-17 papers/IoT2017/transactions.tex
comments and edits.

@@
+%!TEX root = paper.tex
 \subsection{Transactions}
@@
 introduce and detail the format of regulatory transactions, which the
-DSO uses to regulate the microgrid.
+DSO uses to regulate the microgrid.\Abhishek{We need a figure describing the transactive system architecture.
+A collection of agents, arranged in a microgrid and a collection of microgrids being controlled by a DSO after the introduction}
 

### 2017-06-17 papers/IoT2017/analysis.tex
no message

@@
 
-This section presents a semi-formal analysis of our proposed solution
+This section presents a semi-formal analysis of PETra
 and shows that it satisfies the security, safety, and privacy
@@
 \begin{itemize}[noitemsep,topsep=-\parskip]
-\item non-malleability of transactions in the distributed ledger,
+\item immutability of transactions in the distributed ledger,
 \item validity conditions of the transactions, which include conditions on both signatures and asset balances,
@@
 create and sign a transaction, that transactions adhere to the rules
-of the trading process, and that transactions cannot be tampered
+of the trading workflow, and that transactions cannot be tampered
 with.\footnote{Due to lack of space, we leave a detailed discussion
@@
 excessive amounts of energy if normal prosumers follow the rules of
-the trading process.
+the trading workflow.
 %
@@
 $\field{MAXEPA}_i$.
-% amount of EPA.
 Although the prosumer may also buy EPA from another prosumer, this
@@
 sold with the same amount.
-%However, to obtain more EPA, the prosumer has to buy energy from another prosumer, which would decrease its net energy sold by the same amount.
 Hence, the net amount of energy sold by prosumer $i$ cannot exceed
@@
 
-Using a similar argument, we can also show that the total amount of energy bids (or asks) posted at
-the same time by prosumer $i$ for each timestep is at most
-$\field{MAXEPA}_i + \field{MAXECA}_i$.  This limit is higher than for
-net energy sold or bought, since prosumer $i$ may purchase
-$\field{MAXECA}_i$ amount of EPA (or $\field{MAXEPA}_i$ amount of ECA)
-from other prosumers, and then post an energy ask (or bid) in the
-amount of $\field{MAXEPA}_i + \field{MAXECA}_i$.
+%Using a similar argument, we can also show that the total amount of energy bids (or asks) posted at
+%the same time by prosumer $i$ for each timestep is at most
+%$\field{MAXEPA}_i + \field{MAXECA}_i$.  This limit is higher than for
+%net energy sold or bought, since prosumer $i$ may purchase
+%$\field{MAXECA}_i$ amount of EPA (or $\field{MAXEPA}_i$ amount of ECA)
+%from other prosumers, and then post an energy ask (or bid) in the
+%amount of $\field{MAXEPA}_i + \field{MAXECA}_i$.
 
@@
 prosumer from its smart meter.
-% the amount of energy and financial assets withdrawn by a prosumer.
 Since all trading transactions are anonymous, they do not reveal the
-actual amount of assets traded by the prosumer.  If a prosumer has not traded away all of its assets, %is left with assets that were not traded, % does not wish to trade, 
+actual amount of assets traded by the prosumer.  If a prosumer has not traded away all of its assets, 
 then it can also anonymously deposit the remainder to

### 2017-06-17 papers/IoT2017/concl.tex
no message

@@
 to tackle this complexity. Ironically, these decentralized systems
-also give rise to new privacy challenges. %, such as ...
+also give rise to new privacy challenges,
 \Doug{Abhishek, please briefly list the key privacy challenges we cover in this paper.}
-These privacy challenges are exacerbated by the stringent safety and
+which are exacerbated by the stringent safety and
 security requirements of power systems.
 
-This paper describes how we address these challenges via an
+This paper describes \change{how we address these challenges via}{\emph{Privacy-preserving Energy Transactions} (PETra),} an
 innovative solution for anonymous energy trading within a transactive
-microgrid.  Our solution builds on distributed ledgers, such as
-blockchains, and other proven techniques for anonymity, such as mixing
-services and onion routing.  We described our robust process of
+microgrid.  PETra builds on distributed ledgers, such as
+blockchains, and proven techniques for anonymity, such as mixing
+services and onion routing.  We described the workflow of
 anonymous energy trading and explained the novel transactions and
-services used in our system.  Finally, we discussed how the proposed
-solution satisfies security, safety, and privacy requirements.  In
+services used in PETra.  Finally, we discussed how PETra
+ satisfies security, safety, and privacy requirements.  In
 future work, we will provide rigorous proofs of satisfying these
-requirements, and we will present an implementation of our system with
+requirements, and we will present an implementation of PETra with
 performance results.

### 2017-06-17 papers/IoT2017/intro.tex
update
no message

--- 2017-06-16 papers/IoT2017/intro.tex
@@
 \cite{stock2015powerful}, reaching grid parity.
-%\cite{bronski2015economics}
+% \cite{bronski2015economics}
 This massive integration of renewable energy requires detailed
@@
 Recently, demand-response systems have been enabled as applications of
-IoT in smart grid~\cite{Haider2016166}. Transactive energy systems are
-the next step for the smart grid.
-% With the advent of IoT-based solutions in smart-grid  dynamic demand response systems, which are a precursor to transactive sytems have been made possible.
+IoT in smart grid~\cite{Haider2016166}. Transactive grid is the next step \cite{collier2017emerging}.
 
@@
 infrastructure
-%  comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator
 that provides the necessary computation fabric to support the
@@
 and specifically focuses on the following privacy challenges:
-%
-%
-% This is where the RIAPS and computing services discussion will be included. However, it does not solve the following challenges, which is the focus of this paper.
-%
-%\Abhishek{Can we merge this with last paragraph? It seems repetitive.}
-%\Aron{I'll probably just remove this.}
-%Specifically, 
-%in order to take advantage of local energy production and storage capabilities, 
-%in order to take advantage of these capabilities, 
-%electric grids need to become more decentralized.
-%However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
-%\Abhishek{We can introduce these bullets by stating that the privacy challenges specifically are (the privacy challenges were mentioned at the end of the paragraph above.)}
 \begin{itemize}[itemsep=0.25\parskip,topsep=-0.5\parskip]
-\item \textbf{Pithy challenge summary needed.} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
+\item \textbf{Leakage of Energy Usage Patterns to Other Prosumers} 
  Since prosumers\footnote{We
@@
 
-\item \textbf{Pithy challenge summary needed.} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
+\item \textbf{Inference of Future States of a Prosumer} 
  \Abhishek{Is this not
@@
 
-\item \textbf{Pithy challenge summary needed.} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
+\item \textbf{Personally Identifiable Information} 
   Transactions and energy
@@
 
-\Abhishek{Can we cite an example of such a service?}  \Aron{I am not
-  sure what you mean by ``such a service.''}  \Abhishek{We should
-  connect the paper and our work back to IoT in this paragraph.}  This
-paper proposes a solution that (1) enables trading energy futures in a
+In this paper, we \change{describe an overview of the transactive sequence between different components of the systems.
+We also describe in the detail the structure of these transactions and show how these transactions}{propose \emph{Privacy-preserving Energy Transactions} (PETra), a distributed-ledger based solution that} (1) enables trading energy futures in a
 secure and verifiable manner, (2) preserves prosumer privacy, and (3)
 enables DSOs to regulate the trading platform and enforce certain
-safety rules.  \Aron{Since SIGCHI does not have section numbers, this
-  paragraph, which describes the organization of the paper, is not
-  very clear.}  We first describe the basic components of a
+safety rules. 
+%
+\Aron{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}  
+We first describe the basic components of a
 transactive IoT microgrid and formulate security, safety, and privacy
-requirements.  Next, we introduce a decentralized system for
-transactive microgrids based on distributed ledgers and describe the
-transactions and services used to implement this system.  We then
-discuss how the system satisfies the security, safety, and privacy
+requirements.  Next, we introduce PETra and describe the
+transactions and services used to implement it.  We then
+discuss how PETra satisfies the security, safety, and privacy
 requirements.  Finally, we give a brief overview of related work and

### 2017-06-17 papers/IoT2017/paper.tex
no message

@@
 \newcommand{\Doug}[1]{\todo[color=red!40, linecolor=black!50]{\textbf{Doug}: #1}}
+
+\usepackage[normalem]{ulem}
+\newcommand{\change}[2]{\textcolor{red}{\sout{#1}} \textcolor{blue}{#2}}
+%\newcommand{\change}[2]{#2} % DO NOT DISPLAY CHANGES
 
@@
 careless or malicious trading, which could destabilize the entire
-grid.  This paper describes our secure and safe solution for
+grid.  This paper describes \change{our}{\emph{Privacy-preserving Energy Transactions} (PETra), a} secure and safe solution for
 transactive microgrids, which enables consumers to trade energy
-without sacrificing their privacy.  Our solution builds on distributed
+without sacrificing their privacy.  \change{Our solution}{PETra} builds on distributed
 ledgers, such as blockchains, and provides anonymity for

### 2017-06-17 papers/IoT2017/prelim.tex
no message

--- 2017-06-17 papers/IoT2017/prelim.tex
@@
-\section{Preliminaries and Requirements}
+%!TEX root = paper.tex
+\section{System Model and Requirements}
 \Aron{Redundant, previous and following paragraphs state what we do here anyway.}
-This section describes the basic components of a transactive IoT
-microgrid and formulates security, safety, and privacy requirements.
+This section describes a basic system model of transactive IoT
+microgrids and formulates security, safety, and privacy requirements.
 
-\subsection{Transactive Microgrid Components}
-
+\subsection{Transactive Microgrid System Model}
 \Abhishek{This is the perfect paragraph to define transactive microgrid as a special application of IoT spread over a large area. Perhaps we can find a citation that makes this point.}
@@
 prosumers' energy production and consumption.
+Figure~\ref{fig:softwareArchitecture} shows the high-level architecture of 
+\change{our solution.  In this figure, components marked red are introduced to
+provide privacy in a safe and secure manner, whereas components marked
+in blue are typical elements of a decentralized transactive microgrid.}{a decentralized transactive microgrid with PETra. 
+Components marked in blue are basic elements of the decentralized transactive microgrid,
+while components marked in red are added (or extended) by PETra.}
+
+\begin{figure}[h!]
+\center
+\begin{tikzpicture}[x=8cm, y=0.9cm, font=\small,
+  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
+]
+\draw [nodeStyle, fill=red!10]  (0, 1.65) rectangle    (1, 2.25) node [midway, align=center] {Communication anonymity (e.g., onion routing)};
+
+\draw [nodeStyle, fill=blue!10] (0, 2.4) rectangle    (1, 3.0) node [midway, align=center] {Distributed ledger (e.g., blockchain)};
+
+\draw [nodeStyle, fill=red!10]  (0, 3.15) rectangle (0.45, 4.05) node [midway, align=center] {Transaction anonymity\\[-0.2em](mixing service)};
+\draw [nodeStyle, left color=blue!10, right color=red!10] (0.47, 3.15) rectangle (0.72, 4.05) node [midway, align=center] {Bid storage};
+\draw [nodeStyle, left color=blue!10, right color=red!10] (0.74, 3.15) rectangle (1, 4.05) node [midway, align=center] {Active\\[-0.2em]smart meter};
+
+\draw [nodeStyle, fill=red!10] (0, 4.2) rectangle (0.49, 5.1) node [midway, align=center] {Anonymous trading\\[-0.2em]workflow for prosumers};
+\draw [nodeStyle, fill=blue!10] (0.51, 4.2) rectangle (1, 5.1) node [midway, align=center] {Microgrid controller};
+\end{tikzpicture}
+\caption{High-level architecture of a decentralized transactive microgrid with PETra.}
+\label{fig:softwareArchitecture}
+\end{figure}
 
@@
 that enables prosumers to find trade partners.
-%A bid storage service receives energy buy and sell bids from prosumers, stores these 
 We assume that there is a bid storage service that allows prosumers to
@@
 trade partners.
-%Moreover, in addition to simply storing bids and asks, the service may also find matches in the posted bids and asks, and it may notify the posting prosumers of the trade opportunity.
 To enhance scalability and reliability, this service can also be
@@
 
-\subsubsection{Microgrid Controller}
-\Aron{Is this true?}
-The microgrid controller stabilizes the load within the microgrid
-based on the predicted future load within the microgrid and the rest
-of the grid.  The controller first predicts load in the microgrid
+\subsubsection{Microgrid Controller (Distribution System Operator)}
+We assume the existence of a controller at the Distribution System Operator level that regulates the total load that the microgrid should present to the distribution system.
+ The controller first predicts load in the microgrid
 based on (1) bids and asks in the bid storage and (2) outstanding
@@
 safety.
-%Prosumers (or outside attackers) should not be able to tamper with measured energy production and consumption values, with financial balances, with other prosumers' bids.
 More specifically, they require that
@@
   consumption measured by the smart meters,
-% (i.e., prosumers or outside attackers cannot tamper with energy production, consumption, and financial balances) % attackers cannot tamper with energy production and consumption balances or financial balances),
 \item prosumers or outside attackers cannot change microgrid
@@
 amounts of energy that they are unlikely to deliver.
-%Trades which are unlikely to be delivered and would result in a gap between actual production and demand should be prevented.
 Specifically, we require that 
@@
   bought by the prosumer, and the net amount of energy bought is
-  defined analogously,
-\item the energy bids and asks posted by a prosumer are limited in a
-  similar way.
+  defined analogously. %,
+%\item the energy bids and asks posted by a prosumer are limited in a similar way.
 \end{itemize}

### 2017-06-17 papers/IoT2017/related.tex
no message

@@
 
-Our solution extends this earlier work by considering a decentralized
+PETra extends this earlier work by considering a decentralized
 IoT system for transactive energy, and addressing the novel privacy

### 2017-06-17 papers/IoT2017/services.tex
comments and edits.
no message

@@
+%!TEX root = paper.tex
 \subsection{Services}
 
-We now describe the various services that are provided in our system.
-%on which transactions are built and which build on transactions.
+We now describe the various services that are provided in PETra.
 Earlier, we discussed the distributed ledger, which permanently stores
@@
 The anonymous communication layer is the infrastructure upon which all
-other anonymity services in our system are built.  Without this communication
+other anonymity services in PETra are built.  Without this communication
 layer, transactions and bids could be easily de-anonymized based on
@@
 can be built on 
-%In our first implementation, we can use
 the free and open-source Tor software with private Directory
@@
 most distributed ledgers allow users to easily generate new addresses
-%\footnote{The usage of the term \emph{address} varies between distributed ledgers, but our system could be implemented using any popular ledger, such as Bitcoin and Ethereum.
-%Specifically, we use the term address to denote a possible destination for asset transfers. 
-%Assets transferred to an address can be used only by someone who knows the private key of the address (typically, the one who generated the address).} 
 at random, which are anonymous in the sense that no one can tell who
@@
 third party.
-%, which would constitute a single point of failure.
 Some newer cryptocurrencies, such as
@@
 which are often based on cryptographic principles and proofs.
-
-\begin{comment}
-We must provide prosumers with the ability to create and publish
-transactions anonymously.  More specifically, prosumers should be able
-to purchase or sell energy without revealing their identity; however,
-these transaction must also be verifiable and enforceable.
-
-We may achieve this goal using multiple approaches for blockchain transaction anonymity:
-\begin{itemize}
-\item Mixing services (also known as tumblers) mix potentially
-  identifiable assets on a blockchain with others, thereby preventing
-  tracing individual assets back to their original source.  In our
-  case, assets to be mixed include virtual balances of fiat currencies
-  as well as energy production and consumption.
-\item Cryptographic anonymity for transactions is provided, for
-  example, by Zerocoin~\cite{miers2013zerocoin}. Similarly to mixing
-  service, Zerocoin can prevent tracing assets on a blockchain.
-\end{itemize}
-Using the above techniques, we can enable prosumers to trade energy
-anonymously (i.e., without revealing their true identities), but at
-the same time prevent them from altering their energy or financial
-balances without a valid transaction.
-
-However, we must also ensure that 1) smart meters know the amount of
-energy purchased or sold by their prosumer and 2) prosumers cannot
-purchase or sell more energy than their capacity.  To satisfy both of
-these constraints, all energy trades must start with the prosumer
-withdrawing a certain amount of energy production or consumption from
-its smart meter:
-\begin{itemize}
-\item If a prosumer wishes to sell energy, it must first withdraw an
-  energy asset from its smart meter using a blockchain transaction.
-  This transaction must be signed by the smart meter, which enables
-  the smart meter to 1) keep track of the amount of energy traded by
-  the prosumer as well as to 2) enforce safety requirements by
-  limiting the amount of energy that can be withdrawn.
-\item If a prosumer wishes to buy energy, it must first withdraw an
-  energy consumption asset from its smart meter in a way similar to
-  withdrawing an energy production asset.
-\end{itemize}
-\end{comment}
 
@@
 
-%Finally, we must provide prosumers with the ability to post energy bids and asks anonymously.
-%To this end, we create a storage for anonymous bids that is readable by all the prosumers in the microgrid.
-%Any prosumer may submit a bid to this storage; however, in order to do so, they must provide a zero-knowledge proof of owning the assets that are to be traded:
-%\begin{itemize}
-%\item To submit an energy sell bid, the prosumer must prove that it owns an energy production asset on the chain.
-%\item To submit an energy buy bid, the prosumer must prove that it own an energy consumption asset as well as financial assets on the chain.
-%\end{itemize}
-
 \subsubsection{Smart-Meter Based Billing}
@@
 compute the prosumer's bill for timeslot $t$, which will be paid to
-the DSO, as follows.
+the DSO, as follows. \Abhishek{The safety argument should be strengthened here}
 
@@
 \begin{align*}
-E_i^t = & \hphantom{+} \text{measured net energy consumption during timeslot } t \\ %\text{measured consumption} - \text{measured production} \\
+E_i^t = & \hphantom{+} \text{measured net energy consumption during timeslot } t \\ 
  & - \sum_{epa \,\in\, \{\text{EPA deposited by } i\}: ~ epa.\field{start} \,\leq\, t \,\leq\, epa.\field{end}} epa.\field{power} \\
  & + \sum_{epa \,\in\, \{\text{EPA withdrawn by } i\}: ~ epa.\field{start} \,\leq\, t \,\leq\, epa.\field{end}} epa.\field{power} .
-% & + \text{EPA deposited by $i$} - \text{EPA withdrawn by $i$} .
 \end{align*}

### 2017-06-17 papers/IoT2017/solution.tex
update
no message

--- 2017-06-17 papers/IoT2017/solution.tex
@@
-\section{Proposed System}
+%!TEX root = paper.tex
+\section{Privacy-preserving Energy Transactions}
 
-This section describes our solution for providing privacy to prosumers
+This section describes Privacy-preserving Energy Transactions (PETra), our solution for providing privacy to prosumers
 in a transactive energy IoT system, without compromising grid safety
 and security.
-\Doug{Abhishek, could this figure appear earlier, i.e., in the previous section, as per my comment three?}
-Figure~\ref{fig:softwareArchitecture} shows the architecture of 
-\Doug{Abhishek, can we give ``our solution'' a name so that we can refer to it by name throughout the paper?}
-our solution.  In this figure, components marked red are introduced to
-provide privacy in a safe and secure manner, whereas components marked
-in blue are typical elements of a decentralized transactive microgrid.
-
-\begin{figure}[h!]
-\center
-\begin{tikzpicture}[x=8cm, y=1.1cm, font=\small,
-  nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
-]
-%\draw [nodeStyle, fill=white]   (0, 0) rectangle    (1, 0.9) node [midway, align=center] {Communication network\\[-0.2em]and operating system};
-
-%\draw [nodeStyle, fill=red!10]  (0, 1) rectangle    (1, 1.9) node [midway, align=center] {Communication anonymity\\[-0.2em](e.g., onion routing)};
-
-%\draw [nodeStyle, fill=blue!10] (0, 2) rectangle    (1, 2.9) node [midway, align=center] {Distributed ledger\\[-0.2em](e.g., blockchain)};
-
-%\draw [nodeStyle, fill=red!10]  (0,    3) rectangle (0.45, 3.9) node [midway, align=center] {Transaction anonymity\\[-0.2em](mixing service)};
-%\draw [nodeStyle, fill=blue!10] (0.47, 3) rectangle (0.72, 3.9) node [midway, align=center] {Bid storage};
-%\draw [nodeStyle, fill=red!10 ] (0.74, 3) rectangle (1,    3.9) node [midway, align=center] {Active\\[-0.2em]smart meter};
-
-%\draw [nodeStyle, fill=red!10] (0,    4) rectangle (0.49, 4.9) node [midway, align=center] {Prosumer anonymous\\[-0.2em]trading process};
-%\draw [nodeStyle, fill=blue!10] (0.51, 4) rectangle (1,    4.9) node [midway, align=center] {Microgrid\\[-0.2em]controller};
-\draw [nodeStyle, fill=white]   (0, 0.9) rectangle    (1, 1.5) node [midway, align=center] {Communication network and operating system};
-
-\draw [nodeStyle, fill=red!10]  (0, 1.65) rectangle    (1, 2.25) node [midway, align=center] {Communication anonymity (e.g., onion routing)};
-
-\draw [nodeStyle, fill=blue!10] (0, 2.4) rectangle    (1, 3.0) node [midway, align=center] {Distributed ledger (e.g., blockchain)};
-
-\draw [nodeStyle, fill=red!10]  (0, 3.15) rectangle (0.45, 4.05) node [midway, align=center] {Transaction anonymity\\[-0.2em](mixing service)};
-\draw [nodeStyle, fill=blue!10] (0.47, 3.15) rectangle (0.72, 4.05) node [midway, align=center] {Bid storage};
-\draw [nodeStyle, fill=red!10 ] (0.74, 3.15) rectangle (1, 4.05) node [midway, align=center] {Active\\[-0.2em]smart meter};
-
-\draw [nodeStyle, fill=red!10] (0, 4.2) rectangle (0.49, 5.1) node [midway, align=center] {Anonymous trading\\[-0.2em]process for prosumers};
-\draw [nodeStyle, fill=blue!10] (0.51, 4.2) rectangle (1, 5.1) node [midway, align=center] {Microgrid controller};
-\end{tikzpicture}
-\caption{High-level architecture of our solution.}
-\label{fig:softwareArchitecture}
-\end{figure}
 
@@
 ]
-%\node[entity] (smartmeter) at (0.75, 0.5) {smart\\meter};
-%\node[entity] (prosumer1) at (1.25, 1) {prosumer};
-%\node[system] (mixing1) at (2, 1) {mixing\\service};
-%\node[entity] (prosumer2) at (3, 1) {prosumer\\(alternative address)};
-%\node[system] (bidstorage) at (4, 1) {bid\\storage};
-%\node[entity] (partner) at (4, 0) {other prosumer};
-%\node[entity] (prosumer3) at (3, 0) {prosumer\\(alternative address)};
-%\node[system] (mixing2) at (2, 0) {mixing\\service};
-%\node[entity] (prosumer4) at (1.25, 0) {prosumer};
 \node[entity] (smartmeter) at (0, 1) {smart meter};
@@
 \node[entity] (smartmeter2) at (0, 0) {smart meter\\(anonymous address)};
-
-%\draw[transfer] (smartmeter) -- node [asset, above left] {energy\\production asset} (prosumer1);
-%\draw[transfer] (prosumer1) -- node [asset, above] {energy\\production asset} (mixing1);
-%\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
-%\draw[transfer, dashed] (prosumer2) -- node [asset, above] {energy production asset,\\energy bid} (bidstorage);
-%\draw[transfer, dashed] (bidstorage) -- node [asset, right] {energy\\bid} (partner);
-%\draw[transfer, bend right=15] (partner) to node [asset, below] {financial asset,\\energy\\consumption asset} (prosumer3);
-%\draw[transfer, bend right=7.5] (prosumer2) to node [asset, above right] {energy\\prod. asset} (partner);
-%\draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
-%energy consumption asset} (mixing2);
-%\draw[transfer] (mixing2) -- node [asset, below] {financial asset,\\energy consumption asset} (prosumer4);
-%\draw[transfer] (prosumer4) -- node [asset, below left] {financial\\asset} (smartmeter);
 
@@
 
-\subsection{Overview of the Trading Process}
-We now provide a semi-formal description of the energy trading process
+\subsection{Overview of the Trading Workflow}
+We now provide a semi-formal description of the energy trading workflow
 from the prosumers' perspective. 
@@
 
-\subsubsection{Energy Selling Process}
+\subsubsection{Energy Selling Workflow}
 Consider a prosumer who wishes to sell energy to another
-prosumer, as shown in Figure~\ref{fig:sellFlow}. 
+prosumer, as shown in Figure~\ref{fig:sellFlow}\Abhishek{We need to mention what is the expected deadline by which this sequence of task should finish. }. 
 As its first step, the prosumer withdraws an \emph{energy production asset} from its smart meter.
@@
 transfers the production asset to an \emph{anonymous address} \circled{3},
-%\Aron{We should probably insert a good definition here for readers who are unfamiliar with blockchain transactions.}
 which is randomly generated and controlled by the
-prosumer.\footnote{The concept of \emph{address} varies between distributed ledgers, but our system could be implemented using any popular blockchain, such as Bitcoin and Ethereum. 
+prosumer.\footnote{The concept of \emph{address} varies between distributed ledgers, but PETra could be implemented using any popular blockchain, such as Bitcoin and Ethereum. 
 Specifically, we use the term address to denote a possible destination for asset transfers. 
-Assets that have been transferred to an address can be used only by someone who ``controls'' the address (typically, the one who generated it), which usually means knowing a private key that corresponds to the address.} % knows the private key of the address (typically, the one who generated the address).}
+Assets that have been transferred to an address can be used only by someone who ``controls'' the address (typically, the one who generated it), which usually means knowing a private key that corresponds to the address.}
 Since the mixing service transfers assets from multiple prosumers to
@@
 
-\subsubsection{Energy Buying Process}
+\subsubsection{Energy Buying Workflow}
 Consider a prosumer who would like to buy energy from another prosumer.
-Since the trading process is very similar to the case of the selling prosumer, we will discuss only the differences.
+Since the trading workflow is very similar to the case of the selling prosumer, we will discuss only the differences.
 In the first step, the prosumer tries to withdraw a financial asset and an energy consumption asset from its smart meter.

### 2017-06-17 papers/IoT2017/transactions.tex
no message
typos

@@
 In the previous subsection, we gave an overview of how transactions
-are used in the trading process to transfer various assets.  We now
+are used in the trading workflow to transfer various assets.  We now
 describe the format of these transactions, as well as the rules that
@@
 \begin{itemize}[noitemsep,topsep=-\parskip]
-\item \field{power}: non-negative amount of power to produced (for example, measured in watts),
+\item \field{power}: non-negative amount of power to be produced (for example, measured in watts),
 \item \field{start}: first time interval in which energy is to be produced,
@@
 \begin{itemize}[leftmargin=0.5em,nosep]
-\item \field{EPA}: an energy consumption asset,
+\item \field{ECA}: an energy consumption asset,
 \item \field{address}: address to which ECA is transferred,
@@
 \begin{itemize}[leftmargin=0.5em,nosep]
-\item \field{EPA}: a financial asset,
+\item \field{FA}: a financial asset,
 \item \field{address}: address to which FA is transferred.

### 2017-06-17 papers/IoT2017/transactions.tex
no message

@@
 Second, to influence microgrid load, the DSO can set a price policy,
-which includes a price at which prosumer may buy energy from the DSO
+which includes a price at which prosumers may buy energy from the DSO
 and a price at which they may sell energy to the DSO.
 
-A regulatory transactions contain the following fields:
+A regulatory transaction contains the following fields:
 \begin{itemize}[noitemsep,topsep=-\parskip]

### 2017-06-18 papers/IoT2017/prelim.tex
update

@@
 \section{System Model and Requirements}
+
 \Aron{Redundant, previous and following paragraphs state what we do here anyway.}
-This section describes a basic system model of transactive IoT
-microgrids and formulates security, safety, and privacy requirements.
+\change{This section describes a basic system model of transactive IoT
+microgrids and formulates security, safety, and privacy requirements.}{The microgrid is a collection of prosumers (residential nodes) that are arranged within the same distribution feeder that supports exchange of power between them.
+Prosumer nodes typically include a smart inverter and a smart meter that controls the flow of power into and out of the prosumer.
+Additionally, the microgrid contains a set of
+protection nodes that are  responsible for isolating faults on the feeder.
+Finally, a set of distribution system operator (DSO) controlled switching nodes control the connection of the microgrid to the rest of the distribution system.
+The Distribution Systems Operator (DSO) is responsible for regulating the net electric power into and out of the microgrid.
+Starting, from this model we describe the transactive microgrid model in the next section.}
 

### 2017-06-18 papers/IoT2017/intro.tex
no message

@@
 \item \textbf{Inference of Future States of a Prosumer} 
- \Abhishek{Is this not
-  related to the first point?  Perhaps the first point can be just
-  about identity and second point can be specifically about
-  consumption patterns.}\Aron{The first point is about to whom
-  information might be leaked, and the second point is about the type
-  of information. I'll make this more clear.}  Transactions may reveal
+  Transactions may reveal
   the future energy usage of a prosumer, which could be used to infer
@@
 secure and verifiable manner, (2) preserves prosumer privacy, and (3)
-enables DSOs to regulate the trading platform and enforce certain
+enables DSOs to regulate trading and enforce certain
 safety rules. 

### 2017-06-18 papers/IoT2017/paper.tex
update
no message

@@
 
-\usepackage[normalem]{ulem}
-\newcommand{\change}[2]{\textcolor{red}{\sout{#1}} \textcolor{blue}{#2}}
-%\newcommand{\change}[2]{#2} % DO NOT DISPLAY CHANGES
+%\usepackage[normalem]{ulem}
+%\newcommand{\change}[2]{\textcolor{red}{\sout{#1}} \textcolor{blue}{#2}}
+\newcommand{\change}[2]{#2} % DO NOT DISPLAY CHANGES
 
@@
 energy system.  On the one hand, consumers' personal information must
-be protected from their trade partners and \Abhishek{To what extent is
-  this different that the information already known by the system
-  operator? Is this more related to the ``real-time'' nature of
-  transactive information?  Rather than aggregative total information
-  which is available at the end of billing cycle today.} \Aron{Do we
-  need to detail this in the abstract?}\Abhishek{we dont have to} the
+be protected from their trade partners and the
 system operator.  On the other hand, the system must be protected from

### 2017-06-18 papers/IoT2017/prelim.tex
no message

--- 2017-06-17 papers/IoT2017/prelim.tex
@@
 \section{System Model and Requirements}
-\Aron{Redundant, previous and following paragraphs state what we do here anyway.}
-This section describes a basic system model of transactive IoT
-microgrids and formulates security, safety, and privacy requirements.
+\change{This section describes a basic system model of transactive IoT
+microgrids and formulates security, safety, and privacy requirements.}{A microgrid is a collection of prosumers (residential nodes) that are arranged within the same distribution feeder which supports exchange of power between them.
+A prosumer node typically includes a smart inverter and a smart meter, which control the flow of power into and out of the prosumer.
+Additionally, the microgrid contains a set of
+protection nodes that are  responsible for isolating faults on the feeder.
+Finally, a set of switching nodes, which are operated by the Distribution System Operator (DSO), control the connection of the microgrid to the rest of the distribution system.
+The DSO is responsible for regulating the net electric power into and out of the microgrid.
+Starting from this model, we next introduce the transactive microgrid model.}
 
@@
 \Abhishek{This is the perfect paragraph to define transactive microgrid as a special application of IoT spread over a large area. Perhaps we can find a citation that makes this point.}
-We begin by describing a basic system model of decentralized 
+We now describe a basic system model of decentralized 
 \Doug{Abhishek, if there's room can we add a diagram showing how all these components relate to each other?} 
@@
   defined analogously. %,
+\Aron{If we have space, add back the safety requirement on the bid storage (and also add back the relevant parts of the description of the trading workflow and the ``analysis.''}
 %\item the energy bids and asks posted by a prosumer are limited in a similar way.

### 2017-06-18 papers/IoT2017/solution.tex
no message

@@
 \begin{figure*}[h]
-\center
+\centering
 \begin{tikzpicture}[x=3.8cm, y=1.6cm, font=\small,
@@
 \draw[transfer, bend right=50] (prosumer2) to node [asset, right, yshift=0.25em] {\circled{5} energy\\production asset} (partner);
-\draw[transfer] (prosumer3) -- node [asset, below] {\circled{6} financial asset,\\
+\draw[transfer] (prosumer3) -- node [asset, above] {\circled{6} financial asset,\\
 energy consumption asset} (smartmeter2);
@@
 storage service---without revealing its original identity---that it
-owns a production asset stored at an anonymous address.  It can then
+owns a production asset stored at an anonymous address. 
+\Aron{This sentence was added because we removed the relevant safety requirement.}
+Proving ownership prevents the prosumer from ``spamming'' the storage service with bogus asks.
+The prosumer can then
 post the energy ask \circled{4}, which contains an anonymous

### 2017-06-18 papers/IoT2017/transactions.tex
no message

@@
 they have to satisfy to be valid and recorded on the ledger.  We also
-introduce and detail the format of regulatory transactions, which the
-DSO uses to regulate the microgrid.\Abhishek{We need a figure describing the transactive system architecture.
-A collection of agents, arranged in a microgrid and a collection of microgrids being controlled by a DSO after the introduction}
+introduce and detail regulatory transactions, which the
+DSO uses to regulate the microgrid.
 
 \subsubsection{Timing}
-
 The ability to specify points or intervals in time is crucial.  For
@@
 \subsubsection{Energy and Financial Transactions}
-
 Energy and financial transactions transfer energy and financial assets
@@
   transferred only by its current owner. 
-% current owner can transfer an asset. 
 \item For each asset type (and for each timestep), the sums of the
@@
 & = \sum_{\substack{in \,\in\, \field{EPA\_in}:\\in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}}} in.\field{out}.\field{EPA}.\field{power}  .
-%
-%& \forall t: \sum_{out \in \field{EPA\_out}} out.\field{EPA}.\field{power} \cdot 1_{\left\{out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}\right\}} \nonumber \\
-%& = \sum_{in \in \field{EPA\_in}} in.\field{out}.\field{EPA}.\field{power} \cdot 1_{\left\{in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}\right\}} ,
 \end{align*}
-%where $1_x$ is equal to $1$ if $x$ is true, and it is $0$ otherwise.
-%\begin{equation}
-%\forall t: \sum_{out \in \left\{out' \middle| out' \in \text{ EPA outputs} \wedge out'.EPA.start \leq t \leq out'.EPA.end\right\}} out.EPA.Power = \sum_{in \in \left\{in' \middle| in' \in \text{ EPA inputs} \wedge in'.EPA.start \leq t \leq in'.EPA.end\right\}} in.EPA.Power .
-%\end{equation}
 The conditions for consumption and financial assets can be described
@@
 \end{itemize}
-%If a transaction submitted to the ledger is valid, it will be permanently recorded.
 
@@
 the set of authorized smart meters and (2) to change the price policy.
-%First, to change the set of smart meters that are authorized to sign transactions, the DSO authorizes or bans individual smart meters.
 First, whenever a new smart meter is installed, the DSO notifies the
@@
 A regulatory transaction of this type is valid if 
-%the following two conditions hold:
-%\begin{compactitem}
-%\item 
 \field{timestep} is not in the past and 
-% specified in the transaction is in the future.
-%\item 
 the DSO's signature is valid.
-%\end{compactitem}
-%
 The active prices for timestep $t$ are given by the last regulatory

### 2017-06-18 papers/IoT2017/intro.tex
submission ready

@@
 This paper assumes the existence of a distributed IoT infrastructure
-and specifically focuses on the following privacy challenges:
-\begin{itemize}[itemsep=0.25\parskip,topsep=-0.5\parskip]
+and focuses on the following privacy challenges:
+\begin{itemize}[itemsep=0.1\parskip,topsep=-0.75\parskip]
 \item \textbf{Leakage of Energy Usage Patterns to Other Prosumers} 
@@
   usage data in a transactive microgrid are much richer sources of
-  information than the simple energy usage data collected by smart
-  meters.  More specifically, the information available in a
+  information than the simple usage data collected by smart
+  meters.  Specifically, the information available in a
   transactive microgrid is a superset of what is available from smart

### 2017-06-18 papers/IoT2017/prelim.tex
submission ready

@@
 \section{System Model and Requirements}
+
 \change{This section describes a basic system model of transactive IoT
@@
 \Abhishek{This is the perfect paragraph to define transactive microgrid as a special application of IoT spread over a large area. Perhaps we can find a citation that makes this point.}
-We now describe a basic system model of decentralized 
+We describe a basic system model of decentralized 
 \Doug{Abhishek, if there's room can we add a diagram showing how all these components relate to each other?} 
@@
 \center
-\begin{tikzpicture}[x=8cm, y=0.9cm, font=\small,
+\begin{tikzpicture}[x=8cm, y=0.7cm, font=\small,
   nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
@@
 \subsubsection{Microgrid Controller (Distribution System Operator)}
-We assume the existence of a controller at the Distribution System Operator level that regulates the total load that the microgrid should present to the distribution system.
+We assume the existence of a controller at the DSO level that regulates the total load that the microgrid should present to the distribution system.
  The controller first predicts load in the microgrid
@@
 \item the net amount of energy sold (or bought) by a prosumer is upper
-  bounded (by an amount set by the DSO), where the net amount of
+  bounded (by a limit set by the DSO), where the net amount of
   energy sold is the difference between the amount of energy sold and
@@
 \end{itemize}
+In practice, the DSO can set the limits based on the prosumers' production and consumption capacities.
 

### 2017-06-18 papers/IoT2017/related.tex
submission ready

@@
 IoT system for transactive energy, and addressing the novel privacy
-threat posed by trading. In particular, while earlier results
-protected the prosumers' privacy from the DSO, we protect privacy from
-other prosumers as well as from outside attackers.
+threat posed by trading. In particular, while earlier work
+protected the prosumers' privacy from the DSO, we also protect it from
+other prosumers as well as outside attackers.
 
@@
 matures, new frameworks, services, and protocols are being developed
-to leverage blockchain's distributed ledger. For example, Hyperledger
+to leverage the distributed ledgers provided by blockchains. For example, Hyperledger
 Fabric is a platform for distributed ledger solutions, which was
 designed to support pluggable implementations of different
-components~\cite{hyperledger2017fabric}. Bitcoin Lightning Network is
-decentralized system, in which transactions are sent over a network of
-micropayment channels, whose transfer of value occurs
-off-blockchain~\cite{poon2016bitcoin}. Since this paper focuses on
-theoretical foundations of our implementation, any of these
+components~\cite{hyperledger2017fabric}. 
+%Bitcoin Lightning Network is
+%decentralized system, in which transactions are sent over a network of
+%micropayment channels, whose transfer of value occurs
+%off-blockchain~\cite{poon2016bitcoin}. 
+Since this paper focuses on
+the theoretical foundations of PETra, any of these
 distributed ledgers provide the required capabilities.

### 2017-06-20 papers/IoT2017/intro.tex
updates

@@
 
-Power grids are undergoing major changes due to rapid
-acceleration in renewable energy resources, such as wind and solar power \cite{5430489}. 
+Power grids are undergoing major changes due to rapid acceleration in
+renewable energy resources, such as wind and solar power
+\cite{5430489}.
 % \cite{EIA2014}
@@
 % \cite{bronski2015economics}
-This massive integration of renewable energy requires detailed
+The massive integration of renewable energy requires detailed
 information and visibility into all aspects of the network, making it
@@
 the demand and supply across the electrical infrastructure
-\cite{melton2013gridwise}. In this approach, customers on the same
-feeder (\emph{i.e.}, those sharing a power line link) can operate in an
-open market, trading and exchanging generated energy
-locally. Distribution System Operators (DSOs) can be the custodians of
-this market, while still meeting the net demand \cite{7462854}. For
-example, the Brooklyn Microgrid, which was developed by LO3 Energy as
-a pilot project, is a peer-to-peer market for locally generated
-renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}
+\cite{melton2013gridwise}. In this approach, prosumers\footnote{We
+  refer to customers as \emph{prosumers} to emphasize that they can
+  not only consume energy, but may also produce it.} on the same
+feeder (\emph{i.e.}, those sharing a power line link) can operate in
+an open market, trading and exchanging generated energy
+locally. \emph{Distribution System Operators} (DSOs) can be the
+custodians of this market, while still meeting the net demand
+\cite{7462854}. For example, the Brooklyn Microgrid
+(\url{brooklynmicrogrid.com}) is a peer-to-peer market for locally
+generated renewable energy developed by LO3 Energy as a pilot project.
 
@@
 supply, eventually destabilizing the system. In both cases, however,
-this system requires a distributed infrastructure comprising of smart
+this system requires a distributed infrastructure comprising smart
 meters, feeders, smart inverters, utility substations, the utility
@@
 between the energy control and the fiscal market challenges.
-Recently, demand-response systems have been enabled as applications of
-IoT in smart grid~\cite{Haider2016166}. Transactive grid is the next step \cite{collier2017emerging}.
+Recently, demand-response systems have been enabled as IoT
+applications in smart grids~\cite{Haider2016166}. The transactive grid
+described in this paper is the next step in the evolution of energy
+systems \cite{collier2017emerging}.
 
 In general, the focus is now on creating a distributed IoT
-infrastructure
-that provides the necessary computation fabric to support the
-interplay between energy control and fiscal market challenges, as
-shown by Volttron \cite{katipamula2016volttron}, OpenFMB
-\cite{gunthersmart}, and the Resilient Information Architecture
-Platform for Smart Grid (RIAPS)
+infrastructure that provides the necessary computation fabric to
+support the interplay between energy control and fiscal market
+challenges, as shown by Volttron \cite{katipamula2016volttron},
+OpenFMB \cite{gunthersmart}, and the Resilient Information
+Architecture Platform for Smart Grid (RIAPS)
 \cite{eisele2017riaps,Scott2017ICCPS}. For instance, the latter is a
@@
 \begin{itemize}[itemsep=0.1\parskip,topsep=-0.75\parskip]
-\item \textbf{Leakage of Energy Usage Patterns to Other Prosumers} 
- Since prosumers\footnote{We
-  refer to customers as \emph{prosumers} to emphasize that they can
-  not only consume energy, but may also produce it.} may purchase
-  energy from each other in a transactive microgrid, transactions may
-  inadvertently reveal the prosumers' detailed energy usage patterns
-  to other prosumers within the microgrid.  Addressing this issue in a
-  decentralized trading system is hard as it requires hiding the
-  identities of trade partners from each other. In comparison, secure
-  smart metering reveals the prosumers' energy usage patterns only to
-  the operator.
+\item \textbf{Leakage of energy usage patterns to other prosumers}
+  Since prosumers may purchase energy from each other in a transactive
+  microgrid, transactions may inadvertently reveal the prosumers'
+  detailed energy usage patterns to other prosumers within the
+  microgrid.  Addressing this issue in a decentralized trading system
+  is hard as it requires hiding the identities of trade partners from
+  each other. In comparison, secure smart metering reveals the
+  prosumers' energy usage patterns only to the operator.
 
-\item \textbf{Inference of Future States of a Prosumer} 
-  Transactions may reveal
-  the future energy usage of a prosumer, which could be used to infer
-  private information.  For example, a smart home may know that its
-  inhabitants will go out in the evening (\emph{e.g.}, by looking at
-  their calendar), and it may trade energy futures accordingly in the
-  morning.  Without adequate privacy measures, these trades may reveal
-  to other prosumers in the microgrid that the inhabitants will not be
-  at home later.  Note that energy
-  futures, whose delivery may happen several hours after when the
-  transaction is made, can play an important role in predicting and
-  controlling microgrid load.  In comparison, smart metering reveals
-  only current (or past) usage.
+\item \textbf{Inference of future states of a prosumer} Transactions
+  may reveal the future energy usage of a prosumer, which could be
+  used to infer private information.  For example, a smart home may
+  know that its inhabitants will go out in the evening (\emph{e.g.},
+  by looking at their calendar), and it may trade energy futures
+  accordingly in the morning.  Without adequate privacy measures,
+  these trades may reveal to other prosumers in the microgrid that the
+  inhabitants will not be at home later.  Note that energy futures,
+  whose delivery may happen several hours after when the transaction
+  is made, can play an important role in predicting and controlling
+  microgrid load.  In comparison, smart metering reveals only current
+  (or past) usage.
 
-\item \textbf{Personally Identifiable Information} 
-  Transactions and energy
-  usage data in a transactive microgrid are much richer sources of
-  information than the simple usage data collected by smart
-  meters.  Specifically, the information available in a
-  transactive microgrid is a superset of what is available from smart
-  metering, and it may be used to infer personal information, such as
-  risk propensity and financial standing.
+\item \textbf{Personally identifiable information} Transactions and
+  energy usage data in a transactive microgrid are much richer sources
+  of information than the simple usage data collected by smart meters.
+  In particular, the information available in a transactive microgrid
+  is a superset of what is available from smart metering and may be
+  used to infer personal information, such as risk propensity and
+  financial standing.
 \end{itemize}
@@
 Before transactive energy systems can be deployed widely in practice,
-we must address the privacy issues described above. However, addressing these
-issues is hard since solutions must also satisfy security
-and safety requirements, which often conflict with privacy goals.  For
-example, to prevent a prosumer from destabilizing the grid through
-careless of malicious energy trading, the system must check all of the
-prosumer's transactions.  In a decentralized system, this requires
-disseminating information, which could be used to infer the prosumer's
-future energy consumption.
+the privacy issues described above must be addressed.  Addressing
+these issues is hard, however, since solutions must also satisfy
+security and safety requirements, which often conflict with privacy
+goals.  For example, to prevent a prosumer from destabilizing the
+system through careless of malicious energy trading, a transactive
+grid must check all of the prosumer's transactions.  In a
+decentralized system, these checks require disseminating information,
+which could be used to infer the prosumer's future energy consumption.
 
-In this paper, we \change{describe an overview of the transactive sequence between different components of the systems.
-We also describe in the detail the structure of these transactions and show how these transactions}{propose \emph{Privacy-preserving Energy Transactions} (PETra), a distributed-ledger based solution that} (1) enables trading energy futures in a
-secure and verifiable manner, (2) preserves prosumer privacy, and (3)
-enables DSOs to regulate trading and enforce certain
+This paper describes an overview of the transactive sequence between
+different components of the systems. We also describe the structure of
+these transactions and show how they can be used to provide
+\emph{Privacy-preserving Energy Transactions} (PETra). PETra is our
+distributed-ledger based solution that (1) enables trading energy
+futures in a secure and verifiable manner, (2) preserves prosumer
+privacy, and (3) enables DSOs to regulate trading and enforce certain
 safety rules.
-%
-\Aron{Since SIGCHI does not have section numbers, this paragraph, which describes the organization of the paper, is not very clear.}  
-We first describe the basic components of a
-transactive IoT microgrid and formulate security, safety, and privacy
-requirements.  Next, we introduce PETra and describe the
-transactions and services used to implement it.  We then
-discuss how PETra satisfies the security, safety, and privacy
-requirements.  Finally, we give a brief overview of related work and
-offer concluding remarks.
+
+% \Aron{Since SIGCHI does not have section numbers, this paragraph,
+%  which describes the organization of the paper, is not very clear.}
+The remainder of this paper is organized as follows: we first describe
+the basic components of a transactive IoT microgrid and formulate
+security, safety, and privacy requirements; we next introduce PETra
+and describe the transactions and services used to implement it; we
+then discuss how PETra satisfies the security, safety, and privacy
+requirements; finally we compare our work on PETra with related work
+and present concluding remarks.

### 2017-06-20 papers/IoT2017/paper.tex
updates

@@
 systems increases.  To tackle these challenges, decentralized
-Internet-of-Things (IoT) solutions are emerging, which may arrange
-local communities into transactive microgrids.  Within a transactive
-microgrid, consumers with energy generation and storage capabilities
-can trade energy with each other, thereby smoothing the load on the
-main grid using local supply. However, it is hard to provide
-security, safety, and privacy in a decentralized and transactive
-energy system.  On the one hand, consumers' personal information must
-be protected from their trade partners and the
-system operator.  On the other hand, the system must be protected from
+Internet-of-Things (IoT) solutions are emerging, which arrange local
+communities into transactive microgrids.  Within a transactive
+microgrid, ``prosumers'' (i.e., consumers with energy generation and
+storage capabilities) can trade energy with each other, thereby
+smoothing the load on the main grid using local supply.  It is hard,
+however, to provide security, safety, and privacy in a decentralized
+and transactive energy system.  On the one hand, prosumers' personal
+information must be protected from their trade partners and the system
+operator.  On the other hand, the system must be protected from
 careless or malicious trading, which could destabilize the entire
-grid.  This paper describes \change{our}{\emph{Privacy-preserving Energy Transactions} (PETra), a} secure and safe solution for
-transactive microgrids, which enables consumers to trade energy
-without sacrificing their privacy.  \change{Our solution}{PETra} builds on distributed
-ledgers, such as blockchains, and provides anonymity for
-communication, bidding, and trading.
+grid.  This paper describes \change{our}{\emph{Privacy-preserving
+    Energy Transactions} (PETra)}, which is secure and safe solution
+for transactive microgrids that enables consumers to trade energy
+without sacrificing their privacy.  \change{Our solution}{PETra}
+builds on distributed ledgers, such as blockchains, and provides
+anonymity for communication, bidding, and trading.
 \end{abstract}

### 2017-06-20 papers/IoT2017/prelim.tex
updates

@@
 
-\change{This section describes a basic system model of transactive IoT
-microgrids and formulates security, safety, and privacy requirements.}{A microgrid is a collection of prosumers (residential nodes) that are arranged within the same distribution feeder which supports exchange of power between them.
-A prosumer node typically includes a smart inverter and a smart meter, which control the flow of power into and out of the prosumer.
-Additionally, the microgrid contains a set of
-protection nodes that are  responsible for isolating faults on the feeder.
-Finally, a set of switching nodes, which are operated by the Distribution System Operator (DSO), control the connection of the microgrid to the rest of the distribution system.
-The DSO is responsible for regulating the net electric power into and out of the microgrid.
-Starting from this model, we next introduce the transactive microgrid model.}
+This section describes a basic system model of transactive IoT
+microgrids and formulates security, safety, and privacy requirements.
+A microgrid is a collection of prosumers (residential nodes) that are
+arranged within the same distribution feeder and support exchange of
+power between them. A prosumer node typically includes a smart
+inverter and a smart meter, which control the flow of power into and
+out of the prosumer.
+
+A microgrid also typically contains a set of protection nodes that are
+responsible for isolating faults on the feeder.  The
+\emph{Distribution System Operator} (DSO) operations a set of
+switching nodes to control the connection of the microgrid to the rest
+of the distribution system. The DSO is responsible for regulating the
+net electric power into and out of the microgrid. Starting from this
+model, we next introduce the transactive microgrid model.
 
 \subsection{Transactive Microgrid System Model}
-\Abhishek{This is the perfect paragraph to define transactive microgrid as a special application of IoT spread over a large area. Perhaps we can find a citation that makes this point.}
-We describe a basic system model of decentralized 
-\Doug{Abhishek, if there's room can we add a diagram showing how all these components relate to each other?} 
-transactive IoT microgrids.  We discuss the following components: a
-distributed ledger for recording transactions, a bid storage service
-that facilitates finding trade partners, a microgrid controller for
-regulating the microgrid load, and smart meters for measuring the
-prosumers' energy production and consumption.
-Figure~\ref{fig:softwareArchitecture} shows the high-level architecture of 
-\change{our solution.  In this figure, components marked red are introduced to
-provide privacy in a safe and secure manner, whereas components marked
-in blue are typical elements of a decentralized transactive microgrid.}{a decentralized transactive microgrid with PETra. 
-Components marked in blue are basic elements of the decentralized transactive microgrid,
-while components marked in red are added (or extended) by PETra.}
+\Abhishek{This is the perfect paragraph to define transactive
+  microgrid as a special application of IoT spread over a large
+  area. Perhaps we can find a citation that makes this point.}  We
+describe a basic system model of decentralized transactive IoT
+microgrids.  We discuss the following components: a distributed ledger
+for recording transactions, a bid storage service that facilitates
+finding trade partners, a microgrid controller for regulating the
+microgrid load, and smart meters for measuring the prosumers' energy
+production and consumption.
 
+Figure~\ref{fig:softwareArchitecture} shows the a decentralized
+transactive microgrid with PETra.  In this figure, components marked
+red are introduced to provide privacy in a safe and secure manner,
+whereas components marked in blue are typical elements of a
+decentralized transactive microgrid.
 \begin{figure}[h!]
@@
 \end{tikzpicture}
-\caption{High-level architecture of a decentralized transactive microgrid with PETra.}
+\caption{The Architecture of a Decentralized Transactive Microgrid with PETra.}
 \label{fig:softwareArchitecture}
@@
 trades, change regulatory policies for the microgrid, etc.  For
-providing security and safety, it is crucial that transactions are
+providing security and safety, it is crucial that transactions be
 immutable, \emph{i.e.}, after a transaction has been recorded, it
@@
 without a middleman), for the sake of scalability, we need a service
-that enables prosumers to find trade partners.
-We assume that there is a bid storage service that allows prosumers to
-post and read energy \emph{bids} and \emph{asks}.\footnote{A
-  \emph{bid} is an offer to buy at a certain price, while an
-  \emph{ask} is an offer to sell at a certain price.}  This service
-relieves prosumers from contacting a large number of potential trade
-partners since they only communicate with the service to discover
-trade partners.
-To enhance scalability and reliability, this service can also be
-implemented in a distributed manner, using multiple nodes.
+that enables prosumers to find trade partners.  We assume that there
+is a bid storage service that allows prosumers to post and read energy
+\emph{bids} and \emph{asks}.\footnote{A \emph{bid} is an offer to buy
+  at a certain price, while an \emph{ask} is an offer to sell at a
+  certain price.}  This service relieves prosumers from contacting a
+large number of potential trade partners since they only communicate
+with the service to discover trade partners.  To enhance scalability
+and reliability, this service can also be implemented in a distributed
+manner, using multiple nodes.
 
 \subsubsection{Microgrid Controller (Distribution System Operator)}
-We assume the existence of a controller at the DSO level that regulates the total load that the microgrid should present to the distribution system.
- The controller first predicts load in the microgrid
-based on (1) bids and asks in the bid storage and (2) outstanding
-energy trades in the ledger.  By combining this information with the
-prediction for the rest of the grid, the controller produces a control
-signal that specifies how much the microgrid load should be decreased
-or increased.  Based on this signal, the controller then updates the
-price policy for the microgrid to influence energy production and
-consumption.  We also assume the presence of a secondary controller
-that balances voltage and frequency in the microgrid.
+We assume the existence of a controller at the DSO level that
+regulates the total load that the microgrid should present to the
+distribution system.  The controller first predicts load in the
+microgrid based on (1) bids and asks in the bid storage and (2)
+outstanding energy trades in the ledger.  By combining this
+information with the prediction for the rest of the grid, the
+controller produces a control signal that specifies how much the
+microgrid load should be decreased or increased.  Based on this
+signal, the controller then updates the price policy for the microgrid
+to influence energy production and consumption.  We also assume the
+presence of a secondary controller that balances voltage and frequency
+in the microgrid.
 
@@
   information regarding the amount of energy produced, consumed,
-  bought, or sold by a prosumer,\footnote{Note that this requirement
-    is impossible to satisfy if all other prosumers may collude
-    against one target. However, we can assume that the majority of
-    prosumers are non-colluding.}
+  bought, or sold by a prosumer,\footnote{Although this requirement is
+    impossible to satisfy if all other prosumers may collude against
+    one target, we can assume that the majority of prosumers are
+    non-colluding.}
 \item only the prosumer may know which bids and asks it has posted,

### 2017-06-20 papers/IoT2017/analysis.tex
submission ready
updates

@@
 
-This section presents a semi-formal analysis of PETra
-and shows that it satisfies the security, safety, and privacy
-requirements formulated earlier.
+This section presents a semi-formal analysis of PETra and shows that
+it satisfies the security, safety, and privacy requirements formulated
+earlier.
 
@@
 \item immutability of transactions in the distributed ledger,
-\item validity conditions of the transactions, which include conditions on both signatures and asset balances,
+\item validity conditions of the transactions, which include
+  conditions on both signatures and asset balances,
 \item and tamper-resistance of smart meters.
@@
 excessive amounts of energy if normal prosumers follow the rules of
-the trading workflow.
-%
-First, we can show that the net amount of energy sold by prosumer $i$ for
-each timestep is at most $\field{MAXEPA}_i$.  By definition, the
-amount of energy sold is less than or equal to the amount of EPA
-obtained by prosumer $i$.  A prosumer can obtain EPA either by
-withdrawing from its smart meter or by purchasing form another
-prosumer.  From its smart meter, prosumer $i$ can withdraw at most
-$\field{MAXEPA}_i$.
-Although the prosumer may also buy EPA from another prosumer, this
-constitutes buying energy, which decreases the net amount of energy
-sold with the same amount.
-Hence, the net amount of energy sold by prosumer $i$ cannot exceed
-$\field{MAXEPA}_i$.  By extending the argument, we can show that the net
-amount of energy sold by a group of prosumers~$G$ cannot exceed
-$\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, we can show that the net
-amount of energy bought by a group of prosumers $G$ cannot exceed
-$\sum_{i \in G} \field{MAXECA}_i$.
+the trading workflow.  First, we can show that the net amount of
+energy sold by prosumer $i$ for each timestep is at most
+$\field{MAXEPA}_i$.  By definition, the amount of energy sold is less
+than or equal to the amount of EPA obtained by prosumer $i$.
+
+A prosumer can obtain EPA either by withdrawing from its smart meter
+or by purchasing form another prosumer.  From its smart meter,
+prosumer $i$ can withdraw at most $\field{MAXEPA}_i$.  Although the
+prosumer may also buy EPA from another prosumer, this constitutes
+buying energy, which decreases the net amount of energy sold with the
+same amount.  Hence, the net amount of energy sold by prosumer $i$
+cannot exceed $\field{MAXEPA}_i$.  By extending the argument, we can
+show that the net amount of energy sold by a group of prosumers~$G$
+cannot exceed $\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, %we can
+show that the net amount of energy bought by a group of prosumers $G$
+cannot exceed $\sum_{i \in G} \field{MAXECA}_i$.
 
@@
 of a microgrid can observe only the amount of assets withdrawn by a
-prosumer from its smart meter.
-Since all trading transactions are anonymous, they do not reveal the
-actual amount of assets traded by the prosumer.  If a prosumer has not traded away all of its assets, 
-then it can also anonymously deposit the remainder to
-a random address that was freshly generated by its smart meter. Note that even
-if a prosumer does not wish to trade, it should always
-withdraw, mix, and deposit the same amount of assets.  Otherwise, the
-lack (or varying amount) of withdrawal would leak information.
+prosumer from its smart meter.  Since all trading transactions are
+anonymous, they do not reveal the actual amount of assets traded by
+the prosumer.  If a prosumer has not traded away all of its assets,
+then it can also anonymously deposit the remainder to a random address
+that was freshly generated by its smart meter. Even if a prosumer does
+not wish to trade, it should always withdraw, mix, and deposit the
+same amount of assets.  Otherwise, the lack (or varying amount) of
+withdrawal would leak information.
 

### 2017-06-20 papers/IoT2017/concl.tex
updates

@@
-\section{Conclusion}
+\section{Concluding Remarks}
 \label{sec:concl}
@@
 
-This paper describes \change{how we address these challenges via}{\emph{Privacy-preserving Energy Transactions} (PETra),} an
+This paper describes how we address these challenges via
+\emph{Privacy-preserving Energy Transactions} (PETra), which is our
 innovative solution for anonymous energy trading within a transactive
-microgrid.  PETra builds on distributed ledgers, such as
-blockchains, and proven techniques for anonymity, such as mixing
-services and onion routing.  We described the workflow of
-anonymous energy trading and explained the novel transactions and
-services used in PETra.  Finally, we discussed how PETra
- satisfies security, safety, and privacy requirements.  In
-future work, we will provide rigorous proofs of satisfying these
-requirements, and we will present an implementation of PETra with
-performance results.
+microgrid.  PETra builds on distributed ledgers, such as blockchains,
+and proven techniques for anonymity, such as mixing services and onion
+routing.  We described the workflow of anonymous energy trading and
+explained the novel transactions and services used in PETra.  Finally,
+we discussed how PETra satisfies security, safety, and privacy
+requirements.  In future work, we will provide rigorous proofs of
+satisfying these requirements, and we will present an implementation
+of PETra with performance results.

### 2017-06-20 papers/IoT2017/related.tex
updates

@@
 
-Additionally, other approaches such as additional hardware components
-are explored for potential privacy gains. Varodayan and Khisti study
-using a rechargeable battery for partially protecting the privacy of
+Other approaches, such as additional hardware components, are explored
+for potential privacy gains. Varodayan and Khisti study using a
+rechargeable battery for partially protecting the privacy of
 information contained in a household's electrical load
@@
 
-PETra extends this earlier work by considering a decentralized
-IoT system for transactive energy, and addressing the novel privacy
-threat posed by trading. In particular, while earlier work
-protected the prosumers' privacy from the DSO, we also protect it from
-other prosumers as well as outside attackers.
+PETra extends this earlier work by (1) leveraging a decentralized IoT
+system for transactive energy and (2) addressing the novel privacy
+threat posed by trading. In particular, while earlier work protected
+the prosumers' privacy from the DSO, PETra also protects it from other
+prosumers, as well as outside attackers.
 
-A key element of our approach is the ability to distribute information
-among peers via blockchains.  As blockchain technology develops and
-matures, new frameworks, services, and protocols are being developed
-to leverage the distributed ledgers provided by blockchains. For example, Hyperledger
-Fabric is a platform for distributed ledger solutions, which was
-designed to support pluggable implementations of different
+A key element of PETra is its ability to distribute information among
+peers via blockchains.  As blockchain technology develops and matures,
+new frameworks, services, and protocols are being developed to
+leverage the distributed ledgers provided by blockchains. For example,
+Hyperledger Fabric is a platform for distributed ledger solutions,
+which was designed to support pluggable implementations of different
 components~\cite{hyperledger2017fabric}.
@@
 %off-blockchain~\cite{poon2016bitcoin}. 
-Since this paper focuses on
-the theoretical foundations of PETra, any of these
-distributed ledgers provide the required capabilities.
+Since this paper focuses on the theoretical foundations of PETra, any
+of these distributed ledgers provide the required capabilities.
 
@@
 
-As Blockchain technology continues to develop and mature, new frameworks, services, and protocols are being developed to leverage blockchain's distributed ledger.
-Microsoft offers Blockchain as a Service (BaaS) on Azure.
-Additionally, Microsoft has Project Bletchley as its architectural approach to building an Enterprise Consortium Blockchain Ecosystem, introducing two new concepts: blockchain middleware and a secure means for calling code or data outside a SmartContract or blockchain called cryptlets~\cite{gray2016introducing}.
-Hyperledger Fabric is a platform for distributed ledger solutions, which was designed to support pluggable implementations of different components~\cite{hyperledger2017fabric}.
-Bitcoin Lightning Network is decentralized system, in which transactions are sent over a network of micropayment channels whose transfer of value occurs off-blockchain~\cite{poon2016bitcoin}.
-Interledger is a protocol for payments across payment systems, which enables anyone with accounts on two ledgers to create
-a connection between them~\cite{thomas_protocol}.
-Xu et al.\ discuss the use of two pools of proxy agents, an agreement pool and a payment pool, to assist in protection of privacy when using blockchain technologies for transactions on tangible goods~\cite{Xu2017}.
-\fi
+As Blockchain technology continues to develop and mature, new
+frameworks, services, and protocols are being developed to leverage
+blockchain's distributed ledger. Microsoft offers Blockchain as a
+Service (BaaS) on Azure. Additionally, Microsoft has Project Bletchley
+as its architectural approach to building an Enterprise Consortium
+Blockchain Ecosystem, introducing two new concepts: blockchain
+middleware and a secure means for calling code or data outside a
+SmartContract or blockchain called
+cryptlets~\cite{gray2016introducing}. Hyperledger Fabric is a platform
+for distributed ledger solutions, which was designed to support
+pluggable implementations of different
+components~\cite{hyperledger2017fabric}. Bitcoin Lightning Network is
+decentralized system, in which transactions are sent over a network of
+micropayment channels whose transfer of value occurs
+off-blockchain~\cite{poon2016bitcoin}. Interledger is a protocol for
+payments across payment systems, which enables anyone with accounts on
+two ledgers to create a connection between
+them~\cite{thomas_protocol}. Xu et al.\ discuss the use of two pools
+of proxy agents, an agreement pool and a payment pool, to assist in
+protection of privacy when using blockchain technologies for
+transactions on tangible goods~\cite{Xu2017}.  \fi
 

### 2017-06-20 papers/IoT2017/services.tex
updates

@@
 We now describe the various services that are provided in PETra.
-Earlier, we discussed the distributed ledger, which permanently stores
-valid transactions.  Below, we introduce the anonymous communication
-service, the mixing service for transaction anonymity, the anonymous
-bid storage, and smart-meter based billing.
+Earlier, we discussed PETra's distributed ledger, which permanently
+stores valid transactions.  Below, we introduce the anonymous
+communication service, the mixing service for transaction anonymity,
+the anonymous bid storage, and smart-meter based billing.
 
@@
 microgrid can be published on the ledger.  In practice, this service
-can be built on 
-the free and open-source Tor software with private Directory
-Authorities.  In this case, anonymous communication identifiers in
-bids and asks correspond to public-keys that identify Tor hidden
-services.
+can be built on the free and open-source Tor software with private
+Directory Authorities.  In this case, anonymous communication
+identifiers in bids and asks correspond to public-keys that identify
+Tor hidden services.
 % ritter.vg: "run your own tor network"
@@
 at random, which are anonymous in the sense that no one can tell who
-generated them.  However, if prosumers simply transferred assets to these
-addresses, they could be easily de-anonymized by tracing the
+generated them.  If prosumers simply transferred assets to these
+addresses, however, they could be easily de-anonymized by tracing the
 assets back to the prosumers.
@@
 simplest one is to use a \emph{trusted third party}, called a
-cryptocurrency tumbler, which can receive and send assets. However, anonymity
-in this case depends on the trustworthiness and reliability
+cryptocurrency tumbler, which can receive and send assets. Anonymity
+in this case, however, depends on the trustworthiness and reliability
 of the third party, who could easily de-anonymize the addresses.  A
@@
 mix assets with each other, thereby eliminating the need for a trusted
-third party.
-Some newer cryptocurrencies, such as
+third party.  Some newer cryptocurrencies, such as
 Zerocoin~\cite{miers2013zerocoin}, provide built-in mixing services,
@@
 \subsubsection{Bidding Anonymity}
-Prosumers must also be able to anonymously post energy bids and asks on the
-bid storage service.  An anonymous bid (or ask) contains an ECA (or
-EPA), a price, and an anonymous communication identifier (\emph{e.g.},
-Tor hidden service), which can be used to contact the bidding (or
-asking) prosumer.  To enforce safety requirements, the bid storage
-service must verify that the prosumer actually owns the asset to be
-traded.  To this end, the prosumer first has to prove that it controls
-the anonymous address where the asset is stored, which can be
+Prosumers must also be able to anonymously post energy bids and asks
+on the bid storage service.  An anonymous bid (or ask) contains an ECA
+(or EPA), a price, and an anonymous communication identifier
+(\emph{e.g.}, Tor hidden service), which can be used to contact the
+bidding (or asking) prosumer.  To enforce safety requirements, the bid
+storage service must verify that the prosumer actually owns the asset
+to be traded.  To this end, the prosumer first has to prove that it
+controls the anonymous address where the asset is stored, which can be
 performed in multiple ways.
@@
 compute the prosumer's bill for timeslot $t$, which will be paid to
-the DSO, as follows. \Abhishek{The safety argument should be strengthened here}
+the DSO, as follows. \Abhishek{The safety argument should be
+  strengthened here}
 

### 2017-06-20 papers/IoT2017/solution.tex
updates

@@
 
-This section describes Privacy-preserving Energy Transactions (PETra), our solution for providing privacy to prosumers
-in a transactive energy IoT system, without compromising grid safety
-and security.
-
+This section describes \emph{Privacy-preserving Energy Transactions}
+(PETra), which is our solution for providing privacy to prosumers in a
+transactive energy IoT system, without compromising grid safety and
+security.
 \begin{figure*}[h]
@@
 \end{tikzpicture}
-\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy.
-Note that to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing, which we have omitted from the figure for clarity of presentation.}
+\caption{Simplified Overview of the Flow of Assets from the Perspective of a Prosumer Who Sells Energy.}
 \label{fig:sellFlow}
@@
 \subsection{Overview of the Trading Workflow}
-We now provide a semi-formal description of the energy trading workflow
-from the prosumers' perspective. 
-Subsequent subsections will describe the assets, transactions, and services used for trading in more detail.
+We now provide a semi-formal description of the energy trading
+workflow from the prosumers' perspective.  Subsequent subsections
+describe the assets, transactions, and services used for trading in
+more detail.
 
 \subsubsection{Energy Selling Workflow}
-Consider a prosumer who wishes to sell energy to another
-prosumer, as shown in Figure~\ref{fig:sellFlow}\Abhishek{We need to mention what is the expected deadline by which this sequence of task should finish. }. 
-As its first step, the prosumer withdraws an \emph{energy production asset} from its smart meter.
-An energy production asset represents a permission to sell a certain amount of energy, and it is used to enforce safety requirements.
-If the prosumer has sufficient unsold production capacity, the smart meter creates and transfers a production asset to the prosumer using a \emph{smart meter transaction} \circled{1}, which is recorded on the distributed ledger.
+Consider a prosumer who wishes to sell energy to another prosumer, as
+shown in Figure~\ref{fig:sellFlow}\footnote{To prevent
+  de-anonymization, a prosumer should use multiple addresses and
+  multiple rounds of mixing, which we have omitted from the figure for
+  clarity of presentation.}  \Abhishek{We need to mention what is the
+  expected deadline by which this sequence of task should finish.}  As
+its first step, the prosumer withdraws an \emph{energy production
+  asset} from its smart meter.  An energy production asset represents
+a permission to sell a certain amount of energy, and it is used to
+enforce safety requirements.  If the prosumer has sufficient unsold
+production capacity, the smart meter creates and transfers a
+production asset to the prosumer using a \emph{smart meter
+  transaction} \circled{1}, which is recorded on the distributed
+ledger.
 
-At this point, the production asset can still be traced back to the prosumer since the ledger is public.
-To achieve anonymity, the prosumer uses a \emph{mixing service}, which could be implemented as a decentralized protocol, such as CoinShuffle~\cite{ruffing2014coinshuffle} or Xim~\cite{bissias2014sybil}.
-The prosumer transfers the production asset to the mixing service using an \emph{energy and financial transaction} \circled{2}, which is also recorded on the distributed ledger.
-In turn, the mixing service
-transfers the production asset to an \emph{anonymous address} \circled{3},
-which is randomly generated and controlled by the
-prosumer.\footnote{The concept of \emph{address} varies between distributed ledgers, but PETra could be implemented using any popular blockchain, such as Bitcoin and Ethereum. 
-Specifically, we use the term address to denote a possible destination for asset transfers. 
-Assets that have been transferred to an address can be used only by someone who ``controls'' the address (typically, the one who generated it), which usually means knowing a private key that corresponds to the address.}
-Since the mixing service transfers assets from multiple prosumers to
-multiple anonymous addresses at the same time, and the anonymous
-addresses were generated at random by the prosumers, the assets
-cannot be traced back to the original prosumers after
-mixing.\footnote{Note that prosumers should divide their assets between multiple
-  anonymous addresses; otherwise, each asset might be traced back to
-  its prosumer based on the amount of energy that it contains.}
+At this point, the production asset can still be traced back to the
+prosumer since the ledger is public.  To achieve anonymity, the
+prosumer uses a \emph{mixing service}, which could be implemented as a
+decentralized protocol, such as
+CoinShuffle~\cite{ruffing2014coinshuffle} or
+Xim~\cite{bissias2014sybil}.  The prosumer transfers the production
+asset to the mixing service using an \emph{energy and financial
+  transaction} \circled{2}, which is also recorded on the distributed
+ledger.  In turn, the mixing service transfers the production asset to
+an \emph{anonymous address} \circled{3}, which is randomly generated
+and controlled by the prosumer.\footnote{The concept of \emph{address}
+  varies between distributed ledgers, but PETra could be implemented
+  using any popular blockchain, such as Bitcoin and Ethereum.
+  Specifically, we use the term address to denote a possible
+  destination for asset transfers.  Assets that have been transferred
+  to an address can be used only by someone who ``controls'' the
+  address (typically, the one who generated it), which usually means
+  knowing a private key that corresponds to the address.}  Since the
+mixing service transfers assets from multiple prosumers to multiple
+anonymous addresses at the same time, and the anonymous addresses were
+generated at random by the prosumers, the assets cannot be traced back
+to the original prosumers after mixing.\footnote{Note that prosumers
+  should divide their assets between multiple anonymous addresses;
+  otherwise, each asset might be traced back to its prosumer based on
+  the amount of energy that it contains.}
 
@@
 storage service---without revealing its original identity---that it
-owns a production asset stored at an anonymous address. 
-\Aron{This sentence was added because we removed the relevant safety requirement.}
-Proving ownership prevents the prosumer from ``spamming'' the storage service with bogus asks.
-The prosumer can then
-post the energy ask \circled{4}, which contains an anonymous
-communication identifier\footnote{We discuss communication anonymity later.}, a price, and a reference
-to the production asset.  If another prosumer, who is seeking to buy energy,
-finds the ask acceptable it can contact the seller using the
-communication identifier included in the ask.
+owns a production asset stored at an anonymous address.  Proving
+ownership prevents the prosumer from ``spamming'' the storage service
+with bogus asks.  The prosumer can then post the energy ask
+\circled{4}, which contains an anonymous communication
+identifier\footnote{We discuss communication anonymity later.}, a
+price, and a reference to the production asset.  If another prosumer,
+who is seeking to buy energy, finds the ask acceptable it can contact
+the seller using the communication identifier included in the ask.
 
@@
 amount from the prosumer for billing purposes.  To enforce safety
-requirements, the prosumer is required to always deposit the same amount of
-consumption assets as the amount of production assets withdrawn at the
-beginning; otherwise, unaccounted assets could be used to trade
-excessive amounts.
+requirements, the prosumer is required to always deposit the same
+amount of consumption assets as the amount of production assets
+withdrawn at the beginning; otherwise, unaccounted assets could be
+used to trade excessive amounts.
 
 \subsubsection{Energy Buying Workflow}
-Consider a prosumer who would like to buy energy from another prosumer.
-Since the trading workflow is very similar to the case of the selling prosumer, we will discuss only the differences.
-In the first step, the prosumer tries to withdraw a financial asset and an energy consumption asset from its smart meter.
-If the prosumer has the consumption capacity and good financial standing, the smart meter transfers the assets to the prosumer and adds the financial amount to the prosumer's bill.
+Consider a prosumer who would like to buy energy from another
+prosumer.  Since the trading workflow is very similar to the case of
+the selling prosumer, we will discuss only the differences.  In the
+first step, the prosumer tries to withdraw a financial asset and an
+energy consumption asset from its smart meter.  If the prosumer has
+the consumption capacity and good financial standing, the smart meter
+transfers the assets to the prosumer and adds the financial amount to
+the prosumer's bill.
 
-After transferring the assets through a mixing service, the prosumer is ready to post an energy bid on the bid service.
-To do so, it first proves the ownership of both the financial asset and the consumption asset to the service, and then posts the energy bid, which includes an anonymous communication identifier.
-If a partner is found, the trade is executed as described above, with the prosumer playing the role of the buyer this time.
+After transferring the assets through a mixing service, the prosumer
+is ready to post an energy bid on the bid service.  To do so, it first
+proves the ownership of both the financial asset and the consumption
+asset to the service, and then posts the energy bid, which includes an
+anonymous communication identifier.  If a partner is found, the trade
+is executed as described above, with the prosumer playing the role of
+the buyer this time.
 
-Finally, the prosumer deposits the purchased energy production asset to the anonymous address of its smart meter,
-which credits the energy amount to the prosumer, for billing purposes.
-Note that if the prosumer has not spent all of its financial assets, then the remainder may also be deposited back to the smart meter.
+Finally, the prosumer deposits the purchased energy production asset
+to the anonymous address of its smart meter, which credits the energy
+amount to the prosumer, for billing purposes.  Note that if the
+prosumer has not spent all of its financial assets, then the remainder
+may also be deposited back to the smart meter.
 

### 2017-06-20 papers/IoT2017/transactions.tex
updates

@@
 
-In the previous subsection, we gave an overview of how transactions
-are used in the trading workflow to transfer various assets.  We now
-describe the format of these transactions, as well as the rules that
-they have to satisfy to be valid and recorded on the ledger.  We also
-introduce and detail regulatory transactions, which the
-DSO uses to regulate the microgrid.
+The previous subsection gave an overview of how PETRa uses
+transactions in the trading workflow to transfer various assets.  We
+now describe the format of these transactions, as well as the rules
+that they have to satisfy to be valid and recorded on the ledger.  We
+also introduce and detail regulatory transactions, which the DSO uses
+to regulate the microgrid.
 
@@
 \subsubsection{Assets}
-Before we can discuss transactions, we need to define the format of the three
-types of assets that these transactions may transfer.  First, an
-\emph{energy production asset} (EPA) is defined by
+Before we can discuss transactions, we need to define the format of
+the three types of assets that these transactions may transfer.
+First, an \emph{energy production asset} (EPA) is defined by
 \begin{itemize}[noitemsep,topsep=-\parskip]
@@
 
-A regulatory transaction of this type is valid if 
-\field{timestep} is not in the past and 
-the DSO's signature is valid.
-The active prices for timestep $t$ are given by the last regulatory
-transaction recorded on the ledger whose \field{time} is less than
-$t$.  Likewise, regulatory transactions that are recorded on the
-ledger later override the authorizations and bans of earlier
-transactions.
+A regulatory transaction of this type is valid if \field{timestep} is
+not in the past and the DSO's signature is valid.  The active prices
+for timestep $t$ are given by the last regulatory transaction recorded
+on the ledger whose \field{time} is less than $t$.  Likewise,
+regulatory transactions that are recorded on the ledger later override
+the authorizations and bans of earlier transactions.

### 2017-06-21 papers/IoT2017/concl.tex
update

@@
+%!TEX root = paper.tex
 \section{Concluding Remarks}
@@
 to tackle this complexity. Ironically, these decentralized systems
-also give rise to new privacy challenges,
+also give rise to new privacy challenges, such as leakage of energy usage patterns, including the possibility of inference of future state of a prosumer, 
 \Doug{Abhishek, please briefly list the key privacy challenges we cover in this paper.}
@@
 requirements.  In future work, we will provide rigorous proofs of
-satisfying these requirements, and we will present an implementation
-of PETra with performance results.
+satisfying these requirements.
+% and we will present an implementation
+%of PETra with performance results.

### 2017-06-21 papers/IoT2017/related.tex
update

@@
 
-PETra extends this earlier work by (1) leveraging a decentralized IoT
+PETra extends this work by (1) leveraging a decentralized IoT
 system for transactive energy and (2) addressing the novel privacy

### 2017-06-21 papers/IoT2017/analysis.tex
updates

@@
+%!TEX root = paper.tex
 \section{Discussion}
@@
 energy sold by prosumer $i$ for each timestep is at most
-$\field{MAXEPA}_i$.  By definition, the amount of energy sold is less
+$\field{MAXEPA}_i$.  By definition, \textcolor{blue}{we assume that the smart meters enforce a constraint, which ensures that} the amount of energy sold is less
 than or equal to the amount of EPA obtained by prosumer $i$.
@@
 cannot exceed $\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, %we can
-show that the net amount of energy bought by a group of prosumers $G$
+%show that
+ the net amount of energy bought by a group of prosumers $G$
 cannot exceed $\sum_{i \in G} \field{MAXECA}_i$.

### 2017-06-21 papers/IoT2017/concl.tex
updates

@@
 to tackle this complexity. Ironically, these decentralized systems
-also give rise to new privacy challenges, such as leakage of energy usage patterns, including the possibility of inference of future state of a prosumer, 
+also give rise to new privacy challenges, \textcolor{blue}{such as leakage of energy usage patterns, including the possibility of inference of future state of a prosumer}, 
 \Doug{Abhishek, please briefly list the key privacy challenges we cover in this paper.}

### 2017-06-21 papers/IoT2017/intro.tex
updates

@@
 third quarter of 2016 \cite{seia}. This capacity is estimated to grow
-from 4\% in 2015 to 29\% in 2040 \cite{Randal}. At the same time,
-battery technology costs per kWh have dropped significantly
-\cite{stock2015powerful}, reaching grid parity.
+from 4\% in 2015 to 29\% in 2040 \cite{Randal}. 
+%At the same time,
+%battery technology costs per kWh have dropped significantly
+%\cite{stock2015powerful}, reaching grid parity.
 % \cite{bronski2015economics}
@@
 %  which describes the organization of the paper, is not very clear.}
-The remainder of this paper is organized as follows: we first describe
+%The remainder of
+This paper is organized as follows: we first describe
 the basic components of a transactive IoT microgrid and formulate
@@
 and describe the transactions and services used to implement it; we
-then discuss how PETra satisfies the security, safety, and privacy
-requirements; finally we compare our work on PETra with related work
+then discuss how it satisfies the security, safety, and privacy
+requirements; finally we 
+%compare our work on PETra with 
+describe related work
 and present concluding remarks.

### 2017-06-21 papers/IoT2017/prelim.tex
update
updates

@@
 %!TEX root = paper.tex
+%\vspace{-0.15in}
 \section{System Model and Requirements}
@@
 responsible for isolating faults on the feeder.  The
-\emph{Distribution System Operator} (DSO) operations a set of
+\emph{Distribution System Operator} (DSO) operates %a set of
 switching nodes to control the connection of the microgrid to the rest
@@
 
-Figure~\ref{fig:softwareArchitecture} shows the a decentralized
+Figure~\ref{fig:softwareArchitecture} shows a decentralized
 transactive microgrid with PETra.  In this figure, components marked
@@
 \end{tikzpicture}
-\caption{The Architecture of a Decentralized Transactive Microgrid with PETra.}
+\caption{Architecture of a Decentralized Transactive Microgrid with PETra.}
 \label{fig:softwareArchitecture}

### 2017-06-21 papers/IoT2017/related.tex

@@
 
-Other approaches, such as additional hardware components, are explored
-for potential privacy gains. Varodayan and Khisti study using a
+Other approaches, such as additional hardware components, have been explored.
+%for potential privacy gains. 
+Varodayan and Khisti use a
 rechargeable battery for partially protecting the privacy of
@@
 provides increased privacy by diversifying the energy source, while a
-storage device can be used to increase both energy efficiency and
+storage device can be used to increase  energy efficiency and
 privacy.

### 2017-06-21 papers/IoT2017/related.tex
update

--- 2017-06-21 papers/IoT2017/related.tex
@@
 
-Other approaches, such as additional hardware components, are explored
-for potential privacy gains. Varodayan and Khisti study using a
+Other approaches, such as additional hardware components, have also been explored 
+for potential privacy gains. 
+Varodayan and Khisti study using a
 rechargeable battery for partially protecting the privacy of

### 2017-06-21 papers/IARPA-RFI-17-03/rfi.tex

\documentclass[12pt,letterpaper]{article}

\usepackage[letterpaper,margin=1in]{geometry}

\usepackage{times}

\usepackage{enumitem}

\usepackage{hyperref}

\begin{document}

\section*{Executive Summary}

Power grids are undergoing major changes due to rapid growth in
renewable energy resources and improvements in battery technology.
While these changes enhance sustainability and efficiency, they also
create significant management challenges as the complexity of power
systems increases.  To tackle these challenges, decentralized
Internet-of-Things (IoT) solutions are emerging, which may arrange
local communities into transactive microgrids.  Within a transactive
microgrid, consumers with energy generation and storage capabilities
can trade energy with each other, thereby smoothing the load on the
main grid using local supply. However, it is hard to provide
security, safety, and privacy in a decentralized and transactive
energy system.  On the one hand, consumers' personal information must
be protected from their trade partners and the
system operator.  On the other hand, the system must be protected from
careless or malicious trading, which could destabilize the entire
grid.

\clearpage
\section*{Description}

\subsection{Introduction}

Power grids are undergoing major changes due to rapid
acceleration in renewable energy resources, such as wind and solar power \cite{5430489}. 
% \cite{EIA2014}
For example, $4,\!143$ megawatts of solar panels were installed in the
third quarter of 2016 \cite{seia}. This capacity is estimated to grow
from 4\% in 2015 to 29\% in 2040 \cite{Randal}. At the same time,
battery technology costs per kWh have dropped significantly
\cite{stock2015powerful}, reaching grid parity.
% \cite{bronski2015economics}
This massive integration of renewable energy requires detailed
information and visibility into all aspects of the network, making it
hard to manage, especially in the presence of variable distributed
energy resources \cite{7452738}. A different vision for the future of
power-grid operations is therefore emerging: {\em a decentralized
  system in which local communities are arranged in microgrids}
\cite{rahimi2012transactive}. In this vision, energy generation,
transmission, distribution, and even storage (\emph{e.g.}, electric
vehicles in a community) can be strategically used to balance load and
demand spikes.

Furthering the concept of microgrids, transactive energy models have
been proposed to support the next distribution system evolution
\cite{kok2016society,cox2013structured,melton2013gridwise}. Transactive
energy is a set of market-based constructs for dynamically balancing
the demand and supply across the electrical infrastructure
\cite{melton2013gridwise}. In this approach, customers on the same
feeder (\emph{i.e.}, those sharing a power line link) can operate in an
open market, trading and exchanging generated energy
locally. Distribution System Operators (DSOs) can be the custodians of
this market, while still meeting the net demand \cite{7462854}. For
example, the Brooklyn Microgrid, which was developed by LO3 Energy as
a pilot project, is a peer-to-peer market for locally generated
renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}

On one hand, transactive energy is a decentralized power system
controls problem \cite{7452738}, requiring strategic microgrid control
to maintain the stability of the community and the utility. On the
other hand, it is a distributed market problem where erroneous---as
well as malicious---transactions can create a gap between demand and
supply, eventually destabilizing the system. In both cases, however,
this system requires a distributed infrastructure comprising of smart
meters, feeders, smart inverters, utility substations, the utility
central offices, and the transmission system operator, which must
provide the necessary computation fabric to support the interplay
between the energy control and the fiscal market challenges.
Recently, demand-response systems have been enabled as applications of
IoT in smart grid~\cite{Haider2016166}. Transactive grid is the next step \cite{collier2017emerging}.

In general, the focus is now on creating a distributed IoT
infrastructure
that provides the necessary computation fabric to support the
interplay between energy control and fiscal market challenges, as
shown by Volttron \cite{katipamula2016volttron}, OpenFMB
\cite{gunthersmart}, and the Resilient Information Architecture
Platform for Smart Grid (RIAPS)
\cite{eisele2017riaps,Scott2017ICCPS}. For instance, the latter is a
distributed IoT operating system that provides the foundations for all
algorithms, isolates the hardware details from the algorithms, and
provides essential mechanisms for resource management, fault
tolerance, and security. Most of these efforts, however, focus on the
computation and distribution of information, and do not provide the
support required to handle the privacy challenges that arise from the
required information exchange in this decentralized transactive
system.

This paper assumes the existence of a distributed IoT infrastructure
and focuses on the following privacy challenges:
\begin{itemize}[itemsep=0.1\parskip,topsep=-0.75\parskip]
\item \textbf{Leakage of Energy Usage Patterns to Other Prosumers} 
 Since prosumers\footnote{We
  refer to customers as \emph{prosumers} to emphasize that they can
  not only consume energy, but may also produce it.} may purchase
  energy from each other in a transactive microgrid, transactions may
  inadvertently reveal the prosumers' detailed energy usage patterns
  to other prosumers within the microgrid.  Addressing this issue in a
  decentralized trading system is hard as it requires hiding the
  identities of trade partners from each other. In comparison, secure
  smart metering reveals the prosumers' energy usage patterns only to
  the operator.

\item \textbf{Inference of Future States of a Prosumer} 
  Transactions may reveal
  the future energy usage of a prosumer, which could be used to infer
  private information.  For example, a smart home may know that its
  inhabitants will go out in the evening (\emph{e.g.}, by looking at
  their calendar), and it may trade energy futures accordingly in the
  morning.  Without adequate privacy measures, these trades may reveal
  to other prosumers in the microgrid that the inhabitants will not be
  at home later.  Note that energy
  futures, whose delivery may happen several hours after when the
  transaction is made, can play an important role in predicting and
  controlling microgrid load.  In comparison, smart metering reveals
  only current (or past) usage.

\item \textbf{Personally Identifiable Information} 
  Transactions and energy
  usage data in a transactive microgrid are much richer sources of
  information than the simple usage data collected by smart
  meters.  Specifically, the information available in a
  transactive microgrid is a superset of what is available from smart
  metering, and it may be used to infer personal information, such as
  risk propensity and financial standing.
\end{itemize}
\vspace{0.5\parskip}

Before transactive energy systems can be deployed widely in practice,
we must address the privacy issues described above. However, addressing these
issues is hard since solutions must also satisfy security
and safety requirements, which often conflict with privacy goals.  For
example, to prevent a prosumer from destabilizing the grid through
careless of malicious energy trading, the system must check all of the
prosumer's transactions.  In a decentralized system, this requires
disseminating information, which could be used to infer the prosumer's
future energy consumption.

\subsection*{System Model}

A microgrid is a collection of prosumers (residential nodes) that are arranged within the same distribution feeder which supports exchange of power between them. A prosumer node typically includes a smart inverter and a smart meter, which control the flow of power into and out of the prosumer. Additionally, the microgrid contains a set of 
protection nodes that are  responsible for isolating faults on the feeder. Finally, a set of switching nodes, which are operated by the Distribution System Operator (DSO), control the connection of the microgrid to the rest of the distribution system. The DSO is responsible for regulating the net electric power into and out of the microgrid. Starting from this model, we next introduce the transactive microgrid model.

We describe a basic system model of decentralized 
transactive IoT microgrids.  We discuss the following components: a
distributed ledger for recording transactions, a bid storage service
that facilitates finding trade partners, a microgrid controller for
regulating the microgrid load, and smart meters for measuring the
prosumers' energy production and consumption.

\subsubsection*{Distributed Ledger}
This ledger permanently stores transactions that specify energy
trades, change regulatory policies for the microgrid, etc.  For
providing security and safety, it is crucial that transactions are
immutable, \emph{i.e.}, after a transaction has been recorded, it
cannot be modified or removed from the ledger.  To enhance fault
tolerance, however, the ledger should also be distributed.

Since a distributed ledger is maintained by multiple nodes, a key
requirement is reaching consensus on which transactions are valid and
stored on the ledger.  Moreover, this consensus must be reached
quickly and reliably, even in the presence of faulty or malicious
(\emph{e.g.}, compromised) ledger nodes.  This paper assumes that a
distributed ledger service is available, but makes no assumptions
about the ledger implementation, such as the particulars of the
consensus algorithm.  In practice, a distributed ledger can be
implemented using, \emph{e.g.}, \emph{blockchains} with proof-of-stake
consensus or a practical Byzantine fault tolerance
algorithm~\cite{castro1999practical}.

\subsubsection*{Bid Storage Service}
Although prosumers trade energy with each other directly (\emph{i.e.},
without a middleman), for the sake of scalability, we need a service
that enables prosumers to find trade partners.
We assume that there is a bid storage service that allows prosumers to
post and read energy \emph{bids} and \emph{asks}.\footnote{A
  \emph{bid} is an offer to buy at a certain price, while an
  \emph{ask} is an offer to sell at a certain price.}  This service
relieves prosumers from contacting a large number of potential trade
partners since they only communicate with the service to discover
trade partners.
To enhance scalability and reliability, this service can also be
implemented in a distributed manner, using multiple nodes.

\subsubsection*{Microgrid Controller (Distribution System Operator)}
We assume the existence of a controller at the DSO level that regulates the total load that the microgrid should present to the distribution system.
 The controller first predicts load in the microgrid
based on (1) bids and asks in the bid storage and (2) outstanding
energy trades in the ledger.  By combining this information with the
prediction for the rest of the grid, the controller produces a control
signal that specifies how much the microgrid load should be decreased
or increased.  Based on this signal, the controller then updates the
price policy for the microgrid to influence energy production and
consumption.  We also assume the presence of a secondary controller
that balances voltage and frequency in the microgrid.

\subsubsection*{Smart Meters}
To measure the prosumers' energy production and consumption, a smart
meter must be deployed at each prosumer.  In practice, these smart
meters must be tamper resistant to prevent prosumers from ``stealing
electricity'' by tampering with their meters.  After a smart meter has
measured the net amount of energy consumed by the prosumer in some
time interval, it can send this information to the DSO for billing
purposes.

\subsection*{Requirements}
We now discuss the security, safety, and privacy requirements that
must be satisfied by a transactive energy IoT system.

\subsubsection*{Security}
Security requirements ensure primarily that prosumers are billed
correctly, but they also provide necessary prerequisite properties for
safety.
More specifically, they require that
\begin{itemize}[noitemsep,topsep=-\parskip]
\item prosumers are billed correctly based on the energy prices set by
  the DSO, their energy trades, and their actual energy production and
  consumption measured by the smart meters,
\item prosumers or outside attackers cannot change microgrid
  regulatory policies that are set by the DSO, 
\item prosumers cannot back out of trades unilaterally, and they
  cannot tamper with other prosumers' trading or bidding,
\item financial and physical impact of compromised or faulty nodes is
  limited, and nodes can be banned by the DSO. 
\end{itemize}

\subsubsection*{Safety}
A careless or malicious prosumer may destabilize the grid by promising
to produce (or consume) a large amount of energy, but failing to actually
produce (or consume) it.  A significant difference between promised and
actual energy production (or consumption) can result in a large gap
between the aggregate production and consumption of the microgrid.
A large gap threatens the stability of not only the microgrid but also the main
power grid.  Therefore, prosumers should not be able to trade large
amounts of energy that they are unlikely to deliver.
Specifically, we require that 
\begin{itemize}[noitemsep,topsep=-\parskip]
\item the net amount of energy sold (or bought) by a prosumer is upper
  bounded (by a limit set by the DSO), where the net amount of
  energy sold is the difference between the amount of energy sold and
  bought by the prosumer, and the net amount of energy bought is
  defined analogously. 
\end{itemize}
In practice, the DSO can set the limits based on the prosumers' production and consumption capacities.

\subsubsection*{Privacy} 
Privacy requirements ensure that the prosumers' privacy is not
compromised when they participate in energy trading.  We use
non-transactive smart metering as a baseline, and we require that
the transactive system does not leak any additional information
compared to this baseline.  More specifically, we require that
\begin{itemize}[noitemsep,topsep=-\parskip]
\item only the corresponding smart meter and the DSO may gain
  information regarding the amount of energy produced, consumed,
  bought, or sold by a prosumer,\footnote{Note that this requirement
    is impossible to satisfy if all other prosumers may collude
    against one target. However, we can assume that the majority of
    prosumers are non-colluding.}
\item only the prosumer may know which bids and asks it has posted,
  and no one can know who traded energy with whom.
\end{itemize}

\clearpage
\bibliographystyle{plain}
\bibliography{../IoT2017/references.bib}

\end{document}

### 2017-06-21 papers/IARPA-RFI-17-03/rfi.tex
Added a section on transportation use case

@@
 
+\section{Distributed Edge Processing for Multimodal Routing}
+
+Urban spaces are expanding at impressive rates and an efficient transportation system is a key component to any well-functioning city.
+Yet, as cities expand, existing infrastructures are being stressed to their limits.
+To make the problem worse,  building new infrastructures is costly, time consuming, and disruptive.
+Consequently, a number of transit agencies and cities \cite{} are turning towards multimodal  solutions combining transporation operated by both cities and private users.
+However, given the large number of choices and available options this often leads to a dynamic programming problem that must be solved online considering serveral state variables, such as traffic congenstion, mode capacity and the personal preferences.
+
+Many commercially available Internet of Things (IoT) solutions for multimodal
+transit focus on what is best for the individual from their local perspective.
+For example, Google Maps is able to chose between multiple options like busing, driving and biking for an individual user.
+But as the number of these locally optimal solution grows, too grows the misalignment between objectives of individual users and the overall system.
+This gap often results in a tragedy of the commons, where public goods such as roads become congested although no individual user has an incentive to use other modes of transportation.
+At the same time, an information bottleneck is also forming.
+Large scale data is being collected both by municipalities and users, but neither has the resources on their own to develop real-time analytics and controls necessary for a smart transportation system.
+Currently, very little has been done to provide an overarching solution that balances the needs of multiple parties including commercial companies, municipal service providers, and individuals.
+
+\subsection{The privacy problem}
+A solution to this problem requires a social computing and information sharing platform that overcomes the incentive gap between individuals and municipalities.
+This platform must offer mixed-mode routing suggestions and general system information to travelers and in turn provides service providers with high-fidelity information about how users are consuming different transportation resources.
+At the same time, this system must consider the investment required by the cities in the computing infrastructure required to solve the problem at scale.
+Alternatively, a novel proof-of-concept that utilizes the various edge computing resources available in the city, including the mobile devices of the commuters can be employed by municipalities to improve efficiency within their cities with little investment.
+
+However, this precisely leads to the problem of secure and trustworthy computing.
+Privacy of individuals is an important aspect of this solution; use of smart devices of individuals as both a data source and a computational resource  could have the effect of exposing the end-user to risk of a privacy breach.
+Seemingl innocuous data such as transit mode or route choice can lead to inferences of
+private information such as real-time tracking of an individual's position~\cite{koufogiannis:2015aa}, likelihood of affairs~\cite{mueffelmann:2015aa}, forecasting trip destinations~\cite{dewri:2013aa}, etc.
+
+\subsection{The Integrity Problem}
+- the platform must be auditable
+- all incentives must be tracked (new incentives will be recorded as transactions)
+- The algorithms must be easy to manage and deploy. They must be validated for resource and power consumption. The incentives must track that.
+
 \clearpage

### 2017-06-21 papers/IoT2017/analysis.tex
final

@@
 energy sold by prosumer $i$ for each timestep is at most
-$\field{MAXEPA}_i$.  By definition, \textcolor{blue}{we assume that the smart meters enforce a constraint, which ensures that} the amount of energy sold is less
-than or equal to the amount of EPA obtained by prosumer $i$.
-
+$\field{MAXEPA}_i$.  Due to the rules of the trading workflow, the gross amount of energy sold is less than or equal to the amount of EPA
+obtained by prosumer $i$.
+%
 A prosumer can obtain EPA either by withdrawing from its smart meter
-or by purchasing form another prosumer.  From its smart meter,
+or by purchasing from another prosumer.  From its smart meter,
 prosumer $i$ can withdraw at most $\field{MAXEPA}_i$.  Although the

### 2017-06-21 papers/IoT2017/concl.tex
final

--- 2017-06-21 papers/IoT2017/concl.tex
@@
 to tackle this complexity. Ironically, these decentralized systems
-also give rise to new privacy challenges, such as leakage of energy usage patterns, including the possibility of inference of future state of a prosumer, 
-\Doug{Abhishek, please briefly list the key privacy challenges we cover in this paper.}
-which are exacerbated by the stringent safety and
+also give rise to new privacy challenges, such as the potential leakage of energy usage patterns, including the possibility of inferring the future state of a prosumer.
+These challenges are exacerbated by the stringent safety and
 security requirements of power systems.
 
-This paper describes how we address these challenges via
-\emph{Privacy-preserving Energy Transactions} (PETra), which is our
+This paper describes 
+\emph{Privacy-preserving Energy Transactions} (PETra), our
 innovative solution for anonymous energy trading within a transactive

### 2017-06-21 papers/IoT2017/intro.tex
final

@@
 (\url{brooklynmicrogrid.com}) is a peer-to-peer market for locally
-generated renewable energy developed by LO3 Energy as a pilot project.
+generated renewable energy, which was developed by LO3 Energy as a pilot project.
 
@@
 
-This paper describes an overview of the transactive sequence between
-different components of the systems. We also describe the structure of
-these transactions and show how they can be used to provide
-\emph{Privacy-preserving Energy Transactions} (PETra). PETra is our
+This paper introduces %an overview of the transactive sequence between
+%different components of the systems. We also describe the structure of
+%these transactions and show how they can be used to provide
+\emph{Privacy-preserving Energy Transactions} (PETra), which is our
 distributed-ledger based solution that (1) enables trading energy
@@
 safety rules.
-
-% \Aron{Since SIGCHI does not have section numbers, this paragraph,
-%  which describes the organization of the paper, is not very clear.}
-%The remainder of
+%
 This paper is organized as follows: we first describe
@@
 then discuss how it satisfies the security, safety, and privacy
-requirements; finally we 
+requirements; finally, we 
 %compare our work on PETra with 

### 2017-06-21 papers/IoT2017/paper.tex
update
final

@@
 careless or malicious trading, which could destabilize the entire
-grid.  This paper describes \change{our}{\emph{Privacy-preserving
-    Energy Transactions} (PETra)}, which is secure and safe solution
+grid.  This paper describes \emph{Privacy-preserving
+    Energy Transactions} (PETra), which is a secure and safe solution
 for transactive microgrids that enables consumers to trade energy
-without sacrificing their privacy.  \change{Our solution}{PETra}
+without sacrificing their privacy.  PETra
 builds on distributed ledgers, such as blockchains, and provides
@@
 % BALANCE COLUMNS
-\balance{}
+%\balance{}
+%\setlength{\bibsep}{0pt plus 0ex}
+%\let\oldthebibliography\thebibliography
+%\let\endoldthebibliography\endthebibliography
+%\renewenvironment{thebibliography}[1]{
+%  \begin{oldthebibliography}{#1}
+%    \setlength{\itemsep}{0.1em}
+%    \setlength{\parskip}{0em}
+%}
+%{
+%  \end{oldthebibliography}
+%}
 
@@
 \bibliographystyle{SIGCHI-Reference-Format}
+
 \bibliography{references}

### 2017-06-21 papers/IoT2017/solution.tex
updates
final

@@
 security.
+
 \begin{figure*}[h]
@@
 \end{tikzpicture}
-\caption{Simplified Overview of the Flow of Assets from the Perspective of a Prosumer Who Sells Energy.}
+\caption{Simplified overview of the flow of assets from the perspective of a prosumer who sells energy.
+Note that to prevent de-anonymization, a prosumer should use multiple addresses and multiple rounds of mixing, which we have omitted from the figure for clarity of presentation.}
 \label{fig:sellFlow}
+%\vspace{-0.1in}
 \end{figure*}
@@
 Consider a prosumer who wishes to sell energy to another prosumer, as
-shown in Figure~\ref{fig:sellFlow}\footnote{To prevent
-  de-anonymization, a prosumer should use multiple addresses and
-  multiple rounds of mixing, which we have omitted from the figure for
-  clarity of presentation.}  \Abhishek{We need to mention what is the
+shown in Figure~\ref{fig:sellFlow}.  \Abhishek{We need to mention what is the
   expected deadline by which this sequence of task should finish.}  As
@@
 storage service---without revealing its original identity---that it
-owns a production asset stored at an anonymous address.  Proving
-ownership prevents the prosumer from ``spamming'' the storage service
+owns a production asset stored at an anonymous address.  
+\Aron{This sentence was added because we removed the relevant safety requirement.}
+Proving ownership prevents the prosumer from ``spamming'' the storage service
 with bogus asks.  The prosumer can then post the energy ask

### 2017-06-22 papers/IARPA-RFI-17-03/rfi.tex
update

@@
 
+\title{SDC: Social Dispersed Computing}
+\date{}
 \begin{document}
+\maketitle
 
@@
 
-Power grids are undergoing major changes due to rapid growth in
-renewable energy resources and improvements in battery technology.
-While these changes enhance sustainability and efficiency, they also
-create significant management challenges as the complexity of power
-systems increases.  To tackle these challenges, decentralized
-Internet-of-Things (IoT) solutions are emerging, which may arrange
-local communities into transactive microgrids.  Within a transactive
-microgrid, consumers with energy generation and storage capabilities
-can trade energy with each other, thereby smoothing the load on the
-main grid using local supply. However, it is hard to provide
-security, safety, and privacy in a decentralized and transactive
-energy system.  On the one hand, consumers' personal information must
-be protected from their trade partners and the
-system operator.  On the other hand, the system must be protected from
-careless or malicious trading, which could destabilize the entire
-grid.
+The classic Internet architecture assumes computing hosts whose task is to perform computations
+and a network of switches and routers whose sole task is to route network packets.
+This architecture delegates all computing to end-nodes and all communications to the network.
+However every resource (node or edge) in this architecture has a finite capacity potentially leading to inefficient allocation of resources to communications and computations.
+This is the networking model on which our current state of the art cloud computing architectures are built.
+While this is is sufficient for most tasks it does not scale up when we try to use this architecture in the new emerging pardigm of Digitalization where the boundaries between the network node, the sensor, the actuator are blurring, driven primarily by the internet of things and the smart phone revolution.
+The data generated via this network is extremely large and needs clever, scalable and possibly decentralized computing solutions that can scale indepently as required.
+In this network any node in the graph can serve as a computing or network
+router node (or both), and  the complex application can possibly be distributed over the network
+of these nodes, such that the overall performance (e.g., amount of data processed over
+time) is significantly improved.
+This is the concept behin the `Social Dispersed Computing', which our groupt has been working on.
+In this white paper, we describe two usecases for this new computing paradigm and describe the challenges which must be solved.
+
+%Often a complex computational application can be decomposed into computing and
+%communication activities. Now if any node in the graph can serve as a computing or network
+%router node (or both), then the complex application can possibly be distributed over the network
+%of these nodes, such that the overall performance (e.g., amount of data processed over
+%time) is signicantly improved. This is the concept behind 'Dispersed Computing' where
+%computations are eciently distributed over a number of computing and communication
+%resources.
+%
+%
+%Our proposal is about building the technology and tools to create and execute Dispersed
+%Computing applications on Network Computation Points (NCP-s): nodes in the network
+%that can serve a computers, storage devices, or network routers. The proposed work will focus
+%on: (1) developing a technology to model complex software applications (so that they can
+%be eectively assigned to NCP-s), (2) designing techniques and tools to continuously monitor
+%the resources available at and among the NCP-s, (3) developing ecient distributed algorithms
+%to search for resources on the network that can potentially satisfy the requirements
+%of the applications (expressed in their models), (4) developing an approach to fault-tolerance
+%so that the applications continue functioning even if the NCP-s or the communication links
+%between them fail, (5) designing and implementing adaptation strategies so that the running
+%application(s) can be dynamically re-allocated to the available resources if those resources
+%change over time. The work includes research and development of prototypes, as well as
+%experimental evaluation of the technologies developed using realistic applications and scenarios.
+
+%The widespread distribution of 
+%
+%Power grids are undergoing major changes due to rapid growth in
+%renewable energy resources and improvements in battery technology.
+%While these changes enhance sustainability and efficiency, they also
+%create significant management challenges as the complexity of power
+%systems increases.  To tackle these challenges, decentralized
+%Internet-of-Things (IoT) solutions are emerging, which may arrange
+%local communities into transactive microgrids.  Within a transactive
+%microgrid, consumers with energy generation and storage capabilities
+%can trade energy with each other, thereby smoothing the load on the
+%main grid using local supply. However, it is hard to provide
+%security, safety, and privacy in a decentralized and transactive
+%energy system.  On the one hand, consumers' personal information must
+%be protected from their trade partners and the
+%system operator.  On the other hand, the system must be protected from
+%careless or malicious trading, which could destabilize the entire
+%grid.
 
 \clearpage
-\section*{Description}
+\section{Description}
+The existing Internet architecture was envisioned more than 30 years ago.
+This architecture relies on separate computing and communication resources: computing hosts on the edge communicate via a network whose task is to route and deliver network packets as efficiently as possible.
+This strict separation of computation from communication has its drawbacks: for instance computations that reduce large data sets (arriving from another hosts) to smaller ones (that are needed by another group of hosts) are going to be inefficient, due the limits of network communication.
+However, often it would be more efficient to move the computation `closer' to the source hosts and then just send the results to the target hosts.
+A specific example is that of sensor processing: target recognition in sensor streams should be done as close to the source as possible, because doing it somewhere else would incur performance penalties.
+Arguably, this is possible today but on an ad-hoc basis.
+Careful management and deployment of application software components over a network `owned' nodes can be done with a great deal of manual and error-prone operations.
+These solutions are brittle, labor intensive, and not responsive enough to the rapid changes in the network or the utilization of the computing hosts.
 
-\subsection{Introduction}
+\subsection{The Social Dispersed Computing Architecture}
 
-Power grids are undergoing major changes due to rapid
-acceleration in renewable energy resources, such as wind and solar power \cite{5430489}. 
-% \cite{EIA2014}
-For example, $4,\!143$ megawatts of solar panels were installed in the
-third quarter of 2016 \cite{seia}. This capacity is estimated to grow
-from 4\% in 2015 to 29\% in 2040 \cite{Randal}. At the same time,
-battery technology costs per kWh have dropped significantly
-\cite{stock2015powerful}, reaching grid parity.
-% \cite{bronski2015economics}
-This massive integration of renewable energy requires detailed
-information and visibility into all aspects of the network, making it
-hard to manage, especially in the presence of variable distributed
-energy resources \cite{7452738}. A different vision for the future of
-power-grid operations is therefore emerging: {\em a decentralized
-  system in which local communities are arranged in microgrids}
-\cite{rahimi2012transactive}. In this vision, energy generation,
-transmission, distribution, and even storage (\emph{e.g.}, electric
-vehicles in a community) can be strategically used to balance load and
-demand spikes.
+The social dispersed computing architecture consists of a number of network computation points (NCP) \footnote{for example,\url{https://routerboard.com/RB2011UiAS-2HnD-IN}}, which posses the capability to provide both networking and computation resources.
+They can serve as network routers, computing hosts, data storage hosts, sensors,or actuators - in any combination, possibly simultaneously.
+A typical NCP has router/computer/storage functions, an NCP for cyber-physical applications adds sensor/actuator interfaces to these.
+A network-connected conventional computing host can serve as an specialized NCP that is connected to the system but it is not capable of routing.
+These modern networking devices are result of the innovation of software defined networking and the progress made with investments in the Internet of Things technology.
+Additionally, the architecture consists of smart phones, network links, as well as conventional computing and data storage hosts and as well as network routers.
+We expect the  NCP-s run a specialized distributed `meta-operating system'  that facilitates the Dispersed Computing functions by providing a sophisticated \textit{distributed application platform} that is able to effectively deploy and executed distributed (dispersed) applications.
+Finally, the system is highly dynamic: nodes (NCP-s, computing and data hosts, routers, links) can come (join the system) and go (leave the system) at any time, connectivity and corresponding link parameters: bandwidth, latency, packet drop rate, etc.
+are changing continuously, and computational and communication demand generated by applications are varying over time.
 
-Furthering the concept of microgrids, transactive energy models have
+With this architecture, computational tasks, described as  a directed graph, where the directed edges represent network flows\footnote{The directed graph can represent both synchronous and asynchronous data flow(s), control flow(s), or a mixture of the two}, can be deployed on these ad-hoc and shared resources.
+he system is \textit{homogeneous} meaning that any NCP can serve as an entry point to submit an application for deployment into the system.
+The operating system on the entry point NCP will then execute a time- and depth-bounded search on the system to find a feasible \textit{deployment solution} for the application.
+A deployment solution is map of the application tasks to NCP-s and the application flows onto network paths.
+The deployment solution is then implemented: the application tasks are deployed on the selected NCP-s.
+This search is done via a form of flooding protocol which allows the discovery of necessary resources across several paths at once.
+The system is \textit{adaptive} in that even after deployment the deployed configuration may change over time.
+As the NCP-s continuously monitor themselves and their neighbors, the estimates of the utilization of the resources that was used when the deployment configuration was computed may not be valid forever, it may be imperative to recompute the deployment solution.
+Additionally, the application itself may evolve and its resource usage may change over time.
+This necessitates monitoring the application's resource usage over time and updating its model dynamically.
+If a significant discrepancy between the original state of the system and the resource usage of applications and the current situation is detected, a recomputation of the deployment is initiated.
+
+The effective deployment of these complex assemblies on a network of computing nodes is a non-trivial task and requires significant manual labor today.
+The proposed framework will provide the foundation for this new software paradigm: applications deployed on a network of computing and communicating devices, where they can be the most effective, given computational and communication resource constraints.
+This deployment configuration computed during operations, based on the current state of the system.
+The deployment is also adaptive: computation and data can move in the system, as the changing conditions necessitate it.
+This is much more flexible and very different from the existing, typically static deployments.
+
+There are a number of distributed software frameworks, e.g.
+Erlang/OTP, Akka, etc.
+that support the development of distributed applications.
+However, the distribution is completely in the hand of the developer, and it is mainly an error-prone and complex manual task.
+Our approach, through the application modeling, enables the automation of this process.
+Although the application models still need to be supplied, the determination of the deployment and the execution of the necessary operations will be completely automated.
+
+Fault tolerance and adaptivity to changing resources are important requirements for many systems.
+Our approach, through the underlying framework provides a solution so that complex applications can operate autonomously and efficiently, even under adversary conditions.
+Both fault tolerance and adaptivity require cooperation from the developers - i.e.
+the application framework cannot solve the problem, but the framework will provide services to help achieve the required system level fault-tolerance and adaptivity.
+However, there are additional challenges, which we will describe using two case studies.
+The first one looks at the transactive energy pardigm, the other looks at multi-modal transporation analytics and optimization, a critical concept that is required to solve the large transportation challenges that we are facing.
+
+\subsection{Transactive Grid Example}
+
+Transactive energy models have
 been proposed to support the next distribution system evolution
@@
 a pilot project, is a peer-to-peer market for locally generated
-renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}
+renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}.
 
-On one hand, transactive energy is a decentralized power system
-controls problem \cite{7452738}, requiring strategic microgrid control
-to maintain the stability of the community and the utility. On the
-other hand, it is a distributed market problem where erroneous---as
-well as malicious---transactions can create a gap between demand and
-supply, eventually destabilizing the system. In both cases, however,
-this system requires a distributed infrastructure comprising of smart
-meters, feeders, smart inverters, utility substations, the utility
-central offices, and the transmission system operator, which must
-provide the necessary computation fabric to support the interplay
-between the energy control and the fiscal market challenges.
-Recently, demand-response systems have been enabled as applications of
-IoT in smart grid~\cite{Haider2016166}. Transactive grid is the next step \cite{collier2017emerging}.
-
-In general, the focus is now on creating a distributed IoT
-infrastructure
-that provides the necessary computation fabric to support the
-interplay between energy control and fiscal market challenges, as
-shown by Volttron \cite{katipamula2016volttron}, OpenFMB
+These systems are effectively an example of social dispersed computing (Volttron \cite{katipamula2016volttron}, OpenFMB
 \cite{gunthersmart}, and the Resilient Information Architecture
 Platform for Smart Grid (RIAPS)
-\cite{eisele2017riaps,Scott2017ICCPS}. For instance, the latter is a
-distributed IoT operating system that provides the foundations for all
-algorithms, isolates the hardware details from the algorithms, and
-provides essential mechanisms for resource management, fault
-tolerance, and security. Most of these efforts, however, focus on the
-computation and distribution of information, and do not provide the
-support required to handle the privacy challenges that arise from the
+\cite{eisele2017riaps,Scott2017ICCPS}) where consumer power storage and private energy sources as solar panels, achieving grid stability will be challenging.
+With social dispersed computing in transactive grid energy consumers, producers, storage solutions will be discovered automatically, continuously monitored and the system status is updated in case devices appear to be offline.
+However, the computing structure in these systems do not focus on the  privacy challenges that arise from the
 required information exchange in this decentralized transactive
-system.
-
-This paper assumes the existence of a distributed IoT infrastructure
-and focuses on the following privacy challenges:
+system: 
 \begin{itemize}[itemsep=0.1\parskip,topsep=-0.75\parskip]
@@
 careless of malicious energy trading, the system must check all of the
-prosumer's transactions.  In a decentralized system, this requires
-disseminating information, which could be used to infer the prosumer's
-future energy consumption.
+prosumer's transactions.
 
-\subsection*{System Model}
-
-A microgrid is a collection of prosumers (residential nodes) that are arranged within the same distribution feeder which supports exchange of power between them.
-A prosumer node typically includes a smart inverter and a smart meter, which control the flow of power into and out of the prosumer.
-Additionally, the microgrid contains a set of
-protection nodes that are  responsible for isolating faults on the feeder.
-Finally, a set of switching nodes, which are operated by the Distribution System Operator (DSO), control the connection of the microgrid to the rest of the distribution system.
-The DSO is responsible for regulating the net electric power into and out of the microgrid.
-Starting from this model, we next introduce the transactive microgrid model.
-
-We describe a basic system model of decentralized 
-transactive IoT microgrids.  We discuss the following components: a
-distributed ledger for recording transactions, a bid storage service
-that facilitates finding trade partners, a microgrid controller for
-regulating the microgrid load, and smart meters for measuring the
-prosumers' energy production and consumption.
-
-\subsubsection*{Distributed Ledger}
-This ledger permanently stores transactions that specify energy
-trades, change regulatory policies for the microgrid, etc.  For
-providing security and safety, it is crucial that transactions are
-immutable, \emph{i.e.}, after a transaction has been recorded, it
-cannot be modified or removed from the ledger.  To enhance fault
-tolerance, however, the ledger should also be distributed.
-
-Since a distributed ledger is maintained by multiple nodes, a key
-requirement is reaching consensus on which transactions are valid and
-stored on the ledger.  Moreover, this consensus must be reached
-quickly and reliably, even in the presence of faulty or malicious
-(\emph{e.g.}, compromised) ledger nodes.  This paper assumes that a
-distributed ledger service is available, but makes no assumptions
-about the ledger implementation, such as the particulars of the
-consensus algorithm.  In practice, a distributed ledger can be
-implemented using, \emph{e.g.}, \emph{blockchains} with proof-of-stake
-consensus or a practical Byzantine fault tolerance
-algorithm~\cite{castro1999practical}.
-
-\subsubsection*{Bid Storage Service}
-Although prosumers trade energy with each other directly (\emph{i.e.},
-without a middleman), for the sake of scalability, we need a service
-that enables prosumers to find trade partners.
-We assume that there is a bid storage service that allows prosumers to
-post and read energy \emph{bids} and \emph{asks}.\footnote{A
-  \emph{bid} is an offer to buy at a certain price, while an
-  \emph{ask} is an offer to sell at a certain price.}  This service
-relieves prosumers from contacting a large number of potential trade
-partners since they only communicate with the service to discover
-trade partners.
-To enhance scalability and reliability, this service can also be
-implemented in a distributed manner, using multiple nodes.
-
-\subsubsection*{Microgrid Controller (Distribution System Operator)}
-We assume the existence of a controller at the DSO level that regulates the total load that the microgrid should present to the distribution system.
- The controller first predicts load in the microgrid
-based on (1) bids and asks in the bid storage and (2) outstanding
-energy trades in the ledger.  By combining this information with the
-prediction for the rest of the grid, the controller produces a control
-signal that specifies how much the microgrid load should be decreased
-or increased.  Based on this signal, the controller then updates the
-price policy for the microgrid to influence energy production and
-consumption.  We also assume the presence of a secondary controller
-that balances voltage and frequency in the microgrid.
-
-\subsubsection*{Smart Meters}
-To measure the prosumers' energy production and consumption, a smart
-meter must be deployed at each prosumer.  In practice, these smart
-meters must be tamper resistant to prevent prosumers from ``stealing
-electricity'' by tampering with their meters.  After a smart meter has
-measured the net amount of energy consumed by the prosumer in some
-time interval, it can send this information to the DSO for billing
-purposes.
-
-\subsection*{Requirements}
-We now discuss the security, safety, and privacy requirements that
-must be satisfied by a transactive energy IoT system.
-
-\subsubsection*{Security}
-Security requirements ensure primarily that prosumers are billed
-correctly, but they also provide necessary prerequisite properties for
-safety.
-More specifically, they require that
-\begin{itemize}[noitemsep,topsep=-\parskip]
-\item prosumers are billed correctly based on the energy prices set by
-  the DSO, their energy trades, and their actual energy production and
-  consumption measured by the smart meters,
-\item prosumers or outside attackers cannot change microgrid
-  regulatory policies that are set by the DSO, 
-\item prosumers cannot back out of trades unilaterally, and they
-  cannot tamper with other prosumers' trading or bidding,
-\item financial and physical impact of compromised or faulty nodes is
-  limited, and nodes can be banned by the DSO. 
-\end{itemize}
-
-\subsubsection*{Safety}
-A careless or malicious prosumer may destabilize the grid by promising
-to produce (or consume) a large amount of energy, but failing to actually
-produce (or consume) it.  A significant difference between promised and
-actual energy production (or consumption) can result in a large gap
-between the aggregate production and consumption of the microgrid.
-A large gap threatens the stability of not only the microgrid but also the main
-power grid.  Therefore, prosumers should not be able to trade large
-amounts of energy that they are unlikely to deliver.
-Specifically, we require that 
-\begin{itemize}[noitemsep,topsep=-\parskip]
-\item the net amount of energy sold (or bought) by a prosumer is upper
-  bounded (by a limit set by the DSO), where the net amount of
-  energy sold is the difference between the amount of energy sold and
-  bought by the prosumer, and the net amount of energy bought is
-  defined analogously. 
-\end{itemize}
-In practice, the DSO can set the limits based on the prosumers' production and consumption capacities.
-
-\subsubsection*{Privacy} 
-Privacy requirements ensure that the prosumers' privacy is not
-compromised when they participate in energy trading.  We use
-non-transactive smart metering as a baseline, and we require that
-the transactive system does not leak any additional information
-compared to this baseline.  More specifically, we require that
-\begin{itemize}[noitemsep,topsep=-\parskip]
-\item only the corresponding smart meter and the DSO may gain
-  information regarding the amount of energy produced, consumed,
-  bought, or sold by a prosumer,\footnote{Note that this requirement
-    is impossible to satisfy if all other prosumers may collude
-    against one target. However, we can assume that the majority of
-    prosumers are non-colluding.}
-\item only the prosumer may know which bids and asks it has posted,
-  and no one can know who traded energy with whom.
-\end{itemize}
-
-\section{Distributed Edge Processing for Multimodal Routing}
+\subsection{Distributed Processing for Multimodal Routing}
 
@@
 To make the problem worse,  building new infrastructures is costly, time consuming, and disruptive.
-Consequently, a number of transit agencies and cities \cite{} are turning towards multimodal  solutions combining transporation operated by both cities and private users.
+Consequently, a number of transit agencies and cities are turning towards multimodal  solutions combining transporation operated by both cities and private users.
 However, given the large number of choices and available options this often leads to a dynamic programming problem that must be solved online considering serveral state variables, such as traffic congenstion, mode capacity and the personal preferences.
@@
 Privacy of individuals is an important aspect of this solution; use of smart devices of individuals as both a data source and a computational resource  could have the effect of exposing the end-user to risk of a privacy breach.
-Seemingl innocuous data such as transit mode or route choice can lead to inferences of
+Seemingy innocuous data such as transit mode or route choice can lead to inferences of
 private information such as real-time tracking of an individual's position~\cite{koufogiannis:2015aa}, likelihood of affairs~\cite{mueffelmann:2015aa}, forecasting trip destinations~\cite{dewri:2013aa}, etc.
-
-\subsection{The Integrity Problem}
-- the platform must be auditable
-- all incentives must be tracked (new incentives will be recorded as transactions)
-- The algorithms must be easy to manage and deploy. They must be validated for resource and power consumption. The incentives must track that.
 
@@
 \bibliographystyle{plain}
-\bibliography{../IoT2017/references.bib}
+\bibliography{../IoT2017/references}
 

### 2017-06-22 papers/IARPA-RFI-17-03/rfi.tex
fixes

@@
 This architecture delegates all computing to end-nodes and all communications to the network.
-However every resource (node or edge) in this architecture has a finite capacity potentially leading to inefficient allocation of resources to communications and computations.
-This is the networking model on which our current state of the art cloud computing architectures are built.
-While this is is sufficient for most tasks it does not scale up when we try to use this architecture in the new emerging pardigm of Digitalization where the boundaries between the network node, the sensor, the actuator are blurring, driven primarily by the internet of things and the smart phone revolution.
-The data generated via this network is extremely large and needs clever, scalable and possibly decentralized computing solutions that can scale indepently as required.
-In this network any node in the graph can serve as a computing or network
+However, every resource (node or edge) in this architecture has a finite capacity potentially leading to inefficient allocation of resources to communications and computations.
+This is the networking model on which our current state-of-the-art cloud computing architectures are built.
+While this is sufficient for most tasks, it does not scale up when we try to use this architecture in the new emerging paradigm of Digitalization.
+In this new paradigm, the boundaries between the network node, the sensor, and the actuator are blurring, driven primarily by the Internet of Things and the smartphone revolution.
+The data generated via this network is extremely large and needs clever, scalable, and possibly decentralized computing solutions that can scale independently as required.
+In this network, any node in the graph can serve as a computing or network
 router node (or both), and  the complex application can possibly be distributed over the network
-of these nodes, such that the overall performance (e.g., amount of data processed over
+of these nodes, so that the overall performance (e.g., amount of data processed over
 time) is significantly improved.
-This is the concept behin the `Social Dispersed Computing', which our groupt has been working on.
-In this white paper, we describe two usecases for this new computing paradigm and describe the challenges which must be solved.
+This is the concept behind `Social Dispersed Computing,' on which our group has been working.
+In this whitepaper, we describe two use-cases for this new computing paradigm and describe the challenges which must be solved.
 
@@
 However, there are additional challenges, which we will describe using two case studies.
-The first one looks at the transactive energy pardigm, the other looks at multi-modal transporation analytics and optimization, a critical concept that is required to solve the large transportation challenges that we are facing.
+The first one looks at the transactive energy paradigm, the other looks at multi-modal transportation analytics and optimization, a critical concept that is required to solve the large transportation challenges that we are facing.
 
@@
 To make the problem worse,  building new infrastructures is costly, time consuming, and disruptive.
-Consequently, a number of transit agencies and cities are turning towards multimodal  solutions combining transporation operated by both cities and private users.
-However, given the large number of choices and available options this often leads to a dynamic programming problem that must be solved online considering serveral state variables, such as traffic congenstion, mode capacity and the personal preferences.
+Consequently, a number of transit agencies and cities are turning towards multimodal  solutions combining transportation operated by both cities and private users.
+However, given the large number of choices and available options this often leads to a dynamic programming problem that must be solved online considering several state variables, such as traffic congestion, mode capacity and the personal preferences.
 
@@
 Privacy of individuals is an important aspect of this solution; use of smart devices of individuals as both a data source and a computational resource  could have the effect of exposing the end-user to risk of a privacy breach.
-Seemingy innocuous data such as transit mode or route choice can lead to inferences of
+Seemingly innocuous data such as transit mode or route choice can lead to inferences of
 private information such as real-time tracking of an individual's position~\cite{koufogiannis:2015aa}, likelihood of affairs~\cite{mueffelmann:2015aa}, forecasting trip destinations~\cite{dewri:2013aa}, etc.

### 2017-06-22 papers/IARPA-RFI-17-03/rfi.tex
fixes

@@
 
-\usepackage{hyperref}
+\usepackage[textsize=scriptsize]{todonotes}
+\newcommand{\Abhishek}[1]{\todo[color=yellow!50, linecolor=black!50]{\textbf{Abhishek}: #1}}
+\newcommand{\Aron}[1]{\todo[color=green!40, linecolor=black!50]{\textbf{Aron}: #1}}
+\setlength{\marginparwidth}{0.85in}
+
+\usepackage[breaklinks,hidelinks]{hyperref}
 
@@
 %Our proposal is about building the technology and tools to create and execute Dispersed
-%Computing applications on Network Computation Points (NCP-s): nodes in the network
+%Computing applications on Network Computation Points (NCPs): nodes in the network
 %that can serve a computers, storage devices, or network routers. The proposed work will focus
 %on: (1) developing a technology to model complex software applications (so that they can
-%be eectively assigned to NCP-s), (2) designing techniques and tools to continuously monitor
-%the resources available at and among the NCP-s, (3) developing ecient distributed algorithms
+%be eectively assigned to NCPs), (2) designing techniques and tools to continuously monitor
+%the resources available at and among the NCPs, (3) developing ecient distributed algorithms
 %to search for resources on the network that can potentially satisfy the requirements
 %of the applications (expressed in their models), (4) developing an approach to fault-tolerance
-%so that the applications continue functioning even if the NCP-s or the communication links
+%so that the applications continue functioning even if the NCPs or the communication links
 %between them fail, (5) designing and implementing adaptation strategies so that the running
@@
 This architecture relies on separate computing and communication resources: computing hosts on the edge communicate via a network whose task is to route and deliver network packets as efficiently as possible.
-This strict separation of computation from communication has its drawbacks: for instance computations that reduce large data sets (arriving from another hosts) to smaller ones (that are needed by another group of hosts) are going to be inefficient, due the limits of network communication.
-However, often it would be more efficient to move the computation `closer' to the source hosts and then just send the results to the target hosts.
+This strict separation of computation from communication has its drawbacks: for instance, computations that reduce large datasets (arriving from other hosts) to smaller ones (that are needed by another group of hosts) are going to be inefficient, due to the limits of network communication.
+However, it would often be more efficient to move the computation `closer' to the source hosts and then just send the results to the target hosts.
 A specific example is that of sensor processing: target recognition in sensor streams should be done as close to the source as possible, because doing it somewhere else would incur performance penalties.
 Arguably, this is possible today but on an ad-hoc basis.
-Careful management and deployment of application software components over a network `owned' nodes can be done with a great deal of manual and error-prone operations.
-These solutions are brittle, labor intensive, and not responsive enough to the rapid changes in the network or the utilization of the computing hosts.
+Careful management and deployment of application software components over a network of `owned' nodes can be done with a great deal of manual and error-prone operations.
+These solutions are brittle, labor intensive, and not responsive enough to rapid changes in the network or the utilization of computing hosts.
 
-\subsection{The Social Dispersed Computing Architecture}
+\subsection{Social Dispersed Computing Architecture}
 
-The social dispersed computing architecture consists of a number of network computation points (NCP) \footnote{for example,\url{https://routerboard.com/RB2011UiAS-2HnD-IN}}, which posses the capability to provide both networking and computation resources.
-They can serve as network routers, computing hosts, data storage hosts, sensors,or actuators - in any combination, possibly simultaneously.
-A typical NCP has router/computer/storage functions, an NCP for cyber-physical applications adds sensor/actuator interfaces to these.
-A network-connected conventional computing host can serve as an specialized NCP that is connected to the system but it is not capable of routing.
-These modern networking devices are result of the innovation of software defined networking and the progress made with investments in the Internet of Things technology.
-Additionally, the architecture consists of smart phones, network links, as well as conventional computing and data storage hosts and as well as network routers.
-We expect the  NCP-s run a specialized distributed `meta-operating system'  that facilitates the Dispersed Computing functions by providing a sophisticated \textit{distributed application platform} that is able to effectively deploy and executed distributed (dispersed) applications.
-Finally, the system is highly dynamic: nodes (NCP-s, computing and data hosts, routers, links) can come (join the system) and go (leave the system) at any time, connectivity and corresponding link parameters: bandwidth, latency, packet drop rate, etc.
-are changing continuously, and computational and communication demand generated by applications are varying over time.
+The \emph{social dispersed computing architecture} consists of a number of network computation points (NCP) \footnote{For example, see \url{https://routerboard.com/RB2011UiAS-2HnD-IN}.}, which possess the capability to provide both networking and computation resources.
+They can serve as network routers, computing hosts, data storage hosts, sensors, or actuators -- in any combination, possibly simultaneously.
+A typical NCP has router/computer/storage functions, and an NCP for cyber-physical applications adds sensor/actuator interfaces to these.
+A network-connected conventional computing host can serve as a specialized NCP that is connected to the system but is not capable of routing.
+These modern networking devices are the result of the innovation of software-defined networking and the progress made with investments in Internet of Things technology.
+Additionally, the architecture consists of smartphones, network links, conventional computing and data storage hosts, as well as network routers.
+We expect the NCPs to run a specialized distributed `meta-operating system'  that facilitates the Dispersed Computing functions by providing a sophisticated \textit{distributed application platform} that is able to effectively deploy and execute distributed (dispersed) applications.
+Finally, the system is highly dynamic: nodes (NCPs, computing and data hosts, routers, and links) can come (join the system) and go (leave the system) at any time, connectivity and corresponding link parameters (bandwidth, latency, packet drop rate, etc.) are changing continuously, and computational and communication demand generated by applications vary over time.
 
-With this architecture, computational tasks, described as  a directed graph, where the directed edges represent network flows\footnote{The directed graph can represent both synchronous and asynchronous data flow(s), control flow(s), or a mixture of the two}, can be deployed on these ad-hoc and shared resources.
-he system is \textit{homogeneous} meaning that any NCP can serve as an entry point to submit an application for deployment into the system.
+With this architecture, computational tasks, described as  a directed graph in which edges represent network flows\footnote{The directed graph can represent both synchronous and asynchronous data flow(s), control flow(s), or a mixture of the two.}, can be deployed on these ad-hoc and shared resources.
+The system is \textit{homogeneous}, which means that any NCP can serve as an entry point to submit an application for deployment into the system.
 The operating system on the entry point NCP will then execute a time- and depth-bounded search on the system to find a feasible \textit{deployment solution} for the application.
-A deployment solution is map of the application tasks to NCP-s and the application flows onto network paths.
-The deployment solution is then implemented: the application tasks are deployed on the selected NCP-s.
-This search is done via a form of flooding protocol which allows the discovery of necessary resources across several paths at once.
-The system is \textit{adaptive} in that even after deployment the deployed configuration may change over time.
-As the NCP-s continuously monitor themselves and their neighbors, the estimates of the utilization of the resources that was used when the deployment configuration was computed may not be valid forever, it may be imperative to recompute the deployment solution.
+A deployment solution is a mapping of the application tasks to NCPs and the application flows to network paths.
+The deployment solution is then implemented: the application tasks are deployed on the selected NCPs.
+This search is done via a form of flooding protocol, which allows the discovery of necessary resources across several paths at once.
+The system is \textit{adaptive} in the sense that even after deployment, the deployed configuration may change over time.
+As the NCPs continuously monitor themselves and their neighbors, the estimates of resource utilization that were used for computing the initial deployment configuration may become invalid, which necessitates recomputing the deployment solution.
 Additionally, the application itself may evolve and its resource usage may change over time.
-This necessitates monitoring the application's resource usage over time and updating its model dynamically.
+This necessitates monitoring the resource usage of the application over time and updating its model dynamically.
 If a significant discrepancy between the original state of the system and the resource usage of applications and the current situation is detected, a recomputation of the deployment is initiated.
@@
 
-There are a number of distributed software frameworks, e.g.
-Erlang/OTP, Akka, etc.
-that support the development of distributed applications.
-However, the distribution is completely in the hand of the developer, and it is mainly an error-prone and complex manual task.
-Our approach, through the application modeling, enables the automation of this process.
+There are a number of distributed software frameworks, e.g., Erlang/OTP and Akka, that support the development of distributed applications.
+However, the distribution is completely in the hands of the developer, and it is mainly an error-prone and complex manual task.
+Our approach, through application modeling, enables the automation of this process.
 Although the application models still need to be supplied, the determination of the deployment and the execution of the necessary operations will be completely automated.
@@
 Fault tolerance and adaptivity to changing resources are important requirements for many systems.
-Our approach, through the underlying framework provides a solution so that complex applications can operate autonomously and efficiently, even under adversary conditions.
-Both fault tolerance and adaptivity require cooperation from the developers - i.e.
-the application framework cannot solve the problem, but the framework will provide services to help achieve the required system level fault-tolerance and adaptivity.
+Our approach, through the underlying framework, provides a solution so that complex applications can operate autonomously and efficiently, even under adversarial conditions.
+Both fault tolerance and adaptivity require cooperation from the developers -- i.e., the application framework cannot solve the problem, but the framework will provide services to help achieving the required system-level fault-tolerance and adaptivity.
 However, there are additional challenges, which we will describe using two case studies.
-The first one looks at the transactive energy paradigm, the other looks at multi-modal transportation analytics and optimization, a critical concept that is required to solve the large transportation challenges that we are facing.
+The first one looks at the transactive energy paradigm, while the other looks at multi-modal transportation analytics and optimization, a critical concept that is required for solving the large transportation challenges that we are facing.
 
@@
 \cite{melton2013gridwise}. In this approach, customers on the same
-feeder (\emph{i.e.}, those sharing a power line link) can operate in an
+feeder (i.e., those sharing a power line link) can operate in an
 open market, trading and exchanging generated energy
@@
 
+\Aron{I am not sure what this sentence was supposed to say.}
 These systems are effectively an example of social dispersed computing (Volttron \cite{katipamula2016volttron}, OpenFMB
@@
 \cite{eisele2017riaps,Scott2017ICCPS}) where consumer power storage and private energy sources as solar panels, achieving grid stability will be challenging.
-With social dispersed computing in transactive grid energy consumers, producers, storage solutions will be discovered automatically, continuously monitored and the system status is updated in case devices appear to be offline.
-However, the computing structure in these systems do not focus on the  privacy challenges that arise from the
+With social dispersed computing, energy consumers, producers, and storage solutions in a transactive grid will be discovered automatically and monitored continuously, and system status will be updated in case devices appear to be offline.
+
+\subsubsection{Privacy Problem}
+
+However, the computing structure in these systems does not focus on the privacy challenges that arise from the
 required information exchange in this decentralized transactive
 system: 
-\begin{itemize}[itemsep=0.1\parskip,topsep=-0.75\parskip]
-\item \textbf{Leakage of Energy Usage Patterns to Other Prosumers} 
+\begin{itemize}
+\item \textbf{Leakage of Energy Usage Patterns to Other Prosumers:} 
  Since prosumers\footnote{We
@@
   decentralized trading system is hard as it requires hiding the
-  identities of trade partners from each other. In comparison, secure
-  smart metering reveals the prosumers' energy usage patterns only to
-  the operator.
+  identities of trade partners from each other. %In comparison, secure
+%  smart metering reveals the prosumers' energy usage patterns only to
+%  the operator.
 
-\item \textbf{Inference of Future States of a Prosumer} 
+\item \textbf{Inference of Future States of a Prosumer:} 
   Transactions may reveal
@@
   private information.  For example, a smart home may know that its
-  inhabitants will go out in the evening (\emph{e.g.}, by looking at
-  their calendar), and it may trade energy futures accordingly in the
+  inhabitants will go out in the evening (e.g., by looking at
+  their calendars), and it may trade energy futures accordingly in the
   morning.  Without adequate privacy measures, these trades may reveal
@@
   transaction is made, can play an important role in predicting and
-  controlling microgrid load.  In comparison, smart metering reveals
-  only current (or past) usage.
+  controlling microgrid load.  %In comparison, smart metering reveals
+%  only current (or past) usage.
 
-\item \textbf{Personally Identifiable Information} 
+\item \textbf{Personally Identifiable Information:} 
   Transactions and energy
@@
 \end{itemize}
-\vspace{0.5\parskip}
 
 Before transactive energy systems can be deployed widely in practice,
-we must address the privacy issues described above. However, addressing these
-issues is hard since solutions must also satisfy security
+the privacy issues described above must be addressed. However, addressing these
+issues is hard since solutions must also satisfy stringent security
 and safety requirements, which often conflict with privacy goals.  For
@@
 
-\subsection{Distributed Processing for Multimodal Routing}
+\subsection{Distributed Processing for Multimodal Routing Example}
 
-Urban spaces are expanding at impressive rates and an efficient transportation system is a key component to any well-functioning city.
-Yet, as cities expand, existing infrastructures are being stressed to their limits.
-To make the problem worse,  building new infrastructures is costly, time consuming, and disruptive.
+Since urban spaces are expanding at impressive rates, an efficient transportation system is a key component to any well-functioning city.
+Yet, as cities expand, existing infrastructures are stressed to their limits.
+To make the problem worse,  building new infrastructures is expensive, time consuming, and disruptive.
 Consequently, a number of transit agencies and cities are turning towards multimodal  solutions combining transportation operated by both cities and private users.
-However, given the large number of choices and available options this often leads to a dynamic programming problem that must be solved online considering several state variables, such as traffic congestion, mode capacity and the personal preferences.
+However, given the large number of choices and available options, this often leads to a \Aron{Does this alway boil down to a dynamic programming problem in the algorithmic sense?} dynamic programming problem that must be solved online, considering several state variables, such as traffic congestion, mode capacity, and personal preferences.
 
@@
 transit focus on what is best for the individual from their local perspective.
-For example, Google Maps is able to chose between multiple options like busing, driving and biking for an individual user.
-But as the number of these locally optimal solution grows, too grows the misalignment between objectives of individual users and the overall system.
+For example, Google Maps is able to chose between multiple options for an individual user, such as taking the bus, driving, or biking.
+But as the number of these locally optimal solution grows, so does the misalignment between objectives of individual users and the overall system.
 This gap often results in a tragedy of the commons, where public goods such as roads become congested although no individual user has an incentive to use other modes of transportation.
 At the same time, an information bottleneck is also forming.
-Large scale data is being collected both by municipalities and users, but neither has the resources on their own to develop real-time analytics and controls necessary for a smart transportation system.
-Currently, very little has been done to provide an overarching solution that balances the needs of multiple parties including commercial companies, municipal service providers, and individuals.
+Large-scale data is being collected both by municipalities and users, but neither has the resources on their own to develop real-time analytics and controls necessary for a smart transportation system.
+Currently, very little has been done to provide an overarching solution that balances the needs of multiple parties, including commercial companies, municipal service providers, and individuals.
 
-\subsection{The privacy problem}
+\subsubsection{Privacy Problem}
 A solution to this problem requires a social computing and information sharing platform that overcomes the incentive gap between individuals and municipalities.
-This platform must offer mixed-mode routing suggestions and general system information to travelers and in turn provides service providers with high-fidelity information about how users are consuming different transportation resources.
-At the same time, this system must consider the investment required by the cities in the computing infrastructure required to solve the problem at scale.
-Alternatively, a novel proof-of-concept that utilizes the various edge computing resources available in the city, including the mobile devices of the commuters can be employed by municipalities to improve efficiency within their cities with little investment.
+This platform must offer mixed-mode routing suggestions and general system information to travelers and---in turn---supply service providers with high-fidelity information about how users are consuming different transportation resources.
+At the same time, this system must also consider the investment required by the cities in the computing infrastructure required to solve the problem at scale.
+Alternatively, a novel proof-of-concept that utilizes the various edge computing resources available in the city, including the mobile devices of the commuters, can be employed by municipalities to improve efficiency within their cities with little investment.
 
 However, this precisely leads to the problem of secure and trustworthy computing.
-Privacy of individuals is an important aspect of this solution; use of smart devices of individuals as both a data source and a computational resource  could have the effect of exposing the end-user to risk of a privacy breach.
-Seemingly innocuous data such as transit mode or route choice can lead to inferences of
-private information such as real-time tracking of an individual's position~\cite{koufogiannis:2015aa}, likelihood of affairs~\cite{mueffelmann:2015aa}, forecasting trip destinations~\cite{dewri:2013aa}, etc.
+Privacy of individuals is an important aspect of this solution; the usage of individuals' smart devices as both data sources and computational resources  could expose the end-users to a risk of privacy breach.
+Seemingly innocuous data, such as transit mode or route choice, can lead to inferences of
+private information, such as real-time tracking of an individual's position~\cite{koufogiannis:2015aa}, likelihood of affairs~\cite{mueffelmann:2015aa}, and forecasting trip destinations~\cite{dewri:2013aa}.
 

### 2017-06-23 papers/IARPA-RFI-17-03/rfi.tex
new section

@@
 
+\subsection{Blockchains for SDC: Opportunities and Challenges}
+
+One of the key challenges in social dispersed computing is ensuring that NCPs that are operated by multiple parties, who may have limited trust in each other, can work together.
+For example, in transactive energy, devices belonging to individual prosumers, industrial consumers/producers, and DSOs have to coordinate and share information with each other.
+Since these parties have different goals, privacy concerns, and security practices, it is hard to establish a common application platform.
+Moreover, the transactive systems also has to satisfy the stringent security and safety requirements of power grids, which imposes further constraints on coordination.  
+Likewise, in multimodal routing, computational components belonging to the government, private companies, and individual users have to work together, despite having limited trust in each other.
+
+Blockchain based computational platforms may act as a key enabling technology for social dispersed computing, by solving the above coordination problem.
+Using blockchain technology, the NCPs can reach consensus on any state variable in the system, without relying on a trusted third party or trusting each other.
+For example, NCPs within a transactive energy system can reach consensus on energy prices, which is crucial for the stability of the grid.
+Further, distributed consensus not only solves the trust issue, but also provides fault-tolerance since consensus is always reached on the correct state as long as the number of faulty NCPs is below a threshold.
+
+In a blockchain based platform, transitions between system states are recorded as transactions in a ledger.
+To reach system-wide consensus, NCPs must share transactions with all other participants in a system.
+Ironically, the public nature of the ledger is a double-edged sword, which poses severe threats to privacy.
+As every state change must be published as a transaction, it is impossible to keep certain state variables confidential.
+This is clearly unacceptable for most social dispersed computing applications, which handle sensitive personal information, such as individual users' locations or real-time energy usage data of individual households.
+
+The current solution to this privacy problem is to publish certain state variables in an encrypted form (e.g., encrypted energy usage data), which can be decrypted only by authorized entities.
+However, this solution has fundamental limitations.
+Since NCPs must reach consensus on the state of the system, any state update that is based on the values of encrypted variables requires that a majority of NCPs be able to decrypt the variables, which would clearly violate the privacy of the encrypted variables.
+As a consequence, privacy-preserving systems cannot perform computations based on private values.
+
+To enable the next step in the evolution of decentralized computing, blockchain platforms must be extended with functionality that allows them to perform computations on encrypted variables.
+In this direction, homomorphic encryption can act as an enabling technology.
+Using homomorphic encryption, NCPs can perform computation on private state variables without learning their values.
+For example, in a transactive energy system, individual households' real-time energy consumption may be encrypted with a homomorphic encryption scheme and published on the distributed ledger.
+Then, every NCP in the system is able to compute the encrypted aggregate energy consumption by adding together the encrypted individual consumption values.
+This allows the NCPs to reach consensus on state variables without learning their values.
+
 \clearpage

### 2017-06-23 papers/IARPA-RFI-17-03/rfi.tex
update

@@
 renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}.
-
-\Aron{I am not sure what this sentence was supposed to say.}
-These systems are effectively an example of social dispersed computing (Volttron \cite{katipamula2016volttron}, OpenFMB
-\cite{gunthersmart}, and the Resilient Information Architecture
-Platform for Smart Grid (RIAPS)
-\cite{eisele2017riaps,Scott2017ICCPS}) where consumer power storage and private energy sources as solar panels, achieving grid stability will be challenging.
+%\Aron{I am not sure what this sentence was supposed to say.}
+%These systems are effectively an example of social dispersed computing (Volttron \cite{katipamula2016volttron}, OpenFMB
+%\cite{gunthersmart}, and the Resilient Information Architecture
+%Platform for Smart Grid (RIAPS)
+%\cite{eisele2017riaps,Scott2017ICCPS}) where consumer power storage and private energy sources as solar panels, achieving grid stability will be challenging.  
 With social dispersed computing, energy consumers, producers, and storage solutions in a transactive grid will be discovered automatically and monitored continuously, and system status will be updated in case devices appear to be offline.
@@
 
-However, the computing structure in these systems does not focus on the privacy challenges that arise from the
-required information exchange in this decentralized transactive
-system: 
+The computing structure in these systems does not focus on the privacy challenges that arise from the
+required information exchange:
 \begin{itemize}
@@
 Consequently, a number of transit agencies and cities are turning towards multimodal  solutions combining transportation operated by both cities and private users.
-However, given the large number of choices and available options, this often leads to a \Aron{Does this alway boil down to a dynamic programming problem in the algorithmic sense?} dynamic programming problem that must be solved online, considering several state variables, such as traffic congestion, mode capacity, and personal preferences.
+However, given the large number of choices and available options, this can lead to a %\Aron{Does this alway boil down to a dynamic programming problem in the algorithmic sense?}
+dynamic programming problem that must be solved online, considering several state variables, such as traffic congestion, mode capacity, and personal preferences.
 
@@
 At the same time, this system must also consider the investment required by the cities in the computing infrastructure required to solve the problem at scale.
-Alternatively, a novel proof-of-concept that utilizes the various edge computing resources available in the city, including the mobile devices of the commuters, can be employed by municipalities to improve efficiency within their cities with little investment.
+Alternatively, a social dispersed computing approach that utilizes the various edge computing resources available in the city, including the mobile devices of the commuters, can be employed by municipalities to improve efficiency within their cities with little investment.
 

### 2017-07-21 delieverables/July2017/architecture-layers.tex
Initial commit of July Technical specification deliverable.

% The Purdue Enterprise Reference Architecture (PERA) model.
% Author: Erno Pentzin (2013)
\documentclass{standalone}
\usepackage{tikz}
\usetikzlibrary{chains}
\begin{document}

\newcommand{\halfwidth}{3.5cm}
\newcommand{\halfxshift}{2.25cm}

\begin{tikzpicture}[
	scale=0.75,
	start chain=1 going below, 
	start chain=2 going right,
	start chain=3 going right,
	node distance=1mm,
	desc/.style={
		scale=0.75,
		on chain=3,
		rectangle,
		rounded corners,
		draw=black, 
		very thick,
		text centered,
		text width=8cm,
		minimum height=12mm,
		fill=blue!30
		},
	it/.style={
		fill=blue!10
	},
	half/.style={
        text width=\halfwidth,
	},
	level/.style={
		scale=0.75,
		on chain=1,
		minimum height=12mm,
		text width=2cm,
		text centered
	},
	every node/.style={font=\sffamily}
]

% Levels
\node [level] (Level 5) {Level 5};
\node [level] (Level 4) {Level 4};
\node [level] (Level 3) {Level 3};
\node [level] (Level 2) {Level 2};
\node [level] (Level 1.5) { };
\node [level] (Level 1) {Level 1};
\node [level] (Level 0) {Level 0};

\newcommand{\secondhalfxshift}{2.25cm}
\newcommand{\shiftbackafterhalf}{2.25cm}

% Descriptions
\chainin (Level 5); % Start right of Level 5
% IT levels
\node [desc, it] (Archives) {Archives/File Servers};
\node [desc, it, continue chain=going below] (ERP) {ERP/Finance/Messaging};
% ICS levels
\node [desc] (Operations) {Operations Management/Historians};
\node [desc] (Supervisory) {Supervisory Controls};
\node [desc] (OnionRouting) {Communication anonymity (e.g., onion routing)};

\node [desc, half, xshift=\halfxshift] (PLC) {PLC/RTU IP Communication};
\node [desc, half, xshift=-2*\halfxshift] (SIS) {Safety Instrumented Systems};

\node [desc, xshift=\halfxshift] (IO) {Communication network and operating system}; % this is shifted to shift 'back' to starting place.

\end{tikzpicture}

\end{document}

### 2017-07-21 delieverables/July2017/miners-commands.tex
Initial commit of July Technical specification deliverable.

\subsection{Miners}

Miners are the only nodes on the network allowed to do mining. These are required for the operation of the network because new blocks need to be generated so as to store transactions. Also they need to have a predictable frequency (which means adjusting difficulty of the required computations to create a new block) so as to provide timing constraints.

\subsubsection{Create}

The following command allows you to create the miners specified in <network-config.json> on the test network. This command evaluates the number of hosts given, the number of miners specified, the starting port for all clients, and the protocol to use for communication with the client once it has started.
\begin{lstlisting}[language=bash]
$ ./manager miners create file=network-config.json
\end{lstlisting}

\subsubsection{Start}

The following command allows you to start all the Blockchain clients on the test network declared in the provided <network-config.json> file.
\begin{lstlisting}[language=bash]
$ ./manager miners create file=network-config.json
\end{lstlisting}

\subsubsection{Stop}
The following command allows you to stop all the Blockchain clients on the test network declared in the provided <network-config.json> file.
\begin{lstlisting}[language=bash]
$ ./manager miners create file=network-config.json
\end{lstlisting}

\subsubsection{Delete}
The following command allows you to remove all of the Blockchain clients' data on the test network declared in the provided <network-config.json> file.
\begin{lstlisting}[language=bash]
$ ./manager miners create file=network-config.json
\end{lstlisting}

### 2017-07-21 delieverables/July2017/tech.tex
Initial commit of July Technical specification deliverable.

\documentclass[]{article}

\usepackage{listings}
\usepackage{color}
\usepackage{standalone}

% Used in arch layers diagram
\usepackage{tikz}
\usetikzlibrary{chains}

% Used in sequence-diagram.
\usepackage{pgf-umlsd}

\lstset{breaklines=true, tabsize=3,keywordstyle=\color{blue},language=idl,}

%opening
\title{Technical Specifications of\\ Ethereum Network Testing Framework}
\author{}

\begin{document}

\maketitle

\begin{abstract}

Building a test network for Ethereum is a highly complex process with a number of steps involved that are tedious and error prone. We have developed a framework that allows for deployment and management of ethereum clients on a private test network. This allows for testing of not only ethereum client configurations, but also for testing of complex smart contract interactions and related software.

\end{abstract}

\section{Design Goals}

\section{System Architecture}

\subsection{Blockchain}

\subsection{RIAPS}

\subsection{Distributed File Storage}
Include description of a dist. file system that we are going to incorporate

\section{Network Manager}

We have developed a python command line interface program for managing the test network. This 'Network Manager' (manager.py) is stateless, has built in help documentation for manual command line interactions, and each and every command and sub-command in the program has a --verbose flag associated with it. It was designed this way so as to promote easily integration into any existing network administration tool-chain(s).

These commands are designed to allow for interaction with the entire test-network designed in <network-config.json> at once. If interactions with a specific host or client on a host is desired, then the python Fabric tool suite is provided. Run `fab -l` in the root directory of the Network Manager to be listed all Fabric methods given for interaction with individual hosts or clients.

\input{bootnodes-commands}

\input{miners-commands}

\input{clients-commands}

\input{blockchains-commands}

\subsection{IDL for Actors}

\lstinputlisting[language=JAVA]{miner.aidl}

\lstinputlisting[language=JAVA]{dataStore.aidl}

\lstinputlisting[language=JAVA]{dso.aidl}

\lstinputlisting[language=JAVA]{prosumer.aidl}

\lstinputlisting[language=JAVA]{consumer.aidl}

\begin{figure}
	\includestandalone[width=\textwidth]{test-network-setup-seq-diag}%     without .tex extension
	% or use \input{mytikz}
	\caption{Sequence Diagram of Full Test Network Operation Cycle}
	\label{fig:seqdiag:testnetworksetup}
\end{figure}

\section{Test Network Architecture}

\subsection{Host Software}

\subsubsection{Blockchain Client}

\subsubsection{RIAPS}

\subsubsection{Distributed File Storage}

\subsection{Management Software}

command line python application leveraging Fabric for individual host control.

\end{document}

### 2017-07-21 delieverables/July2017/test-network-setup-seq-diag.tex
Initial commit of July Technical specification deliverable.

\documentclass{standalone}

\usepackage{pgf-umlsd}
\usepackage{adjustbox}

\begin{document}
	\trimbox{0cm -.5cm -0.75cm -0.5cm}{

	\begin {sequencediagram}
%	\newinst{name}{:Instance}
	\newthread {a}{: Manager Install}
%	\newinst {b }{: Manager}
	\newinst [1]{d}{: Bootnodes }
%	\newinst [1]{ch}{: Client Hosts }
	\newinst [2]{c}{: Clients }
%	\newinst [3]{mh}{: Miner Hosts }
	\newinst [3]{m}{: Miners }

%	\newinst [5]{dh}{: Discovery Hosts }
\begin{sdblock}{Creation}{Creating all Ethereum related processes}
	\begin{call}{a}{create node(s)}{d}{KEY:IP:PORT (s)}
	\end{call}

	\begin{call}{a}{create miner(s)}{m}{KEY:IP:PORT (s)}
	\end{call}
	\begin{call}{a}{create client(s)}{c}{KEY:IP:PORT (s)}
	\end{call}
	\begin{call}{a}{create Genesis Block, with default credits}{a}{Genesis Block}
	\end{call}

	\begin{call}{a}{copy Genesis Block \& bootnode info}{m}{}
	\end{call}
	\begin{call}{a}{copy Genesis Block \& bootnode info}{c}{}
	\end{call}
\end{sdblock}

\begin{sdblock}{Starting}{Starting all Ethereum related processes}
	\begin{call}{a}{start node(s)}{d}{}
	\end{call}
	\begin{call}{a}{start Miner(s)}{m}{}
	\end{call}
	\begin{call}{a}{Start Client(s)}{c}{}
	\end{call}
\end{sdblock}

\begin{sdblock}{Stopping}{Stopping all Ethereum related processes}
	\begin{call}{a}{stop Client(s)}{c}{}
	\end{call}
	\begin{call}{a}{stop Miner(s)}{m}{}
	\end{call}
	\begin{call}{a}{stop node(s)}{d}{}
	\end{call}
\end{sdblock}

\begin{sdblock}{Removal}{Removing all Ethereum related processes}
	\begin{call}{a}{remove Client(s)}{c}{}
	\end{call}
	\begin{call}{a}{remove Miner(s)}{m}{}
	\end{call}
	\begin{call}{a}{remove node(s)}{d}{}
	\end{call}
\end{sdblock}

	\end {sequencediagram}
}
\end{document}

### 2017-07-22 delieverables/July2017/blockchains-commands.tex

\subsection{Blockchains}

Blockchains are the Distributed Ledger of the network infrastructure that we are setting up. In particular, we have to create a Genesis Block when creating any new test network. For simplicity sake, we also pre-allocate all clients (Consumers, Presumers, etc.) on the test network with a starting amount of currency. This allows all clients to begin translations upon creation of the network without requiring each client to mine in an attempt to gain some currency.

\subsubsection{Make}

The following command allows you to create the <genesis-block.json> configuration file from the input <network-config.json>. This <genesis-block.json> defines the parameters required for creation of a new Blockchain.
\begin{lstlisting}[language=bash]
$ ./network-manager blockchains make file=network-config.json
\end{lstlisting}

\subsubsection{Create}
The following command allows you to create the actual blockchain defined in the <genesis-block.json> configuration file(Created with 'blockchains make' command).
\begin{lstlisting}[language=bash]
$ ./network-manager blockchains create file=network-config.json
\end{lstlisting}

### 2017-08-16 code/PhaseI/components/DSOWrapper.py
no message

@@ -11,6 +11,7 @@ class DSOWrapper(DSO):
     self.contractAddress = CONTRACT_ADDRESS
     self.account = self.geth.get_addresses()[0]
     super(DSOWrapper, self).__init__()
+    # TODO: remove testing code once event filtering works reliably
     logging.info("Test result: " + str(self.geth.command("eth_sendTransaction", params=[{'data': "0xf8a8fd6d", 'to': self.contractAddress, 'from': self.account}])))
     
   def run(self):
@@ -31,8 +32,9 @@ class DSOWrapper(DSO):
             
   def sendEther(self, address):
     # TODO: check this, especially the amount of Ether
+    logging.info("sendEther()")
     result = self.geth.command("eth_sendTransaction", params=[{'to': address, 'value': "0xffffff", 'from': self.account}])
-    logging.info(result)
+    logging.info("Result: " + result)
 
   # contract function calls 
 

### 2017-08-16 code/PhaseI/components/Filter.py

@@ -20,7 +20,7 @@ class Filter:
     logging.info("Created filter (ID = {}).".format(self.filterID))
     
   def poll_events(self):
-    logging.info("Block number = " + str(self.geth.command("eth_blockNumber", params=[])))
+    logging.info("Block number: " + str(self.geth.command("eth_blockNumber", params=[])))
     log = self.geth.command("eth_getFilterChanges", params=[self.filterID])
     logging.info("Raw log: " + str(log))
     for log_item in log:

### 2017-08-16 code/PhaseI/components/Geth.py

@@ -19,7 +19,7 @@ class Geth:
   def command(self, method, params=[], id=1, jsonrpc="2.0", verbose=False):
     """ Method to abstract away 'curl' usage to interact with RPC of geth clients. """
     # the <ip:port> to connect to
-    ipPort = str(ip) + ":" + str(port)
+    ipPort = str(self.ip) + ":" + str(self.port)
     # buffer to capture output
     buffer = BytesIO()
     # start building curl command to process
@@ -51,7 +51,6 @@ class Geth:
             raise Exception('rpc_communication_error', 'Error No: ' + errno + ", message: " + message)
         return {'error':'rpc_comm_error','desc':message,'error_num':errno}
 
-
     # decode result
     results = str(buffer.getvalue().decode('iso-8859-1'))
     if verbose:
@@ -72,7 +71,7 @@ class Geth:
                 raise Exception('rpc_communication_error', "Unknown Error: possible method/parameter(s) were wrong and/or networking issue.")
             return {"error":"Unknown Error: possible method/parameter(s) were wrong and/or networking issue."}
 
-  def get_addresses():
+  def get_addresses(self):
     return self.command("eth_accounts")
 
 

### 2017-08-16 code/PhaseI/components/Offer.py

@@ -1,5 +1,0 @@
-class Offer:
-  def __init__(self, assetID, asset, price):
-    self.assetID = assetID
-    self.asset = asset
-    self.price = price

### 2017-08-16 code/PhaseI/components/SmartHomeTrader.py

@@ -29,11 +29,7 @@ class SmartHomeTrader:
     for i in range(num_addresses):
       addresses.append(str(binascii.hexlify(numpy.random.bytes(20))))
     return addresses
-      
-  def net_production_predictor(self, timestep):
-    # TODO: use data (based on name and timestep)
-    return int((CONSUMPTION_LIMIT + PRODUCTION_LIMIT) * self.random.random() - CONSUMPTION_LIMIT)
-    
+          
   def predict(self):
     # choose random address for trading
     address = self.random.choice(self.addresses)
@@ -81,6 +77,10 @@ class SmartHomeTrader:
       del self.offers[offerID]
     if assetID in self.cons_assets:
       del self.cons_assets[assetID]           
+
+  def net_production_predictor(self, timestep):
+    # random predictor for testing
+    return int((CONSUMPTION_LIMIT + PRODUCTION_LIMIT) * self.random.random() - CONSUMPTION_LIMIT)
 
   # DSO message sender for testing
   def withdraw_assets(self, address, asset, financial):

### 2017-08-16 code/PhaseI/components/SmartHomeTraderWrapper.py

@@ -1,7 +1,6 @@
 import zmq
 import logging
 from time import time, sleep
-from random import randint
 
 from config import *
 from const import *
@@ -9,10 +8,11 @@ from SmartHomeTrader import SmartHomeTrader
 from Filter import Filter
 from Geth import Geth
 
-POLLING_INTERVAL = 5
+POLLING_INTERVAL = 10
 
 class SmartHomeTraderWrapper(SmartHomeTrader):
-  def __init__(self, name):
+  def __init__(self, name, net_production):
+    self.net_production = net_production
     self.geth = Geth()
     logging.info("Connecting to DSO...")
     self.dso = zmq.Context().socket(zmq.REQ)
@@ -38,6 +38,9 @@ class SmartHomeTraderWrapper(SmartHomeTrader):
         next_polling = current_time + POLLING_INTERVAL
         self.poll_events()
       sleep(min(next_prediction - current_time, next_polling - current_time))
+
+  def net_production_predictor(self, timestep):
+    return self.net_production[timestep % len(timestep)]
       
   def get_addresses(self, num_addresses):
     logging.info("Querying own addresses...")
@@ -76,18 +79,38 @@ class SmartHomeTraderWrapper(SmartHomeTrader):
     
   # contract function calls
   def postOffer(self, address, assetID, price):
+    logging.info("{}.postOffer({}, {})".format(address, assetID, price))
     data = "0xed7272e2" + Geth.encode_uint(assetID) + Geth.encode_uint(price)
     result = self.geth.command("eth_sendTransaction", params=[{'from': address, 'data': data, 'to': self.contractAddress}])
-    logging.info(result)
+    logging.info("Result: " + result)
 
   def acceptOffer(self, address, offerID, assetID):
+    logging.info("{}.acceptOffer({}, {})".format(address, offerID, assetID))
     data = "0xf1edd7e2" + Geth.encode_uint(offerID) + Geth.encode_uint(assetID)
     result = self.geth.command("eth_sendTransaction", params=[{'from': address, 'data': data, 'to': self.contractAddress}])
-    logging.info(result)
+    logging.info("Result: " + result)
+
+def read_data(prosumer_id):
+  logging.info("Reading net production values...")
+  with open(DATA_PATH + "day_power_profile.csv", "rt") as fin:
+    lines = fin.readlines()
[…]

### 2017-08-16 code/PhaseI/components/config.py

@@ -1,7 +1,7 @@
 CONTRACT_ADDRESS = '0x0a20794d218450ef3f84499ab5d5cbe252a78aba' # "0x01...23" or whatever the address of the contract is
 DSO_ADDRESS = 'tcp://127.0.0.1:10001'
 LEDGER_ADDRESS = 'tcp://127.0.0.1:10002'
-
+DATA_PATH = "../data/"
 
 BYTECODE = "0x60606040526000600360006101000a81548167ffffffffffffffff021916908367ffffffffffffffff1602179055506000600560006101000a81548167ffffffffffffffff021916908367ffffffffffffffff160217905550341561006357600080fd5b5b336000806101000a81548173ffffffffffffffffffffffffffffffffffffffff021916908373ffffffffffffffffffffffffffffffffffffffff1602179055505b5b6123eb806100b56000396000f3006060604052361561008c576000357c0100000000000000000000000000000000000000000000000000000000900463ffffffff16806323b87507146100915780633436bd0c146101245780633b719dc014610151578063cb791be91461019d578063cbfd042f146101ca578063ed7272e2146101f7578063f1edd7e21461025f578063f8a8fd6d1461029f575b600080fd5b341561009c57600080fd5b6100fa600480803573ffffffffffffffffffffffffffffffffffffffff1690602001909190803560070b90602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff169060200190919050506102b4565b604051808267ffffffffffffffff1667ffffffffffffffff16815260200191505060405180910390f35b341561012f57600080fd5b61014f600480803567ffffffffffffffff16906020019091905050610352565b005b341561015c57600080fd5b61019b600480803573ffffffffffffffffffffffffffffffffffffffff1690602001909190803567ffffffffffffffff169060200190919050506104ca565b005b34156101a857600080fd5b6101c8600480803567ffffffffffffffff16906020019091905050610628565b005b34156101d557600080fd5b6101f5600480803567ffffffffffffffff16906020019091905050610894565b005b341561020257600080fd5b610235600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff16906020019091905050610b9f565b604051808267ffffffffffffffff1667ffffffffffffffff16815260200191505060405180910390f35b341561026a57600080fd5b61029d600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff169060200190919050506111cc565b005b34156102aa57600080fd5b6102b2611b92565b005b
[…]

### 2017-08-16 code/PhaseI/components/const.py

@@ -1,4 +1,4 @@
 TIME_INTERVAL = 30 # seconds
-CONSUMPTION_LIMIT = 50
-PRODUCTION_LIMIT = 50
+CONSUMPTION_LIMIT = 120
+PRODUCTION_LIMIT = 800
 

### 2017-08-16 code/PhaseI/components/DSOWrapper.py
no message

@@ -51,7 +51,7 @@ class DSOWrapper(DSO):
     logging.info("Result: " + result)
     
 if __name__ == "__main__":
-  logging.basicConfig(level=logging.INFO)
+  logging.basicConfig(format='%(asctime)s / %(levelname)s: %(message)s', level=logging.INFO)
   dso = DSOWrapper()
   dso.run()
 

### 2017-08-16 code/PhaseI/components/SmartHomeTraderTesting.py

@@ -67,7 +67,7 @@ class SmartHomeTraderTesting(SmartHomeTraderWrapper):
     logging.info(response)
 
 if __name__ == "__main__":
-  logging.basicConfig(level=logging.INFO)
+  logging.basicConfig(format='%(asctime)s / %(levelname)s: %(message)s', level=logging.INFO)
   trader = SmartHomeTraderTesting("home" + str(randint(0,100)))
   trader.run()
 

### 2017-08-16 code/PhaseI/components/SmartHomeTraderWrapper.py

@@ -1,5 +1,6 @@
 import zmq
 import logging
+import sys
 from time import time, sleep
 
 from config import *
@@ -8,7 +9,7 @@ from SmartHomeTrader import SmartHomeTrader
 from Filter import Filter
 from Geth import Geth
 
-POLLING_INTERVAL = 10
+POLLING_INTERVAL = 5 # seconds
 
 class SmartHomeTraderWrapper(SmartHomeTrader):
   def __init__(self, name, net_production):
@@ -40,7 +41,7 @@ class SmartHomeTraderWrapper(SmartHomeTrader):
       sleep(min(next_prediction - current_time, next_polling - current_time))
 
   def net_production_predictor(self, timestep):
-    return self.net_production[timestep % len(timestep)]
+    return self.net_production[timestep % len(self.net_production)]
       
   def get_addresses(self, num_addresses):
     logging.info("Querying own addresses...")
@@ -48,7 +49,7 @@ class SmartHomeTraderWrapper(SmartHomeTrader):
       
   def poll_events(self):
     for event in self.filter.poll_events():
-      self.info("Event: " + str(event))
+      logging.info("Event: " + str(event))
       params = event['params']
       name = event['name']
       if name == "FinancialAdded":
@@ -103,14 +104,14 @@ def read_data(prosumer_id):
     return data
 
 if __name__ == "__main__":
-  logging.basicConfig(level=logging.INFO)
+  logging.basicConfig(format='%(asctime)s / %(levelname)s: %(message)s', level=logging.INFO)
   if len(sys.argv) > 1:
     prosumer_id = int(sys.argv[1])
     if prosumer_id < 1: 
       print("Prosumer ID must be greater than zero!")
   else:
     prosumer_id = 1
-  trader = SmartHomeTraderWrapper("prosumer_" + str(prosumerID), read_data(prosumer_id)) 
+  trader = SmartHomeTraderWrapper("prosumer_" + str(prosumer_id), read_data(prosumer_id)) 
   trader.run()
 
     

### 2017-08-16 code/PhaseI/components/DSOWrapper.py
no message

@@ -1,5 +1,6 @@
 import zmq
 import logging
+from time import sleep
 
 from config import *
 from DSO import DSO
@@ -7,12 +8,12 @@ from Geth import Geth
 
 class DSOWrapper(DSO): 
   def __init__(self):
-    self.geth = Geth()
-    self.contractAddress = CONTRACT_ADDRESS
+    self.geth = Geth()    
     self.account = self.geth.get_addresses()[0]
+    self.deploy_contract()
     super(DSOWrapper, self).__init__()
     # TODO: remove testing code once event filtering works reliably
-    logging.info("Test result: " + str(self.geth.command("eth_sendTransaction", params=[{'data': "0xf8a8fd6d", 'to': self.contractAddress, 'from': self.account}])))
+    #logging.info("Test result: " + str(self.geth.command("eth_sendTransaction", params=[{'data': "0xf8a8fd6d", 'to': self.contractAddress, 'from': self.account}])))
     
   def run(self):
     logging.info("Entering main function...")
@@ -21,14 +22,35 @@ class DSOWrapper(DSO):
     logging.info("Listening for traders...")
     while True:
       msg = trader.recv_pyobj()
-      logging.info("withdraw_assets({})".format(msg))
-      try:
-        result = self.withdraw_assets(msg['prosumer'], msg['auth'], msg['asset'], msg['financial'], msg['address'])
-      except Exception as e:
-        logging.exception(e)
-        result = "Malformed message."
-      logging.info(result)
-      trader.send_pyobj(result)
+      if msg['request'] == "withdraw_assets":
+        logging.info("withdraw_assets({})".format(msg))
+        params = msg['params']
+        try:
+          result = self.withdraw_assets(params['prosumer'], params['auth'], params['asset'], params['financial'], params['address'])
+        except Exception as e:
+          logging.exception(e)
+          result = "Malformed message."
+        logging.info(result)
+        trader.send_pyobj(result)
+      elif msg['request'] == "query_contract_address":
+        logging.info("query_contract_address()")
+        trader.send_pyobj(self.contractAddress)
+      else:
+        logging.error("Unknown request: " + msg['request'])
+        trader.send_pyobj("Unknown request!")
+      
+  def deploy_contract(self):
+    logging.info("Deploying contract...")
+    receiptID = self.geth.command("eth_sendTransaction", params=[{"data": BYTECODE, "gas": '0x4300000', "from": self.account}])
[…]

### 2017-08-16 code/PhaseI/components/Filter.py

@@ -20,9 +20,9 @@ class Filter:
     logging.info("Created filter (ID = {}).".format(self.filterID))
     
   def poll_events(self):
-    logging.info("Block number: " + str(self.geth.command("eth_blockNumber", params=[])))
+    block = self.geth.command("eth_blockNumber", params=[])
     log = self.geth.command("eth_getFilterChanges", params=[self.filterID])
-    logging.info("Raw log: " + str(log))
+    logging.info("Log: {} items (block number: {})".format(len(log), block))
     for log_item in log:
       yield decode_log(log_item)
 

### 2017-08-16 code/PhaseI/components/Geth.py

@@ -12,7 +12,7 @@ class Geth:
   def encode_int(value):
     return format(value & 0xffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff, "064x")
 
-  def __init__(self, port=9006, ip="10.4.209.25"):
+  def __init__(self, port=9010, ip="10.4.209.25"):
     self.ip = ip
     self.port = port
 

### 2017-08-16 code/PhaseI/components/SmartHomeTrader.py

@@ -6,6 +6,7 @@ from const import *
 from EnergyAsset import EnergyAsset
 
 BASE_PRICE = 1
+START_INTERVAL = 40
 PREDICTION_HORIZON = 1
 
 class SmartHomeTrader: 
@@ -20,7 +21,7 @@ class SmartHomeTrader:
     # create anonymous accounts
     self.addresses = self.get_addresses(num_addresses)
     # predict net production and request assets for trading 
-    self.next_interval = 0
+    self.next_interval = START_INTERVAL
     for timestep in range(PREDICTION_HORIZON):
       self.predict()
       
@@ -42,7 +43,7 @@ class SmartHomeTrader:
   def asset_added(self, address, assetID, asset):
     # check if asset belongs to the prosumer
     # TODO: does this test actually work?
-    if address not in addresses:
+    if address not in self.addresses:
       return
     # production or consumption 
     if asset.power > 0:

### 2017-08-16 code/PhaseI/components/SmartHomeTraderWrapper.py

@@ -17,13 +17,13 @@ class SmartHomeTraderWrapper(SmartHomeTrader):
     self.geth = Geth()
     logging.info("Connecting to DSO...")
     self.dso = zmq.Context().socket(zmq.REQ)
-    logging.info("DSO connected ({}).".format(self.dso))
     self.dso.connect(DSO_ADDRESS)
-    self.contractAddress = CONTRACT_ADDRESS
+    logging.info("DSO connected ({}).".format(self.dso))
+    self.query_contract_address()
     logging.info("Creating event filter...")
     self.filter = Filter()
     super(SmartHomeTraderWrapper, self).__init__(name)
-    
+  
   def run(self):
     logging.info("Entering main loop...")
     next_prediction = time() + TIME_INTERVAL
@@ -53,7 +53,7 @@ class SmartHomeTraderWrapper(SmartHomeTrader):
       params = event['params']
       name = event['name']
       if name == "FinancialAdded":
-        self.FinancialAdded(params['address'], param['amount'])
+        self.FinancialAdded(params['address'], params['amount'])
       elif name == "AssetAdded":
         self.AssetAdded(params['address'], params['assetID'], params['power'], params['start'], params['end'])
       elif name == "OfferPosted":
@@ -64,31 +64,45 @@ class SmartHomeTraderWrapper(SmartHomeTrader):
         self.OfferAccepted(params['offerID'], params['assetID'], params['transPower'], params['transStart'], params['transEnd'], params['price'])
      
   # DSO message sender 
+  
   def withdraw_assets(self, address, asset, financial):
     # TODO: provide auth
     msg = { 
-      'prosumer': self.name, 
-      'auth': "password", 
-      'asset': asset, 
-      'address': address, 
-      'financial': financial 
+      'request': "withdraw_assets", 
+      'params': {
+        'prosumer': self.name, 
+        'auth': "password", 
+        'asset': asset, 
+        'address': address, 
+        'financial': financial 
+      }
     }
     logging.info(msg)
     self.dso.send_pyobj(msg)    
     response = self.dso.recv_pyobj()
     logging.info(response)
-    
+
+  def query_contract_address(self):
+    msg = {
+      'request': "query_contract_address"
+    }
+    logging.info(msg)
+    self.dso.send_pyobj(msg)
+    self.contractAddress = self.dso.recv_pyobj()
+    logging.info("Contract address: " + self.contractAddress)
+        
   # contract function calls
[…]

### 2017-08-16 code/PhaseI/components/config.py

@@ -1,7 +1,4 @@
-CONTRACT_ADDRESS = '0x0a20794d218450ef3f84499ab5d5cbe252a78aba' # "0x01...23" or whatever the address of the contract is
 DSO_ADDRESS = 'tcp://127.0.0.1:10001'
 LEDGER_ADDRESS = 'tcp://127.0.0.1:10002'
 DATA_PATH = "../data/"
-
 BYTECODE = "0x60606040526000600360006101000a81548167ffffffffffffffff021916908367ffffffffffffffff1602179055506000600560006101000a81548167ffffffffffffffff021916908367ffffffffffffffff160217905550341561006357600080fd5b5b336000806101000a81548173ffffffffffffffffffffffffffffffffffffffff021916908373ffffffffffffffffffffffffffffffffffffffff1602179055505b5b6123eb806100b56000396000f3006060604052361561008c576000357c0100000000000000000000000000000000000000000000000000000000900463ffffffff16806323b87507146100915780633436bd0c146101245780633b719dc014610151578063cb791be91461019d578063cbfd042f146101ca578063ed7272e2146101f7578063f1edd7e21461025f578063f8a8fd6d1461029f575b600080fd5b341561009c57600080fd5b6100fa600480803573ffffffffffffffffffffffffffffffffffffffff1690602001909190803560070b90602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff169060200190919050506102b4565b604051808267ffffffffffffffff1667ffffffffffffffff16815260200191505060405180910390f35b341561012f57600080fd5b61014f600480803567ffffffffffffffff16906020019091905050610352565b005b341561015c57600080fd5b61019b600480803573ffffffffffffffffffffffffffffffffffffffff1690602001909190803567ffffffffffffffff169060200190919050506104ca565b005b34156101a857600080fd5b6101c8600480803567ffffffffffffffff16906020019091905050610628565b005b34156101d557600080fd5b6101f5600480803567ffffffffffffffff16906020019091905050610894565b005b341561020257600080fd5b610235600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff16906020019091905050610b9f565b604051808267ffffffffffffffff1667ffffffffffffffff16815260200191505060405180910390f35b341561026a57600080fd5b61029d600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff169060200190919050506111cc565b005b34156102aa57600080fd5b6102b2611b92565b005b6000
[…]

### 2017-08-16 code/PhaseI/components/filtertest.py

@@ -2,6 +2,7 @@ from time import sleep
 
 from config import *
 from Geth import Geth
+from Filter import decode_log
 
 geth = Geth()
 filterID = geth.command("eth_newFilter", params=[{"fromBlock": "0x1"}]) 
@@ -14,11 +15,15 @@ receipt = None
 while receipt is None:
   sleep(5)
   receipt = geth.command("eth_getTransactionReceipt", params=[receiptID])
-  print("receipt = ", receipt)
   print("block = ", geth.command("eth_blockNumber"))
+  print("receipt = ", receipt)
 contract = receipt['contractAddress']
 print("test transaction = ", geth.command("eth_sendTransaction", params=[{"to": contract, "data": '0xf8a8fd6d', "gas": '0x4300000', "from": account}]))
 while True:
   sleep(5)
-  print("log = ", geth.command("eth_getFilterChanges", params=[filterID]))
+  print("block = ", geth.command("eth_blockNumber"))
+  log = geth.command("eth_getFilterChanges", params=[filterID])
+  print("log = ", log)
+  for log_item in log:
+    print(decode_log(log_item))
 

### 2017-08-17 code/PhaseI/components/DSOWrapper.py
no message

@@ -12,8 +12,6 @@ class DSOWrapper(DSO):
     self.account = self.geth.get_addresses()[0]
     self.deploy_contract()
     super(DSOWrapper, self).__init__()
-    # TODO: remove testing code once event filtering works reliably
-    #logging.info("Test result: " + str(self.geth.command("eth_sendTransaction", params=[{'data': "0xf8a8fd6d", 'to': self.contractAddress, 'from': self.account}])))
     
   def run(self):
     logging.info("Entering main function...")
@@ -41,11 +39,11 @@ class DSOWrapper(DSO):
       
   def deploy_contract(self):
     logging.info("Deploying contract...")
-    receiptID = self.geth.command("eth_sendTransaction", params=[{"data": BYTECODE, "gas": '0x4300000', "from": self.account}])
+    receiptID = self.geth.command("eth_sendTransaction", params=[{'data': BYTECODE, 'from': self.account, 'gas': TRANSACTION_GAS}])
     logging.info("Transaction receipt: " + receiptID)
     while True:
       sleep(5)
-      logging.info("Block number: " + self.geth.command("eth_blockNumber", params=[]))
+      logging.info("Waiting for contract to be mined... (block number: {})".format(self.geth.command("eth_blockNumber", params=[])))
       receipt = self.geth.command("eth_getTransactionReceipt", params=[receiptID])
       if receipt is not None:
         self.contractAddress = receipt['contractAddress']
@@ -56,7 +54,7 @@ class DSOWrapper(DSO):
     # TODO: check this, especially the amount of Ether
     logging.info("sendEther()")
     result = self.geth.command("eth_sendTransaction", params=[{'to': address, 'value': "0xffffff", 'from': self.account}])
-    logging.info("Result: " + result)
+    logging.debug("Result: " + result)
 
   # contract function calls 
   
@@ -72,14 +70,14 @@ class DSOWrapper(DSO):
   def addFinancialBalance(self, address, amount):
     logging.info("addFinancialBalance({}, {})".format(address, amount))
     data = "0x3b719dc0" + Geth.encode_address(address) + Geth.encode_uint(amount)
-    result = self.geth.command("eth_sendTransaction", params=[{'data': data, 'to': self.contractAddress, 'from': self.account, 'gas': "0x4300000"}])
-    logging.info("Result: " + result)
[…]

### 2017-08-17 code/PhaseI/components/Filter.py

@@ -22,7 +22,7 @@ class Filter:
   def poll_events(self):
     block = self.geth.command("eth_blockNumber", params=[])
     log = self.geth.command("eth_getFilterChanges", params=[self.filterID])
-    logging.info("Log: {} items (block number: {})".format(len(log), block))
+    logging.debug("Log: {} items (block number: {})".format(len(log), block))
     for log_item in log:
       yield decode_log(log_item)
 

### 2017-08-17 code/PhaseI/components/SmartHomeTraderWrapper.py

@@ -9,12 +9,15 @@ from SmartHomeTrader import SmartHomeTrader
 from Filter import Filter
 from Geth import Geth
 
-POLLING_INTERVAL = 5 # seconds
+POLLING_INTERVAL = 1 # seconds
 
 class SmartHomeTraderWrapper(SmartHomeTrader):
-  def __init__(self, name, net_production):
+  def __init__(self, name, net_production, port):
     self.net_production = net_production
-    self.geth = Geth()
+    if port is None:
+      self.geth = Geth()
+    else:
+      self.geth = Geth(port=port)
     logging.info("Connecting to DSO...")
     self.dso = zmq.Context().socket(zmq.REQ)
     self.dso.connect(DSO_ADDRESS)
@@ -35,7 +38,7 @@ class SmartHomeTraderWrapper(SmartHomeTrader):
         next_prediction = current_time + TIME_INTERVAL
         self.predict()
       if current_time > next_polling:
-        logging.info("Polling events...")
+        logging.debug("Polling events...")
         next_polling = current_time + POLLING_INTERVAL
         self.poll_events()
       sleep(min(next_prediction - current_time, next_polling - current_time))
@@ -94,25 +97,25 @@ class SmartHomeTraderWrapper(SmartHomeTrader):
   # contract function calls
   
   def postOffer(self, address, assetID, price):
-    logging.info("postOffer({}, {}) from address {}".format(assetID, price, address))
+    logging.info("postOffer({}, {}) using address {}".format(assetID, price, address))
     data = "0xed7272e2" + Geth.encode_uint(assetID) + Geth.encode_uint(price)
-    result = self.geth.command("eth_sendTransaction", params=[{'from': address, 'data': data, 'to': self.contractAddress, 'gas': "0x4300000"}])
-    logging.info("Result: " + result)
+    result = self.geth.command("eth_sendTransaction", params=[{'from': address, 'data': data, 'to': self.contractAddress, 'gas': TRANSACTION_GAS}])
+    logging.debug("Result: " + result)
 
   def acceptOffer(self, address, offerID, assetID):
-    logging.info("{}.acceptOffer({}, {})".format(address, offerID, assetID))
+    logging.info("acceptOffer({}, {}) using address {}".format(offerID, assetID, address))
     data = "0xf1edd7e2" + Geth.encode_uint(offerID) + Geth.encode_uint(assetID)
[…]

### 2017-08-17 code/PhaseI/components/config.py

@@ -1,4 +1,5 @@
 DSO_ADDRESS = 'tcp://127.0.0.1:10001'
 LEDGER_ADDRESS = 'tcp://127.0.0.1:10002'
 DATA_PATH = "../data/"
+TRANSACTION_GAS = "0x100000000"
 BYTECODE = "0x60606040526000600360006101000a81548167ffffffffffffffff021916908367ffffffffffffffff1602179055506000600560006101000a81548167ffffffffffffffff021916908367ffffffffffffffff160217905550341561006357600080fd5b5b336000806101000a81548173ffffffffffffffffffffffffffffffffffffffff021916908373ffffffffffffffffffffffffffffffffffffffff1602179055505b5b6123eb806100b56000396000f3006060604052361561008c576000357c0100000000000000000000000000000000000000000000000000000000900463ffffffff16806323b87507146100915780633436bd0c146101245780633b719dc014610151578063cb791be91461019d578063cbfd042f146101ca578063ed7272e2146101f7578063f1edd7e21461025f578063f8a8fd6d1461029f575b600080fd5b341561009c57600080fd5b6100fa600480803573ffffffffffffffffffffffffffffffffffffffff1690602001909190803560070b90602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff169060200190919050506102b4565b604051808267ffffffffffffffff1667ffffffffffffffff16815260200191505060405180910390f35b341561012f57600080fd5b61014f600480803567ffffffffffffffff16906020019091905050610352565b005b341561015c57600080fd5b61019b600480803573ffffffffffffffffffffffffffffffffffffffff1690602001909190803567ffffffffffffffff169060200190919050506104ca565b005b34156101a857600080fd5b6101c8600480803567ffffffffffffffff16906020019091905050610628565b005b34156101d557600080fd5b6101f5600480803567ffffffffffffffff16906020019091905050610894565b005b341561020257600080fd5b610235600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff16906020019091905050610b9f565b604051808267ffffffffffffffff1667ffffffffffffffff16815260200191505060405180910390f35b341561026a57600080fd5b61029d600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff169060200190919050506111cc565b005b34156102aa57600080fd5b6102b2611b92565b005b60008060009054906101000a900473ffffffffffffffffffffffffffffffffffffffff1673fffffffffffffffffff
[…]

### 2017-08-17 code/PhaseI/components/const.py

@@ -1,4 +1,4 @@
-TIME_INTERVAL = 30 # seconds
+TIME_INTERVAL = 90 # seconds
 CONSUMPTION_LIMIT = 120
 PRODUCTION_LIMIT = 800
 

### 2017-08-17 code/PhaseI/components/filtertest.py

@@ -9,7 +9,7 @@ filterID = geth.command("eth_newFilter", params=[{"fromBlock": "0x1"}])
 print("filterID = ", filterID)
 account = geth.command("eth_accounts")[0]
 print("account = ", account)
-receiptID = geth.command("eth_sendTransaction", params=[{"data": BYTECODE, "gas": '0x4300000', "from": account}])
+receiptID = geth.command("eth_sendTransaction", params=[{"data": BYTECODE, "gas": TRANSACTION_GAS, "from": account}])
 print("receiptID = ", receiptID)
 receipt = None
 while receipt is None:
@@ -18,7 +18,7 @@ while receipt is None:
   print("block = ", geth.command("eth_blockNumber"))
   print("receipt = ", receipt)
 contract = receipt['contractAddress']
-print("test transaction = ", geth.command("eth_sendTransaction", params=[{"to": contract, "data": '0xf8a8fd6d', "gas": '0x4300000', "from": account}]))
+print("test transaction = ", geth.command("eth_sendTransaction", params=[{"to": contract, "data": '0xf8a8fd6d', "gas": TRANSACTION_GAS, "from": account}]))
 while True:
   sleep(5)
   print("block = ", geth.command("eth_blockNumber"))

### 2017-08-17 code/PhaseI/components/DSOWrapper.py
no message

@@ -1,5 +1,6 @@
 import zmq
 import logging
+import sys
 from time import sleep
 
 from config import *
@@ -7,8 +8,8 @@ from DSO import DSO
 from Geth import Geth
 
 class DSOWrapper(DSO): 
-  def __init__(self):
-    self.geth = Geth()    
+  def __init__(self, ip, port):
+    self.geth = Geth(ip=ip, port=port)    
     self.account = self.geth.get_addresses()[0]
     self.deploy_contract()
     super(DSOWrapper, self).__init__()
@@ -81,6 +82,12 @@ class DSOWrapper(DSO):
     
 if __name__ == "__main__":
   logging.basicConfig(format='%(asctime)s / %(levelname)s: %(message)s', level=logging.INFO)
-  dso = DSOWrapper()
+  ip = None
+  port = None
+  if len(sys.argv) > 1:
+    ip = sys.argv[1]
+  if len(sys.argv) > 2:
+    port = sys.argv[2]
+  dso = DSOWrapper(ip, port)
   dso.run()
 

### 2017-08-17 code/PhaseI/components/EventRecorder.py

@@ -1,0 +1,63 @@
+import zmq
+import logging
+import sys
+import os
+from time import time, sleep, asctime
+
+from config import *
+from Filter import Filter
+from Geth import Geth
+
+POLLING_INTERVAL = 1 # seconds
+
+class EventRecorder:
+  def __init__(self, ip, port):
+    self.geth = Geth(ip=ip, port=port)
+    logging.info("Connecting to DSO...")
+    self.dso = zmq.Context().socket(zmq.REQ)
+    self.dso.connect(DSO_ADDRESS)
+    logging.info("DSO connected ({}).".format(self.dso))
+    self.query_contract_address()
+    logging.info("Creating event filter...")
+    self.filter = Filter()
+  
+  def run(self):
+    logging.info("Entering main loop...")
+    next_polling = time() + POLLING_INTERVAL
+    with open("events." + asctime(), "wt") as fout:
+      while True:
+        current_time = time()
+        if current_time > next_polling:
+          logging.debug("Polling events...")
+          next_polling = current_time + POLLING_INTERVAL
+          for event in self.filter.poll_events():
+            params = event['params']
+            name = event['name']
+            log = str((asctime(), event['name'], event['params']))
+            print(log)
+            fout.write(log + "\n")
+            fout.flush()
+            os.fsync(fout)
+        sleep(next_polling - current_time)
+
+  def query_contract_address(self):
+    msg = {
+      'request': "query_contract_address"
+    }
+    logging.info(msg)
+    self.dso.send_pyobj(msg)
+    self.contractAddress = self.dso.recv_pyobj()
+    logging.info("Contract address: " + self.contractAddress)
+
+if __name__ == "__main__":
+  logging.basicConfig(format='%(asctime)s / %(levelname)s: %(message)s', level=logging.INFO)
+  ip = None
+  port = None
+  if len(sys.argv) > 1:
+    ip = sys.argv[1]
+  if len(sys.argv) > 2:
+    port = sys.argv[2]
+  recorder = EventRecorder(ip, port) 
+  recorder.run()
+
+    

### 2017-08-17 code/PhaseI/components/Geth.py

@@ -12,9 +12,15 @@ class Geth:
   def encode_int(value):
     return format(value & 0xffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff, "064x")
 
-  def __init__(self, port=9010, ip="10.4.209.25"):
-    self.ip = ip
-    self.port = port
+  def __init__(self, port=None, ip=None):
+    if ip is None:
+      self.ip = "10.4.209.25"
+    else:
+      self.ip = ip
+    if port is None:
+      self.port = 9010
+    else:
+      self.port = port
 
   def command(self, method, params=[], id=1, jsonrpc="2.0", verbose=False):
     """ Method to abstract away 'curl' usage to interact with RPC of geth clients. """

### 2017-08-17 code/PhaseI/components/SmartHomeTrader.py

@@ -6,7 +6,7 @@ from const import *
 from EnergyAsset import EnergyAsset
 
 BASE_PRICE = 1
-START_INTERVAL = 40
+START_INTERVAL = 26
 PREDICTION_HORIZON = 1
 
 class SmartHomeTrader: 

### 2017-08-17 code/PhaseI/components/SmartHomeTraderWrapper.py

@@ -12,12 +12,9 @@ from Geth import Geth
 POLLING_INTERVAL = 1 # seconds
 
 class SmartHomeTraderWrapper(SmartHomeTrader):
-  def __init__(self, name, net_production, port):
+  def __init__(self, name, net_production, ip, port):
     self.net_production = net_production
-    if port is None:
-      self.geth = Geth()
-    else:
-      self.geth = Geth(port=port)
+    self.geth = Geth(ip=ip, port=port)
     logging.info("Connecting to DSO...")
     self.dso = zmq.Context().socket(zmq.REQ)
     self.dso.connect(DSO_ADDRESS)
@@ -120,19 +117,30 @@ def read_data(prosumer_id):
     logging.info("Read {} values.".format(len(data)))
     return data
 
+def read_data2(prosumer_id):
+  logging.info("Reading net production values...")
+  with open(DATA_PATH + "day_power_profile2.csv", "rt") as fin:
+    line = next(fin)
+    name = line.split(',')[prosumer_id]
+    data = [int(10 * float(line.split(',')[prosumer_id])) for line in fin]
+    logging.info("Read {} values.".format(len(data)))
+    return (name, data)
+
 if __name__ == "__main__":
   logging.basicConfig(format='%(asctime)s / %(levelname)s: %(message)s', level=logging.INFO)
+  prosumer_id = 1
+  ip = None
+  port = None
   if len(sys.argv) > 1:
     prosumer_id = int(sys.argv[1])
     if prosumer_id < 1: 
-      print("Prosumer ID must be greater than zero!")
-  else:
-    prosumer_id = 1
+      raise Exception("Prosumer ID must be greater than zero!")
   if len(sys.argv) > 2:
-    port = sys.argv[2]
-  else:
-    port = None
-  trader = SmartHomeTraderWrapper("prosumer_" + str(prosumer_id), read_data(prosumer_id), port) 
+    ip = sys.argv[2]
+  if len(sys.argv) > 3:
+    port = sys.argv[3]
+  (name, data) = read_data2(prosumer_id)
+  trader = SmartHomeTraderWrapper(name, data, ip, port) 
   trader.run()
 
     

### 2017-08-17 code/PhaseI/components/launch_prosumers.sh

@@ -1,0 +1,10 @@
+python3 SmartHomeTraderWrapper.py 1 10.4.209.27 9000 &
+python3 SmartHomeTraderWrapper.py 2 10.4.209.27 9001 &
+python3 SmartHomeTraderWrapper.py 3 10.4.209.27 9002 &
+python3 SmartHomeTraderWrapper.py 4 10.4.209.27 9003 &
+python3 SmartHomeTraderWrapper.py 5 10.4.209.27 9004 &
+python3 SmartHomeTraderWrapper.py 6 10.4.209.26 9005 &
+python3 SmartHomeTraderWrapper.py 7 10.4.209.26 9006 &
+python3 SmartHomeTraderWrapper.py 8 10.4.209.26 9007 &
+python3 SmartHomeTraderWrapper.py 9 10.4.209.26 9008 &
+

### 2017-08-17 code/PhaseI/components/DSO.py
no message

@@ -17,27 +17,30 @@ class DSO:
     if address in self.addresses and self.addresses[address] != prosumer:
       return "Address already taken!"
     self.addresses[address] = prosumer
-    # check if withdrawal would violate safety constraints
-    for t in range(asset.start, asset.end + 1):
-      if asset.power > 0:
-        if (prosumer, t) in self.prod_withdrawn and self.prod_withdrawn[(prosumer, t)] + asset.power > PRODUCTION_LIMIT:
-          return "Withdrawal would violate safety constraints!"    
-      elif (prosumer, t) in self.cons_withdrawn and self.cons_withdrawn[(prosumer, t)] - asset.power > CONSUMPTION_LIMIT:
-        return "Withdrawal would violate safety constraints!"
-    # update amount of assets withdrawn
-    for t in range (asset.start, asset.end + 1):
-      if asset.power > 0:
-        if (prosumer, t) not in self.prod_withdrawn:
-          self.prod_withdrawn[(prosumer, t)] = 0
-        self.prod_withdrawn[(prosumer, t)] = self.prod_withdrawn[(prosumer, t)] + asset.power
-      else:
-        if (prosumer, t) not in self.cons_withdrawn:
-          self.cons_withdrawn[(prosumer, t)] = 0
-        self.cons_withdrawn[(prosumer, t)] = self.cons_withdrawn[(prosumer, t)] - asset.power
-    # create and transfer assets to address      
-    self.addFinancialBalance(address, financial)
-    self.addEnergyAsset(address, asset.power, asset.start, asset.end)
-    self.sendEther(address)
+    if asset is not None:
+      # check if withdrawal would violate safety constraints
+      for t in range(asset.start, asset.end + 1):
+        if asset.power > 0:
+          if (prosumer, t) in self.prod_withdrawn and self.prod_withdrawn[(prosumer, t)] + asset.power > PRODUCTION_LIMIT:
+            return "Withdrawal would violate safety constraints!"    
+        elif (prosumer, t) in self.cons_withdrawn and self.cons_withdrawn[(prosumer, t)] - asset.power > CONSUMPTION_LIMIT:
+          return "Withdrawal would violate safety constraints!"
+      # update amount of assets withdrawn
+      for t in range (asset.start, asset.end + 1):
+        if asset.power > 0:
+          if (prosumer, t) not in self.prod_withdrawn:
+            self.prod_withdrawn[(prosumer, t)] = 0
[…]

### 2017-08-19 papers/middleware-2017/Middleware2017.tex
update

% Middleware 2017 Industry Track

\documentclass[sigplan]{acmart}

\usepackage{booktabs} % For formal tables

\usepackage{tikz}
\usetikzlibrary{shadows}
\usepackage{pgfplots}
\pgfplotsset{compat=1.10}

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{colortbl}
\definecolor{Gray}{gray}{0.90}

\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}

% Copyright
%\setcopyright{none}
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
% \setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
% \acmDOI{10.475/123_4}

% ISBN
% \acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[Middleware'17]{ACM/IFIP/USENIX Middleware conference}
              {December 2017}{Las Vegas, Nevada USA} 
\acmYear{2017}
\copyrightyear{2017}

\usepackage[textsize=tiny, textwidth=1.3cm]{todonotes}
\newcommand{\TODO}[1]{\todo[inline]{#1}}
\newcommand{\Abhishek}[1]{\todo[color=yellow!50, linecolor=black!50]{\textbf{Abhishek}: #1}}
\newcommand{\Karla}[1]{\todo[color=green!50, linecolor=black!50]{\textbf{Karla}: #1}}
% \acmPrice{15.00}

% \acmBadgeL[http://ctuning.org/ae/ppopp2016.html]{ae-logo}
% \acmBadgeR[http://ctuning.org/ae/ppopp2016.html]{ae-logo}

\begin{document}
%\title{Middleware Perspectives on IoT-Based Transactive Energy Systems using Distributed Ledgers
%}
\title{Privacy-Preserving Platform for Transactive Energy Systems}

\author{Karla Kvaternik}
\affiliation{\institution{Siemens Corporate Technology}}
\email{karla.kvaternik@siemens.com}

\author{Monika Sturm}
\affiliation{\institution{Siemens Corporate Technology}}
\email{monika.sturm@siemens.com}

\author{Martin Lehofer}
\affiliation{\institution{Siemens Corporate Technology}}
\email{martin.lehofer@siemens.com}

\author{Aron Laszka}
\affiliation{\institution{Vanderbilt University}}
\email{aron.laszka@vanderbilt.edu}

\author{Michael Walker}
\affiliation{\institution{Vanderbilt University}}
\email{michael.a.walker.1@vanderbilt.edu}

\author{Abhishek Dubey}
\affiliation{\institution{Vanderbilt University}}
\email{abhishek.dubey@vanderbilt.edu}

% \author{Gabor Karsai}
% \affiliation{\institution{Vanderbilt University}}
% \email{gabor.karsai@vanderbilt.edu}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{K. Kvaternik et al.}

\begin{abstract}
Transactive energy systems (TES) are emerging as a transformative solution for the problems faced by distribution system operators due to an increase in the use of distributed energy resources and a rapid acceleration in renewable energy generation. These, on one hand, pose a decentralized power system controls problem, requiring strategic microgrid control to maintain stability for the community and for the utility. On the other hand, they require robust financial markets operating on distributed software platforms that preserve privacy. In this paper, we describe the implementation of a novel blockchain-based transactive energy system. We outline the key requirements and motivation of this platform as well as outline the lessons learned and provide a description of key architectural components of this system.
\end{abstract}

\keywords{Transactive energy platforms, blockchain, privacy, security, safety, smart contracts}

\maketitle

\section{Introduction}
%\Abhishek{We need to reduce the introduction to one page + 1 paragraph}
%\Karla{Okay, will do. We can edit the intro once more of the paper gets written - i.e. we'll gear it more to the actual content}
%It is widely accepted that the electricity industry is undergoing an inevitable paradigm shift away from centralized, monolithic business models characterized by bulk generation and one-way delivery, toward a decentralized model in which end users play a more active role in both production and consumption \cite{NIST_TE}.

Transactive energy systems (TES) have emerged as an anticipated outcome of the shift in electricity industry, away from centralized, monolithic business models characterized by bulk generation and one-way delivery, toward a decentralized model in which end users play a more active role in both production and consumption \cite{NIST_TE}. %There are a number of well-documented factors contributing to this shift, including the increasing deterioration and fragility of the current grid, the regulatory and public mandate for environmental awareness, and general social trends toward the democratization of services as exemplified by the "sharing economy" \cite{TheGrid}.

The GridWise Architecture Council defines TES as ``a system of economic and control mechanisms that allows the dynamic balance of supply and demand across the entire electrical infrastructure using value as a key operational parameter'' \cite{Gridwise}. The vision is to realize a user-centric system that allows residential consumers and prosumers (consumers that also produce energy) to trade energy futures directly in a local, open, peer-to-peer (P2P) market at the distribution level.

A key component of any TES is a transaction management platform (TMP) that handles all market clearing functions in a way that balances supply and demand in the local market. We consider the problem of designing and implementing a TMP that provides the technical ingredients essential to the realization of a TES. The proposed TMP will implement market mechanisms as smart contracts on a blockchain system \cite{MasteringBlockchain}. We focus on the design of middleware that enables secure, reliable and timely communication between various TMP modules, sensors and the blockchain system. We highlight the architectural and protocol specifications of our middleware that ensure \emph{privacy} and \emph{security} for participants in the TES, as well as \emph{safety} for the TES.

\subsection{Problem Setting}

We consider settings involving grid-connected microgrids, or multi-feeder distribution systems comprised primarily of residential loads. The main actors are the consumers, prosumers, and a distribution system operator (DSO). The physical elements of our system include all of the basic components typically found in a microgrid, as described, for example, in Section 3 of \cite{LBNLReport}. The microgrid network contains a number of prosumer-operated distributed energy resources (DERs) such as rooftop solar, batteries or flexible loads capable of demand/response.
%These DERs are assumed to be equipped with standard inverters and primary controllers that regulate their voltage and frequency outputs.

We assume that the microgrid is equipped with an advanced metering infrastructure consisting of TE-enabled smart meters. In addition to the standard functionalities of smart meters i.e. the ability to measure line voltages, power consumption and production, and communicate these to the distribution system operator (DSO), TE-enabled smart meters are capable of communicating with other smart meters, have substantial on-board computational resources, and are capable of accessing the Internet and cloud computing services as needed.

The assumed capabilities of these TE-enabled meters allow them to form a blockchain (BC) system executing a market mechanism as a smart contract \cite{Szabo97}. Examples of BC systems capable of executing smart contracts include Ethereum \cite{Buterin2013} and Hyperledger Fabric \cite{HyperledgerFabric16}.
%In essence, a blockchain is a decentralized (i.e. P2P) database whose state is replicated at each node participating in the BC system. The nodes (i.e. smart meters) execute an interaction protocol that includes elements such as a consensus mechanism, a transaction validation incentivisation mechanism and a cryptographic encryption and authentication subsystem \cite{MasteringBlockchain}.

There are several examples of communities where this problem setting applies, and the equipment described is already deployed. These include the well-known Brookly Microgrid Project \cite{BrooklynMicrogrid} and the Sterling Ranch learning community currently under development \cite{SterlingRanch}.

\subsection{Blockchain in TES}
\Karla{We can shorten the first paragraph significantly if needed}
There are a number of appealing properties of BC systems that motivate their use in a TMP. Firstly, BC technology enables the digital representation of energy and financial assets and their secure transfer from one set of parties to another. By design, the security of this value transfer is guaranteed by the interaction protocol itself, and obviates the need for trusted transaction intermediaries. Secondly, the execution of smart contracts -- i.e. code that captures the market logic and participant roles -- is automated and guaranteed. A TE-enabled smart meter participating in the blockchain network can make automated trades on behalf of the consumer or prosumer whose assets it represents. The combination of these properties is expected to reduce the complexity and cost of market clearing, settlement and billing, and thus to facilitate the high throughput of microtransactions that is anticipated in local distribution markets. Thirdly, the blockchain constitutes an immutable, complete, and fully auditable record of all transactions that have ever occurred in the BC system. These properties ensure market transparency, as well as the availability of detailed market, load profile and grid utilization data. In combination with cloud and edge computing technologies, this data can enable fine-grained analytics and optimization of grid operations, as well as accurate pricing of marginal losses. Finally, the decentralized maintenance of the blockchain ensures robustness by eliminating singular points of failure.

Several private initiatives have already considered the implementation of blockchain-based TMPs \cite{PowerLedger}, \cite{Lo3Patent}, \cite{TenneT}. However, most of these initiatives do not consider the impact of the electricity market on the controller responsible for the stability of the system, due to the expectation that the bulk grid will maintain system stability. Furthermore, although these solutions present interesting case studies, they provide only a subset of services, which do not affect the overall power flow on the grid in a significant way. For example, they do not address the security, stability and privacy requirements, which we describe in next section.

\subsection{Contributions}
The specific contribution of this paper are (a) proposal of a set of TES requirements extracted from our experience, (b) architectural and protocol specification and implementation of a new blockchain-based middleware called PETra, first introduced in  \cite{Laszka17}.  In particular, the high volumes of microtransactions in the envisioned TES pose challenges related to real-time communication of sensor data, request-reply messaging between TMP modules, and other signaling that occurs outside of the blockchain. We will refer to these as ``out of band communications,'' and show how their secure, timely handling is essential to meeting many of the proposed TES requirements.

The outline of this paper is as follows. Section \ref{sec:requirements} describe the requirements for the transactive energy systems...

%In this work we propose a set of TES requirements and we focus on the design of middleware that allows TEP implementations to meet these requirements in the typical IoT context of TES. Building on the work in \cite{Laszka17}, we detail the implementation of the architectural components of the TEP conceptualized therein.

% TODO:
% -- high volumes of microtransactions pose challenges related to real-time communication and data handling
% -- what would need computational resource allocation? in this application? i,e. in BC, users are self-interested, can we even assign to individual nodes computation of parts of the smart contract? Multicast management modules for sharing of data??

\section{TES Trading Scenario and Requirements}
\label{sec:requirements}

We envision a market that allows local prosumers  to trade with each other as well as to bid for resources located on the transmission system (from the DSO), supporting imperfect matches of the bids and asks, while ensuring complete privacy from each other. Such a system is  above and beyond anything that has been proposed to date, and as a result, the information technology backbone required to allow such trades needs to be developed \cite{7747895,7725894}.
%rigorously address system requirements such as security, stability and privacy.

In this market, a prosumer bids to consume energy in set time intervals for a number of consecutive intervals. The bids could be positive or negative -- a positive bid implies that the prosumer has excess energy to offer to the market, while a negative bid implies that the prosumer wants to consume energy. Initially, the prosumer determines her power requirement based on historical power usage data. These bids are aggregated along the residential feeder and at the microgrid level, if available; that is, all prosumers that are located downstream from a protection device would have their bids aggregated together. Note that this has to be done in a way that preserves privacy, and prevents the submission of unrealistic power profiles. Any local trade settlement can occur in the next few intervals, leaving the aggregated bids to be used by the Distribution System Operator (DSO) as planned-ahead bids. At this time, the DSO bids with the bulk producers of energy that have well-defined convex, cost functions \cite{wood2012power}. Next, an algorithm such as the distributed incremental consensus described in \cite{zhang2012convergence} can be used to determine the optimal dispatch of each generator.  Once the algorithm converges, the DSO can set the price for the next intervals in the market. This setup is advantageous for the distribution system operator as they can plan ahead with a stable predicted net-demand. However, these transactions can  affect the feeder power flow and power quality, and therefore, the transactions must be more closely scrutinized to ensure stable system operation. Based on this description, we consider a number of TES requirements, and describe how our proposed architecture addresses them. \Abhishek{Please add a few sentences about the real-world deployment like sterling ranch and LO3}
%\Abhishek{we can just describe how we are meeting the essential requirements and not describe the general requirements}

\paragraph{Operational Safety}
The platform should include components that ensure the stability and resiliency of the physical system operation. In the context of grid-connected microgrids, system stability refers to real-time balancing -- i.e. the system's ability to dynamically match supply and demand as closely as possible, and a tendency to drive the difference between supply and demand to zero under small perturbations. Resiliency refers to the system's ability to react to contingencies and recover from faults.

\paragraph{Market and Transactional Security}
The TMP should include components that ensure the protection of consumer interests, as well as those of the DSO. Consumer interests include being billed correctly based on energy prices set by the DSO and the measurements made by the smart meters, and being billed fairly by the DSO. The platform shall include provisions for limiting the financial impact of compromised or faulty nodes on both the DSO and the participant. The DSO shall be allowed to exercise access control that may ban malicious or negligent trading activity that can destabilize the microgrid. Negligent trading may include producers who commit to a certain production level and fail to deliver. Conversely, prosumers shall be protected from unjust access control and market manipulation. Transactional security is assured by the TMP's ability to guarantee the execution of contractual obligations.
\Karla{Perhaps there should be a reputation system}

\paragraph{Cyber-Physical Security}
The TMP should have provisions for preventing or detecting negligent or malicious interference with smart meters - i.e. the adversarial or natural attacks against the interface between the physical world and the blockchain; data logged shall be securely communicated to the DSO and requests made by the meter on behalf of the prosumer shall be accurately recorded on the blockchain.

\paragraph{Privacy}
Information such as the amount of energy produced, consumed, bought or sold by any prosumer should be available only to the DSO and the essential market functions of the TMP. All bids and asks, and the matching thereof should remain anonymous. A participant's energy usage patterns and personal information such as financial standing shall not be inferable from the participant's trading activity\footnote{Inference of energy usage patterns can be exploited by inferring the presence or absence of a person in their home, for example.}.

%\Karla{Removed the section on general requirements}

% \section{Industrial Case Study}
% To illustrate the implementation of our platform, we consider a simplified test case involving four smart homes. Each home is assumed to be equipped with a TE-enabled smart meter

% - Describe the problem in context of a real deployment

% - Describe the 4 household use case

% - describe the constraints (nodal-pricing) and pricing fluctuations and their affect on system stability.

\section{Analysis of State of the Art}
%\Abhishek{This section has to describe why state of the art mechanisms are not enough - I can write this.}
The TMP system requires peer-to-peer messaging, enabling the stakeholder to receive all the required `bid' messages, concerning a specific ask within a given deadline. The stakeholder can choose to inform the bidders about the current reserves or the best bid so that the bids can be reset. Thereafter, the stakeholder can choose to accept a bid and inform the bidding peer about the acceptance.  This last step can either be evaluated in a centralized manner or using a decentralized voting mechanism. Once the bid has been accepted, both parties must record the transaction into a distributed ledger in a way that allows everyone in the community to agree that the transaction took place. Once  consensus has been established, the transaction is deemed successful, and we  say that the market has cleared. In the context of this workflow, we next describe the state of the art across the two dimensions of Application and Communication platforms in smart grid and distributed transaction management platform for smart grid.

\paragraph{Application Platforms for Smart Grid} As power applications move from centralized to distributed processing paradigms, there seems to be two approaches to dividing up the workload. One approach is to consider each remote computing entity (or node) as an \textit{agent} \cite{underfreq-2015} or \textit{actor} \cite{agha1985actors} \cite{LeeNiddodiSrivastavaBakken2016} that communicates via messages with other agents or actors and focuses on specific grid issues, such as state estimation, remedial action schemes, and load shedding. The other approach utilizes each remote computing entity as an open application platform that can host multiple applications managing varied aspects of the local grid  \cite{freedmSysArch2014}. Both approaches utilize messaging between nodes and leverage a common set of services on each node to handle distributed coordination concerns. \cite{LeeNiddodiSrivastavaBakken2016} calls for group membership, leader election, voting, group consensus or agreement on data values, mutual exclusion on access to shared resources, and multicast communication with same order and atomic properties. Both \cite{underfreq-2015} and \cite{LeeNiddodiSrivastavaBakken2016} prototype their approaches using MATLAB toolkits with \cite{LeeNiddodiSrivastavaBakken2016} utilizing the Akka Java toolkit to model actors. \cite{Meng2010} developed simulations using the SimPowerSystem software in the Simulink environment. Our application platform called Resilient Information Architecture Platform for Smart Grid (RIAPS)\footnote{\url{https://riaps.isis.vanderbilt.edu/}} \cite{riaps1} provides actor and component based abstraction and provides support for deploying algorithms on devices across the network\footnote{RIAPS uses zeroMQ \cite{hintjens2010zeromq} and captnproto \cite{varda2015cap} to manage the communication layer} and solve problems collaboratively, by providing micro-second level time synchronization \cite{riaps2}, failure based reconfiguration \cite{dubey2017resilience} and group creation and coordination services (still under active development) in addition to the services described in \cite{LeeNiddodiSrivastavaBakken2016} . It is capable of handling different communication and running implemented algorithms in real-time.

\paragraph{Transaction Management Platforms for Smart grid} 
Transaction management systems require communication as well as trading mechanisms that provide the capability to match the bids and asks. Additionally, they must provide fairness and integrity assurances.  Blockchain based solutions have the potential to enable large-scale energy trading based on distributed consensus systems. However, popular blockchain solutions, such as Bitcoin \cite{NakamotoBitcoin} and Ethereum \cite{buterin2013ethereum} suffer from design limitations that prevent their direct application to validating energy trades. In particular, their transaction-confirmation time is relatively slow and variable, primarily caused due to the proof of work algorithm and dependence on ``on-the block-chain communication''.  For example, Aitzhan and Svetinovic implemented a proof-of-concept for decentralized smart grid energy trading using blockchains, but their system is based on proof-of-work consensus and they do not consider grid control and stability, or scalability~\cite{aitzhan2016security}. Additionally, there is the problem of privacy - all transactions in these systems are  public \cite{kosba2016hawk}.

Most works in this area have focused on the privacy issue from the context of smart meters. McDaniel and McLaughlin discuss the
privacy concerns of energy usage profiling that smart grids could
potentially enable~\cite{mcdaniel2009security}. Efthymiou and Kalogridis describe a method for securely anonymizing frequent electrical metering data sent by a smart
meter~\cite{efthymiou2010smart} by using a third party escrow mechanism. Tan et
al.\ study privacy in a smart metering system from an information
theoretic perspective in the presence of energy harvesting and storage
units~\cite{tan2013increasing}. They show that energy harvesting
provides increased privacy by diversifying the energy source, while a
storage device can be used to increase both energy efficiency and
privacy. However, the transaction data provides more fine-grained information than the smart meter usage patterns \cite{Privacy2017}.

PETra extends these works by (1) leveraging a decentralized computation fabric provided by the smart homes in the community\footnote{we demonstrate the execution on a network of virtual machines in this paper}(2) addressing the privacy
threat posed by trading using a novel trading sequence implementation, (3) showing how partial trades can be fulfilled and (4) using off-blockchain communication primitives provided by the distributed application management platform RIAPS. While the conceptual design of PETra was presented in \cite{Laszka17}, this paper describes the revised protocol, and the trading algorithm in detail and presents the implementation results. 
%This work is closely related to \cite{kosba2016hawk} .... \Abhishek{Todo:Write about Hawk}

\section{Our Solution - PETra}

\input{PETra.tex}

%\Abhishek{We should provide proof of why the system will be safe and privacy-preserving}

%\section{Results and Discussions}

\section{Case Study}
\input{casestudy.tex}

\section{Conclusions and Future Work}

 \bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}

### 2017-08-19 papers/middleware-2017/PETra.tex
update

%The specific components of our system are described in next section.
\label{sec:petra}
%\subsection{Components}

\begin{figure}
\resizebox {0.7\columnwidth} {!} {
\begin{tikzpicture}[x=1.5cm, y=1.5cm, font=\small,
  Component/.style={fill=white, draw, align=center, rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}},
  Connection/.style={<->, >=stealth, shorten <=0.05cm, shorten >=0.05cm}]

\foreach \pos/\name in {0/pros1, 0.8/pros2, 1.6/pros3} {
  \node [Component] (\name) at (\pos - 4, \pos) {Prosumer\\(\texttt{RIAPS, geth})};
}

\node [Component] (dso) at (-1, 2.6) {DSO\\(\texttt{RIAPS, geth})};

\fill [fill=black!15] (90:1.5) -- (200:1.5) -- (340:1.5) -- (90:1.5);

\foreach \pos in {90, 200, 340} {
  \node [Component] at (\pos:1.5) {Ethereum\\miner (\texttt{geth})};
}

\node [Component, dotted] (contract) at (0, 0) {Smart contract\\(\texttt{Solidity})};

\draw [Connection, bend left=65] (pros1) to node [midway, left, shift={(-0.25,0)}] {RIAPS ($\emptyset$MQ)} (dso);
\draw [Connection, bend left=55] (pros2) to (dso);
\draw [Connection, bend left=45] (pros3) to (dso);

\draw [Connection, bend right=15] (dso) to (contract);
\draw [Connection, bend right=0] (pros1) to node [midway, below left] {Ethereum} (contract);
\draw [Connection, bend right=0] (pros2) to (contract);
\draw [Connection, bend right=0] (pros3) to (contract);
\end{tikzpicture}

}
\vspace{-0.1in}
\caption{Components of PETra. The DSO and prosumers are comprised of RIAPS components and \texttt{geth} Ethereum clients. The smart contract is implemented in Solidity, a high-level language for Ethereum, and it is executed by a network of \texttt{geth} miners.}
\vspace{-0.1in}
\label{fig:components}
\end{figure}

\begin{figure*} [ht]

\center

\begin{tikzpicture}[x=5.3cm, y=-0.068cm, font=\small,
RedDashed/.style={red, dashed}]
\def\posDSO{0}
\def\posProsumer{1}
\def\posLedger{2}
\def\posOtherProsumer{3}
\foreach \name/\pos in {DSO/\posDSO, Prosumer/\posProsumer, Smart contract/\posLedger, Other prosumer/\posOtherProsumer} {
  \draw (\pos, 0) -- (\pos, 91);
  \node [draw, fill=white, rounded corners=0.1cm] at (\pos, 0) {\name};
}
\newcounter{seqTime}
\setcounter{seqTime}{0}
\foreach \action/\from/\to/\styl/\delta in {
  {withdrawAssets(anonAddress, assets)/\posProsumer/\posDSO/solid/11}, 
  {failedWithdrawal(anonAddress, msg)/\posDSO/\posProsumer/red/8},
  {addEnergyAsset(anonAddress, asset), addFinancialBalance(anonAddress, amount)/\posDSO/\posLedger/solid/8},
  {AssetAdded(anonAddress, assetID, asset)/\posLedger/\posProsumer/dashed/8},
  {postOffer({assetID, price})/\posProsumer/\posLedger/solid/8},
  {OfferPosted({offerID, assetID, price})/\posLedger/\posOtherProsumer/dashed/4},
  {rescindOffer(offerID)/\posProsumer/\posLedger/red/6},
  {OfferRescinded(offerID)/\posLedger/\posOtherProsumer/RedDashed/4},
  {acceptOffer({offerID, assetID})/\posOtherProsumer/\posLedger/solid/8},
  {OfferAccepted({offerID, assetID})/\posLedger/\posProsumer/dashed/4},
  {depositEnergyAsset(assetID), depositFinancial(amount)/\posProsumer/\posLedger/solid/14},
  {AssetDeposited(anonAddress, asset), FinancialDeposited(anonAddress, amount)/\posLedger/\posDSO/dashed/8}%
} {
  \addtocounter{seqTime}{\delta}
  \draw [->, >=stealth, shorten <=0.05cm, shorten >=0.05cm, \styl] (\from, \value{seqTime}) -- (\to, \value{seqTime}) node [midway, above, align=center, text width={abs(\to - \from) * 4.8cm}, fill=white, fill opacity=0.67, text opacity=1] {\footnotesize\texttt{\action}};
}

\end{tikzpicture}
\vspace{-0.2em}
\caption{Sequence diagram of the trading workflow. Solid lines represent RIAPS messages and Ethereum transactions, while dashed lines represent smart-contract events. Messages and transaction in \textcolor{red}{red} stop the trading workflow.}
\label{fig:workflow}
\vspace{-0.12in}
\end{figure*}

Our system contains the following types of components (see Figure~\ref{fig:components} for an illustration):
\begin{itemize}[leftmargin=*]
\setlength{\itemsep}{0pt}%
    \setlength{\topsep}{0pt} 
    \setlength{\partopsep}{0pt}
    \setlength{\parsep}{0pt}
    \setlength{\parskip}{0pt}%
\item DSO: There is a single component of this type, which represents the Distribution System Operator of the microgrid. 
The primary responsibilities of this component are ensuring the safe operation of the microgrid and regulating the total load of the microgrid.
To this end, the DSO component can limit the energy and financial assets that the prosumers' withdraw for trading, and it can also set a price policy for the microgrid.
Note that this component does not have to be online during trading, so the reliability of the system does not hinge on the reliability of this component.
\item Prosumer: There is a component of this type for every household.
The prosumer components are responsible for trading energy production and consumption for their households.
To do so, a component first estimates the future production and consumption of the household, withdraws energy production or consumption assets from the DSO, and then trades these assets with other prosumers.
To ensure that trading does not compromise the household's privacy, the component uses randomly generated anonymous addresses for trading, which hide the identities of trade partners from each other.
\item Smart contract: 
%There is a single component of this type, which is deployed as an Ethereum contract on the private blockchain. 
This component (deployed as an Ethereum contract on the private blockchain) is responsible for keeping track of the energy and financial assets belonging to each anonymous address, enabling prosumers to post trade offers, and exchanging assets when another prosumer decides to take an offer.
The contract is executed in a decentralized manner by a network of miners, which provides reliability. Additionally, we have several Ethereum clients, one per prosumer and one for the DSO, which interact with the smart contract.
\end{itemize}

\vspace{-0.08in}
\subsection{Assets and Data Structures}

The ability to specify points or intervals in time is crucial.  For
example, control signals specify how the microgrid load should change
at certain points in time, energy trades specify when energy will be
consumed or produced, etc.  To facilitate representing signals and
transactions, we divide time into fixed-length intervals, and specify
points or periods in time using these discrete timesteps.  The length
of the time interval is determined based on the timing assumptions of
the physical power system.  For example, the
time interval may as low as 4 seconds, which corresponds to how frequently
the control signal of the DSO typically changes \cite{federal2011frequency}.

Prosumers trade energy production and consumption with each other, which are represented in PETra by energy assets, which is a structure that comprises the following fields: (a)
 \texttt{int64 power}: non-negative amount of power to be produced or consumed (for example, measured in watts), (b)
 \texttt{uint64 start}: first time interval in which energy is to be produced (or consumed), and (c) \texttt{uint64 end}: last time interval in which energy is to be produced (or consumed).
An asset with positive power value represents energy production, and we call it an \texttt{EnergyProductionAsset}.
An asset with negative power value, on the other hand, represents energy consumption, and we call it an \texttt{EnergyConsumptionAsset}.

Energy trading must also involve the transfer of currencies, which are represented by financial assets.
A \texttt{FinancialAsset} is simply an \texttt{uint64} value, denominated in a fiat currency.

%\vspace{-0.08in}
\subsection{Trading Workflow}

Next, we discuss the trading workflow that is used by prosumers to trade energy production and consumption assets, as well as financial assets with each other.
This workflow involves both off-blockchain messaging (using RIAPS), and on-blockchain transactions and events.
We list these messages, transactions, and events in the order in which they typically appear in the workflow.
Figure~\ref{fig:workflow} shows a graphical illustration of the workflow.
\vspace{-0.1em}
\begin{itemize}[leftmargin=*]
\setlength{\itemsep}{0pt}%
    \setlength{\topsep}{0pt} 
    \setlength{\partopsep}{0pt}
    \setlength{\parsep}{0pt}
    \setlength{\parskip}{0pt}%
\item 
\texttt{withdrawAssets(anonAddress, assets)}: RIAPS message sent by a prosumer to the DSO, asking the DSO to transfer energy and/or financial assets from the prosumer's account at the DSO to an anonymous address to protect her privacy.
Before sending this message, the prosumer should generate a new random anonymous address.
The message specifies the assets that the prosumer wishes to withdraw, and the anonymous address to which the DSO should transfer them, which must be cryptographically signed by the prosumer.
Note that the prosumer may send this message long before actually engaging in trading, so the DSO does not have to be online continuously.
\item \texttt{failedWithdrawal(anonAddress, msg)}: RIAPS message sent by the DSO to the prosumer,
notifying the prosumer that the requested assets cannot be withdrawn due to, e.g., energy safety requirements or insufficient funds.
\item \texttt{addEnergyAsset(anonAddress, asset)},\\\texttt{addFinancialBalance(anonAddress, amount)}:
smart contract transaction called by the DSO, creating energy and financial assets on the blockchain and transferring them to an anonymous address.
Before recording this transaction, the DSO must first verify whether enabling the prosumer to trade these assets would violate any safety requirements.
The transaction specifies the assets and the anonymous address to which they are transferred, and it must be cryptographically signed by the DSO.
\item \texttt{AssetAdded(anonAddress, assetID, asset)},\\\texttt{FinancialAdded(anonAddress, amount)}: events broadcast by the smart contract,
notifying the prosumer that the requested assets have been transferred to the anonymous address.
\item \texttt{postOffer(assetID, price)}: smart contract transaction called by a prosumer, publicly posting an energy bid or ask.
If the prosumer is interested in buying energy, then it posts an energy bid, which specifies an energy consumption asset and a price.
If the prosumer is interested in selling, then it posts an energy ask, which specifies an energy production asset and a price.
vIn both cases, the transaction must be cryptographically signed by the private key of the address, and it locks the assets until the offer is accepted or rescinded.
\item \texttt{OfferPosted(offerID, assetID, price)}:
event broadcast by the smart contract, notifying prosumers that an offer was posted.
\item \texttt{rescindOffer(offerID)}:
smart contract transaction called by a prosumer, rescinding an offer.
The transaction must be cryptographically signed by the private key of the poster.
\item \texttt{acceptOffer(offerID, assetID)}:
smart contract transaction called by a prosumer,
accepting a previously posted offer. % and transferring the assets between the prosumers.
If the offer was an energy bid, then the other prosumer has to provide an energy production assets;
if the offer was an energy ask, then the other prosumer has to provide both energy consumption and financial assets.
In both cases, the transaction must be cryptographically signed by the private key of the other prosumer's anonymous address.
If there is an overlap between the time intervals of the offered asset, and the asset provided by the other prosumer, then the intersecting parts of the assets are exchanged and the non-overlapping parts are returned to their original owners.
Similarly, based on the price and exchanged energy assets, a part of the financial asset is transferred to the seller, while the rest is returned to the seller. 
%If the energy assets match each other, and the financial asset matches the price, then the assets are exchanged between the prosumers' anonymous addresses. 
\item \texttt{OfferAccepted(offerID, assetID)}:
event broadcast by the smart contract,
notifying the prosumer that its offer has been accepted, and the assets have been exchanged.
\item \texttt{depositEnergyAsset(assetID)},\\\texttt{depositFinancial(amount)}:
smart contract transactions called by a prosumer,
depositing energy and financial assets to the prosumer's account.
The transaction specifies the assets, and it must be cryptographically signed by the anonymous address that owns them.
Note that to protect privacy, the transaction does not specify the prosumer, so the DSO has to keep track of which prosumer has used which anonymous address.
\item \texttt{AssetDeposited(anonAddress, assetID)},\\\texttt{FinancialDeposited(anonAddress, amount)}:
event broadcast by the smart contract,
notifying the DSO that assets have been deposited from anonymous address, which triggers the transfer of these assets to the prosumer's account at the DSO.
\end{itemize}

\begin{comment}
\begin{figure}
\begin{tikzpicture}[x=0.7cm,y=0.3cm, font=\small]
\draw [->, >=stealth] (-0.2,0) -- (9,0) node [right] {\texttt{start}, \texttt{end}};
\draw [->, >=stealth] (0,-0.4) -- (0,10) node [above] {\texttt{power}};

\draw [fill=red!15] (1, 0) -- (1, 8) -- (6, 8) -- (6, 0);
\draw [fill=blue!30, opacity=0.5] (3, 0) -- (3, 4) -- (8, 4) -- (8, 0);

\node at (3.5, 9) {$A_1$};
\node at (7, 5) {$A_2$};

\node at (2, 4) {$A_1^2$};
\node at (4.5, 6) {$A_1^3$};
\node at (4.5, 2) {$A_1^1$, $A_2^1$};
\node at (7, 2) {$A_2^2$};

\node at (1, -0.5) {$A_1$.\texttt{start}};
\node at (6, -0.5) {$A_1$.\texttt{end}};
\node at (3, -0.5) {$A_2$.\texttt{start}};
\node at (8, -0.5) {$A_2$.\texttt{end}};

\draw [dashed] (3,4) -- (3,8);
\end{tikzpicture}
\caption{Example of exchanging two assets, $A_1$ and $A_2$, that do not match each other perfectly.
First, asset $A_1$ is divided into three smaller assets $A_1^1$, $A_1^2$, and $A_1^3$, while asset $A_2$ is divided into two smaller assets $A_2^1$ and $A_2^2$.}
\label{fig:assetExchange}
\end{figure}
\end{comment}

\subsection{Case Study}
\label{sec:results}
\input{casestudy.tex}

\subsection{Requirements Analysis Discussion}
 \label{sec:discussion} 
We conclude this section with a brief discussion of how PETra satisfies the requirements outlined in Section~\ref{sec:requirements}.

\textbf{Communication Fabric:}
%\Aron{Abhishek, could you please check if the statements about RIAPS are correct?}
%\Abhishek{I made minor edits}
The key requirements for communication are reliability and security. 
In PETra, communication and messaging services are built on (a) RIAPS between the DSO and prosumers, and (b) blockchain transactions and events between the smart contract and other components.
The RIAPS communication layer \cite{eisele2017riaps} presents a reliable messaging service, which  is being currently extended to provide message confidentiality, integrity, and non-repudiation with the help of digital signatures.
Since communication between prosumers and the DSO (i.e. withdrawal) may happen well in advance of actual trading, the DSO and the messaging service do not have to be online continuously.
Combined with the features of RIAPS, this flexibility in uptime leads to a very high level of reliability.

For messaging between the smart contract and other components, the blockchain provides a secure and reliable communication medium.
The  blockchain ledger is an immutable, complete, and fully auditable record, which guarantees integrity and non-repudiation for transactions and events.
Note that---by design---the blockchain does not provide confidentiality, since every transaction and event is public; we will discuss privacy implications and requirements in detail below.
Finally, the blockchain provides a high level of reliability since the ledger is maintained by multiple nodes, which can reach consensus even in the presence of some misbehaving or malicious nodes.

\textbf{Operational Safety, Cyber-Physical Security, and Market Safety:}
For safety and cyber-physical security, it is crucial to ensure that  trading activity cannot compromise the stability of the grid and congestion constraints are respected.
PETra achieves these goals by enabling the DSO to tightly control the amount of energy that a prosumer may (offer to) sell or buy.
A prosumer's energy trading workflow (see Figure~\ref{fig:workflow}) always begins with a withdrawal from the DSO.
By limiting the amount assets that can be withdrawn, the DSO limits the bids and asks that may be posted by a prosumer, thereby enforcing safety requirements (e.g., preventing a prosumer from offering to produce more power than her production capacity).
Fine-grained withdrawal rules based on time, power, etc, can be used to prevent a wide range of negligent or malicious trading.

To protect the prosumers' interests, 
we must enable them to detect and prove if they are incorrectly billed or denied fair participation in the market.
%we must ensure that incorrect billing and unfair participation can be detected and proved. we must ensure that billing is correct correctness of billing and fairness of the trading system.
PETra meets these goals due to the public, fully auditable, and immutable nature of the blockchain ledger.

\textbf{Privacy:}
Privacy requirements dictate that prosumers cannot gain information regarding other prosumers' consumption and production---not even if they are trade partners.
This requirement presents an interesting challenge since every transaction on the blockchain ledger is public.
PETra provides privacy through pseudonymous trading; instead of real identities, prosumers use randomly chosen addresses for trading with each other.
However, pseudonymous addresses could be de-anonymized either by (a) learning which addresses belong to the same prosumer or (b) using the prosumers' communication addresses (e.g., IP addresses used to send transactions).
%There are two threats to privacy: de-anonymization by linking addresses together and by linking addresses to communication addresses (e.g., IP addresses)
Firstly, by employing a large number of anonymous addresses, a prosumer can effectively prevent de-anonymization attacks that would link her addresses together.\footnote{Note that generating new addresses is trivial.} %, prosumers can prevent attacks that could de-anonymize trading by linking addresses together
Secondly, by combining our platform with a communication anonymity solution, such as onion routing, we can prevent de-anonymization based on communication addresses.

%for communication anonymity (e.g., onion routing, such as Tor), we can prevent de-anonymization using network traffic analysis

%\subsection{Privacy Protection}

%By combining our platform with a communication anonymity solution, such as onion routing, we can provide pseudonymous trading service, in which there is no apparent connection between the addresses used for trading and the prosumers owning them.

### 2017-08-21 code/PhaseI/python/fab/blockchains/logic.py
Merge of network-manager from server code

@@ -52,6 +52,7 @@ def readJsonFile(jsonFile, verbose=False):
     return data
 
 def makeGenesisBlockchainConfigFile(jsonFile='./network-config.json',
+                            clientsFile='',
                             verbose=False
                            ):
 
@@ -106,11 +107,16 @@ def makeGenesisBlockchainConfigFile(jsonFile='./network-config.json',
         print ("Please Try again...")
         sys.exit(3)
 
+    clientsData = []
+    if clientsFile <> '':
+        clientsJson = readJsonFile(clientsFile, verbose)
+        clientsData = clientsJson["clients"],
+
     createEthereumGenesisBlockConfigFile( chainId,
                                 difficulty,
                                 gasLimit,
-                                clients = [],
-                                balance = 400000,
+                                clients = clientsData,
+                                balance = balance,
                                 homesteadBlock = 0,
                                 eip155Block = 0,
                                 eip158Block = 0,
@@ -119,29 +125,27 @@ def makeGenesisBlockchainConfigFile(jsonFile='./network-config.json',
                               )
 
 
-#    print "Blockchain created at: " + str(datadir)
 
 
+def createEthereumBlockchain(jsonFile='./genesis-data.json',datadir='./ethereum/custom/data',verbose=False):
 
-def createEthereumBlockchain(jsonFile='genesis.json',datadir='./ethereum/custom/data',verbose=False):
-# create genesis blockchain
 #    fh = StringIO();
-    verbose_results = ''
-    results = ''
-    mkdir_command = "mkdir -p " + datadir
-    results = check_output( ["mkdir",  "-p" , str(datadir) ] )
 
-    verbose_results += results + '\n'
-    gethCommand = "geth  --datadir " + str(datadir) + " init " + str(jsonFile)
-    print gethCommand
-#    call([gethCommand])
-#    results = check_output( [ gethCommand ] )
-    results = check_output([ "geth", " --datadir ", datadir , " init ", jsonFile ])
-    verbose_results += results + '\n'
-    print results
+    mkdir_command = "mkdir -p " + str(datadir)
+    call( ["mkdir",  "-p" , str(datadir) ] )
+
+    if os.path.isfile(jsonFile) <> True:
+        print "Operand provided to be the genesis block config file was not a file."
+        sys.exit(2)
+        return
+
+    results = check_output([ "geth", "--datadir", datadir , "init", jsonFile ])
+
+
     if verbose:
         print "** Verbose Output: **"
-        print verbose_results
+        print results
[…]

### 2017-08-21 code/PhaseI/python/fab/bootnodes/logic.py

@@ -2,8 +2,7 @@
 
 ##############################################################################
 #
-#
-#
+# This file contians the code to interact with bootnodes
 #
 # @Author Michael A. Walker
 # @Date 2017-06-27
@@ -13,28 +12,229 @@
 ##############################################################################
 # imports
 ##############################################################################
+import json
+from subprocess import call, check_output
+from StringIO import StringIO
+from subprocess import check_output, call
+import re
+import os.path
+import sys, os
+import stringcase
+
+##############################################################################
+# Helper Methods
+##############################################################################
+
+def readJsonFile(jsonFile, verbose=False):
+# read in a json file and print it if verbose
+    if os.path.isfile(jsonFile) <> True:
+        print "Operand provided to be the network config file was not a file."
+        sys.exit(2)
+        return
+    with open(str(jsonFile)) as data_file:
+        data = json.load(data_file)
+    # read in the configuration JSON file
+    if verbose:
+        print "\nRead in the following network-config json file:\n"
+        print json.dumps(data, indent=4, sort_keys=False) + "\n"
+    return data
+
+def getJsonValues(jsonFile, verbose=False):
+    """ Read in network-config json file and parse out values to return from it.
+    """
+    data = readJsonFile(jsonFile, verbose)
+    try:
+        ##########################################################################
+        # get the values from the JSON file
+        ##########################################################################
+        # network specific data
+        configurationName = data["configurationName"]
+        configurationVersion = data["configurationVersion"]
+        # genesis block data
+        chainId = data["chainId"]
+        difficulty= data["difficulty"]
+        gasLimit = data["gasLimit"]
+        balance = data["balance"]
+        genesisBlockOutFile = data["genesisBlockOutFile"]
+
+        # bootnodes data
+        bootnodes = data["bootnodes"]
+        bootnodesProtocol = bootnodes["protocol"]
+        bootnodesCount = bootnodes["count"]
+        bootnodesHosts = bootnodes["hosts"]
+        bootnodesStartPort = bootnodes["startPort"]
+        bootnodesHostCount = len(bootnodesHosts)
+
+
+    except KeyError as inst:
+        exc_type, exc_obj, exc_tb = sys.exc_info()
[…]

### 2017-08-21 code/PhaseI/python/fab/clients/logic.py

@@ -19,46 +19,376 @@
 # imports
 ##############################################################################
 
+import json
+from subprocess import call,check_output
+from StringIO import StringIO
+from subprocess import check_output,call
+import re
+import os.path
+import sys, os
+import stringcase
+
+##############################################################################
+#
+##############################################################################
+
+def to_camel_case(name):
+# convert a string to camel_case all lower case.
+    print name
+    s1 = re.sub('(.)(\s)([A-Z][a-z]+)', r'\1_\3', name)
+    print s1
+    s2 = re.sub('([a-z0-9])([A-Z])', r'\1_\2', s1).lower()
+    print s2
+    return s2
+
+
+def readJsonFile(jsonFile, verbose=False):
+# read in a json file and print it if verbose
+    if os.path.isfile(jsonFile) <> True:
+        print "Operand provided to be the network config file was not a file."
+        sys.exit(2)
+        return
+
+    with open(str(jsonFile)) as data_file:
+        data = json.load(data_file)
+
+    # read in the configuration JSON file
+    if verbose:
+        print "\nRead in the following network-config json file:\n"
+        print json.dumps(data, indent=4, sort_keys=False) + "\n"
+
+    return data
+
+
+def getJsonValues(jsonFile, verbose=False,type='prosumer'):
+# create all prosumer clients
+    data = readJsonFile(jsonFile, verbose)
+
+    try:
+
+        ##########################################################################
+        # get the values from the JSON file
+        ##########################################################################
+
+        # network specific data
+        configurationName = data["configurationName"]
+        configurationVersion = data["configurationVersion"]
+
+        # genesis block data
+        chainId = data["chainId"]
+        difficulty= data["difficulty"]
+        gasLimit = data["gasLimit"]
+        balance = data["balance"]
+        genesisBlockOutFile = data["genesisBlockOutFile"]
+
+        # clients data
+        clients = data["clients"]
+        clientStartPort = clients["startPort"]
+
+        # prosumer data
+        prosumers = clients["prosumer"]
+        prosumerProtocol = prosumers["protocol"]
+        prosumerCount = prosumers["count"]
+        prosumerHosts = prosumers["hosts"]
+        prosumerHostCount = len(prosumerHosts)
+
+        # miner data
+        miners = clients["miner"]
[…]

### 2017-08-21 code/PhaseI/python/fab/config/network.py

@@ -5,6 +5,8 @@
 # Configure how to properly setup a network topology for testing blockchain
 #    This reads in custom schema JSON and calls associated 'fab' file.
 #
+# NOTE: This file is not currently used. processing is localized in each file.
+#
 # @Author Michael A. Walker
 # @Date   2017-06-21
 #

### 2017-08-21 code/PhaseI/python/fab/fabfile.py

@@ -1,49 +1,100 @@
-#from fabric.api import run
+########################################################################################
+#
+# Python Fabric 'fabfile' for connecting over SSH to control Ethereum's 'geth' Clients.
+#
+#   -This file contains all the SSH-related content for the 'Network-Manager' app.
+#
+#   -This file assumes you have an appropriate SSH key(s) installed in your [ ~/.ssh/ ]
+#   directory, that you have the appropriate [ ~/.ssh/config ] file configured for each
+#   host, and that each host is added to the [ ~/.ssh/known_hosts ] file.
+#
+#   -This file requires each host to have the following installed:
+#       geth - blockchain cleint for ethereum.
+#       dtach - simple program that emulates the detach feature of screen
+#
+#
+# @Author Michael A. Walker
+# @Date 2017-07-21
+#
+########################################################################################
+
+
+########################################################################################
+#
+# Imports
+#
+########################################################################################
+
 from fabric.api import env
-
-from fabric.operations import run, put
+from fabric.operations import run, put, local
 from fabric.contrib.project import rsync_project
-from StringIO import StringIO
-import warnings
-warnings.simplefilter(action='ignore', category=FutureWarning)
+from fabric.api import settings, hide
 
+from StringIO import StringIO
+from random import *
+import sys
+import warnings
+# ignore that an SSH dep. of Fabric will need Fabric to be upgraded in the future.
+warnings.simplefilter(action='ignore', category=FutureWarning)
 env.use_ssh_config = True
 
+
+class FabricException(Exception):
+    # error handling class for exceptions when processes return error (such as kill -9 <pid>)
+    pass
+
+def runCommand(command):
+    """ Run an arbitrary command on a remote system.
+    """
+    run(command)
+
 def mkdir(remotePath):
-# make a remote directory
+    """ make a remote directory
+    """
     run('mkdir -p ' + remotePath)
 
 def rmdir(remotePath):
-# delete a remote directory
+    """ delete a remote directory
+    """
     run('rm -rf ' + remotePath)
 
-def rmMiners(remotePath="./ethereum/miners/"):
-# delete a remote directory
-    run('rm -rf ' + remotePath)
+def runbg(cmd, processname='', stdout=None ,sockname="dtach"):
[…]

### 2017-08-21 code/PhaseI/python/fab/miners/logic.py

@@ -12,27 +12,469 @@
 # imports
 ##############################################################################
 
+import json
+from subprocess import call,check_output
+from StringIO import StringIO
+from subprocess import check_output,call
+import re
+import os.path
+import sys, os
+import stringcase
+
+import clients
 
 ##############################################################################
-# Prosumer Client Methods
+#
 ##############################################################################
 
-def createMiners(file):
+def to_camel_case(name):
+# convert a string to camel_case all lower case.
+    print name
+    s1 = re.sub('(.)(\s)([A-Z][a-z]+)', r'\1_\3', name)
+    print s1
+    s2 = re.sub('([a-z0-9])([A-Z])', r'\1_\2', s1).lower()
+    print s2
+    return s2
+
+
+def readJsonFile(jsonFile, verbose=False):
+# read in a json file and print it if verbose
+    if os.path.isfile(jsonFile) <> True:
+        print "Operand provided to be the network config file was not a file."
+        sys.exit(2)
+        return
+
+    with open(str(jsonFile)) as data_file:
+        data = json.load(data_file)
+
+    # read in the configuration JSON file
+    if verbose:
+        print "\nRead in the following network-config json file:\n"
+        print json.dumps(data, indent=4, sort_keys=False) + "\n"
+
+    return data
+
+
+def getMinerJsonValues(jsonFile, verbose=False):
 # create all prosumer clients
-    print 'called miners.createMiners'
+    data = readJsonFile(jsonFile, verbose)
+
+    try:
+
+        ##########################################################################
+        # get the values from the JSON file
+        ##########################################################################
+
+        # network specific data
+        configurationName = data["configurationName"]
+        configurationVersion = data["configurationVersion"]
+
+        # genesis block data
+        chainId = data["chainId"]
+        difficulty= data["difficulty"]
+        gasLimit = data["gasLimit"]
+        balance = data["balance"]
+        genesisBlockOutFile = data["genesisBlockOutFile"]
+
+        # clients data
+        clients = data["clients"]
+        clientStartPort = clients["startPort"]
+
+        # prosumer data
+        prosumers = clients["prosumer"]
+        prosumerProtocol = prosumers["protocol"]
+        prosumerCount = prosumers["count"]
+        prosumerHosts = prosumers["hosts"]
[…]

### 2017-08-21 code/PhaseI/python/fab/network-manager.py

@@ -2,9 +2,13 @@
 
 ##############################################################################
 #
-# CLI tool to manage Ethereum Test Network.
+# CLI tool to manage Distributed Ledger Test Networks.
 #
 #   This class handles CLI parsing and distrutes workload to submodules.
+#
+#   Current iteration is focused on Ethereum, but is generalized so that
+#   Adoption of other distributed ledger frameworks, such as Hyperledger
+#   should be easy to adopt/manage.
 #
 #	Manages:
 #		Clients
@@ -20,7 +24,7 @@
 ##############################################################################
 # Notes:
 #	-Auto-complete of commands is a feature when script is 'installed', but
-#		is not available when ran as python script.
+#		is not available when ran as purely CLI script.
 ##############################################################################
 
 ##############################################################################
@@ -63,6 +67,7 @@ def clientsGroup():
 # simple method to 'group' 'Clients' commands together
     pass
 
+
 @clientsGroup.command(name='create',
                  help='create all clients based of config file.')
 @click.option('--file',
@@ -71,23 +76,31 @@ def clientsGroup():
 @click.option('--type',
               default='all',
 			  help='Type of clients to create: [ prosumers, dso, all(default) ]')
-def clientsCreate(file,type='all'):
+@click.option('--out',
+              default='',
+			  help='JSON output file of newly created Accounts, If empty, don\'t save a file.')
+@click.option('--verbose',
+              is_flag=True,
+              default=False,
+              help='Verbose Output.')
+def clientsCreate(file,verbose,type='all',out=''):
 # Create all new clients based off config JSON file.
     # switch on what type
     if str(type) == 'all':
-        clients.logic.createProsumerClients(file)
-        clients.logic.createDsoClients(file)
+        clients.logic.createClients(file,outFile=out,verbose=verbose,type="prosumer")
+        clients.logic.createClients(file,outFile=out,verbose=verbose,type="dso")
         return
     if str(type) == 'prosumers':
-        clients.logic.createProsumerClients(file)
+        clients.logic.createClients(file,outFile=out,verbose=verbose,type="prosumer")
         return
     if str(type) == 'dso':
-        clients.logic.createDsoClients(file)
+        clients.logic.createClients(file,outFile=out,verbose=verbose,type="dso")
         return
     # if option was given and isn't valid, then error & quit.
[…]

### 2017-08-21 code/PhaseI/python/fab/start.sh

@@ -1,0 +1,27 @@
+#!/bin/bash
+
+##############################################################################
+#
+# Simple script to create a new test network based on provided config file.
+#
+# To use -> ./create <network-config-file.json>
+#
+# @Author Michael A. Walker
+# @Date   2017-08-09
+#
+##############################################################################
+
+### How to start a test network
+
+# Start the clients (Dso(s) & Prosumer(s))
+./network-manager.py clients start --file $1
+./network-manager.py miners start --file $1
+
+# Connect the network
+
+# Gets the enode of each client, & adds each client as a peer of each miner
+# This creates a star-graph from each miner to each prosumer/dso.
+./network-manager.py miners connect --file $1
+
+## Network is now running and connected
+

### 2017-08-21 code/PhaseI/python/fab/test/createGenBlockchains.py

@@ -1,0 +1,148 @@
+#!/usr/bin/python
+
+##############################################################################
+#
+# Test script to consolidate/improve Ethereum Genesis Blockchain creation.
+#
+# @Author Michael A. Walker
+# @Date 2017-07-05
+#
+##############################################################################
+
+##############################################################################
+# imports
+##############################################################################
+import json
+
+
+def createEthereumGenesisBlock( chainId,
+                                difficulty = "200000000",
+                                gasLimit = "2100000",
+                                clients = [],
+                                balance = 400000,
+                                homesteadBlock = 0,
+                                eip155Block = 0,
+                                eip158Block = 0,
+                                outFile = "genesis-data.json",
+                                verbose = False
+                              ):
+    data = {
+        "config": {
+            "chainId": int(chainId),
+            "homesteadBlock": int(homesteadBlock),
+            "eip155Block": int(eip155Block),
+            "eip158Block": int(eip158Block)
+        },
+        "difficulty": str(difficulty),
+        "gasLimit": str(gasLimit),
+        "alloc": {
+        }
+    }
+
+    if clients <> []:
+        for x in clients:
+            data['alloc'][str(x)] = {u'balance': str(balance)}
+
+    if verbose:
+        print "\nGenesis Block created:\n"
+        print json.dumps(data, indent=4, sort_keys=False) + "\n"
+
+    with open(str(outFile), 'w') as outfile:
+        json.dump(data, outfile, indent=4, sort_keys=False)
+
+
+
+
+if __name__ == '__main__':
+
+    clients = [ '778f8989b580ddb1626ec1c7cc7d305a0cbd68e4',
+                'fd7d97627f9124f7ef10d29024cb7cf1c8d4d924',
+                '97b75fd7ab5c9c787eab46ed89e7783f938f4160',
+                'dead485dea36a22d65a7bbc84b21cf15f288e4f7',
+                '20c8ff11d0108ddae3ebf92d51d1bf8707ae2f34'
+    ]
+
+    createEthereumGenesisBlock("15", clients=clients, balance=300000, verbose=False)
+
+
+##############################################################################
+#
+# Here is a brief discription of the parameters inside an Ethereum
+#   Genesis Blockchain. Taken from: https://ethereum.stackexchange.com/a/2377
+#
+##############################################################################
+#
+# mixhash - A 256-bit hash which proves, combined with the nonce, that a
+# sufficient amount of computation has been carried out on this block:
[…]

### 2017-08-21 code/PhaseI/python/fab/test/pycurlTest.py

@@ -1,0 +1,291 @@
+#!/usr/bin/python3
+
+##############################################################################
+#
+# Sample program to interact with ethereum RPC "2.0" with python.
+#
+#    Uses pycurl to HTTP POST query and returns json data.
+#
+# @Author   Michael A. Walker
+# @Date     2017-08-06
+#
+##############################################################################
+
+import pprint
+import pycurl
+import json
+import sys
+from io import BytesIO
+import time
+
+
+def rpcCommand(method,params=[],ip='localhost',port='9012',id=1,jsonrpc="2.0",verbose=False,exceptions=False):
+    """ Method to abstract away 'curl' usage to interact with RPC of geth clients. """
+    # the <ip:port> to connect to
+    ipPort = str(ip) + ":" + str(port)
+    # buffer to capture output
+    buffer = BytesIO()
+    # start building curl command to process
+    try:
+        c = pycurl.Curl()
+        c.setopt(pycurl.URL, ipPort)
+        c.setopt(pycurl.HTTPHEADER, ['Accept:application/json'])
+        c.setopt(pycurl.WRITEFUNCTION, buffer.write)
+        data2 = {"jsonrpc":str(jsonrpc),"method": str(method),"params":params,"id":str(id)}
+        data = json.dumps(data2)
+        c.setopt(pycurl.POST, 1)
+        c.setopt(pycurl.POSTFIELDS, data)
+        if verbose:
+            c.setopt(pycurl.VERBOSE, 1)
+        #perform pycurl
+        c.perform()
+
+        # check response code (HTTP codes)
+        if (c.getinfo(pycurl.RESPONSE_CODE) != 200):
+            if exceptions:
+                raise Exception('rpc_communication_error', 'return_code_not_200')
+            return {'error':'rpc_comm_error','desc':'return_code_not_200','error_num':None}
+        #close pycurl object
+        c.close()
+    except pycurl.error as e:
+        c.close()
+        errno, message = e.args
+        if exceptions:
+            raise Exception('rpc_communication_error', 'Error No: ' + errno + ", message: " + message)
+        return {'error':'rpc_comm_error','desc':message,'error_num':errno}
+
+
+    # decode result
+    results = str(buffer.getvalue().decode('iso-8859-1'))
+    if verbose:
+        print (results)
+
+    # convert result to json object for parsing
+    data = json.loads(results)
+    # return appropriate result
+    if 'result' in data.keys():
+        return data["result"]
+    else:
+        if 'error' in data.keys():
+            if exceptions:
[…]

### 2017-08-22 docs/July2017/bootnodes-commands.tex
updated the layout

\subsection{Bootnodes}

Bootnodes are the discovery mechanism in Ethereum. These nodes do not have a copy of the blockchain(s) on the network(s). Instead they provide a central location for peer discovery.

\subsubsection{Create}
The following command allows you to create the bootnodes (Ethereum discovery service mechanism) specified in <network-config.json> on the test network. This command evaluates the number of hosts given, the number of bootnodes specified, and the starting port for all clients. 
\begin{lstlisting}[language=bash]
$ ./manager bootnodes create file=network-config.json
\end{lstlisting}

\subsubsection{Start}
The following command allows you to start all the bootnodes clients on the test network declared in the provided <network-config.json> file.
\begin{lstlisting}[language=bash]
$ ./manager bootnodes start file=network-config.json
\end{lstlisting}

\subsubsection{Stop}
The following command allows you to stop all the bootnodes clients on the test network declared in the provided <network-config.json> file
\begin{lstlisting}[language=bash]
$ ./manager bootnodes stop file=network-config.json
\end{lstlisting}

\subsubsection{Delete}
The following command allows you to delete all the bootnodes clients' data on the test network declared in the provided <network-config.json> file
\begin{lstlisting}[language=bash]
$ ./manager bootnodes delete file=network-config.json
\end{lstlisting}

### 2017-08-22 docs/July2017/clients-commands.tex
updated the layout

\subsection{Clients}

Clients are the nodes in the test network that have the potential to interact with the Blockchain that are NOT miners. Note: Mining is a separate process that we dedicate nodes to, so that IoT devices (Smart Meters, etc.) do not need to run intensive computation calculations.

\subsubsection{Create}
The following command allows you to create the clients specified in <network-config.json> on the test network. This command evaluates the number of hosts given, the number of client types specified, the number of clients per type, and the starting port for all clients.
\begin{lstlisting}[language=bash]
$ ./manager clients create file=network-config.json
\end{lstlisting}

\subsubsection{Distribute}
The following command allows you to distribute the <static-nodes.json> that contains the bootnode(s) connection information to all Clients. Note: This includes all types declared within the 'clients' section of the <network-config.json> file, such as: Prosumer, Miners, etc.
\begin{lstlisting}[language=bash]
$ ./manager clients create file=network-config.json nodes=static-nodes.json
\end{lstlisting}

\subsubsection{Start}
The following command allows you to start all the clients on the test network declared in the provided <network-config.json> file.
\begin{lstlisting}[language=bash]
$ ./manager clients create file=network-config.json
\end{lstlisting}

\subsubsection{Stop}
The following command allows you to stop all the clients on the test network declared in the provided <network-config.json> file.
\begin{lstlisting}[language=bash]
$ ./manager clients create file=network-config.json
\end{lstlisting}

\subsubsection{Delete}
The following command allows you to delete all the clients' data on the test network declared in the provided <network-config.json> file.
\begin{lstlisting}[language=bash]
$ ./manager clients create file=network-config.json
\end{lstlisting}

### 2017-08-22 docs/notes/initial_writeup/paper.tex
updated the layout

--- 2017-05-03 notes/initial_writeup/paper.tex
@@
 
+Wood introduces an architecture, the heterogeneous multi-chain, which fundamentally sets canonicality and validity apart and enables many highly divergent types of consensus systems interoperating in a trustless, fully decentralised ``federation''~\cite{wood_polkadot}.
+
+\url{https://geli.net/residential/}
+\url{https://www.greentechmedia.com/articles/read/geli-raises-7m-to-take-energy-storage-software-to-the-next-level}
+
 \bibliographystyle{ACM-Reference-Format}

### 2017-08-22 docs/papers/IARPA-RFI-17-03/rfi.tex
updated the layout

--- 2017-06-23 papers/IARPA-RFI-17-03/rfi.tex
@@
 \usepackage[breaklinks,hidelinks]{hyperref}
+\usepackage{pdfpages}
 
@@
 \begin{document}
+
+\includepdf[pages=-]{coverpage.pdf}
+
 \maketitle
@@
 of these nodes, so that the overall performance (e.g., amount of data processed over
-time) is significantly improved.
-This is the concept behind `Social Dispersed Computing,' on which our group has been working.
+time) is significantly improved.  This is the concept behind `Social Dispersed Computing,' on which our group has been working. 
+Blockchain based computational platforms may act as a key enabling technology for social dispersed computing, by solving the above coordination problem. 
+To enable the next step in the evolution of decentralized computing, blockchain platforms must be extended with functionality that allows them to perform computations on encrypted variables.
+In this direction, homomorphic encryption can act as an enabling technology.
 In this whitepaper, we describe two use-cases for this new computing paradigm and describe the challenges which must be solved.
@@
 
+\thispagestyle{empty}
+
 \clearpage
+\pagenumbering{arabic} 
 \section{Description}
@@
 
-\subsubsection{Privacy Problem}
+\subsubsection{Challenges}
 
@@
 
-\subsubsection{Privacy Problem}
+\subsubsection{Challenges}
 A solution to this problem requires a social computing and information sharing platform that overcomes the incentive gap between individuals and municipalities.

### 2017-08-22 docs/papers/IoT2017/prelim.tex
updated the layout

--- 2017-06-21 papers/IoT2017/prelim.tex
@@
 
-Figure~\ref{fig:softwareArchitecture} shows a decentralized
-transactive microgrid with PETra.  In this figure, components marked
-red are introduced to provide privacy in a safe and secure manner,
-whereas components marked in blue are typical elements of a
-decentralized transactive microgrid.
 \begin{figure}[h!]
@@
 \end{tikzpicture}
-\caption{Architecture of a Decentralized Transactive Microgrid with PETra.}
+\caption{Architecture of a decentralized transactive microgrid with \mbox{PETra}.}
 \label{fig:softwareArchitecture}
 \end{figure}
+
+Figure~\ref{fig:softwareArchitecture} shows a decentralized
+transactive microgrid with PETra.  
+In this figure, components marked in blue are basic elements of the decentralized transactive microgrid,
+while components marked in red are added (or extended) by PETra.
 

### 2017-08-22 docs/papers/middleware-2017/Middleware2017_KK1.tex
updated the layout

% Middleware 2017 Industry Track

\documentclass[sigplan]{acmart}

\usepackage{booktabs} % For formal tables

\usepackage{tikz}
\usetikzlibrary{shadows}
\usepackage{pgfplots}
\pgfplotsset{compat=1.10}

\usepackage{colortbl}
\definecolor{Gray}{gray}{0.90}

\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[inline]{enumitem}
% Copyright
%\setcopyright{none}
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
% \setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
% \acmDOI{10.475/123_4}

% ISBN
% \acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[Middleware'17]{ACM/IFIP/USENIX Middleware conference}
              {December 2017}{Las Vegas, Nevada USA} 
\acmYear{2017}
\copyrightyear{2017}

\usepackage[textsize=tiny, textwidth=1.5cm]{todonotes}
\newcommand{\TODO}[1]{\todo[inline]{#1}}
\newcommand{\Abhishek}[1]{\todo[color=yellow!50, linecolor=black!50]{\textbf{Abhishek}: #1}}
\newcommand{\Karla}[1]{\todo[color=green!50, linecolor=black!50]{\textbf{Karla}: #1}}
\newcommand{\Aron}[1]{\todo[color=blue!30, linecolor=black!50]{\textbf{Aron}: #1}}
% \acmPrice{15.00}

% \acmBadgeL[http://ctuning.org/ae/ppopp2016.html]{ae-logo}
% \acmBadgeR[http://ctuning.org/ae/ppopp2016.html]{ae-logo}

\begin{document}
\setlength{\marginparwidth}{1.5cm}

%\title{Middleware Perspectives on IoT-Based Transactive Energy Systems using Distributed Ledgers
%}
\title{Privacy-Preserving Platform for Transactive Energy Systems}

\author{Karla Kvaternik}
\affiliation{\institution{Siemens Corporate Technology}}
\email{karla.kvaternik@siemens.com}

\author{Aron Laszka}
\affiliation{\institution{Vanderbilt University}}
\email{aron.laszka@vanderbilt.edu}

\author{Michael Walker}
\affiliation{\institution{Vanderbilt University}}
\email{michael.a.walker.1@vanderbilt.edu}

\author{Douglas Schmidt}
\affiliation{\institution{Vanderbilt University}}
\email{d.schmidt@vanderbilt.edu}

\author{Monika Sturm}
\affiliation{\institution{Siemens Corporate Technology}}
\email{monika.sturm@siemens.com}

\author{Martin Lehofer}
\affiliation{\institution{Siemens Corporate Technology}}
\email{martin.lehofer@siemens.com}

\author{Abhishek Dubey}
\affiliation{\institution{Vanderbilt University}}
\email{abhishek.dubey@vanderbilt.edu}

% \author{Gabor Karsai}
% \affiliation{\institution{Vanderbilt University}}
% \email{gabor.karsai@vanderbilt.edu}

\vspace{-0.1in}

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{K. Kvaternik et al.}

\begin{abstract}
Transactive energy systems (TES) are emerging as a transformative solution for the problems faced by distribution system operators due to an increase in the use of distributed energy resources and a rapid acceleration in renewable energy generation. These, on one hand, pose a decentralized power system controls problem, requiring strategic microgrid control to maintain stability for the community and for the utility. On the other hand, they require robust financial markets operating on distributed software platforms that preserve privacy. In this paper, we describe the implementation of a novel, blockchain-based transactive energy system. We outline the key requirements and motivation of this platform, describe the lessons learned, and provide a description of key architectural components of this system.
\end{abstract}

\keywords{Transactive energy platforms, blockchain, privacy, security, safety, smart contracts}

\maketitle

\vspace{-0.1in}
\section{Introduction}
%\Abhishek{We need to reduce the introduction to one page + 1 paragraph}
%\Karla{Okay, will do. We can edit the intro once more of the paper gets written - i.e. we'll gear it more to the actual content}
%It is widely accepted that the electricity industry is undergoing an inevitable paradigm shift away from centralized, monolithic business models characterized by bulk generation and one-way delivery, toward a decentralized model in which end users play a more active role in both production and consumption \cite{NIST_TE}.

\textbf{Emerging Trends:} Transactive energy systems (TES) have emerged as an anticipated outcome of the shift in electricity industry, away from centralized, monolithic business models characterized by bulk generation and one-way delivery, toward a decentralized model in which end users play a more active role in both production and consumption \cite{NIST_TE} \cite{Gridwise}. %There are a number of well-documented factors contributing to this shift, including the increasing deterioration and fragility of the current grid, the regulatory and public mandate for environmental awareness, and general social trends toward the democratization of services as exemplified by the "sharing economy" \cite{TheGrid}.
%The GridWise Architecture Council defines TES as ``a system of economic and control mechanisms that allows the dynamic balance of supply and demand across the entire electrical infrastructure using value as a key operational parameter'' \cite{Gridwise}. The vision is to realize a user-centric system that allows residential consumers and prosumers (consumers that also produce energy) to trade energy futures directly in a local, open, peer-to-peer (P2P) market at the distribution level. 
%middleware components and messaging services that ensure the secure, reliable and timely communication between various TMP modules, sensors and the blockchain system. We highlight the architectural and protocol specifications of our middleware that ensure \emph{privacy} and \emph{security} for participants in the TES, as well as \emph{safety} for the TES. 
In this paper, we consider a class of TES that operates in grid-connected mode. The main actors are the consumers, which are comprised primarily of residential loads and prosumers who operate distributed energy resources (DERs), such as rooftop, solar batteries or flexible loads capable of demand/response. Additionally, a distribution system operator (DSO) manages the grid connection of the network. Such installations are equipped with an advanced metering infrastructure consisting of TE-enabled smart meters. In addition to the standard functionalities of smart meters: i.e. the ability to measure line voltages, power consumption and production, and communicate these to the distribution system operator (DSO); TE-enabled smart meters are capable of communicating with other smart meters, have substantial on-board computational resources, and are capable of accessing the Internet and cloud computing services as needed. Examples of such installations include the well-known Brooklyn Microgrid Project, \cite{BrooklynMicrogrid} and the Sterling Ranch learning community (currently under development) \cite{SterlingRanch}. A key component of TES is a transaction management platform (TMP), which handles all market clearing functions in a way that balances supply and demand in the local market.

%Given the capabilities of the TE-enabled meters,

%We consider the problem of designing and implementing a TMP that provides the technical ingredients essential to the realization of a TES. For example,

%The TMP described in this paper will enable the implementation of various market mechanisms as smart contracts on a blockchain  (BC) system \cite{MasteringBlockchain}.

%There are several examples of communities where this problem setting applies, and the equipment described is already deployed. These include the well-known Brooklyn Microgrid Project \cite{BrooklynMicrogrid} and the Sterling Ranch learning community currently under development \cite{SterlingRanch}

%\subsection{Problem Setting}

%We consider settings involving grid-connected microgrids, or multi-feeder distribution systems comprised primarily of residential loads. The main actors are the consumers, prosumers, and a distribution system operator (DSO). The physical elements of our system include all of the basic components typically found in a microgrid, as described, for example, in Section 3 of \cite{LBNLReport}. The microgrid network contains a number of prosumer-operated distributed energy resources (DERs) such as rooftop solar, batteries or flexible loads capable of demand/response.

%These DERs are assumed to be equipped with standard inverters and primary controllers that regulate their voltage and frequency outputs.

%We assume that the microgrid is equipped with an advanced metering infrastructure consisting of TE-enabled smart meters. In addition to the standard functionalities of smart meters i.e. the ability to measure line voltages, power consumption and production, and communicate these to the distribution system operator (DSO), TE-enabled smart meters are capable of communicating with other smart meters, have substantial on-board computational resources, and are capable of accessing the Internet and cloud computing services as needed.

%The assumed capabilities of these TE-enabled meters allow them to form a blockchain (BC) system executing a market mechanism as a smart contract \cite{Szabo97}. Examples of BC systems capable of executing smart contracts include Ethereum \cite{Buterin2013} and Hyperledger Fabric \cite{HyperledgerFabric16}.
%In essence, a blockchain is a decentralized (i.e. P2P) database whose state is replicated at each node participating in the BC system. The nodes (i.e. smart meters) execute an interaction protocol that includes elements such as a consensus mechanism, a transaction validation incentivisation mechanism and a cryptographic encryption and authentication subsystem \cite{MasteringBlockchain}.

%There are several examples of communities where this problem setting applies, and the equipment described is already deployed. These include the well-known Brooklyn Microgrid Project \cite{BrooklynMicrogrid} and the Sterling Ranch learning community currently under development \cite{SterlingRanch}.

%\subsection{Blockchain in TES}
%\Karla{We can shorten the first paragraph significantly if needed}
\textbf{Why Blockchains?:} The capabilities of TE-enabled meters allow them to form a blockchain (BC) based TMP executing a market mechanism, using smart contracts \cite{Szabo97}. Examples of BC systems capable of executing smart contracts include Ethereum \cite{Buterin2013} and Hyperledger Fabric \cite{HyperledgerFabric16}.
 %Examples of BC systems capable of executing smart contracts include Ethereum \cite{Buterin2013} and Hyperledger Fabric \cite{HyperledgerFabric16}.
There are a number of appealing properties of BC systems that motivate their use in a TMP. Firstly, BC technology enables the digital representation of energy and financial assets, and their secure transfer from one set of parties to another. By design, the security of this value transfer is guaranteed by the interaction protocol itself and obviates the need for trusted transaction intermediaries. Secondly, the execution of smart contracts (i.e. code that captures the market logic and participant roles) is automated and guaranteed.
%A TE-enabled smart meter participating in the blockchain network can make automated trades on behalf of the consumer or prosumer whose assets it represents. The combination of these properties is expected to reduce the complexity and cost of market clearing, settlement and billing, and thus to facilitate the high throughput of microtransactions that is anticipated in local distribution markets. 
Thirdly, the blockchain constitutes an immutable, complete, and fully auditable record of all transactions that have ever occurred in the BC system. These properties ensure market transparency, as well as the availability of a detailed market load profile, and grid utilization data. Thus, \cite{PowerLedger,TenneT,Lo3Patent} have already considered such implementations.

%In combination with cloud and edge computing technologies, this data can enable fine-grained analytics and optimization of grid operations, as well as accurate pricing of marginal losses. Finally, the decentralized maintenance of the blockchain ensures robustness by eliminating singular points of failure.

\textbf{Open challenges:} Existing initiatives such as \cite{PowerLedger,Lo3Patent,TenneT}
%However, most of these initiatives 
do not consider the impact of the electricity market on the controller responsible for the stability of the system due to the expectation that the bulk grid will maintain system stability. Furthermore, although these solutions present interesting case studies, they provide only a subset of services, which do not affect the overall power flow on the grid in a significant way. For example, they do not address the security, stability, and privacy requirements, which we describe in the next section. The information technology backbone that allows energy trades in an open P2P market to take place anonymously, and securely, has yet to be developed \cite{7747895,7725894}.

\textbf{Contributions $\rightarrow$ Design and Implementation of  \emph{Privacy-preserving
    Energy Transactions} (PETra)}
We focus on the specification of the components of the platform, their interfaces, and the distributed ledger in the system. Additionally, we highlight the architectural and protocol specifications of our platform, which ensure \emph{privacy} and \emph{security} for participants in the TES, as well as \emph{safety} for the TES. 
%\Aron{Do we ever explain the acronym PETra?}
The specific contributions of this paper are (a) proposal of a set of TES requirements extracted from our experience, (b) architectural and protocol specification and implementation of a new blockchain-based middleware called PETra, first introduced in  \cite{Laszka17}, and (c) an empirical demonstration of the PETra functionality using an actual load profile data set from a microgrid test installation in Germany.  In particular, the high volumes of microtransactions in the envisioned TES pose challenges related to real-time communication of sensor data; for example, request-reply messaging between TMP modules, and other signaling that occurs outside of the blockchain. We will refer to these as ``out of band communications.''
%and show how their secure and timely handling is essential to meeting many of the proposed TES requirements.

%TODO
%\Karla{TODO!! finish outline}
The outline of this paper is as follows. Section \ref{sec:requirements} describes the requirements for this class of distributed systems. Section \ref{sec:related} describes the state of the art. We present our solution in section \ref{sec:petra}. It is followed by an evaluation and discussion in Sections \ref{sec:results} and \ref{sec:discussion}.

%In this work we propose a set of TES requirements and we focus on the design of middleware that allows TEP implementations to meet these requirements in the typical IoT context of TES. Building on the work in \cite{Laszka17}, we detail the implementation of the architectural components of the TEP conceptualized therein.

% TODO:
% -- high volumes of microtransactions pose challenges related to real-time communication and data handling
% -- what would need computational resource allocation? in this application? i,e. in BC, users are self-interested, can we even assign to individual nodes computation of parts of the smart contract? Multicast management modules for sharing of data??

\section{Requirement Analysis}\label{sec:requirements}

%We aim to design a TMP that can accommodate a number of different P2P trading scenarios. In this section we describe these scenarios, and a set of system requirements that a TMP would need to meet.

The trading scenarios we consider involve consumers and prosumers that participate in a local P2P energy trading market by posting offers to sell produced energy, or offers to buy and consume energy in each consecutive time interval. An offer consists of quantity of energy being bought or sold, the time interval in which the trade is to be made, and possibly a reservation price - the maximum (or respectively, minimum) price at which the buyer (or respectively, seller) is willing to trade. The DSO bargains on the bulk market and provides all residual supply and demand within the microgrid.

We assume that each participant has a means of predicting her future power production and consumption based on historical data, and does so prior to trading on the market. An example of a home energy management system that provides this means is the Siemens Energy IP Analytics Suite.
%\textcolor{red}{Siemens [PRODUCT! @Martin or Monika]}. 
Moreover, each participant is represented by an automated trading agent that strategically posts offers to the TMP based on these predictions and the participant's personal trading goals.

In the simplest trading scenario, the DSO sets the price $p$ per kWH for the local market; $p$ is the price paid by any buyer and received by any seller, including the DSO.  The DSO can then dynamically adjust the price $p$ to affect the market efficiency, evaluated as the number of local transactions  vs. energy demand being met from a bulk supplier. Another scenario includes a fully dynamic market where all sellers, including the DSO, post offers that include a reservation price. Each consumer then picks a selling offer on a first-come, first-served basis. An extension of this scenario involves double auctions where both selling and buying offers are posted to the TMP, which executes an automated, regulator-approved market clearing algorithm as an immutable smart contract on the TMP's blockchain system. This algorithm selects the clearing price $p$ within each time interval. With respect to these trading scenarios we propose the following requirements.

%. We later show how the elements of our architecture can meet these requirements. \Aron{Last sentence seems to be a repetition of the previous too.} With respect to these trading scenarios, we propose the following TES requirements and discuss elements of our TMP architecture that aim to address them.

%\Karla{There will be a requirement that the TMP should provide means of allowing DSO to dynamically adjust the prices $p$, and also that the market should be efficient (which can be achieved when DSO adjusts $p$ using a good policy).}

%In another scenario all sellers, including the DSO, post offers which include a reservation price. Each buyer then picks a selling offer on a first-come, first-served basis. The market is cleared every $T$ minutes.

%A third scenario involves a double auction; both selling and buying offers are posted to the TMP, which executes an automated, regulator-approved market clearing algorithm as an immutable smart contract on the TMP's blockchain system. This algorithm selects the clearing price $p$ within each time interval.

%attempt 1:
%Participants'  bids and asks aggregated along the residential feeder and at the microgrid level, if available; that is, all prosumers that are located downstream from a protection device would have their bids aggregated together. Note that this has to be done in a way that preserves privacy, and prevents the submission of unrealistic power profiles. Any local trade settlement can occur in the next few intervals, leaving the aggregated bids to be used by the Distribution System Operator (DSO) as planned-ahead bids. At this time, the DSO bids with the bulk producers of energy that have well-defined convex, cost functions \cite{wood2012power}. Next, an algorithm such as the distributed incremental consensus described in \cite{zhang2012convergence} can be used to determine the optimal dispatch of each generator.  Once the algorithm converges, the DSO can set the price for the next intervals in the market. This setup is advantageous for the distribution system operator as they can plan ahead with a stable predicted net-demand. However, these transactions can  affect the feeder power flow and power quality, and therefore, the transactions must be more closely scrutinized to ensure stable system operation.

%attempt 2:
%Each trading scenario has advantages for the DSO as they can plan ahead with a stable predicted net-demand. However, these transactions can  affect the feeder power flow and power quality, and therefore, the transactions must be more closely scrutinized to ensure stable system operation. Moreover, any workflow capturing these trading scenarios requires a TMP that satisfies a set requirements carefully crafted for the protection privacy and other interests of each participant in the TES.

\textbf{Communication Fabric}
The first requirement is the existence of an appropriate communication and messaging architecture. The TMP must collect participants' offers and make them available to buyers, and the market algorithm must communicate clearing prices, buyer-seller matchings, or other market-related signals depending on the trading scenario. In order to meet the operational and safety requirements described next, these messages must be reliably delivered under strict timing constraints, derived from the deadline by which a trade must clear. Moreover, the TMP must be capable of handling high volumes of micro-transactions anticipated in P2P trading scenarios.  Finally, the communication fabric must support confidentiality, integrity, and non-repudiation of transactional data.

%\Karla{Abhishek, should we be more specific about this? How quickly are these needed? If not we can leave as is}

\textbf{Operational Safety and Cyber-Physical Security}
The trading activity permitted by the TMP shall not compromise the stability of the physical system operation. Moreover, congestion constraints along any feeder shall be respected.\footnote{In the context of grid-connected microgrids, system stability refers to real-time balancing -- i.e. the system's ability to dynamically match supply and demand as closely as possible, and a tendency to drive the difference between supply and demand to zero under small perturbations. Resiliency refers to the system's ability to react to contingencies and recover from faults. Congestion on a transmission line occurs when the power flow exceeds the line's maximum rated capacity.} This also requires assurance that malicious or negligent trading activity is discouraged.
%by using active mechanisms such as congestion pricing and reputation scores. \Abhishek{Need to clarify in the implementation that this is done at coarse-level so that anonymity is not affected} \Aron{Since we don't actually have a reputation system in our implementation, we could omit this for the sake of simplicity} 
\footnote{Negligent trading may include producers who commit to a certain production level and fail to deliver. Transactional security means that the execution of contractual obligations among all participants, including the DSO, is guaranteed.} 
Finally, the TMP should have provisions for preventing or detecting negligent or malicious interference with smart meters - i.e. the adversarial or natural attacks against the interface between the physical world and the blockchain; data logged shall be securely communicated to the DSO and requests made by the meter on behalf of the prosumer shall be accurately recorded on the blockchain.

\textbf{Market Security}
The TMP shall include provisions for ensuring the protection of consumer interests, as well as those of the DSO. Consumer interests include being billed correctly and fairly
%. \Aron{Fairness?} 
based on energy prices set by the DSO and the measurements made by the smart meters. Additionally, it is important to ensure all prosumers will be allowed to participate in the market fairly.
%, and being billed fairly by the DSO.

%\textbf{Cyber-Physical Security}
%The TMP should have provisions for preventing or detecting negligent or malicious interference with smart meters - i.e. the adversarial or natural attacks against the interface between the physical world and the blockchain; data logged shall be securely communicated to the DSO and requests made by the meter on behalf of the prosumer shall be accurately recorded on the blockchain.

%\paragraph{Market and Transactional Security}
%The TMP shall include provisions for ensuring the protection of consumer interests, as well as those of the DSO. Consumer interests include being billed correctly %based on energy prices set by the DSO and the measurements made by the smart meters, and being billed fairly by the DSO. The DSO's and consumers' interests include limiting financial impact of malicious or negligent trading activity, and ensuring transactional security.\footnote{Negligent trading may include producers who commit to a certain production level and fail to deliver. Transactional security means that the execution of contractual obligations among all participants, including the DSO, is guaranteed. }  
%\Karla{NOTE: "guaranteed execution" is one of the selling points of smart contracts on blockchain \cite{EthereumBook}}

%\Karla{I removed the following sentence, because I think it is not a requirement - it is a solution that helps meet the security requriement: "The DSO shall be allowed to exercise access control that may ban malicious or negligent trading activity that can destabilize the microgrid. Conversely, prosumers shall be protected from unjust access control and market manipulation." i.e. access control and a reputation system are ways of limiting the financial impact of }

%\paragraph{Cyber-Physical Security}
%The TMP should have provisions for preventing or detecting negligent or malicious interference with smart meters - i.e. the adversarial or natural attacks against the interface between the physical world and the blockchain; data logged shall be securely communicated to the DSO and requests made by the meter on behalf of the prosumer shall be accurately recorded on the blockchain.

\textbf{Privacy}
Information such as the amount of energy produced, consumed, bought, or sold by any prosumer should be available only to the DSO and the essential market functions of the TMP. All bids and asks, and the matching thereof, should remain anonymous. A participant's energy usage patterns and personal information, such as financial standing, shall not be inferable from the participant's trading activity\footnote{Inference of energy usage patterns can be exploited by inferring the presence or absence of a person in their home, for example.}.

%\Karla{Removed the section on general requirements}

% \section{Industrial Case Study}
% To illustrate the implementation of our platform, we consider a simplified test case involving four smart homes. Each home is assumed to be equipped with a TE-enabled smart meter

% - Describe the problem in context of a real deployment

% - Describe the 4 household use case

% - describe the constraints (nodal-pricing) and pricing fluctuations and their affect on system stability.

\section{Analysis of State of the Art}
\label{sec:related}
%\Aron{Please note that this is not how our implementation works.}\Abhishek{I changed it - please check now} \Aron{OK, I think it is sufficiently accurate now}
The TMP system requires peer-to-peer messaging, enabling each stakeholder to receive all the required `bid' messages, concerning a specific ask. %within a given deadline. The stakeholder can choose to inform the bidders about the current reserves or the best bid so that the bids can be reset. T
Thereafter, a consumer can choose to accept a bid and inform the ledger about the acceptance.  
%This last step can either be evaluated in a centralized manner or using a decentralized voting mechanism.
Once the bid is accepted, the transaction is recorded into a distributed ledger in a way that allows everyone in the community to agree that the transaction took place. Once consensus is established, the transaction is deemed successful, and we  say that the market has cleared. In the context of this workflow, we next describe the state of the art across the two dimensions of Application and Communication platforms in smart grid and distributed transaction management platform for smart grid.

\textbf{Application Platforms for Smart Grid} There seem to be two approaches in general for moving power applications
%As power applications move 
from centralized to distributed processing paradigms.
%, there seems to be two approaches to dividing up the workload.
One approach is to consider each remote computing entity (or node) as an \textit{agent} \cite{underfreq-2015} or \textit{actor} \cite{agha1985actors} \cite{LeeNiddodiSrivastavaBakken2016} that communicates via messages with other agents or actors, and focuses on specific grid issues such as state estimation, remedial action schemes, and load shedding. The other approach utilizes each remote computing entity as an open application platform that can host multiple applications managing varied aspects of the local grid  \cite{freedmSysArch2014}. Both approaches utilize messaging between nodes, and leverage a common set of services on each node, to handle distributed coordination concerns. \cite{LeeNiddodiSrivastavaBakken2016} calls for group membership, leader election, voting, group consensus or agreement on data values, mutual exclusion on access to shared resources, and multicast communication with same order and atomic properties. Both \cite{underfreq-2015} and \cite{LeeNiddodiSrivastavaBakken2016} prototype their approaches using MATLAB toolkits, with \cite{LeeNiddodiSrivastavaBakken2016} utilizing the Akka Java toolkit to model actors. \cite{Meng2010} developed simulations using the SimPowerSystem software in the Simulink environment. Our application platform, called Resilient Information Architecture Platform for Smart Grid (RIAPS)
%\footnote{\url{https://riaps.isis.vanderbilt.edu/}} 
\cite{riaps1}, provides actor and component based abstraction, as well as support for deploying algorithms on devices across the network\footnote{RIAPS uses ZeroMQ \cite{hintjens2010zeromq}, and Cap'n Proto \cite{varda2015cap}, to manage the communication layer.} and solves problems collaboratively by providing micro-second level time synchronization \cite{riaps2}, failure based reconfiguration \cite{dubey2017resilience}, and group creation and coordination services (still under active development), in addition to the services described in \cite{LeeNiddodiSrivastavaBakken2016}. It is capable of handling different communication and running implemented algorithms in real-time.

\textbf{Transaction Management Platforms (TMP) for Smart grid} 
TMP require communication, as well as trading mechanisms that provide the capability to match the bids and asks. Additionally, they must provide fairness and integrity assurances.  Blockchain based solutions have the potential to enable large-scale energy trading based on distributed consensus systems. However, popular blockchain solutions, such as Bitcoin \cite{Satoshi} and Ethereum \cite{buterin2013ethereum} suffer from design limitations that prevent their direct application to validating energy trades. In particular, their transaction-confirmation time is relatively slow and variable, primarily due to the proof-of-work algorithm and most of the communication occurring via the ledger.
%\Aron{What do we mean by dependence on ``on-the-blockchain communication?'' Where was the quote taken from?} dependence on ``on-the blockchain communication.'' 
For example, Aitzhan and Svetinovic implemented a proof-of-concept platform for decentralized smart grid energy trading using blockchains, but their system is based on proof-of-work consensus, and they do not consider grid control and stability, or scalability~\cite{aitzhan2016security}. Additionally, there is the problem of privacy - all transactions in these systems are  public \cite{kosba2016hawk}.

Most works in this area have focused on the privacy issue from the context of smart meters. McDaniel and McLaughlin discuss the
privacy concerns of energy usage profiling, which smart grids could
potentially enable~\cite{mcdaniel2009security}. Efthymiou and Kalogridis describe a method for securely anonymizing frequent electrical metering data sent by a smart
meter~\cite{efthymiou2010smart} by using a third party escrow mechanism. Tan et
al.\ study privacy in a smart metering system from an information
theoretic perspective in the presence of energy harvesting and storage
units~\cite{tan2013increasing}. They show that energy harvesting
provides increased privacy by diversifying the energy source, while a
storage device can be used to increase both energy efficiency and
privacy. However, the transaction data provides more fine-grained information than the smart meter usage patterns \cite{Privacy2017}.

PETra extends these works by (1) leveraging a decentralized computation fabric provided by smart homes in the community,
%\footnote{We demonstrate the execution on a network of virtual machines in this paper.} 
(2) addressing the privacy
threat posed by trading using a novel trading sequence implementation, (3) showing how partial trades can be fulfilled, and (4) using off-blockchain communication primitives provided by the distributed application management platform RIAPS. While the conceptual design of PETra was presented in \cite{Laszka17}, this paper describes the revised protocol and the trading algorithm, and presents the implementation results. 
%This work is closely related to \cite{kosba2016hawk} .... \Abhishek{Todo:Write about Hawk}

\section{Our Solution - PETra}

\input{PETra.tex}

%\Abhishek{We should provide proof of why the system will be safe and privacy-preserving}

%\section{Results and Discussions}

\section{Conclusions and Future Work}
A transaction management platform (TMP) is the key component of a transactive energy system. The role of the TMP is to facilitate the deployment of applications that help maintain stability of the microgrid, as well as implement efficient market mechanisms and enable an open P2P energy trading market. In this paper we proposed a blockchain-based TMP called PETra, which extends existing works by (1) leveraging a decentralized computation
fabric provided by the smart homes in the microgrid, (2) addressing the privacy threat posed by trading using a novel trading sequence implementation, (3) showing how partial trades can be fulfilled, and (4) using off-blockchain communication primitives provided by the distributed application management platform RIAPS. 
%\Karla{Need to summarize main findings/lessons learned here in one or two sentences}

During the experiments, we made the following observations:
%\textcolor{red}{Aron: some lessons learned
%\begin{itemize}
Blockchains are not enough by themselves to implement a full-fledged TMP for transactive energy systems. We need off-blockchain communication for (1) performance (transactions may be slow) (2) reliability (transactions may be lost before they are permanently recorded) (3) privacy (we can anonymize assets by mixing on the blockchain, but doing it off-blockchain is much more efficient). Additionally,  existing smart contract languages (e.g., Solidity) have some serious limitations (and peculiarities), which complicate the implementation of some domain logic. For instance, at the time of writing, Solidity did not provide floating-point data types.

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}

### 2017-08-22 docs/papers/middleware-2017/casestudy.tex
updated the layout

\definecolor{blueLine}{RGB}{57,106,177}
\definecolor{blueFill}{RGB}{114,147,203}
\definecolor{redLine}{RGB}{204,37,41}

\begin{figure}[t]
\centering
% \vspace{-0.1in}
%    \makebox[\linewidth]{
       % \includegraphics[width=1.0\linewidth]{loadprofile.png}
%    }

\begin{tikzpicture}
\begin{axis}[
  font=\small,
  width=1.05\columnwidth,
  height=0.61\columnwidth,
  ymin=-1,
  ymax=200,
  xmin=-1,
  xmax=97,
  legend pos=north west,
  xlabel=Time,
  ylabel={[kWh]},
  ytick={0, 50, 100, 150},
  xtick={0, 32, 64, 95},
  xticklabels={0:00, 8:00, 16:00,  23:45},
%  ymajorgrids,
%  xmajorgrids,
]
\addplot[no markers, solid, blueLine, semithick] table[x expr=\coordindex, y=Production, comment chars={\%}] {total_prod_cons.csv};
\addlegendentry{Total production};
\addplot[no markers, solid, redLine, semithick] table[x expr=\coordindex, y=Consumption, comment chars={\%}] {total_prod_cons.csv};
\addlegendentry{Total consumption};
\end{axis}
\end{tikzpicture}
\vspace{-2em}
\caption{Load profile and Generation Profile in KWH per 15 minute interval. The horizontal axis shows time of day.}
\label{fig:profile}
% \vspace{-0.2in}
\end{figure}

We use  data collected by Siemens, from a microgrid in Germany,  to demonstrate a simulated transactive scenario. Figure \ref{fig:profile} shows the total energy produced in this system over the day, and  the total energy consumed. We use a $T=15$ minute time interval for bids and asks. We picked a 3.5 hour time interval (from 2:15pm to 5:45pm) and 2 producers and 7 consumers that overlapped with the peak of production capacity (see Figure \ref{fig:profile}). We ran the network across six virtual machines, each with 2 virtual CPUs, 4 GB RAM and 40 GB hard-disk. The \texttt{geth} clients (one per actor) and miners were equally distributed on this network. The actors (Prosumers and DSO) were written in Python, and they communicated with the \texttt{geth} clients using JSON-RPC API provided by Ethereum. The  actors communicated with each other using RIAPS and polled the blockchain ledger for transactional updates using custom filters, which are supported by the Ethereum API.
%\Aron{We could claim that we picked this time interval because it was the busiest.}}} The system has $2$  producers and 7 consumers from a microgrid installation in Germany.  
%\Abhishek{Mike - please explain the figures. they both look very similar.}

Figure~\ref{fig:offer_histogram} shows the distribution of the time between when an offer was made by a producer, and then the time when the offer was accepted by a consumer and cleared. As shown by Figure~\ref{fig:workflow}, this includes two transactions, \texttt{postOffer} and \texttt{acceptOffer}, which have to be verified and recorded by the miners. To clear these two transactions, at least two blocks need to be mined. The statistics of the clearing-time distribution are as follows: 
average = 11.79 seconds, median = 11 seconds, variance = 46.74, maximum = 38 seconds, minimum = 0 seconds, and 90\% of trades were cleared within 23 seconds or less.

%Figure \ref{} shows the setup of virtual machines on which we play out the simulated transactions capturing the timing restrictions and showing the feasibility of the system, while maintaining the safety constraints and the privacy restrictions.

\begin{figure}[t]
% \vspace{-0.1in}
%    \makebox[\linewidth]{
       % \includegraphics[width=1.0\linewidth]{offer_histogram.png}
%        }
  \begin{tikzpicture}
\begin{axis}[
  font=\small,
  width=1.05\columnwidth,
  height=0.54\columnwidth,
  ymin=0,
  ymax=16,
  xmin=-0.5,
  xmax=38.5,
  xlabel={Time until offer was accepted [seconds]},
  ylabel={Number of offers},
  ymajorgrids,
]
\addplot[ybar, bar width=3pt, no markers, fill=blueFill, draw=blueLine, semithick] table[x=Seconds, y=Count, comment chars={\%}, col sep=comma] {TimePerOfferHistogram.csv};
\end{axis}
\end{tikzpicture}
\vspace{-1em}
\caption{Histogram of time it takes to clear the two transactions related to post offer and accept offer. 90\% of the trades were closed within 23 seconds or less.}
\label{fig:offer_histogram}
% \vspace{-0.2in}
\end{figure}

### 2017-08-22 docs/papers/IoT2017/transactions.tex
updated the layout
no message

--- 2017-06-20 papers/IoT2017/transactions.tex
@@
 
-The previous subsection gave an overview of how PETRa uses
+The previous subsection gave an overview of how PETra uses
 transactions in the trading workflow to transfer various assets.  We
@@
 \end{itemize}
-\item \field{ECA\_in}: list of ECA inputs, each of which is defined by
-\begin{itemize}[leftmargin=0.5em,nosep]
-\item \field{out}: reference to an ECA output of a previous transaction,
-\item \field{sig}: signature of the referenced output's address,
-\end{itemize}
-\item \field{FA\_in}: list of FA inputs, each of which is defined by
-\begin{itemize}[leftmargin=0.5em,nosep]
-\item \field{out}: reference to an FA output of a previous transaction,
-\item \field{sig}: signature of the referenced output's address,
-\end{itemize}
+\item \field{ECA\_in}: list of ECA inputs (i.e., list of (\field{out}, \field{sig}) pairs), %, each of which is defined by
+%\begin{itemize}[leftmargin=0.5em,nosep]
+%\item \field{out}: reference to an ECA output of a previous transaction,
+%\item \field{sig}: signature of the referenced output's address,
+%\end{itemize}
+\item \field{FA\_in}: list of FA inputs (i.e., list of (\field{out}, \field{sig}) pairs), %, each of which is defined by
+%\begin{itemize}[leftmargin=0.5em,nosep]
+%\item \field{out}: reference to an FA output of a previous transaction,
+%\item \field{sig}: signature of the referenced output's address,
+%\end{itemize}
 \item \field{EPA\_out}: list of EPA outputs, each of which is defined by
@@
 \end{itemize}
-\item \field{ECA\_out}: list of ECA outputs, each of which is defined by
-\begin{itemize}[leftmargin=0.5em,nosep]
-\item \field{ECA}: an energy consumption asset,
-\item \field{address}: address to which ECA is transferred,
-\end{itemize}
-\item \field{FA\_out}: list of FA outputs, each of which is defined by
-\begin{itemize}[leftmargin=0.5em,nosep]
-\item \field{FA}: a financial asset,
-\item \field{address}: address to which FA is transferred.
-\end{itemize}
+\item \field{ECA\_out}: list of ECA outputs (i.e., (\field{ECA}, \field{address}) pairs), %, each of which is defined by
+%\begin{itemize}[leftmargin=0.5em,nosep]
+%\item \field{ECA}: an energy consumption asset,
+%\item \field{address}: address to which ECA is transferred,
+%\end{itemize}
+\item \field{FA\_out}: list of FA outputs (i.e., (\field{ECA}, \field{address}) pairs). %, each of which is defined by
+%\begin{itemize}[leftmargin=0.5em,nosep]
+%\item \field{FA}: a financial asset,
+%\item \field{address}: address to which FA is transferred.
+%\end{itemize}
 \end{itemize}
@@
 \begin{align*}
-& \forall t: \sum_{\substack{out \,\in\, \field{EPA\_out}:\\out.\field{EPA}.\field{start} \leq t \leq out.\field{EPA}.\field{end}}} out.\field{EPA}.\field{power} \nonumber \\
-& = \sum_{\substack{in \,\in\, \field{EPA\_in}:\\in.\field{out}.\field{EPA}.\field{start} \leq t \leq in.\field{out}.\field{EPA}.\field{end}}} in.\field{out}.\field{EPA}.\field{power}  .
+ \forall t: ~ & \textstyle \sum_{\substack{out ~ \in ~ \field{EPA\_out}:\\out.\field{EPA}.\field{start} \, \leq \, t \, \leq \, out.\field{EPA}.\field{end}}} out.\field{EPA}.\field{power} \nonumber \\
+ & \textstyle = \sum_{\substack{in ~ \in ~ \field{EPA\_in}:\\in.\field{out}.\field{EPA}.\field{start} \, \leq \, t \, \leq \, in.\field{out}.\field{EPA}.\field{end}}} in.\field{out}.\field{EPA}.\field{power}  .
 \end{align*}

### 2017-08-23 docs/papers/IoT2017/intro.tex
trimmed paper to 8 pages

--- 2017-06-21 papers/IoT2017/intro.tex
@@
 been proposed to support the next distribution system evolution
-\cite{kok2016society,cox2013structured,melton2013gridwise}. Transactive
+\cite{kok2016society,melton2013gridwise}. Transactive % NOTE: removed cox2013structured to save space
 energy is a set of market-based constructs for dynamically balancing

### 2017-08-23 docs/papers/IoT2017/related.tex
updated the layout
trimmed paper to 8 pages

--- 2017-06-21 papers/IoT2017/related.tex
@@
 Since this paper focuses on the theoretical foundations of PETra, any
-of these distributed ledgers provide the required capabilities.
+of these  ledgers provide the required capabilities.
 

### 2017-09-27 docs/papers/Serial2017/analysis.tex
added serial 2017 paper

%!TEX root = paper.tex

\section{Conclusion and Discussion}
\label{sec:discussion}

% This section presents an analysis of PETra and shows that
% it satisfies the security, safety, and privacy requirements formulated
% earlier.

% \subsection{Security}
% Satisfaction of the security requirements follows from:
% \begin{itemize}[noitemsep,topsep=-\parskip]
% \item immutability of transactions in the distributed ledger,
% \item validity of transactions
% \item and tamper-resistance of smart meters.
% \end{itemize}
% Together, these properties ensure that only the right entities may
% create and sign a transaction, that transactions adhere to the rules
% of the trading workflow, and that transactions cannot be tampered
% with. Double-spending is resolved by scanning the blockchain to allow only unique outputs.

% \subsection{Safety}
% We now demonstrate that faulty or malicious prosumers cannot trade
% excessive amounts of energy if normal prosumers follow the rules of
% the trading workflow.  Due to the rules of the trading workflow, the gross amount of energy sold is less than or equal to the amount of EPA
% obtained by a prosumer.
% %
% A prosumer can obtain EPA either by withdrawing from its smart meter
% or by purchasing from another prosumer.  From its smart meter,
% prosumer can withdraw at most $\field{MAXEPA}$.  Although the
% prosumer may also buy EPA from another prosumer, this constitutes
% buying energy, which decreases the net amount of energy sold with the
% same amount.  Hence, the net amount of energy sold by prosumer
% cannot exceed $\field{MAXEPA}$.  By extending the argument, we can
% show that the net amount of energy sold by a group of prosumers~$G$
% cannot exceed $\sum_{i \in G} \field{MAXEPA}_i$.  Similarly, %we can
% %show that
%  the net amount of energy bought by a group of prosumers $G$
% cannot exceed $\sum_{i \in G} \field{MAXECA}_i$.

%Using a similar argument, we can also show that the total amount of energy bids (or asks) posted at
%the same time by prosumer $i$ for each timestep is at most
%$\field{MAXEPA}_i + \field{MAXECA}_i$.  This limit is higher than for
%net energy sold or bought, since prosumer $i$ may purchase
%$\field{MAXECA}_i$ amount of EPA (or $\field{MAXEPA}_i$ amount of ECA)
%from other prosumers, and then post an energy ask (or bid) in the
%amount of $\field{MAXEPA}_i + \field{MAXECA}_i$.

Through the use of garlic routing and ring signatures, complete communication and transaction anonymity is achieved. A garlic routing network such as I2P can ensure that no usage, bid, ask or identifiable data is leaked from the system. By using ring signatures, transactions cannot be traced, but it can still be proven that a bid or an ask has been responded to and that a transaction has taken place. The design we've proposed anonymizes the whole chain of transactions, both on a network communication layer and on a distributed ledger transaction layer.

As for the DSO, it receives the same information from the smart meter
as in a non-transactive smart grid (i.e., amount of energy
produced and consumed). In
particular, since price policies are recorded on the ledger (which the
smart meters may read), each prosumer's smart meter may calculate and
send the prosumer's monthly bill to the DSO, without revealing the
prosumer's energy consumption or production. The DSO still gets aggregate information regarding load on the grid, but cannot identify individual users and their energy prosumption.

### 2017-09-27 docs/papers/Serial2017/communicationanonymity.tex
added serial 2017 paper

%!TEX root = paper.tex
% \subsection{Services}\label{Services}

% We now describe the various services that are provided in PETra.
% Earlier, we discussed the distributed ledger, which permanently
% stores valid transactions.  Below, we introduce the anonymous
% communication service, the mixing service for transaction anonymity,
% the anonymous bid storage, and smart-meter based billing.

\subsection{Communication Anonymity}
\label{comm} 
The anonymous communication layer is the infrastructure upon which all
other anonymity services in PETra are built.  The goal of communication anonymity is to allow smart meters and users to exchange transactions and bids without revealing their IP-addresses or other information which can be used to identify them. In almost all cases, at the very least the Internet Service Provider (ISP) has information about the users' communications and identities. The goal of this section is to maximize the anonymity to such an extent that not even ISPs can identify users. Existing protocols for low-latency communication anonymity include onion routing ~\cite{reed1998anonymous} or the similar garlic routing \cite{Liu2014EmpiricalMA}, STAC \cite{7986314} and the decentralized Matrix protocol.\footnote{Open-federated protocol for instant messaging, Voice-over-IP and IoT communications (\url{https://matrix.org/}).} In this section, we present a brief survey of onion and garlic routing, especially with respect to application in PETra.

% \begin{figure}
%  \centering
%  \includegraphics[width=0.6\columnwidth]{onionrouting.png}
%  \caption{Conceptual visualization of onion routing between smart meters to secure communication anonymity. In the figure, smart meter A is sending a message m, with final destination B, through the onion routers.}\label{fig:onionrouting}
%  \end{figure}

\subsubsection{Onion and Garlic Routing}
Onion routing is based on messages in communication being encapsulated in multiple layers of encryption and sent through a number of nodes in a network, called onion routers. It is anonymous because no single node, except for the sender and the receiver, can know the origin and the recipient of the message. In Figure \ref{fig:garlicrouting}, an example shows how smart meter A encrypts a message $m$, with final destination G, through a network of onion routers. A encrypts the message, for example a confirmation of an energy purchase, a certain number of times, along with addresses of members of the onion network. Each subsequent node, selected by the sender and specified in the different layers of encryption, decrypts one layer using its private key, revealing the next node to which the encrypted message is forwarded. Finally, the second to last node reveals the address of smart meter G and sends the still encrypted message to G, who can decrypt it safely. No single node in the network, except for the sender, knows how many times the packages is re-routed, and no node except for the sender and recipient can know their internal position in the chain of routing. Another technique for communication anonymity is called \textit{garlic routing}. It differs from onion routing in that multiple messages are encrypted together to counter tracing attacks.

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{garlicrouting.png}
\caption{The principle behind onion and garlic routing. The difference being that in onion routing, \textit{m} is a single message, whereas in garlic routing, \textit{m} is multiple messages packaged together.}\label{fig:garlicrouting}
\end{figure}

In practice, the deployment of onion routing (or a variant thereof called garlic routing) in the Invisible Internet Project (I2P) works as follows. Each node in the network operates an I2P router, allowing for anonymous communications. A router is distinct from an endpoint application in that it is not a secret who runs a router. By contrast, an application is the destination for the communications and is anonymous.  This disconnect allows for a higher degree of anonymity. To communicate between routers, unidirectional tunnels are set up. The tunnels use layered encryption, meaning that each router in the tunnel only can decrypt one layer. In order to transmit a message between two routers, the sender needs to know  where to direct the message, i.e. what the address of the entry point of the receiver is.

The I2P protocol differs from regular network communications in that, for communications to take place between routers, each router needs to know a structure called the \textit{RouterInfo}. It contains the 2048-bit ELGamal encryption key, a signing key, a certificate, timestamp, text field, signature of bundle and the contact addresses where a router can be reached. The RouterInfo is given along with something called a \textit{LeaseSet}, containing a group of tunnel entry points for a particular client destination, when the tunnel will expire, the destination itself, encryption key for end-to-end encryption of garlic messages, revocation key and a signature of the LeaseSet data. The LeaseSet identifies an application on the I2P network. The I2P protocol ensures the anonymity of its users because of the disconnect between the identities of the applications communicating over the network, and the identities of the routers. This metadata is stored in a distributed directory called the netDb, based on the Kademlia P2P-protocol, which describes a provably consistent and fault-tolerant distributed hash table. \cite{kademlia} The RouterInfo and LeaseSet data are stored on the netDb under the key derived from the SHA256 of the destination.

\subsubsection{Threat Vectors in Onion and Garlic Routing}
\label{commthreat} 
	Murdoch and Danezis \cite{1425067} show that a low-cost traffic analysis is possible of the Tor-network, theoretically and experimentally. Traffic analyses are based on tracking the forwarding of the size of a data package between computers, for example, if computer A sends a package of exactly 42 bytes to computer J, who then sends a package of exactly 42 bytes to B, it can be easily deduced that A sent a package of unknown content to computer B. This is possible because of the distribution of metadata to all routers in the Tor-network~\cite{Hopper:2010:MAN:1698750.1698753}. In what is called a timing analysis attack, an attacker tries to find a correlation between the timing of messages moving through the network to gain information about user identities and their communications. Analyses have shown that these types of attacks can be very effective over a wide range of network parameters when specific defences are not employed~\cite{Levine2004,4797313}.  To counter timing analysis attacks, the I2P network bundles multiple messages together (principle of garlic routing) and renders it more difficult to analyse~\cite{Liu2014EmpiricalMA}. Schimmer, 2009, showed that the bandwidth opportunistic peer-selection and -profiling algorithm does not prioritize anonymity in favor of performance~\cite{peerProfiling:2009}. Herrmann and Grothoff, 2011, exposed a potential weakness in anonymous HTTP-hosting done over the I2P network \cite{Herrmann2011}. The arguably only practical attack against the I2P network was done against the directory, the netDb, by Egger \textit{et al.} \cite{Egger2013}. An improvement of the protocol, aimed at Egger \textit{et al.}'s attack was suggested by Timpanaro \textit{et al.}, 2015 \cite{Timpanaro2015}.

Another potential weakness of onion routing and garlic routing is that, even though the actual message is encrypted and the destinations are unknown, there is always a trace of the communication at the ISP level. The fact that a connection took place will be logged and is openly visible at the very least to the ISP. This attack can be countered in PETra by each node transacting and participating in the mixing network, regardless of the need for trading at that time. Trading of ``zero''-assets can help obfuscate the non-zero-assets of others. Another liability in onion and garlic routing can be that the legitimacy of the sender can not be immediately verified. This can be achieved by the techniques described in the section Transaction Anonymity.

\subsubsection{Proposed Solution}
Given the survey of the previous paragraphs, performing P2P energy trading in transactive grids over a garlic routing network protocol such as the I2P network provides a high amount of communication anonymity for users. Only part of the energy trading in PETra will be anonymized by garlic routing, namely the internet connections. PETra is no different from other network communications in that aspect. The particularity of the trading being local and thus IP-addresses being close, is a potential weakness that can be countered by creating ``fake'' IP-addresses. To apply garlic routing to transactive microgrids, the smart meters, prosumers, and DSO can act as onion routers, and distribution of available routers is done over netDb. In practice, this service
can be built on the free and open-source I2P software
 with private
Directory Authorities.  In this case, anonymous communication
identifiers in bids and asks correspond to public-keys that identify
I2P applications.
% ritter.vg: "run your own tor network"
% https://ritter.vg/blog-run_your_own_tor_network.html

### 2017-09-27 docs/papers/Serial2017/intro.tex
added serial 2017 paper

%!TEX root = paper.tex
\section{Introduction}

Transactive energy models have been proposed as a set of market based mechanisms for balancing the demand and generation of energy in communities \cite{kok2016society,cox2013structured,melton2013gridwise}.
 In this approach, customers on the same feeder (i.e. sharing a power line link) can operate in an open market, trading and exchanging generated energy locally. Distribution System Operators can be the custodian of this market, while still meeting the net demand \cite{7462854}. Blockchains have  recently emerged as a foundation for enabling the transactional service in the microgrids. For example, the Brooklyn Microgrid
(\url{brooklynmicrogrid.com}) is a peer-to-peer market for locally
generated renewable energy, which was developed by LO3 Energy as a pilot project. Similarly, RWE, and Grid Singularity have developed blockchain based solutions for incentivizing neighbors to sell excess energy to the grid and payments for electric car charging %and (c) enabling pre-paid transactions for electric bills in South Africa, respectively. 
However, those solutions do not address the requirements for off-blockchain communication network and the requirements for privacy.

 %Due to a number of challenges, however, these services have been restricted in the present to some pilot programs like Demand/Response \cite{7462854}.  On one hand, transactive energy is a decentralized power system controls problem \cite{7452738}, requiring strategic microgrid control to maintain the stability of the community and the utility. On the other hand, it is a distributed market problem where erroneous as well as malicious transactions can create a gap between demand and supply, eventually destabilizing the system.  Furthermore, this system inherently induces a distributed  infrastructure comprised of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator, which has to provide the necessary computation fabric to support the interplay between the energy control and the fiscal market challenges.

Specifically, while blockchains provide the necessary ledger services, we still need a  communication network for sending control commands from the DSO to the prosumers as well as initiating the trade matching mechanisms.
%as described by our recent publication \textcolor{red}{\cite{Laszka17}}. 
Additionally, this communication network and the blockchain itself must preserve the privacy of the prosumers. Energy usage patterns (actual or predicted) are sensitive, personally identifiable data. Legal requirements and security considerations make it mandatory to provide a mechanism to hide the identities and transaction patterns of trade partners. Additionally, solutions must also satisfy security and safety requirements, which often conflict with privacy goals. For example, to prevent a prosumer from destabilizing the system through careless or malicious energy trading, a transactive grid must check all of the prosumer's transactions. In a decentralized system, these checks require disseminating information, which could be used to infer the prosumer's future energy consumption.

%This paper first describes mechanisms to implement anonymity in both the communication and transactional dimensions

In \cite{Laszka17}, we introduced {\it Privacy-preserving Energy Transactions
(PETra)}, which is our distributed-ledger based solution that
(1) enables trading energy futures in a secure and verifiable
manner, (2) preserves prosumer privacy, and (3) enables distribution system operators to regulate trading and enforce the safety rules. In this paper, we  extend the communication and transaction anonymity mechanisms. The key contributions of this paper are (a) a survey of the key concepts required for implementing the anonymity across the two dimensions, (b) a discussion on the threats that must be considered when we implement the anonymization mechanisms, and lastly (c) a discussion on implementing the anonymization extensions in PETra. 
%This paper describes privacy-aspects of the communication and transactional components of transactive microgrids. Specifically, we analyze two existing schemes for communication anonymity and two schemes for transaction anonymity. They are analyzed with respect to security and known attacks. The schemes are also judged for appropriateness in regards to their application in transactive microgrids. Based on the analysis, we propose a novel design for achieving communication and transaction anonymity in transactive microgrids.
% REDUNDANT OUTLINE
% The outline of this paper is as follows. We first summarize the transaction workflow described in \cite{Laszka17}. Thereafter, we focus on the key contributions of this paper, a discussion on the privacy challenges for both communication as well as transactions.

% This paper introduces Privacy-preserving Energy Transactions (PETra), which is our distributed-ledger based solution that (1) enables trading energy futures in a secure and verifiable manner, (2) preserves prosumer privacy, and (3) enables DSOs to regulate trading and enforce certain safety rules.

The outline of this paper is as follows. We first present an overview of the PETra workflow described in \cite{Laszka17} in Section \ref{sec:petra}. We then discuss the communication anonymity extensions in Section \ref{comm} and transaction anonymity in Section \ref{trans}. Section \ref{commthreat} discusses the threat vectors for the communication anonymity approach. Section \ref{transthreat} describes the transaction anonymity threats.
Finally, we provide concluding remarks in Section~\ref{sec:discussion}.

### 2017-09-27 docs/papers/Serial2017/paper.tex
added serial 2017 paper

\documentclass[sigplan]{acmart}
\usepackage{booktabs} % For formal tables

%\setcopyright{acmcopyright}
% Load basic packages
\usepackage{balance}       % to better equalize the last page
\usepackage{graphics}      % for EPS, load graphicx instead 
\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
\usepackage{txfonts}
\usepackage{mathptmx}
%\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage{color}
\usepackage{booktabs}
\usepackage{textcomp}

% Some optional stuff you might like/need.
\usepackage{microtype}        % Improved Tracking and Kerning
% \usepackage[all]{hypcap}    % Fixes bug in hyperref caption linking
\usepackage{ccicons}          % Cite your images correctly!
% \usepackage[utf8]{inputenc} % for a UTF8 editor only

% Custom packages

\usepackage{paralist}
\usepackage{enumitem}

\usepackage{tikz}
\usetikzlibrary{shadows,shapes}
\usepackage{pgfplots}
\pgfplotsset{compat=1.10}

\usepackage{xcolor}
\usepackage{colortbl}
\definecolor{Gray}{gray}{0.90}

\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}

% If you want to use todo notes, marginpars etc. during creation of
% your draft document, you have to enable the "chi_draft" option for
% the document class. To do this, change the very first line to:
% "\documentclass[chi_draft]{sigchi}". You can then place todo notes
% by using the "\todo{...}"  command. Make sure to disable the draft
% option again before submitting your final document.
\usepackage[textsize=tiny, textwidth=1.5cm]{todonotes}
\newcommand{\TODO}[1]{\todo[inline]{#1}}
\newcommand{\Abhishek}[1]{\todo[color=yellow!50, linecolor=black!50]{\textbf{Abhishek}: #1}}
\newcommand{\Aron}[1]{\todo[color=green!40, linecolor=black!50]{\textbf{Aron}: #1}}
\newcommand{\AronInline}[1]{\todo[inline,size=\small,color=green!40, linecolor=black!50]{\textbf{Aron}: #1}}
\newcommand{\Doug}[1]{\todo[color=red!40, linecolor=black!50]{\textbf{Doug}: #1}}
\newcommand{\Jonatan}[1]{\todo[color=gray!40, linecolor=black!50]{\textbf{Jon}: #1}}
\newcommand{\JonInline}[1]{\todo[inline,size=\small,color=gray!40, linecolor=black!50]{\textbf{Jon}: #1}}

%\usepackage[normalem]{ulem}
%\newcommand{\change}[2]{\textcolor{red}{\sout{#1}} \textcolor{blue}{#2}}
\newcommand{\change}[2]{#2} % DO NOT DISPLAY CHANGES

\newcommand{\circled}[1]{\tikz[baseline=(char.base)]{\node[shape=circle, draw, inner sep=0.5pt, solid] (char) {#1};}}

\newcommand{\field}[1]{\texttt{#1}}

% llt: Define a global style for URLs, rather that the default one
\makeatletter
% \def\url@leostyle{%
%   \@ifundefined{selectfont}{
%     \def\UrlFont{\sf}
%   }{
%     \def\UrlFont{\small\bf\ttfamily}
%   }}
\makeatother
\urlstyle{leo}

\acmConference[SERIAL '17]{SERIAL 2017}
              {December 2017}{Las Vegas, Nevada USA} 
\acmYear{2017}
\copyrightyear{2017}

% create a shortcut to typeset table headings
% \newcommand\tabhead[1]{\small\textbf{#1}}

% End of preamble. Here it comes the document.
\begin{document}

% TODO: remove before submission, added only for todonotes
\setlength{\marginparwidth}{1.5cm}

%\allowdisplaybreaks

\title[Anonymity in Blockchain-Based Transactive Microgrids]{On the Design of Communication and Transaction Anonymity in Blockchain-Based Transactive Microgrids}

\author{Jonatan Bergquist}
\affiliation{\institution{Datarella GmbH}}
\author{Aron Laszka}
\affiliation{\institution{Vanderbilt University}}
\author{Monika Sturm}
\affiliation{\institution{Siemens Corporate Technology}}
\author{Abhishek Dubey}
\affiliation{\institution{Vanderbilt University}}

\renewcommand{\shortauthors}{J. Bergquist et al.}

%\Aron{We need to add authors (\url{https://serial17.ibr.cs.tu-bs.de/cfp.html}: ``Reviewing is single-blind.'')}

\begin{abstract}
%\textcolor{red}{The abstract needs to be rewritten}
%Transactive microgrids are emerging as the next  advancement for power grid. They provide robust capabilities for integrating distributed generation resources in communities, creat
 Transactive microgrids are emerging as a transformative solution for the problems faced by distribution system operators due to an increase in the use of distributed energy resources and a rapid acceleration in renewable energy generation, such as wind and solar power. Distributed ledgers have recently found widespread interest in this domain due to their ability to provide transactional integrity across decentralized computing nodes. However, the existing state of the art has not focused on the privacy preservation requirement of these energy systems --  the transaction level data can provide much greater insights into a prosumer's behavior compared to smart meter data. %\Aron{We could also mention safety requirements as a challenge to privacy (for stable grid control, we need to disseminate information).}\Jonatan{Resolved} 
 There are specific safety requirements in transactive microgrids to ensure the stability of the grid and to control the load. To fulfil these requirements, the distribution system operator needs transaction information from the grid, which poses a further challenge to the privacy-goals. This problem is made worse by requirement for off-blockchain communication in these networks. In this paper, we extend a recently developed trading workflow called PETra and describe our solution for communication and transactional anonymity.    
 %exacerbated further by consideration that 
 %Blockchains is an emerging technology that has found widespread interest in this domain  These, on one hand, pose a decentralized power system controls problem, requiring strategic microgrid control to maintain stability for the community and for the utility. On the other hand, they require robust financial markets where transactions beneficial for the grid should be incentivized, while ensuring that erroneous transactions cannot destabilize the grid. 
% Successful setup and operation of these microgrids require a distributed transactive and control platform that works together to ensure that transactions of energy (a) are unforgeable in the sense that producers should not be able to create a transaction without actually producing energy, (b) are tamper proof, and (c) preserve the anonymity of the actors.
 % This last point is crucial because  the transaction level data can provide much greater insights into a prosumer's behavior compared to smart meter data. \Aron{This is the first mention of blockchains. If we are targeting SERIAL, then I think that the abstract needs to be more focused on blockchains and distributed ledgers. Maybe include them in the title as well?} In this paper, we first describe the use of blockchains to create a transactional workflow that satisfy the first two requirements. The third requirement are met by

% Power grids are undergoing major changes due to rapid growth in renewable energy resources and improvements in battery technology. Significant challenges to manage the increasing complexity of these systems are the consequence. Emerging solutions arrange local communities into transactive microgrids, based on connected devices networked over a decentralized Internet-of-Things (IoT). Within a transactive microgrid, 'prosumers' (i.e., consumers with energy generation and storage capabilities) can trade energy with each other, thereby smoothing the load on the main grid using local supply. Security and safety issues that arise are protecting prosumers' personal information and secure the system from careless or malicious trading, which could destabilize the entire grid. This paper describes Privacy-preserving Energy Transactions (PETra), which is a secure and safe solution for transactive microgrids that enables consumers to trade energy without sacrificing their privacy. PETra builds on distributed ledgers, such as blockchains, and provides anonymity for communication, bidding, and trading.    
\end{abstract}

% TODO!

\keywords{transactive energy platforms, blockchain, distributed ledger, privacy, anonymity, onion routing, zero-knowledge proofs}
\maketitle

\input{intro.tex}

\input{prelim.tex}

\input{solution.tex}

\input{communicationanonymity.tex}

\input{transactionanonymity.tex}

\input{analysis.tex}

\input{related.tex}

\input{concl.tex}

\section*{Acknowledgment}
This work was funded in part by a grant by Siemens Corporation, CT.

% BALANCE COLUMNS
%\balance{}
%\setlength{\bibsep}{0pt plus 0ex}
%\let\oldthebibliography\thebibliography
%\let\endoldthebibliography\endthebibliography
%\renewenvironment{thebibliography}[1]{
%  \begin{oldthebibliography}{#1}
%    \setlength{\itemsep}{0.1em}
%    \setlength{\parskip}{0em}
%}
%{
%  \end{oldthebibliography}
%}

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{SIGCHI-Reference-Format}
\balance
\bibliography{references}

\end{document}

### 2017-09-27 docs/papers/Serial2017/prelim.tex
added serial 2017 paper

%!TEX root = paper.tex
%\vspace{-0.15in}

%\section{Analysis of State of Art}

\section{Privacy-preserving Energy Transactions}
\label{sec:petra}
%\textcolor{red}{There will be a figure here.}
\begin{figure*}[ht]
\centering
\includegraphics[width=\textwidth]{petra.pdf}
\caption{The sequence of activities in PETra. The red arrows show off-block chain communication and blue arrows show transactions on block-chain. Producers and consumers request the DSO to allocate the energy production and consumption assets to blockchain. The consumers receive asynchronous notification about offers from producers. Thereafter, they can finalize transaction. The energy transfer happens at a later time and is also recorded in the chain. Financial transactions are also done on the blockchain. These financial transactions are later tallied with the energy transactions.}\label{fig:petrasequence}
\end{figure*}

There is a systematic pattern emerging in the domain of Internet of Things which requires transactional capabilities. Examples include transactive ride-share systems \cite{yuan2016towards}, transactive health-care systems \cite{azaria2016medrec}, and transactive energy systems described earlier in this section. As shown in Figure \ref{fig:components}, there are three separate layers of this transaction. The first layer is the distributed ledger, which is responsible for keeping track of all log of all events of interest; in the energy domain these events are trades, energy transfer and financial transactions. In case of health care domain, the events record the time of access of the health care data. The data itself is not stored in the block-chain due to the size and privacy issues. Rather, the data is stored in the second layer, which can be implemented by either a cloud or a decentralized storage service like Storj\footnote{https://storj.io/}. The third layer is the IoT layer, which is responsible for sensing and control. This third layer is typically implemented using messaging middlewares like MQTT, DDS, etc.

\definecolor{CustomBlue}{RGB}{88, 154, 214}
\definecolor{CustomOrange}{RGB}{238, 124, 33}

\begin{figure}
\centering
\resizebox {\columnwidth} {!} {
\centering
\begin{tikzpicture}[x=1.5cm, y=1.8cm, font=\small,
  Component/.style={fill=white, draw, align=center, rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}},
  Connection/.style={<->, >=stealth, shorten <=0.15cm, shorten >=0.15cm, very thick, CustomOrange}]

\foreach \pos/\name in {0/pros1, 0.8/pros2, 1.6/pros3} {
  \node [Component] (\name) at (\pos - 4, \pos) {\texttt{IoT Device, geth}};
}

%\node [Component] (dso) at (-1, 2.6) {\texttt{IoT device, geth}};

\fill [fill=black!10] (90:1.5) -- (200:1.5) -- (340:1.5) -- (90:1.5);

\foreach \pos in {90, 200, 340} {
  \node [Component] at (\pos:1.5) {Ethereum\\miner (\texttt{geth})};
}

\node [Component, dotted] (contract) at (0, 0) {Smart contract\\(\texttt{Blockchain})};

\draw [Connection, bend left=0] (pros1) to (pros2);
\draw [Connection, bend left=0] (pros2) to (pros3);
\draw [Connection, bend left=-60] (pros3) to (pros1);

%\draw [Connection, CustomBlue, bend right=15] (dso) to (contract);
\draw [Connection, CustomBlue, bend right=0] (pros1) to (contract);
\draw [Connection, CustomBlue, bend right=0, , shorten <=0.5cm] (pros2) to (contract);
\draw [Connection, CustomBlue, bend right=0] (pros3) to (contract);

\node [Component, minimum width=10.25cm, minimum height=0.7cm] at (-1.39, -1.6) {Decentralized storage service};
\draw [Connection] (-3.2, -1.35) -- (-3.2, -0.32)  node [midway, right,black] {bulk data};
\draw [Connection, CustomBlue, ->] (0, -1.35) -- (0, -0.27)  node [midway, right, align=left, black, yshift={-0.1cm}] {meta\\[-0.2em]data};
\end{tikzpicture}
}
\vspace{-0.1in}
\caption{Components of IoT Blockchain pattern. Typically the IoT devices communicate with each other over a messaging middleware (red arrows). They also communicate with blockchain and smart contracts  (blue arrows) through clients, for example the Ethereum geth client. The miners are entities responsible for validating the events/transactions. %The distributed storage service is not shown in the figure.
}
\vspace{-0.1in}
\label{fig:components}
\end{figure}

The key aspect of this pattern is the tight integration of distributed  messaging patterns between actors and the blockchain-based communication network used for transferring transactional information. For example, in the transactive energy domain,  PETra, described in \cite{Laszka17}, involves the interactions between distribution system operator, prosumer, and a smart contract. The smart contract is  responsible for keeping track of the energy and financial assets enabling prosumers to post trade offers and exchange assets when another prosumer decides to accept.

The  algorithm of PETra uses quantised energy asset tokens\footnote{There are two kinds of energy tokens: Energy Production Asset and Energy Consumption Asset. Token attributes include power and time interval for which the token is valid.} that can represent the non-negative amount of power to be produced or consumed (for example, measured in watts),  the time interval in which energy is to be produced (or consumed) and the  last time interval in which energy is to be produced (or consumed) (Figure \ref{fig:petrasequence} describes the full sequence of activity). These assets are withdrawn and submitted to anonymized accounts on behalf of prosumers by the distribution system operator, which is also responsible for validating that the specific prosumer has the  energy capacity for feasible trades given the assets. Once the DSO posts the assets into the blockchain, prosumers can trade between themselves using these quantised assets and anonymized addresses, hiding their identity from each other. The DSO is also responsible for releasing and managing the transfer of currencies, which are represented by financial assets, which is  simply an unsigned integer value, denominated in a fiat currency. In this workflow, there are both on- and off-blockchain communications between DSO and prosumer. The off-blockchain communication is required to request the transfer of assets. On-blockchain communication occurs via filters that track the posting of assets. Similarly, prosumers also communicate which each other via blockchain to indicate when an offer has been posted and when a transaction has cleared.

While all of the transactive IoT systems require communication and transactional anonymity there are domain-specific requirements and challenges that must be considered.  These characteristics and requirements guide us in the description of the anonymization architecture that we describe in the rest of this paper. Specifically, these characteristics are as follows: 
 (1) transactions in a microgrid must clear in bounded time and any errors must be detected\footnote{Energy trades that have an impact on real-time control (e.g., selling energy production for the near future) must be permanently recorded on the ledger \emph{in time} since grid control signals cannot be delayed.}, (2) typically, there is a dedicated communication channel available in a microgrid that connects the prosumers and the distribution system operator, (3) the set of participants in the network are fixed and known ahead of time. Thus, a discovery procedure is typically not required, and (4) even though all the transactions are anonymous there is still a need for maintaining associativity of properties like maximum generation capacity\footnote{To prevent destabilization of the grid, a producer should not be allowed to bid more than its maximum generation capacity.}, reputation scores to prosumers as they participate in trades to maximize the likelihood of success, while reducing the likelihood of jeopardizing the stability of the microgrid\footnote{A prosumer with low reputation score might have a history of not fulfilling the energy transfer obligations}. In the next two sections, we describe the mechanisms for implementing communication and transaction anonymity in this workflow.

% This section describes a basic system model of transactive IoT
% microgrids and formulates security, safety, and privacy requirements.
% A microgrid is a collection of prosumers (residential nodes) that are
% arranged within the same distribution feeder and support exchange of
% power between them. A prosumer node includes a smart
% inverter and a smart meter, which control the flow of power into and
% out of the prosumer. A microgrid also contains a set of nodes that are responsible for isolating faults on the feeder.  The
% \emph{Distribution System Operator} (DSO) operates %a set of
% switching nodes to control the connection of the microgrid to the rest
% of the distribution system. The DSO is responsible for regulating the
% net electric power into and out of the microgrid. Starting from this
% model, we next introduce the transactive microgrid model.

% \subsection{Transactive Microgrid System Model}
% \Abhishek{This is the perfect paragraph to define transactive
%   microgrid as a special application of IoT spread over a large
%   area. Perhaps we can find a citation that makes this point.}  We
% describe a basic system model of decentralized transactive IoT
% microgrids.  We discuss the following components: a distributed ledger
% for recording transactions, a bid storage service that facilitates
% finding trade partners, a microgrid controller for regulating the
% microgrid load, and smart meters for measuring the prosumers' energy
% production and consumption.

% \begin{figure}[h!]
% \center
% \begin{tikzpicture}[x=8cm, y=0.7cm, font=\small,
%   nodeStyle/.style={rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}}
% ]
% \draw [nodeStyle, fill=red!10]  (0, 1.65) rectangle    (1, 2.25) node [midway, align=center] {Communication anonymity (e.g., onion routing)};

% \draw [nodeStyle, fill=blue!10] (0, 2.4) rectangle    (1, 3.0) node [midway, align=center] {Distributed ledger (e.g., blockchain)};

% \draw [nodeStyle, fill=red!10]  (0, 3.15) rectangle (0.45, 4.05) node [midway, align=center] {Transaction anonymity\\[-0.2em](mixing service)};
% \draw [nodeStyle, left color=blue!10, right color=red!10] (0.47, 3.15) rectangle (0.72, 4.05) node [midway, align=center] {Bid storage};
% \draw [nodeStyle, left color=blue!10, right color=red!10] (0.74, 3.15) rectangle (1, 4.05) node [midway, align=center] {Active\\[-0.2em]smart meter};

% \draw [nodeStyle, fill=red!10] (0, 4.2) rectangle (0.49, 5.1) node [midway, align=center] {Anonymous trading\\[-0.2em]workflow for prosumers};
% \draw [nodeStyle, fill=blue!10] (0.51, 4.2) rectangle (1, 5.1) node [midway, align=center] {Microgrid controller};
% \end{tikzpicture}
% \caption{Architecture of a decentralized transactive microgrid with \mbox{PETra}.}
% \label{fig:softwareArchitecture}
% \end{figure}

% Figure~\ref{fig:softwareArchitecture} shows a decentralized
% transactive microgrid with PETra.  
% In this figure, components marked in blue are basic elements of the decentralized transactive microgrid,
% while components marked in red are added (or extended) by PETra.

% \subsubsection{Distributed Ledger}
% Distributed ledger technologies, usually summarized under the term "blockchain" provide a distributed, decentrilized and highly fault tolerant database to facilitate secure transactions (messages) between all participants, and immutably store these transactions.

% \subsubsection{Bid Storage Service}
% In large networks of prosumers it might make sense -for the sake of scalability- to offer platform services where bids and calls for trades can be published.

% \subsubsection{Microgrid Controller (Distribution System Operator)}
% The DSO includes a controller that regulates the total load on the microgrid and from the microgrid to the distribution system. The controller first predicts load in the
% microgrid based on (1) bids and asks in the bid storage and (2)
% outstanding energy trades in the ledger.  By combining this
% information with the prediction for the rest of the grid, the
% controller produces a control signal that specifies how much the
% microgrid load should be decreased or increased. Based on this
% signal, the controller then updates the price policy for the microgrid
% to influence energy production and consumption.  We also assume the
% presence of a secondary controller that balances voltage and frequency
% in the microgrid.

% \subsubsection{Smart Meters}
% To measure the prosumers' energy production and consumption, a smart
% meter must be deployed at each prosumer.  As with any blockchain-connected device, it needs to be tamper-resistant, in this case to prevent electricity theft.

% \subsection{Requirements}
% We now discuss the security, safety, and privacy requirements that
% must be satisfied by a transactive energy IoT system.

% \subsubsection{Security}
% Security requirements ensure primarily that prosumers are billed
% correctly, but they also provide necessary prerequisite properties for
% safety.
% More specifically, they require that
% \begin{itemize}[noitemsep,topsep=-\parskip]
% \item prosumers are billed correctly based on the energy prices set by
%   the DSO, their energy trades, and their actual energy production and
%   consumption measured by the smart meters,
% \item prosumers or outside attackers cannot change microgrid
%   regulatory policies that are set by the DSO, 
% \item prosumers cannot back out of trades unilaterally, and they
%   cannot tamper with other prosumers' trading or bidding,
% \item financial and physical impact of compromised or faulty nodes is
%   limited, and nodes can be banned by the DSO. 
% \end{itemize}

% \subsubsection{Safety}
% A large gap between the aggregate production and consumption threatens the stability of not only the microgrid but also the main
% power grid.  Therefore, prosumers should not be able to trade large
% amounts of energy that they are unlikely to deliver.
% Specifically, we require that 
% \begin{itemize}[noitemsep,topsep=-\parskip]
% \item the net amount of energy sold (or bought) by a prosumer is upper
%   bounded (by a limit set by the DSO), where the net amount of
%   energy sold is the difference between the amount of energy sold and
%   bought by the prosumer, and the net amount of energy bought is
%   defined analogously. %,
% \Aron{If we have space, add back the safety requirement on the bid storage (and also add back the relevant parts of the description of the trading workflow and the ``analysis.''}
% %\item the energy bids and asks posted by a prosumer are limited in a similar way.
% \end{itemize}
% In practice, the DSO can set the limits based on the prosumers' production and consumption capacities.

% \subsubsection{Privacy} 
% Privacy requirements ensure that the prosumers' privacy is not
% compromised when they participate in energy trading.  We use
% non-transactive smart metering as a baseline, and we require that
% the transactive system does not leak any additional information
% compared to this baseline.  More specifically, we require that
% \begin{itemize}[noitemsep,topsep=-\parskip]
% \item the corresponding smart meter and DSO shall gain and retain as little information regarding the energy produced, consumed, bought and sold by a prosumer,
% \item only the prosumer may know which bids and asks it has posted,
%   and no one can know who traded energy with whom.
% \end{itemize}

### 2017-09-27 docs/papers/Serial2017/transactionanonymity.tex
added serial 2017 paper

\subsection{Transaction Anonymity}
\label{trans}
Communication anonymity is necessary but not sufficient for
anonymous trading, as the cryptographic objectives of authentication and legitimacy are not fulfilled. We suggest using cryptographic techniques from distributed ledgers, \textit{blockchains} and cryptocurrencies. The most adopted of which is the Bitcoin blockchain and currency. It allows for very simple digital cash spending but has serious privacy and anonymity flaws~\cite{Barber2012,Reid2013,apostolaki2017}. Additionally, Biryukov and Pustogarov, 2015, show that using Bitcoin over the Tor network opens an entirely new attack surface~\cite{biryukov2015}. Solutions to the tracing and identification problems identified by these researchers have been proposed and implemented in alternative cryptocurrency protocols: mixing using ring signatures and zero-knowledge proofs.~\cite{miers2013zerocoin,cryptonote}

\subsubsection{Mixing Through Ring Signatures}
The CryptoNote protocol prevents tracing assets back to their original owners by
mixing together multiple incoming transactions and multiple outgoing
transactions. This service thus hides the connections between the
prosumers and the anonymous addresses. Mixing requires the possibility to create new wallets at will, something that is generally recommended upon any cryptocurrency transfer and it requires the existence of a sufficient number of participants in the network. These protocols enable participants to
mix assets with each other, thereby eliminating the need for a trusted
third party. Monero is an example of a cryptocurrency that provides built-in mixing services by implementing the CryptoNote protocol.~\cite{cryptoeprint:2015:1098} There are however alternative implementations of mixing protocols such as CoinShuffle~\cite{ruffing2014coinshuffle} or
Xim~\cite{bissias2014sybil}.

The CryptoNote protocol achieves two objectives:  
\begin{compactenum}
\item Untraceable transactions - \textit{for each incoming transaction all possible senders are equiprobable}. 
\item Unlinkable transactions - \textit{for any two outgoing transactions it is impossible to prove they were
sent to the same person}~\cite{cryptonote}.
\end{compactenum}

Group signatures were first introduced by Chaum and van Heyst, 1991,~\cite{Chaum1991} and then built upon by Rivest \textit{et al.}, 2001.~\cite{Rivest2001} The basis for anonymity in the CryptoNote protocol, however, is a slightly modified version of the \textit{Traceable ring signature} algorithm by Fukisaki and Suzuki, 2007.~\cite{Fujisaki2007} The algorithm allows a member of a group to send a transaction in such a way that it is impossible for a receiver to know any more about the sender than that it came from a group member without the use of a central authority.

Unlinkability is achieved by \textit{one-time ring signatures}, making use of four algorithms: \textbf{GEN, SIG, VER, LNK}. The general principle of the unconditional unlinkability is that a sender signs a transaction using a public key and a key image generated by \textbf{GEN} and produces a one-time ring signature using \textbf{SIG} and the public key pair and key image. \textbf{SIG} makes use of a non-interactive zero-knowledge proof which the verifier(s) then use to check the signature in \textbf{VER}. If the signature is valid, the verifier checks if the key image has been used in previous transactions, which mean that the same secret key was used to produce multiple signatures. She does that by running the algorithm \textbf{LNK}. Assuming that the mapping of the secret key to the key image is a one-way injection, it is certain that: \textbf{A.} The signer is not identifiable by way of recovering the secret key from the key image. \textbf{B.} The signer cannot create another key image with the same secret key.

Additionally, if the receiver and sender have randomly generated, unique and new addresses, the Diffie-Hellman protocol can be used to generate a new pair of public-private keys. This is how untraceability of public keys is achieved. The sender should generate ephemeral keys for each transfer, enabling only the receiver to recover the corresponding private key. As an illustrative example, in Figure \ref{fig:ringsigs}, a schematic diagram shows households A, B and C signing a transaction since they are part of the same ring. A ring would, in reality, be many more households, not necessarily of the same microgrid. Let's assume that A is the true origin of the transaction. When E receives the transaction, the only thing that E can know with certainty is that one of A, B or C initiated the transaction. To increase the transaction anonymity further, a second, third or n rounds of ring signatures can be algorithmically imposed upon the network. With each round of signing parties, the group of potential origins grows linearly. Notably, the ring signature algorithm by Fujisaki and Suzuki, \cite{Fujisaki2007}, has been published in a peer-reviewed paper. This can be compared favorably to many cryptocurrency protocols which are simply published as white papers without any formal review-process. \cite{cryptonote}
In practice, a transaction using the mixing service should be performed in the following way to ensure anonymity:

It is also possible for household A that it paid prosumer B for energy by either disclosing the random number used in the generation of the one-time public destination key used in that transaction to B. Or she can use any other kind of zero-knowledge protocol to prove she knows the random number. The ring signatures would also allow the auditing of transactions by, for example, the DSO. This would be achieved by prosumer B giving the tracking key or truncated address to the DSO, who would then be able to link all incoming transactions to B.

\subsubsection{Mixing through Zero-Knowledge Proofs}
Zero-knowledge proofs (ZKP) are ways for a person to prove the knowledge of some specific fact to a verifier, without actually having to disclose the knowledge. Blum \textit{et al.} provided non-interactive ZKPs (NIZK) in 1988 \cite{Blum:1988:NZA:62212.62222}, where the prover and verifier don't have to interact or communicate directly with each other. The Zerocoin protocol \cite{miers2013zerocoin} outlines a way how NIZKs can achieve the untraceability objective of the previous section and it ensures that no double-spending is allowed.\footnote{Each coin in the protocol is identified uniquely by a serial number.} Zerocoin is a protocol for the decentralized mixing of coins, so that they can not be traced, or \textit{tainted}. However, senders and destinations can still be identified.~\cite{miers2013zerocoin} Luckily, Zerocash~\cite{Sasson:2014:ZDA:2650286.2650810} extends the NIZK functionality to allow for anonymous transactions, anonymous balances and coins, improved performance of transactions and sending of assets to a receivers fixed address without action required from the receiver. Zerocash makes use of a more efficient version of the NIZK, used in Zerocoin, called ZK \textit{Succinct Non-interactive ARguments of Knowledge} (zk-SNARK). 
% It features the algorithms: \textbf{Setup($1^\lambda$)}$\rightarrow \textit{params}$, \textbf{Mint(}\textit{params})$\rightarrow \textit{(c,skc)}$, \textbf{Spend}(\textit{params, c, skc, R, \textbf{C}})$\rightarrow(\pi, S)$ and \textbf{Verify}(\textit{params, $\pi$, S, R, \textbf{C}})$\rightarrow$$\{$0,1$\}$. The \textbf{Setup} function takes a secret parameter and returns a global public set of parameters and description of the set of coins. It is only executed once in the lifetime of the scheme, and the authors of the protocol recommend the usage of a trusted party for this. \textbf{Mint} is used to create coins from the coin set, given the parameters. \textbf{Spend} and \textbf{Verify} are executed by a sender and a receiver, respectively at the beginning and end of each transaction.

The Zerocash-scheme could be carried out using a simple messaging board, but would not be safe in practice since information might be manipulated or the owner of said board might collude etc. Therefore, an immutable, decentralized data storage, governed by the consensus of its peers is required to assure the secure transmission of information. The blockchain provides such a structure. 
% \begin{enumerate}[noitemsep,topsep=-\parskip]
% \item A mints a new message by generating a new random serial number $S$ of value $V$ and commits to it.
% \item The commitment, $C$, is such that only the secret message $m$ can reveal $S$.
% \item A then mints a second message by generating a new serial number $S_m$ so that the commitment $C$ is decrypted by the message $m$. 
% \item A posts the commitments to a blockchain along with the corresponding value in cryptocurrency.
% \item B has sold energy during the last timeperiod with references ($m_i,\dots m_j$) and has thereby $j-i$ number of references to scan the blockchain for.
% \item To redeem the payment, B produces a ZKP $\pi$ for the following statements:
% \begin{enumerate}[noitemsep,topsep=-\parskip]
% \item B knows a tuple ($C$) from all valid commitments available and
% \item B knows the secret $m$ such that the commitment ($C$) opens to ($S$) 
% \end{enumerate}
% \item B can now post a 'spend'-transaction containing ($S,\pi$) on the blockchain.
% \item The other users verify $\pi$ and ensure that ($S$) didn't occur already in the history of transactions.
% \item If correct, then the blockchain protocol allows B to collect cryptocurrency of value $V$. 
% \end{enumerate}
% This requires B to know all references to energy transactions that are outstanding (and coming from prosumer B) to date, and to be able to compare them to the available, valid commitments.

\subsubsection{Threats and weaknesses in Ring Signature- and Zero-Knowledge Proof-schemes}
\label{transthreat} 
\begin{figure}[t]
\centering
\includegraphics[width=\columnwidth]{ringsigs.png}
\caption{Visualization of untraceability in ring signatures in smart meter-based energy trading and the potential deductions of origin of the transaction by a single household in the chain of signatures.}\label{fig:ringsigs}
\end{figure}
When applying either ring signatures or zero-knowledge SNARKs to PETra, potential weaknesses or attacks need to be considered.A potential threat to ring signatures is when a large amount of the unspent transactions are owned by an adversary or when insufficient amounts of signatures are included in a ring. When a prosumer A wishes to select a group of signatures to sign her transaction as well, then it is likely that she will select many of the transactions from the adversary. Assuming the adversary spends his outputs without \textit{mixing}\footnote{The number of other signatures used in the ring.}, then A's transaction is exposed as well.~\cite{monero2014} Recent research  also show that up to 65\% of Monero transactions are trivially traceable using one attack. They also exposes two more attacks that have been amended in the latest versions of the protocol, lowering the amount of transactions traceable to 20\%.~\cite{monero2014,DBLP:journals/corr/MillerMLN17}

One of the main weaknesses of the Zerocash-based protocol is that for each private transaction, a costly zk-SNARK needs to be computed. But that is not a threat to anonymity, just a practical reason why it might be difficult to run the scheme over a congested public blockchain. In \cite{Sasson:2014:ZDA:2650286.2650810}, experiments show an average time of 3 min to create the zk-SNARK for a private transaction, verifying it takes only 8.5 ms. Another large practical drawback of Zerocash is the lack of programmability and functionality that would be required in PETra. Zhang \textit{et al.} solve some of the practical flaws and amend security issues.~\cite{zhangz}

\subsubsection{Proposed Solution to Achieve Transaction Anonymity}
Applying the CryptoNote protocol to PETra could be done by performing both energy transactions and monetary transactions using ring signatures. They would be securely logged, tamper-proof and anonymous through the usage of a blockchain. Even though  some security flaws exists, as seen in the previous paragraph, the risk of identification, linking or tracing of transactions can be minimized by imposing a high minimum number of signatures per transaction. We also propose to connect the global transaction networks to augment the number of transactions and thereby limit the chance of deduction by elimination.

Applying ZKPs to PETra would require that a smart meter can encrypt and sign a transaction, transmit a proof of it to the blockchain and thus the receiver of the payment, without having to reveal the actual amount of energy or cost incurred to anyone but the receiver. This is achieved by the Zerocash-protocol and is implemented as a fork of the Bitcoin blockchain. Neither the receiver, nor any other participants can gain information about the transactions sent over the blockchain. To provide full functionality for PETra, the Zerocash-protocol would need to be implemented for the transmission of bids and asks as well as the already existing monetary transactions. The second implementation would need to be modified to transmit and link bids and asks to the payments ledger. A more straightforward but bloated structure would be to create transactions without monetary value to post a bid or an ask and then directly reference the final bid-/ask-transaction in the payment-transaction. 
% \subsubsection{Bidding Anonymity}
% Prosumers must also be able to anonymously post energy bids and asks
% on the bid storage service.  An anonymous bid (or ask) contains an ECA
% (or EPA), a price, and an anonymous communication identifier
% (\emph{e.g.}, Tor hidden service), which can be used to contact the
% bidding (or asking) prosumer.  To enforce safety requirements, the bid
% storage service must verify that the prosumer actually owns the asset
% to be traded.  To this end, the prosumer first has to prove that it
% controls the anonymous address where the asset is stored, which can be
% performed in multiple ways.

% In many distributed ledgers, an address represents a public key, and
% controlling means knowing the corresponding private key.  In this
% case, the prosumer can prove that it controls an address by signing a
% challenge, which was freshly generated by the service, with the
% private key of the address.

% \subsubsection{Smart-Meter Based Billing}
% After a prosumer has finished trading, it deposits all of its EPA,
% ECA, and FA to the smart meter by transferring them to an anonymous
% address generated by the smart meter.  Later, during timeslot $t$, the
% smart meter measures the amount of energy actually consumed (or
% produced) by the prosumer using physical sensors.  The meter can then
% compute the prosumer's bill for timeslot $t$, which will be paid to
% the DSO, as follows. \Abhishek{The safety argument should be
%   strengthened here}

% Notice that consumption assets are not used directly for billing, they are only used to enforce security and safety requirements.

### 2017-09-27 docs/papers/m4iot-2017/main-body.tex
m4iot

\section{Introduction}

Interest in---and commercial adoption of---blockchain technology has increased in recent years~\cite{TheTruthAdoption:online}. For example, blockchain adoption in the financial industry has yielded market capitalization surpassing \$75 billion USD~\cite{BitcoinPrices:online} for Bitcoin and \$36 billion USD for Ethereum ~\cite{EthereumPrices:online}.  One reason for this growth stems from blockchains' combination of existing technologies to enable  the interoperation of non-trusted parties in a decentralized, cryptographically secure, and immutable ecosystem without the need of a trusted central authority.
%\AbhishekOld{You should also state that at the same time the adoption of IoT devices has been increasing significantly to the point where these devices are not only passive data generating devices but are active participants, which leads to the necessity of providing transactional integrity.}

During roughly the same time, the increased proliferation of IoT devices has motivated the need for transactional integrity due to the transition of IoT devices from just being smart-sensors to being active participants that impact their environment via communication, decision making, and physical actuation. These abilities require transactional integrity to provide auditing of actions made by potentially untrusted networked 3rd party IoT devices. The demand for transactional integrity in IoT devices that simultaneously leverage  blockchain features (such as decentralization, cryptographic security, and immutability) has motivated research on creating transactive IoT blockchain applications~\cite{Bogner2016,Buccafurri2017}.

Blockchain deployments (and specifically Ethereum, which is the focus of this paper due to its large installed base, and its powerful smart contract language) are generally managed via programs that have different modes in which they can operate. They broadly fall into Command-Line Interfaces (CLI), RPC APIs, or creating Graphical Interfaces via the use of HTML pages and JavaScript code~\cite{EthereumAPInterfaces:online}. These interfaces provide standard means to either run Ethereum applications within the clients themselves, or to interface other applications with the Ethereum clients.

In practice, however, the existing blockchain deployment interfaces lack built-in fault tolerance, most notably for either network communication errors or application execution faults. Moreover, Ethereum clients are deployed manually since no official manager exists for them. As a result, developers can---and do~\cite{ethereumLostCoinAPI:online}---lose all of their Ether (Ethereum's digital currency) due to insecure client configurations. This problem is compounded by the fact that Ethereum's clients do not warn of this risk within their built-in help feature, and instead rely upon online documentation to warn developers.

Addressing this problem requires patterns and tools that enable the deployment of blockchain clients in a repeatable and systematic way.
This requirement becomes even more important when integrating IoT blockchain applications (ITBAs). The IoT component of ITBAs add other requirements atop traditional blockchain applications due to their interactions with the physical environment and increased privacy concerns, \emph{e.g.}, thus preventing leakage of personal data, such as  energy usage that would reveal a user's activity patterns in their home~\cite{gubbi2013IoT}.

Moreover, ITBAs may not only communicate over the blockchain, but may also use off-blockchain communications via TCP/IP or other networking protocols for the following reasons:
\begin{itemize}
\item  There are interactions with the physical environment that might require communication with sensors and/or actuators.  For example, a user's smart-meter might communicate wirelessly with their smart-car's battery to activate charging based on current energy production/cost considerations. 
\item The distributed ledger (which makes an immutable record of transactions in blockchain) is public, so it is common to only  include information within transactions that can safely be stored publicly. In particular, if some or all data from a transaction must be kept secret for privacy or any other reasons the transaction can, instead, contain the meta-data and a cryptographic hash of the secret data.  Private information must, therefore, be communicated off-blockchain while still preserving integrity by storing meta-data and hash information on the blockchain ledger.
\item Management tasks such as: updates, monitoring, calibration, debugging, or auditing may require off-blockchain communication (with possible on-blockchain components for logging). Currently, these management tasks are done manually in conventional blockchain ecosystems. Similar to the need for a systematic means of deploying apps in a blockchain network, there is a need to systematically configure the network topology between all components of ITBAs.
\end{itemize}
%Blockchain constraints 
%Enabling Blockchain to interact with IoT brings an additional dynamic, interactions with the physical environment to blockchain, that doesn't normally exist. Interacting with the physical environment also brings with it additional constraints. These constraints will vary depending on specific IoT deployment scenarios. However, some

%What is the pattern of deploying/testing/recovering/communication in a BC IOT?
%Blockchain and IoT interactions need a

%\subsubsection{Blockchain}
%-What are distributed ledgers and why are they so important for IoT systems? \cite{TheEnerg14:online}

%-What are the typical design patterns and communication requirements for these systems? Note the challenge is to mix off-blockchain and on-blockchain communication primitives.

%-What are the current state of the art solutions that are available, and how are they tested?

%-What are the gaps in the state of the art, and why is it important to have comprehensive testing?

%-The contribution of this paper is an architecture and description of lessons learned.

%\cite{Eisele2017}

% \cite{zhang2017applying} % Dana's PLOP paper

This paper presents the structure and functionality of PlaTIBART, which is a \textit{Platform for Transactive IoT Blockchain Applications with Repeatable Testing} that provides a set of tools and techniques for enhancing the development, deployment, execution, management, and testing of ITBAs. In particular, we describe a pattern for developing ITBAs, a Domain Specific Language (DSL) for defining a private blockchain deployment network, Actor components upon which the application can be deployed and tested, a tool using these DSL models to manage deployment networks in a reproducible test environment, and interfaces that provide fault tolerance via an application of the \textit{Observer} pattern.

The remainder of this paper is organized as follows: 
Section \ref{system_model} explains the system model underlying PlaTIBART and describes the scenario of transactive energy used in this paper to motivate the need for ITBAs;
Section \ref{stateOfArt} reviews the current state-of-the-art regarding IoT and blockchain integration;
Section \ref{proposedArch} illustrates our proposed ITBA architecture and shows how we use the \textit{Actor} pattern to construct our solution, the DSL we created, and the network manager script we created to generate  test networks for ITBAs; Section \ref{empirical} examines our experimental testbed configuration and analyzes our results; Section \ref{lessonslearned} summarizes lessons learned, while implementing our proposed architecture; and Section \ref{conclusion} presents concluding remarks and outlines future work.

\section{System Model}
\label{system_model}

This section explains the system model underlying PlaTIBART and describes the use case scenario of transactive energy we employ in this paper to motivate the need for ITBAs.
%
% 3 layers - 
%	3) system-wide agreed upon sequence events
%	2) distribued database
% 	1) IoT Interactions , events, decisions
% we ignore #2 for now
%  We address #1 and #3 for now. and provide testing 
Based on our experience developing decentralized apps (DApps) for blockchain ecosystems~\cite{Zhang2016,dubey2017resilience},  three key capabilities are essential for DApps to function effectively in an ITBA ecosystem: traditional IoT computations and interactions should be supported, information should be robustly sorted in a distributed database, and a system-wide accepted sequential log of events should be provided. Each requirement can be delegated to a separate layer in a three-tiered architecture.  The first tier is the IoT middleware layer that facilitates communication between networked devices, which can be addressed by existing IoT middleware, such as RIAPS~\cite{RIAPS_IEEE_ISORC_2017}. The second tier is a distributed database layer. The third tier is a sequential log of events layer, which can be solved by blockchain integration.

PlaTIBART provides an architecture for coordinating all these layers in a fault tolerant manner, along with tools for repeatable testing at scale. It leverages the Actor model~\cite{lee2003actor} to integrate these three layers. Each layer is composed of components that accomplish their designated layer-dependent tasks. These components are then combined into a single actor that can interact with each layer and other actors in the network, as described in Section~\ref{proposedArch}.

%IoT system requirements are much more demanding than most traditional Blockchain software. Specifically IoT systems, due to their interaction with the physical environment, having constraints

% Traditional Blockchian software bugs and crashes result in possible lost work, but IoT bugs and crashes can potentially result in property damage, injury, and even potential loss of life. There is also the underlying concept of \"Internet of Things\", in that an ever increasing number of devices or "things" will be added to the network in the future. These two things combine to give us a large number of devices that, if not trustworthy, can potentially be disastrous. Therefore, there needs to be a means to allow for the system as a whole to protect itself from either malicious or faulty devices within the network. Blockchain addressees this concerns by providing a Byzentine fault-tolerant mechanism for a distributed ledger. This alone isn't enough to provide a complete system, but it does provide a core component upon which to build. 
%
%In the Proof-of-Work operating manner, Byzentine Fault-Tolerance is guaranteed when less than 50\% of the network's computation is faulty or malicious. This provides a acceptable guarantee on a public network, due to the insatiability of controlling 51\% of the world-wide network's computational power. There are other Proof mechanisms, such as Proof-of-Stake, that are being explored but are not yet widely adopted specifically on the Ethereum network, which we are using for our testing, so we will assume a Proof-of-Work mechanism is being used for the remainder of this paper.

\subsection{Case Study: Transactive Energy System}
\label{case_study}

%Transactive Energy, or technology used for managing the creation and consumption of electricity within an electrical grid, provides a good case study because not only the demand of electricity could potentially be life-threatening if demands are not met appropriately, but it is also being explored in actual deployments. \{cite here} Let us explore a Transactive Energy enabled smart grid, where the grid itself is connected to a traditional power company. The power company provides smart-meters to every property that has the ability to measure energy consumed, and also, potentially produced. The smart-grid would also have a network adjacent to it that provides a communication network upon which components of the network can communicate.

Transactive Energy Systems (TES) have emerged in response to the shift in the power industry away from centralized, monolithic business models characterized by bulk generation and one-way delivery toward a decentralized model in which end users play a more active role in both production and consumption \cite{NIST_TE,Gridwise}.
 %There are a number of well-documented factors contributing to this shift, including the increasing deterioration and fragility of the current grid, the regulatory and public mandate for environmental awareness, and general social trends toward the democratization of services, as exemplified by the "sharing economy" \cite{TheGrid}.
The GridWise Architecture Council defines TES as ``a system of economic and control mechanisms that allows the dynamic balance of supply and demand across the entire electrical infrastructure, using value as a key operational parameter'' \cite{Gridwise}. 
%The idea is to realize a user-centric system that allows residential consumers and prosumers (consumers that also produce energy) to trade energy futures directly in a local, open, peer-to-peer (P2P) market at the distribution level, which includes middleware components and messaging services that ensure secure, reliable, and timely communication between various TMP modules, sensors, and the blockchain system.
%We highlight the architectural and protocol specifications of our middleware that ensure \emph{privacy} and \emph{security} for participants in the TES, as well as \emph{safety} for the TES.

In this paper, we consider a class of TES that operates in a grid-connected mode, meaning the local electric network is connected to a Distribution System Operator (DSO) that provides electricity when the demand is greater than what the local-network can generate. The main actors are the consumers, which are comprised primarily of residential loads, and prosumers who operate distributed energy resources, such as rooftop solar batteries or flexible loads capable of demand/response. Additionally, the DSO manages the grid connection of the network. Such installations are equipped with an advanced metering infrastructure consisting of TES-enabled smart meters.
%In addition to the standard functionalities of smart meters: i.e. the ability to measure line voltages, power consumption and production, and communicate these to the DSO. TE-enabled smart meters are also capable of communicating with other smart meters, have substantial on-board computational resources, and are capable of accessing the Internet and cloud computing services as needed. 
Examples of such installations include the Brooklyn Microgrid Project \cite{BrooklynMicrogrid} and the Sterling Ranch learning community~\cite{SterlingRanch}. A key component of TES is a transaction management platform (TMP), which handles market clearing functions in a way that balances supply and demand in a local market.

%Use the transactive energy system to explain the timing and criticality requirements for these systems. Explain the nature of the communication patterns here. Also explain that there are differences between privately managed systems and public systems.

\iffalse
Figure \ref{fig:workflow} shows a proposed TES trading workflow, which demonstrates several key aspects and interactions of IoT blockchain applications . For example, this figure shows patterns of communication that can occur both on-blockchain and off-blockchain. Likewise, it shows that multi-step transactions can be terminated mid-process. It also shows how a prosumer and a consumer interact only via on-blockchain communication through the use of a smart contract.

%In the figure, we have both on-blockchain and off-blockchain communication, smart contract method invocations, smart contract triggered events, and messages and transactions that cause the trading workflow to terminate. Additionally, neither the timing constraints for each step in the trading process, nor the logic to handle transactions or messaging being lost and needing resubmission to the blockchain are expressly shown, but both must be accounted for.

%Figure \ref{fig:workflow}
\begin{figure*} [h]

	\center

	\includestandalone[scale=0.9]{sequence-diagram}
	\vspace{-0.2em}
	\caption{Sequence diagram of a proposed Transactive Energy (TE) trading workflow. Dotted lines are RIAPS messages, solid lines are Ethereum transactions, and dashed lines are smart contract events. Messages and transactions in \textcolor{red}{red} stop the trading workflow. %\textcolor{blue}{I don't think RIAPS has been mentioned before. Describe this as an example application that needs to be tested. RIAPS is not important, say that this off block-chain communication.}
		%	Both Ethereum transactions and smart-contract events are processed through associated geth client.
	}
	\label{fig:workflow}
	\vspace{-0.12in}
\end{figure*}
\fi

\section{Analysis of State-of-the-Art}
\label{stateOfArt}

This section reviews the state-of-the-art in IoT and blockchain integration,  focusing on testing. Prior work~\cite{christidis2016blockchains} has shown that IoT and blockchain can be integrated, allowing peers to interact in a trustless, auditable manner via the use of blockchain as a resilient, decentralized, and peer-to-peer ledger. Work has also been done on the topics of security and privacy of IoT and Blockchain integrations~\cite{dorri2017blockchain,ouaddah2017towards}. Beyond that, work has focused on formal verification of smart contracts~\cite{kumaresan2014use}, and how to write smart contracts ``defensively''~\cite{delmolino2016step} to avoid exceptions when multiple contracts interact. The current state-of-the-art with respect to testing, however, is lacking because blockchains are infrequently tested at scale in a systematic and repeatable manner, so we focus on that below.

%\AbhishekOld{This paragraph does not describe related research for this work. Please search specific literature that talks about using IoT and Blockchain together and perhaps discussing the reliability issues. }
%Additionally, it has been disclosed that the United State Internal Revenue Service has purchased software to deanonymize Bitcoin tax fraud~\cite{IRSBlockchain:online} through advanced tracking of transactions, including across multiple addresses and associating off-blockchain information. 
 %This demonstrates the maturity of Blockchain profiling tools, which further increases the already high privacy requirements on development of Blockchain enabled IoT devices and networks. Additionally, this shows that considerations need to be taken into account to consider all possible avenues in which personal information is disclosed to prevent profiling.

% 
% > Additionally, it has been disclosed that the United State Internal Revenue Service has purchased software to deanonymize Bitcoin tax fraud\cite{IRSBlockchain:online} through advanced tracking of transactions, including across addresses. This demonstrates the maturity of Blockchain profiling tools. 
% >  are lacking in privacy protection because of the existence of external Blockchain sources of data can assist in profiling users.
% > of the power of axillary information has in creating data profiling models. This is why creation of new Blockchain accounts and cycling of these accounts quickly is so important.
% 
% ^.

%are lacking in privacy protection because of the existence of external Blockchain sources of data can assist in profiling users.

%of the power of axillary information has in creating data profiling models. This is why creation of new Blockchain accounts and cycling of these accounts quickly is so important.

\subsection{Testing IoT Blockchain Systems}

%Explain current IoT-BC systems and how are they tested.

Popular blockchain ecosystems, such as Bitcoin and Ethereum, suffer from design limitations that prevent their direct application to IoT. In particular, transaction-confirmation times are relatively long (around tens of minutes) and variable on public blockchain networks due largely to their proof-of-work algorithms. Likewise, IoT devices have limited processing power and storage capabilities, which must be accounted for and tested~\cite{IoTandBl20:online} to ensure constraints are met.
% \AronOld{I don't see why ``predominantly designed to communicate via the ledger'' implies long/variable confirmation time} most applications being predominantly designed to communicate via the ledger~\cite{IoTandBl20:online}.

Prior work on testing of IoT blockchain systems generally fall into two categories: (1) their test implementation has a single client and one or more smart contracts or (2) they focus purely on theoretical aspects and discuss future work implementing a test example. For example, Beck et.\ al~\cite{beck2016blockchain} discusses their implementation, but apparently (since it is not discussed in detail) the implementation only uses a single client, two smart contracts, and no additional transactions on the ledger. Conversely, Simic et.\ al \cite{simicCaseStudyIoTBlockchainHealthcare2017}  presents a purely theoretical paper where they discuss IoT and blockchain powered healthcare at a high level, without addressing privacy or any of the many other significant implementation difficulties. 
%Even those that do implement a slightly broader testing 
%Aitzhan and Svetinovic who implemented a proof-of-concept platform for decentralized smart grid energy trading using blockchains using a proof-of-work consensus, but they do not consider grid control and stability, or scalability~\cite{aitzhan2016security}.

\subsection{Testing Repeatability}
%Also explain that in distributed systems deter-lab and EMulab enabled significant progress because of the repeatability and testing mechanisms available.
%\AbhishekOld{What exactly is the challenge of testing for block-chain IOT applications. Can you describe the complexity in terms of figure 1. Consider should all of the actors come online at the same time. Should they come online sequentially. The actor to geth client (you should explain what is geth client) connection can lose transactions. Actor can lose messages. Then you can say we need a testing network that help us introduce these test cases.}

The importance of integration and regression testing in software development has been well-established for over 20 years~\cite{rothermel2001prioritizing,agrawal1993incremental,leung1990study}. Integration and regression testing of distributed systems has been improved via network emulation testbeds, such as DETERLAB~\cite{mirkovic2012teachingDETERLAB} and Emulab~\cite{siaterlis2013useEmulab}. These testbeds provide mechanisms to repeatably deploy and test a distributed system for both integration and regression testing.

Testing ITBAs incurs additional difficulties that standard IoT applications do not face. For example, there is a completely separate network for each component of the actor in an ITBA: the IoT middleware/application layer, possibly a distributed database layer, and the blockchain layer.  We focus on the IoT middleware/application layer and blockchain layer in this paper. Testing thus requires that for each actor, we must run both the actor's IoT middleware/application code and a blockchain client instance. This pairing incurs a wide range of conditions that must be planned for, tracked, corrected, and tested.

Some examples of what must be tested include: (1) the order of actor/blockchain client starting; (2) whether all actors should be started before processing on either the IoT and/or blockchain network starts; and (3) what detection and recovery mechanisms are needed to account for lost messages between the blockchain client and the actor, the actor losing a message, and transactions being lost on the blockchain. A testing environment for ITBAs, thus, needs to repeatably create networks and network conditions to address these conditions. Section~\ref{proposedArch} describes how the PlaTIBART architecture enables the building of such test networks.

\section{The Architecture of PlaTIBART}
\label{proposedArch}

%Your architecture
%\AbhishekOld{Where is figure 1 referenced. See the blue comments in figure 1}
PlaTIBART architecture for creating repeatable test network deployments of IoT/blockchain applications combines a Domain Specific Language (DSL) to define the network topology and settings, a Python program leveraging the Fabric API to manage the test network, and the RIAPS middleware~\cite{RIAPS_IEEE_ISORC_2017} to facilitate communication between nodes on the network. 
\iffalse
PlaTIBART's DSL is textual and uses the JSON formatting for notation. The network manager application leverages the usage of SSH via the Python Fabric API to allow remote management of potentially multiple nodes on each host in the network. The RIAPS middleware provides each node on the network the off-blockchain communication mechanism to communicate with other nodes and contains the application logic for each node. 
\fi
Each of these components is described below.

\subsection{Application Platform}

%Resilient Information Architecture Platform for the Smart Grid (RIAPS) is the middleware platform our solution uses to facilitate discovery of peers on the network, containment of application logic, and

%Explain all the pieces and show the execution of the transactive energy application as example
%\Mike{This is 3rd time we use RIAPS, but first spelling out, is that okay?}
The \textit{Resilient Information Architecture Platform} for Smart Grid (RIAPS)~\cite{RIAPS_IEEE_ISORC_2017} is the application platform used by PlaTIBART to implement our case-study example described in Section~\ref{case_study}. %\footnote{\url{https://riaps.isis.vanderbilt.edu/}} 
RIAPS provides actor and component based abstraction, as well as support for deploying algorithms on devices across the network \footnote{RIAPS uses ZeroMQ \cite{hintjens2010zeromq} and Cap'n Proto \cite{varda2015cap} to manage the communication layer.} and solves problems collaboratively by providing micro-second level time synchronization \cite{RIAPS_IEEE_ISORC_2017}, failure based reconfiguration \cite{dubey2017resilience}, and group creation and coordination services (still under active development), in addition to the services described in \cite{LeeNiddodiSrivastavaBakken2016}. It is capable of handling different communications and running implemented algorithms in real-time.

\subsection{Actor Pattern}
Each application client in the network is implemented as an actor with two main components: (1) a wrapper class specific to the role the actor is given and (2) a geth client, the  reference client for Ethereum\footnote{\url{https://github.com/ethereum/go-ethereum/wiki/geth}}. Figure \ref{fig:network-component-topology} shows a small network of five actors (indicated by an ellipse around a wrapper and geth client pair) and the networking connections between each actor's components. Geth clients communicate exclusively via on-blockchain means,\textit{ i.e.}, the geth client of each actor communicates directly with its associated wrapper, and the wrapper  communicates directly with other wrappers via an off-blockchain channel, such as TCP P2P communications.

\begin{figure}[ht]
\vspace{-0.10in}
	%\textbf{Sample Model}\par\medskip
	\centering
	\includestandalone[width=0.8\columnwidth]{pic2}
	%    \resizebox{\textwidth}
    \vspace{-0.05in}
	\caption{Sample Actor Component Network with an Actor is a Geth Client and a Wrapper.}
	\label{fig:network-component-topology}
    \vspace{-0.10in}
\end{figure}

\subsection{Fault Tolerance}

%\Abhishek{Be precise about the fault model. In this case you are considering transaction loss. Say that this is one of the problems we have witnessed. Refer to the online bug report of ethereum and cite it. Say that other kinds of faults, specially in actor communication are handled by other middleware solutions like RIAPS - cite RIAPS}
A key benefit of decoupling the blockchain client and the wrapper into two  components of an actor is enhanced fault tolerance around transaction loss, compared with tightly coupled solutions. Specifically, it allows the wrapper to not only monitor the blockchain client, but also shut down and restart the client as needed. This design allows the wrapper component to ensure that if any known or discovered faults arise from defects in the blockchain software, the wrapper can at least attempt to recover.

For example, in our Ethereum test network described in Section~\ref{experiment}, we have encountered faults where transactions are never mined~\cite{EthereumIssue14893:online} until a client is restarted. These lost transactions are problematic since they prevent a client from being able to interact with the blockchain network. Other types of faults, such as those related to an actor's communication with other components of the network, are handled by other middleware solutions, such as RIAPS.

PlaTIBART applies the \textit{Observer} pattern to notify the wrapper of the occurrence of events, such as faults and other blockchain-related conditions. This notification is accomplished by a separate thread within the wrapper that monitors its paired geth client for new events, such as completed transactions, or potential faults. This thread then notifies registered callback(s) when target events occur. For example, if the geth client becomes unresponsive or transactions appear to have stalled, then registered callback method(s) are called to notify the wrapper. 
%\AbhishekOld{I though the observer pattern is done. Explain how does this pattern work by describing the sequence of activities.}.

\subsection{Domain Specific Language}

PlaTIBART's DSL defines the roles that different clients in our network have, based on the \textit{Actor} pattern. This DSL model implements a correct-by-construction design, thereby allowing for a verification stage on the model to check for internal consistency before any deployment is attempted. This verification prevents inconsistencies, such as two clients requesting the same port on the same host.

Figure \ref{fig:model-sample} shows an example of our DSL, which specifies a full network configuration file for a test network. The first two lines of the configuration file contain two unique identifiers for this test network and its current version, ``configurationName'' and ``configurationVersion'', respectively. Next, it contains values specific for the creation of an Ethereum private network's Genesis block.

A Genesis block in Ethereum is the first block in a blockchain and has special properties, such as not having a predecessor and being able to declare accounts that already have balances before any mining or transactions begin. The ``chainID'' is a unique positive integer identifying which blockchain the test network is using; 1 through 4 are public Ethereum blockchains of varying production/testing phases\footnote{By setting ``chainID'' to a public value, it is possible to connect a test network to a preexisting public blockchain network instead of creating a new one.}.

Next, ``difficulty'' indicates how computationally hard it is to mine a block, and ``gasLimit'' is the maximum difficulty of a transaction based on length in bytes of the data and other Ethereum runtime values. The ``balance'' is the starting balance that we allocate to each client's starting account upon creation of the network\footnote{``balance'' applies only to accounts created before a new blockchain is created. Accounts created after the blockchain, be it public or private, is created will not receive any starting balance.}, which eliminates the situation where clients cannot begin transactions to request assets before any mining has begun. Lastly, the ``clients'' represent the actual nodes in our network.

%\AbhishekOld{Make sure you separate the DSL from the example. An easy way to do this is to have separate paragraphs for DSL explanation and example.}
Clients in the DSL represent the individual actors in our network, comprised of a geth client and a RIAPs instance using a wrapper interface. The geth client has two interfaces and TCP ports associated with it: one for incoming Blockchain connections, and one for administration.

%\Mike{Took out Par. talking about port allocation for space}
%In the network defined in Figure \ref{fig:model-sample}, we allocate each client a pair of ports on a private subnet, and for each new client type we offset the port by 1,000. This means that in the example network defined by Figure \ref{fig:model-sample}, Prosumers use ports 9,000-9,029, DSO uses ports 10,000 and 10,001, and "miners" use ports 11,000 and 11,001. This design limits the total number of clients to 1,000, though this limit can be removed by assigning unique start ports to each client type.
\begin{figure}[t]
%\textbf{Sample Model}\par\medskip
\lstinputlisting{sample-contract.json}
\vspace{-0.12in}
\caption{Sample DSL model.}
\label{fig:model-sample}
\vspace{-0.15in}
\end{figure}

\subsection{Network Manager}
\label{networkmanager}
%We wrote a network manager application for PlaTIBART that uses the DSL to create and manage test network instances. To simplify deployment requirements on test machines the only requirements, other than required ssh key management logistics, are that each test machine have geth and dtach installed and that an ssh daemon(assumed A Linux operating system) be running.

The PlaTIBART network manager is written in Python and leverages the Fabric API to manage the SSH connections from a deployment/management host to each test host. The network manager is a stateless command-line program that takes a DSL file and a series of command operands to determine which operation it should perform. This design makes the manager readily adaptable into existing development workflows.

Based on an input DSL file, PlaTIBART's network manager can create, start, stop, and delete ``clients'', ``miner''(s), and entire test network instances. The only exception to this approach is managing blockchains, which must have a configuration file made from the DSL file, and then adds that file into a new Genesis block. A Genesis block is the first block in a new Ethereum network. This Genesis block must be distributed to geth's private storage for each ``miner'' and ``clients'', before the test network can be started.

% interesting, but not 'directly' relevant & cut to save space.
%To provide additional comparability for other designs, the model fully supports Ethereum's discovery mechanism Bootnodes, despite not being used in our network. Called "bootnodes", it is an optional top-level dict that follows the same conventions as a  "clients" grouping.

%\begin{figure}[h]
%%\textbf{Sample Model Bootnode Extension}\par\medskip
%\lstinputlisting{sample-contract-bootnodes.json}
%\caption{Sample Model Bootnode Extension}
%\label{fig:model-bootnodes}
%\end{figure}
%\subsection{Network Manager}
%
%The

\section{Empirical Results}
\label{empirical}
This section examines our experimental testbed configuration and analyzes our experiment's results.
\subsection{Experimental Testbed Configuration}

To test PlaTIBART we implemented a solution to the Transactive Energy case study discussed in Section \ref{case_study} and deployed it to the test network defined in Figure \ref{fig:model-sample}. This network was installed on a private cloud instance hosted at Vanderbilt University. We ran our tests on 6 virtual hosts, each with: 4GB RAM, 40GB hard drive space, running Ubuntu 16.04.02, and gigabit networking.

For these tests we implemented a custom smart contract and wrappers for both Smart Grid distribution system operators (DSO) and prosumer clients in Python. Each wrapper had one geth client associated with it. We used PlaTIBART's network manager tool outlined in Section~\ref{networkmanager} to create, start, shutdown, and delete the test network. We manually paired each wrapper with its geth client's IP address and port (in future work this is to be integrated and automated into the network manager's capabilities).

Using our custom written wrappers, smart contract, and managed test network we simulated a day's worth of transactive energy trading between actors. Via the Linux ``time'' command we measured each step needed in the entire process to create a test network, including Clients Create, Miners Create, Blockchain Make, Blockchain Create, Distribute to Clients, and Distribute to Miners. We also measured the steps required to start and connect the geth instance for each ``clients'' (``prosumer'' and ``DSO'') to the geth client of each ``miner.''\footnote{Miners are treated as a special case of ``clients'' and have their own unique set of network manager commands.} Currently, this star-network is the only network topology supported by PlaTIBART, but we will expand the supported topologies in the future.

\subsection{Analysis of Results}
\label{results}
After running our tests, described above, we observed the results shown in Table~\ref{tab:1}. As shown in this table, the standard deviation for each testing phase was small (the largest being 0.09\% of the time taken). Likewise, the average time either remained relatively static, or scaled linearly, in relation to the number of clients (2, 5, 10, 15, 20 prosumers + 1 DSO) with one exception, that being ``network stop'', which had a sudden jump in its otherwise linear times at the 20 prosumer test.

\label{experiment}
\begin{table*}[!htbp]
	\centering
	%	\vspace{-0.2em}
	\input{results-tabular}
	\caption{Average Time (Seconds) and Standard Deviation of Five Tests for Each Variation of Number of Prosumer Clients}
	\label{tab:1}
	\vspace{-0.3in}
\end{table*}

The test phases that remained relatively static included: Miners Create, Blockchain Make, Blockchain Create, Distribute to Miners, Miners Start, and Network Delete. The test phases that scaled with increase in number of prosumers were: Clients Create, Distribute to Clients, Full Network Created, Clients Start, Network Connect, and Network Stop. Other than Network Stop, which appears exponential but we suspect might become linear at greater network sizes, all of the scaling increases were linear (Std Dev < 0.065) after dividing the average time increase by the difference in number of clients.

The results of our experiments indicate that there exists high consistency and predictability of managing PlaTIBART-based blockchain test networks, with the exception of the network stop operation, which needs further testing. These results help build confidence that PlaTIBART's approach to creating repeatable testing networks for IoT blockchain applications scales well, which is important to encourage adoption by IoT system developers.

%We believe that it is likely that in addition to these phases, that the time required for each phase related to Miners would scale with the number of miners if they were increased.\Mike{This is likely true, but should we mention this, b/c we should have tested it?}

\section{Lessons Learned}
\label{lessonslearned}

During the implementation of our initial PlaTIBART prototype, we learned many lessons related to integrating IoT and blockchain. The three main categories of lessons learned involved documentation deficiencies, buggy behavior of the Ethereum geth client, and limitations of both Ethereum's management APIs and the Solidity smart contract language.

The official documentation for Ethereum is deficient in many key areas, such as organization, completeness, lack of meaningful examples, and clarity on best practices and security warnings. Here are some examples that demonstrate this:

\begin{itemize}
	\item Ethereum does not maintain its own documentation, instead linking to an outside resource maintained by volunteers from the Ethereum Community.
	\item The only official documentation is a FAQ on the main page, and the wikis in Ethereum's various source code repositories. 
	\item Important side effects of a management API call are only found listed under other method's documentation.
\end{itemize}

There are also programmatic bugs with Ethereum's reference client implementation, geth. While building and evaluating our test network, we experienced new transactions that were not mined regardless of how many new blocks were being mined, Ether available to the client, or any other obvious cause.

Similar issues have been reported frequently on the public bug-reporting/tracking system about others attempting to setup private networks~\cite{EthereumIssue14893:online}. As of writing this paper, however, there is no solution other than to restart the geth client. This issue is addressable, but highlights the importance of fault tolerance in individual client execution and ways to recover from faults at that level.

There are also idiosyncrasies of the Ethereum management APIs that are not well documented. An example is the polling mechanism that clients use to see if transactions occurred, which meet certain search criteria, and are called filters. The problem is that created filters are set to an undefined timer and will simply cease to work if not used ``for a while''~\cite{EthereumJSONRPC}. This quote, however, does not come from the description of the method for creating the filter. Instead, it is on a secondary method, eth\_uninstallFilter(), which is never referenced (directly or indirectly) from the original method, eth\_newFilter().

There are also limits to the Solidity smart contract language that must be accounted for in early planning stages of development. For example, the language currently does not support floating-point numbers. Moreover, all values must be converted to a specific binary representation for submission as a transaction. These limitations prevent---or dramatically increase the complexity (and therefore computational cost)---of advanced mathematical computations on-blockchain, which yields more off-blockchain processing and communication.

%\AbhishekOld{Why don't we have an experiment and results section?}

\section{Concluding Remarks}
\label{conclusion}
This paper describes how PlaTIBART applies the \textit{Actor} pattern with DSL-driven test network management software and component creation to enable the development of resilient, fault-tolerant IoT-blockchain applications and middleware. We employed PlaTIBART to dynamically deploy and manage test blockchain networks of varying sizes based on DSL configuration files. We also defined APIs for monitoring and recovering from faults, which standard blockchain applications were unable to recover from. This capability provides the means for fully integrated regression testing of blockchain applications, which is a novel contribution.

PlaTIBART currently  uses Ethereum as its blockchain implementation. For example, our DSL has Ethereum-specific required settings, such as ``chainId'' and ``gasLimit.'' Future versions of PlaTIBART will refactor these requirements so that other blockchain platforms, such as Hyperledger, can be substituted seamlessly.  Other areas of future work focus on formal verification of internal-consistency of a configuration file and a means of defining incremental adjustments to a test network through the DSL. Likewise, we are developing network management tools that help to simplify and automate the network topology for both the overall test framework instance, as well as which Actor components are paired.

%Our solution's DSL for configuring test networks has  a lot of areas of improvement, such as better support for different Blockchain network software, more precisely configured TCP port designations per client type, and for a means of declaring a network topology for clients to have upon deployment.

%\end{section}  % This is where a 'short' article might terminate

%\appendix
%Appendix A
%\section{Headings in Appendices}

### 2017-09-27 docs/papers/m4iot-2017/paper.tex
m4iot

\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage[mode=buildnew]{standalone}% requires -shell-escape
\usepackage{xcolor}

\usepackage{hyperref}

\usepackage{tikz}
\usetikzlibrary{calc}

\usepackage{standalone}

\usepackage{listings}

\usetikzlibrary{shadows}
\usepackage{pgfplots}
\pgfplotsset{compat=1.14}
%\pgfplotsset{compat=1.10}

\usepackage{multirow}

\lstset{
	basicstyle=\ttfamily,
	frame=single
}

% Put % before of what you want disabled

% Select what to do with todonotes: 
\usepackage[textsize=tiny]{todonotes} % notes not showed
%\usepackage[draft, textsize=scriptsize, textwidth=1.55cm]{todonotes}   % notes showed
\newcommand{\Aron}[1]{\todo{\textbf{Aron}: #1}}
\newcommand{\Abhishek}[1]{\todo{\textbf{Abhishek}: #1}}
\newcommand{\Mike}[1]{\todo[backgroundcolor=blue!25]{\textbf{Mike}: #1}}
\newcommand{\Doug}[1]{\todo{\textbf{Doug}: #1}}

\newcommand{\AronOld}[1]{\todo[backgroundcolor=yellow!15]{\textbf{Aron\\Addressed}: #1}}
\newcommand{\MikeOld}[1]{\todo[backgroundcolor=yellow!15]{\textbf{Mike\\Addressed}: #1}}
\newcommand{\DougOld}[1]{\todo[backgroundcolor=yellow!15]{\textbf{Doug\\Addressed}: #1}}
%\newcommand{\AbhishekOld}[1]{\todo[backgroundcolor=yellow!25]{\textbf{Abhishek\\Addressed}: #1}}
\newcommand{\AbhishekOld}[1]{}
% Select what to do with command \comment:  
% \renewcommand{\comment}[1]{}  %comment not showed
 \renewcommand{\comment}[1] {\par {\bfseries \color{blue} #1 \par}} %comment showed

% Copyright
%\setcopyright{none} %\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{}

% ISBN
\acmISBN{}

%Conference
\acmConference[M4IoT]{4th Workshop on Middleware and Applications for the Internet of Things}{December 2017}{Las Vegas, USA} 
\acmYear{2017}
\copyrightyear{2017}

\acmPrice{15.00}

\begin{document}
\setlength{\marginparwidth}{1.5cm}

 \title[PlaTIBART: a Platform for Transactive IoT Blockchain Applications with Repeatable Testing]{PlaTIBART: a Platform for Transactive IoT Blockchain Applications with Repeatable Testing}

%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
 % \texttt{acmart.pdf} document}

\author{Michael A. Walker, Abhishek Dubey, Aron Laszka, and Douglas C. Schmidt}
\affiliation{\institution{Vanderbilt University}}
\email{{michael.a.walker.1, abhishek.dubey, a.laszka, d.schmidt}@vanderbilt.edu, }

% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{M. Walker et al.}

\begin{abstract}
{\em
With the advent of blockchain-enabled IoT applications, there is an increased need for related software patterns, middleware concepts, and testing practices to ensure adequate quality and productivity. IoT and blockchain each provide different design goals, concepts, and practices that must be integrated, including the distributed actor model and fault tolerance from IoT and transactive information integrity over untrustworthy sources from blockchain.
\AbhishekOld{for example, .. are we referring to distributed actor model and transactive information integrity over untrustworthy sources. It will be good to be precise}
Both IoT and blockchain are emerging technologies and both lack codified patterns and practices for development of applications when combined.
\AbhishekOld{This is first time we have used the world cyber-physical here}
This paper describes PlaTIBART, which is a platform for transactive IoT blockchain applications with repeatable testing that combines the Actor pattern (which is a commonly used model of computation in IoT\AbhishekOld{How does this relate to IoT, you can say a commonly used model of computation in IoT}) together with a custom Domain Specific Language (DSL) and test network management tools. We show how PlaTIBART has been applied to develop, test, and analyze fault-tolerant \AbhishekOld{Fault-tolerant is being described very late. you should describe this earlier as an example of the well-defined patterns} IoT blockchain applications.}

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
  <concept>
<concept_id>10011007.10011006.10011073</concept_id>
<concept_desc>Software and its engineering~Software maintenance tools</concept_desc>
<concept_significance>500</concept_significance>
</concept>
 <concept>
<concept_id>10011007.10011074.10011081.10011082.10011088</concept_id>
<concept_desc>Software and its engineering~Design patterns</concept_desc>
<concept_significance>500</concept_significance>
</concept>
  <concept>
<concept_id>10010520.10010575</concept_id>
<concept_desc>Computer systems organization~Dependable and fault-tolerant systems and networks</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[500]{Software and its engineering~Software maintenance tools}
\ccsdesc[500]{Software and its engineering~Design patterns}
\ccsdesc[300]{Computer systems organization~Dependable and fault-tolerant systems and networks}

\keywords{Internet of Things, Blockchain, Design Patterns, Testing}

%\acmBadgeR{artifacts_available}

\maketitle

\input{main-body}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

\end{document}

### 2017-09-27 docs/papers/m4iot-2017/pic2.tex
m4iot

\documentclass{standalone}

\usepackage{tikz}
\usepackage{lmodern}
\usetikzlibrary{shapes}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{backgrounds}
\usetikzlibrary{calc}

%\setlength\oddsidemargin{0in}

\begin{document}

	% declare that we use 2 layers= background & main
	\pgfdeclarelayer{background}
	\pgfsetlayers{background,main}

	% define styles, similar to CSS 
	\newcommand*\ab{.4}
	\tikzset{
		net node/.style = {circle, minimum width=2.75*\ab cm, inner sep=2pt, outer sep=0pt, draw},
		net node2/.style = {circle, minimum width=2.75*\ab cm, inner sep=7pt, outer sep=0pt, draw, fill=white!100},
		net root node/.style = {net node, minimum width=3*\ab cm},
		dashed connect/.style = {line width=2pt,dashed, draw=blue!50!cyan!25!black},
		net connect/.style = {line width=3pt, draw=blue!50!cyan!25!black},
		snake it/.style = {line width=2pt,decorate, decoration=snake, draw=blue!50!cyan!25!black},
		texter/.style = {draw, rectangle,anchor=west},
	}

	\begin{tikzpicture}

		% draw nodes
		\foreach \i in {0,...,4} {
			% draw wrapper nodes
			\path (-90+\i*72:2.25) node (i\i) [net node] {Wrapper};
			% draw geth nodes
			\path (-90+\i*72:4.5) node (o\i) [net node2] {geth};
			% draw the json-rpc thick lines 
			\path [net connect] (i\i) -- (o\i);

			% draw eclipse around node pairs
			\draw let \p1=(o\i), \p2=(i\i), \n1={atan2(\y2-\y1,\x2-\x1)}, \n2={veclen(\y2-\y1,\x2-\x1)}
			% no clue why 4*\n1 works, just played with it + radius
			in ($ (o\i)!0.5!(i\i) $) ellipse [x radius=\n2/2+30pt, y radius=1.1cm,rotate=90-4*\n1];
		}

		% draw the perimeter lines, needs to be background due to snake line overdrawing into geth
		\begin{pgfonlayer}{background}
			% loop through list tupple
			\foreach \x/\nodename in {o/snake it, i/dashed connect}
				% draw connector lines
				\path [\nodename] (\x0) -- (\x1) -- (\x2) -- (\x3) -- (\x4) -- (\x0);
		\end{pgfonlayer}

		% define variables for 'key' dimensions
		\newcommand{\y}{-3.2}
		\newcommand{\x}{-3.5}
		\newcommand{\yscale}{0.7}
		\newcommand{\keylinestart}{2.1}
		\newcommand{\keylineend}{1.5}

		% define values tuple 'list'
		\newcommand{\mylist} { dashed connect/.5/Off-Blockchain, net connect/2.5/Management APIs, snake it/1.5/On-Blockchain }

		% loop through the 'list' 
		\foreach \nodename/\spacer/\text in \mylist {

			% draw 'sample' line
			\draw [\nodename] (\x-\keylineend,\y-\spacer*\yscale) -- (\x-\keylinestart,\y-\spacer*\yscale);	
			% draw 'sample' text
			\draw [texter] (\x-1.2,\y-\spacer*\yscale) node {\text};
		}

		\end{tikzpicture}

\end{document}

### 2017-09-30 docs/papers/m4iot-2017/main-body.tex
update

@@
 Also explain that there are differences between privately managed systems and public systems.
-
-\iffalse
-Figure \ref{fig:workflow} shows a proposed TES trading workflow, which demonstrates several key aspects and interactions of IoT blockchain applications .
-For example, this figure shows patterns of communication that can occur both on-blockchain and off-blockchain.
-Likewise, it shows that multi-step transactions can be terminated mid-process.
-It also shows how a prosumer and a consumer interact only via on-blockchain communication through the use of a smart contract.
-
-%In the figure, we have both on-blockchain and off-blockchain communication, smart contract method invocations, smart contract triggered events, and messages and transactions that cause the trading workflow to terminate.
-Additionally, neither the timing constraints for each step in the trading process, nor the logic to handle transactions or messaging being lost and needing resubmission to the blockchain are expressly shown, but both must be accounted for.
-
-%Figure \ref{fig:workflow}
-\begin{figure*} [h]
-
-	\center
-
-	\includestandalone[scale=0.9]{sequence-diagram}
-	\vspace{-0.2em}
-	\caption{Sequence diagram of a proposed Transactive Energy (TE) trading workflow.
-Dotted lines are RIAPS messages, solid lines are Ethereum transactions, and dashed lines are smart contract events.
-Messages and transactions in \textcolor{red}{red} stop the trading workflow.
-%\textcolor{blue}{I don't think RIAPS has been mentioned before.
-Describe this as an example application that needs to be tested.
-RIAPS is not important, say that this off block-chain communication.}
-		%	Both Ethereum transactions and smart-contract events are processed through associated geth client.
-	}
-	\label{fig:workflow}
-	\vspace{-0.12in}
-\end{figure*}
-\fi
 

### 2017-10-14 code/PhaseII/prosumers.sh
some scripts, and their output from the prosumer*.out files

@@ -1,0 +1,7 @@
+#!/bin/bash
+for i in `ls ~/projects/transactive-blockchain/code/PhaseII/results/test-10-11-nobattery/prosumer*.out`
+do 
+#echo $i
+python3 stats.py $i
+done
+

### 2017-10-14 code/PhaseII/components/MatchingSolverWrapper.py
no message

@@ -30,6 +30,10 @@ class MatchingSolverWrapper(MatchingSolver):
     finalized = START_INTERVAL - 1
     buying_offers = []
     selling_offers = []
+    # BEGIN TESTING
+    b_to_offer = {}
+    s_to_offer = {}
+    # END TESTING
     new_offers = False
     waiting_solutionID = False
     logging.info("Entering main loop...")
@@ -51,8 +55,10 @@ class MatchingSolverWrapper(MatchingSolver):
             offer = Offer(params['ID'], params['prosumer'], params['startTime'], params['endTime'], params['energy'])
             if name == "BuyingOfferPosted":
               buying_offers.append(offer)
+              b_to_offer[params['ID']] = offer # TESTING
             else:
               selling_offers.append(offer)
+              s_to_offer[params['ID']] = offer # TESTING
           elif name == "SolutionCreated":
             waiting_solutionID = False
             solutionID = params['ID']
@@ -61,7 +67,13 @@ class MatchingSolverWrapper(MatchingSolver):
               trades = [trade for trade in self.solution if int(trade['p']) > 0]
               for trade in trades:
                 self.contract.addTrade(self.account, solutionID, trade['s'].ID, trade['b'].ID, trade['t'], int(trade['p']))
+                # BEGIN TESTING
+                selling_feeder = MICROGRID.prosumer_feeder[s_to_offer[trade['s']].prosumer]
+                buying_feeder = MICROGRID.prosumer_feeder[b_to_offer[trade['b']].prosumer]
+                logging.info("Adding trade {} (selling feeder: {}, buying feeder: {})".format(trade, selling_feeder, buying_feeder)
+                # END TESTING
               logging.info("{} trades have been submitted to the contract.".format(len(trades)))
+              logging.info("Amount of energy traded in the solution for interval {}: {}".format(finalized + 1, sum([trade['p'] for trade in trades if trade['t'] == finalized + 1]))) # TESTING
             else:
               logging.info("Solution {} created by contract, but no solution has been found for this time interval (yet).".format(solutionID))
           elif name == "TradeAdded":

### 2017-10-14 code/PhaseII/components/config.py

@@ -7,7 +7,7 @@ SOLVING_INTERVAL = 5 # seconds (how often MatchingSolverWrapper tries to solve t
 INTERVAL_LENGTH = 120 # seconds (how often the components move onto the next time interval)
 PREDICTION_WINDOW = 5 # how many time intervals ahead SmartHomeTraderWrapper trade (i.e., an offer is posted if offer['start'] <= time_interval + PREDICTION_WINDOW)
 START_INTERVAL = 28 # starting time interval for the components
-END_INTERVAL= 100 # Last Interval
+END_INTERVAL= 100 # last time interval
 
 
 # model

### 2017-10-15 code/PhaseII/components/MatchingSolverWrapper.py
no message

@@ -70,7 +70,7 @@ class MatchingSolverWrapper(MatchingSolver):
                 # BEGIN TESTING
                 selling_feeder = MICROGRID.prosumer_feeder[s_to_offer[trade['s']].prosumer]
                 buying_feeder = MICROGRID.prosumer_feeder[b_to_offer[trade['b']].prosumer]
-                logging.info("Adding trade {} (selling feeder: {}, buying feeder: {})".format(trade, selling_feeder, buying_feeder)
+                logging.info("Adding trade {} (selling feeder: {}, buying feeder: {})".format(trade, selling_feeder, buying_feeder))
                 # END TESTING
               logging.info("{} trades have been submitted to the contract.".format(len(trades)))
               logging.info("Amount of energy traded in the solution for interval {}: {}".format(finalized + 1, sum([trade['p'] for trade in trades if trade['t'] == finalized + 1]))) # TESTING

### 2017-10-16 docs/papers/iotdi2018/ICCPS18.tex
added iotdi paper

\documentclass[conference,10pt,letterpaper]{IEEEtran}

\newif\ifShowLog
\ShowLogfalse

\usepackage[utf8]{inputenc}

% IEEE recommended packages
\usepackage{amsmath}
\interdisplaylinepenalty=2500
\usepackage{algorithmic}
\ifCLASSOPTIONcompsoc
\usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
\usepackage[caption=false,font=footnotesize]{subfig}
\fi
\usepackage{dblfloatfix}
\usepackage{url}

% custom packages
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage{soul}
\usepackage{paralist}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{colortbl}
\definecolor{TableRowGray}{gray}{0.93}

\usepackage{tikz}
\usetikzlibrary{shadows}
\usepackage{pgfplots}
\pgfplotsset{compat=1.10}

\definecolor{blueLine}{RGB}{57,106,177}
\definecolor{blueFill}{RGB}{114,147,203}
\definecolor{redLine}{RGB}{204,37,41}
\definecolor{greenline}{RGB}{0,250,0}
\definecolor{blackLine}{RGB}{0,0,0}
\definecolor{goldLine}{RGB}{160,82,45}

\usepackage{listings}%

\usepackage[textsize=tiny, textwidth=1.5cm,disable]{todonotes}
%\usepackage{marginnote} 
%\let\marginpar\marginnote

\newcommand{\Abhishek}[1]{\todo[color=yellow!50, linecolor=black!50,inline]{\textbf{Abhishek}: #1}}
\newcommand{\AbhishekC}[1]{\todo[color=yellow!50, linecolor=black!50]{\textbf{Abhishek}: #1}}

\newcommand{\Karla}[1]{\todo[color=green!30, linecolor=black!50,inline]{\textbf{Karla}: #1}}
\newcommand{\KarlaC}[1]{\todo[color=green!30, linecolor=black!50]{\textbf{Karla}: #1}}

\newcommand{\Aron}[1]{\todo[color=blue!10, linecolor=black!50,inline]{\textbf{Aron}: #1}}
\newcommand{\AronC}[1]{\todo[color=blue!10, linecolor=black!50]{\textbf{Aron}: #1}}

\newcommand{\Mike}[1]{\todo[color=orange!30, linecolor=black!50,inline]{\textbf{Mike}: #1}}
\newcommand{\MikeC}[1]{\todo[color=orange!30, linecolor=black!50]{\textbf{Mike}: #1}}

\newcommand{\scott}[1]{\todo[color=purple!30, linecolor=black!50,inline]{\textbf{Scott}: #1}}
\newcommand{\scottC}[1]{\todo[color=purple!30, linecolor=black!50]{\textbf{Scott}: #1}}

\begin{document}
\setlength{\marginparwidth}{1.5cm} % THIS IS REQUIRED FOR THE CORRECT PLACEMENT OF TODONOTES MARGIN NOTES

\title{Design and Implementation of Safe and Private Forward-Trading Platform for\\ IoT-Based Transactive Microgrids}

\author{\IEEEauthorblockN{Aron Laszka}
\IEEEauthorblockA{University of Houston}\\
%\IEEEauthorblockN{Monika Sturm}
%\IEEEauthorblockA{Siemens Corporate Technology}
\and
\IEEEauthorblockN{Abhishek Dubey}
\IEEEauthorblockA{Vanderbilt University}
\and
\IEEEauthorblockN{Scott Eisele}
\IEEEauthorblockA{Vanderbilt University}
\and
\IEEEauthorblockN{Michael Walker}
\IEEEauthorblockA{Vanderbilt University}
\and
\IEEEauthorblockN{Karla Kvaternik}
\IEEEauthorblockA{Siemens Corporate Technology}\\
%\IEEEauthorblockN{Martin Lehofer}
%\IEEEauthorblockA{Siemens Corporate Technology}
}
\renewcommand{\lstlistingname}{log}

\maketitle

% REMOVE BEFORE SUBMISSION!
\thispagestyle{plain}
\pagestyle{plain}

\begin{abstract}
Power grids are undergoing major changes due to rapid growth in renewable energy and improvements in battery technology. Prompted by the increasing complexity of power systems, decentralized IoT solutions are emerging, which arrange local communities into transactive microgrids.
We address the problem of implementing transactive energy mechanisms in a distributed setting, providing both privacy and safety.  Specifically, we design and implement an automated auction and matching system that ensures safety (i.e. satisfaction of line capacity constraints), preserves privacy, and promotes local trade and market efficiency for IoT-based transactive energy systems. This design problem is challenging because safety, market efficiency, and privacy are competing objectives.
We implement our solution as a decentralized IoT-based trading platform, which is built on blockchain technology and smart contracts.
To demonstrate the feasibility of our platform, we perform experiments with dozens of embedded devices and energy production and consumption profiles from a real dataset.
\end{abstract}

\begin{IEEEkeywords}Transactive energy platform, Internet of Things, blockchain, privacy, security, safety, smart contract.\end{IEEEkeywords}

\input{intro.tex}

\input{setting.tex}

\input{problem.tex}

\input{solution.tex}

\input{system.tex}

\input{implementation.tex}

\input{resultsandtestbed.tex}

\input{concl.tex}

\bibliographystyle{IEEEtran}
\bibliography{references}

\clearpage
%\input{draft.tex}

\end{document}

### 2017-10-16 docs/papers/iotdi2018/concl.tex
added iotdi paper

\section{Conclusion}
\label{sec:conclusion}

In this paper, we described the design and implementation of a  transaction management platform (TMP) for IoT-based transactive microgrids. Our solution enables prosumers to trade energy without threatening their privacy or the safety of the system. Our hybrid solver approach, which combines a smart-contract based validator with an external optimizer, enables the platform to clear offers securely and efficiently. Further, the ability to trade across multiple time intervals enables participants to take full advantage of batteries, thereby smoothening the load on the main grid. Finally, the use of blockchains provides decentralized trust and consensus capabilities, which protect from  malicious actors.

\AronC{future work:
- recovery from failures: retroactively change matching in case of a physical failure

- fault-tolerant matching: safety constraints will be satisfied even if a certain number of physical elements fail (or prosumers get disconnected)

- propose alternative market mechanisms, including those that involve double auctions and its variants.}

### 2017-10-16 docs/papers/iotdi2018/draft.tex
added iotdi paper

\clearpage
\section{Draft}

%\Karla{An idea: Carry out a two-stage market. First at the feeder level: match as much supply and demand at the feeder. Second: take what is left over and run a second matching at the inter-feeder level. Advantages: (1) satisfying capacity constraints could be simplified. (2) aggregating residual supply/demand and running a separate inter-feeder market could help make privacy easier? (3) matching itself might be simpler?}

%\Aron{Regarding aggregation at the feeder level: This might give us a much worse matching than the optimum. For example, suppose that there are two feeders, called 1 and 2, and both feeders have a producer and a consumer, called 1p, 1c and 2p, 2c, respectively. Suppose that 1p can be matched with either 1c or 2c, but 2p can be matched only with 1c. If we aggregate at the feeder level, we match 1p and 1c, after which we cannot match 2p and 2c to anyone. On the other hand, the optimal matching (i.e., 1p to 2c and 2p to 1c) satisfies everyone. (Btw, this reminded me of \url{http://www.cs.cmu.edu/~arielpro/15896s16/slides/896s16-14.pdf})}

%\Abhishek{To actually solve the capacity constraints properly we will need to do a load flow analysis. That is, consider all the generators in the system in that time interval (we can aggregate them per feeder), consider all the loads (we can aggregate them per feeder) and solve the nodal equations. However, this might not be feasible to do in a smart contract. Aggregation based on matched trades if done by the DSO can absolve us of the privacy leak issue/.}

%\Karla{An idea: Obfuscate identity within feeder by breaking up every offer received by the OSS into a random number of positive and negative offers that sum to the original offer. Assign different identities to each piece of the original offer}

%\Abhishek{But  these identities will still be associated with the feeder and I think aggregation per feeder will solve the same issue.}

\Karla{To maximize the amount of energy traded in the microgrid, we need to scrap the trade finalization process I proposed earlier, where periodic clearing pertains only to a single time slot and feeder. However, if we do so, we need to think about the following:}
 \begin{itemize}
\item how often the market is to be cleared across all time slots beyond $t+H$. (As a side note, I have added a comment explaining the rationale for the time horizon $H$)
\Aron{The optimal value of the market clearing frequency could be found using experiments. We need to keep it low so that prosumers hear back from the trading system in a reasonable amount of time, and we need to keep it high to minimize computational cost and maximize matching efficiency (the more we wait, the more offers we have, which means more matches).}
\Karla{We can identify it as another tunable parameter, without offering heuristics on how to select it.}
\item The sequence of events involving arrival of offers, solving the matching problem, finalization of transactions (a transaction is finalized if it is ready for execution - i.e. the parties involved are in a binding agreement, and now only the actual delivery or consumption are left.)
\Aron{1) offers are submitted by participants 2) market is cleared (matching algorithm), the end (we should discuss this somewhere between the problem setting and the matching problem formulation)}
\Karla{@Aron, maybe this is trivial, as you suggest. However, please consider the following two points; the implementations would be different depending on which of the two sequences of events we adopt, and I would imagine that the overall system behavior would also be quite different. There could be other possibilities in addition to the two below}
\item One possibility: Collect all unmatched offers that have arrived in any slot prior to the $k$th time slot. In the $k$'th time slot, finalize the transactions for time slot $k+H+1$ by solving the matching problem across all feeders, across all time slots starting at $k+H+1$. So the input to the problem is the set of all offers with at least one time slot in the interval $[(k+H)T,\infty)$, and the output is a set of matchings that may pertain to time slots beyond $k+H+1$. So, in the $k$th time slot, the matching algorithm outputs matchings that may pertain to time slots beyond $k+H+1$. However, we consider as "finalized" only those matchings in the $k+H+1$th time slot. In the next time slot - i.e. $k+1$, we simply repeat this process, and re-input all unfinalized offers, even if they were previously matched (because now we have new offers that have come in, and there might be more optimal matchings than those outputted in the $k$th time slot.). Note this is why it may be useful to distinguish between ``matching'' and ``finalization''.
\item Another possibility: Same as above, except we finalize all matchings arbitrarily far into the future (or up to some maximal time horizon restricting $\max I_{i,k}$). In the $(k+1)$'th time slot, collect all offers that have arrived since the beginning of the $k$th time slot and those that are still left unmatched. Solve the matching problem, but using new constraints for all future time slots, since some trades have already been finalized (there is now less capacity remaining). 
\end{itemize}

\subsection{Problem Statement}
The problem addressed in this paper is to design a trading mechanism and propose an architecture for a \emph{Transaction Management Platform} (TMP) that is able to implement the proposed trading mechanism in a way that satisfies the following requirements:
\subsubsection{Safety}
\begin{itemize}
\item At any given time $t$, $P(n,t)$, where $n \in N$, is the instantaneous power transferred by the home. Note that if the home is not a prosumer its value becomes $0$.

\item DSO also operates as a trading entity and can inject power into the microgrid. \textcolor{red}{We need to consider the effect of DSO's trade. The DSO will inject power into the whole grid. Its ratio for a feeder will depend upon the load ratio of the feeder}. Suppose we calculate the function $P(dso,f,t)$, where $f \in F$ provides the power transmitted by dso into the feeder $f$. This function can be approximated as the load divider circuit. $P(dso,f,t)=P(dso,t)\frac{\sum_{i=1}^{|F|}{load(i)}}{load(f)}$. This fractional term is a constant value that can be calculated before hand.
\item Then, safety constraint is $(\forall{f})(\forall{t})(P(dso,f,t)+\sum_{i=1}^{|F_M(f)|}(P(i,t)) \leq L(f))$
\end{itemize}
\Karla{@Abhishek: consider the following reformulation:}
\Abhishek{@Karla: The problem is that you cannot compute or control the instantaneous power injected by DSO per feeder. The DSO effectively is responsible for current $i$ at a given voltage. This current will redistribute through out the microgrid depending upon the loads of each feeder. Note that while load in each feeder is in series. The feeders themselves are in parallel. Thus, the equation I had above with the fraction is required to know how the current will distribute. Alternatively, as we discussed we can just ignore the DSO's power injection by not including it in the trading process. And if we consider that we ensure that total consumption  in a feeder is less than the limit across all feeders, we have effectively solved the problem. Of course it requires that the producer will never inject power if no matching trade exists. }
\begin{itemize}
\item For each feeder $f$ in the microgrid, we require the total power flow along any segment to not exceed the feeder capacity $C_f$. More precisely, let $S_f$ denote the set of all participants on feeder $f$, $P_i(t)$ denote the instantaneous power being supplied by participant $i$ at time $t$
\Aron{Is this the same as $P(i, t)$?}
, and $P_{f,DSO}(t)$ denote the instantaneous power delivered by the DSO to feeder $f$ at time $t$. For each feeder $f$ in the microgrid, the safety constraint can then be formulated as:
\begin{equation}
P_{f,DSO}(t) + \sum_{i\in S_f} P_i(t) \leq C_f,\quad \forall t\in\mathbb{R}_{\geq 0},
\end{equation}
\Aron{How is this different from the previous equation? What is the relation between $L(f)$ and $C_f$? Where is $L(f)$ defined?}
\Karla{Yes, just offering an alternative to the formulation above i.e., consider omitting the functional definition L(f) - keep it as simple as possible}
where it is understood that $P_i(t)=0$ if participant $i$ is not a producer.
\item Given the total instantaneous power supplied to the microgrid by the DSO and the aggregate load on feeder $f$, the quantity $P_{f,DSO}(t)$ can be calculated according to a current divider relationship. 
\end{itemize}

\subsection{Background}
\begin{itemize}
\item we explain the transactive energy workflow.
\end{itemize}
\subsection{Privacy}
TODO 
\begin{itemize}
\item List the threats and the sequence of steps where the individual identity can either be directly revealed or analytically inferred. we should show by proof that it will be possible to infer the aggregative trading activity per feeder. But, individual activity cannot be inferred.
\end{itemize}
\subsection{Market Efficiency and Fairness}
TODO
\begin{itemize}
\item Formally describe the constraint that all producers should eventually be matched if their offer is lowest and the capacity request is higher than the production capacity.
\Aron{I think that this goal may contradict the second one. For example, if the DSO would like the microgrid demand (i.e., net consumption) to be 1 MW but there is 1 MW production capacity and only 1.5 MW consumption capacity in the microgrid, then 0.5 MW of the production capacity should be unmatched. Since the DSO is primarily interested in load shaping, I think that it will opt for the second goal. (I know that the example is atypical, but even for typical cases, the second objective would be sufficient.)}

\item The market closely follows the demand profile set by the DSO.
\Aron{I think that this is better, see previous point.}
\Karla{Agreed}
\end{itemize}

\section{Market and TMP Design}

\subsection{Market interaction protocol}
\begin{itemize}
\item There is an \emph{Offer Storage Service} (OSS) that pools all incoming offers until they are either cleared or rejected
\Abhishek{We can use the blockhain for this. The trade service will add filters to know when new offers/bids have come in.}
\item There is a \emph{Trade Service} that performs trade finalization---i.e. market clearing and offer matching functions.
\Abhishek{The trade service is run as a smart contract. Either the DSO or the miner will be responsible for submitting the function. The result of successful execution of the function will be a list of assets that have been traded. new assets can be created as a result. Each prosumer/consumer will have a filter that will let them know when their asset has been traded. }

\Karla{I simplified this part from what I originally wrote}
\item \textbf{Time:} Time is divided into equal slots of duration $T$. 
\item During the $k$'th time slot:
\begin{itemize}
\item Previously finalized trades get executed
\Aron{What do we mean by executed? Does it mean that prosumers produce/consume energy?}
\Karla{I think it is useful to distinguish between finalization and execution. When I say a Tx is finalized, I mean that the parties involved have entered an enforcible contract, and when the time slot in question arrives, the trade actually executes - i.e. production and consumption take place. Moreover, matching takes place prior to finalization, though it could be synonymous to it.}
\Aron{Okay, but we need to keep in mind that prosumers can only consume or produce energy, there is not direct transfer between them. Further, prosumer may consume/produce more than what they agreed to (no one can predict their load perfectly), and pay/get spot market prices. So there is no explicit ``execution'' of a trade.}
\Karla{@Aron, I agree - in fact, the point you make is yet another reason to adopt this distinction. So a trade is ``executed'' when the seller attempts to inject power into the grid and the buyer actually consumes it (even if the amount actually injected / consumed may differ from the amount in the finalized trade) }
\Aron{``adopt this distinction'' Distinction between what?}
\item Unmet demand for slot $k$ is supplied by the DSO at regulator-approved maximal prices
\item Trades in slot $k+H+1$ get finalized\footnote{We say that a trade if finalized if it is ready for execution. Matched offers become finalized trades.}, where $H$ is the time horizon associated with the primary market.\footnote{We can consider implementing a secondary market with a shorter time horizon. This ``second round'' market accepts new offers on \emph{top} of all trades already finalized in the primary market, and tires to finalize them before the end of the $k$'th time slot.}
\Aron{What do we mean by finalized? How is $H$ chosen? Are we still optimizing multiple slots at the same time?}
\Karla{re finalized, see comment above}
\Karla{H is a tunable parameter; we do not have to provide a method of selecting H. H could be adjusted by the DSO for example, to affect factors such as volatility, or predictability to aid in planning. I do not know what all the implications of various values of H are, but they probably depend on the physical structure of the microgrid, and the trading policies adopted by the participants.}
\end{itemize}

% \Aron{How is this interval related to the intervals $T_M$ and $T_E$?}
% \item The market clears every $T_M$ units of time, producing an interval sequence $\{[t+kT_M, t+(k+1)T_M)\}_{k\in\{0,1,2,\ldots\}}$, starting from time $t$. 
% \Aron{For sake of simplicity, can we assume that $t = 0$, and interval numbers start from some initial number $k_0$?}
% \item Energy trades are scheduled to occur every $T_E$ units of time, producing an interval sequence $\{[t+kT_E, t+(k+1)T_E)\}_{k\in\{0,1,2,\ldots\}}$, starting from time $t$. 
% \Aron{For sake of simplicity, can we assume that $t = 0$, and interval numbers start from some initial number $k_0$?}
% \item $T_E$ need not be the same as $T_M$.

\item Market participants include the consumers, prosumers and the DSO.
\Aron{Is the behavior of prosumers a ``strict superset'' of the behavior of consumers?}
\Karla{Behaviorally they are nearly identical: consumers only submit offers with $X_i\leq0$.. I don't mind referring to everyone as prosumer, but I felt that conceptually it is helpful to distinguish between consumers and prosumers, and refer to them collectively as participants... So prosumers may have either negative or positive offers, while consumers only submit negative offers.}
\Aron{Do we need to explicitly model consumers? We could model them simply as prosumers with zero production capacity. If we model them explicitly, is their number $N - M$ fixed?}
\Karla{As a first modeling and implementation step it may help to fix $N-M$ an think later about generalizing}

\item \textbf{Offer Specification:}\Karla{I modified this 9/20/17, got rid of t} The $i$th market participant may interact with the market within the $k$'th time slot by submitting a single \emph{offer} $O_{i,k} = (X_{i,k},I_{i,k}, p_{i,k})$ to the OSS, which collects all offers submitted since the last time the market cleared. 
\Karla{We will need k in order to express the possibility that a single participant submits two distinct offers, $O_{i,k_1}$ and $O_{i,k_2}$ for which $I_{i,k_1}\cap I_{i,k_2}\neq \emptyset$.}
\Karla{Only one offer per time slot per participant: This is without loss of generality, since if a participant wishes to submit multiple offers during the $k$th interval they can just be combined into a single offer by adding the $X$'s and taking union of time slot sets}
\Aron{Not necessarily. Prosumers will actually need to submit multiple offers covering the same time interval.}
\Karla{Note that I am talking here about submission of offers, not the time slots they cover.}
\Aron{But there are many cases in which offers cannot be combined: for example, if I could produce 100 Watt in intervals 0 or 1 and 150 Watt in intervals 2 or 3, then I need to submit two offers because they cannot be combined.}

\item The elements of an offer are:
\begin{itemize}
% \item $t\in\mathbb{R}_{\geq 0}$ indicates the time at which $O_{i,t}$ is received by the OSS.\footnote{The first sanity check to perform is whether there exist some time intervals in the offer that are sufficiently far in the future, prior to forwarding the offer to the matching algorithm.}
% \Abhishek{This assumes that the clocks are synchronized.}
% \Karla{@Abhishek, We may not need a time stamp after all - need to think about this more...}
% \Aron{I don't think that will need $t$ for the matching. More importantly, what happens if the prosumer submits multiple offers at the same time? Do they all get the same subscript?}

\item $X_{i,k}$, the amount of power in [W] that participant $i$ is offering to either consume (if $X_{i,k}\leq 0$) or produce (if $X_{i,k}\geq 0$) at a constant rate within one of the specified time slots.  
\Abhishek{We assume the presence of power electronics and battery to ensure the constant production rate. See the paper at https://arxiv.org/pdf/1705.06130.pdf. if the offer intervals are small then the constant power assumption can be implemented.}
\Karla{Awesome - thank you Abhishek!}
\item $I_{i,k}\subset \mathbb{N}$ is an index set that identifies those intervals in which participant $i$ is able to consume or produce energy at a constant rate of $X_{i,k}$ Watts. Specifically, $I_{i,k}$ indicates that participant $i$ is able to produce or consume $X_{i,k}$ Watts of power constantly throughout \emph{any one} of the intervals in the set $\{[kT, (k+1)T)\}_{k\in I}$. 
\Karla{@Aron, do we still need "atomic values" below? If not, can we change it to $X_i\in\mathbb{R}$?}
\Aron{Probably not. It might make solving the problem computationally easier, but at this point I don't see if it actually will...}

%\item $X_i$ can take atomic / quantized values in a finite set $\mathcal{P}\subset\mathbb{R}$.
\Aron{I think that it might be simpler to present $X_i$ as the amount of energy to be produced/consumed (noting of course that the prosumer is expected to produce/consume it with constant power in the interval that is determined by the auction.}
\Karla{@Aron, can you explain?}
\Aron{Which part? I would like to emphasize again that if we consider generating in a single (fixed length) interval, then power and energy are interchangeable.}

\Abhishek{Either we assume that the consumers also use storage devices to shape their consumption considering energy transfer will not help. A consumer requires exact power input when they plug in a new device. Thus, the consumers power requirement will be constant for the time when the trade is settled. In other words, we have to match the $X_i$, the power transferred to the consumer in the  requested time interval. Or, tell the consumer that the matched profile is some $X^{'}_{i}$, which is less than $X_i$. Also the time when the power has been matched can be a subset of the requested interval. Given that consumers can always pull power from DSO, the difference in settled asset and requested asset will be billed using DSO rates.} 
\Karla{@Abhishek - That is a nice point. Instead of "rejecting" offers, we could consider (later) proposing a curtailment scheme (for both loads and producers) to satisfy capacity and possibly other constraints. The question is whether there is a way to do this as a preliminary step prior to matching, or if it needs to be incorporated this into the matching problem formulation, and if so, how... }
\Karla{@Aron, we can do it like that, or obtain this info from $X_i$ directly see item I added below:}
\item  Define $s_i = \tfrac{1}{2}(X_i+|X_i|)$ and $b_i = -\tfrac{1}{2}(X_i-|X_i|)$, so that if $X_i\geq 0$, $s_i = X_i$ while $b_i = 0$, and if $X_i\leq 0$, $s_i=0$ while $b_i=|X_i|$. In that case $s_i$ represents the amount of power produced and to be sold, and $b_i$ represents the amount of power to be bought and consumed. 
\item $p_{i,k}$ is the \emph{reservation price} for the current offer. If $X_{i,k}>0$ then $p_{i,k}$ indicates the minimum price that participant $i$ is willing to sell $X_{i,k}$ Watts of power within the intervals indicated by $I_{i,k}$
\end{itemize}

 \item To protect against denial-of-service attacks, each participant is allowed to submit at most $\bar{o}$ offers within any single time slot.  
 \Aron{I think that we can leave the introduction of such constraints to the discussion of the implementation. (We would also need to limit the size of $I_i$, and I think that we should rather try to keep the model ``clean.'')}
 \Karla{Hi Aron, as per my comment above, I think we should omit the $\bar{o}$ constraint and, WOLOG allow only a single offer to be submitted per participant per time slot...  }
 \Aron{I am afraid that this would not be WOLOG.}
 \Karla{I believe that under the offer specification and event sequencing I proposed previously, it would be WOLOG. What would be the benefit of having a single participant submit multiple offers within time slot $k$? Note that I am referring here to the time of submission, not the time slots specified in $I_i$.}
 \Aron{See comment above. Another example: I don't have a battery, but I have solar power. I am trying to sell 120 Watt between 4pm and 5pm and 80 Watt between 5pm and 6pm. If I am restricted in the number of offers that I can post, I have to wait until I post the second one, which could put me at disadvantage or decrease matching efficiency. Also, I do not see the advantage of introducing this 1 offer per 1 time interval limit.}
 \Karla{@Aron, looking at your matching problem formulation, I guess we should limit the horizon over which time slots are specified in the $I_{i,k}$, since this affects the dimensionality of the problem... }

\item  There are no restrictions on specifying $I_{i,k}$; the OSS accepts offers to buy or sell power arbitrarily far into the future, and it automatically rejects (and notifies the participant) time slots that are insufficiently far into the future. The cardinality of $I_{i,k}$ is also not restricted.
\item The rationale for allowing participants to specify an index set identifying those time slots in which they are able to provide or consume power is to leverage the flexibility afforded by battery storage.

\item If an offer $O_{i,k}$ is matched, participant $i$ is required to produce or consume a constant power level of $X_{i,k}$ Watts (within some tolerance) for the entire duration $T$ of the trade interval in the match, regardless of instantaneous energy requirements by the participant's local load.
\item Upon receiving an offer, the OSS first checks whether any of the time intervals in the offer are sufficiently far in the future. If not, the offer is rejected and the participant who submitted it is notified. 
\end{itemize}

\subsection{Trade Finalization Process}
Within time slot $k$:
\begin{itemize}
\item The OSS forms a set $O_{f,k}$ of offers $O_{i,t}$ submitted to the OSS prior to time $t=kT$, with $k+H+1\in I_i$, and $i$ a participant in feeder $f$. 
\item There is some sort of anonymization step. (??)
\Aron{Anonymization needs to be earlier if we use blockchains for OSS (which I think we do).}
\item The OSS submits $O_{f,k}$ to the Trading Service, which:
\begin{itemize}
\item Enforces the capacity constraint for feeder $f$ by checking that the aggregate demand in time slot $k+H+1$ does not exceed the feeder capacity (NOTE: supply need not be  checked). If capacity is exceeded, some offers are rejected according to one or more prioritization schemes\footnote{One possibility is to prioritize offers with time slot index sets whose cardinalities have undergone the greatest number of reductions, which indirectly prioritizes offers that have been waiting longest to be matched.}, and the OSS is notified about the rejected offers. Let $\tilde{O}_{f,k}$ denote the remaining set of offers.
\item The remaining offers $\tilde{O}_{f,k}$ undergo the Market Clearing Process, which finalizes the trades for interval $k+H+1$.
\end{itemize}
\item For each offer $O_{i,t}\in O_{f,k}$ rejected by the Trade 
 Service, the OSS makes the replacement $I_i\leftarrow I_i \setminus \{k\}$, and notifies participant $i$. If $I_i$ is now empty, the offer is rejected and the participant is notified. In other words, offers not matched in time slot $k+H+1$ remain in the OSS until they are matched in a subsequent time slot, or rejected.  
 \Karla{Sorry - there is some notational overloading here - I will fix this}
\end{itemize}

\Aron{For the sake of readability, we could first present a single-market solution, and then propose the multi-market solution as a straightforward extension for improving efficiency.}
\Karla{Agreed}
\Abhishek{yes, I think that will work.}

\subsection{Market Clearing Process}
The market clearing process is designed to maximize some measure of market efficiency. For example, maximize the normalized difference between total trades that took place and the total trades that would have taken place if all offers were matched. 
\Karla{Probably not the best measure of "efficiency". Have to think about this.}
The market clearing process takes the following steps:
\begin{itemize}
\item From $\tilde{O}_{f,k}$, determine the market clearing price $p$ for time slot $k+H+1$ according to the procedure outlined in \cite{Basar14}:
\Karla{i.e., see the discussion starting at equation (3) in the paper}
\begin{itemize}
\item Sort all sellers in an increasing order of their reservation prices, and sort all buyers in a decreasing order of their reservation prices. 
\item Form the supply and demand curves (price vs. volume)
\item Determine the seller $s^*$ and buyer $b^*$ at the intersection point of the demand and supply curve
\item Allow the first $s^*-1$ sellers and the first $b^*-1$ buyers to participate in this double auction. The rest are rejected and notified. Let $\tilde{\tilde{O}}_{f,k}$ denote the remaining set of offers. 
\item It is shown in \cite{Emarket} that excluding $s^*$ and $b^*$ ensures that total supply and demand match and that the double auction is \emph{strategy proof} -- i.e., there is no incentive for participants to submit untruthful reservation prices. 
\item The market clearing price for time slot $k+H+1$ is selected as $p=\tfrac{p_{s^*} - p_{b^*}}{2}$, where $p_{s^*}$ and $p_{b^*}$ are reservation prices of seller $s^*$ and buyer $b^*$. 
\item Apply any matching mechanism to match all remaining offers in $\tilde{\tilde{O}}_{f,k}$, and finalize the matched trades at price $p$.
\Karla{@Aron, do we need to elaborate on this? i.e. how matching is done? I was thinking at this point, since we are still within a single feeder, we just match any which way - i.e. line up all the demand and line up all the supply, break up as needed, and match in the obvious way.}
\end{itemize}
\Aron{Are we sure that we want to use this matching algorithm? It's suboptimal.}
\end{itemize}

\subsection{Other Market Architectures}
A selling feature of the proposed platform is that it provides a messaging framework for a variety of market architectures, including:
\begin{itemize}
\item Full double auction, with automated market clearing and matching service
\item Producers (including DSO) post offers, and consumers manually pick producers with whom to transact.
\item DSO sets all prices, producers and consumers post offers without prices. Automated matching. DSO takes transaction fee... 
\end{itemize}

\subsection{TODO}
\begin{itemize}
\item Think of other meaningful market efficiency measures (i.e. max total dollars exchanged?), or other objectives (fairness?). 
\item explain rationale for spot v futures market include graphic. 
\item fix notational overloading
\end{itemize}

\section{Old Problem Formulation}

\Aron{\textbf{Note}: I'll rewrite this section based on the comments (e.g., using arbitrary sets of intervals in the offers instead of pairs of beginning and ending intervals), and move the old version to the appendix.}

\newcommand{\vx}[0]{\ensuremath{\boldsymbol{x}}}
\newcommand{\PUD}[0]{\ensuremath{\textit{PD}}}
\newcommand{\PUDD}[0]{\ensuremath{\textit{PDD}}}
\newcommand{\Real}[0]{\ensuremath{\mathbb{R}}}
\newcommand{\Natural}[0]{\ensuremath{\mathbb{N}}}

Constants:
\begin{itemize}
\item $D_t$: ideal unmet demand in the microgrid in time interval $t$ (for traffic shaping by DSO)
\Karla{what is $D_t$ - a function of time? What are the units? Can we give a pictorial example? }
\Aron{Yes, $D_t$ depends on the time interval $t$. It is measured in Watts (or whatever we use to measure power/energy). Since it is for a single fixed-length time interval, we can measure it either as power or energy.  I am not sure what you mean by pictorial example.}
\item $F$: set of feeders
\Karla{Defining ``set of feeders'' might be notational overkill ;-). Could just say ``there are F feeders'' (i.e. use F to denote the cardinality), and then talk about feeder $f$}
\Aron{Hmmm... I think that using $F$ to denote the set will be simpler because we can then say $f \in F$ instead of $1 \leq f \leq F$ (or $f \in \{1, \ldots, F\}$).}
\item for feeder $f \in F$,
\begin{itemize}
\item $S_f$: set of selling offers
\item $B_f$: set of buying offers
\item $C_f$: energy flow capacity
\end{itemize}
\item for selling offer $s \in S_f$ (or buying offer $b \in B_f$),
\begin{itemize}
%\item $F_s$ (or $F_b$): feeder
\item $E_s$ (or $E_b$): amount of energy
\Karla{This should be power, no?}
\Aron{No, prosumers are trading energy, which they will produce/consume in some time intervals. (Again, the usage is somewhat interchangeable because we could say that $E_s$ is the amount of power that the prosumer will produce/consume in exactly on time interval.)}
\item $T^{begin}_s$ (or $T^{begin}_b$): first time interval in which energy could be produced (or consumed)
\item $T^{end}_s$ (or $T^{end}_b$): last time interval in which energy could be produced (or consumed)
\Karla{From the participants' point of view, it might be better if they can specify an arbitrary list of time intervals in which they are willing to trade - i.e. don't impose that the intervals have to be consecutive.}
\Aron{Sure, we can definitely change that.}
\item $P_s$ (or $P_b$): reservation price
\end{itemize}
\end{itemize}

For convenience, we also introduce
\begin{itemize}
\item $S = \cup_{f \in F} S_f$: set of selling offers 
\item $B = \cup_{f \in F} B_f$: set of buying offers 
\end{itemize}

A pair of selling and buying offers $(s, b)$
\Karla{these need to be associated with participants - i.e. maybe subscripted by $i$, for the $i$'th participant} 
\Aron{Yes, after the optimal matching is found, we need to know which offer belongs to which prosumer. (Of course, we also need to provide privacy, so we should include an anonymous address in the offer rather than the actual identity of the prosumer.)}
match each other if
\Karla{Nice - let us define what we mean by "match"}
\begin{itemize}
\item $P_s \leq B_s$
\item $T^{begin}_s \leq T^{end}_b$
\item $T^{begin}_b \leq T^{end}_s$ 
\Karla{3 things to consider when defining "matching": (1) What if the power quantities do not match? (2) what if the intervals don't perfectly overlap? (3) It might be more flexible for participants to indicate a set of numbered time slots in which they are willing to trade, instead of specifying a contiguous interval with a start and finish. And, it may not be more difficult to do matching when numbered intervals are indicated. i.e., consider definition of offer provided above. On the other hand, there may be an advantage to indicating contiguous intervals instead of time slots... What is the advantage?}
\Aron{(1) and (2) ``Match'' here means only that the prosumers may exchange some amount of energy (not necessarily all the energy that they offered). We should mention this in text before the definition. We could also use a different word instead of ``match'' (e.g., we could say that the offers are ``compatible'' or  ``matchable'' or that they ``intersect'' or ``overlap''). (3) Yes, in the model it will indeed be simpler to work with arbitrary sets of intervals. Contiguous intervals can simplify the implementation (e.g., each offer can be represented by a fixed-size structure instead of a structure containing a variable-length list).}
\end{itemize}
For convenience, we let $M(s)$ and $M(b)$ denote the set of offers that match offer $s$ and $b$, respectively.
Further, we let $T(s, b)$ denote the time intervals in the intersection of offers $s$ and $b$, i.e., 
\begin{equation}
T(s, b) = \left\{t ~\middle|~  \max\{T^{begin}_s, T^{begin}_b\} \leq t \leq \min\{T^{end}_s, T^{end}_b\} \right\} .
\end{equation}

Variables:
\begin{itemize}
\item $\forall s \in S, b \in M(s), t \in T(s, b): x_{s,b,t} \in \Real_{\geq 0}$: amount of energy transferred from selling offer~$s$ to buying offer $b$ in time interval $t$
\end{itemize}
For convenience, we let $x_{s,b,t} \equiv 0$ for $s \in S, b \not\in M(s)$ or $s \in S, b \in M(s), t \not\in T(s, b)$.

Further variables (for certain optimization objectives, see below):
\begin{itemize}
\item $\PUD \in \Real_{\geq 0}$: peak unmet demand
\item $\PUDD \in \Real_{\geq 0}$: peak difference to ideal unmet demand
\end{itemize}

Constraints:
\begin{itemize}
\item amount of energy:
\begin{align}
\forall b \in B: ~& \sum_{s \in S} \sum_t x_{s,b,t} \leq E_b \\
\forall s \in S: ~& \sum_{b \in B} \sum_t x_{s,b,t} \leq E_s 
\end{align}
\item safety:
\begin{align}
\forall f \in F, t: -C_f \leq & \left( \sum_{s \in S_f} \sum_{\bar{f} \in F} \sum_{b \in B_{\bar{f}}} x_{s,b,t} \right) \nonumber \\
 & - \left( \sum_{b \in B_f} \sum_{\bar{f} \in F} \sum_{s \in S_{\bar{f}}} x_{s,b,t} \right)
\leq C_f 
\end{align}
\begin{align}
\forall f \in F, t: & \left( \sum_{s \in S_f} \sum_{\bar{f} \in F} \sum_{b \in B_{\bar{f}}} x_{s,b,t} \right) \leq totalProdLimit \\
\forall f \in F, t: & \left( \sum_{b \in B_f} \sum_{\bar{f} \in F} \sum_{s \in S_{\bar{f}}} x_{s,b,t} \right) \leq totalConsLimit 
\end{align}
\end{itemize}

Further constraints (for certain optimization objectives):
\begin{itemize}
\item peak unmet demand:
\begin{align}
\forall t: ~\sum_{b \in B} E_b - \sum_{s \in S} \sum_t x_{s,b,t} \leq \PUD 
\end{align}
\item peak difference to ideal unmet demand:
\begin{align}
\forall t: -\PUDD \leq D_t - \left( \sum_{b \in B} E_b - \sum_{s \in S} \sum_t x_{s,b,t} \right) \leq \PUDD
\end{align}
\end{itemize}

Objective (we consider multiple formulations):
\begin{itemize}
\item maximize trading activity (i.e., amount of energy demand met using local supply):
\begin{align}
\max_{\vx} \sum_{b \in B} \sum_{s \in S} \sum_t x_{s,b,t}
\end{align}
\item minimize peak of unmet demand:
\begin{align}
\min_{\vx, \PUD} \PUD
\end{align}
\item minimize peak difference to  unmet demand:
\begin{align}
\min_{\vx, \PUDD} \PUDD
\end{align}
\end{itemize}

### 2017-10-16 docs/papers/iotdi2018/extensions.tex
added iotdi paper

\subsection{Advanced Problem Formulation}
\label{sec:extendedProblem}

In our basic problem formulation, we assumed that all buying and selling offers $\calB$ and $\calS$ are available at once, and we cleared the market in one take.
In practice, however, both the prosumers and the DSO may continuously submit new offers as their predictions, their physical state, and the market conditions change over time.
As the set of submitted offers grows, the optimal solution to the energy trading problem may change, and the optimal value of each $p_{s,b,t}$ may vary.
While each change can increase the amount of energy traded, the \emph{trade values} $p_{s,b,t}$ and $\pi_{s,b,t}$ need to be \emph{finalized} at some point in time.
At the very latest, values for interval $t$ need to be finalized by the end of interval $t - 1$; otherwise, participants would have no chance of actually delivering the trade.
Here, we extend the energy trading problem to consider a growing set of offers and a time constraint for finalizing trades.
Our approach finalizes a minimum set of trades in each interval, which maximizes efficiency while providing safety.

%Consequently, the optimal matching changes over time as new offers arrive.
%A simple approach for accommodating an evolving set of offers would be to periodically find an optimal matching, finalize the trades, and start from scratch for the next set of offers. 
%In this section, we propose a superior approach, which improves trading by matching as many offers at the same time as possible, while finalizing as few of them as possible.

We assume that all trades for time interval $t$ (i.e., all values~$p_{s,b,t}$ and $\pi_{s,b,t}$) must be finalized by the end of time interval $t - T_{clear}$, where $T_{clear}$ is a positive integer constant, which is set by the operator. 
Preventing ``last-minute'' changes can be crucial for safety and fairness since it allows both the DSO and the prosumers to prepare for delivering (or consuming) the right amount of power. %\KarlaC{Gotta be careful about making categorical statements like that. We have no evidence to support this claim. Future (experimental) work!}\AronC{Okay, we should motivate this more and emphasize that this is a tweakable parameter.}
In practice, the value of $T_{clear}$ must be chosen taking into account both physical constraints (e.g., how long it takes to turn on a generator) and communication delay (e.g., some participants might learn of a trade with delay due to network disruptions).

We let $\hat{p}_{s,b,t}$ and $\hat{\pi}_{s,b,t}$ denote the finalized trade values, and we let $\calB^{(t)}$ and $\calS^{(t)}$ denote the set of buying and selling offers that participants have submitted by the end of time interval $t$.
Then, the system takes the following steps at the end of each time interval $t$:
\begin{itemize}
\item Find an optimal solution $(\vp^*, \vpi^*)$ to the extended energy trading problem:
\begin{equation}
\max_{(\vp, \vpi) \, \in \textit{ Feasible}(\calS^{(t)}\!,\, \calB^{(t)})} \sum_{s \in \calS^{(t)}} \sum_{b \in \calM(s)} \sum_{\tau \in I(s,b)} p_{s,b,\tau}
%\max_{\substack{(\vp, \vpi) \, \in \textit{ Feasible}(\calS^{(t)}\!,\, \calB^{(t)}) \\ \text{subject to} \\ \forall \tau \leq t - T_{clear}: ~ \hat{p}_{s,b,t} = p_{s,b,t} \wedge \hat{\pi}_{s,b,t} = \pi_{s,b,t}}}
\end{equation}
subject to
\begin{align}
\forall \, \tau < t + T_{clear}\!: ~ & p_{s,b,\tau} = \hat{p}_{s,b,\tau} \\ %~\wedge~ \pi_{s,b,t} = \hat{\pi}_{s,b,t} .
& \pi_{s,b,\tau} = \hat{\pi}_{s,b,\tau} 
\end{align}
\item Finalize trade values for time interval $t + T_{clear}$ based on the optimal solution $(\vp^*, \vpi^*)$:
\begin{align}
& \hat{p}_{s,b,t + T_{clear}} := p^*_{s,b,t + T_{clear}} \\ 
& \hat{\pi}_{s,b,t + T_{clear}} := \pi^*_{s,b,t + T_{clear}} 
\end{align}
\end{itemize}

By taking the above steps at the end of each time interval, trades are always cleared based on as much information as possible (i.e., considering as many offers as possible) without violating any safety or timing constraints.
Next, we discuss how to implement the market using a blockchain-based decentralized platform.

%\AbhishekC{We should reference the earlier discussion to emphasize why we choose blockchains}

%Every $T_{match}$ ($\leq T_{clear}$) time intervals, the smart contract finalizes trades based on the solution of the matching problem.
%More specifically, at the beginning of time interval $t$, where $t$ is a multiple of $T_{match}$, the smart contract marks values $p_{s,b,\tau}$ as final for all $\tau \leq t + T_{match}$. 
%Then, the next solution for the matching contract must consider the values $p_{s,b,\tau}$ to be constant.

### 2017-10-16 docs/papers/iotdi2018/feeder.tex
added iotdi paper

% !TeX root = ICCPS18.tex

     \begin{figure}[t]
 \centering
\resizebox{0.45\textwidth}{!}{%
 \begin{tikzpicture}[rotate=270,font=\tiny,
   oc/.style={fill=black,rectangle,minimum size=0.01cm,font=\tiny},
     feeder/.style={fill=brown,rectangle,minimum size=0.005cm,font=\tiny},
   Producer/.style={fill=green,circle,minimum size=0.01cm},
     Consumer/.style={fill=red,circle,minimum size=0.01cm},
   Connection/.style={<->, >=stealth, shorten <=0.05cm, shorten >=0.05cm}]
 \draw node[oc] (oc1) at (-5,0){};
 \draw node[oc] (oc2) at (-4,0){};
 \draw node[oc] (oc3) at (-3,0){};
 \draw node[oc] (oc4)  at (-2,0){};
 \draw node[oc](oc5)  at (-1,0){};
 \draw node[oc] (oc6)  at (0,0){};
 \draw node[oc] (oc7) at (1,0){};
 \draw node[oc] (oc8)  at (2,0){};
 \draw node[oc] (oc9) at (3,0){};
 \draw node[oc] (oc10) at (4,0){};
 \draw node[oc] (oc11) at (5,0){};

 \draw node[feeder] (feeder1) at (-5,-1){};
 \draw node[feeder] (feeder2) at (-4,-1){};
 \draw node[feeder] (feeder3) at (-3,-1){};
 \draw node[feeder] (feeder4)  at (-2,-1){};
 \draw node[feeder](feeder5)  at (-1,-1){};
 \draw node[feeder] (feeder6)  at (0,-1){};
 \draw node[feeder] (feeder7) at (1,-1){};
 \draw node[feeder] (feeder8)  at (2,-1){};
 \draw node[feeder] (feeder9) at (3,-1){};
 \draw node[feeder] (feeder10) at (4,-1){};
 \draw node[feeder] (feeder11) at (5,-1){};

 \draw [Connection] (feeder1) to (feeder2);
 \draw [Connection] (feeder2) to (feeder3);
 \draw [Connection] (feeder3) to (feeder4);
 \draw [Connection] (feeder4) to (feeder5);
 \draw [Connection] (feeder5) to (feeder6);
 \draw [Connection] (feeder6) to (feeder7);
 \draw [Connection] (feeder7) to (feeder8);
 \draw [Connection] (feeder8) to (feeder9);
 \draw [Connection] (feeder9) to (feeder10);
 \draw [Connection] (feeder10) to (feeder11);

\draw [Connection] (feeder1) to (oc1);
\draw [Connection] (feeder2) to (oc2);
\draw [Connection] (feeder3) to (oc3);
\draw [Connection] (feeder4) to (oc4);
\draw [Connection] (feeder5) to (oc5);
\draw [Connection] (feeder6) to (oc6);
\draw [Connection] (feeder7) to (oc7);
\draw [Connection] (feeder8) to (oc8);
\draw [Connection] (feeder9) to (oc9);
\draw [Connection] (feeder10) to (oc10);
\draw [Connection] (feeder11) to (oc11);

 \foreach \pos in {1,2} {
   \node [Producer] (p10\pos)at (-5,\pos) {};
 }

 \foreach \pos in {3,4,5,6,7,8,9} {
   \node [Consumer] (c10\pos)at (-5,\pos) {};
 }

 \foreach \pos in {1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17} {
   \node [Consumer] (c20\pos)at (-4,\pos) {};
 }

 \foreach \pos in {1,2,3,4,5} {
   \node [Consumer] (c30\pos)at (-3,\pos) {};
 }

 \foreach \pos in {1,2,3,4,5,6,7,8,9,10,11,12,13} {
   \node [Consumer] (c40\pos)at (-2,\pos) {};
 }

 \foreach \pos in {1,2,3,4,5,6,7,8} {
   \node [Consumer] (c50\pos)at (-1,\pos) {};
 }

 \foreach \pos in {1} {
   \node [Consumer] (c60\pos)at (0,\pos) {};
 }

 \foreach \pos in {1} {
   \node [Producer] (p70\pos)at (1,\pos) {};
 }

 \foreach \pos in {2,3,4,5,6,7,8,9,10,11} {
   \node [Consumer] (c70\pos)at (1,\pos) {};
 }

 \foreach \pos in {17} {
   \node [Producer] (p80\pos)at (2,\pos) {};
 }

 \foreach \pos in {1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16} {
   \node [Consumer] (c80\pos)at (2,\pos) {};
 }

 \foreach \pos in {1,2,3,4,5} {
   \node [Consumer] (c90\pos)at (3,\pos) {};
 }

 \foreach \pos in {11} {
   \node [Producer] (p100\pos)at (4,\pos) {};
 }

 \foreach \pos in {1,2,3,4,5,6,7,8,9,10,12,13} {
   \node [Consumer] (c100\pos)at (4,\pos) {};
 }

 \foreach \pos in {1,2,3,4,5} {
   \node [Consumer] (c110\pos)at (5,\pos) {};
 }

 \draw [Connection] (oc1) to (p101);
 \draw [Connection] (p101) to (p102);
 \draw [Connection] (p102) to (c103);
 \draw [Connection] (c103) to (c104);
 \draw [Connection] (c104) to (c105);
 \draw [Connection] (c105) to (c106);
 \draw [Connection] (c106) to (c107);
 \draw [Connection] (c107) to (c108);
 \draw [Connection] (c108) to (c109);

\draw [Connection] (oc2) to (c201);
\draw [Connection] (c201) to (c202);
\draw [Connection] (c202) to (c203);
\draw [Connection] (c203) to (c204);
\draw [Connection] (c204) to (c205);
\draw [Connection] (c205) to (c206);
\draw [Connection] (c206) to (c207);
\draw [Connection] (c207) to (c208);
\draw [Connection] (c208) to (c209);
\draw [Connection] (c209) to (c2010);
\draw [Connection] (c2010) to (c2011);
\draw [Connection] (c2011) to (c2012);
\draw [Connection] (c2012) to (c2013);
\draw [Connection] (c2013) to (c2014);
\draw [Connection] (c2014) to (c2015);
\draw [Connection] (c2015) to (c2016);
\draw [Connection] (c2016) to (c2017);

\draw [Connection] (oc3) to (c301);
\draw [Connection] (c301) to (c302);
\draw [Connection] (c302) to (c303);
\draw [Connection] (c303) to (c304);
\draw [Connection] (c304) to (c305);

\draw [Connection] (oc4) to (c401);
\draw [Connection] (c401) to (c402);
\draw [Connection] (c402) to (c403);
\draw [Connection] (c403) to (c404);
\draw [Connection] (c404) to (c405);
\draw [Connection] (c405) to (c406);
\draw [Connection] (c406) to (c407);
\draw [Connection] (c407) to (c408);
\draw [Connection] (c408) to (c409);
\draw [Connection] (c409) to (c4010);
\draw [Connection] (c4010) to (c4011);
\draw [Connection] (c4011) to (c4012);
\draw [Connection] (c4012) to (c4013);

\draw [Connection] (oc5) to (c501);
\draw [Connection] (c501) to (c502);
\draw [Connection] (c502) to (c503);
\draw [Connection] (c503) to (c504);
\draw [Connection] (c504) to (c505);
\draw [Connection] (c505) to (c506);
\draw [Connection] (c506) to (c507);
\draw [Connection] (c507) to (c508);

\draw [Connection] (oc6) to (c601);

\draw [Connection] (oc7) to (p701);
\draw [Connection] (p701) to (c702);
\draw [Connection] (c702) to (c703);
\draw [Connection] (c703) to (c704);
\draw [Connection] (c704) to (c705);
\draw [Connection] (c705) to (c706);
\draw [Connection] (c706) to (c707);
\draw [Connection] (c707) to (c708);
\draw [Connection] (c708) to (c709);
\draw [Connection] (c709) to (c7010);
\draw [Connection] (c7010) to (c7011);

\draw [Connection] (oc8) to (c801);
\draw [Connection] (c801) to (c802);
\draw [Connection] (c802) to (c803);
\draw [Connection] (c803) to (c804);
\draw [Connection] (c804) to (c805);
\draw [Connection] (c805) to (c806);
\draw [Connection] (c806) to (c807);
\draw [Connection] (c807) to (c808);
\draw [Connection] (c808) to (c809);
\draw [Connection] (c809) to (c8010);
\draw [Connection] (c8010) to (c8011);
\draw [Connection] (c8011) to (c8012);
\draw [Connection] (c8012) to (c8013);
\draw [Connection] (c8013) to (c8014);
\draw [Connection] (c8014) to (c8015);
\draw [Connection] (c8015) to (c8016);
\draw [Connection] (c8016) to (p8017);

\draw [Connection] (oc9) to (c901);
\draw [Connection] (c901) to (c902);
\draw [Connection] (c902) to (c903);
\draw [Connection] (c903) to (c904);
\draw [Connection] (c904) to (c905);

\draw [Connection] (oc10) to (c1001);
\draw [Connection] (c1001) to (c1002);
\draw [Connection] (c1002) to (c1003);
\draw [Connection] (c1003) to (c1004);
\draw [Connection] (c1004) to (c1005);
\draw [Connection] (c1005) to (c1006);
\draw [Connection] (c1006) to (c1007);
\draw [Connection] (c1007) to (c1008);
\draw [Connection] (c1008) to (c1009);
\draw [Connection] (c1009) to (c10010);
\draw [Connection] (c10010) to (p10011);
\draw [Connection] (p10011) to (c10012);
\draw [Connection] (c10012) to (c10013);

\draw [Connection] (oc11) to (c1101);
\draw [Connection] (c1101) to (c1102);
\draw [Connection] (c1102) to (c1103);
\draw [Connection] (c1103) to (c1104);

 \end{tikzpicture}
 }
 \caption{Feeder diagram. Brown nodes are feeder junctions, numbered 1 to 11 from top to bottom.  Black nodes are the overcurrent relays, which ensure that the total power flowing in and out of the feeder is below 20 kW. The green nodes are the junction points for the producers ($5$), and the red nodes are junction points for the consumers ($97$). There are $102$ prosumers in total.}
 \label{fig:feeder}
 \end{figure}

\begin{figure}[t]
\centering
\begin{tikzpicture}
\begin{axis}[
  font=\footnotesize,
  width=\columnwidth,
  height=0.61\columnwidth,
  ymin=-1,
 legend columns=3, 
  legend style={font=\fontsize{5}{6}\selectfont,cells={align=left},text width=4.3em,text height=1.5ex,text depth=.5ex,row sep=0.1em},
  ymax=220,
grid=both,
    grid style={line width=.1pt, draw=gray!10},
    major grid style={line width=.2pt,draw=gray!50},
  xmin=-1,
  xmax=97,
  legend pos=north west,
  xlabel=Time,
  ylabel={[kWh]},
  ytick={0, 50, 100, 150, 200},
  xtick={0, 16, 32, 48, 64, 80, 95},
  xticklabels={0:00, 4:00, 8:00, 12:00, 16:00,  20:00, 23:45},
]
\addplot[no markers, solid, greenline, semithick] table[x expr=\coordindex, y=WithoutBattery,  comment chars={\%}, col sep=comma] {diagrams/interval-energy-traded.csv};
\addlegendentry{Total energy traded (Test A)};
\addplot[no markers, solid, blackLine, semithick] table[x expr=\coordindex, y=WithBattery5,  comment chars={\%}, col sep=comma] {diagrams/interval-energy-traded.csv};
\addlegendentry{Total energy traded (Test C)};
\addplot[no markers, solid, goldLine, semithick] table[x expr=\coordindex, y=WithBattery12,  comment chars={\%}, col sep=comma] {diagrams/interval-energy-traded.csv};
\addlegendentry{Total energy traded (Test D)};
\addplot[no markers, solid, blueLine, semithick] table[x expr=\coordindex, y=TotalProduction, comment chars={\%}] {diagrams/TotalProductionConsumption.csv};
\addlegendentry{Total production};
\addplot[no markers, solid, redLine, semithick] table[x expr=\coordindex, y=TotalConsumption, comment chars={\%}] {diagrams/TotalProductionConsumption.csv};
\addlegendentry{Total consumption};
\end{axis}
\end{tikzpicture}
\caption{Load profile (i.e., total consumption) and generation profile (i.e., total production) in kWh per 15 minute interval aggregated across the microgrid.  The graph also shows the energy traded per interval without battery, with battery and prediction window of 5 intervals, and with battery and prediction window of 12 intervals. Note that the amount of energy traded can be lower than both demand and supply at the same time because of safety constraints, which limit the amount of energy that can flow out of the producers' feeders.}
\label{fig:profile}
% \vspace{-0.2in}
\end{figure}

\begin{figure}[ht]
\begin{tikzpicture}
\begin{axis}[
  font=\footnotesize,
  width=0.94\columnwidth,
  height=0.65\columnwidth,
  ymin=-0.2,
  ymax=10,
  xmin=28,
  xmax=95,
  ylabel={Energy [kWh]},
  xtick={0, 16, 32, 48, 64, 80, 95},
  xticklabels={0:00, 4:00, 8:00, 12:00, 16:00,  20:00, 23:45},
grid=both,
    grid style={line width=.1pt, draw=gray!10},
    major grid style={line width=.2pt,draw=gray!50},
]
\addplot[mark=*, mark size=0.5, solid, blueLine, semithick] table[x= startTime, y=Energy, comment chars={\%}] {diagrams/outputTestA.csv};
\end{axis}
\begin{axis}[
  font=\footnotesize,
  width=0.94\columnwidth,
  height=0.65\columnwidth,
  ymin=-1,
  ymax=50,
  xmin=28,
  xmax=95,
  xtick={},
  xticklabels={},
  ylabel={Offer length [intervals]},
  ytick={0, 10, 20, 30, 40, 50},
  axis y line*=right,
  legend pos=north east,
]
\addlegendimage{blueLine, semithick}
\addlegendentry{Energy}
\addplot[ybar interval,redLine] table[ x=startTime,y=Availability, comment chars={\%}] {diagrams/outputTestA.csv};
\addlegendentry{Offer length}
\end{axis}
\end{tikzpicture}
\caption{Energy offered in each time interval by the first prosumer of the first feeder when using a battery (blue line). The red bars indicate the number of contiguous intervals for which the offer is valid. The total battery capacity is 90 kWh. It is assumed that the battery charges at a rate of 10 kWh per interval. Producers are assumed to keep the battery available till the end of the test, which is the 95th interval. Consequently, the red bars taper off in consecutive intervals.}
\label{fig:batteryEffect}
\end{figure}

 \begin{figure}[ht]
	\centering		\includegraphics[width=1\columnwidth]{diagrams/testbed.jpg}
	\caption{Hardware test bed.}
   \label{fig:testbed_architecture}
\end{figure}

\begin{table}[ht]    
%\setlength{\tabcolsep}{4pt}
\caption{Parameter Values for Experiments (See Table \ref{tab:symbols})}
\label{table:test-parameters}  
\centering
\begin{tabular}{lllll}
& A  & B  & C  & D     \\ \cline{2-5} 
\multicolumn{1}{l|}{$\Delta$[m]}   & 15 & 15 & 15 & 15   \\
\multicolumn{1}{l|}{$\Delta_s$ [s]}   & 5 & 5 & 5 & 5   \\
\multicolumn{1}{l|}{$\hat{\Delta}$ [s]} & 120 & 120 & 120 & 120   \\
\multicolumn{1}{l|}{$L$}          & 2,3,5,7,10,13  & 2,3,7,10  & 5  & 13    \\
\multicolumn{1}{l|}{Battery}     & no & yes & yes & yes \\
\hline
\multicolumn{1}{l|}{Figure}     & \ref{fig:multihorizon} &\ref{fig:multihorizon} & \ref{fig:allocate1NRG},\ref{fig:time},\ref{fig:profile},\ref{fig:multihorizon} &  \ref{fig:profile},\ref{fig:multihorizon} 
\end{tabular}
\end{table}

### 2017-10-16 docs/papers/iotdi2018/intro.tex
added iotdi paper

% !TeX root = ICCPS18.tex

%\scottC{the sub text in figure \ref{fig:microgrid} it is not clear. does the smart meter handle the billing or the DSO? Both?}

\section{Introduction}
%\Abhishek{I am going to use the publications of the Vermont guys - the quantised energy work to justify how we are setting up the framework}

%{\bf Emerging Trends:}
Power grids are undergoing major changes due to the
%an increase in the use of distributed energy resources (DER) and a 
rapid adoption of renewable energy resources, such as wind and solar power \cite{EIA2014,5430489}. For example, 
$4,\!143$ megawatts of solar panels were installed in the third quarter of 2016 \cite{seia}. This capacity is predicted to grow from 4\% of the total global energy production
%\AronC{4\% of what? I'm assuming total production in the US, but could be clarified.} 
in 2015 to 29\% in 2040 \cite{Randal}. Simultaneously, the battery technology costs per kWh have been dropping significantly \cite{stock2015powerful}, reaching grid parity \cite{bronski2015economics}. These trends are enabling a different vision for the future of power-grid operations: a decentralized system in which local communities are arranged in microgrids \cite{rahimi2012transactive}. In this vision, energy generation, transmission, distribution, and storage (i.e., electric vehicles or wall-mounted residential batteries) can be strategically used to balance load and demand spikes. A key feature of this vision is the support for local peer-to-peer energy trading within microgrids to reduce the load on the distribution system operators (DSO), leading to the development of Transactive Energy Systems (TES) \cite{kok2016society,cox2013structured,melton2013gridwise}. Such mechanisms 
can improve system reliability and efficiency by integrating inverter-based renewable resources into the grid and by supplying power to the local loads when the main grid is  interrupted.

\begin{figure*}[t]
\centering
\vspace{-2.25em}
\includegraphics[width=0.75\textwidth]{diagrams/ProblemSetting}
\vspace{-1.25em}
\caption{We consider a multi-feeder microgrid. A feeder has number of nodes, some of whom have the capability to sell energy. Each feeder is protected by an overcurrent relay at the junction of the common bus. The inset figure shows that a node in the network has different kinds of loads, some of which can be scheduled, making it possible for a consumer to bid in advance for those loads. The smart meter ensures proper billing per node. The blockchain network is an immutable record of all transactions and is used for scheduling energy transfers between homes in the microgrid and between homes and the DSO.%and also by the Distribution System Operator (DSO) to produce a monthly bill.
}
\label{fig:microgrid}
\end{figure*}

This new vision of decentralized peer-to-peer energy market is synergistic with the recent advances and push towards Internet of Things, as shown by Volttron \cite{katipamula2016volttron},
OpenFMB \cite{gunthersmart}, and the Resilient Information
Architecture Platform for Smart Grid (RIAPS)
\cite{eisele2017riaps,Scott2017ICCPS}. The latter is a platform developed by our extended research team, and it provides foundations for all
algorithms, isolates the hardware details from the algorithms, and
provides essential mechanisms for resource management, fault
tolerance, and security.

With the assumption of the availability of these new IoT platforms in the microgrid, we can develop appropriate transaction management platforms (TMPs) that allow  \emph{prosumers} (consumers who may also produce electricity) within a microgrid to participate freely in a local peer-to-peer energy trading market. With the advent and anticipated ubiquity of residential energy storage in the form of EVs or wall-mounted battery units \cite{Powerwall}, an important challenge is to design TMPs that allow for the efficient trade of \emph{energy futures}. However, the implementation of such TMPs remains difficult because of three integrated problems that must be addressed.

%These changes and the realization that the massive integration of renewable energy makes

% This massive integration of renewable energy  makes it difficult
% to manage\AronC{Makes it difficult to manage what? Or what does it refer to?}, especially in the presence of variable distributed energy resources \cite{7452738}. Therefore, a different vision for the future of power-grid operations is emerging: a decentralized system in which local communities are arranged in microgrids \cite{rahimi2012transactive}. In this vision, energy generation, transmission, distribution, and storage (i.e., electric vehicles or wall-mounted residential batteries) can be strategically used to balance load and demand spikes. % Furthermore, distributed assets can provide the rest of the bulk power grid with ancillary services, including regulation and frequency response and supplemental reserves \cite{7725892}. 
%  Additionally, microgrids can improve system reliability and efficiency by integrating inverter-based renewable resources into the grid and by supplying power to the local loads when the main grid is  interrupted.

%Furthering the concept of microgrids, transactive energy models have been proposed to support the next distribution system evolution \cite{kok2016society,cox2013structured,melton2013gridwise}.

%Transactive energy systems (TES) are defined as a set of market-based constructs for dynamically balancing the demand and supply across the electrical infrastructure \cite{melton2013gridwise}. \Karla{Considering the third point in next paragraph, we should emphasize trade of energy futures in this paragraph}.

%In this approach, customers on the same feeder \AronC{In our work, we also allow trading between feeders, so we might want to revise this sentence (e.g., ``customers in the same microgrid'').} (i.e. sharing a power line link) can operate in a P2P market, trading and exchanging generated energy locally. However, realization of this market is still difficult because of three integrated problems that must be addressed.

The first problem relates to ensuring the physical stability and safety of the grid apparatus, and is mainly concerned with dynamically balancing supply and demand without violating line capacity constraints. The second is a distributed systems problem, which requires ensuring that this peer-to-peer market operates in a trustworthy manner even if some of the nodes are malicious. The third problem is related to privacy. 
While non-transactive smart metering systems require sharing prosumer information only with the DSO, transactive systems need to disseminate information among the participants to enable finding trade partners.
The dissemination of trading information threatens the privacy of prosumers since it  may expose their private information to anyone in the same microgrid. 
Further,
data collected from energy transactions is expected to be more fine-grained than data collected by currently deployed smart meters \cite{Privacy2017}, and may be used to infer personal information about the market participants. For example, a participant's presence or absence at their residence might be inferable from their energy future offers (e.g., if a prosumer posts an energy selling offer, the residents are less likely to be at home).
%\textcolor{red}{For example, a smart home may
%   know that its inhabitants will go out in the evening (\emph{e.g.},
%   by looking at their calendar), and it may trade energy futures
%   accordingly in the morning.  Without adequate privacy measures,
%   these trades may reveal to other prosumers in the microgrid that the
%   inhabitants will not be at home later.  
  Note that energy futures,
  whose delivery may happen several hours after  the transaction
  is made, can play an important role in predicting and controlling
  microgrid load.  In comparison, smart metering reveals only current
  (or past) usage.

%can be used to infer private information about the households

%On the one hand, design of transactive energy systems is a decentralized power system controls problem \cite{7452738}, requiring strategic microgrid control that maintains the stability of the community and the utility. On the other hand, it is a distributed market problem where erroneous as well as malicious transactions can create a gap between demand and supply, eventually destabilizing the system.

%\Karla{Made changes to next three paragraphs. Small re-org}
In recent work \cite{Laszka17}, we have introduced {\it Privacy preserving Energy Transactions
(PETra)}, which is our distributed-ledger based solution that
(1) enables trading energy futures in a secure and verifiable
manner and (2) preserves prosumer privacy. 
Privacy in our previous work was implemented by using anonymized identifiers, a public distributed ledger, and a mixing service that prevents tracing the assets being traded back to the owner.
However, the transactive mechanism implemented in \cite{Laszka17} was opportunistic, where each consumer looked at the available asks from producers and chose the one that fit the needs of the consumer the best. In the present work, we consider an automated matching system that maximizes the amount of energy traded within the local market. Further, in the prior work, we did not consider system-wide safety constraints, only constraints on individual prosumers.

%\AronC{This paragraph seems a bit out of place.}
%In this paper, we consider a mechanism where energy is transferred at uniform power in discrete fixed-length intervals, which allows participants to plan their energy consumption and production. The company Packetized Energy \cite{packetizedenergy} has shown that selling power in discrete units is practical. However, their work requires  coordination from a centralized, trusted entity. As a result, they do not have to worry about the privacy challenges, which become apparent when we allow decentralized trades between entities.

%In the model considered in this paper, we assume that Distribution System Operators (DSOs) can act as custodians of this market, while still meeting the net demand in the microgrid \cite{7462854}. Thereafter, we consider the problem of decentralized trades, which use  the services of a distributed ledger to ensure that all events and transactions are tracked robustly through the entire system.
%However, due to a number of challenges, these services have been restricted in the present to some pilot programs like Demand/Response \cite{7462854}.

Building on our work in \cite{Laszka17}, 
we continue to use a blockchain to implement parts of our proposed TMP design. The use of blockchains (i.e. distributed ledgers) for implementations of TMPs is in line with the recent trends in the research community and industry focused on transactive energy markets \cite{Lo3Patent,PowerLedger}.
%\AbhishekC{we need more references}\Karla{added powerledger}
Although disintermediation of trust is widely regarded as the primary feature of blockchain-based transaction systems \cite{SpectrumBC}, their use in TES is appealing also because they elegantly integrate the ability to immutably record the ownership and transfer of assets, with essential distributed computing services such as Byzantine fault-tolerant consensus on the ledger state as well as event chronology. The ability to establish consensus on state and timing is important in the context of TESs since these are envisioned to involve the participation of self-interested parties, interacting with one another via a distributed computing platform that executes the transaction management. %Moreover,  records kept on blockchain systems benefit from being fully auditable, immutable, and redundantly replicated at many nodes.

%\textcolor{red}{Advantages of blockchain: 1) does not require a trusted entity 2) fully auditable 3) decentralized. These properties are necessary because in a transactive microgrid: 1) we do not necessarily have a trusted entity locally at all times (microgrid might not be continuously connected to the Internet, and we do not necessarily have a trusted hardware platform locally) 2) everyone should be able to verify that no one (not even the distribution system operator (DSO)) has cheated in trading 3) fault tolerance (platform needs to be run by multiple nodes).}

%In the paper, we should first state these requirements/constraints, and then present blockchains as the obvious best solution.

%However, those solutions do not consider the impact of the electricity market on the controller responsible for the stability of the system. Neither do they consider the challenges of privacy for the prosumers participating in the market.

%\textcolor{red}{we must declare why a blockchain based technology is interesting.}
%\Aron{Advantages of blockchain: 1) does not require a trusted entity 2) fully auditable 3) decentralized. These properties are necessary because in a transactive microgrid: 1) we do not necessarily have a trusted entity locally at all times (microgrid might not be continuously connected to the Internet, and we do not necessarily have a trusted hardware platform locally) 2) everyone should be able to verify that no one (not even the DSO) has cheated in trading 3) fault tolerance (platform needs to be run by multiple nodes). In the paper, we should first state these requirements/constraints, and then present blockchains as the obvious best solution.}

%\Karla{Although disintermediation of trust is widely regarded as the main feature of blockchain-based transaction systems, their use in applications such transactive energy is desirable also because many represent an integrated, practical alternative to PBFT algorithms used to achieve consensus on data and event chronology for boundedly asynchronous distributed systems.}

%\Aron{Do blockchains have any advantage over PBFT other than supporting public platforms?}

%In recent work \cite{Laszka17}, we have introduced {\it Privacy preserving Energy Transactions
%(PETra)}, which is our distributed-ledger based solution that
%(1) enables trading energy futures in a secure and verifiable
%manner, (2) preserves prosumer privacy, and (3) enables distribution system operators to regulate trading and enforce the safety rules\AronC{I think that we should emphasize that PETra safety rules were imposed on individual prosumers, while in this paper, we can also impose rules on feeders.}.

\noindent{\bf Contribution}: Our contributions in this paper are as follows: %We make the following contributions in this~paper:
\begin{compactitem}
\item  We co-design an automated matching mechanism and a decentralized IoT-based transaction management platform, whose goal is to support the energy trading workflow while ensuring privacy of the prosumers (i.e., their identity) and the safety of the system (i.e. satisfaction of line capacity constraints). 
This design problem is challenging because there is a direct conflict between safety, privacy, and market efficiency.

%\item We design and implement an automated  matching mechanism that ensures safety , preserves prosumers' privacy\scottC{What specifically is kept private in this case?}, and promotes local trade and market efficiency. This design problem is challenging because there is a direct conflict between safety, privacy and market efficiency.\Karla{Recommend we de-emphasize design of matching mechanism (also I removed "auction" above) since our intent is not to compete against existing market designs. I recommend we emphasize that our matching mechanism/workflow is a "co-design" aimed at facilitating implementation, and specifically implementation that ensures privacy and safety. }
\item We allow prosumers to consider the effect of energy storage in batteries by enabling them to specify multiple time intervals in which they could trade energy, which is necessary for taking full advantage of batteries.
\item We describe the architecture and the protocol specification of our platform.
%and \AronC{We could remove this.}\textcolor{red}{discuss the challenges faced while building such a platform.}
Our solution combines the security and immutability of blockchain-based smart contracts with the efficiency of traditional computational platforms.
\item 
Finally, we present an experimental evaluation of the proposed TMP and the resulting market performance, with and without the availability of prosumer-owned battery storage. We consider total energy trade throughput as the market performance metric.
%Finally, we present an experimental evaluation of the proposed system and compare the effectiveness \scottC{what is market effectiveness? Power provided/power requested?} of the market with and without battery storage.\Karla{Consider: "Finally, we present an experimental evaluation of the proposed TMP and resulting market performance, with and without the availability of prosumer-owned battery storage. We consider total energy trade throughput as the market performance metric."}
\end{compactitem}
%describe the design and implement

% \textcolor{red}{In this paper, we  extend the work to implement an optimal  decentralized future trading mechanism that preserves privacy of the individual home owners, while following the safety constraints of the system\AronC{Another novel contribution compared to PETra (and some other related work) is allowing offers to specify multiple time intervals, which is necessary for taking full advantage of batteries.}.}

% \textcolor{red}{{\bf Contribution}: We design and implement an automated auction and matching mechanism that ensures safety (i.e. satisfaction of line capacity constraints), preserves privacy, and promotes local trade and market efficiency. This design problem is challenging because there is a direct conflict between safety and privacy on the one hand, \scottC{Isn't there a tradeoff between safety and privacy as well? This makes them sound like they're together.}\AronC{I agree, there is definitely a tradeoff between privacy and safety.} and market efficiency on the other. \st{A  second contribution of our work is a demonstration of the ability of the microgrid to be used as a regulation market by the DSO. That is, the microgrid follows an aggregated time variant demand signal throughout the day. Ability to closely regulate the demand curve enables efficient pre-planning of generation resources by the DSO. }}

%\Abhishek{
\noindent{\bf Outline:}  We present our transactive microgrid model and a review of requirements in Section \ref{sec:system}.
Then, we give an overview of the state of the art in Section \ref{sec:related}.
We formalize the energy trading problem in Section~\ref{sec:problem}.
%Two versions of the problem formulation are presented in sections \ref{sec:4a}, \ref{sec:4b} and \ref{sec:extendedProblem}. 
Our solution approach is described in Section \ref{sec:solution}. The implementation architecture is summarized in Section \ref{sec:tradingsystem}. We present results and discussions in Section \ref{sec:results}. Finally, we conclude the paper in Section \ref{sec:conclusion}.

% \begin{itemize}
% \item What is transactive microgrid. Why is it important and what are they key challenges. Describe existing transactive energy demonstrations.
% \item Describe the key architectural and algorithmic advances that have taken place already. And what are the missing gaps.
% \begin{itemize}
% \item Most works do not address trades of futures (i.e. Basar). If they do, the setting is simplistic in not considering offers that involve a logical ``or'' (i.e. allowing a participant to indicate the ability to provide or consume a certain level of power within \emph{any one} of a set of time slots), which limits market efficiency. 
% \end{itemize}
% \item Describe the problem being addressed, and motivate. (precise definition later)
% \begin{itemize}
% \item Design and implement an automated auction and matching mechanism that ensures safety (i.e. satisfaction of line capacity constraints), preserves privacy and promotes local trade and market efficiency. 
% \item This problem is interesting and challenging because there is a direct conflict between safety and privacy, and market efficiency. 
% \end{itemize}
% \item What have we done in the past and is this paper about. What are they results and lessons learned
% \begin{itemize}
% \item we introduced the problem formulation, 
% \item A second contribution of our work is demonstration of the ability of microgrid to be used as a regulation market by the DSO. That is, the microgrid follows an aggregated time variant demand signal throughout the day. Ability to closely regulate the demand curve enables efficient pre-planning of generation resources by the DSO.
% \end{itemize}
% \item What is the outline of the paper.
% \end{itemize}

% = All homes can be classified into feeder sets: F, Feedermembership function M:F\rightarrow 2^N maps the set of homes into feeders. Mp:F\rightarrow 2^P
% = For each feeder there exists an over current protection unit that sets the limit of total current flowing through the feeder. The limit is specified in terms of Integers (smart contract cannot do floats) L:F\rightarrow Z+.
% ==Each prosumer has the instantenous energy transfer, planned energy transfer written in terms of power. Controlling how much power is exchanged for how long controls the net energy transferred.
% === This limit puts a net constraint on total power being exchanged at any given time through the feeder. Thus 
% \sum_{DSO(f,t)+ \sum_{Mp(f,t)}} \leq l(f)

### 2017-10-16 docs/papers/iotdi2018/problem.tex
added iotdi paper

% !TeX root = ICCPS18.tex
\section{Energy Trading Problem}
\label{sec:problem}

\newcommand{\vect}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\ve}{\vect{e}}
\newcommand{\vp}{\vect{p}}
\newcommand{\vpi}{\vect{\pi}}

\newcommand{\calB}[0]{\ensuremath{\mathcal{B}}}
\newcommand{\calF}[0]{\ensuremath{\mathcal{F}}}
\newcommand{\calM}[0]{\ensuremath{\mathcal{M}}}
\newcommand{\calS}[0]{\ensuremath{\mathcal{S}}}

In this section, we formulate the problem of matching energy future bids with asks (i.e., offers to buy energy to be delivered in the future with offers to sell energy) in the local energy trading market. Our formulation aims to promote market efficiency by maximizing the amount of energy futures traded within the microgrid, while satisfying microgrid safety requirements. We first introduce an initial problem formulation, in which we assume that all offers are available at the same time, and we clear the market at once.  Then, we describe the generalized version of the problem, in which we consider a stream of incoming offers, which are cleared periodically. % while ensuring that no two participants can know the exact identity of their peers later.

\subsection{Safety Requirements}

While these trades are being cleared, we must consider \emph{safety requirements}.  
 At the distribution level, the amount of power that can be sent over a transmission line is typically limited by the thermal properties of the conductor, and it is physically enforced by protection equipment such as overcurrent relays. In traditional power systems, these capacity constraints are logically enforced by deploying some combination of load and generation curtailment schemes. Such schemes effectively impose upper bounds on the amount of power consumed by each load and the amount of power injected into the network by each source. For dispatchable generation, these upper bounds are typically calculated by solving some variant of an optimal power flow problem \cite{OPFtutorial}.

Since the setting of TES is fundamentally different from settings in which economic dispatch is appropriate (i.e. privately-owned DERs are not dispatchable by the DSO), we implement line capacity safety constraints by formulating them as constraints in the trading problem described below.

\subsection{Problem Formalization}

\begin{table}
\caption{List of Symbols}
\centering
\label{tab:symbols}
\renewcommand*{\arraystretch}{1.2}
\begin{tabular}{|l|p{5.8cm}|}
\hline
Symbol & Description \\
\hline
\multicolumn{2}{|c|}{Microgrid} \\
\hline
$\calF$ & set of feeders \\
\rowcolor{TableRowGray} $C_f^{ext}$ & maximum net power consumption or net power production in feeder $f \in \calF$ \\
$C_f^{int}$ & maximum total power consumption or total power production in feeder $f \in \calF$ \\
\rowcolor{TableRowGray} $\Delta$ & length of time intervals \\
$T_{clear}$ & minimum number of time intervals between the finalization and delivery of a trade \\
\hline
\multicolumn{2}{|c|}{Offers} \\
\hline
\rowcolor{TableRowGray} $\calS_f$ & set of selling offers from feeder $f \in \calF$ \\
$\calB_f$ & set of buying offers from feeder $f \in \calF$ \\
\rowcolor{TableRowGray} $\calS$, $\calB$ & set of all selling and buying offers, resp. \\
$\calS^{(t)}$, $\calB^{(t)}$ & set of selling and buying offers submitted by the end of time interval $t$, resp. \\
\rowcolor{TableRowGray} $E_s$, $E_b$ & amount of energy to be sold or bought by offers $s \in \calS$ and $b \in \calB$, resp. \\
$I_s$, $I_b$ & time intervals in which energy could be provided or consumed by offers $s \in \calS$ and $b \in \calB$, resp. \\
\rowcolor{TableRowGray} $R_s$, $R_b$ & reservation prices of offers $s \in \calS$ and $b \in \calB$, resp. \\
$\calM(s)$, $\calM(b)$ & set of offers that are matchable with offers $s$ and~$b$, resp. \\
\rowcolor{TableRowGray} $I(s, b)$ & $I_s \cap I_b$ \\
\hline
\multicolumn{2}{|c|}{Solution} \\
\hline
$p_{s,b,t}$ & amount of energy that should be provided by $s$ to $b$ in interval $t$ \\
\rowcolor{TableRowGray} $\pi_{s,b,t}$ & unit price for the energy provided by $s$ to $b$ in interval~$t$ \\
$\textit{Feasible}(\calS, \calB)$ & set of feasible solutions given sets of selling and buying offers $\calS$ and $\calB$ \\
\rowcolor{TableRowGray} $\hat{p}_{s,b,t}$, $\hat{\pi}_{s,b,t}$ & finalized trade values \\
\hline
\multicolumn{2}{|c|}{Implementation Parameters} \\
\hline
$L$ & prediction window used by prosumers when posting selling and buying offers ($\min(L) = 2$) \\
\rowcolor{TableRowGray} $\hat{\Delta}$ &  length of the time step used for simulating the real-interval of length $\Delta$ \\
$\Delta_s$ & periodicity of solver that matches offers \\
\hline
\end{tabular}
\end{table}

We begin by introducing notation for elements of the microgrid.
For a list of symbols used in this paper, see Table~\ref{tab:symbols}.
We let $\calF$ denote the set of feeders.
For a feeder $f \in \calF$, we let $C_f^{ext}$ denote the maximum amount of power that is allowed to flow into or out of the feeder at any point in time. 
Similarly, we let $C_f^{int}$ denote the maximum amount of power that is allowed to be consumed or produced within the feeder at any point in time.\footnote{In other words, limit $C_f^{ext}$ is imposed on the net production and net consumption of all prosumers in feeder $f$, while limit $C_f^{int}$ is imposed on the total production and total consumption.} 
We assume that time is divided into intervals of fixed length~$\Delta$, and we refer to the $t$th interval simply as time interval $t$.

The input of the energy trading problem is the set of buying and selling offers posted by the participants.\footnote{Participants may include both prosumers and the DSO. The DSO can shape load and trade energy futures by participating in the energy market the same way as prosumers do.}
%
For feeder $f \in \calF$, we let $\calS_f$ and $\calB_f$ denote the set of selling and buying offers posted by participants located in that feeder, respectively.\footnote{If the DSO wants to participate in this energy trading market, it can be assigned to a ``dummy'' feeder in the problem formulation.} 
A selling offer $s \in \calS_f$ is a tuple $\left(E_s, I_s, R_s\right)$, where
\begin{itemize}
\item $E_s$ is the amount of energy to be sold,
\item $I_s$ is the set of time intervals in which the energy could be provided,
%\KarlaC{A time interval is different from the index of a time interval. I recommend we emphasize that $I$ denotes a set of indices that identify time intervals in question. See below for reason.}
%\AronC{I don't see why this needs to be emphasized, we only ever use discrete time. In any case, there is a one-to-one correspondence between time intervals and their indices.}
%\KarlaC{It needs to be emphasized because it does not mean the same thing}
\item $R_s$ is the reservation price, i.e., lowest unit price for which the participant is willing to sell energy. %\AbhishekC{We should clarify why our results do not include pricing experiments. We can mention that this is because of lack of real-data. However, it is clear that the formulation will work for that.}\AronC{Done (in experiments section)}
\end{itemize}
Similarly, a buying offer $b \in \calB_f$ is a tuple $\left(E_b, I_b, R_b\right)$, where the values pertain to consuming/buying energy instead of producing/selling, and $R_b$ is the highest price that the participant is willing to pay.
For convenience, we also let $\calS$ and $\calB$ denote the set of all buying and selling offers (i.e., we let $\calS = \cup_{f \in \calF} \calS_f$ and $\calB = \cup_{f \in \calF} \calB_f$).

We say that a pair of selling and buying offers $s \in \calS$ and $b \in \calB$ is \emph{matchable} if
\begin{align}
R_s \leq R_b \\
I_s \cap I_b \neq \emptyset .
\end{align}
In other words, a pair of offers is matchable if there exists a price that both participants would accept and a time interval in which the seller and buyer could provide and consume energy.
For a given selling offer $s \in \calS$,
we let the set of buying offers that are matchable with $s$ be denoted by $\calM(s)$.
Similarly, we let the set of selling offers that are matchable with a buying offer $b$ be denoted by $\calM(b)$.
Further, we let $I(s, b) = I_s \cap I_b$.

A solution to the energy trading problem is a pair of vectors $(\vp, \vpi)$, where
\begin{itemize}
\item $p_{s,b,t}$ is a non-negative amount of power that should be provided by the seller $s \in \calS$ and consumed by the buyer $b \in \calM(s)$ in time interval $t \in I(s, b)$.\footnote{We require the both the seller and buyer to produce a constant level of power during the time interval.}
%     \KarlaC{we should distinguish between $t$, which normally denotes an instant of time, and a time interval itself. I recommend we use $k$ to index the time intervals and $t$ to refer to time instances within intervals, if needed. So, for example, $E_s$ energy is transferred in the $k$th interval means that $P(t)=\tfrac{E_s}{\delta}$, for all $t\in [k\delta, (k+1)\delta)$. }
%     \AronC{Sure, we can switch to using $k$ for time intervals. I don't think that we ever specify instances of time, so $t$ will be unused}
%     \AbhishekC{Also note that all participants have synchronized intervals. Thus, they will never have to sell or buy anything a time segment that is smaller than an interval.}
\item $\pi_{s,b,t}$ is the unit price for the energy provided by seller $s \in \calS$ to buyer $b \in \calM(s)$ in time interval $t \in I(s, b)$.
\end{itemize}

A pair of vectors $(\vp, \vpi)$ is a feasible solution to the energy trading problem if it satisfies the following constraints:
\begin{itemize}
\item The amount of energy sold or bought from each offer is at most the amount of energy offered:
\begin{align}
\forall s \in \calS: ~ \sum_{b \in \calM(s)} \sum_{t \in I(s,b)} p_{s,b,t} \cdot \Delta \leq E_s \label{eq:constrEnergyProd} \\
\forall b \in \calB: ~ \sum_{s \in \calM(b)} \sum_{t \in I(s,b)} p_{s,b,t} \cdot \Delta \leq E_b \label{eq:constrEnergyCons} 
\end{align}
\item The amount of power flowing into or out of each feeder is below the safety limit in all time intervals:
%\KarlaC{Note, a reviewer might object: the amount of power sold / bought is not an indicator of actual power flows between feeders... because electrons don't care about transactions... Consider adding explanation...}
%\AronC{I think that we need to make it clear earlier that the trading system can only tell participants what they should do, but it cannot force them to do anything. By this point, I think that the reader will understand that we are proposing a market clearing mechanism, not a power flow controller.}
%\KarlaC{I don't think this needs to even be pointed out, since it is obvious that actual power injection and consumption need not match the transaction amounts, for a number of different reasons. My point was not about whether or not participants do what they say they will, but the formulation itself, assuming that participants do exactly what they say they will. I think we should leave it as is right now, but somehow I am not completely convinced that limiting the difference between the total power sold to other feeders and the total power bought from other feeders implies that the actual power flows between the feeders will satisfy line capacity constraints... No time to think of a counterexample now. Also, I disagree with your last statement - The fact that we are even considering line constraints puts our proposed solution into the intersection of market and control design.}
%\KarlaC{One way to think about this: first calculate the net deficit or surplus in each feeder (you can use the transformation I proposed earlier with calculating $s$ and $b$ from $X$). Net surplus won't go anywhere unless there is demand for it in another feeder.... }
%\AronC{That is exactly what the formulae below calculate, the net production (sum production minus sum consumption) for each feeder.}
\begin{align}
\forall f \in & \, \calF, t: \nonumber \\ 
& \left( \sum_{s \in \calS_f} \sum_{b \in \calB} p_{s,b,t} \right) - \left( \sum_{b \in \calB_f} \sum_{s \in \calS} p_{s,b,t} \right) \leq C_f^{ext} \label{eq:constrExtProd} \\
\forall f \in & \, \calF, t: \nonumber \\
& \left( \sum_{s \in \calS_f} \sum_{b \in \calB} p_{s,b,t} \right) - \left( \sum_{b \in \calB_f} \sum_{s \in \calS} p_{s,b,t} \right) \geq -C_f^{ext} \label{eq:constrExtCons} 
\end{align}
\item The amount of energy consumed and produced within each feeder is below the safety limit in all time intervals:
\begin{align}
\forall f \in \calF, t: ~ \sum_{b \in \calB_f} \sum_{s \in \calS} p_{s,b,t} \leq C_f^{int} \label{eq:constrIntCons} \\
\forall f \in \calF, t: ~ \sum_{s \in \calS_f} \sum_{b \in \calB} p_{s,b,t} \leq C_f^{int} \label{eq:constrIntProd} 
\end{align}
\item The unit prices are between the reservation prices of the seller and buyer:
\begin{align}
\forall s \in \calS, b \in \calM(s), t \in I(s,b): ~ R_s \leq \pi_{s,b,t} \leq R_b \label{eq:constrPrice} 
\end{align}
\end{itemize}

The objective of the energy trading problem is to maximize the amount of energy traded.
Formally, an optimal solution to the energy trading problem is
\begin{align}
\max_{(\vp,\vpi) \, \in \textit{ Feasible}(\calS, \calB)} ~
\sum_{s \in \calS} \sum_{b \in \calM(s)} \sum_{t \in I(s,b)} p_{s,b,t} \, , 
\end{align}
where $\textit{Feasible}(\calS, \calB)$ is the set of feasible solutions given selling and buying offers $\calS$ and $\calB$ (i.e., set of solutions satisfying Equations~\eqref{eq:constrEnergyProd} to \eqref{eq:constrPrice} with $\calS$ and $\calB$).

\input{extensions.tex}

### 2017-10-16 docs/papers/iotdi2018/resultsandtestbed.tex
added iotdi paper

% !TeX root = ICCPS18.tex
\section{Experimental Evaluation and Discussions}
\label{sec:results}

We consider a collection of load traces recorded by Siemens from a microgrid in Germany, containing $102$ homes across $11$ feeders ($5$ producers and $97$ consumers). %Table \ref{tab:prosumers}
Figure~\ref{fig:feeder} describes the feeder structure, the number of participants per feeder, and  the feeder safety limits. We use $\Delta =15$ minute intervals, resulting in a total of $96$ intervals across the whole day.   Figure~\ref{fig:profile} shows the total production and consumption across this microgrid. The horizontal axis shows the starting time for each of the $96$ intervals. 
\AronC{I added this to address the lack of prices in our }
Since the dataset does not include prices, we assume reservation prices to be uniform in our experiments, and focus on studying the amount of energy traded and the performance of the system.

As one of our primary contributions in this work is the ability to specify multiple time intervals for  selling offers, we extended the trace that was collected by Siemens to allow each producer to have a battery with a total capacity of $90$ kWh. With a battery, a producer can take the energy produced in  a time interval and decide to make it available in future time intervals.
Note that the resulting offers always span a contiguous set of time intervals, so they can be specified by their starting time and length. 
Figure \ref{fig:batteryEffect} shows these intervals for one particular producer. The producers charge their batteries only when the total consumption is less than the total production, which happens just after 12:00 PM, see Figure~\ref{fig:profile}.

\input{feeder}

\begin{figure}[ht]
\begin{tikzpicture}
\begin{axis}[
  font=\footnotesize,
  width=\columnwidth,
  height=0.61\columnwidth,
  ymin=2865,
  ymax=2975,
  ytick={2875,2900,2925,2950},
  xtick={2,3,5,7,10,13},
  legend pos=north west,
  xlabel={Prosumer prediction window [time intervals]},
  ylabel={Total energy traded [kWh]},
grid=both,
    grid style={line width=.1pt, draw=gray!10},
    major grid style={line width=.2pt,draw=gray!50},
]
\addplot[mark=o, color=blueLine, only marks, thick] table[x=predictionWindow, y=withoutBattery, comment chars={\%}, col sep=comma] {diagrams/total-energy-traded.csv};
\addlegendentry{without battery};
\addplot[mark=+, color=redLine, only marks, thick] table[x=predictionWindow, y=withBattery, comment chars={\%}, col sep=comma] {diagrams/total-energy-traded.csv};
\addlegendentry{with battery};
\end{axis}
\end{tikzpicture}
\caption{Total amount of energy traded in the entire microgrid with and without batteries, for various prediction window lengths.}
\label{fig:multihorizon}
\end{figure}

\begin{figure}[t]
	\centering
\includegraphics[width=1\columnwidth]{diagrams/prosumer101.pdf}
	\caption{Energy generated in each interval (blue line) and energy traded to a set of consumers in each interval (vertical bars) for the first prosumer of the first feeder (Test case C). The stacked colors show the different consumers that were matched with the prosumer in each interval (note that the same color across multiple intervals does not necessarily mean the same consumer). When the energy traded exceeds the generation, the excess is drawn from the battery.}
	\label{fig:allocate1NRG}
\end{figure}

\begin{figure}[htb]
	\centering
    \begin{tikzpicture}
    	\begin{axis}[
	width=\columnwidth,
	height=0.5\columnwidth,
	bar width=0.04\textwidth,
    font=\footnotesize,
    grid=both,
    grid style={line width=.1pt, draw=gray!10},
    major grid style={line width=.2pt,draw=gray!50},
	ybar,
	ytick={0, 5, 10, 15, 20},
	%yticklabels={40, 60, 90, 135},
	xlabel style={align=center},
	xlabel={Real time [seconds]},
	ylabel={Number of Offers},
	symbolic x coords={0,1,2,3,4,5},
	xticklabels={{[11, 23]}, {(23, 35]}, {(35, 47]}, {(47, 59]}, {(59, 71]}, {(71, 84]}},
	xtick=data,
	ylabel style={align=center},
	]
\addplot[fill=blueFill] coordinates { 
		(0, 20)
		(1, 20)
		(2, 12)
		(3, 5)
		(4, 1)
		(5, 1)
	};
	\end{axis}
\end{tikzpicture}
%\includegraphics[width=1\columnwidth]{diagrams/timechart.pdf}
	\caption{Real time in seconds between posting an offer and recording a trade that includes the offer (Test case C). This time includes the communication delay, the time to mine the blockchain, and the running time required to find a solution. Since the solver runs periodically and receives offers asynchronously, there might be a few runs before a suitable match is found.}
	\label{fig:time}
\end{figure}

%\textcolor{red}{Table ... describes our data conversion rules.}

\subsection{Test Bed}
The hardware test bed is a cluster of 31 BeagleBone Black~\footnote{https://beagleboard.org/black} (BBB)  single-board computers (see Figure~\ref{fig:testbed_architecture}) acting as participants in the energy trading system. The BBBs are set up as light clients because they are resource constrained and therefore are not suitable for mining or acting as solvers. This means that they can safely access the blockchain but do not participate in the consensus process.  In the dataset provided by Siemens, there are 95 consumers and 7 producers of power,  see Figure \ref{fig:components}. These participants are divided between the BBBs in the cluster. The  PlaTIBART (Platform for Transactive IoT Blockchain Applications with Repeatable Testing platform) \cite{platibart}  platform provided us with the necessary devops support.

The block mining is provided by external hardware, locally or in a cloud server. We had a single miner instance that was responsible for maintaining the blockchain, and a single solver instance that used CPLEX \cite{cplex2009v12} to solve the energy trading problem. This setup can be easily scaled to add more miners and solvers if there are enough computational resources available. The communication between the components was implemented using ZeroMQ, which is one of the communication protocols available in RIAPS.

%To evaluate our approach, we use a decentralized blockchain testbed that has been established in our lab. The  PlaTIBART (Platform for Transactive IoT Blockchain Applications with Repeatable Testing platform) \cite{platibart}  platform provided us with the necessary devops support to start the trading processes for all $102$ homes in the system, see Figure \ref{fig:components}.

\subsection{Experiments}
Table~\ref{table:test-parameters} describes the specifics of the four categories of tests that we ran. The tests vary the different implementation parameters (see Table \ref{tab:symbols} and Section~\ref{sec:implementation}). This allows us to study how changing these parameters affects the total amount of energy traded.

Figure \ref{fig:multihorizon} shows the total energy traded for different tests. We varied the prediction window ($L$) for the participants from $2$ to $13$. That is, in each interval, the participants submitted offers starting from the next $1$ to $12$ intervals (current interval is always counted in the prediction window). The experiment simulated the whole day from the first interval starting at 0:00 (12:00 AM) to the $95^{th}$ interval ending at 23:59 (11:59 PM). % in the next night.
%
As expected, increasing the prediction window without batteries has no effect on the total amount energy traded. This is because any production must be dispatched within one time interval, so the solver cannot optimize energy usage across multiple intervals even if future offers are available. % So, the solver can never use the energy from a previous interval in a producer to provide energy to a consumer in a subsequent interval.

However, this is possible if there are batteries in the system. With batteries, the amount of energy traded increases as we allow the solver to match offers across multiple time intervals at once. Trading increases with the prediction window because of the increased analysis space available to the solver.
Figure~\ref{fig:profile} shows the  per interval trades for three of these cases (A, C, and D): without battery, with battery and $L=5$, as well as with battery and $L=13$.

Figure \ref{fig:allocate1NRG} shows the energy matched per interval in test case~C for the first prosumer of the first feeder. Figure \ref{fig:time} shows a histogram of the time between posting an offer and recording a trade on the blockchain that includes the offer (also in test case C). The time length was always less than $\hat{\Delta}$, which was $120$ seconds (see Table \ref{table:test-parameters}).
\ifShowLog
Figure \ref{fig:log} shows an extract of raw log messages from the system that were used to produce this chart.
\fi

\ifShowLog
\definecolor{keywords}{HTML}{8A4A0B}
\definecolor{background}{HTML}{EEEEEE}
\definecolor{comments}{HTML}{868686}

\lstdefinelanguage{log}{
 morekeywords={ prosumer,  INFO, Postingoffers, SellingOfferPosted, TradeAdded, solutionID, time, objective, buyerID, power, energy, sellerID},
 keywordstyle=\color{keywords},
 basicstyle=\scriptsize\ttfamily,
 morecomment=[l]{//}, 
 morecomment=[s]{/*}{*/}, 
 morestring=[b]",
 basicstyle=\scriptsize\ttfamily,%
 commentstyle=\color{comments}\ttfamily,
numbers=none,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
breaklines=true,
    frame=tb,
 tabsize=4}

 \begin{figure}
 \begin{lstlisting}[language=log,numbers=none]
2017-10-12 03:27:05,122 / prosumer 101 / INFO: Posting offers for interval 28...
...
2017-10-12 03:27:05,123 / prosumer 101 / INFO: postSellingOffer(101, 28, 28, 100)
...
2017-10-12 03:27:19,973 / prosumer 101 / INFO: SellingOfferPosted({'endTime': 28, 'ID': 6, 'startTime': 28, 'prosumer': 101, 'energy': 100}).
...
2017-10-12 03:27:38,131 / prosumer 101 / INFO: TradeAdded({'solutionID': 1, 'time': 28, 'objective': 5400, 'buyerID': 133, 'energy': 100, 'sellerID': 6}).
...
 \end{lstlisting}
 \caption{Example log output from prosumer 101. The \texttt{postSellingOffer} call happens when the prosumer posts the selling offer. At the same time, there are prosumers who have posted the buying offer. The smart contract records the offer and the event \texttt{SellingOfferPosted} is generated. We see the \texttt{TradeAdded} event when the solution has been generated by the solver and certified by the smart contract. The objective is the total energy traded. All values have been scaled by $1000$ to account for the problem that the current Ethereum smart contract cannot handle floating-point numbers. Thus the actual objective value is $5.4$ kWh.\textcolor{red}{take out this figure if space is needed}}
 \label{fig:log}
 \end{figure}
\fi

\subsection{Discussion}

\Abhishek{The discussion should include reinforcement about the privacy aspect. it should also explain how using blockchains enables us to handle malicious actors. we should discuss why decentralization is better for resilience.}

\Abhishek{Describe the lessons learned as an itemized list}

We conclude our evaluation by providing a brief discussion of how our platform satisfies the requirements listed in Section~\ref{sec:requirements} (see Table~\ref{tab:discussion} for a summary).
First, the communication architecture is provided by Ethereum and our middleware RIAPS.
Our performance results in Figure~\ref{fig:time} demonstrate that our platform can process and match trades much faster than what would typically be required in practice (Section~\ref{sec:implementation}).
Second, we enforce feeder-level operational safety and stability constraints on trading using a blockchain-based smart contract (Section~\ref{sec:hybridSolver}).
These are in addition to the prosumer-level constraints enforced by tracking energy assets~(Section~\ref{sec:privacy}, \cite{Laszka17}).
Third, we ensure market efficiency and security by enabling the smart contract to validate and evaluate the trading solutions that it receives (Section~\ref{sec:hybridSolver}).
Finally, we provide privacy for prosumers by allowing them to hide their identity using anonymous addresses (Section~\ref{sec:privacy} and~\cite{Laszka17}). However, prosumers are required to reveal which feeder they belong to in order to enable enforcing feeder-level safety constraints.

\begin{table}[h]
\caption{Requirements and Proposed Solutions}
\label{tab:discussion}
\centering
\setlength{\tabcolsep}{0.3em}
\renewcommand*{\arraystretch}{1.3}
\begin{tabular}{|p{2.6cm}|p{5.75cm}|}
\hline
Requirement & Proposed Solution \\
\hline
\hline
Communication Fabric & RIAPS~\cite{riaps} and Ethereum \\
\hline
Operational Safety and Stability & feeder-level constraints modeled in the energy trading problem and enforced by the smart contract (Section~\ref{sec:hybridSolver}); prosumer-level constraints enforced by energy asset tracking~(Section~\ref{sec:privacy}, \cite{Laszka17}) \\
\hline
Market Efficiency and Security & objective modeled in the energy trading problem and enforced by the smart contract (Section~\ref{sec:hybridSolver})\\
\hline
Privacy & anonymous addresses~(Section~\ref{sec:privacy}, \cite{Laszka17}) \\
\hline
\end{tabular}
\end{table}

During the design and evaluation of our platform, one of the main challenges was the conflict between safety, privacy, and efficiency.
For example, the enforcement of feeder-level safety constraints required prosumers to reveal their feeder during trading, instead of staying completely anonymous.
Further, feeder-level safety constraints can also prevent meeting energy demand with local supply, even if there is surplus production in the microgrid (Figure~\ref{fig:profile}).

### 2017-10-16 docs/papers/iotdi2018/setting.tex
added iotdi paper

% !TeX root = ICCPS18.tex

%\vspace{-0.2in}
\section{System Model}
\label{sec:system}
We consider a microgrid with a set of feeders arranged in a radial topology.\footnote{The methods developed in this paper are extensible to more general tree topologies involving branching. We work with a radial topology to simplify our notation.} 
A feeder has a fixed set of nodes, each representing a residential load or a combination of load and distributed energy resources (DERs) such as rooftop solar and batteries, as shown in Figure~\ref{fig:microgrid}.
Each node is associated with a participant in the local peer-to-peer energy trading market. There is a distribution system operator (DSO) that also participates in the market, and may thus use the market to incentivize timed energy production within the microgrid to aid in grid stabilization and promotion of related ancillary services \cite{7462854}. In addition, the DSO supplies residual demand not met through the local market.
%Figure \ref{fig:commonsequence} describes a typical trading scenario. 
The participants settle trades in advance, which allows them to schedule their transfer of power into the local distribution system. Alternatively, a mechanism can be responsible for matching the producers and consumers. There are typically three phases in these operations: discovery of compatible offers, matching of buying offers to selling offers (it can be made either by each prosumer individually or by an automated matching mechanism). Once the matching is done, the energy transaction and the financial transaction are then handled at a later time.

% We assume that Distribution System Operators (DSOs) can act as custodians of this market, while still meeting the net demand in the microgrid \cite{7462854}.

% \begin{figure}[ht]
% \centering
% \includegraphics[width=0.5\textwidth]{diagrams/TE.png}
% \caption{A conceptual sequence of activities in a transactive energy system.  %The buyer and seller agree on the trading terms. Then, they do the actual energy transaction.
% %which must be validated.
% %Thereafter, the financial assets are transferred.
% %The red arrows show off-block chain communication and blue arrows show transactions on block-chain. Producers and consumers request the DSO to allocate the energy production and consumption assets to blockchain. The consumers receive asynchronous notification about offers from producers. Thereafter, they can finalize transaction. The energy transfer happens at a later time and is also recorded in the chain. Financial transactions are also done on the blockchain. These financial transactions are later tallied with the energy transactions.\Abhishek{Aron Lets recaption the figure
% }\label{fig:commonsequence}
% \end{figure}

%\AronC{In the problem formulation, we use ``participants'' to refer to all market participants, including the DSO.}. In this formulation, we ignore reactive power.

% \subsection{Transactive Energy Workflow}

% \label{sec:petra}
% %\textcolor{red}{There will be a figure here.}

% \Abhishek{This section should describe a typical transactive energy workflow}
% \AronC{In that case, we could keep Fig.~\ref{fig:petrasequence} and present it as an illustration of a typical workflow.}

%The key aspect of this pattern is the tight integration of distributed  messaging patterns between actors and the blockchain-based communication network used for transferring transactional information. For example, in the transactive energy domain,  
%\Karla{Unfinished sentence}

% In  \cite{Laszka17}, we introduced the key concept of privacy-preserving energy transactions where a consumer selects the producers to trade with. In this basic sequence, the smart contract is  responsible for keeping track of the energy and financial assets enabling producers to post trade offers and exchange assets when a consumer decides to accept. PETra uses quantized energy asset tokens
% %\footnote{There are two kinds of energy tokens: Energy Production Asset and Energy Consumption Asset. Token attributes include power and time interval for which the token is valid.} 
% that can represent the non-negative amount of power to be produced or consumed (for example, measured in watts),  the time interval in which energy is to be produced (or consumed), and the  last time interval in which energy is to be produced (or consumed) (Figure \ref{fig:petrasequence} describes the full sequence of activity)\AronC{Figure \ref{fig:petrasequence} is not an accurate representation of PETra or the Middleware'17 sequence!}.\AbhishekC{Aron please remove this figure and update the sequence} These assets are withdrawn and submitted to anonymized accounts on behalf of prosumers by the DSO, who is also responsible for validating that the specific prosumer has the  energy capacity for feasible trades given the assets. Once the DSO posts the assets into the blockchain, prosumers can trade between themselves using these quantized assets and anonymized addresses, hiding their identity from each other. The DSO is also responsible for releasing and managing the transfer of currencies, which are represented by financial assets, which is  simply an unsigned integer value, denominated in a fiat currency. In this workflow, there are both on- and off-blockchain communications between DSO and prosumer. The off-blockchain communication is required to request the transfer of assets. On-blockchain communication occurs via filters that track the posting of assets. Similarly, prosumers also communicate which each other via blockchain to indicate when an offer has been posted and when a transaction has cleared.

% \Abhishek{We need to introduce  the energy trading problem using this figure}

%\item Participates in a wholesale market to supply residual demand

% \begin{itemize}
% \item 
% %\item We consider a microgrid consisting of a set

% \Abhishek{We assume that the DSO manages the necessary reactive power balance via local capacitor banks in this setup. Note that in a generalized problem, we will have to consider that the prosumers can control reactive power generation via power electronics. A related paper is \\cite\{Kotur2016\}}
% \item  The limit is specified in terms of integers (smart contract cannot do floats). 
% %\Karla{Consider the alternative formulation above}

% %\item Feeder $f$ has a maximal carrying capacity of $C_f$ Watts. This carrying capacity is enforced using a over-current protection unit that sets the limit of total current flowing through the feeder. The limit is specified in terms of Integers (smart contract cannot do floats). 
% \Karla{We need to make sure we are consistent about the meaning of $C_f$ - power or energy? We should make sure we are consistent with the literature}
% \Abhishek{The feeders are rated with instantaneous power.}
% \Aron{I would avoid mentioning implementation details here (e.g., representing certain numbers as integers due to lack of built-in support for floats).
% Regarding the energy/power question, they are interchangeable as long as we fix the time interval (which we do in most cases).}

% \item There is a DSO that operates the microgrid and has the following abilities and responsibilities:
% \begin{itemize}
% \item Controls the participants' access to the local market
% \item Participates in the futures market to shape the prosumers' consumption and production
% \item Participates in a wholesale market to supply residual demand
% %\item Incentivizes appropriate levels of trade activity in order to shape the overall microgrid load profile
% %\Karla{@Abhishek: does DSO do this by setting prices alone? What are it's ``acutators'' in the market? Do we want to consider some sort of load curtailment scheme in addition to the market?}
% %\Abhishek{I dont think we are talking about incentives in this paper. So, we can ignore this. The optimization problem itself includes a term for matching the load profile.}
% \end{itemize}
% \end{itemize}

%\subsection{Requirement Analysis}\label{sec:requirements}
%\Abhishek{I copied this over from Middleware paper. We need to keep the things that are required for this paper}
%We aim to design a TMP that can accommodate a number of different P2P trading scenarios. In this section we describe these scenarios, and a set of system requirements that a TMP would need to meet.

%There are a number of commercially available products that enable the real-time management and operation of microgrid distribution systems such as those considered here. For example, the Siemens DERMS suite includes Spectrum Power \cite{SpectrumPower}, which allows utilities and DSOs to optimize and control the operation of DERs on a distribution microgrid. Such products are appropriate for systems involving utility-owned DER and/or prosumer-owned DERs that are operated by the utility under utility-run opt-in programs.
%However, in order to realize a local peer-to-peer electricity market, such products need to integrate market logic that allows participants to post offers to buy and sell electricity futures in a way that preserves both system stability and prosumer interests such as privacy. From the utilities' or DSO's perspective, such extensions to existing products would enable new business models and the availability of fine-grained ancillary services.

%In this paper, we consider problem settings in which the distribution system operator (DSO) controls the participants' access to the local market and also participates in the futures market to shape the prosumers' consumption and production. Additionally, the DSO participates in a wholesale market to provide support for any residual demand from the microgrid.

%\AbhishekC{Integrate Prior Petra Concepts}

%For example, in our prior work \cite{Laszka17} an offer consists of quantity of energy being bought or sold, the time interval in which the energy is to be produced or consumed, and a reservation price - the maximum (or respectively, minimum) price at which the buyer (or respectively, seller) is willing to trade. 
%This is done by first posting offers to sell produced energy, or offers to buy and consume energy. An offer consists of quantity of energy being bought or sold, the time interval in which the energy is to be produced or consumed, and a reservation price - the maximum (or respectively, minimum) price at which the buyer (or respectively, seller) is willing to trade. \scott{does the offer need to include when the power will be available? The time interval mentioned here sounds like the time when the offer will expire.}\Karla{@Scott, see now}%The DSO bargains on the bulk market and provides all residual supply and demand within the microgrid.

%\Karla{I recommend describing the workflow (i.e. event sequencing) here. When is the market cleared}

\subsection{System Requirements}
\label{sec:requirements}

We now describe  requirements that  must be considered for building a decentralized Transaction Management Platform (TMP) that supports the workflow across the microgrid described above.
%consider and specify.

\subsubsection{Communication Fabric}

The first requirement is the existence of an appropriate communication and messaging architecture. The TMP must collect participants' offers and make them available to buyers and sellers, and the market algorithm must communicate clearing prices and buyer-seller matchings.
%, or other market-related signals depending on the trading scenario. 
In order to meet the operational and safety requirements described next, these messages must be reliably delivered under strict timing constraints, derived from the deadline by which a trade must clear. Moreover, the TMP must be capable of handling high volumes of micro-transactions anticipated in peer-to-peer trading scenarios.  Finally, the communication fabric must support confidentiality, integrity, and non-repudiation of transactional data.

%two important points to consider (a)  Each feeder is rated for a maximal power capacity\footnote{Physically, the capacity limit of a feeder can be enforced using an overcurrent protection unit that limits the total current flowing through the feeder.}. Therefore, it is important to ensure that local energy trade settlements involve net power production and consumption which result in instantaneous power flows that never violate this safety constraint; and (b) It is important to be able to track and validate the settlement of all trades in this market while ensuring privacy of the participants is preserved. Specifically these points

\subsubsection{Operational Safety and Stability}

%\scottC{This section could be clearer. It's hard to tell what the actual requirements are. These should be listed then explained. I'd guess to be considered operationally safe the grid must be balanced, the hardware limits cannot be exceeded and the system must tolerate malicious or negligent behavior. Then describe each of those in more detail.}
The trading activity shall not compromise the stability of the physical system operation. For example, capacity constraints along any feeder should be respected. Specifically, each feeder is rated for a maximal power capacity.\footnote{Physically, the capacity limit of a feeder can be enforced using an overcurrent protection unit that limits the total current flowing through the feeder.} Therefore, it is important to ensure that local energy trade settlements involve power production and consumption which result in instantaneous power flows that never violate this safety constraint.
%\scottC{the congestion part is confusing. Should it say something like: "The trading activity shall not compromise the stability of the system. This can be enforced by respecting the feeder congestion constraints. Feeders are rated for a maximal power capacity ..." }

%Resiliency refers to the system's ability to react to contingencies and recover from faults. 
%Capacity constraints refer to the maximal power flow allowed on a transmission line. %The satisfaction of capacity constraints requires assurance that malicious or negligent trading activity is discouraged.
%by using active mechanisms such as congestion pricing and reputation scores. \Abhishek{Need to clarify in the implementation that this is done at coarse-level so that anonymity is not affected} \Aron{Since we don't actually have a reputation system in our implementation, we could omit this for the sake of simplicity} 
%Negligent trading may include producers who commit to a certain production level and fail to deliver. Transactional security means that the execution of contractual obligations among all participants, including the DSO, is guaranteed.
%Finally, the TMP should have provisions for preventing or detecting negligent or malicious interference with smart meters - i.e. the adversarial or natural attacks against the interface between the physical world and the blockchain; data logged shall be securely communicated to the DSO and requests made by the meter on behalf of the prosumer shall be accurately recorded on the blockchain.

\subsubsection{Market Security and Efficiency}

The TMP shall include provisions for ensuring the protection of prosumer interests, as well as those of the DSO. Prosumer interests include being billed correctly based on energy prices set by the market and the measurements made by the smart meters. In the context of grid-connected microgrids, the system should match supply and demand as closely as possible, while respecting safety constraints. Therefore, the TMP should  aim to maximize the amount of energy traded.

%s market efficiency by maximizing transaction volume. %Additionally, it is important to ensure all prosumers will be allowed to participate in the market fairly \scott{what does it mean to participate fairly?}.
%, and being billed fairly by the DSO.

\subsubsection{Privacy}

Information such as the amount of energy produced, consumed, bought, or sold by any prosumer should be available only to the Distribution System Operator\footnote{We are building a trading system in this paper and do not explicitly address the problem of billing. However, multiple billing approaches may be implemented on top of the blockchain, some of which could provide a very high level of privacy. This will be part of our future work.}. All bids and asks, and the matching thereof, should remain anonymous to the other participants. A participant's energy usage patterns and personal information, such as financial standing, shall not be inferable from the participant's trading activity. For example, inference of energy usage patterns can be exploited by inferring the presence or absence of a person in their home.

%\scottC{does the DSO only know the total consumption for the billing cycle, or do they have all the detailed information?} \AronC{We are building the trading system, billing is on top of that, so we do not address this question in this paper. We could add a sentence saying that multiple billing approaches may be implemented on top of the blockchain, some of which could provide a very high level of privacy.} and the essential market functions of the TMP.

\section{Analysis of State of the Art}
\label{sec:related}
%\AbhishekC{We need to describe and update the state of the art by a deep dive on how transactive energy has been implemented till now - the current related research is not going into depth}

%\textbf{Transaction Management Platforms (TMP) for Smart grid} 
Implementing a Transaction Management Platforms (TMP) requires a communication architecture, as well as trading mechanisms that provide the capability to match the bids and asks.  Blockchain-based solutions have the potential to enable large-scale energy trading based on distributed consensus systems. However, popular blockchain solutions, such as Bitcoin \cite{Satoshi} and Ethereum \cite{buterin2013ethereum}, suffer from design limitations that prevent their direct application to validating energy trades. This is primarily due to the lack of additional constraints and checks required, beyond just the transactional integrity check provided by proof-of-work algorithms.
%In particular, their transaction-confirmation time is relatively slow and variable.
%proof-of-work algorithm\AronC{Our implementation also uses proof-of-work, so I would be careful with dissing it like this}.
%\Aron{What do we mean by dependence on ``on-the-blockchain communication?'' Where was the quote taken from?} dependence on ``on-the blockchain communication.''

For example, Aitzhan and Svetinovic implemented a proof-of-concept platform for decentralized smart grid energy trading using blockchains, but their system is based on proof-of-work consensus, and they do not consider grid control and stability, or scalability~\cite{aitzhan2016security}. Additionally, there is still the problem of privacy---all transactions in these systems are  public \cite{kosba2016hawk}.

Most works discussing privacy look at it from the context of smart meters. McDaniel and McLaughlin discuss the
privacy concerns of energy usage profiling, which smart grids could
potentially enable~\cite{mcdaniel2009security}. Efthymiou and Kalogridis describe a method for securely anonymizing frequent electrical metering data sent by a smart
meter~\cite{efthymiou2010smart} by using a third party escrow mechanism. Tan et
al.\ study privacy in a smart metering system from an information
theoretic perspective in the presence of energy harvesting and storage
units~\cite{tan2013increasing}. They show that energy harvesting
provides increased privacy by diversifying the energy source, while a
storage device can be used to increase both energy efficiency and
privacy. However, the transaction data provides more fine-grained information than the smart meter usage patterns \cite{Privacy2017}.

Majumder et al.\ present an iterative double auction trading mechanism that preserves the participants' privacy~\cite{majumder_efficient_2014}. However, the privacy property pertains to the participants' utility function models, not their identities. 
%In \cite{majumder_efficient_2014} Majumder et al, present an iterative double auction which aims to maximize agent utilities and overall social welfare. They also claim to maintain the privacy of users, however the objective of their approach is to incentivize participants to share personal information and that privacy is preserved because they do not relinquish all of their data. Additionally they assume  there are many participants that have limited computational power. Second, they do not consider the safety constraints of the feeders. Finally, they do not have protection against malicious participants.

Existing energy trading markets, such as the European Energy Exchange \cite{EPEX_SPOT_operation} and project NOBEL in Spain, employ the double-auction market mechanism \cite{Ilic12}, which can be implemented to preserve participant privacy. However, typical exchange implementations involve centralized database architectures prone to single points of failure.

%Zhang et al., also present a TMP, recognizing that transactive energy systems are vulnerable to attack due to the public transactions, and grid control over the Internet~\cite{zhang_cyber_????}. \Karla{Please fix reference!} In their work they develop a simulation architecture on top of the open source TESP (Transactive Energy Simulation Platform) in order to analyze the effects of two types of attacks (malicious bid price and quantity) on the double-auction market they implemented. This data allowed them to use a deep learning approach called deep stacked autoencoder to train a classifier to identify the two attacks. They are able to do this using the raw sensor data.

Faqiry and Das present an auction mechanism for maximizing social welfare of buyers and sellers (if the supply is small)~\cite{faqiry_transactive_2016}. Their approach also provides some privacy meaning that a participant does not reveal their utility function. By constricting the buyers' utility functions to be convex, the social welfare objective function is maximized when the micro-grid controller objective function, whose goal is to pair as maximize the power sold, is maximized. In the later part of the paper, in order to make the trading fair, they consider an approach that discards the privacy maintained during the first phase. In their work, there is no mechanism to check whether the buyer can produce the power they claim they can supply, which could result in instability. The authors also mention in passing that their approach can be implemented as a distributed algorithm, but this was not carried out.

In contrast, the work presented in this paper is a distributed systems mechanism that considers the problem of a broader definition of privacy, safety, and protection from malicious actors as a combined problem.
%\AbhishekC{we need to reprhase our contributions and requirements here again and show why the state of the art has not yet solved the problem.}
% The work presewnted in this paper extends these works by  (1) leveraging a decentralized computation fabric provided by smart homes in the community,
% %\footnote{We demonstrate the execution on a network of virtual machines in this paper.} 
% (2) addressing the privacy
% threat posed by trading using a novel trading sequence implementation, (3) showing how partial trades can be fulfilled, and (4) designing and implementing the distributed

% and (4) using off-blockchain communication primitives provided by the distributed application management platform RIAPS. While the conceptual design of PETra was presented in \cite{Laszka17}, this paper describes the revised protocol and the trading algorithm, and presents the implementation results. 
% %This work is closely related to \cite{kosba2016hawk} .... \Abhishek{Todo:Write about Hawk}
% on, as well as support for deploying algorithms on devices across the network\footnote{RIAPS uses ZeroMQ \cite{hintjens2010zeromq}, and Cap'n Proto \cite{varda2015cap}, to manage the communication layer.} and solves problems collaboratively by providing micro-second level time synchronization \cite{riaps2}, failure based reconfiguration \cite{dubey2017resilience}, and group creation and coordination services (still under active development), in addition to the services described in \cite{LeeNiddodiSrivastavaBakken2016}. It is capable of handling different communication and running implemented algorithms in real-time.

% \Karla{this section is a duplicate of the previous}
% \color{red}
% \textbf{Transaction Management Platforms (TMP) for Smart grid} 
% TMP require communication, as well as trading mechanisms that provide the capability to match the bids and asks. Additionally, they must provide fairness and integrity assurances.  Blockchain based solutions have the potential to enable large-scale energy trading based on distributed consensus systems. However, popular blockchain solutions, such as Bitcoin \cite{Satoshi} and Ethereum \cite{buterin2013ethereum} suffer from design limitations that prevent their direct application to validating energy trades. In particular, their transaction-confirmation time is relatively slow and variable, primarily due to the proof-of-work algorithm and most of the communication occurring via the ledger.
% %\Aron{What do we mean by dependence on ``on-the-blockchain communication?'' Where was the quote taken from?} dependence on ``on-the blockchain communication.'' 
% For example, Aitzhan and Svetinovic implemented a proof-of-concept platform for decentralized smart grid energy trading using blockchains, but their system is based on proof-of-work consensus, and they do not consider grid control and stability, or scalability~\cite{aitzhan2016security}. Additionally, there is the problem of privacy - all transactions in these systems are  public \cite{kosba2016hawk}.

% Most works in this area have focused on the privacy issue from the context of smart meters. McDaniel and McLaughlin discuss the
% privacy concerns of energy usage profiling, which smart grids could
% potentially enable~\cite{mcdaniel2009security}. Efthymiou and Kalogridis describe a method for securely anonymizing frequent electrical metering data sent by a smart
% meter~\cite{efthymiou2010smart} by using a third party escrow mechanism. Tan et
% al.\ study privacy in a smart metering system from an information
% theoretic perspective in the presence of energy harvesting and storage
% units~\cite{tan2013increasing}. They show that energy harvesting
% provides increased privacy by diversifying the energy source, while a
% storage device can be used to increase both energy efficiency and
% privacy. However, the transaction data provides more fine-grained information than the smart meter usage patterns \cite{Privacy2017}.

% PETra extends these works by (1) leveraging a decentralized computation fabric provided by smart homes in the community,
% %\footnote{We demonstrate the execution on a network of virtual machines in this paper.} 
% (2) addressing the privacy
% threat posed by trading using a novel trading sequence implementation, (3) showing how partial trades can be fulfilled, and (4) using off-blockchain communication primitives provided by the distributed application management platform RIAPS. While the conceptual design of PETra was presented in \cite{Laszka17}, this paper describes the revised protocol and the trading algorithm, and presents the implementation results. 
% %This work is closely related to \cite{kosba2016hawk} .... \Abhishek{Todo:Write about Hawk}

% \color{black}

### 2017-10-16 docs/papers/iotdi2018/solution.tex
added iotdi paper

\section{Solution Approach}
\label{sec:solution}
In this section, we present a hybrid approach for solving the energy trading problem on a decentralized computing platform.
Our hybrid approach combines the auditability and trustworthiness of blockchain-based smart contracts\footnote{Our current implementation uses Ethereum.} with the efficiency of more traditional computing platforms.
We first show how to solve the problem by formulating it as a linear program.
Then, we describe the computation and verification that need to be performed by the computational nodes and the smart contract in a decentralized microgrid.

\subsection{Linear-Programming Solution}
%\KarlaC{Equation (16) is identical to (10); Not sure what this subsection adds (it just repeats the previous section). I think we can just omit the whole subsection, and rename section 5 as "Hybrid solver implementation"}
We can solve the basic energy trading problem efficiently by formulating it as a linear program.
First, create real-valued variables $p_{s,b,t}$ and $\pi_{s,b,t}$ for each $s \in S, b \in \calM(s), t \in I(s, b)$.
Then, the following reformulation of the matching problem is a linear program:
\begin{equation}
\max_{\vp,\vpi}
\sum_{s \in \calS} \sum_{b \in \calM(s)} \sum_{t \in I(s,b)} p_{s,b,t} \label{eq:linProgObj}
\end{equation}
subject to Equations~\eqref{eq:constrEnergyProd} to \eqref{eq:constrPrice} and
\begin{equation}
\vp \geq \vect{0} \text{ and } \vpi \geq \vect{0} .
\end{equation} 
The extended energy trading problem introduced in Section~\ref{sec:extendedProblem} can be reformulated as a linear program similarly, by considering $\calS^{(t)}$, $\calB^{(t)}$, $\hat{\vp}$, $\hat{\vpi}$, and the additional constraints.

\subsection{Hybrid Solver Implementation}
\label{sec:hybridSolver}

Although solving linear programs is not computationally hard, it can be challenging with a large number of variables and constraints in resource-constrained computing environments.
Since computation is relatively expensive on blockchain-based distributed platforms\footnote{Further, Solidity, the preferred high-level language for Ethereum, currently lacks built-in support for certain features that would facilitate the implementation of a linear programming solver, such as floating-point arithmetics.}, solving the energy trading problem using a block\-chain-based smart contract would not be scalable in practice.
In light of this, we propose a \emph{hybrid implementation approach}, which combines the trustworthiness of blockchain-based smart contracts with the efficiency of more traditional computational platforms.

The key idea of our hybrid approach is to (1) use a high-performance computer to solve the computationally expensive linear program \emph{off-blockchain} and then (2) use a smart contract to record the solution \emph{on the blockchain}.
To implement this hybrid approach securely and reliably, we must address the following issues.
\begin{compactitem}
\item Computation that is performed off-blockchain does not satisfy the auditability and security requirements that smart contracts do. Thus, the results of any off-blockchain computation must be verified in some way by the smart contract before recording them on the blockchain.
\item Due to network disruptions and other errors (including deliberate denial-of-service attacks), the off-blockchain solver might fail to provide the smart contract with a solution on time (i.e., before trades are supposed to be finalized). Thus, the smart contract must be able to proceed without an up-to-date solution.
\item For the sake of reliability, the smart contract should accept solutions from multiple off-blockchain sources; however, these sources might provide different solutions.
Thus, the smart contract must be able to choose from multiple solutions (some of which may come from a compromised computer).
\end{compactitem}

%\Abhishek{The time synchronization discussion can go here.}
\subsubsection{Blockchain-based Smart Contract}

We implement a smart contract that can (1) verify whether a solution $(\vp, \vpi)$ is feasible and (2) compute the value of the objective function for a feasible solution.
Compared to finding an optimal solution, these operations are computationally inexpensive, and they can easily be performed on a blockchain-based decentralized platform.
Using these capabilities, the smart contract provides the following functionality:
\begin{compactitem}
\item Solutions may be submitted to the contract at any time. 
The contract verifies the feasibility of each submitted solution, and if the solution is feasible, then it computes the value of the objective function.
The contract always keeps track of the best feasible solution submitted so far, which we call the \emph{candidate solution}.
\item At the end of each time interval $t$, the contract finalizes the trade values for interval $t + T_{clear}$ based on the candidate solution.\footnote{If no solution has been submitted to the contract so far, which might be the case right after the trading system has been launched, $\vp = \vect{0}$ may be used as a candidate solution.}
\end{compactitem}

This simple functionality achieves a high level of security and reliability.
Firstly, it is clear that an adversary cannot force the contract to finalize trades based on an unsafe (i.e., infeasible) solution since such a solution would be rejected.
Similarly, an adversary cannot force the contract to choose an inferior solution instead of a superior one.
In sum, the only action available to the adversary is proposing a superior feasible solution, which would actually improve energy trading in the microgrid.

The contract is also reliable and can tolerate temporary disruptions in the solver or the communication network.
Notice that any solution $(\vp, \vpi)$ that is feasible for sets $\calS$ and $\calB$ is also feasible for supersets $\calS' \supseteq \calS$ and $\calB' \supseteq \calB$.
As the sets of offers can only grow over time, the contract can use a candidate solution submitted during time interval $t$ to finalize trades in any subsequent time interval $\tau > t$.
In fact, without receiving new solutions, the difference between the amount of finalized trades and the optimum will increase only gradually:
since the earlier candidate solution can specify trades for any future time interval,
the difference is only due to the offers that have been posted since the solution was found and submitted.

%In our hybrid approach, we implement a relatively simple algorithm in our smart contract, which can (1) check if a solution $(\vp, \vpi)$ is feasible and (2) evaluate the objective function for a given solution (see Equation~\eqref{eq:linProgObj}).

\subsubsection{Off-blockchain Solver}

We complement the smart contract with an efficient linear programming solver, which can be run off-blockchain, on any capable computer (or multiple computers for reliability).
The solver is run periodically to find a solution to the energy trading problem based on the latest set of offers posted. 
Once a solution is found by the solver, it is submitted to the smart contract in a blockchain transaction.
Note that if new offers have been posted since the solver started working on the solution, the contract will still consider the solution to be feasible. 
This again due to any feasible solution for sets $\calS$ and $\calB$ also being feasible for supersets $\calS' \supseteq \calS$ and $\calB' \supseteq \calB$.
%The smart contract then verifies whether the solution is feasible and whether it is better than any feasible solution submitted before,  and if both conditions hold, accepts the solution as the best matching (found so far).

From the perspective of the solver, being able to submit multiple solutions to the contract for the same problem has many advantages. %that multiple solutions may be submitted to the smart contract, which will always choose the best feasible one.
%This is advantageous because
For example, it allows the linear programming solver to be run as an anytime algorithm.
Further, we can allow multiple---potentially untrusted---entities to try to solve the problem and submit solutions, since the smart contract will always choose the best feasible one.
This is especially important in microgrids where a trusted third party is not guaranteed to always be present.
In such settings, prosumers can be allowed to volunteer and provide solutions to the energy trading problem.%
\footnote{Of course, each prosumer will try to submit a solution that favors the prosumer. However, the submitted solution still needs to be superior with respect to the optimization objective, which roughly corresponds to social utility. Hence, each prosumer is incentivized to improve social utility by submitting a superior solutions that favors the prosumer. We leave the analysis of these incentives for future work.}
Thereby, we enable finding solutions in an efficient and very flexible manner, while reaping the benefits of smart contracts, such as auditability and trustworthiness.

### 2017-10-16 docs/papers/iotdi2018/system.tex
added iotdi paper

\begin{figure}[t]
\centering
%\resizebox{\columnwidth}{%
\begin{tikzpicture}[x=1.2cm, y=1.2cm, font=\tiny,
  Component/.style={fill=white, draw, align=center, rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}},
  Connection/.style={<->, >=stealth, shorten <=0.05cm, shorten >=0.05cm}]

\foreach \pos/\name in {1.6/pros3, 0.8/pros2} { %, 0.0/pros1} {
  \node [Component] (\name) at (\pos - 4, \pos) {Prosumer\\(\texttt{Python, geth})};
}

\node [Component] (dso) at (-1, 2.6) {DSO\\(\texttt{Python, geth})};

\node [Component] (solver) at (-4, 0) {Solver\\(\texttt{Python, CPLEX})};

\fill [fill=black!15] (90:1.5) -- (200:1.5) -- (340:1.5) -- (90:1.5);

\foreach \pos in {90, 200, 340} {
  \node [Component] at (\pos:1.5) {Blockchain\\ miner (\texttt{geth})};
}

\node [Component, dotted] (contract) at (0, 0) {Smart contract\\(\texttt{Solidity})};

%\draw [Connection, bend left=45] (solver) to (dso);

%\draw [Connection, bend left=65] (pros1) to node [midway, left, shift={(-0.25,0)}] {$\emptyset$MQ} (dso);
\draw [Connection, bend left=55] (pros2) to node [midway, left, shift={(-0.25,0)}] {$\emptyset$MQ} (dso);
\draw [Connection, bend left=45] (pros3) to (dso);

\draw [Connection, bend right=0] (solver) to node [midway, below left] {Ethereum} (contract);
\draw [Connection, bend right=15] (dso) to (contract);
%\draw [Connection, bend right=0] (pros1) to node [midway, below left] {Ethereum} (contract);
\draw [Connection, bend right=0] (pros2) to (contract);
\draw [Connection, bend right=0] (pros3) to (contract);
\end{tikzpicture}%
%}
\caption{Components of the energy trading system. In our implementation, we use Ethereum as the decentralized computation platform running smart contracts, and the other components interact with the blockchain network using the \texttt{geth} Ethereum client. The smart contract is implemented in Solidity, a high-level language for Ethereum, and it is executed by a network of \texttt{geth} mining nodes.}
\label{fig:components}
\end{figure}

\input{workflowdiagram.tex}

\section{Energy Trading System}
\label{sec:tradingsystem}

In this section, we outline a system that can provide the energy trading and market clearing functionality described in the preceding sections. We first describe the main components of the system, including a short background on the runtime platform. 
Then, we give an overview of the messages exchanged between these components in the trading workflow.

\subsection{Background}
% \begin{figure}
% \includegraphics[width=0.48\textwidth]{diagrams/RIAPSBroch_FINALPRINT.jpg}
%   \caption{RIAPS concept.}
% 	\label{fig:concept}
% \end{figure}

In any technical system that relies on embedded computing, the most important ingredient is an ``operating system'' that provides the foundations for all algorithms, isolates the hardware details from the algorithms, and provides essential mechanisms for resource management, fault tolerance, and security. For example, in the work presented in this paper, this framework allows us to disseminate information between the actors. Our extended team has developed a platform called `Resilient Information Architecture Platform for Smart Grid' (RIAPS) \cite{riaps}, where each actor is a composition of several libraries that provide (1) a component model that provides a concurrent model of computation for building distributed real-time applications, (2) a messaging framework for facilitating interactions among actors, (3) a resource-management framework for controlling the use of computational resources, (4) a fault-management framework for detecting and mitigating faults in all layers of the system, (5) a security framework to protect the confidentiality, integrity, and availability of system under cyber-attacks, (6) a fault tolerant time synchronization service,  (7) a discovery framework for establishing the network of interacting actors of an application, and (7) a deployment and management framework for the administration and control of the distributed applications from a control room.

\subsection{Trading System Architecture}
\label{sec:architecture}

Figure~\ref{fig:components} shows the architecture of the energy trading system. The specific platforms and tools used in our implementation are shown in parentheses and as arrow labels. All components are written in Python and communicate with each other using ZeroMQ, one of the protocols supported by the RIAPS platform.

\subsection{Providing Privacy}
\label{sec:privacy}

To protect their privacy, prosumers use anonymous addresses when interacting with the blockchain (e.g., posting offers).
By generating new anonymous addresses at random periodically, they can prevent other participants from linking the anonymous addresses to their actual identities~\cite{Laszka17}, thereby keeping their trading activities private. 
However, in contrast with our prior work~\cite{Laszka17}, the addresses used in the workflow described in the next section are not completely anonymous. Since the blockchain-based smart contract has to check feeder-level safety constraints, each anonymous address must be linked to a feeder.
Hence, an anonymous address can hide only the prosumer's identity but not its feeder, which is a manifestation of the trade-off between safety and privacy.\footnote{Actually, participants can remain anonymous among a class of feeders with same number of participants and identical safety constraints.}

However, anonymous addresses pose a further threat to safety.
Since participants can generate anonymous addresses at almost no cost, they could post selling and buying offers for large amounts of energy, without any intention of delivering and without facing any repercussions.
A malicious or faulty participant could easily destabilize the grid with this form of reckless trading.
Consequently, the amount of energy that may be traded by anonymous addresses belonging to a participant must be limited.

Thus, we use the concept of energy assets, initially introduced  in~\cite{Laszka17} and  used in the trading workflow described in the next section.
%\AronC{They were only used but not described in the workflow.}  described in the workflow of above.
%In~\cite{Laszka17}, we introduced \emph{energy assets} to enforce participant-level safety constraints.
An energy asset represents a permission to sell or buy a specific amount of energy in a specific set of  time intervals. 
Each prosumer can ask the DSO to transfer assets to an anonymous address, who can check whether it would be safe to give permission to the participant.
If it would be, then the DSO records this transfer on the blockchain.
Later, when the participant posts an offer from the anonymous address, the smart contract can check whether the address has the assets required for the offer.
Since only the DSO can link the anonymous address to the participant, assets enable enforcing participant-level constraints without violating privacy.

\subsection{Trading Workflow}

Figure~\ref{fig:workflow} illustrates the trading workflow.
For ease of presentation, the figure shows only one prosumer and only a single message of each type.
In practice, a large number of prosumers may interact with the DSO and the smart contract, and each of them may exchange multiple messages.

\newcommand{\msgDesc}[1]{{\footnotesize{\texttt{#1}}}}

The workflow includes the following messages:
\begin{compactitem}
\item 
\msgDesc{withdrawAssets(anonAddress, energy, intervals, amount)}: message sent by a prosumer to the DSO, asking the DSO to transfer energy and/or financial assets from the prosumer's account at the DSO to an anonymous address.
Before sending this message, the prosumer first generates a random anonymous address to protect her privacy.
The message specifies the assets that the prosumer wishes to withdraw (i.e., amount of energy and time intervals) and the anonymous address to which the DSO should transfer them.
Note that the prosumer may send this message long before actually engaging in trading, so the DSO does not have to be online continuously.
\item \msgDesc{failedWithdrawal(anonAddress, msg)}: message sent by the DSO to the prosumer,
notifying the prosumer that the requested assets cannot be withdrawn due to, e.g., energy safety requirements or insufficient funds.
\item \msgDesc{addEnergy(anonAddress, energy, intervals)},\\\msgDesc{addFinancialBalance(anonAddress, amount)}:
smart contract functions called by the DSO (i.e., transactions recorded on the blockchain) in response to the prosumer's request, creating energy and financial assets on the blockchain and transferring them to an anonymous address.
Before recording this transaction, the DSO must first verify that enabling the prosumer to trade these assets does not violate any safety constraints and that the anonymous address is linked to the correct feeder.
%The call specifies the assets and the anonymous address to which they are transferred. 
\item \msgDesc{AssetAdded(anonAddress, energy, intervals)},\\\msgDesc{FinancialAdded(anonAddress, amount)}: broadcast messages emitted by the smart contract (i.e., events logged on the blockchain),
notifying the prosumer that the requested assets have been transferred to the anonymous address.
\item \msgDesc{postOffer(energy, intervals, price)}: smart-contract function called by a prosumer (from its anonymous address), publicly posting an energy bid or ask.
%If the prosumer is interested in buying energy, then it posts an energy bid, which specifies an energy consumption asset and a price.
%If the prosumer is interested in selling, then it posts an energy ask, which specifies an energy production asset and a price.
%In both cases, the transaction must be cryptographically signed by the private key of the address, and it locks the assets until the offer is accepted or rescinded.
\item \msgDesc{OfferPosted(offerID, energy, intervals, price)}:
message broadcast by the smart contract, notifying solvers that an offer was posted.
\item \msgDesc{submitSolution(powers, prices)}:
smart-contract function called by a solver,
submitting a new solution for the energy trading problem. %If the offer was an energy bid, then the other prosumer has to provide an energy production assets;
%if the offer was an energy ask, then the other prosumer has to provide both energy consumption and financial assets.
%In both cases, the transaction must be cryptographically signed by the private key of the other prosumer's anonymous address.
%If there is an overlap between the time intervals of the offered asset, and the asset provided by the other prosumer, then the intersecting parts of the assets are exchanged and the non-overlapping parts are returned to their original owners.
%Similarly, based on the price and exchanged energy assets, a part of the financial asset is transferred to the seller, while the rest is returned to the seller. 
\item \msgDesc{SolutionFinalized(powers, prices)}:
message broadcast by the smart contract,
notifying both prosumers and solvers of energy trades that have been finalized. %that its offer has been accepted, and the assets have been exchanged.
\item \msgDesc{depositEnergy(energy, intervals)},\\\msgDesc{depositFinancial(amount)}:
smart-contract functions called by a prosumer,
depositing energy and financial assets to the prosumer's account.
%The transaction specifies the assets, and it must be cryptographically signed by the anonymous address that owns them.
Note that to protect privacy, the calls do not specify the prosumer, so the DSO has to keep track of which prosumer has used which anonymous address.
\item \msgDesc{EnergyDeposited(anonAddress, energy, intervals)},\\\msgDesc{FinancialDeposited(anonAddress, amount)}:
messages broadcast by the smart contract,
notifying the DSO that assets have been deposited from anonymous address, which triggers the transfer of these assets to the prosumer's account at the DSO.
\end{compactitem}

\subsection{Implementation Considerations}
\label{sec:implementation}

\subsubsection{Parameters} The system of prosumers, solvers, DSO, and smart contract operates mostly asynchronously. The only synchronous communication  occurs between prosumers and the DSO. They all operate as  independent processes running on remote nodes, with their own time bases. In particular, the solver can operate as a periodic process (with a period $\Delta_s$), waiting on information from the smart contract about all the offers that have been posted in the prior period. The prosumers  can also operate as periodic processes, submitting their offers and bids to the smart contract.  In practice, prosumers will be synchronized with real wall-clock time, making their bids and asks known for future intervals, depending upon the time at which they post their bids/asks and how far in the future  they can predict their usage or operation. We make  their prediction window $L$ a parameter of the system. The value of this parameter is at least $2$, because prosumers have to  make a bid/ask for at least the next interval (we count the current interval in $L$). A larger value of this prediction window will increase the risk of uncertainty for the prosumer, since they are expected to be able to fulfill their bid or ask.\footnote{The size of the prediction window is part of the prosumer strategy, which is not explored in this paper as our focus is on the implementation of the TMP.} Additionally, during our experiments, we can simulate $\Delta$ as $\hat{\Delta}$ to speed up the process.\footnote{Note that this is the amount of real time passed in the simulation before proceeding to the next interval. This allows us to speed things up for the experiment, since running the system slower would just be easier.} These parameters are described in Table \ref{tab:symbols}.

\subsubsection{Speed and Synchronization Considerations}
A relevant problem for TMP is deciding how fast it can run and ensuring that trades for the next interval can clear before the $T_{clear}$ parameter, which has a minimum bound of $1$.
In our system, regular network communication mechanisms are assumed to be fast. However, the communication with the smart contract is limited by the block mining rate, and we need multiple messages exchanged in each interval (see Figure~\ref{fig:workflow}), so the miners need to work fast enough to mine a few blocks in each time interval. In a closed environment, this can be achieved by reducing the difficulty of the cryptographic puzzle solved for proof-of-work consensus. In our system, as shown in the next section, we are able to clear transactions much faster than one time interval. 
For larger systems, the proof-of-work consensus may be replaced by, e.g., proof-of-stake, for scalability.

Another problem is the synchronization between the different agents. The runtime platform of RIAPS provides us with high-precision time synchronization \cite{riaps2}. However, even if we only have NTP as the synchronization mechanism, we can operate the system correctly. This is because intervals in practice are relatively (i.e.,  compared to typical communication delays) long (e.g., 15 minutes). Additionally, the smart contract can ensure that the system always proceeds to the next time interval (however, the accuracy of this is limited by the mining rate, see previous paragraph). Additionally, our system can  tolerate or discard out-of-order and late messages due to the event chronology implemented in the blockchain platform. In practice, however, prosumers should try to post their offers early within a time interval, so that solvers will include them in the solution for the current time interval. On the other hand, solvers should wait some time before starting to work, so that they can collect all (or at least most) of the offers posted in the interval.

% \Aron{Talk about timing issues in smart contracts!}

% \color{red}
% Ideas:
% \begin{itemize}
% \item communication over the blockchain is limited by the block mining rate, and we need multiple messages exchanged in each interval, so the miners need to work fast enough to mine a few blocks in each time interval
% \item no time synchronization is necessary since 1) intervals in practice are relatively (i.e.,  compared to typical communication delays) long (e.g., 15 minutes) 2) smart contract can ensure that the system always proceeds to the next time interval (however, the accuracy of this is also limited by the mining rate, see previous point) 3) our system can tolerate or discard out-of-order and late messages\AbhishekC{Can we address what will happen if there are multiple miners.}
% \item in practice, prosumers should try to post their offers early within a time interval, so the solver can include them in the solution for the current time interval; on the other hand, solvers should wait some time before starting to work so that they have all (or at least most) of the offers posted in the interval
% \end{itemize}
% \color{black}

### 2017-10-16 docs/papers/iotdi2018/workflowdiagram.tex
added iotdi paper

\begin{figure*} [!t]
\centering
\begin{tikzpicture}[x=5.65cm, y=-0.063cm, semithick, font=\small,
RedDashed/.style={red, dashed}]
\def\posDSO{0}
\def\posProsumer{1}
\def\posLedger{2.05}
\def\posSolver{3}
\foreach \name/\pos in {DSO/\posDSO, Prosumer/\posProsumer, Smart contract/\posLedger, Solver/\posSolver} {
  \draw (\pos, 0) -- (\pos, 110);
  \node [draw, fill=white, rounded corners=0.1cm] at (\pos, 0) {\name};
}
\newcounter{seqTime}
\setcounter{seqTime}{0}
\foreach \action/\from/\to/\styl/\delta in {
  {withdrawAssets(anonAddress, energy, intervals, amount)/\posProsumer/\posDSO/solid/17},
  {failedWithdrawal(anonAddress, msg)/\posDSO/\posProsumer/red/8},
  {addEnergy(anonAddress, energy, intervals), addFinancialBalance(anonAddress, amount)/\posDSO/\posLedger/solid/14},
  {AssetAdded(anonAddress, energy, intervals)/\posLedger/\posProsumer/dashed/14},
  {postOffer({energy, intervals, price})/\posProsumer/\posLedger/solid/8},
  {OfferPosted({offerID, energy, intervals, price})/\posLedger/\posSolver/dashed/6},
%  {rescindOffer(offerID)/\posProsumer/\posLedger/red/6},
%  {OfferRescinded(offerID)/\posLedger/\posSolver/RedDashed/4},
  {submitSolution({powers, prices})/\posSolver/\posLedger/solid/8},
  {SolutionFinalized({powers, prices})/\posLedger/\posProsumer/dashed/6},
  {depositEnergy(energy, intervals), depositFinancial(amount)/\posProsumer/\posLedger/solid/14},
  {EnergyDeposited(anonAddress, energy, intervals), FinancialDeposited(anonAddress, amount)/\posLedger/\posDSO/dashed/14}%
} {
  \addtocounter{seqTime}{\delta}
  \draw [->, >=stealth, shorten <=0.05cm, shorten >=0.05cm, \styl] (\from, \value{seqTime}) -- (\to, \value{seqTime}) node [midway, above, align=center, text width={abs(\to - \from) * 5.1cm}, fill=white, fill opacity=0.67, text opacity=1] {\footnotesize\texttt{\scriptsize\action}};
}
\end{tikzpicture}
\caption{Sequence diagram of the trading workflow. Solid lines represent messages, including smart-contract function calls (i.e., blockchain transactions), while dashed lines represent smart-contract events. For ease of presentation, we show only a single prosumer and one instance of each communication. 
}
\label{fig:workflow}
\end{figure*}

### 2017-10-16 docs/papers/iotdi2018/feeder.tex
corrected figure caption

@@
 \caption{Load profile (i.e., total consumption) and generation profile (i.e., total production) in kWh per 15 minute interval aggregated across the microgrid.
-The graph also shows the energy traded per interval without battery, with battery and prediction window of 5 intervals, and with battery and prediction window of 12 intervals.
+The graph also shows the energy traded per interval without battery (Test A),  and with battery Tests C and D (see Table \ref{table:test-parameters}).
 Note that the amount of energy traded can be lower than both demand and supply at the same time because of safety constraints, which limit the amount of energy that can flow out of the producers' feeders.}

### 2017-10-16 docs/papers/Serial2017/communicationanonymity.tex
fixed typos in SERIAL'17

@@
 The tunnels use layered encryption, meaning that each router in the tunnel only can decrypt one layer.
-In order to transmit a message between two routers, the sender needs to know  where to direct the message, i.e.
-what the address of the entry point of the receiver is.
+In order to transmit a message between two routers, the sender needs to know  where to direct the message, i.e., what the address of the entry point of the receiver is.
 
@@
 The I2P protocol ensures the anonymity of its users because of the disconnect between the identities of the applications communicating over the network, and the identities of the routers.
-This metadata is stored in a distributed directory called the netDb, based on the Kademlia P2P-protocol, which describes a provably consistent and fault-tolerant distributed hash table.
-\cite{kademlia} The RouterInfo and LeaseSet data are stored on the netDb under the key derived from the SHA256 of the destination.
+This metadata is stored in a distributed directory called the netDb, based on the Kademlia P2P-protocol, which describes a provably consistent and fault-tolerant distributed hash table~\cite{kademlia}.
+The RouterInfo and LeaseSet data are stored on the netDb under the key derived from the SHA256 of the destination.
 

### 2017-10-16 docs/papers/Serial2017/intro.tex
fixed typos in SERIAL'17

@@
 generated renewable energy, which was developed by LO3 Energy as a pilot project.
-Similarly, RWE, and Grid Singularity have developed blockchain based solutions for incentivizing neighbors to sell excess energy to the grid and payments for electric car charging %and (c) enabling pre-paid transactions for electric bills in South Africa, respectively.
+Similarly, RWE, and Grid Singularity have developed blockchain based solutions for incentivizing neighbors to sell excess energy to the grid and payments for electric car charging.
+%and (c) enabling pre-paid transactions for electric bills in South Africa, respectively.
 However, those solutions do not address the requirements for off-blockchain communication network and the requirements for privacy.
@@
 Section \ref{commthreat} discusses the threat vectors for the communication anonymity approach.
-Section \ref{transthreat} describes the transaction anonymity threats.
+Section~\ref{transthreat} describes the transaction anonymity threats.
 Finally, we provide concluding remarks in Section~\ref{sec:discussion}.

### 2017-10-16 docs/papers/Serial2017/paper.tex
fixed typos in SERIAL'17

@@
  There are specific safety requirements in transactive microgrids to ensure the stability of the grid and to control the load.
-To fulfil these requirements, the distribution system operator needs transaction information from the grid, which poses a further challenge to the privacy-goals.
+To fulfil these requirements, the distribution system operator needs transaction information from the grid, which poses a further challenge to the privacy goals.
 This problem is made worse by requirement for off-blockchain communication in these networks.

### 2017-10-16 docs/papers/Serial2017/transactionanonymity.tex
fixed typos in SERIAL'17

@@
 Additionally, Biryukov and Pustogarov, 2015, show that using Bitcoin over the Tor network opens an entirely new attack surface~\cite{biryukov2015}.
-Solutions to the tracing and identification problems identified by these researchers have been proposed and implemented in alternative cryptocurrency protocols: mixing using ring signatures and zero-knowledge proofs.~\cite{miers2013zerocoin,cryptonote}
+Solutions to the tracing and identification problems identified by these researchers have been proposed and implemented in alternative cryptocurrency protocols: mixing using ring signatures and zero-knowledge proofs~\cite{miers2013zerocoin,cryptonote}.
 
@@
 third party.
-Monero is an example of a cryptocurrency that provides built-in mixing services by implementing the CryptoNote protocol.~\cite{cryptoeprint:2015:1098} There are however alternative implementations of mixing protocols such as CoinShuffle~\cite{ruffing2014coinshuffle} or
+Monero is an example of a cryptocurrency that provides built-in mixing services by implementing the CryptoNote protocol~\cite{cryptoeprint:2015:1098}.
+There are however alternative implementations of mixing protocols such as CoinShuffle~\cite{ruffing2014coinshuffle} or
 Xim~\cite{bissias2014sybil}.
@@
 
-Group signatures were first introduced by Chaum and van Heyst, 1991,~\cite{Chaum1991} and then built upon by Rivest \textit{et al.}, 2001.~\cite{Rivest2001} The basis for anonymity in the CryptoNote protocol, however, is a slightly modified version of the \textit{Traceable ring signature} algorithm by Fukisaki and Suzuki, 2007.~\cite{Fujisaki2007} The algorithm allows a member of a group to send a transaction in such a way that it is impossible for a receiver to know any more about the sender than that it came from a group member without the use of a central authority.
+Group signatures were first introduced by Chaum and van Heyst, 1991,~\cite{Chaum1991} and then built upon by Rivest \textit{et al.}, 2001~\cite{Rivest2001}.
+The basis for anonymity in the CryptoNote protocol, however, is a slightly modified version of the \textit{Traceable ring signature} algorithm by Fukisaki and Suzuki, 2007~\cite{Fujisaki2007}.
+The algorithm allows a member of a group to send a transaction in such a way that it is impossible for a receiver to know any more about the sender than that it came from a group member without the use of a central authority.
 
@@
 Notably, the ring signature algorithm by Fujisaki and Suzuki, \cite{Fujisaki2007}, has been published in a peer-reviewed paper.
-This can be compared favorably to many cryptocurrency protocols which are simply published as white papers without any formal review-process.
-\cite{cryptonote}
+This can be compared favorably to many cryptocurrency protocols which are simply published as white papers without any formal review-process~\cite{cryptonote}.
 In practice, a transaction using the mixing service should be performed in the following way to ensure anonymity:
@@
 The Zerocoin protocol \cite{miers2013zerocoin} outlines a way how NIZKs can achieve the untraceability objective of the previous section and it ensures that no double-spending is allowed.\footnote{Each coin in the protocol is identified uniquely by a serial number.} Zerocoin is a protocol for the decentralized mixing of coins, so that they can not be traced, or \textit{tainted}.
-However, senders and destinations can still be identified.~\cite{miers2013zerocoin} Luckily, Zerocash~\cite{Sasson:2014:ZDA:2650286.2650810} extends the NIZK functionality to allow for anonymous transactions, anonymous balances and coins, improved performance of transactions and sending of assets to a receivers fixed address without action required from the receiver.
+However, senders and destinations can still be identified~\cite{miers2013zerocoin}.
+Luckily, Zerocash~\cite{Sasson:2014:ZDA:2650286.2650810} extends the NIZK functionality to allow for anonymous transactions, anonymous balances and coins, improved performance of transactions and sending of assets to a receivers fixed address without action required from the receiver.
 Zerocash makes use of a more efficient version of the NIZK, used in Zerocoin, called ZK \textit{Succinct Non-interactive ARguments of Knowledge} (zk-SNARK).
@@
 When a prosumer A wishes to select a group of signatures to sign her transaction as well, then it is likely that she will select many of the transactions from the adversary.
-Assuming the adversary spends his outputs without \textit{mixing}\footnote{The number of other signatures used in the ring.}, then A's transaction is exposed as well.~\cite{monero2014} Recent research  also show that up to 65\% of Monero transactions are trivially traceable using one attack.
-They also exposes two more attacks that have been amended in the latest versions of the protocol, lowering the amount of transactions traceable to 20\%.~\cite{monero2014,DBLP:journals/corr/MillerMLN17}
+Assuming the adversary spends his outputs without \textit{mixing}\footnote{The number of other signatures used in the ring.}, then A's transaction is exposed as well~\cite{monero2014}.
+Recent research  also show that up to 65\% of Monero transactions are trivially traceable using one attack.
+They also exposes two more attacks that have been amended in the latest versions of the protocol, lowering the amount of transactions traceable to 20\%~\cite{monero2014,DBLP:journals/corr/MillerMLN17}.
 
@@
 Another large practical drawback of Zerocash is the lack of programmability and functionality that would be required in PETra.
-Zhang \textit{et al.} solve some of the practical flaws and amend security issues.~\cite{zhangz}
+Zhang \textit{et al.} solve some of the practical flaws and amend security issues~\cite{zhangz}.
 

### 2017-12-07 docs/notes/PhaseIII/prosumer_trading.tex
no message

\documentclass{article}

\usepackage{fullpage}

\usepackage[hyphens]{url}
\usepackage[breaklinks,hidelinks]{hyperref}
\usepackage[anythingbreaks]{breakurl}

\begin{document}

\paragraph{Bidirectional Energy Trading and Residential Load Scheduling with Electric Vehicles in the Smart Grid} (2013)
\cite{kim2013bidirectional} \\
\url{http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=6547831} \\
\url{http://medianetlab.ee.ucla.edu/papers/Kim&Ren&vdS&Lee-BidirectionalEnergy-JSAC-2013.pdf}
\begin{itemize}
\item ``electricity load scheduling algorithms which jointly consider load scheduling for appliances and energy trading using electric vehicles''
\item customers: determine how much energy to purchase from or to sell to the aggregator, considering the load demands of their residential appliances and the associated electricity bill
\item approaches
\begin{itemize}
\item collaborative: optimal distributed load scheduling algorithm that maximizes the social welfare of the power system
\item non-collaborative: model the energy scheduling problem as a non-cooperative game among self-interested customers
\end{itemize}
\item impact of uncertainty: consider worst-case-uncertainty approach and develop distributed load scheduling algorithms that provide the guaranteed minimum performances in uncertain environments
\item ``energy trading leads to an increase in the social welfare''
\item customer incentives for participation
\end{itemize}

\paragraph{Demand Side Management in Smart Grids Using a Repeated Game Framework} (2014)
\cite{song2014demand} \\
\url{http://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=6840289}
\url{http://www.seas.ucla.edu/~linqi/smartgrids.pdf}
\begin{itemize}
\item ``model the interaction emerging among self-interested and foresighted consumers as a repeated energy scheduling game and prove that the stationary strategies are suboptimal in terms of long-term total billing and discomfort costs''
\item ``novel framework for determining optimal nonstationary demand-side management strategies, in which consumers can choose different daily power consumption patterns depending on their preferences, routines, and needs''
\item incentive compatible strategies
\end{itemize}

\paragraph{Optimal Residential Load Control with Price Prediction in Real-Time Electricity Pricing Environments} (2010)
\cite{mohsenian2010optimal} \\
\url{http://www.ee.ucr.edu/~hamed/MRLGjTSG10.pdf}
\begin{itemize}
\item ``lack of knowledge among users about how to respond to time-varying prices as well as the lack of effective building automation systems are two major barriers for fully utilizing the potential benefits of real-time pricing tariffs''
\item optimal and automatic residential energy consumption scheduling based on simple linear programming computations
\item ``residential load control strategy in real-time electricity pricing environments requires price prediction capabilities'' (especially if ``utility companies provide price information only one or two hours ahead of time'')
\item weighted average price prediction
\end{itemize}

\paragraph{Appliance Commitment for Household Load Scheduling} (2011)
\cite{du2011appliance} \\
\url{https://www.researchgate.net/profile/Ning_Lu4/publication/220592828_Appliance_Commitment_for_House_Hold_Load_Scheduling/links/53fdeb450cf2dca80003abf0.pdf}
\begin{itemize}
\item ``appliance commitment algorithm that schedules thermostatically controlled household loads based on price and consumption forecasts considering users’ comfort settings to meet an optimization objective such as minimum payment or maximum comfort''
\item two-step adjustment process: day-ahead scheduling and real-time adjustment
\item example: electrical water heater, whose thermal dynamics are modeled with physical methods
\item random hot water consumption: modeled with statistical methods
\item user comfort: set of linear constraints
\end{itemize}

\paragraph{Scheduling Power Consumption With Price Uncertainty} (2011)
\cite{kim2011scheduling} \\
\url{http://ieeexplore.ieee.org/abstract/document/5959241/}
\begin{itemize}
\item ``scheduling power consumption to minimize the expected cost at the consumer side''
\item scheduling problem: find decision thresholds for a Markov decision process (for both noninterruptible and interruptible loads under a deadline constraint)
\item incorporating the statistical knowledge about future prices into the scheduling policies can result in significant savings
\end{itemize}

\bibliographystyle{plain}
\bibliography{references}

\end{document}

### 2017-12-11 docs/papers/IoT2017/paper.tex
updated the layout
no message
updated copyright
switch to CCS 2012 classification

--- 2017-06-21 papers/IoT2017/paper.tex
@@
 \CopyrightYear{2017}
-%\setcopyright{acmcopyright}
 \setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-% DOI
-\doi{} %http://dx.doi.org/10.475/123_4}
-% ISBN
-\isbn{} %123-4567-24-567/08/06}
-%Conference
-\conferenceinfo{IoT'17,}{October 22--25, 2017, Linz, Austria}
-%Price
-\acmPrice{\$15.00}
+\conferenceinfo{IoT 2017,}{October 22--25, 2017, Linz, Austria}
+\isbn{978-1-4503-5318-2/17/10}\acmPrice{\$15.00}
+\doi{https://doi.org/10.1145/3131542.3131562}
 
@@
 
-\numberofauthors{3}
+\numberofauthors{4}
 \author{%
-%  \alignauthor{Leave Authors Anonymous\\
-%    \affaddr{for Submission}\\
-%    \affaddr{City, Country}\\
-%    \email{e-mail address}}\\
-%  \alignauthor{Leave Authors Anonymous\\
-%    \affaddr{for Submission}\\
-%    \affaddr{City, Country}\\
-%    \email{e-mail address}}\\
-%  \alignauthor{Leave Authors Anonymous\\
-%    \affaddr{for Submission}\\
-%    \affaddr{City, Country}\\
-%    \email{e-mail address}}\\
+ \alignauthor{Aron Laszka\\
+   \affaddr{Vanderbilt University}\\
+%   \affaddr{Nashville, TN}\\
+   \email{aron.laszka@vanderbilt.edu}}
+ \alignauthor{Abhishek Dubey\\
+\affaddr{Vanderbilt University}\\
+%   \affaddr{Nashville, TN}\\
+   \email{abhishek.dubey@vanderbilt.edu}}
+ \alignauthor{Michael Walker\\
+\affaddr{Vanderbilt University}\\
+%   \affaddr{Nashville, TN}\\
+   \email{michael.a.walker.1@vanderbilt.edu}}
+    \alignauthor{Doug Schmidt\\
+\affaddr{Vanderbilt University}\\
+%   \affaddr{Nashville, TN}\\
+   \email{d.schmidt@vanderbilt.edu}}
 }
@@
 
-% TODO!
-\category{K.6.m}{Miscellaneous}{Security}
-\category{D.4.7}{Organization and Design}{Distributed systems}
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10002978.10003022</concept_id>
+<concept_desc>Security and privacy~Software and application security</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10010520.10010553</concept_id>
+<concept_desc>Computer systems organization~Embedded and cyber-physical systems</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10010583.10010662.10010668</concept_id>
+<concept_desc>Hardware~Energy distribution</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[300]{Security and privacy~Software and application security}
+\ccsdesc[300]{Computer systems organization~Embedded and cyber-physical systems}
+\ccsdesc[300]{Hardware~Energy distribution}
+
+\vspace{-0.5em}
+\printccsdesc
+\vspace{-0.5em}
 
@@
 \input{concl.tex}
+
+\section*{Acknowledgment}
+This work was funded in part by a grant by Siemens Corporation, CT.
 

### 2018-03-13 code/TransactivePlatform/components/Contract.py
generic transactive platform

@@ -1,0 +1,113 @@
+import logging
+
+class Contract:
+  def encode_address(address):
+    return "000000000000000000000000" + address[2:]
+
+  def encode_uint(value):
+    return format(value, "064x")
+
+  def encode_int(value):
+    return format(value & 0xffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff, "064x")
+    
+  def encode_bool(value):
+    return Contract.encode_uint(1 if value else 0)
+ 
+  def decode_address(data, pos):
+    return "0x" + data[pos * 64 + 24 : (pos + 1) * 64]
+
+  def decode_uint(data, pos):
+    return int(data[pos * 64 : (pos + 1) * 64], 16)
+
+  def decode_int(data, pos):
+    uint = Contract.decode_uint(data, pos)
+    if uint > 0x7fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff:
+      uint -= 0x10000000000000000000000000000000000000000000000000000000000000000
+    return uint
+    
+  def decode_bool(data, pos):
+    uint = Contract.decode_uint(data, pos)
+    if uint == 1:
+      return True
+    elif uint == 0:
+      return False
+    raise Exception("Unexpected boolean value {}".format(uint))
+    
+  def generate_topics(self, events):
+    self.topics = {}
+    for event in events:
+      name = event.split("(")[0].strip()
+      topic = {'name': name}
+      params = []
+      for param in [s.strip() for s in event.split("(")[1].replace(")", "").split(",")]:
+        ptype = param.split(" ")[0]
+        pname = param.split(" ")[-1]
+        params.append((ptype, pname))
+      topic['params'] = params
+      signature = "{}({})".format(name, ",".join([ptype for (ptype, pname) in params]))
+      keccak256 = self.client.keccak256(signature)
+      if not (keccak256.startswith("0x") and len(keccak256) == 66):
+        raise Exception("Incorrect hash {} computed for signature {}!".format(keccak256, signature))
+      self.topics[keccak256] = topic 
+   
+  def __init__(self, client, address, events):
+    self.client = client # instance of EthereumClient
+    self.address = address # Ethereum contract address
+    self.filter_id = client.new_filter()
+    self.func_hash = {}
+    self.generate_topics(events)
+    
+  def call_func(self, from_account, name, *args):
+    # generate signature
+    arg_types = []
+    arg_values = []
+    for i in range(len(args) >> 1):
[…]

### 2018-03-13 code/TransactivePlatform/components/Directory.py

@@ -1,0 +1,59 @@
+import zmq
+import logging
+import sys
+from time import time, sleep
+from threading import Thread
+
+from config import *
+from EthereumClient import EthereumClient
+from ResourceAllocationContract import ResourceAllocationContract
+
+class Directory: 
+  def __init__(self, ip, port):
+    self.client = EthereumClient(ip=ip, port=port)    
+    self.account = self.client.accounts()[0] # use the first owned address
+    self.deploy_contract()
+    super(Directory, self).__init__()
+      
+  def run(self):
+    logging.info("Entering main function...")
+    client = zmq.Context().socket(zmq.REP)
+    client.bind(DIRECTORY_ADDRESS)
+    epoch = time() - START_INTERVAL * INTERVAL_LENGTH
+    logging.info("Listening for clients...")
+    while True:
+      msg = client.recv_pyobj()
+      if msg['request'] == "query_contract_address":
+        logging.info("query_contract_address()")
+        client.send_pyobj({'contract': self.contract_address, 'time': time() - epoch})
+      else:
+        logging.error("Unknown request: " + msg['request'])
+        client.send_pyobj("Unknown request!")
+      
+  def deploy_contract(self):
+    logging.info("Deploying contract...")
+    # use command function because we need to get the contract address later
+    receiptID = self.client.command("eth_sendTransaction", params=[{'data': BYTECODE, 'from': self.account, 'gas': TRANSACTION_GAS}])
+    logging.info("Transaction receipt: " + receiptID)
+    while True:
+      sleep(5)
+      logging.info("Waiting for contract to be mined... (block number: {})".format(self.client.command("eth_blockNumber", params=[])))
+      receipt = self.client.command("eth_getTransactionReceipt", params=[receiptID])
+      if receipt is not None:
+        self.contract_address = receipt['contractAddress']
+        break
+    self.contract = ResourceAllocationContract(self.client, self.contract_address)  
+    self.contract.setup(self.account, NUM_TYPES, PRECISION, MAX_QUANTITY)
+    logging.info("Contract address: " + self.contract_address)   
+    
+if __name__ == "__main__":
+  logging.basicConfig(format='%(asctime)s / %(levelname)s: %(message)s', level=logging.INFO)
+  ip = None
+  port = None
+  if len(sys.argv) > 1:
+    ip = sys.argv[1]
+  if len(sys.argv) > 2:
+    port = sys.argv[2]
+  directory = Directory(ip, port)
+  directory.run()
+

### 2018-03-13 code/TransactivePlatform/components/EventRecorder.py

@@ -1,0 +1,60 @@
+import zmq
+import logging
+import sys
+from time import time, sleep
+
+from config import *
+from EthereumClient import EthereumClient
+from ResourceAllocationContract import ResourceAllocationContract
+
+POLLING_INTERVAL = 1 # seconds
+
+class EventRecorder():
+  def __init__(self, ip, port):
+    logging.info("Connecting to directory...")
+    self.directory = zmq.Context().socket(zmq.REQ)
+    self.directory.connect(DIRECTORY_ADDRESS)
+    logging.info("Directory connected ({}).".format(self.directory))
+    self.query_contract_address()
+    logging.info("Setting up connection to Ethereum client...")
+    client = EthereumClient(ip=ip, port=port) 
+    self.account = client.accounts()[0] # use the first owned address
+    logging.info("Creating contract object...")
+    self.contract = MatchingContract(client, self.contract_address)
+
+  def run(self):
+    logging.info("Entering main loop...")
+    next_polling = time()
+    while True:
+      logging.debug("Polling events...")
+      simulation_time = time() - self.epoch
+      for event in self.contract.poll_events():
+        params = event['params']
+        name = event['name']
+        logging.info("[time = {}] {}({}).".format(simulation_time, name, params))
+        # TODO: record data to database
+      next_polling += POLLING_INTERVAL
+      sleep(max(next_polling - time(), 0))
+      
+  def query_contract_address(self):
+    msg = {
+      'request': "query_contract_address"
+    }
+    logging.info(msg)
+    self.directory.send_pyobj(msg)
+    response = self.directory.recv_pyobj()
+    self.epoch = time() - response['time']
+    self.contract_address = response['contract']
+    logging.info("Contract address: " + self.contract_address)
+
+if __name__ == "__main__":
+  logging.basicConfig(format='%(asctime)s / %(levelname)s: %(message)s', level=logging.INFO)
+  ip = None
+  port = None
+  if len(sys.argv) > 1:
+    ip = sys.argv[1]
+  if len(sys.argv) > 2:
+    port = sys.argv[2]
+  recorder = EventRecorder(ip, port)
+  recorder.run()
+

### 2018-03-13 code/TransactivePlatform/components/Prosumer.py

@@ -1,0 +1,68 @@
+import zmq
+import logging
+import sys
+from time import time, sleep
+from random import random
+
+from config import *
+from EthereumClient import EthereumClient
+from ResourceAllocationContract import ResourceAllocationContract
+
+POLLING_INTERVAL = 1 # seconds
+
+class Prosumer:
+  def __init__(self, prosumer_id, ip, port):
+    self.prosumer_id = prosumer_id
+    logging.info("Connecting to directory...")
+    self.directory = zmq.Context().socket(zmq.REQ)
+    self.directory.connect(DIRECTORY_ADDRESS)
+    logging.info("Directory connected ({}).".format(self.directory))
+    contract_address = self.query_contract_address()
+    logging.info("Setting up connection to Ethereum client...")
+    client = EthereumClient(ip=ip, port=port)
+    self.account = client.accounts()[0] # use the first owned address
+    self.contract = ResourceAllocationContract(client, contract_address)
+    super(Prosumer, self).__init__()
+
+  def run(self):
+    current_time = time()
+    time_interval = int(current_time - self.epoch) // INTERVAL_LENGTH
+    next_polling = current_time + POLLING_INTERVAL
+    # we stop after the END_INTERVAL
+    while time_interval <= END_INTERVAL:
+      current_time = time()
+      if current_time > next_polling:
+        logging.debug("Polling events...")
+        next_polling = current_time + POLLING_INTERVAL
+        for event in self.contract.poll_events():
+          params = event['params']
+          name = event['name']
+      sleep(max(next_polling - time(), 0))
+  
+  def query_contract_address(self):
+    msg = {
+      'request': "query_contract_address"
+    }
+    logging.info(msg)
+    self.directory.send_pyobj(msg)
+    response = self.directory.recv_pyobj()
+    self.epoch = time() - response['time']
+    contract_address = response['contract']
+    logging.info("Contract address: " + contract_address)
+    return contract_address
+
+if __name__ == "__main__":
+  prosumer_id = 101
+  ip = None
+  port = None
+  if len(sys.argv) > 1:
+    prosumer_id = int(sys.argv[1])
+  if len(sys.argv) > 2:
+    ip = sys.argv[2]
+  if len(sys.argv) > 3:
+    port = sys.argv[3]
+  logging.basicConfig(format='%(asctime)s / prosumer {} / %(levelname)s: %(message)s'.format(prosumer_id), level=logging.INFO)
+  trader = Prosumer(prosumer_id, ip, port) 
+  trader.run()
+
+    

### 2018-03-13 code/TransactivePlatform/components/ResourceAllocationContract.py

@@ -1,0 +1,54 @@
+import logging
+
+from Contract import Contract
+
+class ResourceAllocationContract(Contract):
+  def __init__(self, client, address):
+    super(ResourceAllocationContract, self).__init__(client, address, [
+      "OfferCreated(uint64 ID, bool providing, uint64 misc, uint64 prosumer)",
+      "OfferUpdated(uint64 ID, uint64 resourceType, uint64 quantity, uint64 value)",
+      "OfferPosted(uint64 ID)",
+      "SolutionCreated(uint64 ID, uint64 misc)",
+      "AssignmentAdded(uint64 ID, uint64 providingOfferID, uint64 consumingOfferID, uint64 resourceType, uint64 quantity, uint64 value, uint64 objective)",
+      "AssignmentFinalized(uint64 providingOfferID, uint64 consumingOfferID, uint64 resourceType, uint64 quantity, uint64 value)"
+    ])
+    
+  def setup(self, from_account, numTypes, precision, maxQuantity):
+    self.call_func(from_account, "setup",
+      "uint64", numTypes,
+      "uint64", precision,
+      "uint64", maxQuantity)      
+    
+  def createOffer(self, from_account, providing, misc, prosumer):
+    self.call_func(from_account, "createOffer",
+      "bool", providing,
+      "uint64", misc,
+      "uint64", prosumer)
+
+  def updateOffer(self, ID, resourceType, quantity, value):
+    self.call_func(from_account, "updateOffer", 
+      "uint64", ID, 
+      "uint64", resourceType, 
+      "uint64", quantity, 
+      "uint64", value)
+
+  def postOffer(self, from_account, ID):
+    self.call_func(from_account, "postSellingOffer", 
+      "uint64", ID)
+            
+  def createSolution(self, from_account, misc):
+    self.call_func(from_account, "createSolution",
+      "uint64", misc)
+    
+  def addAssignment(self, from_account, ID, providingOfferID, consumingOfferID, resourceType, quantity, value):
+    self.call_func(from_account, "addAssignment",
+      "uint64", ID,
+      "uint64", providingOfferID,
+      "uint64", consumingOfferID,
+      "uint64", resourceType,
+      "uint64", quantity,
+      "uint64", value)
+      
+  def finalize(self, from_account):
+    self.call_func(from_account, "finalize")
+

### 2018-03-13 code/TransactivePlatform/components/ResourceAllocationLP.py

@@ -1,0 +1,73 @@
+import logging
+
+from LinearProgramCplex import LinearProgramCplex 
+
+class Offer:
+  def __init__(self, ID, providing, prosumer, quantity={}, value={}):
+    self.ID = ID
+    self.providing = providing
+    self.prosumer = prosumer 
+    self.quantity = quantity
+    self.value = value
+    
+  def matchable(self, offer):
+    for res_type in self.quantity:
+      if res_type in offer.quantity:
+        if (self.providing and (not offer.providing) and (self.value[res_type] <= offer.value[res_type])) or ((not self.providing) and offer.providing and (self.value[res_type] >= offer.value[res_type])):
+          return True
+    return False
+    
+  def intersection(self, offer):
+    res_types = []
+    for res_type in self.quantity:
+      if res_type in offer.quantity:
+        if (self.providing and (not offer.providing) and (self.value[res_type] <= offer.value[res_type])) or ((not self.providing) and offer.providing and (self.value[res_type] >= offer.value[res_type])):
+          res_types.append(res_type)
+    return res_types
+
+class ResourceAllocationLP:
+  def __init__(self, precision):
+    self.precision = precision
+    
+  def solve(self, providing_offers, consuming_offers, lp_solver=LinearProgramCplex):
+    program = lp_solver()
+    variables = {}
+    prov_vars = {}
+    cons_vars = {}
+    for po in providing_offers:
+      for co in consuming_offers:
+        for t in po.intersection(co):
+          variable = {'po': po, 'co': co, 't': t}
+          varname = 'q_{}_{}_{}'.format(po.ID, c.ID, t)
+          variables[varname] = variable
+          if po in prov_vars:
+            prov_vars[po][varname] = po.quantity[t]
+          else:
+            prov_vars[po] = {varname: po.quantity[t]}
+          if co in cons_vars:
+            cons_vars[co][varname] = co.quantity[t]
+          else:
+            cons_vars[co] = {varname: co.quantity[t]}
+    if not len(variables):
+      logging.info("No matchable offers, skipping solver.")
+      return ([], 0)
+            
+    # TODO: add integer constraints based on precision
+    program.set_objective({varname: -1.0 for varname in variables})
+    for po in prov_vars:
+      program.add_constraint(
+        {varname: 1.0 / float(prov_vars[po][varname]) for varname in prov_vars[po]}, 1.0)
+    for co in cons_vars:
+      program.add_constraint(
[…]

### 2018-03-13 code/TransactivePlatform/components/Solver.py

@@ -1,0 +1,116 @@
+import zmq
+import logging
+import sys
+import os
+from time import time, sleep
+
+from config import *
+from ResourceAllocationLP import ResourceAllocationLP, Offer
+from EthereumClient import EthereumClient
+from ResourceAllocationContract import ResourceAllocationContract
+
+POLLING_INTERVAL = 1 # seconds
+
+class Solver(ResourceAllocationLP):
+  def __init__(self, ip, port, solverID):
+    self.solverID = solverID
+    logging.info("Connecting to directory...")
+    self.directory = zmq.Context().socket(zmq.REQ)
+    self.directory.connect(DIRECTORY_ADDRESS)
+    logging.info("Directory connected ({}).".format(self.directory))
+    self.query_contract_address()
+    logging.info("Setting up connection to Ethereum client...")
+    client = EthereumClient(ip=ip, port=port) 
+    self.account = client.accounts()[0] # use the first owned address
+    logging.info("Creating contract object...")
+    self.contract = ResourceAllocationContract(client, self.contract_address)
+    self.objective = 0
+    self.solution = None
+    super(Solver, self).__init__(PRECISION)
+
+  def run(self):
+    offers = {}
+    cons_offers = []
+    prov_offers = []
+    new_offers = False
+    waiting_solutionID = False
+    logging.info("Entering main loop...")
+    current_time = time()
+    next_polling = current_time + POLLING_INTERVAL
+    next_solving = current_time + SOLVING_INTERVAL
+    while True:
+      current_time = time()
+      if current_time > next_polling:
+        logging.debug("Polling events...")
+        next_polling = current_time + POLLING_INTERVAL
+        for event in self.contract.poll_events():
+          params = event['params']
+          name = event['name']
+          if name == "OfferCreated":  
+            logging.info("{}({}).".format(name, params))
+            offers[params['ID']] = Offer(params['ID'], params['providing'], params['prosumer'])
+          elif name == "OfferUpdated":
+            logging.info("{}({}).".format(name, params))  
+            offer = offers[params['ID']]
+            res_type = params['resourceType']
+            offer.quantity[res_type] = params['quantity']
+            offer.value[res_type] = params['value']
+          elif name == "OfferPosted":
+            logging.info("{}({}).".format(name, params))
+            new_offers = True
+            offer = offers[params['ID']]
+            if offer.providing:
+              prov_offers.append(offer)
+            else:
+              cons_offers.append(offer)
[…]

### 2018-03-13 code/TransactivePlatform/components/config.py

@@ -1,0 +1,8 @@
+# deployment
+DIRECTORY_ADDRESS = 'tcp://127.0.0.1:10001'
+TRANSACTION_GAS = "0x100000000"
+BYTECODE = "606060405260016000806101000a81548167ffffffffffffffff021916908367ffffffffffffffff160217905550640100000000600060086101000a81548167ffffffffffffffff021916908367ffffffffffffffff1602179055506001600060106101000a81548167ffffffffffffffff021916908367ffffffffffffffff1602179055506000600360006101000a81548167ffffffffffffffff021916908367ffffffffffffffff16021790555034156100ba57600080fd5b611755806100c96000396000f300606060405260043610610083576000357c0100000000000000000000000000000000000000000000000000000000900463ffffffff16806340d599c0146100885780634bb278f3146100db578063696e89d6146100f05780637f49f33c1461013b57806383bbb2cc14610168578063be38aaf0146101f4578063e1f967381461025a575b600080fd5b341561009357600080fd5b6100d9600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff16906020019091905050610287565b005b34156100e657600080fd5b6100ee610306565b005b34156100fb57600080fd5b6101396004808035151590602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff169060200190919050506105af565b005b341561014657600080fd5b610166600480803567ffffffffffffffff16906020019091905050610710565b005b341561017357600080fd5b6101f2600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff16906020019091905050610837565b005b34156101ff57600080fd5b610258600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190505061123f565b005b341561026557600080fd5b610285600480803567ffffffffffffffff169060200190919050506114ba565b005b826000806101000a81548167ffffffffffffffff021916908367ffffffffffffffff16021790555081600060086101000a81548167ffffffffffffffff021916908367ffffffffffffffff16021790555080600060106101000a81548167ffffffffffffffff021916908367ffffffffffffffff160217905550505050565b6000806103116115ab565b600060028054905011151561032557600080fd5b600
[…]

### 2018-03-13 code/TransactivePlatform/components/Prosumer.py
finished platform

@@ -22,6 +22,10 @@ class Prosumer:
     client = EthereumClient(ip=ip, port=port)
     self.account = client.accounts()[0] # use the first owned address
     self.contract = ResourceAllocationContract(client, contract_address)
+    # offer management
+    self.next_offer = 0 # offer ID that is unique within prosumer
+    self.pending_offers = {} # between createOffer and OfferCreated
+    self.created_offers = {} # between updateOffer and OfferUpdated
     super(Prosumer, self).__init__()
 
   def run(self):
@@ -37,7 +41,22 @@ class Prosumer:
         for event in self.contract.poll_events():
           params = event['params']
           name = event['name']
+          if (name == "OfferCreated") and (params['prosumer'] == self.prosumer_id):
+            offer = self.pending_offers.pop(params['misc'])
+            self.created_offers[params['ID']] = offer
+            for res_type in offer['quantity']:
+              self.contract.updateOffer(self.account, params['ID'], res_type, offer['quantity'][res_type], offer['value'][res_type])
+          elif (name == "OfferUpdated") and (params['ID'] in self.created_offers):
+            offer = self.created_offers[params['ID']]
+            offer['quantity'].pop(params['resourceType'])
+            if not len(offer['quantity']):
+              self.contract.postOffer(self.account, params['ID'])
       sleep(max(next_polling - time(), 0))
+      
+  def post_offer(self, providing, quantity, value):
+    self.pending_offers[self.next_offer] = {'quantity': quantity, 'value': value}
+    self.contract.createOffer(self.account, providing, self.next_offer, self.prosumer_id)
+    self.next_offer += 1
   
   def query_contract_address(self):
     msg = {

### 2018-03-13 code/TransactivePlatform/components/ResourceAllocationContract.py

@@ -25,7 +25,7 @@ class ResourceAllocationContract(Contract):
       "uint64", misc,
       "uint64", prosumer)
 
-  def updateOffer(self, ID, resourceType, quantity, value):
+  def updateOffer(self, from_account, ID, resourceType, quantity, value):
     self.call_func(from_account, "updateOffer", 
       "uint64", ID, 
       "uint64", resourceType, 

### 2018-03-13 code/TransactivePlatform/components/Solver.py

@@ -29,9 +29,9 @@ class Solver(ResourceAllocationLP):
     super(Solver, self).__init__(PRECISION)
 
   def run(self):
-    offers = {}
-    cons_offers = []
-    prov_offers = []
+    offers = {} # between OfferCreated and OfferPosted
+    cons_offers = [] # after OfferPosted
+    prov_offers = [] # after OfferPosted
     new_offers = False
     waiting_solutionID = False
     logging.info("Entering main loop...")

### 2018-03-15 code/PhaseII/fab/create.sh
add platibart to PhaseII

@@ -1,0 +1,66 @@
+#!/bin/bash
+
+##############################################################################
+#
+# Simple script to create a new test network based on provided config file.
+#
+# To use -> ./create <network-config-file.json>
+#
+# @Author Michael A. Walker
+# @Date   2017-08-09
+#
+##############################################################################
+
+### How to create a test network
+
+# simple timestamp method
+timestamp() {
+  date +"%T"
+}
+
+# delete temp files beforehand.
+
+rm -f ./static-nodes.json
+rm -f ./new-miners.json
+rm -f ./new-clients.json
+rm -rf ./new-blockchain/
+rm -f ./genesis-data.json
+
+#create start-timestamp
+timestamp
+
+OUT=../miner/tmp/
+mkdir --path $OUT
+
+#### create bootnodes and store them as 'static-nodes.json' for each etherium client connecting to them.
+# Uncomment this line if you wish to use bootnodes as Ethereum client discovery mechanism
+#./network-manager.py bootnodes create --file $1 --out=./static-nodes.json
+
+#### create each client (all 'clients' are prosumers in current version)
+./network-manager.py clients create --file $1 --out=./new-clients.json
+
+#### create each miners we have separate miners that do nothing but mine as an option, and we use it in our test network.
+./network-manager.py miners create --file $1 --out=./new-miners.json
+
+#### create a genesis blockchain configuration file with pre-loaded accounts for clients.
+./network-manager.py blockchains make --file $1 --clients ./new-clients.json
+
+
+#### make new blockchain from genesis-data created above, store in ./new-blockchain  directory
+./network-manager.py blockchains create --file genesis-data.json --datadir $OUT/new-blockchain/
+
+#### distribute static-nodes.json to each prosumer and each miner client
+# Uncomment these 2 lines if you wish to use bootnodes as Ethereum client discovery mechanism
+#./network-manager.py clients distribute --file $1 --local ./static-nodes.json
+#./network-manager.py miners distribute --file $1 --local ./static-nodes.json
+
+#### distribute the new blockchain genesis block to each client (including miners)
+./network-manager.py clients distribute --file $1 --local ./new-blockchain/
+
+./network-manager.py miners distribute --file $1 --local ./new-blockchain/
+
+#create end-timestamp
+timestamp
+
+#### Network is now created.
+echo "New test-network is now created."

### 2018-03-15 code/PhaseII/fab/miners/logic.py

@@ -1,0 +1,480 @@
+#!/usr/bin/python
+
+##############################################################################
+#
+#
+# @Author Michael A. Walker
+# @Date 2017-06-27
+#
+##############################################################################
+
+##############################################################################
+# imports
+##############################################################################
+
+import json
+from subprocess import call,check_output
+from StringIO import StringIO
+from subprocess import check_output,call
+import re
+import os.path
+import sys, os
+import stringcase
+
+import clients
+
+##############################################################################
+#
+##############################################################################
+
+def to_camel_case(name):
+# convert a string to camel_case all lower case.
+    print name
+    s1 = re.sub('(.)(\s)([A-Z][a-z]+)', r'\1_\3', name)
+    print s1
+    s2 = re.sub('([a-z0-9])([A-Z])', r'\1_\2', s1).lower()
+    print s2
+    return s2
+
+
+def readJsonFile(jsonFile, verbose=False):
+# read in a json file and print it if verbose
+    if os.path.isfile(jsonFile) <> True:
+        print "Operand provided to be the network config file was not a file."
+        sys.exit(2)
+        return
+
+    with open(str(jsonFile)) as data_file:
+        data = json.load(data_file)
+
+    # read in the configuration JSON file
+    if verbose:
+        print "\nRead in the following network-config json file:\n"
+        print json.dumps(data, indent=4, sort_keys=False) + "\n"
+
+    return data
+
+
+def getMinerJsonValues(jsonFile, verbose=False):
+# create all prosumer clients
+    data = readJsonFile(jsonFile, verbose)
+
+    try:
+
+        ##########################################################################
+        # get the values from the JSON file
+        ##########################################################################
+
+        # network specific data
+        configurationName = data["configurationName"]
+        configurationVersion = data["configurationVersion"]
+
+        # genesis block data
+        chainId = data["chainId"]
+        difficulty= data["difficulty"]
+        gasLimit = data["gasLimit"]
+        balance = data["balance"]
+        genesisBlockOutFile = data["genesisBlockOutFile"]
+
+        # clients data
+        clients = data["clients"]
+        clientStartPort = clients["startPort"]
+
+        # prosumer data
[…]

### 2018-03-15 code/PhaseII/fab/test/pycurlUpgraded.py

@@ -1,0 +1,116 @@
+#!/usr/bin/python3
+
+##############################################################################
+#
+# Sample program to interact with ethereum RPC "2.0" with python.
+#
+#    Uses pycurl to HTTP POST query and returns json data.
+#
+# @Author   Michael A. Walker
+# @Date     2017-08-06
+#
+##############################################################################
+
+import pycurl, json
+from io import BytesIO
+
+def rpcCommand(method,params=[],ip='localhost',port='9012',id=1,jsonrpc="2.0",verbose=False):
+    # the <ip:port> to connect to
+    ipPort = str(ip) + ":" + str(port)
+    # buffer to capture output
+    buffer = BytesIO()
+    # start building curl command to process
+    try:
+        c = pycurl.Curl()
+        c.setopt(pycurl.URL, ipPort)
+        c.setopt(pycurl.HTTPHEADER, ['Accept:application/json'])
+        c.setopt(pycurl.WRITEFUNCTION, buffer.write)
+        data2 = {"jsonrpc":str(jsonrpc),"method": str(method),"params":params,"id":str(id)}
+        data = json.dumps(data2)
+        c.setopt(pycurl.POST, 1)
+        c.setopt(pycurl.POSTFIELDS, data)
+        if verbose:
+            c.setopt(pycurl.VERBOSE, 1)
+        #perform pycurl
+        c.perform()
+
+        # check response code (HTTP codes)
+        if (c.getinfo(pycurl.RESPONSE_CODE) != 200):
+ #           raise Exception('rpc_communication_error', 'return_code_not_200')
+            return {'error':'rpc_comm_error','desc':'return_code_not_200','error_num':None}
+        #close pycurl object
+        c.close()
+    except pycurl.error as e:
+        c.close()
+#        raise Exception('rpc_communication_error', 'return_code_not_200')\
+        errno, message = e.args
+        return {'error':'rpc_comm_error','desc':message,'error_num':errno}
+
+
+    # decode result
+    results = str(buffer.getvalue().decode('iso-8859-1'))
+    if verbose:
+        print (results)
+
+    # convert result to json object for parsing
+    data = json.loads(results)
+    # return appropriate result
+    if 'result' in data.keys():
+        return data["result"]
+    else:
+        if 'error' in data.keys():
+            return data
+        else:
+            return {"error":"Unknown Error: possible method/parameter(s) were wrong and/or networking issue."}
+
+
[…]

### 2018-03-16 code/PhaseII/fab/create.sh
getting closer

@@ -29,9 +29,6 @@ rm -f ./genesis-data.json
 #create start-timestamp
 timestamp
 
-OUT=../miner/tmp/
-mkdir --path $OUT
-
 #### create bootnodes and store them as 'static-nodes.json' for each etherium client connecting to them.
 # Uncomment this line if you wish to use bootnodes as Ethereum client discovery mechanism
 #./network-manager.py bootnodes create --file $1 --out=./static-nodes.json
@@ -47,7 +44,7 @@ mkdir --path $OUT
 
 
 #### make new blockchain from genesis-data created above, store in ./new-blockchain  directory
-./network-manager.py blockchains create --file genesis-data.json --datadir $OUT/new-blockchain/
+./network-manager.py blockchains create --file genesis-data.json --datadir ./new-blockchain/
 
 #### distribute static-nodes.json to each prosumer and each miner client
 # Uncomment these 2 lines if you wish to use bootnodes as Ethereum client discovery mechanism

### 2018-03-16 code/PhaseII/fab/fabfile.py

@@ -153,7 +153,7 @@ def startClients(numberOfClients,
                 mineThreads=1,
                 etherbase='0x0000000000000000000000000000000000000000',
                 overrideCommand='',
-                netrestrict='10.4.0.0/16'):
+                netrestrict='127.0.0.0/16'):
     fh = StringIO();
     result=''
     verboseResults = ''
@@ -161,6 +161,7 @@ def startClients(numberOfClients,
 
     port = int(startPort)
     for i in range(1,int(numberOfClients)+1):
+        fullDataDir = str(datadir) + "/" + str(i).rjust(5,'0')
         command = "geth --password ./password.txt"
         command += " --datadir " + str(datadir) + "/"  + str(i).rjust(5,'0')
         command += " --networkid " + str(network)
@@ -177,6 +178,8 @@ def startClients(numberOfClients,
         if isMiner == 'True':
             command += " --mine --minerthreads=" + str(mineThreads)  + " --etherbase=" + str(etherbase)
         name += str(i).rjust(5,'0')
+
+        command += ">" + fullDataDir + "/output.log" + " 2>&1"
 
         # run built command or 'overrideCommand'
         if overrideCommand <> '':

### 2018-03-16 code/PhaseII/fab/miners/logic.py

@@ -231,13 +231,15 @@ def connectMinerClients(jsonFile,verbose=False):
         print data
 
     configurationName , configurationVersion, minerHostAllocation, clientStartPort, networkId = getMinerJsonValues(jsonFile,verbose)
+    print "minerHostAllocation" 
+    print minerHostAllocation
 
     for host in minerHostAllocation:
         verboseResults += "\nresults: "
 
         for enode in data['enodes']:
 #            print enode + "\n"
-            results = check_output(["./test/pycurlAddPeer.py", str(host), str(minerHostAllocation[host]+int(clientStartPort)+2000-1), str(enode) ])
+            results = check_output(["./test/pycurlAddPeer.py", str(host), str(minerHostAllocation[host]+int(clientStartPort)+3000-1), str(enode) ])
             verboseResults += "\n" + str(results)
     if verbose:
         print verboseResults
@@ -252,7 +254,7 @@ def startMinerClients(jsonFile,verbose=False):
     verboseResults = ""
 
     # make variable to hold current Port to use for clients
-    currentProsumerRpcPort = int(clientStartPort) + 2000
+    currentProsumerRpcPort = int(clientStartPort) + 3000
 
     verboseResults = "prosumer port start = " + str(currentProsumerRpcPort)
 

### 2018-03-16 code/PhaseII/fab/start.sh

@@ -21,7 +21,7 @@
 
 # Gets the enode of each client, & adds each client as a peer of each miner
 # This creates a star-graph from each miner to each prosumer/dso.
-./network-manager.py miners connect --file $1
+./network-manager.py miners connect --file $1 --verbose
 
 ## Network is now running and connected
 

### 2018-03-16 code/PhaseII/launch-market.sh

@@ -21,10 +21,10 @@ DIR=$(pwd)
 echo $DIR
 rm -rf logs/*
 
-nohup python3 components/DSOWrapper.py $MINER 10000 > logs/DSO.out 2>&1 &
+nohup python3 components/DSOWrapper.py $MINER 9000 > logs/DSO.out 2>&1 &
 sleep 5
-nohup python3 components/MatchingSolverWrapper.py $MINER 10000 > logs/Solver.out 2>&1 &
-nohup python3 components/EventRecorder.py $MINER 10000 > logs/Recorder.out 2>&1 &
+nohup python3 components/MatchingSolverWrapper.py $MINER 9000 > logs/Solver.out 2>&1 &
+nohup python3 components/EventRecorder.py $MINER 9000 > logs/Recorder.out 2>&1 &
 
 #rm -rf $DIR/test-10-11-withbattery/prosumer*
 #$DIR/test-10-11-withbattery/testrun.sh

### 2018-03-16 code/PhaseII/test-10-11-withbattery/testrun.sh

@@ -8,5 +8,5 @@ echo PARENT $PARENT
 for i in `ls $DIR/all_data/ | cut -d '_' -f2 |tr -d "*.csv"`;
 do
 echo "launching prosumer $i"
-nohup python3 components/SmartHomeTraderWrapper.py $i localhost 10000 > test-10-11-withbattery/prosumer$i.out 2>&1 &
+nohup python3 components/SmartHomeTraderWrapper.py $i localhost 9000 > test-10-11-withbattery/prosumer$i.out 2>&1 &
 done

### 2018-03-16 code/PhaseII/fab/miners/logic.py
fixed logic of miners/logic connectMinerClients(...) to handle multiple miners per host.

@@ -234,13 +234,16 @@ def connectMinerClients(jsonFile,verbose=False):
     print "minerHostAllocation" 
     print minerHostAllocation
 
+    # for each host
     for host in minerHostAllocation:
         verboseResults += "\nresults: "
-
-        for enode in data['enodes']:
-#            print enode + "\n"
-            results = check_output(["./test/pycurlAddPeer.py", str(host), str(minerHostAllocation[host]+int(clientStartPort)+3000-1), str(enode) ])
-            verboseResults += "\n" + str(results)
+        # for each miner on each host
+        for minerNum in minerHostAllocation[host]:
+            # for each 'client' enode that is being paired with each host/minerNum(port) pair.
+            for enode in data['enodes']:
+#                print enode + "\n"
+                results = check_output(["./test/pycurlAddPeer.py", str(host), str(minerNum+int(clientStartPort)+3000-1), str(enode) ])
+                verboseResults += "\n" + str(results)
     if verbose:
         print verboseResults
 

### 2018-03-16 code/PhaseII/fab/miners/logic.py
fixed logic of miners/logic connectMinerClients(...) to handle multiple miners per host. v2

@@ -238,7 +238,7 @@ def connectMinerClients(jsonFile,verbose=False):
     for host in minerHostAllocation:
         verboseResults += "\nresults: "
         # for each miner on each host
-        for minerNum in minerHostAllocation[host]:
+        for minerNum in range(1, int(minerHostAllocation[host])):
             # for each 'client' enode that is being paired with each host/minerNum(port) pair.
             for enode in data['enodes']:
 #                print enode + "\n"

### 2018-04-16 docs/papers/IEEEBlockchain2018/conclusion.tex
added Blockchain paper

% Section 7
% Conclusion:
% - discussion 
% - future work?

%\color{red}

Smart and connected community applications require decentralized and scalable platforms due to the large number of participants and the lack of mutual trust between them. In this paper,  we introduced a transactive platform for resource allocation, called \Platform. We first formulated a general problem that can be used to represent a variety of resource allocation problems in smart and connected communities. Then, we described an efficient and trustworthy platform based on a hybrid approach, which combines the efficiency of traditional computing environments with the trustworthiness of blockchain-based smart contracts. Finally, we demonstrated the applicability of our platform using two case studies based on real-world data.

% Challenges in smart and connected communities: lack of trust, large number of participants, distributed system \newline
% To overcome these challenges, in this paper,
% \begin{itemize}
%     \item we introduced a transactive platform for resource allocation
%     \item we formulated a general problem that can be used to represent resource allocation problems in various smart and connected communities
%     \item we described an efficient and trustworthy platform based on a hybrid approach that combines the efficiency of traditional computing environments with the trustworthiness of blockchain based smart contracts
%     \item we evaluated and demonstrated the applicability of our platform using two case studies based on real-world data
% \end{itemize}
% \color{black}

### 2018-04-16 docs/papers/IEEEBlockchain2018/fsolidm.tex
added Blockchain paper

\label{sec:smartcontract}

We implement a smart contract that can (1) verify whether a solution is feasible and (2) compute the value of the objective function for a feasible solution.
Compared to finding an optimal solution, these operations are computationally inexpensive, and they can easily be performed on a blockchain-based decentralized platform. Thus, we implement a smart contract that provides the following functionality:
\begin{itemize}
\item Solutions may be submitted to the contract at any time during the solving phase. 
The contract verifies the feasibility of each submitted solution, and if the solution is feasible, then it computes the value of the objective function.
The contract always keeps track of the best feasible solution submitted so far, which we call the \emph{candidate solution}.
\item At the end of the solving phase, the contract finalizes resource assignments for the cycle based on the candidate solution. If no solution has been submitted to the contract, then an empty allocation is used as a solution, which is always feasible but attains zero objective. % which might be the case right after the trading system has been launched then the finalization event does not return any solution.
%\item Upon finalization, the contract must notify providers and consumers about finalized assignments. 
%This can be done using the event filter mechanisms provided by blockchains like Ethereuem. \cite{ref}.
\end{itemize}

This simple functionality achieves a high level of security and reliability.
Firstly, it is clear that an adversary cannot force the contract to finalize assignments based on an incorrect (i.e., infeasible) solution since such a solution would be rejected.
Similarly, an adversary cannot force the contract to choose an inferior solution instead of a superior one.
In sum, the only action available to the adversary is proposing a superior feasible solution, which would actually improve the transactive management platform.

%\Aron{This paragraph should be omitted (and included in the Industrial Informatics paper).}
%The contract is also reliable and can tolerate temporary disruptions in the solver or the communication network. As the sets of offers can only grow over time, the contract can use a candidate solution submitted during time interval $t$ to finalize assignments in any subsequent time interval $\tau > t$.
%In fact, without receiving new solutions, the difference between the amount of finalized assignments and the optimum will increase only gradually:
%since the earlier candidate solution can specify assignments for any future time interval,
%the difference is only due to the offers that have been posted since the solution was found and submitted.

%\subsection{Correct-by-Construction Design of the Smart Contract}
To ensure that the smart-contract code is correct-by-construction~\cite{sifakis2013RSD}, we use the formal design environment FSolidM~\cite{mavridou2018designing} to design and generate the Solidity code of the smart contract. FSolidM allows designing Ethereum smart contracts as Labelled Transition Systems (LTS) with formal semantics. Each LTS can then be given to the NuSMV model checker~\cite{cimatti2002nusmv} to verify liveness, deadlock-freedom, and safety properties, which can capture important security concerns. % and vulnerabilities.

\begin{figure}[t]
\centering
\includegraphics[width=0.8\columnwidth]{ResourceAllocationFSM.pdf}
\caption{FSolidM model of the \Platform smart contract.}
\label{fig:FSM}
\end{figure}

%\ad{Aron - please explain all the states of the smart contract here. The state machine diagram should be updated as well. please describe the mapping structure - how types are mapped in the smart contract here as well.}
%\Aron{What do you mean by mapping structure?}
%\Anastasia{I have updated the LTS figure and the description. }

In Figure~\ref{fig:FSM}, we present the LTS representation of the transactive-platform smart contract, designed with FSolidM. The contract has three states:\footnote{Generated smart-contract code is not included in the paper because of space constraints. However, interested readers can view the code at \texttt{\url{https://github.com/visor-vu/transaction-management-platform}}}
\begin{itemize}[noitemsep, topsep=0pt, leftmargin=1em]
    \item \texttt{Init}, in which the contract has been deployed but  not been initialized. Before the contract can be used, it must be initialized (i.e., numerical parameters must be set~up).
    \item \texttt{Receive}, which corresponds to the \emph{offering} phase of a cycle (see Section~\ref{sec:scheduling}).
    In this state, prosumers may post (or cancel) their offers.
    \item \texttt{Solve}, which corresponds to the \emph{solving} phase of a cycle (see Section~\ref{sec:scheduling}). In this state, solvers may submit solutions (i.e., resource allocations) based on the posted (but not cancelled) offers.
\end{itemize}

In FSolidM, smart-contract functions are modeled as LTS transitions. Note that by design, each function may be executed only if the contract is in the origin state of the corresponding transition.
Our smart contract  has the following transitions (after the name of each transition, we list the function parameters):
\begin{itemize}[leftmargin=1em, noitemsep]
    \item from state \texttt{Init}:
    \begin{itemize}[noitemsep, leftmargin=0.5em]
        \item \texttt{setup(uint64 numTypes, uint64 precision, uint64 maxQuantity)}: initializes a contract with numerical parameter values, setting up the number of resource types, the arithmetic precision for calculations, and the maximum quantity that may be offered; upon execution, the contract transitions to state \texttt{Receive}.
    \end{itemize}
    \item from state \texttt{Receive}:
    \begin{itemize}[noitemsep, leftmargin=0.5em]
        \item \texttt{createOffer(bool providing, uint64 misc))}: creates a blank offer (belonging to the prosumer invoking this transition) within the smart contract; parameter \texttt{providing} is true for providers and false for consumers, parameter \texttt{misc} is an arbitrary value that prosumers may use for their own purposes (e.g., to distinguish between their own offers); emits an \texttt{OfferCreated} event.
        \item \texttt{updateOffer(uint64 ID, uint64 resourceType, uint64 quantity, uint64 value)}: sets quantity and value for a resource type in an existing  offer (identified by the \texttt{ID} given in the \texttt{OfferCreated} event); may be invoked only by the entity that created the offer, and only if the offer exists but has not been posted yet; emits an \texttt{OfferUpdated} event.
        \item \texttt{postOffer(uint64 ID)}: posts an existing offer, enabling solvers to include this offer in a solution; may be invoked only by the entity that created the offer; emits an \texttt{OfferPosted} event.
        \item \texttt{cancelOffer(uint64 ID)}: cancels (i.e., ``unposts'') an offer, forbidding solvers from including this offer in a solution; may be invoked only by the entity that created the offer; emits an \texttt{OfferCanceled} event.
        \item \texttt{close()}: protected by a  guard condition on time, which prevents the execution of this transition before the offering phase of the current cycle ends; transitions to state \texttt{Solve}; emits a \texttt{Closed} event.
    \end{itemize}
    \item from state \texttt{Solve}:
    \begin{itemize}[noitemsep, leftmargin=0.5em]
        \item \texttt{createSolution(uint64 misc)}: creates a new, empty solution (i.e., resource allocation) within the smart contract; parameter \texttt{misc} is an arbitrary value that solvers may use for their own purposes (e.g., to distinguish between their own solutions); emits a \texttt{SolutionCreated} event.
        \item \texttt{addAssignment(uint64 ID, uint64 providingOfferID, uint64 consumingOfferID, uint64 resourceType, uint64 quantity, uint64 value)}: adds a resource assignment to an existing solution (identified by the \texttt{ID} given in the \texttt{SolutionCreated} event); may be invoked only by the entity that created the solution; checks a number of constraints ensuring that the solution remains valid if this assignment is added; emits an \texttt{AssignmentAdded} event.
        \item \texttt{finalize()}: selects the best solution and finalizes it by emitting an \texttt{AssignmentFinalized} event for each assignment in the solution; protected by a guard condition on time, which prevents the execution of this transition before the solving phase of the current cycle ends; transitions to state \texttt{Receive}.
    \end{itemize}
\end{itemize}
Notice that posting an offer and submitting a solution require at least three and two function calls, respectively.
The reason for dividing these operations into multiple functions is to ensure that the computational costs of these functions are constant.
Otherwise, posting a complex offer or submitting a complex solution could be infeasible due to large computational costs, which could exceed the gas limit.\footnote{In Ethereum, each transaction is allowed to consume only a limited amount of gas, which corresponds to the computational and storage cost of executing the transaction.}

% \begin{lstlisting}[language=Solidity, caption=Extract of the Generated Smart Contract. Full contract is available at \url{https://github.com/visor-vu/transaction-management-platform}. ,label={lst:finalize}]
% pragma solidity ^0.4.19;
% contract SolidWorx {     
%     function setup(...) public {
%         //setup SolidWorx to be used with a fixed type of resources. 
%     }
%     //This is the syntax of an offer.
%     struct Offer {
%         bool providing; 
%         // true: providing offer
%         // false: consumption offer
%         uint64 prosumer; 
%         bool posted;
%         mapping(uint64 => uint64) quantity;
%         mapping(uint64 => uint64) value;
%     }
%     //syntax of an Assignment
%     struct Assignment {
%         uint64 providingOfferID;
%         uint64 consumingOfferID;
%         uint64 resourceType;
%         uint64 quantity;
%         uint64 value;
%     }
%     //A solution contains many assignments.
%     struct Solution {
%         mapping(uint64 => Assignment) assignments;
%         uint64 numAssignments;
%         uint64 objective;
%         mapping(uint64 => uint256) allocated;     
%     }
%     function createOffer(bool providing, uint64 misc, uint64 prosumer) public {
%         ...
%     }
%     function updateOffer(uint64 ID, uint64 resourceType, uint64 quantity, uint64 value) public {
%         ...
%     }
%     function postOffer(uint64 ID) public {
%         ...
%     }
%     function cancelOffer(uint64 ID) public {
%         ...
%     }
%     ...
%     function createSolution(uint64 misc) public {
%         ...
%     }
%     function addAssignment(...) public {
%         ...
%     }
%     function finalize() public {
%         ...
%     }
% }
% \end{lstlisting}

%Listing \ref{lst:finalize} presents the generated API and the guards for the smart contract in \Platform.

%\subsection{Operation Workflow }

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{Workflow.pdf}
    \caption{A possible sequence of operations in \Platform. Underlined text denotes events emitted by the smart contract. Some events, such as \texttt{OfferUpdated}, are omitted for simplicity. %The offers can be updated by a prosumer before they are marked as posted. 
    %See Listing \ref{lst:finalize} for the API.} % Prosumers and Solvers use the directory to find one of the miner nodes running the smart contract. They then connect to the  mining node.
    }
    \vspace{-0.1in}
    \label{fig:workflow}
\end{figure}

 A typical sequence of function calls and events in \Platform is shown in Figure \ref{fig:workflow}.

### 2018-04-16 docs/papers/IEEEBlockchain2018/introduction.tex
added Blockchain paper

%
% - motivation: in a smart and connected community, a number of stakeholders must collaborate and share/trade resources
%   * trust problem: stakeholders may have limited trust in each other
%   * distributed system problem: large number of stakeholder must cooperate and reach consensus on the state of the market
%   * auditability requirement: market must be transparent
%   * resilience problem: malicious or negligent stakeholder threaten the entire community

% decentralized ledger and computational platform
% - challenges:
%   * efficiency <- large number of transaction must be cleared in short amount of time
%   * privacy <- personal information from residents
%   * correctness <- critical infrastructure for smart communities
%
Smart and connected communities (SCC) as a research area lies at the intersection of social science, machine learning, cyber-physical systems, civil infrastructures, and data sciences. This research area is  enabled by the rapid and transformational changes driven by  innovations in smart sensors, such as cameras and air quality monitors, which are now  embedded in almost every physical device and system that we use, ranging from watches and smartphones to automobiles, homes, roads, and workplaces. 
%Coupled with emerging new modes of networking, new algorithms for data analytics, and new paradigms of distributed computing like fog computing, these sensors create an ``Internet of Things'' (IoT)  that provide endless opportunities for innovation and improving the quality of life, such as improved transportation with reduced congestion and more efficient uses of energy and water. 
The effects of these innovations can be seen in a number of diverse domains, including transportation, energy, emergency response, and  health care, to name a few.

\ifExtended
At its core, smart and connected community applications are distributed programs where the results received by the end users or the performance that they experience is affected by others using the same application. A classical example of this kind is traffic routing,  implemented by many commercial mobility planning solutions, such as Waze and Google. The routes provided to the end users depend upon the interaction that other users in the systems have had with the application. An effective route planning solution will be proactive in the sense that it will analyze the demands being made by users and will use the dynamic demand model for effectively distributing vehicles and people across space, time, and modes of transportation, improving the efficiency of the mobility system and leading to a reduction of congestion.
\fi

At its core, a smart and connected community is a
%Thus, an SCC system can be abstracted as a 
multi-agent system where agents may enter or leave the system for different reasons. Agents may act on behalf of service owners, managing access to services and ensuring that contracts are fulfilled. Agents can also act on behalf of service consumers, locating services, making contracts, as well as receiving and presenting results.
For example, agents may coordinate carpooling services. Another example of such coordination exists in transactive energy systems~\cite{Gridwise}, where homeowners in a community exchange excess energy. Consequently, these  agents are required to engage in interactions, negotiate with each other, enter agreements, and make proactive run-time decisions---individually and collectively---while responding to changing circumstances. %In some cases,  agents also need to collaborate within organizations and to form coalitions of agents with different capabilities in support of virtual organizations in order to reach global and individual goals.

This exchange of information and resources  leads to a problem where the stakeholders of the system may have limited trust in each other. Thus, collaboratively reaching consensus on when, how, and who should access certain resources becomes problematic. However, instead of solving these problems in a domain specific manner, we present \Platform  and show how this platform can provide key design patterns to implement mechanisms for arbitrating resource consumption across different SCC applications.

Blockchains may form a key component of SCC platforms because they enable participants to reach a consensus on the value of any state variable in the system, without relying on a trusted third party or trusting each other. Distributed consensus not only solves the trust issue, but also provides fault-tolerance since consensus is always reached on the correct state as long as the number of faulty nodes is below a threshold. Further, blockchains can also enable performing computation in a distributed and trustworthy manner in the form of smart contracts. However, while the distributed integrity of a blockchain ledger presents unique opportunities, it also introduces new assurance challenges that must be addressed before protocols and implementations can live up to their potential. For instance, Ethereum smart contracts deployed in practice are riddled with bugs and security vulnerabilities.  Thus, we use a correct-by-construction design toolchain, called FSolidM \cite{mavridou2018designing}, to design and implement  the smart-contract code of \Platform. 
\ifExtended
Finally, we present an evaluation of the architecture using a community-based energy-sharing problem and a carpooling problem.
\fi

The outline of this paper is as follows. We formulate a resource-allocation problem for SCC in Section~\ref{sec:problem},  describing two concrete  applications of the platform in Section~\ref{sec:ExaApp} and presenting extensions to the basic problem formulation in Section~\ref{sec:ProForExt}. We describe our solution architecture in Section~\ref{sec:solution}, which consists of off-blockchain solvers (Section~\ref{sec:solver}) and a smart contract (Section~\ref{sec:smartcontract}), providing a brief analysis in Section~\ref{sec:analysis}. In Section~\ref{sec:results}, we evaluate \Platform using two case studies, a carpooling assignment (Section~\ref{sec:carpool})
 and an energy trading system  (Section~\ref{sec:energy}). Finally, we discuss the architecture of \Platform in the context of related research in Section~\ref{sec:related},  and we provide concluding remarks in Section \ref{sec:conclusion}.

%\Aron{Do we?} Thus, we present a formal analysis and  a proof of correctness for our architecture.  Finally, we present an evaluation of the architecture using a community energy sharing problem and a carpooling problem.

%Table \ref{tab:innovations} describe the key innovations of \Platform compared to the state of the art.

%\textcolor{red}{The outline of this paper is as follows...}

### 2018-04-16 docs/papers/IEEEBlockchain2018/related.tex
added Blockchain paper

%\section{Related Research}
%Section 2
%Related Work
%- PETra
%- other papers

\ifExtended
Our paper is related to three concepts (a) online information management platform for scheduling transactions, (b) managing trust and integrity using distributed consensus mechanisms provided by block-chains and (c) correctness of architecture. 
%\ifExtended
Since smart contracts are the basis for providing trust and integrity, their correctness is very important. Thus, we discuss related work in correctness checks and auto-generation of smart contracts in this section as well.
\fi

\textbf{Online Information Management Platforms:}
Smart and connected community systems are designed to collect, process, transmit, and analyze data. In this context, data collection usually happens at the edge because that is where edge devices with sensors are deployed to monitor surrounding environments. \Platform does not suggest a specific data collection methodology. Rather, it follows an actor-driven design pattern where ``prosumer'' actors can integrate their own agents into \Platform by using the provided APIs.  Another concern of these platforms is the cost of processing. Traditionally, this problem was solved using scalable cloud resources in-house~\cite{schmidt2014elastic}. However, \Platform enables a decentralized ecosystem, where components of the platform can run directly on edge nodes, which is one of the reasons why we designed it to be asynchronous in nature.

To an extent, the information architecture of \Platform can be compared to  dataflow engines~\cite{Storm, Spark, neumeyer2010s4}. All of these existing dataflow engines use some form of a computation graph, comprising computation nodes and dataflow edges. These engines are designed for batch-processing and/or stream-processing high volumes of data in resource intensive nodes, and do not necessarily provide additional ``platform services'' like trust management or solver nodes. 
\ifExtended
There are solutions that build upon middleware mechanisms like FIWARE, for example \cite{lopez2017software}. However, they do not provide mechanisms to manage trust by allowing the community architecture to operate without intermediaries. 
\fi
%Our architecture uses the concept of a ``directory'' actor, however, as discussed earlier it can also be decentralized \cite{riaps1}.

\textbf{Integration with Blockchains:}
\Platform integrates a blockchain because it enables the digital representation of resources, such as energy and financial assets, and their secure transfer from one  party to another. Further, blockchains constitute an immutable, complete, and fully auditable record of all transactions that have ever occurred in the  system. This is in line with the increased interest and commercial adoption of blockchains~\cite{TheTruthAdoption:online}, which %. For example, blockchain adoption %in the financial industry 
has yielded market capitalization surpassing \$75 billion USD~\cite{BitcoinPrices:online} for Bitcoin and \$36 billion USD for Ethereum ~\cite{EthereumPrices:online}. Prior work has also considered the security and privacy of IoT and Blockchain integrations~\cite{dorri2017blockchain,ouaddah2017towards,christidis2016blockchains}.

The biggest challenge  in these integrated systems comes from computational-complexity limitations and from the complexity of the consensus algorithms. 
In particular, their transaction-confirmation time is relatively long and variable, primarily due to the widely-used proof-of-work algorithm. % and most of the communication occurring via the ledger. 
Further, blockchain-based  computation is relatively expensive, which is the main reason why we  separated finding a solution and validating the solution into two separate components in \Platform.

\textbf{Correctness of Smart Contracts:}
% \ad{Anastasia can you please 
% - write about possible bugs and problems
% - what are other mechanisms
% - what is special about our approach}
% \Anastasia{Partly done. I am not sure we should write about typical bugs (e.g. reentrancy) since our contract does not exploit any.}
% \ad{No that is okay. I agree with your comment.}
%work has focused on formal verification of smart contracts~\cite{kumaresan2014use}, and how to write smart contracts ``defensively''~\cite{delmolino2016step} to avoid exceptions when multiple contracts interact. 
Both verification and automated vulnerability discovery are considered in the literature for identifying smart-contract vulnerabilities. 
For example, Hirai performs a formal verification of a smart contract that is used by the Ethereum Name Service~\cite{hirai2016formal}.
However, this verification proves only one particular property and it involves relatively large amount of manual analysis.
In later work, Hirai defines the complete instruction set of the Ethereum Virtual Machine in Lem, a language that can be compiled for interactive theorem provers~\cite{hirai2017defining}.
Using this definition, certain safety properties can be proven for existing contracts.

Bhargavan et al.\ outline a framework for verifying the safety and correctness of Ethereum smart contracts~\cite{bhargavan2016short}.
The framework is built on tools for translating Solidity and Ethereum Virtual Machine bytecode contracts into $F^*$, a functional programming language aimed
at program verification.
Using the~$F^*$ representations, the framework can verify the correctness of the Solidity-to-bytecode compilation as well as detect certain vulnerable patterns. Luu et al.\ provide a tool called \textsc{Oyente}, which can analyze smart contracts and detect certain typical security vulnerabilities~\cite{luu2016making}. The main difference between prior work and the approach that we are using (i.e., verifying FSolidM models with NuSMV) is that the former can prevent a set of typical vulnerabilities, but they are not effective against vulnerabilities that are atypical or belong to types which have not been identified yet.

### 2018-04-16 docs/papers/IEEEBlockchain2018/summary.tex
added Blockchain paper

\begin{abstract}
Internet of Things and data sciences are fueling the development of innovative solutions for various applications in Smart and Connected Communities. These applications provide participants with the capability to exchange not only data but also resources, which raises the concerns of integrity, trust, and above all the need for fair and optimal solutions to the problem of resource allocation. Blockchain-based computational platforms may act as an enabling technology for these applications by providing immutability and distributed event chronology, enabling the implementation of ``higher-level contracts,'' which monitor system execution and provide guarantees on services that the rest of the system can depend upon. In this paper, we introduce the \Platform platform, which provides (a) distributed coordination and (b) decentralized market mechanisms as service. %We also describe the requirements and 
Based on case studies of energy trading and carpooling applications, we demonstrate the capabilities of \Platform.

% \textcolor{red}{the abstract has to be re-written}
% If the last decade viewed computational services as a \textit{utility}, 
% then surely this decade has transformed computation into a \textit{commodity}. Computation is now progressively integrated into physical networks in a seamless way, which enables smart and connected community applications to meet their latency requirements.  In this new  scenario, the boundaries between the network node, the sensor, and the actuator are blurring. Any node can be seen as part of a graph, with the capacity to serve as a computing or network router node (or both), and complex applications can possibly be distributed over this graph/network of nodes, so that the overall performance (e.g., amount of data processed over time) is significantly improved. However, the shared nature of resources and  the dependence on data-driven mechanisms make smart and connected community applications vulnerable. Classical, redundancy based mechanisms, such as self-checking pair and recovery blocks, are not applicable because of the dynamism and uncertainties---both endogenous (computation resources) and exogenous (environment). Blockchain based computational platforms may act as an enabling technology for these applications by providing immutability and distributed event chronology, enabling ``higher-level contracts'' to be written, which monitor system execution and provide guarantees on services that the rest of the system can depend upon. In this paper, we describe \Platform, which provides (a) distributed co-ordination and (b) decentralized market mechanisms as service. %We also describe the requirements and 
% Using case studies of energy distributed systems and carpooling, we demonstrate the capabilities of \Platform.
% %A use case of energy distribution systems is used as a casestudy. \Abhishek{title will be updated later.}
\end{abstract}

### 2018-04-16 docs/papers/IEEEBlockchain2018/workflow.tex
added Blockchain paper

\label{sec:workflow}
% api and sequence

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{Workflow.pdf}
    \caption{Sequence of operations in the transaction management platform.} % Prosumers and Solvers use the directory to find one of the miner nodes running the smart contract. They then connect to the  mining node.}
    \label{fig:workflow}
\end{figure}

\Aron{The figure has not much to do with the current platform. Key functions are missing, and non-existing functions are shown. Needs to be remove or updated!}
\Aron{What is the point of this subsection? This needs to be made clear at the beginning.}
Figure \ref{fig:workflow} describes the workflow of activity in this transaction management platform.  The specific operations in this workflow are described below. Note that the events in this workflow can arrive out of order at the smart contract. %For example, a consumer can request a resource from a time interval that has already been finalized by the smart contract. However, those consumption offers will be rejected.

\begin{itemize}[leftmargin=*]
\setlength{\itemsep}{0pt}%
    \setlength{\topsep}{0pt} 
    \setlength{\partopsep}{0pt}
    \setlength{\parsep}{0pt}
    \setlength{\parskip}{0pt}%
\item Deploying the contract \texttt{(bytecode)}\Aron{Writing ``deployContract'' in the figure suggests that there is a function named ``deployContract'' in the smart contract or the blockchain, which is not true.}: 
Blockchain transaction submitted by a directory actor. \Aron{Directory has not been mentioned in the text before!} The transaction deploys the smart contract, making it available for all participants to use. The blockchain returns the address of the deployed contract.\Aron{This is kind of obvious.}
\item \texttt{Connect}: \Aron{This is practically just establishing a TCP connection. Why do we mention this?!} Any new participant first connects to the directory. The directory can run an optional mixing service\Aron{Anonymization needs to be discussed more detail or omitted.}, providing the participants with an anonymous identifier.
\item \texttt{query\_contract\_address}:  This is an off-blockchain communication between participants and the directory, which returns the address of the smart contract. 
\item \texttt{registerProsumer(uint64 prosumer)}: \Aron{Remove this! It was not listed in the contract (see FSolidM section), and it has not been implemented.} Each prosumer registers with the smart contract, providing an anonymous identifier.
\item \texttt{ProsumerRegistered}: \Aron{Again, what is this doing here? There is nothing like this in the platform.} Event broadcast by the smart contract, notifying prosumers that they have registered. 
\item \texttt{postOffer(assetID, price)}: \Aron{Fuction signatures are all wrong...} smart contract function called by a prosumer, publicly posting an offer to produce or consume a resource. The resource type is encoded in the assetID and checked by the smart contract.
\item \texttt{OfferPosted(offerID, assetID, price)}: event broadcast by the smart contract, notifying solvers that an offer was posted.
%\item \texttt{Solve} : Once offers have been posted the Solver begins solving for potential matchings of the offers of which it has been notified. \Aron{This is not an interaction, so it should not be on this list. Further, we don't assume anything about solvers, so we really shouldn't discuss their internal working here.}
\item \texttt{createSolution(uint64 solverID)}: The Solver sends a request to the smart contract to tell it that a new solution has been found..
\item \texttt{SolutionCreated}: event broadcast by the smart contract, notifying the solver that it can submit the trades that constitute the new solution.
\item \texttt{addAssignment(uint64 solutionID, uint64 sellerID, uint64 buyerID, uint64 time, uint64 power)}: smart contract function called by the solver, which posts the trades to the solution created previously on the blockchain. As the trades are added the smart contract verifies that each is a valid trade and does not violate any of the system constraints.
\item \texttt{AssignmentAdded}: An event broadcast by the smart contract notifying the solver and the prosumers that a trade has been added to a potential solution. 
\item \texttt{finalize} : smart contract function called by the directory causing the contract to stop accepting new solutions which include the interval being finalized. The contract selects the best solution\footnote{The smart contract keeps track of the best solution as a new solution is added. This ensures that it does not have to search the list of solutions to select the best solution (max objective value) during finalization.} and broadcasts the \texttt{Finalize} event. 
\item \texttt{Finalized} : event broadcast by the smart contract notifying the solver to begin working on the next interval
\item \texttt{AssignmentFinalized}: An event broadcast by the smart contract notifying participants off all trades that were in the final accepted solution. 
\end{itemize}
\Aron{This subsection needs to be rewritten almost completely!}

### 2018-04-16 code/TransactivePlatform/components/Carpooler.py
final code used to run IEE blockchain carpool example

@@ -103,13 +103,10 @@ class Carpooler(Prosumer):
         self.mid = self.midpoint(float(self.srclat), float(self.srclng), float(self.dstlat), float(self.dstlng))
         self.pud = self.directDist*.6
         #self.pud = random.randint(1, floor(self.directDist))
-        #----Randomly assign provider state------------------------------------
-        rnd = random.random()
-        if rnd <= .5:
-            self.providing = True
+        #----Depending on provider state from mongodb set pups------------------------------------
+        if self.providing:
             self.pups = list(self.getPickups(self.pud, self.mid[0],self.mid[1]))
         else:
-            self.providing = False
             self.pups = list(self.getPickups(self.pud, self.srclat, srclng))
         print("mid.pups: %s" %list(self.getPickups(self.pud, self.mid[0],self.mid[1])))
         print("home.pups: %s" %list(self.getPickups(self.pud, self.srclat, srclng)))
@@ -293,13 +290,17 @@ if __name__ == "__main__":
 
     CP = Carpooler(srclat,srclng,dstlat,dstlng)
     #pprint.pprint("all dst: %s" %list(CP.geo_db.Dests.find({})))
-    #print(srclat,srclng,dstlat,dstlng)
+    print(srclat,srclng,dstlat,dstlng)
     #pprint.pprint("dst: %s" %list(CP.geo_db.Dests.find({"location.coordinates": [dstlng, dstlat]})))
 
     #dst = list(CP.geo_db.Dests.find({"location.coordinates": [dstlng, dstlat]}))
     #CP.dst_id = dst[0]['location']['dstID']
+    #GET THE ID OF MY DESTINATION
     dst = list(CP.geo_db.Dests.find({"geometry.coordinates": [dstlng, dstlat]}))
     CP.dst_id = dst[0]['geometry']['dstID']
+
+    residence = list(CP.geo_db.residences.find({"geometry.coordinates": [srclng, srclat]}))[0]
+    CP.providing = residence['properties']['prosumer']
 
     #print("pups: %s" %list(CP.geo_db.Pickups.find({})))
     # pups = list(CP.getPickups(self.pud, self.srclat, srclng))

### 2018-04-16 code/TransactivePlatform/components/EventRecorder.py

@@ -41,15 +41,15 @@ class EventRecorder():
         # TODO: record data to database
         if (name == "Debug"):
             logging.info("{}({}).".format(name, params))
-        elif (name == "FinalizeRequested"):
-            stopWatch = {"start":time(), "running" : 1}
-            logging.info("{}({}).".format(name, params))
-        elif(name == "FinalizeComplete"):
-            stopWatch["split"] = time() - stopWatch["start"]
-            logging.info("{}({}).".format(name, params))
-            tag_dict = {}
-            self.dbase.log(self.time-datetime.timedelta(seconds=1), tag_dict, "FinalizeTime", 0)
-            self.dbase.log(self.time, tag_dict, "FinalizeTime", stopWatch["split"])
+        # elif (name == "FinalizeRequested"):
+        #     stopWatch = {"start":time(), "running" : 1}
+        #     logging.info("{}({}).".format(name, params))
+        # elif(name == "FinalizeComplete"):
+        #     stopWatch["split"] = time() - stopWatch["start"]
+        #     logging.info("{}({}).".format(name, params))
+        #     tag_dict = {}
+        #     self.dbase.log(self.time-datetime.timedelta(seconds=1), tag_dict, "FinalizeTime", 0)
+        #     self.dbase.log(self.time, tag_dict, "FinalizeTime", stopWatch["split"])
       next_polling += POLLING_INTERVAL
       sleep(max(next_polling - time(), 0))
 

### 2018-04-16 code/TransactivePlatform/components/ResourceAllocationLP.py

@@ -5,12 +5,18 @@ import pprint
 import json
 
 class Offer:
-  def __init__(self, ID, providing, prosumer, quantity={}, value={}):
-    self.ID = ID
-    self.providing = providing
-    self.prosumer = prosumer
-    self.quantity = quantity
-    self.value = value
+  def __init__(self, ID, providing, prosumer, quantity=None, value=None):
+      self.ID = ID
+      self.providing = providing
+      self.prosumer = prosumer
+      if quantity is None:
+          self.quantity = {}
+      else:
+          self.quantity = quantity
+      if value is None:
+          self.value = {}
+      else:
+          self.value = value
 
   def __repr__(self):
     return "<{}, {}, {}, {}, {}>".format(self.ID, self.providing, self.prosumer, self.quantity, self.value)

### 2018-04-16 code/TransactivePlatform/components/Solver.py

@@ -54,37 +54,58 @@ class Solver(ResourceAllocationLP):
       if current_time > next_polling:
         logging.debug("Polling events...")
         next_polling = current_time + POLLING_INTERVAL
+        event_counter = 0
+        update_counter = 0
         for event in self.contract.poll_events():
           params = event['params']
           name = event['name']
-          logging.info("{}({}).".format(name, params))
+          #logging.info("{}({}).".format(name, params))
           if name == "OfferCreated":
             offers[params['ID']] = Offer(params['ID'], params['providing'], params['prosumer'])
+            print("OfferCreated")
+            pprint.pprint(offers[params['ID']])
+            print("params['ID']: %s" %params['ID'])
+            event_counter += 1
+            print("event count: %s" %event_counter)
+
           elif name == "OfferUpdated":
             offer = offers[params['ID']]
+            print("WHAT IS THE OFFER?")
+            pprint.pprint(offer)
             res_type = params['resourceType']
             offer.quantity[res_type] = params['quantity']
             offer.value[res_type] = params['value']
+            print("params['ID']: %s" %params['ID'])
+            update_counter += 1
+            print("update counter: %s" %update_counter)
+
           elif name == "OfferPosted":
             new_offers = True
             offer = offers[params['ID']]
             if offer.providing:
               prov_offers.append(offer)
+            #   print("APPEND OFFER")
+            #   pprint.pprint(prov_offers)
             else:
               cons_offers.append(offer)
+
           elif name == "OfferCanceled":
             offer = offers[params['ID']]
             if offer.providing:
               prov_offers.remove(offer)
             else:
               cons_offers.remove(offer)
+
+
           elif (name == "SolutionCreated") and (params['misc'] == self.solverID):
             logging.info("{}({}).".format(name, params))
             waiting_solutionID = False
             solutionID = params['ID']
+
             if self.solution is not None:
               logging.info("Solution {} created by contract, adding assignments...".format(solutionID))
               assignments = [assign for assign in self.solution if int(assign['q']) > 0]
+
               for assign in assignments:
                 print("solutionID : POID : COID : T : Q : V")
                 print(solutionID,assign['po'].ID, assign['co'].ID, assign['t'],
@@ -93,9 +114,20 @@ class Solver(ResourceAllocationLP):
                 self.contract.addAssignment(self.account, solutionID,
[…]

### 2018-04-16 code/TransactivePlatform/components/prep-carpool-data.py

@@ -43,7 +43,7 @@ def get_centermost_point(cluster):
 
 try :
     trip_data = pd.read_csv(data_dir)
-    trip_data = trip_data.iloc[0:100]
+    trip_data = trip_data.iloc[0:75]
     #pprint.pprint(trip_data.iloc[0:100])
     # from_coordinate, from_taz to_coordinate, to_taz, departure_time
 except FileNotFoundError:
@@ -78,7 +78,7 @@ pprint.pprint("dst: %s" %list(geo_db.Dests.find({"geometry.coordinates": [-86.81
 
 
 #---- Put from points into DB---------------------------------------------------
-if  not os.path.exists("data/latlng.csv"):
+if  os.path.exists("data/latlng.csv"):
     df = pd.DataFrame(columns=['ID','from_lat','from_lng', 'to_lat', 'to_lng'])
     print("parse coordinate data")
     ID = 0
@@ -86,15 +86,26 @@ if  not os.path.exists("data/latlng.csv"):
         from_lat, from_lng = row.from_coordinate.split(" ")
         to_lat, to_lng = row.to_coordinate.split(" ")
         #print(ID, "tooo", float(to_lat), float(to_lng))
-        #print(ID, "from", float(from_lat), float(from_lng))
-        geo_db.residences.insert_one({"geometry":{"type":"Point", "coordinates":[float(from_lng),float(from_lat)]}})
-        # geo_db.residences.insert_one({"location":{"type":"Point", "coordinates":[float(from_lng),float(from_lat)]}})
-
         df = df.append({'ID' : ID,
                         'from_lat':float(from_lat), 'from_lng' : float(from_lng),
                         'to_lat':float(to_lat), 'to_lng':float(to_lng)}, ignore_index=True)
         ID += 1
+
+    dfround = df.round(6)
     df.round(6).to_csv("data/latlng.csv")
+
+    for row in dfround.itertuples():
+        from_lng = row.from_lng
+        from_lat = row.from_lat
+        print("from", float(from_lat), float(from_lng))
+        rnd = random.random()
+        if rnd <= .5:
+            providing = 1
+        else:
+            providing = 0
+        geo_db.residences.insert_one({"geometry":{"type":"Point", "coordinates":[float(from_lng),float(from_lat)]}, "properties": {"prosumer" : providing}})
+        # geo_db.residences.insert_one({"location":{"type":"Point", "coordinates":[float(from_lng),float(from_lat)]}})
+
 else:
[…]

### 2018-04-16 code/TransactivePlatform/tests/scripts/launch-m1s1.sh

@@ -18,15 +18,18 @@ influx -execute 'drop database CarpoolMarket'
 rm -rf "$DIR/miner/eth"
 
 #start TMUX
-i=0
-xterm -geometry 93x31+${x[i]}+${y[i]} -hold -e tmux new -s miner &
-i=1
-xterm -geometry 93x31+${x[i]}+${y[i]} -hold -e tmux new -s Directory &
-i=2
-xterm -geometry 93x31+${x[i]}+${y[i]} -hold -e tmux new -s Solver &
-i=3
-xterm -geometry 93x31+${x[i]}+${y[i]} -hold -e tmux new -s Recorder &
-sleep 1 #wait for tmux to start
+ i=0
+ xterm -geometry 93x31+${x[i]}+${y[i]} -hold -e tmux new -s miner &
+ i=1
+ xterm -geometry 93x31+${x[i]}+${y[i]} -hold -e tmux new -s Directory &
+ i=2
+ xterm -geometry 93x31+${x[i]}+${y[i]} -hold -e tmux new -s Solver &
+ i=3
+ xterm -geometry 93x31+${x[i]}+${y[i]} -hold -e tmux new -s Recorder &
+ sleep 1 #wait for tmux to start
+
+#tmux send -t carpooler$i.0 "python3 $DIR/$PROJECT/components/Carpooler.py $i $GETHCLIENT $PORT $FILE" ENTER
+
 
 # Start miner
 tmux send -t miner.0 "cd $DIR/miner; pwd" ENTER
@@ -37,9 +40,9 @@ tmux send -t miner.0 "geth-linux-amd64/geth --datadir eth/ --rpc --rpcport $PORT
 
 # Start market
 read -p "Wait for at least 15 blocks to be mined. Then press enter to start Market"
-tmux send -t Directory.0 "python3 $DIR/$PROJECT/components/Directory.py $MINER $PORT" ENTER
-tmux send -t Solver.0 "python3 $DIR/$PROJECT/components/Solver.py $MINER $PORT" ENTER
-tmux send -t Recorder.0 "python3 $DIR/$PROJECT/components/EventRecorder.py $MINER $PORT" ENTER
+tmux send -t Directory.0 "python3 $DIR/$PROJECT/components/Directory.py $MINER $PORT  | tee logs/miner.log" ENTER
+tmux send -t Solver.0 "python3 $DIR/$PROJECT/components/Solver.py $MINER $PORT | tee logs/solver.log" ENTER
[…]

### 2018-05-17 code/ResourcePlatform/components/JobCreatorDev.py
resource platform

@@ -1,0 +1,65 @@
+import sys
+import os
+import logging
+import pprint
+logging.basicConfig(level=logging.INFO)
+import pymongo
+import docker
+
+class JobCreator():
+    pass
+
+
+if __name__ == "__main__":
+    ip = 'localhost' #GETH CLIENT IP
+    port = 10000 #GETH CLIENT PORT
+    if len(sys.argv) > 1:
+        prosumer_id = int(sys.argv[1])
+    if len(sys.argv) > 2:
+        ip = sys.argv[2]
+    if len(sys.argv) > 3:
+        port = sys.argv[3]
+    if len(sys.argv) > 4:
+        providing = sys.argv[4]
+    if len(sys.argv) > 5 :
+        jobspath = sys.argv[5]
+
+    # for (dirpath, dirnames, filenames) in os.walk(jobspath):
+    #     if filenames :
+    #         print(dirpath)
+    #         print(filenames)
+
+    jobpath = "/home/riaps/projects/transactive-blockchain/code/ResourcePlatform/jobs/job0"
+    jobname = "eiselesr/job0"
+
+    APIclient = docker.APIClient(base_url='unix://var/run/docker.sock')
+
+    client = docker.from_env()
+    client.login(username='eiselesr', password='eiselesr@docker')
+
+    #build image
+    image = client.images.build(path=jobpath, tag=jobname)[0]
+
+    for line in client.images.push(jobname, stream=True):
+        print (line)
+
+#     dist_dict = APIclient.inspect_distribution(jobname)
+#     pprint.pprint(dist_dict)
+#     sha256 = dist_dict['Descriptor']['digest']
+#     size = dist_dict['Descriptor']['size']
+#     os = dist_dict['Platforms'][0]['os']
+#     arch = dist_dict['Platforms'][0]['architecture']
+# print(sha256, size, os, arch)
+
+    image_dict = APIclient.inspect_image(jobname)
+    pprint.pprint(image_dict)
+    repoDigestSha = image_dict["RepoDigests"][0]
+    IDsha = image_dict["Id"]
+    size = image_dict["Size"]
+    os = image_dict["Os"]
+    arch = image_dict["Architecture"]
+    print(repoDigestSha, IDsha, size, os, arch)
+
+
+    #push image
+    #get sha

### 2018-05-17 code/ResourcePlatform/components/ResourceAllocationContract.py

@@ -1,0 +1,89 @@
+import logging
+
+from Contract import Contract
+
+class ResourceAllocationContract(Contract):
+  def __init__(self, client, address):
+    super(ResourceAllocationContract, self).__init__(client, address, [
+      "OfferCreated(uint64 ID, bool providing, uint64 misc, uint64 prosumer)",
+      "OfferUpdated(uint64 ID, uint64 resourceType, uint64 quantity, uint64 value)",
+      "OfferPosted(uint64 ID)",
+      "OfferCanceled(uint64 ID)",
+      "SolutionCreated(uint64 ID, uint64 misc)",
+      "AssignmentAdded(uint64 ID, uint64 providingOfferID, uint64 consumingOfferID, uint64 resourceType, uint64 quantity, uint64 value, uint64 objective)",
+      "AssignmentFinalized(uint64 providingOfferID, uint64 consumingOfferID, uint64 resourceType, uint64 quantity, uint64 value)",
+      "Debug(string Description, uint64 value, bool boolean, uint64 state)",
+      "FinalizeRequested(string Description, uint64 state)",
+      "FinalizeComplete(string Description, uint64 state)"
+    ])
+
+  def setup(self, from_account, numTypes, precision, maxQuantity):
+    print("numTypes %s : %s" %(numTypes, Contract.encode_uint(numTypes)))
+    print("precision %s : %s" %(precision, Contract.encode_uint(precision)))
+    print("max %s : %s" %(maxQuantity, Contract.encode_uint(maxQuantity)))
+    self.call_func(from_account, "setup",
+      "uint64", numTypes,
+      "uint64", precision,
+      "uint64", maxQuantity)
+
+  def createOffer(self, from_account, providing, misc, prosumer):
+    print("providing %s : %s" %(providing, Contract.encode_bool(providing)))
+    print("misc %s : %s" %(misc, Contract.encode_uint(misc)))
+    print("prosumer %s : %s" %(prosumer, Contract.encode_uint(prosumer)))
+    self.call_func(from_account, "createOffer",
+      "bool", providing,
+      "uint64", misc,
+      "uint64", prosumer)
+
+  def updateOffer(self, from_account, ID, resourceType, quantity, value):
+    print("ID %s : %s" %(ID, Contract.encode_uint(ID)))
+    print("RT %s : %s" %(resourceType, Contract.encode_uint(resourceType)))
+    print("Q %s : %s" %(quantity, Contract.encode_uint(quantity)))
[…]

### 2018-05-17 code/ResourcePlatform/components/config.py

@@ -1,0 +1,15 @@
+# deployment
+DIRECTORY_ADDRESS = 'tcp://127.0.0.1:10001'
+TRANSACTION_GAS = "0x100000000"
+from bytecode import *
+#BYTECODE = "0x606060405260016000806101000a81548167ffffffffffffffff021916908367ffffffffffffffff160217905550640100000000600060086101000a81548167ffffffffffffffff021916908367ffffffffffffffff1602179055506001600060106101000a81548167ffffffffffffffff021916908367ffffffffffffffff1602179055506000600360006101000a81548167ffffffffffffffff021916908367ffffffffffffffff16021790555034156100ba57600080fd5b61187e806100c96000396000f30060606040526004361061008e576000357c0100000000000000000000000000000000000000000000000000000000900463ffffffff16806340d599c0146100935780634bb278f3146100e657806366948833146100fb578063696e89d6146101285780637f49f33c1461017357806383bbb2cc146101a0578063be38aaf01461022c578063e1f9673814610292575b600080fd5b341561009e57600080fd5b6100e4600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff169060200190919050506102bf565b005b34156100f157600080fd5b6100f961033e565b005b341561010657600080fd5b610126600480803567ffffffffffffffff169060200190919050506105e7565b005b341561013357600080fd5b6101716004808035151590602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff169060200190919050506106d8565b005b341561017e57600080fd5b61019e600480803567ffffffffffffffff16906020019091905050610839565b005b34156101ab57600080fd5b61022a600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff16906020019091905050610960565b005b341561023757600080fd5b610290600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff16906020019091905050611368565b005b341561029d57600080fd5b6102bd600480803567ffffffffffffffff169060200190919050506115e3565b005b826000806101000a81548167ffffffffffffffff021916908367ffffffffffffffff16021790555081600060086101000a81548167ffffffffffffffff021916908367ffffffffffffffff1602179055508060
[…]

### 2018-05-17 code/ResourcePlatform/tests/context.py

@@ -1,0 +1,9 @@
+import os
+import sys
+sys.path.insert(0, os.path.abspath(os.path.join(os.path.dirname(__file__), '..')))
+
+import components.Actor as Actor
+import components.Prosumer as Prosumer
+#import components.Prosumer as Prosumer
+# ^ not needed, because TrasactivePlatfrom was added to the the path, and components has __init__.py,
+# but I'd rather be explicit about why access to Prosumer is possible

### 2018-05-17 code/ResourcePlatform/tests/scripts/m1s1-launch.sh

@@ -1,0 +1,52 @@
+#!/bin/bash
+
+#Setup
+MINER=localhost
+PORT=10000
+DIR="~/projects/transactive-blockchain/code"
+PROJECT="TransactivePlatform"
+echo $DIR
+x=(700 1300 700 1300)
+y=(150 150 600 600)
+
+# Cleanup
+pkill python3
+pkill geth
+pkill tmux
+pkill xterm
+influx -execute 'drop database ResourceMarket'
+rm -rf "$DIR/miner/eth"
+
+#start TMUX
+ i=0
+ xterm -geometry 93x31+${x[i]}+${y[i]} -hold -e tmux new -s miner &
+ i=1
+ xterm -geometry 93x31+${x[i]}+${y[i]} -hold -e tmux new -s Directory &
+ i=2
+ xterm -geometry 93x31+${x[i]}+${y[i]} -hold -e tmux new -s Solver &
+ i=3
+ xterm -geometry 93x31+${x[i]}+${y[i]} -hold -e tmux new -s Recorder &
+ sleep 1 #wait for tmux to start
+
+#tmux send -t carpooler$i.0 "python3 $DIR/$PROJECT/components/Carpooler.py $i $GETHCLIENT $PORT $FILE" ENTER
+
+
+# Start miner
+tmux send -t miner.0 "cd $DIR/miner; pwd" ENTER
+tmux send -t miner.0 "pwd ; geth-linux-amd64/geth --datadir eth/  init genesis-data.json" ENTER
+tmux send -t miner.0 "geth-linux-amd64/geth account new --password password.txt --datadir eth/" ENTER
+sleep 5 #Wait for account address
+tmux send -t miner.0 "geth-linux-amd64/geth --datadir eth/ --rpc --rpcport $PORT --rpcaddr localhost --nodiscover --rpcapi "eth,web3,admin,miner,net,db" --password password.txt --verbosity 3 --unlock 0 --networkid 15 --mine | tee miner.out" ENTER
+
+# Start market
+read -p "Wait for at least 15 blocks to be mined. Then press enter to start Market"
+tmux send -t Directory.0 "python3 $DIR/$PROJECT/components/Directory.py $MINER $PORT  | tee logs/miner.log" ENTER
+tmux send -t Solver.0 "python3 $DIR/$PROJECT/components/Solver.py $MINER $PORT | tee logs/solver.log" ENTER
[…]

### 2018-05-17 code/ResourcePlatform/tests/scripts/reset.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+pkill python3
+pkill geth
+pkill tmux
+pkill xterm
+pkill sleep
+
+appName=job0
+sudo docker ps -a | grep $appName | awk '{print $1}' | xargs sudo docker rm
+sudo docker images -a | grep $appName | awk '{print $3}' | xargs sudo docker rmi
+
+
+#sudo docker rm $(sudo docker ps -a -q)
+#docker rmi $(docker images -q)

### 2018-05-17 code/ResourcePlatform/components/Contract.py
no message

@@ -35,21 +35,6 @@ class Contract:
       return False
     raise Exception("Unexpected boolean value {}".format(uint))
 
-
-  def decode_string(data, pos):
-    n = 64
-    arrays = [data[i:i+n] for i in range(0, len(data), n)]
-    for array in arrays:
-        out = unhexlify(array)
-        try:
-            utf8 = out.decode('utf-8')
-            if 'str' in utf8:
-                print("line")
-                string = utf8.strip("\x00")
-        except UnicodeDecodeError:
-            print("not utf-8")
-    return string
-
   def generate_topics(self, events):
     self.topics = {}
     for event in events:
@@ -92,6 +77,8 @@ class Contract:
     for i in range(len(arg_types)):
       if arg_types[i] == "uint64":
         data += Contract.encode_uint(arg_values[i])
+      if arg_types[i] == "uint256":
+        data += Contract.encode_uint(arg_values[i])
       elif arg_types[i] == "int64":
         data += Contract.encode_int(arg_values[i])
       elif arg_types[i] == "address":
@@ -123,8 +110,6 @@ class Contract:
               params[pname] = Contract.decode_address(data, data_pos)
             elif ptype == "bool":
               params[pname] = Contract.decode_bool(data, data_pos)
-            elif ptype == "string":
-              params[pname] = Contract.decode_string(data, data_pos)
             data_pos += 1
           event['params'] = params
           events.append(event)

### 2018-05-17 code/ResourcePlatform/components/ResourceAllocationContract.py

@@ -1,89 +1,62 @@
-import logging
-
 from Contract import Contract
 
 class ResourceAllocationContract(Contract):
   def __init__(self, client, address):
     super(ResourceAllocationContract, self).__init__(client, address, [
-      "OfferCreated(uint64 ID, bool providing, uint64 misc, uint64 prosumer)",
-      "OfferUpdated(uint64 ID, uint64 resourceType, uint64 quantity, uint64 value)",
-      "OfferPosted(uint64 ID)",
-      "OfferCanceled(uint64 ID)",
-      "SolutionCreated(uint64 ID, uint64 misc)",
-      "AssignmentAdded(uint64 ID, uint64 providingOfferID, uint64 consumingOfferID, uint64 resourceType, uint64 quantity, uint64 value, uint64 objective)",
-      "AssignmentFinalized(uint64 providingOfferID, uint64 consumingOfferID, uint64 resourceType, uint64 quantity, uint64 value)",
-      "Debug(string Description, uint64 value, bool boolean, uint64 state)",
-      "FinalizeRequested(string Description, uint64 state)",
-      "FinalizeComplete(string Description, uint64 state)"
+      "ResourceOfferPosted(uint64 offerID, uint64 actorID, uint64 architecture, uint64 capCPU, uint64 capRAM, uint64 capStorage, uint64 price)",
+      "ResourceOfferCanceled(uint64 offerID)",
+      "JobOfferCreated(uint64 offerID, uint64 actorID, uint64 timeLimit, uint64 price)",
+      "JobOfferUpdated(uint64 offerID, uint64 architecture, uint64 reqCPU, uint64 reqRAM, uint64 reqStorage, uint256 imageHash)",
+      "JobOfferPosted(uint64 offerID)",
+      "JobOfferCanceled(uint64 offerID)",
+      "SolutionCreated(uint64 solutionID, uint64 actorID)",
+      "AssignmentAdded(uint64 solutionID, uint64 jobOfferID, uint64 resourceOfferID)",
+      "AssignmentFinalized(uint64 jobOfferID, uint64 resourceOfferID)",
     ])
 
-  def setup(self, from_account, numTypes, precision, maxQuantity):
-    print("numTypes %s : %s" %(numTypes, Contract.encode_uint(numTypes)))
-    print("precision %s : %s" %(precision, Contract.encode_uint(precision)))
-    print("max %s : %s" %(maxQuantity, Contract.encode_uint(maxQuantity)))
[…]

### 2018-05-17 code/ResourcePlatform/components/contractInterface.py

@@ -1,0 +1,47 @@
+import argparse
+import re
+from os.path import basename
+
+parser = argparse.ArgumentParser(description='Process a Solidity source file and generate a Python class for Contract.py.')
+parser.add_argument('src', metavar='src', type=str,
+                   help='path to Solidity source file')
+
+args = parser.parse_args()
+
+events = []
+functions = []
+with open(args.src, 'rt') as fin:
+  for part in fin.read().split(';'):
+    event = re.search(r'event\s+(\w+)\(([^\)]+)\)', part)
+    if event is not None:
+      events.append(f"{event.group(1)}({event.group(2)})")
+    function = re.search(r'function\s+(\w+)\(([^\)]+)\)', part)
+    if function is not None:
+      params = []
+      for param in function.group(2).split(","):
+        type_name = param.strip().split(" ")
+        params.append((type_name[0], type_name[-1]))
+      functions.append((function.group(1), params))
+      
+classname = basename(args.src).split('.')[0] + "Contract"
+  
+with open(classname + ".py", 'wt') as fout:
+  fout.write(f"""from Contract import Contract
+
+class {classname}(Contract):
+  def __init__(self, client, address):
+    super({classname}, self).__init__(client, address, [
+""")
+  for event in events:
+    fout.write(f'      "{event}",\n')
+  fout.write("""    ])
+
+""")
+  for (name, params) in functions:
+    paramnames = ", ".join([pname for (ptype, pname) in params])
+    fout.write(f"""  def {name}(self, from_account, {paramnames}):
+    self.call_func(from_account, "{name}" """)
+    for (ptype, pname) in params:
+      fout.write(f',\n      "{ptype}", {pname}')
+    fout.write(")\n\n")
+    

### 2018-05-18 docs/papers/IEEEBlockchain2018/analysis.tex

%\subsubsection{Performance}
%\textcolor{red}{computational and communication costs (e.g., number of transactions, messages, contract-function calls, time complexity of solving and verification) and privacy}

\Aron{Note to self: extend!}
The computational cost of every smart-contract function is constant (i.e., $O(1)$) except for \texttt{finalize}, whose cost is an affine function of the size of the solution (i.e., $O(|A|)$).
Note that the cost of \texttt{finalize} depends on the size of the solution $A$ only because it emits an event for every assignment $\va \in A$.
These could be omitted for the sake of maximizing performance since the assignments have already been recorded in the blockchain anyway.
The number of function calls required for posting an offer depends on the number of resource types with non-zero quantity in the offer.
If there are $n$ such resource types, then $n + 2$ calls are required (\texttt{createOffer}, $n$ \texttt{updateOffer}, and \texttt{postOffer}).
The number of function calls required for submitting a solution $A$ is $1 + |A|$ (\texttt{createSolution} and $|A|$ \texttt{addAssignment}).

\subsubsection{Verification}
%\textcolor{red}{Describe how the properties were verified. Mention NuSMV - also provide hint what is the signficance of these properties}
%
For the specification of safety and liveness properties, we use Computation Tree Logic (CTL)~\cite{baier2008principles}. CTL formulas specify properties of execution trees generated by transitions systems. The formulas are built from atomic predicates that represent 
transitions and statements of the
transition system (i.e., smart contract), using several operators, such as $\mathtt{AX}$, $\mathtt{AF}$, $\mathtt{AG}$ (unary) and,
$\mathtt{A}[\cdot\,\mathtt{U}\,\cdot]$,
$\mathtt{A}[\cdot\,\mathtt{W}\,\cdot]$ (binary).  Each operator
consists of a quantifier on the branches of the tree and a temporal modality, which together define when in the execution the operand sub-formulas must hold.  The intuition behind the letters is the
following: the branch quantifier is $\mathtt{A}$ (for ``All'') and the temporal modalities are
$\mathtt{X}$ (for ``neXt''), $\mathtt{F}$ (for ``some time in the
Future''), $\mathtt{G}$ (for ``Globally''), 
$\mathtt{U}$ (for ``Until'') and $\mathtt{W}$ (for ``Weak until'').  
A property is satisfied if it holds in the initial state of the transition systems.  
For instance, the formula
$\mathtt{A}[p\,\mathtt{W}\,q]$ specifies that in \emph{all execution
  branches} the predicate $p$ must hold \emph{up to the first state}
(not including this latter) where the predicate $q$ holds.  
%
Since we used the weak until operator $\mathtt{W}$, if $q$ never
holds, $p$ must hold forever.
%
As soon
as $q$ holds in one state of an execution branch, $p$ does not need to hold
anymore, even if $q$ does not hold.  On the contrary, the formula
$\mathtt{AG}\,\mathtt{A}[p\,\mathtt{W}\,q]$ specifies that the
subformula $\mathtt{A}[p\,\mathtt{W}\,q]$ must hold in \emph{all
  branches at all times}.  Thus, $p$ must hold whenever $q$ does not hold, i.e., $\mathtt{AG}\,\mathtt{A}[p\,\mathtt{W}\,q] = \mathtt{AG}\,(p \lor q)$.
  %\Aron{Reference? I think that most reviewers will not be familiar with CTL.} \Anastasia{Added reference and small description of the operators}

We verified correctness of behavioral semantics with the NuSMV model checker~\cite{cimatti2002nusmv}, by verifying the following properties:
\begin{itemize}
    \item \emph{deadlock-freedom}, which ensures that the contract cannot enter a state in which progress is impossible;
    \item \emph{``if \texttt{close} happens, then \texttt{postOffer} or \texttt{cancelOffer} can happen only after \texttt{finalize}''}, translated to CTL as:\\ $\mathtt{AG}(\texttt{close})$ $\rightarrow$ $\mathtt{AX}$ $\mathtt{A}$ $[\neg ($\texttt{postOffer} $\wedge$ \texttt{cancelOffer}) $\mathtt{W}$ \texttt{finalize}$]$, which ensures that prosumers cannot post or cancel their offers once the solvers have started working;
    % \item \Aron{This cannot be true... What if no one every calls createSolution?!} \Anastasia{I have added fairness assumptions for the verification. In general we need fairness assumptions for the verification of liveness properties.} \emph{``\texttt{createSolution} will eventually happen after \texttt{postOffer}''}, which is translated to CTL as:\\
    % $\mathtt{AG}$ $($\texttt{createSolution} $\rightarrow$ $\mathtt{AF}$ $($\texttt{postOffer}$))$;
    % \item \emph{``\texttt{OfferCanceled} can happen only after \texttt{cancel}''}, which is translated to CTL as:\\ 
    % $\mathtt{A}[ \neg$ \texttt{OfferCanceled} $\mathtt{W}$ \texttt{cancel}$]$\Aron{I'm not sure what to say, this seems kinda obvious. This event is emitted only in this function, so the function obviously needs to be called before the event.};
    \item \emph{``\texttt{OfferPosted(ID)} can happen only if \texttt{ID < offers.length \&\& !offers[ID].posted}''}, translated to CTL as:\\ $\mathtt{A}[ \neg$\texttt{OfferPosted(ID)}$\mathtt{W}$ \texttt{ID < offers.length \&\& !offers[ID].posted}$]$, which ensures that an offer can be posted only if it has been created but not posted yet;
    \item \emph{``\texttt{OfferCanceled(ID)} can happen only if  \texttt{ID $<$ offers.length \&\&} \texttt{offers[ID].posted}''}, translated to CTL as:\\ $\mathtt{A}[ \neg$\texttt{OfferPosted(ID)}$\mathtt{W}$ \texttt{ID $<$ offers.length \&\& offers[ID].posted   }$]$, which ensures that an offer can be canceled only if it has been posted;
    \item \emph{``if \texttt{finalize} happens, then \texttt{createSolution} can happen only after \texttt{close}''}, translated to CTL as:\\ $\mathtt{AG}(\texttt{finalize})$ $\rightarrow$ $\mathtt{AX}$ $\mathtt{A}$ $[\neg$\texttt{createSolution} $\mathtt{W}$ \texttt{close}$]$, which ensures that solutions can be posted only in the solving phase.
    % \item \emph{``if \texttt{finalize} happens, then \texttt{addAssignment} can happen only after \texttt{createSolution}''}, translated to CTL as:\\ $\mathtt{AG}(\texttt{finalize})$ $\rightarrow$ $\mathtt{AX}$ $\mathtt{A}$ $[\neg$\texttt{addAssignment} $\mathtt{W}$ \texttt{createSolution}$]$, which ensures that assignments can be added only to existing solutions.
\end{itemize}

% after close happens, postOffer can happen only after finalize;
% after finalize happens, createSolution can happen only after close happens;
% after finalize happens, 
% addAssignment can happen only after createSolution happens

% \Anastasia{Are we going to post the generated code somewhere? Because for the last three verified properties we need it.}
% \Aron{Can we say something about how these properties were verified? Maybe mention NuSMV again?}
% \Anastasia{I mentioned NuSMV and a description of the CTL operators that we are using.}
% Section 5.1
% Analysis:
% - computational and communication costs (e.g., number of transactions, messages, contract-function calls, time complexity of solving and verification)
% - privacy

% Section 5.2
% Verification:
% - CTL properties (based on CSF’18 submission)

### 2018-05-18 docs/papers/IEEEBlockchain2018/main.tex

\documentclass[conference, compsoc]{IEEEtran}

\newif\ifExtended
\Extendedfalse

\usepackage{booktabs} % For formal tables
\usepackage{tikz}
\usetikzlibrary{shadows}
\usepackage{pgfplots}
\pgfplotsset{compat=1.10}

\usepackage{colortbl}
\definecolor{Gray}{gray}{0.925}

\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[inline]{enumitem}
\usepackage{comment}
\usepackage{soul}
\usepackage{xspace}

\usepackage{amssymb}
\usepackage{amsmath}

\newcommand{\vect}[1]{\ensuremath{\boldsymbol{#1}}}
\newcommand{\va}{\vect{a}}
\newcommand{\vo}{\vect{o}}

\newcommand{\calA}[0]{\ensuremath{\mathcal{A}}}
\newcommand{\calC}[0]{\ensuremath{\mathcal{C}}}
\newcommand{\calO}[0]{\ensuremath{\mathcal{O}}}
\newcommand{\calP}[0]{\ensuremath{\mathcal{P}}}
\newcommand{\calR}[0]{\ensuremath{\mathcal{R}}}

\newcommand{\Natural}[0]{\ensuremath{\mathbb{N}}}
\newcommand{\Real}[0]{\ensuremath{\mathbb{R}}}

\usepackage{amsthm}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

%-----Solidity Environment--------------------------------
\usepackage{listings, xcolor}
\definecolor{verylightgray}{rgb}{.97,.97,.97}
\lstdefinelanguage{Solidity}{
	keywords=[1]{anonymous, assembly, assert, balance, break, call, callcode, case, catch, class, constant, continue, contract, debugger, default, delegatecall, delete, do, else, event, export, external, false, finally, for, function, gas, if, implements, import, in, indexed, instanceof, interface, internal, is, length, library, log0, log1, log2, log3, log4, memory, modifier, new, payable, pragma, private, protected, public, pure, push, require, return, returns, revert, selfdestruct, send, storage, struct, suicide, super, switch, then, this, throw, transfer, true, try, typeof, using, value, view, while, with, addmod, ecrecover, keccak256, mulmod, ripemd160, sha256, sha3}, % generic keywords including crypto operations
	keywordstyle=[1]\color{blue}\bfseries,
	keywords=[2]{address,..., bool, byte, bytes, bytes1, bytes2, bytes3, bytes4, bytes5, bytes6, bytes7, bytes8, bytes9, bytes10, bytes11, bytes12, bytes13, bytes14, bytes15, bytes16, bytes17, bytes18, bytes19, bytes20, bytes21, bytes22, bytes23, bytes24, bytes25, bytes26, bytes27, bytes28, bytes29, bytes30, bytes31, bytes32, enum, int, int8, int16, int24, int32, int40, int48, int56, int64, int72, int80, int88, int96, int104, int112, int120, int128, int136, int144, int152, int160, int168, int176, int184, int192, int200, int208, int216, int224, int232, int240, int248, int256, mapping, string, uint, uint8, uint16, uint24, uint32, uint40, uint48, uint56, uint64, uint72, uint80, uint88, uint96, uint104, uint112, uint120, uint128, uint136, uint144, uint152, uint160, uint168, uint176, uint184, uint192, uint200, uint208, uint216, uint224, uint232, uint240, uint248, uint256, var, void, ether, finney, szabo, wei, days, hours, minutes, seconds, weeks, years},	% types; money and time units
	keywordstyle=[2]\color{teal}\bfseries,
	keywords=[3]{block, blockhash, coinbase, difficulty, gaslimit, number, timestamp, msg, data, gas, sender, sig, value, now, tx, gasprice, origin},	% environment variables
	keywordstyle=[3]\color{violet}\bfseries,
	identifierstyle=\color{black},
	sensitive=false,
	comment=[l]{//},
	morecomment=[s]{/*}{*/},
	commentstyle=\color{gray}\ttfamily,
	stringstyle=\color{red}\ttfamily,
	morestring=[b]',
	morestring=[b]"
}
\lstset{
	language=Solidity,
	backgroundcolor=\color{verylightgray},
	extendedchars=true,
	basicstyle=\footnotesize\ttfamily,
	showstringspaces=false,
	showspaces=false,
	numbers=left,
	numberstyle=\footnotesize,
	numbersep=1pt,
	tabsize=2,
	breaklines=true,
	showtabs=false,
	captionpos=b,
	xleftmargin=.5em,
	xrightmargin=.5em
}

\newcommand{\change}[2]{\st{#1} {\textcolor{blue}{#2}}}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[textsize=tiny, textwidth=1.5cm,disable]{todonotes}
\newcommand{\TODO}[1]{\todo[inline]{#1}}
\newcommand{\ad}[1]{\todo[color=yellow!50, linecolor=black!50]{\textbf{Abhishek}: #1}}
\newcommand{\Aron}[1]{\todo[color=blue!25, linecolor=black!50]{\textbf{Aron}: #1}}
\newcommand{\Anastasia}[1]{\todo[color=pink, linecolor=black!50]{\textbf{Anastasia}: #1}}
\newcommand{\Scott}[1]{\todo[color=orange!30, linecolor=black!50]{\textbf{Scott}: #1}}

%\usepackage{hyperref}

\usepackage{url}
\graphicspath{{./figs/}}

\usepackage{titlesec}

\titlespacing\section{0pt}{8pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{8pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{8pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

\newcommand{\Platform}{\textit{SolidWorx}\xspace}

\begin{document}

\setlength{\marginparwidth}{1.4cm}

\thispagestyle{plain}
\pagestyle{plain}

\title{\Platform: A Resilient and Trustworthy Transactive Platform for\\Smart and Connected Communities}
\author{
\IEEEauthorblockN{Scott Eisele}
\IEEEauthorblockA{Vanderbilt University \\
Nashville, TN, USA \\ 
scott.r.eisele@vanderbilt.edu
}

\and
\IEEEauthorblockN{Aron Laszka}
\IEEEauthorblockA{University of Houston\\
Houston, TX, USA \\
alaszka@houston.edu}
\and
\IEEEauthorblockN{Anastasia Mavridou}
\IEEEauthorblockA{Vanderbilt University\\
Nashville, TN, USA \\
anastasia.mavridou@vanderbilt.edu}
\and
\IEEEauthorblockN{Abhishek Dubey}
\IEEEauthorblockA{Vanderbilt University \\
Nashville, TN, USA \\ 
abhishek.dubey@vanderbilt.edu
}
}

\maketitle

\input{summary}
\setlength{\belowcaptionskip}{-10pt}
\section{Introduction}
\label{sec:intro}
\input{introduction}

\section{Problem Formulation}
\label{sec:problem}
\input{problem}

\section{\Platform: A Decentralized Transaction Management Platform}
\label{sec:solution}
\input{solution}
\subsection{Smart Contract}
\input{fsolidm}

%\subsection{Workflow}
%\label{sec:analysis}
%\input{workflow}

\subsection{Analysis}
\label{sec:analysis}
\input{analysis}
\section{Case Studies}
\label{sec:results}
\input{results}
\section{Related Research}
\label{sec:related}
\input{related}
\section{Conclusion}
\label{sec:conclusion}
\input{conclusion}

\vspace{0.5em}
\noindent\textbf{Acknowledgement:}
This work was funded in part by a grant from Siemens, CT and in part by a grant from NSF under award number CNS-1647015.

\let\oldbibliography\thebibliography
\renewcommand{\thebibliography}[1]{\oldbibliography{#1}
\setlength{\itemsep}{0pt}} %Reducing spacing in the bibliography.

\bibliographystyle{IEEEtran}
%\setlength{\bibsep}{0.0pt}
\small{
\bibliography{references} 
}

%\newpage
%\tableofcontents

\end{document}

### 2018-05-18 docs/papers/IEEEBlockchain2018/problem.tex

We first introduce a base formulation of an abstract resource allocation problem (Section~\ref{sec:ResAllPro}), which captures the core functionality of a transactive platform for SCC.
Then, we describe two  examples of applying this formulation to solving practical problems in SCC (Section~\ref{sec:ExaApp}).
We conclude the section by introducing various extensions to the base problem formulation, in the form of alternative objectives and additional constraints (Section~\ref{sec:ProForExt}).
A list of the key symbols used in the resource allocation problem can be found in Table~\ref{tab:symbols}.
%\ad{we need to include validity interval (described wrt to a global time base) as a property for the offers.}
%\Aron{maybe as an extension in Section~\ref{sec:ProForExt}}

\begin{table}[t]
    \centering
    \caption{List of Symbols}
    \label{tab:symbols}
    \renewcommand{\arraystretch}{1.2}
    \begin{tabular}{|c|p{6.86cm}|}
        \hline
        Symbol & Description \\
        \hline
        \rowcolor{Gray} $P$ & set of resource providers \\
        $C$ & set of resource consumers \\
        \rowcolor{Gray} $T$ & set of resource types \\
        $O\!P$ & set of providing offers \\
        \rowcolor{Gray} $OC$ & set of consumption offers \\
        $o_P$ & resource provider who posted offer $\vo \in O\!P$ \\
        \rowcolor{Gray} $o_C$ & resource consumer who posted offer $\vo \in OC$ \\
        $o_Q(t)$ & amount of resources of type $t \in T$ provided or requested by offer $\vo$ \\
        \rowcolor{Gray} $o_V(t)$ & unit reservation price of offer $\vo$ for resource type $t \in T$ \\
        $a_{O\!P}$ & providing offer from which assignment $\va$ allocates resources \\
        \rowcolor{Gray} $a_{OC}$ & consuming offer to which assignment $\va$ allocates resources \\
        $a_Q$ & amount of resources allocated by assignment $\va$ \\
        \rowcolor{Gray} $a_T$ & type of resources allocated by assignment $\va$ \\
        $a_V$ & unit price for the resources allocated by assignment $\va$ \\
        \hline
    \end{tabular}
\end{table}

\subsection{Resource Allocation Problem}
\label{sec:ResAllPro}

In essence, the objective of the transactive platform is to allocate resources from users who provide resources to users who consume them.
The sets of \emph{resource providers} and \emph{resource consumers} are denoted by $P$ and $C$, respectively.
Note that a user may act both as a resource provider and as a resource consumer at the same time, in which case the user is a member of both $P$ and~$C$. 
Resources that are provided or consumed belong to a set of \emph{resource types}, which are denoted by $T$.
A resource type is an abstract concept, which captures not only the inherent characteristics of a resource, but all aspects related to providing or consuming resources.
For example, a resource type could correspond to energy production and consumption in a specific time interval, or it could correspond to a ride between certain location at a certain time.

Each provider $p \in P$ may post a set of \emph{providing offers}. % $O_p$.
Each providing offer $\vo$ % \in O_p$ 
is a tuple $\vo = \langle o_P, o_Q, o_V \rangle$, where $o_P \in P$ is the provider who posted the offer, $o_Q \in T \mapsto \Natural$ is the amount of resources offered from each type (i.e., $o_Q(t)$ is the amount of resources offered from type $t \in T$), and $o_V \in T \mapsto \Natural$ is the unit reservation price asked for each resource type (i.e., $o_V(t)$ is the value asked for providing a unit resource of type $t \in T$).
Each offer $\vo = \langle o_P, o_Q, o_V \rangle$ defines a set of alternatives: provider $o_p$ offers to provide either $o_Q(t_1)$ resources of type $t_1 \in T$ or $o_Q(t_2)$ resources of type $t_2 \in T$, but not at the same time.
However, convex linear combinations, such as providing $\lfloor \alpha \cdot o_Q(t_1)  \rfloor$ resources of type $t_1 \in T$ and $\lfloor (1 - \alpha) \cdot o_Q(t_2) \rfloor$ resources of type $t_2 \in T$ at the same time (where $\alpha \in [0, 1]$), are allowed.
For example, an offer $\vo$ providing $o_Q(t_1)$ units of energy in time interval~$t_1$ or $o_Q(t_2)$ units of energy in time interval $t_2$ may provide $\lfloor 0.5 \cdot o_Q(t_1) \rfloor$ energy in time interval $t_1$ and $\lfloor 0.5 \cdot o_Q(t_2) \rfloor$ energy in time interval $t_2$.
The set of all offers posted by all the providers is denoted by $O\!P$. % = \bigcup_{p \in P} O_p$.

Each consumer $c \in C$ posts a set of \emph{consumption offers}. % $O_c$.
Each consumption offer $\vo$ % \in O_c$ 
is a tuple $\vo = \langle o_C, o_Q, o_V \rangle$, where $o_C \in C$ is the consumer who posted the offer, $o_Q \in T \mapsto \Natural$ is the amount of resources requested from each type (i.e., $o_Q(t)$ is the amount of resources requested from type $t \in T$), and $o_V \in T \mapsto \Natural$ is the unit reservation price offered for each resource type (i.e., $o_V(t)$ is the value offered for a unit resource of type $t \in T$).
Similar to providing offers, consumption offers also define a set of alternatives.
The set of all offers posted by all the consumers is denoted by $OC$. % = \bigcup_{c \in C} O_c$.

A \emph{resource allocation} $A$ is a set of resource assignments.
Each resource assignment $\va \in A$ is a tuple $\va = \langle a_{O\!P}, a_{OC}, a_Q, a_T, a_V \rangle$, where $a_{O\!P} \in O\!P$ is a providing offer posted by a provider, $a_{OC} \in OC$ is a consumption offer posted by a consumer, $a_Q \in \Natural$ and $a_T \in T$ are the amount and type of resources allocated from offer $a_{O\!P}$ to $a_{OC}$, and $a_V \in \Natural$ is the unit price for the assignment.

A resource allocation $A$ is \emph{feasible} if
\begin{align}
\forall \vo \in O\!P: ~ & \sum_{t \in T} ~ \sum_{\substack{\va \in A:\\a_{O\!P} = \vo \,\wedge\, a_T = t}} \frac{a_Q}{o_Q(t)} \leq 1 \label{eq:feasable1} \\
\forall \vo \in OC: ~ & \sum_{t \in T} ~ \sum_{\substack{\va \in A:\\a_{OC} = \vo \,\wedge\, a_T = t}} \frac{a_Q}{o_Q(t)} \leq 1 \\
%\end{align}
%\begin{align}
\forall \va \in A: ~ & {\left(a_{O\!P}\right)}_V(a_T) \leq a_V \\
\forall \va \in A: ~ & {\left(a_{OC}\right)}_V(a_T) \geq a_V \label{eq:feasable4} .
\end{align}

In other words, a resource allocation is feasible if the resources assigned from each providing offer (or consuming offer) is a convex linear combination of the offered (or requested) resources, and if the value in each assignment is higher than (or lower than) the reservation price of the providing offer (or consuming offer).
%\begin{align}
%\forall op = \langle p, q, v \rangle \in O\!P: & \sum_{t \in T} ~ \sum_{\langle op, oc, q', t, v' \rangle \in A} \frac{q'}{q(t)} \leq 1 \\
%\forall oc = \langle c, q, v \rangle \in OC: & \sum_{t \in T} ~ \sum_{\langle op, oc, q', t, v' \rangle \in A} \frac{q'}{q(t)} \leq 1 
%\end{align}
%\begin{align}
%\forall op = \langle p, q, v \rangle \in O\!P, \, \forall \langle op, oc, q', t, v' \rangle \in A: \, & v(t) \leq v' \\
%\forall op = \langle p, q, v \rangle \in O\!P, \, \forall \langle op, oc, q', t, v' \rangle \in A: \, & v(t) \geq v' .
%\end{align}

The objective of the base formulation of the \emph{resource allocation problem} is to maximize the amount of resources assigned from providers to consumers.
We define the base formulation of the problem as follows.

\begin{definition}[Resource Allocation Problem]
Given sets of providing and consumption offers $O\!P$ and $OC$, find a feasible resource allocation $A$ that attains the maximum
\begin{equation}
\max_{A:\, A \textnormal{ is feasible}} \, 
\sum_{\va \in A} a_Q . \label{eq:objective}
\end{equation}
\end{definition}

\subsection{Example Applications}
\label{sec:ExaApp}

To illustrate how the Resource Allocation Problem (RAP) may be applied in smart and connected communities, we now describe two example problems that can be expressed using RAP.

\subsubsection{Energy Futures Market}
\label{sec:energyFuturesMarket}

\newcommand{\etime}[0]{\ensuremath{t}}

We consider a residential energy-futures market in a transactive microgrid.
In this application, resource consumers model residential energy consumers (i.e., households), while resource providers model the subset of consumers who have energy providing capabilities (e.g., solar panels, batteries).
We divide time into fixed-length intervals (e.g., 15 minutes),
%\ad{we should include time as a first class concept in the problem formulation itself}
 and let each resource type correspond to providing or consuming a unit amount of power (e.g., 1 W) in a particular time interval.

Based on their predicted energy supply and demand, residential consumers (or smart homes acting on their behalf) post offers to provide or consume energy in future time intervals.
For instance, a provider may predict that it will be able to generate a certain amount of power $\pi$ using its solar panel during time intervals $\etime_1, \etime_2, \ldots, \etime_N \in T$.
Then, it will submit a \emph{set of $N$ offers}: for each time interval~$\etime \in \{\etime_1, \ldots, \etime_N\}$ in which energy may be produced, it posts an offer specifying % to provide the predicted amount $o_Q(t)$ of power (and setting all other intervals $t' \neq t$ to $o_Q(t') = 0$ in the offer for interval $t$):
\begin{equation}
    o_Q(t) = \begin{cases}
    \pi & \textnormal{ if } t = \etime \\
    0 & \textnormal{ otherwise.}
    \end{cases}
\end{equation}
Alternatively, the provider may have a fully charged battery, which could be discharged in any of the next $N$ intervals $\etime_1, \etime_2 \ldots, \etime_N$.
Let $\pi$ denote the amount of power that could be provided if the battery was fully discharged in a single time interval.
Then, the provider will submit a \emph{single offer} specifying
%with $o_Q(t), o_Q(t+1), \ldots, o_Q(t+9)$ all being equal to the battery capacity over interval length (and setting all other intervals $t' < t$ or $t' > t+9$ to $o_Q(t') = 0$).
\begin{equation}
    o_Q(t) = \begin{cases}
    \pi & \textnormal{ if } t \in \left\{ \etime_1, \etime_2, \ldots, \etime_N \right\} \\
    0 & \textnormal{ otherwise.}
    \end{cases}
\end{equation}

The reservation prices of the offers should consider the energy prices of the utility company (i.e., the alternative to local trading) and %, the flexibility of the residents' demand (e.g., some appliances, such as a dishwasher, may be rescheduled), and 
the cost of providing energy (e.g., cost of battery depreciation due to charging and discharging).

% Example Problem: Energy Trading
% - each commodity corresponds to a unit amount of energy production in a given time interval
% - objective: maximize total amount of energy traded
% - constraint: clearing price set by a DSO

\subsubsection{Carpooling Assignment}
\label{sec:carpoolingprob}
We consider the problem of assigning carpooling riders to drivers with empty seats in their cars.
In this application, resource consumers model riders, while resource providers model drivers.
We again divide time into fixed-length intervals, and we divide the space of pick-up locations into a set of areas (e.g., city blocks).
Then, we let a resource type correspond to a ride from a particular area in a particular time interval to a particular area. 
A unit of a resource is a single seat for a ride.

A provider (i.e., driver) who has $\pi$ empty seats in its car will post a providing offer. 
Let $\Pi \subseteq T$ denote the set of   combinations of pick-up and drop-off areas and pick-up times that are feasible for the provider.
Then, the provider's offer specifies
\begin{equation}
    o_Q(t) = \begin{cases}
    \pi & \textnormal{ if } t \in \Pi \\
    0 & \textnormal{ otherwise.}
    \end{cases}
\end{equation}
Similarly, a consumer (i.e., rider) who needs 1 seat will post a consuming offer, specifying
\begin{equation}
    o_Q(t) = \begin{cases}
    1 & \textnormal{ if } t \in \Pi \\
    0 & \textnormal{ otherwise,}
    \end{cases}
\end{equation}
where $\Pi$ is the set of combinations (i.e., pick-up and drop-off areas and pick-up times) that are feasible for the rider.

\subsection{Problem Formulation Extensions}
\label{sec:ProForExt}

\Aron{Note to self: review this subsection!}
The Resource Allocation Problem that we introduced in Section~\ref{sec:ResAllPro} can capture a wide range of real-world problems.
However, some problems may not be easily expressed using the constraints (Equations \eqref{eq:feasable1} to \eqref{eq:feasable4}) and the objective (Equation \eqref{eq:objective}) of the base problem formulation.
For this reason, here we introduce a set of alternative objective formulations and additional constraints for resource allocation.

\subsubsection{Objectives}
\label{sec:extObj}

We first introduce alternative objective formulations, which quantify the utility of a resource allocation based on alternative goals.

\textbf{Resource Type Preferences:}
Equation \eqref{eq:objective} assumes that exchanging a unit of any resource type is equally beneficial.
In some practical scenarios, exchanging certain resource types may be more beneficial than exchanging others.
For each resource type~$t \in T$, let $\beta_t$ denote the utility derived from exchanging a unit of resources of type $t$.
Then, the utility of a resource allocation~$A$ can be expressed as
\begin{equation}
    \sum_{\va \in A} \beta_{\left(a_T\right)} \cdot a_Q .
\end{equation}

\textbf{Provider and Consumer Benefit:}
The reservation price~$o_V(t)$ of a providing offer $\vo$ means that provider $o_P$ is indifferent to (i.e., derives zero benefit from) exchanging resources of type $t$ at unit price $o_V(t)$.
Hence, the unit benefit derived by the provider from exchanging at a higher price $a_V \geq o_V(t)$ is equal to $a_V - o_V(t)$.
Similarly, the unit benefit derived by a consumer, who posted an offer $\vo$, from exchanging resources of type $t$ at price $a_V$ is equal to $o_V(t) - a_V$.
Therefore, the total benefit created by an assignment $\va$ for provider $a_{O\!P}$ and consumer $a_{OC}$ is
\begin{align}
    & a_Q \cdot \left[ a_V - \left(a_{O\!P}\right)_V(a_T) \right] + a_Q \cdot \left[ \left(a_{OC}\right)_V(a_T) - a_V \right] \nonumber \\
    = & a_Q \cdot \left[ \left(a_{OC}\right)_V(a_T) - \left(a_{O\!P}\right)_V(a_T) \right] ,
\end{align}
and the total benefit created by a resource allocation $A$ for all the providers and consumers is
\begin{equation}
    \sum_{\va \in A}  a_Q \cdot \left[ \left(a_{OC}\right)_V(a_T) - \left(a_{O\!P}\right)_V(a_T) \right] .
\end{equation}

\subsubsection{Constraints}
\label{sec:extConstr}

Next, we introduce additional feasibility constraints that may be imposed on the resource allocations.

\textbf{Price Constraints:}
A regulator (e.g., utility company in a transactive energy platform) may impose constraints on the prices at which resources may be exchanged (e.g., based on bulk-market prices).
If the minimum and maximum unit prices for resource type $t \in T$ are $min_t$ and $max_t$, respectively, then we can express price constraints as
\begin{equation}
    \forall \va \in A: ~ min_{\left( a_T \right)} \leq a_V \leq max_{\left( a_T \right)} . 
\end{equation}

\textbf{Pairwise Constraints:}
Due to physical constraints, exchanging resources of certain types between certain pairs of prosumers may be impossible.
If the set of prosumer pairs that may exchange resources of type $t \in T$ is denoted by~$E_t \subseteq P \times C$,  we can express pairwise constraints as
\begin{equation}
    \forall \va \in A: \left( a_{O\!P} , a_{OC} \right) \in E_{\left( a_T \right)} .
\end{equation}

\textbf{System-wide Constraints:}
Similar to pairs of providers and consumers, the system itself may be subject to physical limitations on exchanging resources.
For instance, if the total amount of resources that may be exchanged for type $t \in T$ is at most $limit_t$, then we can impose the following system-wide constraint on resource allocations:
\begin{equation}
\forall t \in T: ~
    \sum_{\va \in A: \, a_T = t} a_Q \leq {limit}_t .
\end{equation}

\textbf{Real-Valued Offers and Allocations:}
Finally, we may also relax some of the constraints of the base formulation.
In particular, we may allow real-valued quantities in offers and allocations (i.e., $o_Q: T \mapsto \Real_+$ and $a_Q \in \Real_+$) as well as real-valued prices (i.e., $o_V: T \mapsto \Real_+$ and $a_V \in \Real_+$).

% - market must be cleared according to some schedule (e.g., every hour)
% - may be computationally hard due to additional constraints (basic problem is a simple matching)

### 2018-05-18 docs/papers/IEEEBlockchain2018/results.tex

% Section 6.1
% Testbed?

% Section 6.2
% Numerical results

To evaluate our platform, we present two case studies, based on the energy trading and carpooling problems (Section~\ref{sec:ExaApp}), with numerical results. 
%
The computational results for the carpool example were obtained on a virtual machine configured with 16 GB of RAM and 4 cores of a i7-6700HQ processor. The energy market example results were obtained on a virtual machine configured with 8GB of RAM and 2 cores of an i7-6700HQ processor. For these experiments, we used
 our private Ethereum blockchain network~\cite{EthereumBook}.

\subsection{Carpooling Problem}
\label{sec:carpool}

\ifExtended
\begin{figure}[t]
\begin{center}
\centerline{\includegraphics[width=.85\columnwidth]{taz_chloropeth.png}}
\caption{Vanderbilt University traffic demand distribution.}
\label{fig:demand_dist}
\end{center}
\vspace{-0.3in}
\end{figure}
\fi

%\Aron{This paragraph is just one sentence.}
In this section, we describe a simulated carpooling scenario. The problem of carpooling assignment was introduced earlier in Section~\ref{sec:carpoolingprob}.
%the implementation of the carpooling problem (Section~\ref{sec:carpoolingprob}).
Here, we model a carpool prosumer as an actor that specifies
\begin{enumerate*}
    \item whether it is providing or requesting a ride,
    \item the number of seats being offered/requested,
    \item a residence,
    \item a destination,
    \item a time interval during which the ride is available/required,
    \item and a radius specifying how far out of their way they are willing to travel.
\end{enumerate*}
%and is able to submit offers based on these factors. 
To setup the carpooling problem, we need to identify these parameters and encode them as offers.

\begin{figure}[t]
\centering
\includegraphics[width=0.7\columnwidth]{figs/clusters.png}
\caption{
%Distribution of riders, carpool locations, and destinations. 
Green and red dots mark the 75 residences (anonymized and resampled). Blue dots are destinations on campus. We used K-Means to identify 20 central locations (yellow dots) for pickup.
%from which providers and consumers travel. Blue dots are destinations on campus. We used K-Means to identify 20 central locations (yellow dots) for pickup. At this zoom level, some of the red and green points overlap and hide each other.
}
\label{fig:clusters}
\end{figure}

Residences were generated by sampling from real-trip distribution data of Vanderbilt 
\ifExtended
University, see Figure~\ref{fig:demand_dist}.
\else
University.
\fi
\ifExtended
This data provides Traffic Analysis Zone (TAZ)\footnote{TAZ is a special area delineated by state and/or local transportation officials for tabulating traffic-related data, especially journey-to-work and place-of-work statistics.} level data for trips taken from different parts of the city to the main university campus.
\fi
Destinations were chosen uniformly at random for each prosumer from the~5 garages around Vanderbilt University.
Other parameters were also chosen randomly:  number of seats from the range of 1 to 3,  prosumer type from producer or consumer,  time interval from 15-minute intervals between 7:00 and 9:30AM. The ``out of the way'' metric was chosen to be half of the distance between the residence and the destination. For a provider, the center of the pick-up circle is the midway point between the residence and the destination, and for a consumer,  the center is the residence.

Since each prosumer has a distinct residence, encoding it as a unique resource type would mean that every  prosumer would need to have the address of every other prosumer to determine if they are in their pick-up range. Instead, we specify \textit{pick-up points} which are public locations were carpoolers can meet. Each prosumer can determine which pick-up points are within their out-of-the-way radius and list those points in their offer. To encode these values, we assign an ID to each pickup point and destination. Finally, we encode each 15-minute interval using a timestamp. %s in the time range specified.

An offer consists of a collection of alternative resource types, each with a quantity and value.
We encode a resource type, which is a combination of a time interval, a pick-up point, and  a destination, as a 64-bit unsigned integer. %The generic form of this resource type is ``timestampSrcIdDstId'', and specific instance is 152362170053 where the
For example, if timestamp is 1523621700,  pick-up location ID is 15, and destination ID is 3, then the resource type is 1523621700153. %An offer can be composed of multiple resource types and so we include one for combination of 15 minute interval and pick up point within range. An example of a full 
A complete offer may look as follows: 
%{64, True, 55, {1523623500173: 2, 1523621700153: 2, 152362440053: 2, 1523624400173: 2}, {1523623500173: 10, 1523621700153: 10, 152362440053: 10, 1523624400173: 10}.
%\footnotesize{
%\vspace{-0.1in}
\begin{align*}
      \{ \texttt{True}, ~ %& \\
     & \{1523623500173: 2, %\\ 
        1523623500153: 2, \\
     &  ~\,1523624400153: 2, %\\
        1523624400173: 2\}, \\
     & \{1523623500173: 10, %\\ 
        1523623500153: 10, \\
     & ~\,1523624400153: 10, %\\
        1523624400173: 10\} ~\} .
\end{align*}
%\vspace{-0.1in}
%\normal
%
In this offer, the prosumer is offering rides (\texttt{True} for providing), has two pick-up locations in range (17 and 15), drives to destination 3, is available in two time intervals, offers 2 seats, and asks for value 10 in exchange for a ride. %It has 4 resource types, they specify 2 times (1523623500, 1523624400) and two pickup points (17, 15).

%\Aron{This sentence seems to have been mixed up, I'm not sure what it is supposed to be.}
%We have used Vanderbilt University employees' trip distribution data for modeling agents used in our simulation. and \textbf{Traffic analysis zone (TAZ)} dataset from US Census \cite{census2016nashville} to model demand distribution of Vanderbilt employees in each TAZ. TAZ is a special area delineated by state and/or local transportation officials for tabulating traffic-related data, especially journey-to-work and place-of-work statistics. Based on the demand distribution in each TAZ, we have sampled random points in each TAZ based on likelihood. So, if one TAZ has 100 people and another TAZ has 1000 people, then the likelihood of picking people from the 1000-people TAZ will be 10 times higher than from the 100-people TAZ. Figure~\ref{fig:demand_dist} shows the demand rate of Vanderbilt employees in each TAZ.
In our experiment, we selected 75 prosumers for the carpool service simulation. The red and green points in Figure~\ref{fig:clusters} are the locations of the consumers and producers randomly sampled from the anonymized distribution data of employees of Vanderbilt University. The yellow points were selected as pick up locations using K-Means clustering choosing 20 clusters. The blue points are 5 garages around Vanderbilt campus where employees typically park.

Figure \ref{fig:offers} shows all the offers posted to the carpool platform. Each color is a unique offer. For example, the providing offer that is represented by red bars on the first six columns (7:00--8:15AM) having a height of 2, offers 2 seats with pick-up any time between 7:00AM and 8:15AM. The offers are stacked, showing how many seats are potentially available at that time. The chart combines all start and end locations; however, these could be separated.

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/Offers.png}
\caption{Carpooling offers posted.}
\label{fig:offers}
\end{figure}

Figure \ref{fig:matches} shows the offers matched in each interval. For example, at 7:45AM, 2 providing offers--yellow (1 seat) and blue (1 seat)--and two consuming offers--yellow (1 seat) and orange (1 seat)--were matched. These are again grouped only by time in the figure, and not by start or end points. 
%This experiment was run on a \textcolor{red}{describe the machine}.  
%other runs solver: 18.3ms, 26.6ms
%other runs finzlize : 29s, 11.78s
The running time of the solver was $23$ ms, while the time between the request for finalization and emission of \texttt{AssignmentFinalized} events was $29$ s.
%

%between the receipt of the start finalize event and finalize completion event \Aron{I still don't understand, what is the ``start finalize event''? What is the ``finalize completion event''? When the contract emits AssignmentFinalized? When it is mined?} was $0.00039$ seconds.

%Note that in this experiment, we are running our own private Ethereum blockchain network~\cite{EthereumBook}.

\begin{figure}[t]
\centering
\includegraphics[width=0.9\columnwidth]{figs/matches.png}
\caption{Matched (i.e., assigned) offers in the solution.}
\label{fig:matches}
\end{figure}

% Table \ref{tab:timing} shows the measured time taken to solve the system of equations and the time between the receipt of the start finalize event and finalize completion event. 
% \begin{table}[t]
%     \centering
%     \caption{Performance Timings}
%     \label{tab:timing}
%     \renewcommand{\arraystretch}{1.2}
%     \begin{tabular}{|c|c|}
%         \hline
%         Solve Time & .0233s \\
%         \hline
%         Finalize Time & 0.00039s\\
%         \hline
%     \end{tabular}
% \end{table}

\begin{figure}[t]
    \centering
% \vspace{-0.1in}
%    \makebox[\linewidth]{
    \includegraphics[width=0.95\linewidth]{totals.png}
%    }
    %\vspace{-0.2em}
    \caption{Total energy production capacity (green) and energy demand (red) for each interval, as well as the total energy traded in each interval (blue).}
    \label{fig:totals}
\end{figure}

\ifExtended
\begin{figure}[t]
\centering
    \includegraphics[width=0.95\linewidth]{figs/MultipleSolutions_white.png}
%    }
    %\vspace{-0.2em}
    \caption{\Platform recomputes the  solution for each future interval as more information becomes available. Each interval is finalized 2 cycles before it has to be actuated on the microgrid. The top stack for each interval is the ``finalized'' solution.}
    \label{fig:MultipleSolutions}

%     \includegraphics[width=1.0\linewidth]{totals_numbers.png}
% %    }
%     %\vspace{-0.2em}
%     \caption{Monetary impact of trades assuming a cost of \$0.12 per KWH }
%     \label{fig:monetary}
    %\vspace{-0.12in}
\end{figure}
 \fi 
 \ifExtended

\begin{figure}[t]
    \centering
\includegraphics[width=\linewidth]{solveTime.png}
    \caption{ Running time of the solver for each cycle}
    \label{fig:solve-time}
% \end{subfigure}%
%  \begin{subfigure}{.5\columnwidth}
%   \centering
%   \includegraphics[width=\linewidth]{FinalizeTime.png}
% \caption{}
%   \label{fig:finalize-time}
% \end{subfigure}   
%\caption{ Running time of the solver for each cycle.}
%(b) Time for smart contract to finalize a trade}  
\end{figure}
\fi
\begin{figure} [h]
    \centering
% \vspace{-0.1in}
%    \makebox[\linewidth]{
    \includegraphics[width=0.9\linewidth]{failure.pdf}
%    }
    %\vspace{-0.2em}
    \caption{A failure scenario with failure at 8:15AM. The solver can submit new solutions as time progresses; the most recent solution is the color that is on the top of the stack for an interval.}
    \label{fig:failure}
    \vspace{-0.05in}
\end{figure}

% \begin{figure} [t]
%     \centering
% % \vspace{-0.1in}
% %    \makebox[\linewidth]{
%     \includegraphics[width=1.0\linewidth]{trades.png}
% %    }
%     %\vspace{-0.2em}
%     \caption{Shows finalized solution for the amount of energy each prosumer is expected to produce(top) or consume(bottom) during each interval}
%     \label{fig:trades}
%     %\vspace{-0.12in}
% \end{figure}

\subsection{Energy Trading Problem}
 \label{sec:energy}

  To show the versatility of our transaction management platform, we now apply it to the problem of energy trading  within a microgrid, which we introduced in Section~\ref{sec:energyFuturesMarket}.
  %which we described in \cite{Laszka17}\Aron{We should mention what we did in~\cite{Laszka17} if we reference it.}.  
\ifExtended
  A key feature of this problem is peer-to-peer energy trading within microgrids to reduce the load on  distribution system operators (DSO) \cite{kok2016society,cox2013structured,melton2013gridwise}.  Such mechanisms can improve system reliability and efficiency by integrating inverter-based renewable resources into the grid and  supplying power to local loads when the main grid is interrupted.
  \fi
%  \input{feeder}
  In this example, a prosumer is modeled as an actor with an energy generation and consumption profile for the near future. In practice, the generation profile would be typically derived from predictions based on the weather, energy generation capabilities, and the amount of battery storage available. The consumption profile would be derived from flexible power loads, like  washers and electric vehicles.

To represent future generation or consumption at a certain time, % loads as offers to the platform the 
resource types encode %composing an offer would simply be the
timestamps for 15-minute intervals, during which the power will be generated or consumed. 
As an example, consider a battery that has 500 Wh energy, which could be discharged any time between 9AM and 10AM.
%A simplified example (using clock time, rather than epoch time) could be a batter has stored 500W-h of energy and makes it available from 9:00-10:00AM. 
This can be represented by an offer having resource types 900, 915, 930, and 945, specifying a quantity of 500 Wh for each.

 For our simulation, the prosumer energy profiles are load traces recorded by Siemens during a day from a microgrid in Germany, containing $102$ homes %across $11$ feeders 
 ($5$ producers and $97$ consumers). Since the dataset does not include prices, we assume reservation prices to be uniform in our experiments, and focus on studying the amount of energy traded and the performance of the system. %Table \ref{tab:prosumers}
%Figure~\ref{fig:feeder} describes the feeder structure, the number of participants per feeder, and  the feeder safety limits.

%Each trace was divided into 15-minute time intervals that the prosumer can sumbit as an offer.

Figure~\ref{fig:totals} shows the total production (green) and consumption (red) across this microgrid, as well as the total energy traded per interval (blue) using our platform. The horizontal axis shows the starting time for each of the $96$ intervals.

\ifExtended
In this implementation, the prosumers do not submit all of the offers simultaneously, instead they post offers for the 5 intervals beyond the current interval being finalized. The justification for this is that a prosumer may not know their energy profile for the entire day and may only be able to make accurate estimates for a few future intervals at a time. Similarly a solver may be implemented to create matches for only the interval being finalized or may ``look-ahead'' at future offers and create match that may not be optimal for the current interval but allows better matches to be made in the future. This is a trade off between the complexity of the problem and how close the solution is to the global optimum.
%In this implementation, our solver finds a match for the current interval while looking ahead at the next 4 intervals.
%This can be seen in Figure  \ref{fig:MultipleSolutions},
%Since additional offers are being submitted during the simulation 
\Aron{This will be very unclear to the reviewers since the platform described in this paper does not do this.}
\Scott{Is that a better explanation?}
% Since the prosumers have a schedule for their energy consumption, they can post offers for several intervals in the future. By including offers for multiple intervals, the solver can find assignments for future intervals.
% As more information becomes available over time, the solver may find better solutions, as shown by Figure \ref{fig:MultipleSolutions}.
\fi

\ifExtended
For example, in the first interval, the green solution is submitted, which includes a matching for then current interval (at 7:30AM) as well as the next four intervals.
%, 7:45, 8:00, 8:15, and 8:30. 
Then, in the second interval, the yellow solution is added, which supersedes the green solution for intervals at 8:00AM, 8:15AM, and 8:30AM because more offers are now available and a better solution may be found. %, it also adds a solution for the 8:45 interval. 
% In this simulation, the solver solves for the current interval to be finalized as well as the next 4 intervals. The number of additional intervals can be varied to trade off between solve time, and overall solution optimality. 
\fi

%The solver time in this casestudy was 3s on average. Compared to carpool problem, this problem has more variables

\ifExtended
Figure \ref{fig:solve-time} shows the running time of the solver.
%with the 4 interval look-ahead. 
The time on the horizontal axis is the actual clock time, which shows that the simulation ran for about an hour. We also note that at about 20 minutes from the beginning (i.e., around interval 48), %which corresponds to noon in the simulated time series, 
solving time begins to increase. 
This increase is due to offers being made that span multiple intervals, i.e there are multiple resource types as in our 500Wh example.
\fi
%These kind of offers are possible because some of the selling offers can be valid for a range of future intervals instead of requiring immediate consumption (thanks to battery storage). 
%\Aron{Again, the reviewer will have no idea what we are talking about here.}
%\Scott{Is that more clear?}

In another simulation, we exercise the hybrid solver architecture by running multiple solvers, and after some time, cause one to fail. This result is shown in Figure~\ref{fig:failure}. The narrow vertical red line indicates when solver 1 fails at 8:15AM. Up until that point, solver 1 submitted the green, yellow, light blue, orange solutions, with the final solution being red.% Since the solver computes matching for the subsequent four intervals.
%solver 1 has a solution for them but they are not improved as new information is available. 
On the other hand we see that solver 2 continues to provide solutions for later intervals.

% %To evaluate the performance of our solution, we take the following measurements:  running time of the solver to find a potential solution; time taken by the smart contract to finalize an interval\Aron{What is included in this? How is it measured? Very uncler!};  percentage of demand that is met with trades;  percentage of supply that is consumed through trades.

% Results are shown in Figure \ref{fig:totals}.
% \Aron{?}

% \Aron{Font in figure is unreadable, it needs to be orders of magnitude bigger.}
% Figure \ref{fig:finalize-time} shows the time between the finalize event and the finalization of trades.

%The vertical narrow red line identifies the interval at 9:00am. In Solution 1 (), the purple bars were the last solution provided by Solver 1, while Solver 2 provides 4 more solutions during the next 4 intervals.

%\Aron{We should move the detailed descriptions from the figure captions into the main text!}

### 2018-05-18 docs/papers/IEEEBlockchain2018/solution.tex

Now, we describe the \Platform platform, which (1) allows prosumers\footnote{An actor or an agent that can both provide and consume resources.} to post offers and (2) can find a solution to the resource allocation problem in an efficient and trustworthy manner. The actor-based architecture, proposed initially in~\cite{agha1985actors}, has been accepted as a standard model for building distributed applications. The key aspect of an actor-based system are interfaces with well defined execution models~\cite{basu2011rigorous}.

%\Aron{We need to explain why we do this and why this way.}
%We \change{envision the system as an actor-based distributed architecture}{propose an actor based distributed architecture for the system}, where multiple \Aron{What are the actors?}actors exchange information about their resources and offers. We follow the \Aron{Is this relevant to this conference?} component based software-engineering (CBSE) principle, which has been accepted as a standard practice to develop robust, modular, and maintainable software stacks~\cite{heineman2001component}.  The guiding principles of CBSE are interfaces with well defined execution models \cite{basu2011rigorous}, compositional  semantics \cite{schmidt2003trustworthy}, and model driven analysis \cite{kumar2014colored}. We use an architecture called `Resilient Information Architecture Platform for Smart systems' (RIAPS), developed at our institute~\cite{riaps}. \Aron{How is this related to blockchains?} Each actor in RIAPS is a composition of several libraries that provide (1) a component model that provides a concurrent model of computation for building distributed real-time applications, (2) a messaging framework for facilitating interactions among actors, (3) a resource-management framework for controlling the use of computational resources, (4) a fault-management framework for detecting and mitigating faults in all layers of the system, (5) a security framework to protect the confidentiality, integrity, and availability of system under cyber-attacks, (6) a fault tolerant time synchronization service,  (7) a discovery framework for establishing the network of interacting actors of an application, and (7) a deployment and management framework for the administration and control of the distributed applications from a control room. In this paper, we do not discuss the RIAPS architecture further. Rather, we focus on the architecture of the transaction management platform, which is a distributed application built on top of RIAPS platform. \Aron{It is not actually built on top of RIAPS.}
%\Aron{Can we just omit this paragraph starting from RIAPS? We did not use it, and it might just confuse the reviewers (e.g., how the RIAPS functionality would be integrated with the Ethereum peer-to-peer network.)}

%\subsection{Transaction Management Platform}

\begin{figure}[t]
    \centering

% \end{figure}

% \begin{figure}[t]
% \centering
%\resizebox{\columnwidth}{%
\begin{tikzpicture}[x=1.2cm, y=1.2cm, font=\tiny,
  Component/.style={fill=white, draw, align=center, rounded corners=0.1cm, drop shadow={shadow xshift=0.05cm, shadow yshift=-0.05cm, fill=black}},
  Connection/.style={<->, >=stealth, shorten <=0.05cm, shorten >=0.05cm}]

\foreach \pos/\name in {1.6/pros3, 0.8/pros2} { %, 0.0/pros1} {
  \node [Component] (\name) at (\pos - 4, \pos) {Prosumer\\(\texttt{Python}, \texttt{geth})};
}

\node [Component] (dso) at (-1, 2.6) {Directory\\(\texttt{Python}, \texttt{geth})};

\node [Component] (solver) at (-4, 0) {Solver\\(\texttt{Python}, \texttt{CPLEX}, \texttt{geth})};

\fill [fill=black!15] (90:1.5) -- (200:1.5) -- (340:1.5) -- (90:1.5);

\foreach \pos in {90, 200, 340} {
  \node [Component] at (\pos:1.5) {Blockchain\\ miner (\texttt{geth})};
}

\node [Component, dotted] (contract) at (0, 0) {Smart contract\\(\texttt{Solidity})};

\draw [Connection, bend left=62] (solver) to node [midway, left, shift={(-0.25,0)}] {} (dso);

%\draw [Connection, bend left=65] (pros1) to node [midway, left, shift={(-0.25,0)}] {$\emptyset$MQ} (dso);
\draw [Connection, bend left=53] (pros2) to  (dso);
\draw [Connection, bend left=42] (pros3) to (dso);

\draw [Connection, bend right=0] (solver) to node [midway, below left] {Ethereum} (contract);
\draw [Connection, bend right=15] (dso) to (contract);
%\draw [Connection, bend right=0] (pros1) to node [midway, below left] {Ethereum} (contract);
\draw [Connection, bend right=0] (pros2) to (contract);
\draw [Connection, bend right=0] (pros3) to (contract);
\end{tikzpicture}%
%}
\caption{Implementation view of the \Platform. A private Ethereum network (used for testing purposes) is the decentralized computation platform running smart 
\ifExtended
contracts, and the other components interact with the network using the \texttt{geth} Ethereum client. The smart contract is implemented in Solidity, a high-level language for Ethereum.
\else
contracts.
\fi
}
\label{fig:components}
\end{figure}

\begin{figure}[t]
\centering
 \includegraphics[width=0.9\columnwidth]{BlockchainPaper-update.pdf}
    \caption{Data flow between actors of \Platform. %Information store is part of the blockchain.
        }
    \label{fig:tmp}
\end{figure}

Figure \ref{fig:components} shows the key actors of our transaction management platform,
while
Figure \ref{fig:tmp} describes the data flow between these actors.
A directory actor provides a mechanism to look up connection endpoints, including the address of a deployed smart contract. In our previous work, we  described how to create a decentralized directory service using distributed hash tables~\cite{riaps1}. Therefore, we do not describe the implementation of this service any further in this paper. 
%
Prosumers (i.e., resource providers and consumers) submit offers to the system using functions provided by the smart contract. These functions check the correctness of the offer and then store it in the smart contract. An optional mixer service can be used to obfuscate the identity of the prosumers \cite{serial17}. By generating new anonymous addresses at random periodically, they can prevent other entities from linking the anonymous addresses to their actual identities~\cite{Laszka17,serial17}, thereby keeping their activities private. A set of solvers (pre-configured with constraints and a utility function) can subscribe to smart-contract events, which provide the solvers with information about offers. Solvers run at a pre-configured frequency, compute an optimal resource allocation, and push the assignments into the distributed ledger via the smart contract. An external service director can then choose to frequently operate and finalize the solutions. That is, choose from a number of possible solutions that are available. Once a solution has been finalized, the information is received by the participants via events. 
The following subsections describe the transaction management platform in more detail.
\iffalse
\ad{We need to reinforce the idea that ethereum is just an implementation choice and we believe that in future a proof of stake algorithm should be used for consensus. It does away with wasteful computation and creates a negative incentive for miners to cheat.}
\fi
% Figure \ref{fig:tmp} describes the architecture of our framework. \Aron{Constraints are checked within both the smartcontract and the solver, but not in addition to them.} The orderbook and contracted solutions are stored in a distributed ledger. The automated billing settlement is handled by a smart contract (not described in this paper). \Aron{What is this ``market mechanism''? A collection of services?} The market mechanism is the most important aspect of this platform. It consists of four sub-modules (a) anonymizer/mixer - a cryptographic service that enables the external actors to participate in the market without compromising their privacy, (b) a solver - that is responsible for solving the optimization problem maximizing the configured utility function. Examples of different utility functions were described in the previous section. \Aron{?}The solver is responsible for storing potential solutions to the resource matching problem in the order book, (c) \Aron{Actually, the smart contract does this.} constraint checkers--they ensure the validity of the offers that are stored in the order book and finally (d) a decentralized smart contract that is responsible for finalizing the potential solutions proposed by the solvers. The smart contract is also responsible for running the constraint checkers and then registering the  offers in the \Aron{What is this order book?} order book.

%\Aron{This seems redundant since the following subsection describes this in more detail.}
%This architecture by design separates the solvers from the smart contract code. There are three reasons for this design decision. The first is that the computation resources required to solve a complex optimization problem are going to be prohibitive to be run within a smart contract. The second reason is that often the state-of-the-art smart-contract languages do not provide native support floating point computations, which are necessary for many solution approaches. The third reason is that this architecture enables us to support a `solver' market where multiple solvers can run in parallel and compete for identifying the best solution (in case they use heuristics to solve the optimization problem). Additionally, it enables us to tolerate solver failures.

\subsection{Scheduling}
\label{sec:scheduling}

Once the system is deployed,
providers and consumers will need to use it repeatedly for finding optimal resource allocations. 
For example, riders and drivers want to find optimal carpooling assignments every day, while users in an energy futures market want to find optimal energy trades every, e.g., 20 minutes.
Consequently, the platform has to gather offers and solve the resource allocation problem at regular time intervals.
Each one of these cycles is divided into two phases.
First, an \emph{offering phase}, in which providers and consumers can post new offers or cancel their existing offers (e.g., if they wish to change their offer based on changes in the market).
Second, a \emph{solving phase}, in which the resource allocation problem is solved for the posted (but not cancelled) offers.
At the end of the second phase, the assignments between providers and consumers are finalized based on the solution.
Then, a new cycle begins with an offering phase.

\subsection{Hybrid Solver Architecture}
\label{sec:solver}
The Resource Allocation Problem described in Section~\ref{sec:problem} can be solved by formulating it as an (integer) linear program (LP): feasibility constraints (Equations~\eqref{eq:feasable1} to~\eqref{eq:feasable4}) and constraint extensions (Section~\ref{sec:extConstr}) can all be formulated as linear inequalities, while the objective function (Equation~\eqref{eq:objective}) as well as the alternative objectives (Section~\ref{sec:extObj}) can be formulated as linear functions. Arguably, we could set up a solver actor that would receive offers from  prosumers, formulate a linear program, and use a state-of-the-art LP-solver (e.g., CPLEX~\cite{cplex2009v12}) to find an optimal solution. However, a simple N-to-1 architecture with N prosumers and 1 solver would suffer from the following problems: 
\begin{itemize}
    \item {\it Lack of trust in solver nodes:} Prosumers would need to trust that the solver is acting selflessly and is providing correct and optimal solutions. 
  %  \item {\it Lack of synchronization between prosumers and the solver:} Prosumers and the solver would have to coordinate the offering and solving phases over a  network. This could be done synchronously, by letting prosumers assume that messages are never lost and letting them actively wait for all messages to arrive in order. However, in practice, we have to allow the possibility of messages being lost and actors losing synchrony. 
    \item {\it Vulnerability of the transaction management platform:} A single solver would be a single point of failure. If it were faulty or compromised, the entire platform would be faulty or compromised.  %A solution will be to use multiple solvers. However, in that case it is important to achieve consensus between the solvers.
    \item {\it Data storage:} For the sake of auditability, information about past offers and allocations should remain available even in case of node failures. 
\end{itemize}

%(a) {\it lack of trust in solver nodes} - how can the prosumers trust that the solver is acting selflessly and is providing correct and optimal solutions.

%\Aron{I don't understand this sentence. What do you mean by online solutions?} If repeated over a time horizon, an integer linear program solver, such as CPLEX \cite{ref}, end up providing online solutions to the problem. However, there are primarily three problems that arise when we consider \Aron{What architecture?} this architecture (a) lack of trust in solver nodes, (b) asynchrony of the architecture, and (c) failure of the solver nodes.

A decentralized ledger with distributed information storage and consensus provided by blockchain solutions, such as Ethereum, is an obvious choice for ensuring the auditability of all events and providing distributed trust. However, computation is relatively expensive on blockchain-based distributed platforms\footnote{Further, Solidity, the preferred high-level language for Ethereum, currently lacks built-in support for certain features that would facilitate the implementation of an LP solver, such as floating-point arithmetics.}, solving the trading problem using a block\-chain-based smart contract would not be scalable in practice.
In light of this, we propose a \emph{hybrid implementation approach}, which combines the trustworthiness of blockchain-based smart contracts with the efficiency of more traditional computational platforms.

Thus, the key idea of our hybrid approach is to (1) use a high-performance computer to solve the computationally expensive linear program \emph{off-blockchain} and then (2) use a smart contract to record the solution \emph{on the blockchain}.
To implement this hybrid approach securely and reliably, we must address the following issues.
\begin{itemize}
\item Computation that is performed off-blockchain does not satisfy the auditability and security requirements that smart contracts do. Thus, the results of any off-blockchain computation must be verified %in some way 
by the smart contract before recording them on the blockchain.
\item Due to network disruptions and other errors (including deliberate denial-of-service attacks), the off-blockchain solver might fail to provide the smart contract with a solution on time (i.e., before assignments are supposed to be finalized). Thus, the smart contract must not be strongly coupled to the solver.
\item For the sake of reliability, the smart contract should accept solutions from multiple off-blockchain sources; however, these sources might provide different solutions.
Thus, the smart contract must be able to choose from multiple solutions (some of which may come from a compromised computer).
\end{itemize}

% Section 4.1
% Hybrid Approach for Matching:
% - N solvers (efficient but non-trustworthy platform) + 1 smart contract (trustworthy but not efficient)
% - protocol: each solver may efficiently find a matching and submit it to the smart contract, which selects the best feasible matching
% - trading problem: easy to verify the feasibility of a matching
%   * exact time complexity?
%   * additional constraints might not be easy to verify, depends on the specific trading problem (constraints mentioned above are all easy to verify)
% - workflow (i.e., sequence diagram)
% - system architecture

% Section 4.2
% Privacy:
% - anonymizing mixers and communication anonymity (e.g., onion routing)

### 2018-07-10 code/RIAPSDemo/cpp/Client.cc
RIAPS demo

@@ -1,0 +1,29 @@
+#include <Client.h>
+
+namespace transactiveenergy {
+   namespace components {
+      
+      Client::Client(_component_conf &config, riaps::Actor &actor) :
+      ClientBase(config, actor) {
+      }
+      
+      
+      void Client::OnGroupMessage(const riaps::groups::GroupId& groupId,
+      capnp::FlatArrayMessageReader& capnpreader, riaps::ports::PortBase* port){
+         
+      }
+      
+      Client::~Client() {
+         
+      }
+   }
+}
+
+riaps::ComponentBase *create_component(_component_conf &config, riaps::Actor &actor) {
+   auto result = new transactiveenergy::components::Client(config, actor);
+   return result;
+}
+
+void destroy_component(riaps::ComponentBase *comp) {
+   delete comp;
+}

### 2018-07-10 code/RIAPSDemo/cpp/DSOBase.cc

@@ -1,0 +1,40 @@
+//
+// Auto-generated by edu.vanderbilt.riaps.generator.ComponenetGenerator.xtend
+//
+#include <DSOBase.h>
+
+namespace transactiveenergy {
+   namespace components {
+      
+      DSOBase::DSOBase(_component_conf &config, riaps::Actor &actor) : ComponentBase(config, actor) {
+         
+      }
+      
+      void DSOBase::DispatchMessage(capnp::FlatArrayMessageReader* capnpreader, riaps::ports::PortBase *port,std::shared_ptr<riaps::MessageParams> params) {
+         auto portName = port->GetPortName();
+         if (portName == PORT_REP_CONTRACTADDR) {
+            auto reader = capnpreader->getRoot<ReqAddr>();
+            OnContractAddr(reader, port);
+         }
+         
+         if (portName == PORT_TIMER_FINALIZER) {
+            OnFinalizer(port);
+         }
+         
+      }
+      
+      void DSOBase::DispatchInsideMessage(zmsg_t* zmsg, riaps::ports::PortBase* port) {
+         //empty the header
+      }
+      
+      bool DSOBase::SendContractAddr(capnp::MallocMessageBuilder& messageBuilder,
+      RepAddr::Builder& message) {
+         std::cout<< "DSOBase::SendContractAddr()"<< std::endl;
+         return SendMessageOnPort(messageBuilder, PORT_REP_CONTRACTADDR);
+      }
+      
+      DSOBase::~DSOBase() {
+         
+      }
+   }
+}

### 2018-07-10 code/RIAPSDemo/cpp/TraderBase.cc

@@ -1,0 +1,54 @@
+//
+// Auto-generated by edu.vanderbilt.riaps.generator.ComponenetGenerator.xtend
+//
+#include <TraderBase.h>
+
+namespace transactiveenergy {
+   namespace components {
+      
+      TraderBase::TraderBase(_component_conf &config, riaps::Actor &actor) : ComponentBase(config, actor) {
+         
+      }
+      
+      void TraderBase::DispatchMessage(capnp::FlatArrayMessageReader* capnpreader, riaps::ports::PortBase *port,std::shared_ptr<riaps::MessageParams> params) {
+         auto portName = port->GetPortName();
+         
+         if (portName == PORT_TIMER_POLLER) {
+            OnPoller(port);
+         }
+         
+         if (portName == PORT_TIMER_POST) {
+            OnPost(port);
+         }
+         
+      }
+      
+      void TraderBase::DispatchInsideMessage(zmsg_t* zmsg, riaps::ports::PortBase* port) {
+         //empty the header
+      }
+      
+      bool TraderBase::SendContractAddr(capnp::MallocMessageBuilder &messageBuilder,
+      ReqAddr::Builder &message) {
+         //std::cout<< "TraderBase::SendContractAddr()"<< std::endl;
+         return SendMessageOnPort(messageBuilder, PORT_REQ_CONTRACTADDR);
+      }
+      
+      bool TraderBase::RecvContractAddr(RepAddr::Reader &message) {
+         //std::cout<< "TraderBase::RecvContractAddr()"<< std::endl;
+         auto port = GetRequestPortByName(PORT_REQ_CONTRACTADDR);
+         if (port == NULL) return false;
+         
+         capnp::FlatArrayMessageReader* messageReader;
+         
+         if (port->Recv(&messageReader)){
+            message = messageReader->getRoot<RepAddr>();
+            return true;
+         }
+         return false;
+      }
+      
+      TraderBase::~TraderBase() {
+         
+      }
+   }
+}

### 2018-07-10 code/RIAPSDemo/cpp/include/ClientBase.h

@@ -1,0 +1,35 @@
+//
+// Auto-generated by edu.vanderbilt.riaps.generator.ComponenetGenerator.xtend
+//
+
+#ifndef RIAPS_CORE_CLIENT_H
+#define RIAPS_CORE_CLIENT_H
+
+#include "componentmodel/r_componentbase.h"
+#include "ReqAddr.capnp.h"
+#include "RepAddr.capnp.h"
+
+// Name of the ports from the model file
+#define PORT_REQ_DSO "dso"
+
+namespace transactiveenergy {
+   namespace components {
+      
+      class ClientBase : public riaps::ComponentBase {
+         
+         public:
+         ClientBase(_component_conf &config, riaps::Actor &actor);
+         
+         bool SendDso(capnp::MallocMessageBuilder&    messageBuilder,
+         ReqAddr::Builder& message);
+         
+         bool RecvDso(RepAddr::Reader &message);
+         
+         virtual ~ClientBase();
+         protected:
+         virtual void DispatchMessage(capnp::FlatArrayMessageReader* capnpreader, riaps::ports::PortBase *port,std::shared_ptr<riaps::MessageParams> params=nullptr );
+         virtual void DispatchInsideMessage(zmsg_t* zmsg, riaps::ports::PortBase* port);
+      };
+   }
+}
+#endif //RIAPS_CORE_CLIENT_H

### 2018-07-10 code/RIAPSDemo/cpp/include/DSOBase.h

@@ -1,0 +1,39 @@
+//
+// Auto-generated by edu.vanderbilt.riaps.generator.ComponenetGenerator.xtend
+//
+
+#ifndef RIAPS_CORE_DSO_H
+#define RIAPS_CORE_DSO_H
+
+#include "componentmodel/r_componentbase.h"
+#include "ReqAddr.capnp.h"
+#include "RepAddr.capnp.h"
+
+// Name of the ports from the model file
+#define PORT_REP_CONTRACTADDR "contractAddr"
+#define PORT_TIMER_FINALIZER "finalizer"
+
+namespace transactiveenergy {
+   namespace components {
+      
+      class DSOBase : public riaps::ComponentBase {
+         
+         public:
+         DSOBase(_component_conf &config, riaps::Actor &actor);
+         
+         virtual void OnContractAddr(const ReqAddr::Reader &message,
+         riaps::ports::PortBase *port)=0;
+         
+         virtual bool SendContractAddr(capnp::MallocMessageBuilder& messageBuilder,
+         RepAddr::Builder& message);
+         
+         virtual void OnFinalizer(riaps::ports::PortBase *port)=0;
+         
+         virtual ~DSOBase();
+         protected:
+         virtual void DispatchMessage(capnp::FlatArrayMessageReader* capnpreader, riaps::ports::PortBase *port,std::shared_ptr<riaps::MessageParams> params=nullptr );
+         virtual void DispatchInsideMessage(zmsg_t* zmsg, riaps::ports::PortBase* port);
+      };
+   }
+}
+#endif //RIAPS_CORE_DSO_H

### 2018-07-10 code/RIAPSDemo/cpp/include/Recorder.h

@@ -1,0 +1,33 @@
+//
+// Auto-generated by edu.vanderbilt.riaps.generator.ComponenetGenerator.xtend
+//
+#ifndef RIAPS_FW_RECORDER_H
+#define RIAPS_FW_RECORDER_H
+
+#include "RecorderBase.h"
+
+namespace transactiveenergy {
+   namespace components {
+      
+      class Recorder : public RecorderBase {
+         
+         public:
+         
+         Recorder(_component_conf &config, riaps::Actor &actor);
+         
+         
+         virtual void OnPoller(riaps::ports::PortBase *port);
+         
+         void OnGroupMessage(const riaps::groups::GroupId& groupId, capnp::FlatArrayMessageReader& capnpreader, riaps::ports::PortBase* port);
+         
+         virtual ~Recorder();
+         
+      };
+   }
+}
+
+extern "C" riaps::ComponentBase* create_component(_component_conf&, riaps::Actor& actor);
+extern "C" void destroy_component(riaps::ComponentBase*);
+
+
+#endif //RIAPS_FW_RECORDER_H

### 2018-07-10 code/RIAPSDemo/cpp/include/Trader.h

@@ -1,0 +1,31 @@
+//
+// Auto-generated by edu.vanderbilt.riaps.generator.ComponenetGenerator.xtend
+//
+#ifndef RIAPS_FW_TRADER_H
+#define RIAPS_FW_TRADER_H
+
+#include "TraderBase.h"
+
+namespace transactiveenergy {
+   namespace components {
+      
+      class Trader : public TraderBase {
+         
+         public:
+         
+         Trader(_component_conf &config, riaps::Actor &actor);
+         
+         
+         void OnGroupMessage(const riaps::groups::GroupId& groupId, capnp::FlatArrayMessageReader& capnpreader, riaps::ports::PortBase* port);
+         
+         virtual ~Trader();
+         
+      };
+   }
+}
+
+extern "C" riaps::ComponentBase* create_component(_component_conf&, riaps::Actor& actor);
+extern "C" void destroy_component(riaps::ComponentBase*);
+
+
+#endif //RIAPS_FW_TRADER_H

### 2018-07-10 code/RIAPSDemo/pkg/libs/EthereumClient.py

@@ -1,0 +1,139 @@
+import pycurl
+import json
+import logging
+from io import BytesIO
+from time import time, sleep
+from threading import Thread, RLock
+
+from libs.config import * 
+
+CHECK_INTERVAL = 1 # check for receipts every second
+PENDING_TIMEOUT = 120 # if a transaction has been pending for more than 120 seconds, submit it again
+CLIENT_TIMEOUT = 600 # if a transaction has been stuck for more than 600 seconds, restart the client
+
+class EthereumClient:
+  def __init__(self, ip, port):
+    self.ip = ip
+    self.port = port
+    self.waiting = [] # transactions which have not been submitted
+    self.pending = [] # transactions which have been submitted but not yet mined
+    self.lock = RLock()
+    thread = Thread(target=self.__run)
+    thread.start()
+    
+  def __run(self):
+    while True:
+      sleep(CHECK_INTERVAL) # wait one second
+      current_time = time()
+      with self.lock:
+        for trans in self.pending + self.waiting:
+          if current_time > trans['request_time'] + CLIENT_TIMEOUT: # transaction has been stuck for a long time
+            self.__restart_client()
+        for trans in list(self.pending): # iterate over a copy so that we can remove items
+          receipt = self.command("eth_getTransactionReceipt", params=[trans['hash']])
+          if receipt is not None: # transaction receipt is available
+            self.pending.remove(trans)
+            logging.debug("Transaction {} has been mined.".format(trans['data']))
+          elif current_time > trans['submission_time'] + PENDING_TIMEOUT: # timeout for pending transaction
+            self.pending.remove(trans)
+            logging.info("Pending transaction {} has timed out, resubmitting...".format(trans['data']))
+            self.__submit_trans(trans)
+          # otherwise, wait more for this transaction
+        for trans in list(self.waiting): # iterate over a copy so that we can remove items
+          self.waiting.remove(trans)
+          self.__submit_trans(trans) # resubmit
+          
+  def __restart_client(self):
+    logging.info("Restarting the client...")
+    # TODO: writeme
+    # TODO: handle filter re-creation?
+            
+  def __submit_trans(self, trans):
+    try:
+      trans_hash = self.command("eth_sendTransaction", params=[{
+        'from': trans['from'], 
+        'data': trans['data'], 
+        'to': trans['to'], 
[…]

### 2018-07-10 code/RIAPSDemo/pkg/libs/Grafana/config.py

@@ -1,0 +1,30 @@
+'''
+Created on Jan 29, 2018
+'''
+import sys
+import os,signal
+from os.path import join
+import argparse
+import logging
+import logging.config
+import configparser
+
+class Config(object):
+    '''
+    Configuration database for RIAPS tools
+    Including logging configuration
+    '''
+
+    #grafana Setup
+    INFLUX_DBASE_HOST='172.21.20.34'
+    INFLUX_DBASE_PORT=8086
+    INFLUX_DBASE_USER='riaps'
+    INFLUX_DBASE_PASSWORD = 'riaps'
+    INFLUX_DBASE_NAME = 'RIAPSEnergyMarket'
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        pass

### 2018-07-10 code/RIAPSDemo/pkg/libs/config.py

@@ -1,0 +1,33 @@
+MINER='172.21.20.34'
+PORT=10000
+
+DSO_ADDRESS = 'tcp://172.21.130.248:10001'
+DATA_PATH = "libs/TenNodes10x/"
+TRANSACTION_GAS = "0x100000000"
+BYTECODE = "0x60606040526000600360006101000a81548167ffffffffffffffff021916908367ffffffffffffffff1602179055506000600560006101000a81548167ffffffffffffffff021916908367ffffffffffffffff1602179055506000600760006101000a81548167ffffffffffffffff021916908367ffffffffffffffff1602179055507fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff600760086101000a81548167ffffffffffffffff021916908360070b67ffffffffffffffff16021790555034156100d957600080fd5b611c64806100e86000396000f300606060405260043610610083576000357c0100000000000000000000000000000000000000000000000000000000900463ffffffff168063359bc19e1461008857806340d599c0146100b55780637f49f33c146101085780638375ced0146101355780639e52b99f1461019b578063a543c01814610214578063c37df44e14610254575b600080fd5b341561009357600080fd5b6100b3600480803567ffffffffffffffff169060200190919050506102ba565b005b34156100c057600080fd5b610106600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff16906020019091905050610729565b005b341561011357600080fd5b610133600480803567ffffffffffffffff169060200190919050506107a8565b005b341561014057600080fd5b610199600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff16906020019091905050610934565b005b34156101a657600080fd5b610212600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff16906020019091905050610ba3565b005b341561021f57600080fd5b610252600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff16906020019091905050611910565b005b341561025f57600080fd5b6102b8600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff169060200190919050506119c9565b005b600080600080600060109054906101000a900467ffffffffffffffff1667ffffffffffffffff168567ffffff
[…]

### 2018-07-10 code/RIAPSDemo/pkg/test.py

@@ -1,0 +1,22 @@
+from influxdb import InfluxDBClient
+from influxdb.client import InfluxDBClientError
+from libs.Grafana.config import Config
+from libs.Grafana.dbase import Database
+
+from time import time, sleep
+import datetime
+
+print(time())
+
+dbase = Database()
+
+tag_dict={ "name" : "test" }
+now = int(time())
+print(now)
+
+dbase.post(now=now, tag_dict=tag_dict, seriesName='testSeries', value=25)
+
+now = datetime.datetime.now()
+print(now)
+
+dbase.post(now=now, tag_dict=tag_dict, seriesName='testSeries', value=30)

### 2018-07-10 code/RIAPSDemo/python/libs/LinearProgramCplex.py

@@ -1,0 +1,41 @@
+import logging
+import libs.cplex as cplex
+
+from libs.LinearProgram import LinearProgram
+
+class LinearProgramCplex(LinearProgram):
+  def __init__(self):
+    super(LinearProgramCplex, self).__init__()
+
+  def solve(self):
+    logging.info("Solving linear program with {} variables and {} constraints...".format(len(self.variables), len(self.constraints)))
+    (A, b, c) = self.construct()
+    
+    A_cplex = []
+    for row in A:
+      A_cplex.append([list(range(len(self.variables))), row])    
+    
+    prob = cplex.Cplex()
+    
+    prob.set_log_stream(None)
+    #prob.set_error_stream(None)
+    #prob.set_warning_stream(None)
+    prob.set_results_stream(None)
+
+    prob.objective.set_sense(prob.objective.sense.minimize)
+    prob.variables.add(obj=c)
+    prob.linear_constraints.add(lin_expr=A_cplex, senses=['L'] * len(self.constraints), rhs=b)
+    prob.solve()
+    x = prob.solution.get_values()
+#    logging.info("Solver output: message = '{}', fun = {}, status = {}".format(result.message, result.fun, result.status))
+    solution = {name: x[var] for (name, var) in self.variables.items()}
+    objective = prob.solution.get_objective_value()
+    return (solution, objective)
+
+if __name__ == "__main__":
+  program = LinearProgramCplex()
+  program.set_objective({"x1": -1, "x2": -1})
+  program.add_constraint({"x1" : 1}, 2)
+  program.add_constraint({"x2" : 1}, 1)
+  print(program.solve())
+

### 2018-07-10 code/RIAPSDemo/python/libs/MatchingSolver.py

@@ -1,0 +1,130 @@
+import logging
+
+from libs.Microgrid import Microgrid
+from libs.LinearProgramCplex import LinearProgramCplex 
+
+class Offer:
+  def __init__(self, ID, prosumer, startTime, endTime, energy):
+    self.ID = ID
+    self.prosumer = prosumer 
+    self.startTime = startTime
+    self.endTime = endTime
+    self.energy = energy
+    
+  def matchable(self, offer):
+    return (self.endTime >= offer.startTime) and (self.startTime <= offer.endTime)
+    
+  def intersection(self, offer):
+    if not self.matchable(offer):
+      return []
+    start = max(self.startTime, offer.startTime)
+    end = min(self.endTime, offer.endTime)
+    return list(range(start, end + 1))  
+
+class MatchingSolver:
+  def __init__(self, microgrid):
+    self.microgrid = microgrid
+    
+  def solve(self, buying_offers, selling_offers, finalized=-1, lp_solver=LinearProgramCplex):
+    program = lp_solver()
+    variables = {}
+    prosumer_prod = {}
+    prosumer_cons = {}
+    feeder_prod = {f: {} for f in self.microgrid.feeders}
+    feeder_cons = {f: {} for f in self.microgrid.feeders}
+    for b in range(len(buying_offers)):
+      for s in range(len(selling_offers)):
+        b_offer = buying_offers[b]
+        s_offer = selling_offers[s]
+        for t in b_offer.intersection(s_offer):
+          if t > finalized: # skip time intervals that have been finalized
+            variable = {'s': s_offer, 'b': b_offer, 't': t}
+            varname = 'p_{}_{}_{}'.format(s, b, t)
+            variables[varname] = variable
+            # prosumer production
+            try:
+              prosumer_prod[s_offer].append(varname)
+            except KeyError:
+              prosumer_prod[s_offer] = [varname]
+            # prosumer consumption
+            try:
+              prosumer_cons[b_offer].append(varname)
+            except KeyError:
+              prosumer_cons[b_offer] = [varname]
+            # feeder production
+            s_feeder = self.microgrid.prosumer_feeder[s_offer.prosumer]
+            if t not in feeder_prod[s_feeder]:
+              feeder_prod[s_feeder][t] = [varname]
+            else:
[…]

### 2018-07-10 code/RIAPSDemo/python/libs/config.py

@@ -1,0 +1,33 @@
+MINER='192.168.88.235'
+PORT=10000
+
+DSO_ADDRESS = 'tcp://192.168.88.235:10001'
+DATA_PATH = "libs/TenNodes10x/"
+TRANSACTION_GAS = "0x100000000"
+BYTECODE = "0x60606040526000600360006101000a81548167ffffffffffffffff021916908367ffffffffffffffff1602179055506000600560006101000a81548167ffffffffffffffff021916908367ffffffffffffffff1602179055506000600760006101000a81548167ffffffffffffffff021916908367ffffffffffffffff1602179055507fffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff600760086101000a81548167ffffffffffffffff021916908360070b67ffffffffffffffff16021790555034156100d957600080fd5b611c64806100e86000396000f300606060405260043610610083576000357c0100000000000000000000000000000000000000000000000000000000900463ffffffff168063359bc19e1461008857806340d599c0146100b55780637f49f33c146101085780638375ced0146101355780639e52b99f1461019b578063a543c01814610214578063c37df44e14610254575b600080fd5b341561009357600080fd5b6100b3600480803567ffffffffffffffff169060200190919050506102ba565b005b34156100c057600080fd5b610106600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff16906020019091905050610729565b005b341561011357600080fd5b610133600480803567ffffffffffffffff169060200190919050506107a8565b005b341561014057600080fd5b610199600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff16906020019091905050610934565b005b34156101a657600080fd5b610212600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff16906020019091905050610ba3565b005b341561021f57600080fd5b610252600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff16906020019091905050611910565b005b341561025f57600080fd5b6102b8600480803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff1690602001909190803567ffffffffffffffff169060200190919050506119c9565b005b600080600080600060109054906101000a900467ffffffffffffffff1667ffffffffffffffff168567fffff
[…]

### 2018-07-10 code/RIAPSDemo/python/libs/cplex/_internal/_procedural.py

@@ -1,0 +1,3236 @@
+# --------------------------------------------------------------------------
+# File: _procedural.py
+# ---------------------------------------------------------------------------
+# Licensed Materials - Property of IBM
+# 5725-A06 5725-A29 5724-Y48 5724-Y49 5724-Y54 5724-Y55 5655-Y21
+# Copyright IBM Corporation 2008, 2017. All Rights Reserved.
+#
+# US Government Users Restricted Rights - Use, duplication or
+# disclosure restricted by GSA ADP Schedule Contract with
+# IBM Corp.
+# ------------------------------------------------------------------------
+
+from __future__ import print_function
+
+from contextlib import contextmanager
+from random import randrange
+import signal
+
+from . import _list_array_utils as LAU
+from . import _pycplex as CR
+
+from ._constants import *
+from ..exceptions import CplexSolverError, CplexError, ErrorChannelMessage
+
+from .. import six
+from ..six.moves import map, zip
+
+import threading
+
+default_encoding     = "UTF-8"
+cpx_default_encoding = "UTF-8"
+
+def cpx_decode(my_str, enc):
+    if my_str is None:
+        return my_str
+    elif isinstance(my_str, six.binary_type):
+        if enc == cpx_default_encoding:
+            return my_str
+        else:
+            return six.text_type(my_str, enc).encode(cpx_default_encoding)
+    else:
+        assert isinstance(my_str, six.text_type)
+        return my_str.encode(cpx_default_encoding)
+
+def cpx_decode_noop3(my_str, enc):
+    if six.PY2:
+        return cpx_decode(my_str, enc)
+    else:
+        return my_str
+
+def _cpx_encode_py2(my_str, enc):
+    assert six.PY2
+    if enc == cpx_default_encoding:
+        return my_str
+    else:
+        return six.text_type(my_str, cpx_default_encoding).encode(enc)
+
+def _cpx_encode_py3(my_str, enc):
+    assert not six.PY2
+    if isinstance(my_str, six.binary_type):
+        return my_str.decode(enc)
+    else:
+        assert isinstance(my_str, six.text_type)
+        if enc == cpx_default_encoding:
+            return my_str
+        else:
+            return my_str.encode(cpx_default_encoding).decode(enc)
+
+def cpx_encode_noop3(my_str, enc):
+    if six.PY2:
+        return cpx_encode(my_str, enc)
+    else:
+        return my_str
+
+def cpx_encode(my_str, enc):
+    if six.PY2:
[…]

### 2018-07-10 code/RIAPSDemo/tmp/TransactiveEnergy/Grafana/config.py

@@ -1,0 +1,30 @@
+'''
+Created on Jan 29, 2018
+'''
+import sys
+import os,signal
+from os.path import join
+import argparse
+import logging
+import logging.config
+import configparser
+
+class Config(object):
+    '''
+    Configuration database for RIAPS tools
+    Including logging configuration
+    '''
+
+    #grafana Setup
+    INFLUX_DBASE_HOST='192.168.88.242'
+    INFLUX_DBASE_PORT=8086
+    INFLUX_DBASE_USER='riaps'
+    INFLUX_DBASE_PASSWORD = 'riaps'
+    INFLUX_DBASE_NAME = 'EnergyMarket'
+
+
+    def __init__(self):
+        '''
+        Constructor
+        '''
+        pass

### 2018-07-10 code/RIAPSDemo/tmp/TransactiveEnergy/Microgrid.py

@@ -1,0 +1,8 @@
+class Microgrid:
+  def __init__(self, interval_length, C_ext, C_int, feeders, prosumer_feeder):
+    self.interval_length = interval_length
+    self.C_ext = C_ext
+    self.C_int = C_int
+    self.feeders = feeders
+    self.prosumer_feeder = prosumer_feeder
+

### 2018-07-10 code/RIAPSDemo/tmp/TransactiveEnergy/Trader.py

@@ -1,0 +1,61 @@
+#Trader.py
+from riaps.run.comp import Component
+import os
+import logging
+
+class Trader(Component):
+    def __init__(self):
+        super(Trader, self).__init__()	        
+        self.pid = os.getpid()
+        self.logger.info("(PID %s) - starting Trader",str(self.pid))
+        
+        self.prosumer_id = 101
+        self.net_production = net_production
+        self.selling_offers = set()
+        self.buying_offers = set()
+        self.connected =0
+        
+        self.dbase = Database()
+        self.role = None
+        self.roleID = 0
+        #self.grid = zmq.Context().socket(zmq.PUB)
+        #self.grid.bind('tcp://127.0.0.1:2000')
+        self.interval_asks = {}
+        self.interval_bids = {}
+
+        
+
+    def on_contractAddr(self):
+        req = self.contractAddr.recv_pyobj()
+        self.logger.info("PID (%s) - on_contractAddr():%s",str(self.pid),str(req))
+        
+        self.epoch = time() - req['time']
+        self.contract_address = req['contract']
+        self.logger.info("Contract address: " + self.contract_address)     
+        self.logger.info("Setting up connection to Ethereum client...")
+        client = EthereumClient(ip=MINER, port=PORT)
+        self.account = client.accounts()[0] # use the first owned address
+        self.logger.info("Creating contract object...")
+        self.contract = MatchingContract(client, self.contract_address)
+        self.contract.registerProsumer(self.account, prosumer_id, PROSUMER_FEEDER[prosumer_id])
+
+
+    def on_poller(self):
+        now = self.poller.recv_pyobj()
+        self.logger.info('PID(%s) - on_poller(): %s',str(self.pid),str(now))
+        
+        if self.connected == 0:
+            self.query_contract_address()
+            if self.contract:
+                self.connected =1 
+    
+    def __destroy__(self):			
+        self.logger.info("(PID %s) - stopping Trader",str(self.pid))   	        	        
+
+
+    def query_contract_address(self):
+        msg = {
+            'request': "query_contract_address"
+        }
+        self.logger.info(msg)
+        self.contractAddr.send_pyobj(msg)      

### 2018-07-13 docs/papers/iotdi2018/feeder.tex
update

@@
 ]
-\addplot[no markers, solid, greenline, semithick] table[x expr=\coordindex, y=WithoutBattery,  comment chars={\%}, col sep=comma] {diagrams/interval-energy-traded.csv};
-\addlegendentry{Total energy traded (Test A)};
-\addplot[no markers, solid, blackLine, semithick] table[x expr=\coordindex, y=WithBattery5,  comment chars={\%}, col sep=comma] {diagrams/interval-energy-traded.csv};
-\addlegendentry{Total energy traded (Test C)};
-\addplot[no markers, solid, goldLine, semithick] table[x expr=\coordindex, y=WithBattery12,  comment chars={\%}, col sep=comma] {diagrams/interval-energy-traded.csv};
-\addlegendentry{Total energy traded (Test D)};
+%\addplot[no markers, solid, greenline, semithick] table[x expr=\coordindex, y=WithoutBattery,  comment chars={\%}, col sep=comma] {diagrams/interval-energy-traded.csv};
+%\addlegendentry{Total energy traded (Test A)};
+%\addplot[no markers, solid, blackLine, semithick] table[x expr=\coordindex, y=WithBattery5,  comment chars={\%}, col sep=comma] {diagrams/interval-energy-traded.csv};
+%\addlegendentry{Total energy traded (Test C)};
+%\addplot[no markers, solid, goldLine, semithick] table[x expr=\coordindex, y=WithBattery12,  comment chars={\%}, col sep=comma] {diagrams/interval-energy-traded.csv};
+%\addlegendentry{Total energy traded (Test D)};
 \addplot[no markers, solid, blueLine, semithick] table[x expr=\coordindex, y=TotalProduction, comment chars={\%}] {diagrams/TotalProductionConsumption.csv};
